\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{result}{Literature Answer}

\title{Negative Literature Answer to the Classical Schreier\\
Uniform $\lambda$-Property Question}
\author{FA/Banach run status packet}
\date{19 July 2026}

\begin{document}
\maketitle

\section*{Status}

\texttt{literature\_already\_answered (classical Schreier subquestion)}.
This note records an exact answer by a separate later paper; it is not an
original result of the run.

\section*{Original question}

Antunes, Beanland, and Chu ask on page 9 of
\emph{On the geometry of higher order Schreier spaces}
\cite{ABC}, immediately before Theorem 3.1, whether the classical Schreier
space $X_{\mathcal S_1}$ has the uniform $\lambda$-property.  Their same
paragraph separately asks about the ordinary $\lambda$-property of
$X_{\mathcal F}$ for every regular family $\mathcal F$.

\section*{Supporting answer}

Beanland and Chu explicitly state that their first main theorem solves the
problem restated in \cite{ABC}.

\begin{result}[Beanland--Chu, Theorem 1.1]
The classical Schreier space $X_{\mathcal S_1}$ does not have the uniform
$\lambda$-property.
\end{result}

In Section 3 of \cite{BC}, they construct, for sufficiently large $n$, unit
vectors $x_n$ and show that every extremal decomposition
\[
  x_n=\lambda e+(1-\lambda)y,
  \qquad e\in E(X_{\mathcal S_1}),\quad y\in Ba(X_{\mathcal S_1}),
\]
satisfies
\[
  \lambda\leq \frac{n+1}{n^2}.
\]
The upper bound tends to zero.  Hence no positive constant can uniformly
lower-bound the $\lambda$-function on the unit ball.  Theorem 1.2 of the same
paper also gives the negative answer for the dual space.

\section*{Scope limitations}

This answer clears only the classical $X_{\mathcal S_1}$ uniform-property
question.  It does not answer the broader regular-family question in the same
source paragraph.  The supporting paper lists uniformity for higher-order
Schreier spaces and their duals as future research and conjectures a negative
answer.

\section*{Verification}

The source question is on page 9 of arXiv:1903.03492.  The answer is Theorem
1.1 on page 1 of arXiv:1904.10384, with proof on pages 4--6.  The answer paper
names the earlier paper and says that Theorem 1.1 solves the problem restated
there.  The sources are distinct and the answer paper was posted later.
An exact-id and keyword search found no pre-existing run packet for this
question.

\begin{thebibliography}{9}

\bibitem{ABC}
L. Antunes, K. Beanland, and H. V. Chu,
\emph{On the geometry of higher order Schreier spaces},
arXiv:1903.03492.

\bibitem{BC}
K. Beanland and H. V. Chu,
\emph{The Schreier space does not have the uniform $\lambda$-property},
Proc. Amer. Math. Soc. 149 (2021), 5131--5137;
arXiv:1904.10384; DOI: \href{https://doi.org/10.1090/proc/14766}{10.1090/proc/14766}.

\end{thebibliography}

\end{document}

