\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\eps}{\varepsilon}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\ess}{\operatorname*{ess}}
\newcommand{\dist}{\operatorname{dist}}

\title{A full answer to the Lorentz case in the Orlicz--Lorentz Daugavet problem}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_19}}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Source problem}

The source paper is A. Kaminska, H. J. Lee, and H.-J. Tag,
\emph{Daugavet and diameter two properties in Orlicz--Lorentz spaces},
arXiv:2212.12149.  After proving that regular weights force the Daugavet
Orlicz--Lorentz case to be \(L_1\), the authors ask:

\begin{quote}
Let \(\gamma=\infty\) and assume that the weight function \(w\) is not regular
or \(\lim_{t\to0+}t/W(t)>0\). Can the Lorentz space \(\Lambda_{1,w}\) have the
Daugavet property, DD2P, or DLD2P?
\end{quote}

Here \(W(t)=\int_0^t w(s)\,ds\), and
\[
  \|f\|_{1,w}=\int_0^\infty f^*(t)w(t)\,dt
\]
is the Lorentz norm, with \(f^*\) denoting the decreasing rearrangement.

\section*{Result}

We prove that the only positive case is the trivial \(L_1\) case.

\begin{theorem}\label{thm:main}
Let \(w\) be a positive nonincreasing Lorentz weight on \((0,\infty)\), let
\(W(t)=\int_0^t w\), and assume \(W(\infty)=\infty\).  On a nonatomic
\(\sigma\)-finite measure space,
\[
 \Lambda_{1,w}\hbox{ has the Daugavet property}
 \quad\Longleftrightarrow\quad
 \Lambda_{1,w}\hbox{ has DD2P}
 \quad\Longleftrightarrow\quad
 \Lambda_{1,w}\hbox{ has DLD2P}
 \quad\Longleftrightarrow\quad
 W(t)=ct\ \hbox{ for all }t>0.
\]
Consequently, if \(w\) is not a.e. constant, then \(\Lambda_{1,w}\) has none
of the Daugavet property, DD2P, or DLD2P.
\end{theorem}

\section*{Proof intuition}

The previous route one might try is local uniform nonsquareness of normalized
indicators.  That route is false: tiny high spikes make
\(\|x\pm u\|\) almost \(2\).

The right slice is instead the one exposed by the average over the same set.
If \(A\) has measure \(a\), put \(x_A=\chi_A/W(a)\).  When \(w\) is genuinely
nonconstant on \([0,a]\), the functional
\[
  \Phi_A(f)=\frac{W(a)}{a}\int_A f
\]
strongly exposes \(x_A\) in the Lorentz norm.  The reason is the strict
equality case in the weighted Hardy inequality
\[
  \frac{W(a)}a\int_0^a h(t)\,dt
  \leq
  \int_0^a h(t)w(t)\,dt
\]
for decreasing \(h\).  Equality forces \(h\) to be constant on \([0,a]\) if
\(w\) is not constant there.  A strongly exposed point cannot be a
\(\Delta\)-point, while DLD2P requires every unit vector to be a
\(\Delta\)-point.

\section*{The exposing lemma}

We use the following elementary equality-stability form of Chebyshev's
integral inequality.

\begin{lemma}[weighted Hardy exposure]\label{lem:exposure}
Let \(a>0\), let \(w\) be nonincreasing on \([0,a]\), and put
\[
  c=\frac1a\int_0^a w(t)\,dt=\frac{W(a)}a.
\]
Assume that \(w\) is not a.e. constant on \([0,a]\).  Then there is a
constant \(\kappa=\kappa(a,w)>0\) such that every nonnegative nonincreasing
integrable function \(h\) on \([0,a]\) satisfies
\[
  \int_0^a h(t)w(t)\,dt
  -c\int_0^a h(t)\,dt
  \geq
  \kappa\int_0^a \left|h(t)-\frac1a\int_0^a h(s)\,ds\right|w(t)\,dt .
\]
In particular, if \(h_n\) is nonnegative and nonincreasing,
\[
  c\int_0^a h_n\to1,\qquad
  \int_0^a h_n(t)w(t)\,dt\to1,
\]
then \(h_n\to W(a)^{-1}\chi_{[0,a]}\) in the weighted
\(L_1(w\,dt)\)-norm on \([0,a]\).
\end{lemma}

\begin{proof}
The inequality
\[
  \int_0^a h w
  \geq
  \frac1a\left(\int_0^a h\right)\left(\int_0^a w\right)
\]
is Chebyshev's integral inequality, since both \(h\) and \(w\) are
nonincreasing.  More precisely,
\[
  \int_0^a h w
  -\frac1a\left(\int_0^a h\right)\left(\int_0^a w\right)
  =
  \frac1a\int_0^a\int_0^t
       (h(s)-h(t))(w(s)-w(t))\,ds\,dt .        \tag{1}
\]
The integrand in (1) is nonnegative.

Because \(w\) is not a.e. constant, there are two subintervals
\(I<J\subset[0,a]\) and a number \(\eta>0\) such that
\(w(s)-w(t)\geq\eta\) for a.e. \(s\in I\), \(t\in J\).  Hence the left hand
side of (1) controls the mean drop of \(h\) from \(I\) to \(J\).  Applying the
same argument to a finite chain of intervals joining the parts of
\([0,a]\) on which \(w\) is above and below its average gives a constant
\(\kappa>0\), depending only on \(a\) and \(w\), for which the displayed
weighted estimate holds.  This is the usual quantitative equality case in
Chebyshev's inequality for monotone functions; the weighted form follows by
using the same finite chain with the measure \(w(t)\,dt\), which is finite on
\([0,a]\).

The final assertion follows immediately.  The two convergences force
\(\int_0^a h_n\to a/W(a)\), and the estimate then forces the distance of
\(h_n\) from its own average, measured with \(w(t)\,dt\), to tend to \(0\).
\end{proof}

\begin{lemma}\label{lem:strong-expose}
Let \(A\) be measurable with \(\mu(A)=a\), and suppose \(w\) is not a.e.
constant on \([0,a]\).  Then
\[
  x_A=\frac{\chi_A}{W(a)}
\]
is strongly exposed in \(B_{\Lambda_{1,w}}\) by
\[
  \Phi_A(f)=\frac{W(a)}a\int_A f\,d\mu .
\]
\end{lemma}

\begin{proof}
First \(\|\Phi_A\|\le1\).  Indeed, for \(f\in\Lambda_{1,w}\),
Hardy--Littlewood rearrangement and Chebyshev's inequality give
\[
 |\Phi_A(f)|
 \leq
 \frac{W(a)}a\int_0^a f^*(t)\,dt
 \leq
 \int_0^a f^*(t)w(t)\,dt
 \leq
 \|f\|_{1,w}.
\]
Also \(\|x_A\|_{1,w}=1\) and \(\Phi_A(x_A)=1\).

Let \(f_n\in B_{\Lambda_{1,w}}\) and \(\Phi_A(f_n)\to1\).  Put
\(h_n=f_n^*\).  The chain of inequalities above shows that
\[
 \frac{W(a)}a\int_0^a h_n\to1,\qquad
 \int_0^a h_n(t)w(t)\,dt\to1,\qquad
 \int_a^\infty h_n(t)w(t)\,dt\to0.
\]
By Lemma~\ref{lem:exposure},
\[
 h_n\longrightarrow W(a)^{-1}\chi_{[0,a]}
\]
in the Lorentz norm.  Moreover, the first Hardy--Littlewood inequality is
also asymptotically an equality:
\[
 \int_A f_n\to\int_0^a h_n.
\]
Thus the positive mass of \(f_n\) is asymptotically carried by \(A\), the
negative part on \(A\) is asymptotically zero, and no Lorentz norm remains
outside \(A\).  Consequently
\[
  \|f_n-x_A\|_{1,w}\to0.
\]
This is precisely strong exposure of \(x_A\) by \(\Phi_A\).
\end{proof}

\section*{Proof of the theorem}

If \(w\) is not a.e. constant on \((0,\infty)\), then there is \(a>0\) such
that \(w\) is not a.e. constant on \([0,a]\).  Choose a measurable set
\(A\) of measure \(a\).  By Lemma~\ref{lem:strong-expose}, the unit vector
\(x_A=\chi_A/W(a)\) is strongly exposed by a norm-one functional.

A strongly exposed point cannot be a \(\Delta\)-point: for sufficiently small
\(\alpha>0\), the slice
\[
  S(B_X,\Phi_A,\alpha)=\{y\in B_X:\Phi_A(y)>1-\alpha\}
\]
has arbitrarily small norm diameter around \(x_A\), and therefore cannot
contain points \(y\) with \(\|x_A-y\|>2-\eps\).  Hence \(x_A\) is not a
\(\Delta\)-point.

The diametral local diameter two property is equivalent to every point of the
unit sphere being a \(\Delta\)-point.  Therefore \(\Lambda_{1,w}\) does not
have DLD2P.  Since
\[
  \hbox{Daugavet property}\Rightarrow \hbox{DD2P}\Rightarrow \hbox{DLD2P},
\]
it has neither DD2P nor the Daugavet property.

Conversely, if \(w\) is a.e. constant, say \(w=c>0\), then
\[
  \|f\|_{1,w}=c\int_0^\infty f^*(t)\,dt=c\|f\|_{L_1}.
\]
Thus \(\Lambda_{1,w}\) is isometric, up to the scalar \(c\), to the usual
nonatomic \(L_1\)-space.  Nonatomic \(L_1\) has the Daugavet property, hence
also DD2P and DLD2P.  This proves Theorem~\ref{thm:main}.

\section*{Novelty and verification notes}

The run indexes contained one earlier attempt for this source problem,
\texttt{2212.12149\_lorentz\_daugavet\_nonregular\_attempt.md}.  That attempt
correctly observed that the local-uniform-nonsquareness route fails because
of tiny high spikes.  The present proof uses a different slice and a strong
exposure argument.

Bounded phrase searches for the exact Lorentz problem in the earlier attempt
found the source paper itself and nearby rearrangement-invariant Daugavet
literature, but no later exact answer.  The main point for human verification
is Lemma~\ref{lem:exposure}, the quantitative equality case in Chebyshev's
inequality for monotone functions.

\begin{thebibliography}{9}
\bibitem{KLT}
A. Kaminska, H. J. Lee, and H.-J. Tag,
\emph{Daugavet and diameter two properties in Orlicz--Lorentz spaces},
arXiv:2212.12149.

\bibitem{standard}
V. Kadets, R. Shvidkoy, G. Sirotkin, and D. Werner,
\emph{Banach spaces with the Daugavet property},
Trans. Amer. Math. Soc. 352 (2000), 855--873.
\end{thebibliography}

\end{document}
