\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\XX}{X}
\newcommand{\XB}{\mathcal X}
\newcommand{\LRP}{\mathrm{LRP}}

\begin{document}

\begin{center}
{\Large Literature-implied partial answer: subsymmetric bases with LRP}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:1705.03924; supporting arXiv:2603.21733}
\end{center}

\section*{Status}

\textbf{literature\_implied\_answer (partial subcase).}

Albiac--Ansorena--Wallis ask in arXiv:1705.03924, Problem 3.3, whether every
Banach space with a subsymmetric basis admits a \(1\)-greedy renorming. This
note records the later partial answer supplied by Albiac--Ansorena--Berasategui--Berna.

\section*{Claim}

Let \(\XB\) be a subsymmetric basis of a Banach space \(\XX\). If the upper
superdemocracy function, equivalently the fundamental function in this
subsymmetric setting, has the lower regularity property, then \(\XX\) admits
an equivalent norm for which \(\XB\) is isometrically greedy, isometrically
bidemocratic, and isometrically subsymmetric.

In particular, if \(\XX\) has nontrivial cotype and \(\XB\) is subsymmetric,
then \(\XX\) admits such a \(1\)-greedy renorming.

\section*{Identification}

The source question asks for a \(1\)-greedy renorming of an arbitrary
subsymmetric basis. Theorem 5.2 of arXiv:2603.21733 gives exactly this
conclusion under the lower regularity property on the fundamental function.
Theorem 5.3 of the same paper derives the nontrivial-cotype subcase by
combining Theorem 5.2 with the standard fact that quasi-greedy bases in spaces
with nontrivial cotype have lower regularity for the relevant democracy
function.

This is not an exact full answer to Problem 3.3. The supporting paper states
that, in the absence of a general answer for subsymmetric bases, one must still
study the case where the fundamental function does not have the LRP.

\section*{Evidence}

The source problem appears in arXiv:1705.03924, page 11, Problem 3.3. The
supporting statements are arXiv:2603.21733, page 23, Theorems 5.2 and 5.3.
The remaining open scope is stated on arXiv:2603.21733, page 26.

The packet includes local copies of both PDFs:
\[
\texttt{source\_paper.pdf}, \qquad
\texttt{supporting\_paper\_2603.21733.pdf}.
\]

\section*{Scope}

The broad question remains open for subsymmetric bases whose fundamental
function lacks the lower regularity property. The supporting paper singles out
the dual Schlumprecht-space canonical basis as a concrete remaining question.

\section*{Search Notes}

Local run-index searches for arXiv:1705.03924, Garling sequence spaces,
subsymmetric bases, \(1\)-greedy renorming, \(1\)-GUR, Property~(A), and greedy
bases found no prior packet for this exact subcase. Web searches on
2026-06-15 found arXiv:2603.21733 as the decisive recent supporting paper, but
no full solution of the broad source problem.

\begin{thebibliography}{9}

\bibitem{AAW}
F. Albiac, J. L. Ansorena, and B. Wallis,
\emph{\(1\)-Greedy renormings of Garling sequence spaces},
arXiv:1705.03924.

\bibitem{AABB}
F. Albiac, J. L. Ansorena, M. Berasategui, and P. M. Berna,
\emph{Isometric renormings for greedy bases in Banach spaces, with applications
to the Haar System in \(L_p[0,1]\), \(1<p<\infty\)},
arXiv:2603.21733.

\end{thebibliography}

\end{document}

