\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer to the \(L\)-Orthogonal Sequence Question}
\author{Agent lane 17}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight \texttt{literature\_already\_answered} packet. The
remaining headline question from Aviles--Martinez-Cervantes--Rueda
\cite{AMR2021} is explicitly answered by the later paper of
Aviles--Martinez-Cervantes--Poveda--Saenz \cite{AMPS2025}.

\section*{Original Question}

In \cite[Question 1.1]{AMR2021}, the authors ask:
\begin{quote}
Let \(X\) be a Banach space with an \(L\)-orthogonal sequence
\(\{x_n\}\). Is there an \(L\)-orthogonal element \(u\) in \(X^{**}\)?
\end{quote}
They also ask the stronger weak-star-closure variant in
\cite[Question 1.2]{AMR2021}. The 2021 paper proves positive consistency
results and shows that the weak-star-closure variant is undecidable in ZFC,
but it leaves open whether a negative answer to Question 1.1 is consistent.

\section*{Answering Paper}

The later paper \cite{AMPS2025} explicitly identifies this problem. Its
abstract says that it provides a definitive answer to
\cite[Question 1.1]{AMR2021}. In \cite[Main Theorem, ``Independence of
\(L\)-elements'']{AMPS2025}, the authors prove:
\begin{quote}
The existence of a Banach space with an \(L\)-orthogonal sequence but without
\(L\)-orthogonal elements in its bidual is independent of ZFC.
\end{quote}
Thus the original Question 1.1 is settled in the precise set-theoretic sense:
the positive universal statement holds in some models of ZFC, while in other
models there is a Banach space counterexample.

\section*{Scope and Duplicate Check}

This packet does not claim a new proof. It records an explicit later-literature
answer. A local registry hit for arXiv:2501.06537 already existed, but it
concerns the later paper's quantitative Question 2 about epsilon-strong
\(Q\)-measures, not the headline answer to arXiv:2104.05535. Web search on
2026-06-20 for exact phrases around ``2104.05535'', ``L-orthogonal sequences'',
and ``without L-orthogonal elements'' located arXiv:2501.06537 as the decisive
supporting source.

\begin{thebibliography}{9}

\bibitem{AMR2021}
A. Aviles, G. Martinez-Cervantes, and A. Rueda Zoca,
\emph{\(L\)-orthogonal elements and \(L\)-orthogonal sequences},
arXiv:2104.05535, 2021.
\url{https://arxiv.org/abs/2104.05535}

\bibitem{AMPS2025}
A. Aviles, G. Martinez-Cervantes, A. Poveda, and L. Saenz,
\emph{A Banach space with \(L\)-orthogonal sequences but without
\(L\)-orthogonal elements},
arXiv:2501.06537, 2025.
\url{https://arxiv.org/abs/2501.06537}

\end{thebibliography}

\end{document}
