\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\g}{\mathfrak g}
\newcommand{\h}{\mathfrak h}
\newcommand{\f}{\mathfrak f}
\newcommand{\dd}{\,\mathrm d}
\newcommand{\abs}[1]{\lvert #1\rvert}
\newcommand{\norm}[1]{\lVert #1\rVert}
\newcommand{\A}[2]{A_{#1}^{#2}}
\newcommand{\HH}{\mathcal H}
\newcommand{\B}[4]{\mathcal B^{#1}_{#2;#3,#4}}
\newcommand{\Bw}[3]{\mathcal B^{#1}_{#2;#3,\infty}}
\newcommand{\prof}[3]{\Phi^{#1}_{#2}[#3]}
\newcommand{\weak}{L^{q,\infty}}
\newcommand{\less}{\lesssim}
\newcommand{\eps}{\varepsilon}
\DeclareMathOperator{\spanop}{span}
\DeclareMathOperator{\esssup}{ess\,sup}

\title{Endpoint \(L^1\) Vertical Inequalities on Nilpotent Groups\\
Verified Theorems, Lorentz Propagation, and the Cartan Barrier}
\author{}
\date{June 19, 2026}

\begin{document}
\maketitle

\begin{abstract}
Ryoo asked whether every nonabelian simply connected nilpotent Lie group admits a
finite scale-summability exponent in the endpoint \(L^1\) vertical-versus-horizontal
inequality along a last-layer direction~\cite{Ryoo2026}.  This note records the strongest
conclusions obtained in a sustained attempt to answer that question.  The complete step-two case is
proved with exponent \(4\), in fact for arbitrary bracket-generating left-invariant
Carnot--Carath\'eodory structures on step-two groups.  A universal mixed-bracket theorem
is proved in the full Lorentz scale: regularity and scale summability propagate from a
direction \(W\) to \([X,W]\), with the exact Carnot-weight transformation.  The weak
endpoint version is particularly useful because a finite weak scale exponent, together
with the deterministic path bound, automatically gives every larger strong exponent.
Consequently, the whole step-three problem---including arbitrary bracket-generating
left-invariant horizontal structures---is equivalent to a single finite weak-type estimate
for one top-layer direction on the five-dimensional Cartan group.  A still more
structured weak estimate for its noncentral second-layer direction would imply the
strong step-three theorem for every exponent greater than \(6\).  More generally, one
weak rank-two seed on the free group \(F_{2,s}\) yields the full strong theorem in step
\(s\) above an explicit exponent.  These reductions also give unconditional higher-step
examples, including exponent \(2s\) for the top direction of \(UT_{s+1}(\R)\).

No proof or counterexample for the remaining Cartan weak estimate is obtained here.
The final sections explain why quotient lifting and plain Heisenberg slicing do not close,
and isolate the missing statement as a finite-index kinetic/Carleson cancellation
estimate.  The results in this note are intended as a rigorous research record and have
not been peer reviewed.
\end{abstract}

\begin{center}
\fbox{\begin{minipage}{0.91\linewidth}
\textbf{Status.}  The general conjecture is not proved in this note.  What is proved is:
(i) the complete step-two theorem; (ii) strong and weak Lorentz mixed-bracket
propagation; (iii) permanence under subgroups and nilpotent quotients; (iv) an exact
weak-type reduction of all step-three nilpotent groups to the Cartan group; (v) a
rank-two weak seed theorem in arbitrary step; and (vi) unconditional higher-step
structured examples.
The sole universal step-three target is the weak Cartan estimate in
\cref{eq:cartan-weak-target} below.
\end{minipage}}
\end{center}

\tableofcontents

\section{The endpoint question and scale profiles}

Let \(G\) be a connected, simply connected nilpotent Lie group with Haar measure
\(\mu\).  A fixed bracket-generating horizontal space is equipped with a Euclidean norm,
and \(\nabla_H f\) denotes the corresponding left-invariant horizontal gradient.  For
\(U\in\g\), set
\begin{equation}\label{eq:Adef}
 \A{U}{f}(t)=\int_G\abs{f(g\exp(tU))-f(g)}\dd\mu(g),\qquad t>0.
\end{equation}
If \(U\) is homogeneous of Carnot weight \(k\), define its normalized logarithmic scale
profile by
\begin{equation}\label{eq:profile}
 \prof{\alpha}{U}{f}(x)=e^{-\alpha x}\A{U}{f}(e^x),\qquad x\in\R,
 \quad \alpha=\frac1k.
\end{equation}
For \(1<q<\infty\) and \(1\le r\le\infty\), let
\begin{equation}\label{eq:LorentzBesov}
 \B{U}{\alpha}{q}{r}(f)=
 \norm{\prof{\alpha}{U}{f}}_{L^{q,r}(\R)}.
\end{equation}
Here \(L^{q,r}\) is the usual Lorentz space with respect to Lebesgue measure in the
logarithmic variable.  Thus
\[
 \B{U}{\alpha}{q}{q}(f)=
 \left(\int_0^\infty
 \left(\frac{\A{U}{f}(t)}{t^\alpha}\right)^q\frac{\dd t}{t}
 \right)^{1/q},
\]
and the weak endpoint is
\begin{equation}\label{eq:weakdef}
 \Bw{U}{\alpha}{q}(f)=
 \sup_{\lambda>0}\lambda
 \abs{\{x\in\R:\prof{\alpha}{U}{f}(x)>\lambda\}}^{1/q}.
\end{equation}
We write
\begin{equation}\label{eq:Hdef}
 \HH_G(f)=\int_G\abs{\nabla_Hf(g)}\dd\mu(g).
\end{equation}

If \(G\) has nilpotency step \(s\), write \(\g_s=[\g,[\g,\ldots,[\g,\g]\ldots]]\)
for its final nonzero lower-central layer.  For \(0\ne v\in\g_s\), Ryoo's endpoint
question asks whether there is a finite \(q\) such that
\begin{equation}\label{eq:Ryoo}
 \B{v}{1/s}{q}{q}(f)\less_{G,v,q}\HH_G(f)
 \qquad\forall f\in C_c^\infty(G).
\end{equation}
This is Question 38 in \cite{Ryoo2026}; by coarea it is equivalent to the vertical
perimeter formulation in Question 42 of that paper.

The elementary deterministic bound will be used repeatedly.  Whenever a direction
\(U\) admits horizontal paths from \(e\) to \(\exp(tU)\) of length at most
\(C_Ut^\alpha\) for every \(t>0\), differentiation along such a path and right
invariance of Haar measure give
\begin{equation}\label{eq:Linfty}
 \norm{\prof{\alpha}{U}{f}}_{L^\infty(\R)}
 \less_{G,U}\HH_G(f).
\end{equation}
This applies to \(U\in V_k\) in a Carnot group with \(\alpha=1/k\).  It also applies,
with the same exponent, to a fixed \(k\)-fold horizontal bracket in an arbitrary
step-at-most-\(k\) nilpotent group, and to finite sums of such brackets when they are
central.  In particular it applies with \(\alpha=1/s\) to every final-layer direction
used below.  The difficulty is therefore not a bound at one scale, but summability over
all scales.

\subsection*{Main conclusions of this note}

The central new reduction is the following informal statement, proved precisely in
\cref{sec:weak,sec:cartan}:
\[
 \boxed{\text{A finite weak scale exponent is enough.}}
\]
Indeed, weak \(L^r\) plus \eqref{eq:Linfty} gives strong \(L^q\) for every \(q>r\).
In step three, it is enough to prove this weak estimate for one direction on one group,
the Cartan group.

\section{The complete step-two theorem}\label{sec:step2}

We first verify and strengthen the supplied partial result.  In this section \(G\) is any
connected, simply connected, step-two nilpotent group, not necessarily Carnot graded.
Let \(W\subseteq\g\) be a bracket-generating horizontal space with its fixed norm.  Then
\([\g,\g]=[W,W]\) is central.  For \(z\in[\g,\g]\), define
\begin{equation}\label{eq:kappa}
 \kappa_W(z)=\inf\left\{
 \sum_{j=1}^m\sqrt{\abs{a_j}\abs{b_j}}:
 z=\sum_{j=1}^m[a_j,b_j],\ a_j,b_j\in W
 \right\}.
\end{equation}

\begin{theorem}[Complete step-two endpoint theorem]\label{thm:step2}
There is a universal constant \(C<\infty\) such that every
\(f\in C_c^\infty(G)\) and \(z\in[\g,\g]\) satisfy
\begin{equation}\label{eq:step2q4}
 \left(\int_0^\infty
 \left(\frac{\A{z}{f}(t)}{\sqrt t}\right)^4\frac{\dd t}{t}
 \right)^{1/4}
 \le C\kappa_W(z)\int_G\abs{\nabla_Wf}\dd\mu.
\end{equation}
Consequently the same estimate holds for every strong exponent \(q\ge4\), with a
constant depending on \(q\).  In particular, Ryoo's endpoint question is completely
resolved in nilpotency step two.
\end{theorem}

\begin{lemma}[Elementary Heisenberg transfer]\label{lem:heis-transfer}
Let \(a,b\in W\) and \(z=[a,b]\ne0\).  Then
\begin{equation}\label{eq:heis-transfer}
 \left(\int_0^\infty
 \left(\frac{\A{z}{f}(t)}{\sqrt t}\right)^4\frac{\dd t}{t}
 \right)^{1/4}
 \less \sqrt{\abs a\abs b}\int_G\abs{\nabla_Wf}\dd\mu.
\end{equation}
\end{lemma}

\begin{proof}
The vectors \(a,b,z\) span a three-dimensional Heisenberg Lie algebra.  The connected
subgroup
\[
 H=\exp(\spanop\{a,b,z\})
\]
is closed because the exponential map of a simply connected nilpotent group is a
diffeomorphism and the displayed linear subspace is closed.  Both \(G\) and \(H\) are
unimodular.  Weil disintegration therefore gives
\[
 \int_G\Psi(g)\dd\mu(g)=\int_{G/H}\int_H\Psi(xh)\dd\mu_H(h)\dd\bar\mu(x).
\]
On each left coset, apply the sharp three-dimensional Heisenberg inequality of Naor and
Young \cite{NaorYoung2022} to \(h\mapsto f(xh)\).  Minkowski's integral inequality in
\(L^4(\dd t/t)\) and Weil disintegration yield
\[
 \B{z}{1/2}{4}{4}(f)
 \less\int_G\bigl(\abs{af}+\abs{bf}\bigr)\dd\mu.
\]
Replace \((a,b)\) by \((\lambda a,\lambda^{-1}b)\) and minimize
\(\lambda\abs a+\lambda^{-1}\abs b\) over \(\lambda>0\).  This gives
\eqref{eq:heis-transfer}.
\end{proof}

\begin{proof}[Proof of \cref{thm:step2}]
Choose a representation \(z=\sum_{j=1}^m[a_j,b_j]\) and set
\(z_j=[a_j,b_j]\).  Since all \(z_j\) are central,
\(\exp(tz)=\prod_j\exp(tz_j)\).  Telescoping and right invariance of Haar measure give
\[
 \A{z}{f}(t)\le\sum_{j=1}^m\A{z_j}{f}(t).
\]
Minkowski and \cref{lem:heis-transfer} imply
\[
 \B{z}{1/2}{4}{4}(f)
 \less\left(\sum_{j=1}^m\sqrt{\abs{a_j}\abs{b_j}}\right)
 \int_G\abs{\nabla_Wf}\dd\mu.
\]
Take the infimum over all representations to prove \eqref{eq:step2q4}.

A commutator rectangle of side lengths \(r,u\) reaches
\(\exp(ru[a,b])\) with horizontal length \(2r\abs a+2u\abs b\).  Optimizing under
\(ru=t\), summing over a representation of \(z\), and then taking the infimum yields
\[
 \sup_{t>0}\frac{\A{z}{f}(t)}{\sqrt t}
 \less\kappa_W(z)\int_G\abs{\nabla_Wf}\dd\mu.
\]
Interpolation of the scalar scale profile between \(L^4\) and \(L^\infty\) proves all
\(q\ge4\).
\end{proof}

\begin{remark}
The exponent \(4\) is not always optimal.  It is sharp for the three-dimensional
Heisenberg group, whereas for \(\mathbb H^{2k+1}\), \(k\ge2\), the sharp known exponent is
\(2\); see \cite{NaorYoung2018,NaorYoung2022}.  The point of \cref{thm:step2} is
existence for every step-two group and every commutator direction.
\end{remark}

\section{Permanence principles}\label{sec:permanence}

The reductions below use three elementary permanence facts.  They are stated for the
strong norm and for the finite weak norm.  The weak case uses the equivalent Banach
function norm, valid for \(q>1\),
\begin{equation}\label{eq:weak-equivalent}
 \norm{F}_{(q,\infty)}=
 \sup_{0<\abs E<\infty}\abs E^{-1/q'}\int_E\abs{F(x)}\dd x,
\end{equation}
which is equivalent to the distribution-function expression in \eqref{eq:weakdef}.

\begin{lemma}[Coset transfer]\label{lem:coset}
Let \(H\le G\) be a closed connected subgroup.  Suppose an estimate in a direction
\(U\in\h\), with either a strong \(L^q\) scale norm or a weak \(L^{q,\infty}\) scale norm,
holds on \(H\) with horizontal derivatives belonging to the ambient horizontal space.
Then the same estimate holds on \(G\), with a constant changed only by the fixed norm
comparison.
\end{lemma}

\begin{proof}
Apply the estimate to \(h\mapsto f(xh)\) on each left coset.  For a strong norm, integrate
in \(G/H\) and use Minkowski.  For a weak norm, use \eqref{eq:weak-equivalent}; its
definition gives the corresponding Minkowski integral inequality directly.  Finish with
Weil disintegration.
\end{proof}

\begin{proposition}[Descent through nilpotent quotients]\label{prop:quotient}
Let \(\pi:G\to\bar G\) be a surjective homomorphism between connected, simply
connected nilpotent groups, with the quotient horizontal structure.  If a strong or finite
weak scale estimate holds on \(G\) in direction \(U\), then it holds on \(\bar G\) in
direction \(\pi_*U\ne0\).
\end{proposition}

\begin{proof}
It is enough to treat a quotient by a connected central subgroup, since every ideal in a
finite-dimensional nilpotent Lie algebra admits a finite filtration with central successive
quotients.  Write the central quotient measure-theoretically as
\(G\cong\bar G\times\R^m\).  Given \(\bar f\in C_c^\infty(\bar G)\), choose a smooth
cutoff \(\eta_R\) on \(\R^m\) with mass \(m_R\to\infty\), and put
\(F_R(\bar g,z)=\bar f(\bar g)\eta_R(z)\).  After division by \(m_R\), the horizontal
energy converges to that of \(\bar f\), while for every fixed scale the normalized
translation integral converges to the corresponding quotient translation integral.
Fatou's lemma proves the strong case.  For the weak case, apply Fatou inside
\eqref{eq:weak-equivalent}, then take the supremum over measurable scale sets.  Iterate
the central filtration.
\end{proof}

\begin{lemma}[Finite central sums]\label{lem:central-sum}
Let \(U_1,\ldots,U_N\) be commuting directions.  If a strong or finite weak scale
estimate with the same homogeneity and exponent holds for each \(U_j\), then it holds for
\(U_1+\cdots+U_N\).
\end{lemma}

\begin{proof}
Central telescoping gives
\(\A{U_1+\cdots+U_N}{f}(t)\le\sum_j\A{U_j}{f}(t)\).  Use the triangle inequality in the
strong scale space or in the equivalent weak norm \eqref{eq:weak-equivalent}.
\end{proof}

\section{A universal Lorentz mixed-bracket theorem}\label{sec:mixed}

The following theorem is the main propagation mechanism.  It does not require \(W\) or
\([X,W]\) to be central.

\begin{lemma}[Universal anisotropic bracket word]\label{lem:word}
For every nilpotency bound \(s\ge2\), there are a finite number of coefficients and a word,
depending only on \(s\), such that for every step-at-most-\(s\) nilpotent group, every
\(X,W\in\g\), and every \(r,u>0\),
\begin{equation}\label{eq:word}
 \exp(ru[X,W])=
 \prod_{j=1}^{N(s)}\exp\bigl(c_j\lambda_j(r,u)\Sigma_j\bigr),
\end{equation}
where \(\Sigma_j\in\{X,W\}\), and \(\lambda_j=r\) when \(\Sigma_j=X\), while
\(\lambda_j=u\) when \(\Sigma_j=W\).
\end{lemma}

\begin{proof}
Work in the free step-\(s\) nilpotent group on generators \(x,w\).  Let \(S\) be the
set of finite products of elements of the one-parameter subgroups \(\exp(\R x)\) and
\(\exp(\R w)\).  It is a subgroup.  By Chow--Rashevskii (equivalently, by the orbit
theorem), the reachable set from the identity has nonempty interior because \(x,w\)
Lie-generate the free algebra.  Hence \(S\) is an open subgroup; the free group is
connected, so \(S\) is the whole group.  In particular \(\exp([x,w])\) is a finite word in
those two one-parameter subgroups.  Apply the multigraded automorphism
\(x\mapsto rx\), \(w\mapsto uw\), and then the universal homomorphism
\(x\mapsto X\), \(w\mapsto W\).
\end{proof}

Let \(D_h(f)=\int_G\abs{f(gh)-f(g)}\dd\mu(g)\).  Unimodularity gives
\(D_{h_1\cdots h_N}(f)\le\sum_jD_{h_j}(f)\).  Thus \cref{lem:word} implies
\begin{equation}\label{eq:rectangle}
 \A{[X,W]}{f}(ru)
 \less_s\sum_j\A{X}{f}(c_jr)+\sum_j\A{W}{f}(d_ju),
\end{equation}
with fixed positive constants after replacing signs by absolute values.

\begin{theorem}[Lorentz mixed-bracket propagation]\label{thm:lorentz-mixed}
Let \(G\) have nilpotency step at most \(s\), let \(X,W\in\g\), let \(\alpha>0\),
\(1<q<\infty\), and \(1\le r\le\infty\).  Put
\begin{equation}\label{eq:betaQ}
 \beta=\frac{\alpha}{1+\alpha},\qquad Q=(1+\alpha)q,
 \qquad R=(1+\alpha)r,
\end{equation}
with \(R=\infty\) when \(r=\infty\).  Then
\begin{equation}\label{eq:lorentz-mixed}
 \B{[X,W]}{\beta}{Q}{R}(f)
 \less_{s,\alpha,q,r}
 \left(\int_G\abs{Xf}\dd\mu\right)^\beta
 \left(\B{W}{\alpha}{q}{r}(f)\right)^{1-\beta}.
\end{equation}
In particular:
\begin{equation}\label{eq:strongmixed}
 \B{[X,W]}{\beta}{Q}{Q}(f)
 \less
 \left(\int_G\abs{Xf}\dd\mu\right)^\beta
 \left(\B{W}{\alpha}{q}{q}(f)\right)^{1-\beta}.
\end{equation}
\begin{equation}\label{eq:weakmixed}
 \Bw{[X,W]}{\beta}{Q}(f)
 \less
 \left(\int_G\abs{Xf}\dd\mu\right)^\beta
 \left(\Bw{W}{\alpha}{q}(f)\right)^{1-\beta}.
\end{equation}
\end{theorem}

\begin{proof}
Set
\[
 a(r)=\A{X}{f}(r),\quad b(u)=\A{W}{f}(u),\quad
 c(t)=\A{[X,W]}{f}(t),\quad M=\int_G\abs{Xf}\dd\mu.
\]
The path bound gives \(a(r)\le rM\).  Define
\[
 B(y)=e^{-\alpha y}b(e^y),\qquad C(x)=e^{-\beta x}c(e^x).
\]
The finite word \eqref{eq:rectangle} gives, after absorbing its fixed dilations into a
finite sum of translates \(\widetilde B\),
\begin{equation}\label{eq:prelog}
 c(ru)\less_s rM+u^\alpha\widetilde B(\log u),
 \qquad
 \norm{\widetilde B}_{L^{q,r}}\less_s\norm{B}_{L^{q,r}}.
\end{equation}
Choose
\[
 u=\exp\left(\frac{x}{1+\alpha}+z\right),\qquad
 r=\exp\left(\frac{\alpha x}{1+\alpha}-z\right).
\]
Then \(ru=e^x\), and \eqref{eq:prelog} becomes
\begin{equation}\label{eq:logbound}
 C(x)\less_s Me^{-z}+e^{\alpha z}
 \widetilde B\left(\frac{x}{1+\alpha}+z\right).
\end{equation}
Assume first \(M>0\).  If \(C(x)>\lambda\), choose
\(z=\log(c_sM/\lambda)\) with the constant adjusted so that the first term in
\eqref{eq:logbound} is at most \(\lambda/2\).  It follows that
\[
 \widetilde B\left(\frac{x}{1+\alpha}+z\right)
 \gtrsim_{s,\alpha}M^{-\alpha}\lambda^{1+\alpha}.
\]
Writing \(m_F(\lambda)=\abs{\{F>\lambda\}}\), we obtain
\begin{equation}\label{eq:distribution}
 m_C(\lambda)\le(1+\alpha)
 m_{\widetilde B}(c_{s,\alpha}M^{-\alpha}\lambda^{1+\alpha}).
\end{equation}
Equivalently, in terms of decreasing rearrangements,
\begin{equation}\label{eq:rearrangement}
 C^*(t)\less_{s,\alpha}M^\beta
 \bigl(\widetilde B^*(c_\alpha t)\bigr)^{1/(1+\alpha)}.
\end{equation}
Multiply by \(t^{1/Q}\), raise to the power
\(R=(1+\alpha)r\), and integrate \(\dd t/t\).  Since
\(Q=(1+\alpha)q\), this gives
\[
 \norm{C}_{L^{Q,R}}
 \less M^\beta\norm{\widetilde B}_{L^{q,r}}^{1/(1+\alpha)}.
\]
Use \eqref{eq:prelog}.  If \(M=0\), replace it by an arbitrary positive upper bound and
let that bound decrease to zero.
\end{proof}

\begin{corollary}[Exact Carnot-weight recurrence]\label{cor:recurrence}
Suppose \(W_k\in V_k\) satisfies a strong or weak estimate with regularity \(1/k\) and
scale exponent \(q_k\).  For \(a\in V_1\), set \(W_{k+1}=[a,W_k]\).  Then the same type
of estimate holds for \(W_{k+1}\), with
\begin{equation}\label{eq:recurrence}
 q_{k+1}=\frac{k+1}{k}q_k.
\end{equation}
Starting at weight two, this telescopes to
\begin{equation}\label{eq:qk}
 q_k=\frac{k}{2}q_2.
\end{equation}
\end{corollary}

\begin{proof}
Apply \cref{thm:lorentz-mixed} with \(\alpha=1/k\).  Then
\(\beta=1/(k+1)\), and \(Q=(k+1)q_k/k\).  If both factors on the right are controlled
by \(\HH_G(f)\), their weighted product is also controlled by \(\HH_G(f)\).
\end{proof}

\section{Why a finite weak exponent is enough}\label{sec:weak}

\begin{lemma}[Weak-to-strong upgrade]\label{lem:weak-strong}
Let \(0<r<p<\infty\), and suppose \(F\in L^{r,\infty}(\R)\cap L^\infty(\R)\).  Then
\begin{equation}\label{eq:weak-strong}
 \norm{F}_{L^p}
 \le\left(\frac{p}{p-r}\right)^{1/p}
 \norm{F}_{L^{r,\infty}}^{r/p}
 \norm{F}_{L^\infty}^{1-r/p}.
\end{equation}
\end{lemma}

\begin{proof}
If \(K=\norm{F}_{L^{r,\infty}}\) and \(M=\norm{F}_{L^\infty}\), then
\(m_F(\lambda)\le(K/\lambda)^r\) for \(0<\lambda\le M\).  The layer-cake formula gives
\[
 \norm{F}_{L^p}^p
 =p\int_0^M\lambda^{p-1}m_F(\lambda)\dd\lambda
 \le\frac{p}{p-r}K^rM^{p-r}.
\]
\end{proof}

\begin{corollary}[Finite weak endpoint suffices]\label{cor:weak-suffices}
Let \(\alpha>0\), and suppose the deterministic profile bound
\(\norm{\prof{\alpha}{U}{f}}_\infty\lesssim\HH_G(f)\) holds.  If for some
\(1<r<\infty\)
\begin{equation}\label{eq:weakassume}
 \Bw{U}{\alpha}{r}(f)\less\HH_G(f),
\end{equation}
then for every \(p>r\),
\begin{equation}\label{eq:strongabove}
 \B{U}{\alpha}{p}{p}(f)\less_p\HH_G(f).
\end{equation}
\end{corollary}

\begin{proof}
Combine \cref{lem:weak-strong} with the assumed deterministic \(L^\infty\) profile
bound.  The applications below use \(\alpha=1/k\) for a weight-\(k\) direction, or
\(\alpha=1/s\) for a final-layer direction in a step-\(s\) group.
\end{proof}

This observation changes the remaining target substantially.  One does not need to prove
a sharp strong estimate at its endpoint.  Any polynomial distribution bound for the bad
scales is enough.

\section{Universal finite models and rank-two seeds}\label{sec:free}

\subsection{A fixed-step free-model equivalence}

Let \(F_{m,s}\) denote the free step-\(s\) Carnot group on \(m\) horizontal generators.

\begin{proposition}[Finite universal model at each step]\label{prop:free-model}
Fix \(s\ge2\).  The following assertions are equivalent.
\begin{enumerate}[label=(\roman*)]
\item Every connected, simply connected, step-\(s\) nilpotent group, equipped with any
bracket-generating left-invariant horizontal structure, and every nonzero direction in its
final lower-central layer satisfy Ryoo's inequality for some finite strong exponent.
\item Every basis vector of \(V_s(F_{s,s})\) satisfies a finite weak-type estimate.
\end{enumerate}
If (ii) holds with a common weak exponent \(r>1\), then every step-\(s\) group in (i)
satisfies the strong estimate for every \(p>r\).
\end{proposition}

\begin{proof}
The implication (i)\(\Rightarrow\)(ii) is immediate.  Conversely, there are only finitely many chosen basis vectors.  Increase the exponent
past all of their weak exponents, use \cref{lem:weak-strong}, and then use finite central
sums.  This gives a common finite strong (hence weak) estimate for every vector in the
finite-dimensional space \(V_s(F_{s,s})\).  Let \(W\) be the given horizontal space in an
arbitrary step-\(s\) group.  Since the image of \(W\) spans \(\g/[\g,\g]\), multilinearity
of the bracket and the identity \([\g_2,\g_{s-1}]\subseteq\g_{s+1}=0\) show that the final
layer \(\g_s\) is spanned by right-normed brackets
\[
 [a_s,[a_{s-1},\ldots,[a_2,a_1]\ldots]]],\qquad a_j\in W.
\]
Each such bracket is the quotient image of a top-layer vector in \(F_{s,s}\).  Use
quotient descent, coset transfer, and central sums.  Finally apply
\cref{cor:weak-suffices}.
\end{proof}

\subsection{The rank-two weak seed theorem}

Let \(F_{2,s}\) have free horizontal generators \(X,Y\), and put
\begin{equation}\label{eq:Tseed}
 T=[X,Y]\in V_2(F_{2,s}).
\end{equation}
For \(s\ge3\), this direction is noncentral.

\begin{theorem}[One weak rank-two seed controls every group]\label{thm:ranktwo}
Fix \(s\ge2\).  Suppose that for some \(1<q_2<\infty\),
\begin{equation}\label{eq:weakseed}
 \Bw{T}{1/2}{q_2}(f)
 \less_{s,q_2}\int_{F_{2,s}}\bigl(\abs{Xf}+\abs{Yf}\bigr)
 \qquad\forall f\in C_c^\infty(F_{2,s}).
\end{equation}
Then for every connected, simply connected, step-\(s\) nilpotent group \(G\), every
bracket-generating horizontal space \(W\), every \(v\in\g_s\), and every \(p>sq_2/2\),
\begin{equation}\label{eq:ranktwo-output}
 \B{v}{1/s}{p}{p}(f)\less_{G,W,v,p}\int_G\abs{\nabla_Wf}\dd\mu.
\end{equation}
Before the weak-to-strong upgrade, the final direction satisfies weak exponent
\(sq_2/2\).
\end{theorem}

\begin{proof}
By the spanning argument in \cref{prop:free-model}, it is enough to treat a
right-normed bracket
\[
 v=[a_s,[a_{s-1},\ldots,[a_3,[a_2,a_1]]\ldots]],\qquad a_j\in W.
\]
Map the free generators \(X,Y\) to \(a_2,a_1\).  The subgroup they generate is a
nilpotent quotient of \(F_{2,s}\).  Thus \eqref{eq:weakseed} descends to the direction
\([a_2,a_1]\), and then transfers from that subgroup to \(G\).  Apply the weak form
\eqref{eq:weakmixed} successively with \(a_3,\ldots,a_s\).  By
\eqref{eq:qk}, the final weak exponent is \(sq_2/2\).  Sum the finitely many central
right-normed terms and use \cref{cor:weak-suffices}.
\end{proof}

\begin{remark}
The natural hoped-for seed is \(q_2=4\), inherited from the three-dimensional Heisenberg
quotient.  A weak lift of that one estimate through the central extensions
\(F_{2,s}\to F_{2,s-1}\) would give the universal strong conclusion for every
\(p>2s\).  The reverse lift through a central extension is precisely where the current
argument stops.
\end{remark}

\section{The Cartan group is the complete step-three test}\label{sec:cartan}

Let \(C=F_{2,3}\) be the five-dimensional Cartan group, with Lie algebra
\begin{equation}\label{eq:cartan-brackets}
 [X,Y]=T,\qquad [X,T]=U,\qquad [Y,T]=V,
\end{equation}
where \(U,V\) are central.  Its grading has dimensions \((2,1,2)\).

\subsection{Polarization and symmetry}

For \(P(a,b)=[a,[a,b]]\), the identity
\begin{equation}\label{eq:polarization}
 3[a,[b,c]]=
 P(a+b,c)-P(a,c)-P(b,c)-P(a+c,b)+P(a,b)+P(c,b)
\end{equation}
shows that every triple bracket is a linear combination of brackets involving only two
horizontal vectors.  Each \(P(a,b)\) is the image of \(U=[X,[X,Y]]\) under the
homomorphism \(C\to G\) sending \(X\mapsto a\), \(Y\mapsto b\).

Moreover, \(\mathrm{GL}_2(\R)\) acts by graded automorphisms on \(C\).  On
\(V_3(C)=\spanop\{U,V\}\), this action is the standard two-dimensional action twisted
by the determinant, and is transitive on nonzero vectors.  Thus all nonzero top-layer
directions of \(C\) are equivalent.

\begin{theorem}[Exact weak Cartan reduction]\label{thm:cartan-equivalence}
The following are equivalent.
\begin{enumerate}[label=(\roman*)]
\item Ryoo's endpoint conjecture has a positive answer for every connected, simply
connected, step-three nilpotent group with every bracket-generating left-invariant
horizontal structure.
\item For some \(1<r<\infty\), every \(f\in C_c^\infty(C)\) satisfies
\begin{equation}\label{eq:cartan-weak-target}
 \boxed{
 \Bw{U}{1/3}{r}(f)
 \less_r\int_C\bigl(\abs{Xf}+\abs{Yf}\bigr).}
\end{equation}
\end{enumerate}
If \eqref{eq:cartan-weak-target} holds, then every group and horizontal structure in
(i) satisfies the strong inequality for every exponent \(p>r\).
\end{theorem}

\begin{proof}
The implication (i)\(\Rightarrow\)(ii) follows by applying (i) to \(C\), since a strong
estimate implies a weak estimate.  Conversely, the graded automorphism action gives the same weak estimate for every top
direction in \(C\).  Let \(W\) be a bracket-generating horizontal space in an arbitrary
step-three nilpotent group.  Its final layer is spanned by \([a,[b,c]]\) with
\(a,b,c\in W\).  The polarization identity \eqref{eq:polarization} writes each such vector
as a finite sum of terms \(P(u,w)=[u,[u,w]]\), each of which is a quotient image of
\(U=[X,[X,Y]]\).  Quotient descent, coset transfer, and central sums therefore transfer
the weak estimate to every final-layer direction.  Apply \cref{cor:weak-suffices}.
\end{proof}

Thus the whole step-three problem is not merely reduced to Cartan in a heuristic sense:
it is equivalent to one explicit weak distribution estimate on that group.

\subsection{A stronger but reusable noncentral seed}

A particularly useful sufficient statement concerns the second-layer direction \(T\).

\begin{corollary}[Weak Cartan seed in the noncentral direction]\label{cor:Tseed}
Suppose that for some \(1<q_2<\infty\),
\begin{equation}\label{eq:Tweak}
 \Bw{T}{1/2}{q_2}(f)
 \less\int_C\bigl(\abs{Xf}+\abs{Yf}\bigr).
\end{equation}
Then \(U\) and \(V\) satisfy weak exponent \(3q_2/2\), and every step-three nilpotent
group with a bracket-generating horizontal structure satisfies the strong endpoint
inequality for every
\(p>3q_2/2\).  In particular, the natural quotient-Heisenberg value \(q_2=4\) would give
every strong exponent \(p>6\).
\end{corollary}

\begin{proof}
Apply \eqref{eq:weakmixed} to \(U=[X,T]\) and \(V=[Y,T]\) with
\(\alpha=1/2\).  Then \(\beta=1/3\) and \(Q=3q_2/2\).  Finish with
\cref{thm:cartan-equivalence,cor:weak-suffices}.
\end{proof}

\begin{proposition}[A concrete absorption criterion]\label{prop:absorption}
Suppose the following twisted Heisenberg lifting estimate holds on \(C\):
\begin{equation}\label{eq:twisted-lift}
 \B{T}{1/2}{4}{4}(f)
 \less \HH_C(f)+\B{U}{1/3}{6}{6}(f)+\B{V}{1/3}{6}{6}(f).
\end{equation}
Then
\begin{equation}\label{eq:cartan-strong-closure}
 \B{T}{1/2}{4}{4}(f)+\B{U}{1/3}{6}{6}(f)+\B{V}{1/3}{6}{6}(f)
 \less \HH_C(f).
\end{equation}
Consequently every step-three nilpotent group with a bracket-generating horizontal
structure satisfies the strong endpoint inequality for every \(q\ge6\).
\end{proposition}

\begin{proof}
The strong mixed-bracket theorem gives
\[
 \B{U}{1/3}{6}{6}(f)+\B{V}{1/3}{6}{6}(f)
 \less \HH_C(f)^{1/3}\B{T}{1/2}{4}{4}(f)^{2/3}.
\]
Insert this into \eqref{eq:twisted-lift} and use Young's inequality with a sufficiently
small coefficient to absorb the \(T\)-term.  The estimates for \(U,V\) then follow from
the displayed mixed bound.  Apply \cref{thm:cartan-equivalence} and the deterministic
profile bound to obtain all \(q\ge6\).
\end{proof}

Thus \eqref{eq:twisted-lift} is a second, stronger formulation of the missing analytic
step.  Unlike the weak target \eqref{eq:cartan-weak-target}, it is scale-critical and has a
specified exponent; its advantage is that it is directly compatible with absorption.

\section{Unconditional higher-step families}\label{sec:families}

The propagation theorem already proves nontrivial examples in every step.

\begin{theorem}[Step-three groups of type \(\star\)]\label{thm:type-star}
Let \(G\) be a step-three Carnot group of type \(\star\) in the sense of
Marchi~\cite{Marchi2014}.  Thus \(V_1\) has a basis \(X_1,\ldots,X_m\) satisfying
\begin{equation}\label{eq:type-star}
 [X_j,[X_j,X_i]]=0\qquad\forall i,j.
\end{equation}
Then every \(v\in V_3\) satisfies
\begin{equation}\label{eq:type-star-q6}
 \B{v}{1/3}{6}{6}(f)\less_{G,v}\HH_G(f).
\end{equation}
Hence every exponent \(q\ge6\) is admissible.
\end{theorem}

\begin{proof}
For each pair \(i,j\), the relations \eqref{eq:type-star} imply that
\(W_{ij}=[X_j,X_i]\) commutes with both \(X_i\) and \(X_j\).  If \(W_{ij}\ne0\), these
three vectors generate a three-dimensional Heisenberg subgroup.  The Naor--Young
theorem and coset transfer therefore give the strong \((1/2,4)\) estimate for
\(W_{ij}\).  Since \(V_3=[V_1,V_2]\), every \(v\in V_3\) is a finite sum of vectors
\([X_k,W_{ij}]\).  Apply the strong mixed-bracket theorem with \(\alpha=1/2\) to obtain
exponent \(6\) for each term, and then use central telescoping.
\end{proof}

\begin{theorem}[Upper unitriangular groups]\label{thm:UT}
Let \(UT_{s+1}(\R)\) have its standard Carnot grading and horizontal generators
\(X_i=E_{i,i+1}\), \(1\le i\le s\).  For the top direction
\(Z=E_{1,s+1}\),
\begin{equation}\label{eq:UT}
 \B{Z}{1/s}{2s}{2s}(f)\less_s\HH_{UT_{s+1}}(f).
\end{equation}
Hence every exponent \(q\ge2s\) is admissible for this direction.
\end{theorem}

\begin{proof}
Set \(W_2=[X_{s-1},X_s]=E_{s-1,s+1}\).  The subgroup generated by
\(X_{s-1},X_s\) is three-dimensional Heisenberg, so the Naor--Young theorem and coset
transfer give strong exponent \(q_2=4\) for \(W_2\).  Recursively define
\[
 W_k=[X_{s-k+1},W_{k-1}]=E_{s-k+1,s+1},\qquad 3\le k\le s.
\]
Apply \cref{cor:recurrence}; \(q_k=(k/2)4=2k\).  At \(k=s\), \(W_s=Z\).
\end{proof}

This family gives a positive endpoint theorem in every nilpotency step without assuming
any unproved seed.

\section{Why the Cartan estimate does not follow by the obvious lifts}\label{sec:barrier}

The quotient \(C/\exp(\spanop\{U,V\})\) is the three-dimensional Heisenberg group, where
the \(T\)-estimate with exponent \(4\) is known.  It is tempting to lift that estimate back
to \(C\), but the two simplest routes fail for structural reasons.

\subsection{Failure of plain quotient lifting}

A section of the central quotient turns quotient horizontal derivatives into ambient
horizontal derivatives plus top-layer drift.  In any fixed trivialization the two lifted
horizontal fields cannot both be made drift-free, because the connection has curvature.
The resulting \(U\)- and \(V\)-derivatives are not controlled in \(L^1\) by
\(\abs{Xf}+\abs{Yf}\).  Averaging over larger and larger central fibers proves descent
from an extension to its quotient, as in \cref{prop:quotient}, but gives no reverse
estimate.

\subsection{Failure of plain Heisenberg slicing}

The subgroup \(\exp(\spanop\{X,T,U\})\) is a genuine Heisenberg group.  Slicing by its
left cosets and applying Naor--Young controls top translation in \(U\) by the derivatives
\(Xf\) and \(Tf\).  The latter is not an ambient horizontal derivative.  The analogous
subgroup \(\exp(\spanop\{Y,T,V\})\) has the same defect.

\begin{proposition}[No first-derivative substitute for compensation]\label{prop:no-T}
There is no constant \(C_0\) such that
\begin{equation}\label{eq:no-T}
 \norm{Tf}_{L^1(C)}\le C_0\bigl(\norm{Xf}_{L^1(C)}+\norm{Yf}_{L^1(C)}\bigr)
 \qquad\forall f\in C_c^\infty(C).
\end{equation}
\end{proposition}

\begin{proof}
Use polynomial coordinates \((x,y,a,b,c)\) in which
\[
 Y=\partial_y,\qquad
 X=\partial_x-y\partial_a-\frac{y^2}{2}\partial_b-xy\partial_c,
 \qquad
 T=\partial_a+y\partial_b+x\partial_c.
\]
Choose nonzero smooth compactly supported one-variable cutoffs and set
\[
 f_\eps(x,y,a,b,c)=
 \chi_1(x)\eta(y/\eps)\varphi(a/\eps^2)\chi_2(b)\chi_3(c).
\]
Choose \(\chi_2,\chi_3\) equal to one on a fixed neighborhood and choose
\(\varphi'\not\equiv0\).  Direct scaling gives
\[
 \norm{Yf_\eps}_1=O(\eps^2),\qquad
 \norm{Xf_\eps}_1=O(\eps^2),\qquad
 \norm{Tf_\eps}_1\gtrsim\eps.
\]
For the last inequality, restrict to the region where \(\chi_2=\chi_3=1\); there the
\(\partial_a\)-term has size \(\asymp\eps\) in \(L^1\), while the remaining terms are of
smaller order.  Letting \(\eps\downarrow0\) contradicts \eqref{eq:no-T}.
\end{proof}

Therefore a successful argument must use compensation or multiscale cancellation, not
a pointwise derivative comparison.

\subsection{Exact commutator geometry}

The Baker--Campbell--Hausdorff formula gives, up to harmless sign conventions,
\begin{equation}\label{eq:cartan-commutator}
 \exp(aX)\exp(bY)\exp(-aX)\exp(-bY)
 =\exp\left(abT+\frac{a^2b}{2}U+\frac{ab^2}{2}V\right).
\end{equation}
The top-layer errors have exactly the correct ambient homogeneity: when \(a\asymp b\asymp
\sqrt t\), they have size \(t^{3/2}\), whose Carnot distance is \(t^{1/2}\).  Thus the
obstruction is not a mismatch of powers.  It is the need to sum the horizontal cost over
many scales without charging the entire perimeter at each scale.

\section{Kinetic and Rumin formulations of the missing estimate}\label{sec:kinetic}

Continue in the polynomial coordinates used in the proof of \cref{prop:no-T}:
\begin{equation}\label{eq:kinetic-fields}
 Y=\partial_y,
 \qquad
 X=\partial_x-y\partial_a-\frac{y^2}{2}\partial_b-xy\partial_c.
\end{equation}
For an intrinsic graph \(y=\psi(x,a,b,c)\), the horizontal slope is governed by
\[
 \partial_x\psi-\partial_a\frac{\psi^2}{2}
 -\partial_b\frac{\psi^3}{6}
 -x\partial_c\frac{\psi^2}{2}.
\]
Introducing a kinetic parameter \(\xi\), define
\begin{equation}\label{eq:Lxi}
 L_\xi=\partial_x-\xi\partial_a-\frac{\xi^2}{2}\partial_b-x\xi\partial_c.
\end{equation}
The exact commutator identities are
\begin{align}
 [L_\xi,\partial_\xi]
 &=\partial_a+\xi\partial_b+x\partial_c,\label{eq:kin1}\\
 [L_\xi,[L_\xi,\partial_\xi]]&=\partial_c,\label{eq:kin2}\\
 [\partial_\xi,[L_\xi,\partial_\xi]]&=\partial_b,\label{eq:kin3}\\
 [L_\xi,L_\eta]&=(\xi-\eta)\partial_c.\label{eq:kin4}
\end{align}
These identities show that the missing top-layer estimate is a critical kinetic
transfer-of-regularity statement.  The closest available trajectory-based theorem reaches
the critical regularity in a Besov class with fine index \(\infty\)~\cite{Niebel2026}; the
desired result asks for a finite distribution exponent, or equivalently a polynomial bound
on the number of bad logarithmic scales.

There is also a Rumin-complex formulation.  The horizontal gradient
\(d_cf=(Xf,Yf)\) is not an arbitrary \(L^1\) vector field: it satisfies the compatibility
relation \(d_c(d_cf)=0\).  A successful proof should exploit this cancellation to solve a
multiscale horizontal divergence equation.  For example, standard
\(L^6\)--\(L^{6/5}\), \(L^1\)--\(L^\infty\), and Hahn--Banach duality reduces the strong
top-layer estimate at exponent \(6\) to the following construction.  For every family
\(\phi_t\) satisfying
\[
 \norm{\phi}_{L^{6/5}((0,\infty),\dd t/t;L^\infty(C))}\le1,
\]
one seeks a horizontal vector field \(\Psi\) with
\begin{equation}\label{eq:dual}
 \operatorname{div}_H\Psi
 =\int_0^\infty
 \frac{\phi_t(\,\cdot\,\exp(-tU))-\phi_t}{t^{1/3}}\frac{\dd t}{t},
 \qquad \norm{\Psi}_\infty\less1.
\end{equation}
Indeed, integration by parts would then bound the dual pairing by \(\HH_C(f)\).  Solving
each scale separately causes a logarithmic divergence; the desired theorem is exactly the
missing cancellation across scales.

Recent endpoint Poincar\'e and Hodge estimates on the Cartan group
\cite{BaldiRosa2026}, critical kinetic Besov estimates \cite{Niebel2026}, and nonlocal
Sobolev--BV characterizations on Carnot groups \cite{SerraCassanoZambanini2026} are
highly relevant to this formulation.  The Cartan estimates are spatial, the kinetic theorem
reaches the critical regularity with fine index \(\infty\), and none of the three papers
states the directional finite logarithmic-scale summability in
\eqref{eq:cartan-weak-target}.

\section{Counterexample audit and literature status}\label{sec:literature}

Ryoo's version of record, accepted on March 22, 2026 and available online in April
2026 (with issue publication listed for August 1, 2026), still states the endpoint problem
as Questions 38 and 42 and Conjecture 43
\cite{Ryoo2026}.  The sharp Heisenberg inputs are the \(q=2\) result in dimensions at
least five \cite{NaorYoung2018} and the sharp \(q=4\) result in dimension three
\cite{NaorYoung2022}.  The theorem that general nonabelian nilpotent groups do not
embed bi-Lipschitzly into \(L^1\) is qualitative and does not provide a finite
scale-summability exponent \cite{EBGLD2023}.

A literature search through June 19, 2026 did not locate a later proof or counterexample
for Ryoo's finite-exponent endpoint conjecture.  Several plausible counterexample
sources were examined:
\begin{itemize}[leftmargin=2em]
\item pathological constant-normal sets in the Engel and Cartan groups;
\item translated homogeneous cones in the Cartan group;
\item critical kinetic examples of De Lellis--Westdickenberg type;
\item rough intrinsic graphs in higher-step groups.
\end{itemize}
None of these produced a verified divergence of every finite scale norm.  In the explicit
Cartan cone models, the top-layer translation modulus appears at least as good as the
critical homogeneity, so they do not presently furnish a counterexample.  This negative
search result is not a proof that no counterexample exists.

\section{Final formulation of the remaining problem}\label{sec:final}

After all reductions, the first unresolved universal statement can be written without any
auxiliary group theory.

\begin{conjecture}[Weak Cartan endpoint]\label{conj:weak-cartan}
There exists \(1<r<\infty\) such that every \(f\in C_c^\infty(C)\) satisfies
\[
 \sup_{\lambda>0}\lambda
 \abs{\left\{x\in\R:
 e^{-x/3}\int_C\abs{f(g\exp(e^xU))-f(g)}\dd g>\lambda
 \right\}}^{1/r}
 \less_r\int_C(\abs{Xf}+\abs{Yf}).
\]
\end{conjecture}

By \cref{thm:cartan-equivalence}, this conjecture is equivalent to a positive resolution
of the endpoint problem for every step-three nilpotent group with every bracket-generating
left-invariant horizontal structure.  By
\cref{cor:weak-suffices}, it immediately yields strong estimates at every larger
exponent.  Alternatively, the stronger noncentral weak seed \eqref{eq:Tweak} with
\(q_2=4\) would imply every strong step-three exponent \(p>6\), and a weak rank-two
seed on \(F_{2,s}\) would propagate to arbitrary step by \cref{thm:ranktwo}.

The final attempt therefore does not close the conjecture, but it reduces the first hard
case to a strictly weaker and more concrete target than the original strong inequality:
a polynomial distribution estimate for the bad scales of one Cartan translation profile.

\begin{thebibliography}{99}

\bibitem{BaldiRosa2026}
A.~Baldi and F.~Rosa.
\newblock \(L^p\)-Hodge decomposition and global integral estimates on the Cartan group.
\newblock arXiv:2604.15206, 2026.

\bibitem{EBGLD2023}
S.~Eriksson-Bique, C.~Gartland, E.~Le Donne, L.~Naples, and S.~Nicolussi Golo.
\newblock Nilpotent groups and bi-Lipschitz embeddings into \(L^1\).
\newblock \emph{International Mathematics Research Notices}, 2023(12):10759--10797, 2023.

\bibitem{Marchi2014}
M.~Marchi.
\newblock Regularity of sets with constant intrinsic normal in a class of Carnot groups.
\newblock \emph{Annales de l'Institut Fourier}, 64(2):429--455, 2014.

\bibitem{NaorYoung2018}
A.~Naor and R.~Young.
\newblock Vertical perimeter versus horizontal perimeter.
\newblock \emph{Annals of Mathematics}, 188(1):171--279, 2018.

\bibitem{NaorYoung2022}
A.~Naor and R.~Young.
\newblock Foliated corona decompositions.
\newblock \emph{Acta Mathematica}, 229(1):55--200, 2022.

\bibitem{Niebel2026}
L.~Niebel.
\newblock Transfer of regularity by kinetic mollification along critical trajectories.
\newblock arXiv:2605.13582v2, 2026.

\bibitem{SerraCassanoZambanini2026}
F.~Serra Cassano and K.~Zambanini.
\newblock Characterizations of Sobolev and BV functions on Carnot groups.
\newblock arXiv:2603.28996, 2026.

\bibitem{Ryoo2026}
S.-Y.~Ryoo.
\newblock Quantitative nonembeddability of groups of polynomial growth into uniformly convex spaces.
\newblock \emph{Journal of Functional Analysis}, article 111491, 2026.
\newblock DOI: 10.1016/j.jfa.2026.111491; arXiv:2207.11305v2.

\end{thebibliography}

\end{document}
