\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{center}
{\Large Chaotic operators need not be frequently hypercyclic}\\[4pt]
{\normalsize Literature-status packet for arXiv:1005.1416}
\end{center}

\section*{Status}

This is a \texttt{literature\_already\_answered} packet.  It records a later
answer to one subquestion explicitly mentioned in De la Rosa--Frerick--Grivaux--Peris,
\emph{Frequent hypercyclicity, chaos, and unconditional Schauder
decompositions}, arXiv:1005.1416 \cite{DFGP}.

\section*{Source question}

In the introduction, immediately after proving that complex separable Banach
spaces with unconditional Schauder decompositions support operators which are
both chaotic and frequently hypercyclic, the source states:
\begin{quote}
``it is still an open question to know whether every chaotic operator on a
Banach space is automatically frequently hypercyclic.''
\end{quote}
This is distinct from the broader characterization question in the source and
from the later real-space question about frequent hypercyclicity on Gowers'
real space.

\section*{Supporting answer}

Quentin Menet's later paper \emph{Linear chaos and frequent hypercyclicity},
arXiv:1410.7173 \cite{Menet}, explicitly formulates the same problem:
\begin{quote}
``Is every chaotic operator frequently hypercyclic?''
\end{quote}
Theorem 1.2 of that paper constructs a chaotic operator \(T\) on
\(\ell^1\) which is not \(U\)-frequently hypercyclic and therefore is not
frequently hypercyclic.  This gives a negative answer to the source
subquestion.

\section*{Scope limitations}

This is not a new result from this run.  It is a later-literature answer
recorded to prevent rediscovery work on this subquestion.  The source's broad
Question 1.1, asking for a characterization of complex separable Banach spaces
supporting frequently hypercyclic or chaotic operators, remains outside this
packet.  The source's final real-space question about whether the real
Gowers space \(X_G\) supports a frequently hypercyclic operator is also not
settled here.

\begin{thebibliography}{9}
\bibitem{DFGP}
M. De la Rosa, L. Frerick, S. Grivaux, and A. Peris,
\emph{Frequent hypercyclicity, chaos, and unconditional Schauder decompositions},
arXiv:1005.1416.

\bibitem{Menet}
Q. Menet,
\emph{Linear chaos and frequent hypercyclicity},
arXiv:1410.7173.
\end{thebibliography}

\end{document}
