\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note: The Mixed-Norm Matrix Greedy-Basis Problem}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-26}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.  The question in
Dilworth--Freeman--Odell--Schlumprecht \cite{DFOS} is answered negatively by
Schechtman \cite{Schechtman}.

\paragraph{Source question.}
In the introduction of \cite{DFOS}, immediately after Theorem 2a, the authors
write:
\[
  \text{Assume } 1<p\ne q<\infty. \text{ Does }
  \ell_q(\ell_p)=(\oplus \ell_p)_{\ell_q}
  \text{ have a greedy basis?}
\]
This is the extracted target from arXiv:0910.3867.

\paragraph{Supporting answer.}
Schechtman \cite{Schechtman} explicitly identifies the same question.  In the
introduction he writes that Dilworth, Freeman, Odell and Schlumprecht raised
the question whether
\[
  \Big(\bigoplus_{n=1}^{\infty} \ell_p\Big)_{\ell_q},
  \qquad 1<p\ne q<\infty,
\]
has greedy bases, and then states that these spaces do not have greedy bases.
Theorem 1 in \cite{Schechtman} proves the stronger assertion that each
normalized unconditional basis of
\[
  \Big(\bigoplus_{n=1}^{\infty} \ell_p\Big)_{\ell_q},
  \qquad 1\le p\ne q<\infty,
\]
has one subsequence equivalent to the unit vector basis of $\ell_p$ and another
equivalent to the unit vector basis of $\ell_q$. Consequently none of these
spaces has a greedy basis.

\paragraph{Why this answers the source problem.}
The source problem is exactly the reflexive subrange
$1<p\ne q<\infty$ of Schechtman's Theorem 1.  The answer is therefore negative:
$\ell_q(\ell_p)$ does not have a greedy basis when $1<p\ne q<\infty$.
The supporting author explicitly cites the source paper and states that this
solves the problem, so this packet is a literature-status record rather than a
new proof packet.

\paragraph{Scope limitations.}
No part of the stated source problem remains open in this packet.  Schechtman's
additional endpoint conclusions for mixed $c_0$ variants are not part of the
source question recorded here.

\paragraph{Search evidence.}
The local parsed source for arXiv:0910.3867 contains the problem immediately
after Theorem 2a.  The local parsed source for arXiv:1310.2371 contains the
explicit DFOS citation, the phrase that the paper solves the raised question,
and Theorem 1.  Web search for the exact phrases
\texttt{"ell\_q(ell\_p)" "greedy basis"} and
\texttt{"Greedy bases for Besov spaces" "ell\_q(ell\_p)"} returned
arXiv:1310.2371 as the direct answer.

\begin{thebibliography}{9}
\bibitem{DFOS}
S. J. Dilworth, D. Freeman, E. Odell, and Th. Schlumprecht,
\emph{Greedy bases for Besov spaces},
arXiv:0910.3867.

\bibitem{Schechtman}
Gideon Schechtman,
\emph{No greedy bases for matrix spaces with mixed $\ell_p$ and $\ell_q$ norms},
arXiv:1310.2371.
\end{thebibliography}

\end{document}
