\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Ssp}{\mathcal S}
\newcommand{\ph}{\varphi}

\begin{document}

\section*{Human Review: Schlumprecht Szlenk-radius converse}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Companion notation rewrite: \texttt{human\_requested\_better\_notation.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Manually checked.

\noindent Verdict: Appears correct.

\section*{Human Comments}

The proposed proof appears to be correct.  It gives the reverse inequality
for the Szlenk-radius formula in Schlumprecht's space, and therefore appears
to complete the converse left open in the source paper.

The idea of the proof is to show that, if a vector has norm smaller than the
proposed radius, then, after harmlessly reducing to the finitely supported
case, one can perturb it far out by
\[
  \pm \alpha e_N,
\]
where \(\alpha>\varepsilon/2\).  These two perturbations are
\[
  x+\alpha e_N
  \quad\text{and}\quad
  x-\alpha e_N.
\]
They are weakly close to \(x\), because \(e_N\to 0\) weakly, but they are
separated by
\[
  \|(x+\alpha e_N)-(x-\alpha e_N)\|_{\Ssp}
  =
  2\alpha
  >
  \varepsilon.
\]
Thus they witness diameter \(>\varepsilon\) in every weak neighbourhood of
\(x\), provided they remain in the unit ball.

The key technical step is exactly this unit-ball control:
\[
  \|x\pm \alpha e_N\|_{\Ssp}\le 1
\]
whenever
\[
  \|x\|_{\Ssp}<a_\alpha,
  \qquad
  a_\alpha=
  \inf_{n\ge 1}\frac{\ph(n+1)-\alpha}{\ph(n)}.
\]
This is the part where one has to control the size of the new vectors in the
recursive Schlumprecht norm.  The scalar majorant \(M_\alpha\), the
logarithmic product lemma, and the local comparison argument are all used to
prove precisely this point.

I checked the main scalar estimate and the comparison argument.  The
argument appears sound.  The original notation was somewhat difficult to
follow, so I requested a separate improved-notation rewrite of the proof.
That rewrite is included only as a human-requested notational aid; it is not
the original automatic output.

\section*{Short Version}

The proof works by taking \(x\) below the proposed radius and perturbing it
far out by \(\pm\alpha e_N\).  The perturbations are weakly close to \(x\)
and are more than \(\varepsilon\) apart.  The main work is to show that both
perturbed vectors remain in the unit ball of Schlumprecht's space.  Once this
is proved, the reverse Szlenk-radius inclusion follows by the standard
density and weak-closedness argument.

\section*{Literature and Follow-Up}

This appears to be a serious candidate full solution to the converse problem
in the source paper.  I recommend checking the argument with the authors,
both to confirm correctness and to understand whether the result or method
was already known to them.

\section*{Review Outcome}

Archive this packet as an apparently correct candidate full solution.  The
main mathematical content is the far-coordinate perturbation argument and
the scalar estimate controlling the Schlumprecht norm after adding
\(\pm\alpha e_N\).

\end{document}
