\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Xp}{\mathsf{X}_p}

\title{Literature Status: Main Metric \(\Xp\) Conjectures Answered}
\author{Source arXiv:1408.5819; support arXiv:1601.03332}
\date{2026-07-03}

\begin{document}
\maketitle

\paragraph{Status.}
\emph{Literature already answered.}  The later paper arXiv:1601.03332 explicitly states that it resolves positively Conjectures 1.5, 1.8, and 1.12 from arXiv:1408.5819.

\paragraph{Source questions.}
Naor--Schechtman, arXiv:1408.5819, poses the following central metric \(\Xp\) conjectures:
\begin{itemize}
\item Conjecture 1.5: for every \(p>2\), the metric \(\Xp\) inequality for \(L_p\) should hold with the sharp scaling parameter \(m\gtrsim_p \sqrt{n/k}\).
\item Conjecture 1.8: for \(2<q<p\), if \((L_q,\|x-y\|_q^\theta)\) embeds bi-Lipschitzly into \(L_p\), then \(\theta\le q/p\).
\item Conjecture 1.12: for \(2<q<p\), the distortion of the grid \([m]_q^n\) into \(L_p\) should be asymptotic, up to constants depending only on \(p,q\), to
\[
\min\left\{
n^{\frac{(p-q)(q-2)}{q^2(p-2)}},
m^{1-\frac{2}{q}}
\right\}.
\]
\end{itemize}

\paragraph{Supporting answer.}
Naor, arXiv:1601.03332, states in the introduction that ``Conjecture 1.5, Conjecture 1.8 and Conjecture 1.12'' of arXiv:1408.5819 all have positive answers.  The concrete results are:
\begin{itemize}
\item Theorem 1: for \(p\ge 2\), every \(f:\Z_{8m}^n\to L_p\) satisfies the metric \(\Xp\) inequality when \(m\ge \sqrt{n/k}\), giving the sharp scaling parameter.
\item Theorem 2: for \(2<q<p\), the maximal snowflake exponent for \(L_q\) into \(L_p\) is exactly \(q/p\).
\item Theorem 3: for \(2\le q<p\), the grid distortion satisfies
\[
c_p([m]_q^n)\asymp_{p,q}
\min\left\{
n^{\frac{(p-q)(q-2)}{q^2(p-2)}},
m^{1-\frac{2}{q}}
\right\}.
\]
\end{itemize}

\paragraph{Scope.}
This status packet clears those three main conjectures, not every open item in arXiv:1408.5819.  In particular, arXiv:1601.03332 says that the convolution approach posed as Question 6.1 in arXiv:1408.5819 remains open.

\begin{thebibliography}{9}
\bibitem{NS14}
Assaf Naor and Gideon Schechtman.
\newblock \emph{Metric \(X_p\) inequalities}.
\newblock arXiv:1408.5819, 2014.

\bibitem{N16}
Assaf Naor.
\newblock \emph{Discrete Riesz transforms and sharp metric \(X_p\) inequalities}.
\newblock arXiv:1601.03332, 2016.
\end{thebibliography}

\end{document}

