\documentclass[11pt]{amsart}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbf{E}}

\title{Literature Status Note for arXiv:1610.05199}
\author{agent\_lane\_10}
\date{2026-06-21}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature\_already\_answered.}
The open-question signal in van Handel's
\emph{Chaining, Interpolation, and Convexity II: The contraction principle}
(arXiv:1610.05199) points to the discussion after Corollary 3.3 and to
Section 3.3.  There the author asks whether the positive-semidefinite
assumption in the random-matrix chaining bounds can be weakened, and notes
that Latala's conjecture for symmetric Gaussian matrices with independent,
non-identically distributed entries would follow from such an extension.

\section*{Source Question}

In arXiv:1610.05199, after Corollary 3.3, the paper observes that the
positive-semidefinite hypothesis ensures that the auxiliary functional
$\vert\!\vert\!\vert\cdot\vert\!\vert\!\vert$ is a norm and that
$\|v\|_z \leq
\vert\!\vert\!\vert v\vert\!\vert\!\vert
\vert\!\vert\!\vert z\vert\!\vert\!\vert$.
It then asks whether this positive-semidefinite assumption can be weakened.
Section 3.3 makes the consequence explicit: for a symmetric Gaussian
matrix with independent entries $X_{ij}\sim N(0,b_{ij}^2)$, Latala's
conjecture predicts
\[
        \E\|X\| \asymp
        \E\max_i\Big(\sum_j X_{ij}^2\Big)^{1/2}.
\]

\section*{Answering Source}

The primary answering paper is Latala--van Handel--Youssef,
\emph{The dimension-free structure of nonhomogeneous random matrices}
(arXiv:1711.00807; Invent. Math. 214 (2018), 1031--1080).
Its abstract states that the main result settles, for $p=\infty$, a
conjecture of the first author.  Theorem 1.1 proves that if
$X_{ij}=b_{ij}g_{ij}$ is a symmetric matrix with independent standard
Gaussian variables $g_{ij}$ for $i\geq j$, then
\[
        \E\|X\|_{S_\infty}
        \asymp
        \max_i\Big(\sum_j b_{ij}^2\Big)^{1/2}
        + \max_{ij} b_{ij}^{*}\sqrt{\log i},
\]
with universal constants.  The preceding paper arXiv:1502.05003 identifies
this expression with the row-norm formulation of Latala's conjecture, and
a later contextual source, arXiv:2112.14413, explicitly records that the
Latala--van Handel--Youssef result finally answered the conjecture in the
affirmative.

\section*{Scope and Caveat}

This is an already-known literature answer, not a new proof produced in
the run.  The packet records that the main open consequence highlighted in
arXiv:1610.05199, namely Latala's Gaussian spectral-norm conjecture, was
settled by arXiv:1711.00807.  It does not assert that the particular
positive-semidefinite chaining corollary from arXiv:1610.05199 was itself
extended verbatim.

\section*{Search Notes}

Cheap run indexes were searched for arXiv:1610.05199, contraction
principle, Latala, Gaussian random matrices, positive semidefinite
assumption, and the label \texttt{supernck}.  No existing solution,
attempt, proof-gap, or registry entry for this source question was found.
Local source search found arXiv:1711.00807 as the primary answer and
arXiv:2112.14413 as independent later confirmation of the answer status.

\end{document}
