\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newcommand{\R}{\mathbb R}
\newcommand{\aext}{\operatorname{ae}}
\newcommand{\lip}{\operatorname{Lip}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\F}{\mathcal F}
\newcommand{\nuone}{\nu_1}

\title{A Symmetric Four-Leaf Tree Subcase of Basso's \(\aext(4)\) Conjecture}
\author{FA/Banach smoke run, lane 17}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Source Problem}

The source paper is Giuliano Basso, \emph{Absolute Lipschitz extendability and
linear projection constants}, arXiv:2104.14238.  Proposition 1.4 proves
\[
   \frac{5+4\sqrt2}{7}\leq \aext(4)\leq \frac{3+6\sqrt2}{7},
\]
and the introduction states that numerical simulations strongly suggest that
the lower bound is sharp, i.e.
\[
   \aext(4)=\frac{5+4\sqrt2}{7}.
\]
The lower-bound example is a four-point rectangle in \(\ell_\infty^2\); as a
metric space it is the four leaves of a weighted tree with two internal
vertices, four equal pendant edges, and a central edge of length \(\sqrt2-1\).

\section*{Result}

For \(r\geq 0\), let \(T_r\) be the weighted tree with vertices
\[
  p_1,p_2,q_1,q_2,u,v,
\]
edges \(p_1u,p_2u,q_1v,q_2v\) of length \(1\), and central edge \(uv\) of
length \(r\).  Let
\[
  X_r=\{p_1,p_2,q_1,q_2\}
\]
with the metric induced from \(T_r\).

\begin{theorem}
\[
   \aext(X_r)=\frac{(r+2)(r+3)}{r^2+3r+4}\qquad (r\geq 0).
\]
Consequently
\[
   \sup_{r\geq0}\aext(X_r)=\frac{5+4\sqrt2}{7},
\]
with equality at \(r=\sqrt2-1\).
\end{theorem}

\section*{Proof Intuition}

Basso's theorem turns the absolute Lipschitz extension constant of a finite
metric space into a relative projection constant of its Lipschitz-free space.
For a tree this becomes especially concrete: the free space over the six
vertices of \(T_r\) is \(\ell_1^5\), one coordinate per edge.  The four-leaf
subspace is a three-dimensional ``balanced flow'' subspace.  We compute its
relative projection constant exactly by giving both sides of the projection
constant duality: an explicit projection for the upper bound and an explicit
trace witness for the lower bound.

\section*{Proof}

For \(r>0\), the injective hull of \(X_r\) is the metric tree \(T_r\).  For
\(r=0\), this is understood after identifying the two internal vertices; the
formula below also follows by continuity, or directly from Basso's discrete
\(n\)-pod computation.  Let
\[
  Y_r=\{p_1,p_2,q_1,q_2,u,v\}.
\]
Any Lipschitz map defined on \(Y_r\) extends to the whole tree by affine
interpolation along the edges without increasing the Lipschitz constant. Hence
Basso's reduction to the injective hull gives
\[
  \aext(X_r)=\nu(X_r,Y_r)
          =\lambda(\F(X_r),\F(Y_r)).
\]

Identify \(\F(Y_r)\) with \(\ell_1^5\) by the edge basis, scaling the central
edge coordinate by its length.  We use coordinates \((a,b,z,c,d)\), where
\(a,b\) are the two left pendant-edge coordinates, \(c,d\) the two right
pendant-edge coordinates, and \(z\) the scaled central coordinate.  The leaf
subspace is
\[
 E_r=\F(X_r)
 =\left\{(a,b,z,c,d):\ a+b+c+d=0,\quad
 z=\frac r2(a+b-c-d)\right\}\subset \ell_1^5 .
\]
Thus it remains to compute \(\lambda(E_r,\ell_1^5)\).

Put
\[
  D=r^2+3r+4,\qquad
  t_r=\frac{(r+2)(r+3)}{D},\qquad
  q=\frac{r+3}{2D}.
\]
For \(x=(a,b,z,c,d)\in\ell_1^5\), define
\[
  s=a+b+c+d,\qquad
  h=z-\frac r2(a+b-c-d),
\]
and set \(Q_r x=(a',b',z',c',d')\), where
\[
\begin{aligned}
a'&=a-\frac{s}{4}+qh,              & b'&=b-\frac{s}{4}+qh,\\
c'&=c-\frac{s}{4}-qh,              & d'&=d-\frac{s}{4}-qh,\\
z'&=z+(2rq-1)h.
\end{aligned}
\]
A direct calculation gives \(a'+b'+c'+d'=0\) and
\[
 z'=\frac r2(a'+b'-c'-d').
\]
Also \(Q_r x=x\) whenever \(x\in E_r\).  Hence \(Q_r\) is a projection from
\(\ell_1^5\) onto \(E_r\).

With respect to the standard basis of \(\ell_1^5\), the column \(\ell_1\)-norms
of \(Q_r\) are all equal to \(t_r\).  Indeed the relevant signs are fixed for
\(r\geq0\), since \(qr<1/2\), and the first column has norm
\[
 \left(\frac34-\frac{qr}{2}\right)
 +\left(\frac14+\frac{qr}{2}\right)
 +\frac r2(1-2qr)
 +2\left(\frac14-\frac{qr}{2}\right)
 = \frac32+\frac r2-q(r^2+r)=t_r,
\]
while the central column has norm \(2q(r+2)=t_r\); the remaining pendant
columns are symmetric.  Since the operator norm on \(\ell_1^5\) is the maximum
column \(\ell_1\)-norm, \(\lambda(E_r,\ell_1^5)\leq t_r\).

For the reverse inequality we use the standard trace duality for relative
projection constants in finite-dimensional polyhedral spaces: if
\(A(E_r)\subset E_r\) and \(\nu_1(A)\leq1\), then every projection \(P\) from
\(\ell_1^5\) onto \(E_r\) satisfies
\[
   \|P\|\geq \tr(A|_{E_r}).
\]
Here \(\nu_1\) denotes the nuclear norm as an operator on \(\ell_1^5\), so
\(\nu_1(A)=\sum_i\max_j |a_{ij}|\).

Let
\[
S=\begin{pmatrix}
 1&-1& 1&-1&-1\\
-1& 1& 1&-1&-1\\
 1& 1& 1&-1&-1\\
-1&-1&-1& 1&-1\\
-1&-1&-1&-1& 1
\end{pmatrix}
\]
and \(A=\operatorname{diag}(\alpha,\alpha,\beta,\alpha,\alpha)S\), where
\[
  \alpha=\frac{r+2}{2D},\qquad
  \beta=\frac{r(r+1)}{D}.
\]
The row maxima sum to \(4\alpha+\beta=1\), hence \(\nu_1(A)=1\).  On the basis
\[
 e_1=(1,-1,0,0,0),\quad
 e_2=(0,0,0,1,-1),\quad
 e_3=(1,1,2r,-1,-1)
\]
of \(E_r\), the matrix \(A\) acts diagonally:
\[
  Ae_1=\frac{r+2}{D}e_1,\qquad
  Ae_2=\frac{r+2}{D}e_2,\qquad
  Ae_3=\frac{r^2+3r+2}{D}e_3 .
\]
In particular \(A(E_r)\subset E_r\), and therefore
\[
 \lambda(E_r,\ell_1^5)
 \geq \tr(A|_{E_r})
 =\frac{r+2}{D}+\frac{r+2}{D}+\frac{r^2+3r+2}{D}
 =\frac{(r+2)(r+3)}{D}.
\]
Together with the explicit projection this proves the formula for
\(\aext(X_r)\).

Finally,
\[
  \frac{d}{dr}\frac{(r+2)(r+3)}{r^2+3r+4}
  =-\frac{2(r^2+2r-1)}{(r^2+3r+4)^2}.
\]
The unique critical point on \([0,\infty)\) is \(r=\sqrt2-1\), where the
maximum value is
\[
  \frac{5+4\sqrt2}{7}.
\]
\(\square\)

\section*{Verification Notes}

The script \texttt{code/verify\_symmetric\_tree.py} evaluates the explicit
projection and trace witness for representative values of \(r\).  It is only a
sanity check; the proof above is symbolic.

The source paper itself contains the lower-bound example at Proposition 1.4
and proves the general reduction from absolute Lipschitz extendability to
relative projection constants of Lipschitz-free spaces.  Web and local-index
searches on the phrases ``four-leaf absolute Lipschitz extendability'',
``two-cherry projection constant'', and the exact formula
\((r+2)(r+3)/(r^2+3r+4)\) found no prior statement of this one-parameter
subfamily formula.

\section*{Limitations}

This does not prove Basso's full conjecture for all four-point metric spaces.
It proves the conjectured value for the symmetric tree-like family containing
the proposed extremal example.  The general four-point injective hull may have
a genuine two-dimensional rectangular cell or unequal pendant lengths; those
cases remain outside this packet.

\section*{References}

\begin{itemize}
\item Giuliano Basso, \emph{Absolute Lipschitz extendability and linear
projection constants}, arXiv:2104.14238.
\item The proof uses the reduction and trace-duality framework stated in the
source paper, especially Theorem 1.2, Lemma 2.6, and Proposition 4.2 there.
\end{itemize}

\end{document}
