\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath,amssymb}

\title{Literature Status: Unconditional Bases and SCD Spaces}
\author{Run \texttt{fa\_banach\_001}, agent lane 8}
\date{2026-06-14}

\begin{document}
\maketitle

\section*{Status}

\textbf{literature\_already\_answered.}  The open question extracted from
arXiv:2311.03064 is answered negatively in the later paper arXiv:2603.12947.
This packet records provenance only; it is not an original proof from the run.

\section*{Source Question}

The source paper is Johann Langemets, Marcus Loo, Miguel Martin, and Abraham
Rueda Zoca, \emph{Slicely countably determined points in Banach spaces},
arXiv:2311.03064.  In the introduction, immediately after recalling that the
unit ball of every Banach space with a one-unconditional basis is SCD, the
authors state:
\[
\text{``It is an open question whether every Banach space with an
unconditional basis is an SCD space.''}
\]

\section*{Supporting Answer}

The supporting paper is Marcus Loo and Yoel Perreau, \emph{A Banach space with
an unconditional basis which is not slicely countably determined},
arXiv:2603.12947.  Its Introduction explicitly restates the same problem as
Question 1.2:
\[
\text{``Let }X\text{ be a Banach space with an unconditional basis. Is }X
\text{ necessarily an SCD space?''}
\]
The paper then says that it provides a negative answer to Question 1.2.  Its
Theorem 1.3 states that the positive unit ball \(B_{X_T}^+\) of the binary
tree space is not an SCD set and, in particular, \(X_T\) is a Banach space
with an unconditional basis which fails to be SCD.

\section*{Scope}

The answer is negative for the exact unconditional-basis SCD-space question.
The supporting authors explicitly know they are answering this question: they
state it as Question 1.2 and identify Theorem 1.3 as the negative answer.  No
claim is made here about the later paper's separate open questions, such as
countable \(\pi\)-bases or the existence of a Banach space with an
unconditional basis whose unit ball has no SCD point.

\section*{Search Evidence}

The source arXiv id, title keywords, and SCD/unconditional-basis keywords were
searched in the run's cheap indexes.  No existing packet recorded the
arXiv:2311.03064 source-question relation.  A web search for
\texttt{"every Banach space with an unconditional basis" "SCD"} found
arXiv:2603.12947, whose abstract and introduction state the negative answer.
The run already contains a separate packet about a different question from
arXiv:2603.12947, namely \(k\)-unconditional renormings; this packet records
only the later-paper answer to the arXiv:2311.03064 unconditional-basis
question.

\begin{thebibliography}{9}

\bibitem{LangemetsLooMartinRuedaZoca2023}
J. Langemets, M. Loo, M. Martin, and A. Rueda Zoca,
\emph{Slicely countably determined points in Banach spaces},
arXiv:2311.03064, 2023.
\url{https://arxiv.org/abs/2311.03064}.

\bibitem{LooPerreau2026}
M. Loo and Y. Perreau,
\emph{A Banach space with an unconditional basis which is not slicely countably determined},
arXiv:2603.12947, 2026.
\url{https://arxiv.org/abs/2603.12947}.

\end{thebibliography}

\end{document}
