\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\R}{\mathbb R}
\newcommand{\calO}{\mathcal O}

\title{A Scattered-Orbit Partial Result for Invariant Strictly Convex Renormings}
\author{fa\_banach\_001, agent\_lane\_16}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Source Question}

The source paper is Michal Doucha, \emph{Invariant strictly convex renormings},
arXiv:2508.16182v1.  Question 7.1 asks:
\begin{quote}
Do there exist a separable Banach space \(X\) and a surjective linear isometry
\(T:X\to X\) such that there is no \(T\)-invariant strictly convex renorming of
\(X\)?
\end{quote}
Equivalently, this is the cyclic, or \(\Z\)-action, case of the invariant
strict convex renorming problem.  Question 7.2 asks the corresponding question
for countable amenable groups.

\section*{Result}

This packet proves a partial positive result for induced actions on \(C(K)\).
It does not solve Questions 7.1 or 7.2 in full, but it removes a natural source
of possible cyclic counterexamples.

\begin{theorem}\label{thm:scattered-orbits}
Let \(G\) be a group acting by homeomorphisms on a compact metrizable space
\(K\).  Assume that, for every \(p\in K\), the orbit closure
\[
K_p=\overline{G\cdot p}
\]
is scattered.  Then the induced isometric action of \(G\) on \(C(K)\) admits an
equivalent \(G\)-invariant strictly convex norm.
\end{theorem}

\begin{corollary}\label{cor:interval}
For every homeomorphism \(h:[0,1]\to[0,1]\), the composition isometry
\[
Tf=f\circ h
\qquad (f\in C[0,1])
\]
admits an equivalent \(T\)-invariant strictly convex norm on \(C[0,1]\).
\end{corollary}

\section*{Idea of the Proof}

The key observation is that an invariant strictly convex renorming can be built
from countably many equivariant maps into already strictly convex \(G\)-spaces,
provided those maps separate points.  For \(C(K)\), a nonzero function is
detected on some orbit closure \(K_p\).  If \(K_p\) is scattered and metrizable,
then \(C(K_p)\) is separable and has the Radon--Nikodym property.  Lancien's
invariant LUR renorming theorem gives a \(G\)-invariant locally uniformly
rotund norm on \(C(K_p)\), hence a strictly convex one.  The restriction maps
\[
C(K)\to C(K_p)
\]
therefore supply enough equivariant strictly convex coordinates to separate
all nonzero functions in \(C(K)\).

\section*{Proof}

\begin{lemma}\label{lem:separating-family}
Let \(X\) be a separable Banach space and let \(G\) act on \(X\) by linear
isometries.  Suppose that for every nonzero \(x\in X\) there are a Banach
\(G\)-space \(Y_x\), an equivalent \(G\)-invariant strictly convex norm on
\(Y_x\), and a bounded \(G\)-equivariant linear map
\[
A_x:X\to Y_x
\]
such that \(A_xx\neq 0\).  Then \(X\) admits an equivalent \(G\)-invariant
strictly convex norm.
\end{lemma}

\begin{proof}
For each nonzero \(x\in X\), fix such a map \(A_x\) and write
\(|\cdot|_x\) for the chosen invariant strictly convex norm on \(Y_x\).
The sets
\[
U_x=\{z\in X: |A_xz|_x> |A_xx|_x/2\}
\]
form an open cover of \(X\setminus\{0\}\).  Since \(X\) is separable, choose a
countable subcover \(U_{x_n}\), \(n\in\N\).  After multiplying each \(A_{x_n}\)
by a positive scalar, assume \(\|A_{x_n}\|\leq 1\), where the range norm is
\(|\cdot|_{x_n}\).

Let
\[
Y=\Big(\bigoplus_{n=1}^{\infty} Y_{x_n}\Big)_{\ell_2}
\]
with its diagonal \(G\)-action and its \(\ell_2\)-sum norm.  This norm is
\(G\)-invariant and strictly convex.  Define
\[
A:X\to Y,\qquad
A z=\big(2^{-n}A_{x_n}z\big)_{n=1}^{\infty}.
\]
The map \(A\) is bounded and \(G\)-equivariant.  It is injective: if
\(z\neq0\), then \(z\in U_{x_n}\) for some \(n\), so \(A_{x_n}z\neq0\).
Therefore
\[
\|z\|'=\|z\|_X+\|Az\|_Y
\]
is an equivalent \(G\)-invariant strictly convex norm on \(X\).  Indeed, the
first summand is an equivalent invariant norm and the second summand is a
strictly convex norm on \(X\) because \(A\) is injective.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:scattered-orbits}]
Let \(0\neq f\in C(K)\).  Pick \(p\in K\) with \(f(p)\neq0\).  The orbit
closure \(K_p=\overline{G\cdot p}\) is compact, metrizable, scattered, and
\(G\)-invariant.  The restriction map
\[
R_p:C(K)\to C(K_p),\qquad R_p(g)=g|_{K_p},
\]
is bounded, linear, and \(G\)-equivariant, and \(R_pf\neq0\).

Since \(K_p\) is compact metrizable, \(C(K_p)\) is separable.  Since \(K_p\) is
scattered, the classical \(C(K)\)-criterion gives that \(C(K_p)\) has the
Radon--Nikodym property.  Lancien's theorem says that every separable
\(G\)-Banach space with the Radon--Nikodym property admits an equivalent
\(G\)-invariant locally uniformly rotund norm.  In particular, \(C(K_p)\)
admits an equivalent \(G\)-invariant strictly convex norm.

Thus every nonzero \(f\in C(K)\) is detected by a bounded equivariant map into
a \(G\)-space with an invariant strictly convex norm.  Lemma
\ref{lem:separating-family} applies and gives the desired invariant strictly
convex renorming of \(C(K)\).
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:interval}]
If \(h\) is increasing and \(p\in[0,1]\), then either \(p\) is fixed, or \(p\)
lies in a component \((a,b)\) of \([0,1]\setminus \mathrm{Fix}(h)\).  On such a
component all iterates move monotonically toward one endpoint in positive time
and toward the other endpoint in negative time.  Hence
\[
\overline{\{h^n(p):n\in\Z\}}
\]
is either a singleton or a countable compact set with at most two accumulation
points.  It is scattered.

If \(h\) is decreasing, apply the same argument to the increasing
homeomorphism \(h^2\).  The \(h\)-orbit closure of \(p\) is the union of at most
two \(h^2\)-orbit closures, hence is again compact, countable, and scattered.
Theorem~\ref{thm:scattered-orbits} now applies with \(G=\Z\).
\end{proof}

\section*{Verification and Limitations}

The argument is purely structural; no computation is used.  The main external
inputs are standard: \(C(L)\) has the Radon--Nikodym property when \(L\) is
compact scattered, and Lancien's invariant LUR theorem for separable RNP
\(G\)-spaces.

The theorem does not cover orbit closures containing perfect minimal parts,
such as adding-machine components in the generic Cantor homeomorphism.  It
therefore does not settle the \(C(2^\mathbb N)\) generic-action question from
Doucha's Question 7.4, nor the full cyclic Question 7.1.

\section*{Novelty Check}

The run indexes were searched for arXiv:2508.16182, invariant strictly convex
renormings, cyclic/\(\Z\)-actions, and \(C(K)\) variants.  Web searches were
also made for exact phrases including ``T-invariant strictly convex
renorming'', ``Z-invariant strictly convex renorming'', ``cyclic group
invariant strictly convex renorming'', and related AFGR/Lancien terminology.
No exact prior answer to Questions 7.1--7.2 or to the scattered orbit-closure
subcase was found.  Because the proof is a short combination of known tools, it
should be treated as a likely-valid partial observation rather than a high
novelty full solution.

\section*{References}

\begin{itemize}
\item M. Doucha, \emph{Invariant strictly convex renormings},
arXiv:2508.16182v1, 2025.
\item G. Lancien, \emph{Dentability indices and locally uniformly convex
renormings}, Rocky Mountain J. Math. 23 (1993), 635--647.
\item R. Deville, G. Godefroy, and V. Zizler, \emph{Smoothness and Renormings
in Banach Spaces}, Pitman Monographs and Surveys in Pure and Applied
Mathematics 64, 1993.
\end{itemize}

\section*{Human Review Recommendation}

Check the separating-family lemma and the use of the \(C(K)\)-RNP criterion.
If those standard inputs are accepted, the packet gives a clean positive
subcase: single composition isometries on \(C[0,1]\) cannot witness a negative
answer to Doucha's cyclic question.

\end{document}
