\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{claim}{Claim}
\newcommand{\ellp}{\ell_p}

\title{Literature-Implied Partial Subcase for arXiv:1106.5020}
\author{FA/Banach run fa\_banach\_001}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_implied\_answer (partial subcase)} packet. It
does not claim a new proof of Mazur's general rotation problem. It records
that a later theorem of Dilworth and Randrianantoanina
\cite{DilworthRandrianantoanina2013} excludes a classical family of possible
non-Hilbertian counterexamples to the problem as stated by Ferenczi and
Rosendal \cite{FerencziRosendal2011}.

\section*{Source Problem}

Ferenczi and Rosendal recall Mazur's rotation problem in the following
isomorphic form: if $X$ is a separable Banach space whose isometry group acts
transitively on the sphere $S_X$, must $X$ be Hilbertian, i.e. isomorphic to
the separable Hilbert space?

The same source uses the standard hierarchy of symmetry notions. A norm is
transitive when every unit vector has full unit-sphere orbit under the
surjective linear isometries, and it is almost transitive when every such orbit
is dense. Hence
\[
  \hbox{transitive} \quad \Longrightarrow \quad \hbox{almost transitive}.
\]

\section*{Supporting Literature}

Dilworth and Randrianantoanina prove that the spaces $\ell_p$,
$1<p<\infty$, $p\ne 2$, and all infinite-dimensional subspaces of their
quotient spaces admit no equivalent almost transitive renormings. Their
abstract describes this as a step toward the Banach--Mazur rotation problem.
The paper's Theorem 2.4 gives the subspace-of-$\ell_p$ obstruction, and
Corollary 2.11 gives the quotient-space formulation.

\begin{theorem}[Dilworth--Randrianantoanina]
Let $1<p<\infty$ and $p\ne 2$. No infinite-dimensional subspace of a quotient
space of $\ell_p$ admits an equivalent almost transitive norm. In particular,
$\ell_p$ itself admits no equivalent almost transitive norm.
\end{theorem}

\section*{Implication for the Source Problem}

\begin{claim}
No Banach space isomorphic to $\ell_p$, $1<p<\infty$, $p\ne 2$, nor to an
infinite-dimensional subspace of a quotient space of such an $\ell_p$, can be a
non-Hilbertian counterexample to the isomorphic Mazur rotation problem recorded
in arXiv:1106.5020.
\end{claim}

\begin{proof}
Suppose that a Banach space $Y$ in one of the listed isomorphic classes had a
transitive norm. Choose an isomorphism from the corresponding model space $X$
onto $Y$ and pull the norm back to $X$. The pulled-back norm is equivalent to
the original norm on $X$, and its isometry group is conjugate to the isometry
group of $Y$ with the transitive norm. Thus $X$ would admit an equivalent
transitive norm.

Every transitive norm is almost transitive. This would give an equivalent
almost transitive renorming of $X$, contradicting the theorem of Dilworth and
Randrianantoanina. Therefore the listed isomorphic classes cannot supply
counterexamples to the source problem.
\end{proof}

\section*{Verification and Limitations}

The verification is a direct literature identification:
\begin{itemize}
  \item arXiv:1106.5020, page 2, states Mazur's rotation problem for separable
  Banach spaces with transitive isometry group on the sphere;
  \item arXiv:1106.5020, page 31, records that transitivity implies almost
  transitivity;
  \item arXiv:1310.7139, page 1, states the no-almost-transitive-renorming
  result in the abstract;
  \item arXiv:1310.7139, page 5, contains Theorem 2.4 for subspaces of
  $\ell_p$;
  \item arXiv:1310.7139, page 7, contains Corollary 2.11 for subspaces of
  quotient spaces of $\ell_p$.
\end{itemize}

This packet does not solve the general Mazur rotation problem. It gives only a
classical isomorphic-class exclusion for $\ell_p$-based spaces when
$1<p<\infty$ and $p\ne2$.

\section*{Search Bounds}

The cheap run indexes were searched for \texttt{1106.5020},
\texttt{1310.7139}, Dilworth, Randrianantoanina, Mazur rotation,
Banach--Mazur rotation, almost transitive renorming, \texttt{ell\_p}, and
subspaces of quotient spaces. No prior packet or attempt for this exact
subcase was found.

External arXiv/web search on June 14, 2026 found arXiv:1310.7139 as the
relevant later source. No full solution of Mazur's general rotation problem
was identified within this bounded check.

\section*{Human Review Recommendation}

Review as a literature-status partial subcase. In particular, check that the
statement is counted only as an isomorphic-class exclusion and that the
quotient-space conclusion is restricted to $1<p<\infty$, $p\ne2$.

\begin{thebibliography}{9}

\bibitem{FerencziRosendal2011}
V. Ferenczi and C. Rosendal,
\emph{On isometry groups and maximal symmetry},
arXiv:1106.5020.

\bibitem{DilworthRandrianantoanina2013}
S. J. Dilworth and B. Randrianantoanina,
\emph{On an isomorphic Banach--Mazur rotation problem and maximal norms in
Banach spaces},
arXiv:1310.7139.

\end{thebibliography}

\end{document}
