\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\newcommand{\Id}{\operatorname{Id}}
\newcommand{\MUP}{\mathrm{MUP}}

\title{A literature-implied Mazur--Ulam subcase for numerical-index-one spaces}
\author{Run fa\_banach\_001, lane 4}
\date{2026-06-29}

\begin{document}
\maketitle

\section*{Status}

\textbf{literature\_implied\_answer (partial subcase).}

\section*{Source question}

The source paper is Dongni Tan, Xujian Huang, and Rui Liu,
\emph{Generalized-Lush Spaces and the Mazur-Ulam Property},
arXiv:1210.7324.  After proving that every local-GL space, hence every lush
space, has the Mazur--Ulam property, the authors ask at the end of the paper:
\[
\text{Does every Banach space with numerical index }1\text{ have the MUP?}
\]

\section*{Supporting theorem}

The supporting source is Vladimir Kadets, Miguel Martin, Javier Meri, and
Antonio Perez, \emph{Spear operators between Banach spaces},
arXiv:1701.02977.  In the identity case, that source records that \(X\) has
numerical index one exactly when \(\Id_X\) is a spear operator; numerical
index one implies the alternative Daugavet property (aDP).  It also cites the
SCD theorem that if \(X\) has the aDP and \(B_Y\) is SCD for every separable
subspace \(Y\subset X\), then \(X\) is lush.  In particular, this applies when
\(X\) has the convex point of continuity property, the Radon--Nikodym
property, or contains no copy of \(\ell_1\).

\section*{Deduction}

Let \(X\) be a Banach space with numerical index one and suppose that
\(B_Y\) is SCD for every separable subspace \(Y\subset X\).  Since \(n(X)=1\),
\(\Id_X\) is spear, so \(X\) has the aDP.  The SCD theorem from
Kadets--Martin--Meri--Perez then implies that \(X\) is lush.  By the main
corollary of Tan--Huang--Liu, every lush space has the Mazur--Ulam property.
Therefore \(X\) has the MUP.

Thus the final question of arXiv:1210.7324 has an affirmative answer for
numerical-index-one spaces satisfying the SCD separable-subspace condition.
This includes finite-dimensional spaces and, more generally, spaces with
CPCP, RNP, or no isomorphic copy of \(\ell_1\).

\section*{Scope}

This is not a full solution of the unrestricted numerical-index-one question.
The implication still goes through lushness, while both the source paper and
the later spear-operator literature record numerical-index-one spaces which
are not lush.  The remaining case is precisely outside this SCD/lushness
mechanism.

\section*{Search notes}

Local run indexes were searched for arXiv:1210.7324 and the core phrases
``Mazur--Ulam'', ``MUP'', ``Tingley'', ``numerical index'', ``lush'',
``local-GL'', and ``spear''.  Web searches on 2026-06-29 for combinations of
``numerical index one'', ``Mazur--Ulam property'', ``MUP'', ``Tingley's
problem'', ``lush'', and ``SCD'' found no exact full answer to the unrestricted
question.  The implication recorded here is agent-identified from the two
papers above.

\begin{thebibliography}{9}

\bibitem{THL}
D. Tan, X. Huang, and R. Liu,
\emph{Generalized-Lush Spaces and the Mazur-Ulam Property},
arXiv:1210.7324.

\bibitem{KMMP}
V. Kadets, M. Martin, J. Meri, and A. Perez,
\emph{Spear operators between Banach spaces},
arXiv:1701.02977; Lecture Notes in Mathematics 2205, Springer, 2018.

\bibitem{Banakh}
T. Banakh,
\emph{Every 2-dimensional Banach space has the Mazur-Ulam property},
arXiv:2103.09268; Linear Algebra Appl. 632 (2022), 268--280.

\end{thebibliography}

\end{document}
