\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer: Markov Convexity Problems from \texttt{0706.0545}}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-07-03}

\newcommand{\dist}{\operatorname{dist}}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.  Two extracted open problems from
Lee--Naor--Peres, \emph{Trees and Markov convexity}, arXiv:0706.0545, are
answered in the later paper Mendel--Naor, \emph{Markov convexity and local
rigidity of distorted metrics}, arXiv:0803.1697.

\paragraph{Source questions.}
In arXiv:0706.0545, Section ``Some open problems'' (PDF pp. 5--6),
Problem 1 asks for the relation between Markov \(p\)-convexity and uniform
\(p\)-convexity for general Banach spaces.  The source had proved that
\(p\)-uniform convexity implies Markov \(p\)-convexity and had a Banach-lattice
converse up to exponents \(q>p\), but left the general Banach-space relation
unclear.

Problem 2 asks whether the metric-tree obstruction theorem extends to arbitrary
metric spaces: if a metric space is not Markov \(p\)-convex for any finite
\(p\), must it contain arbitrarily large complete binary trees with distortion
arbitrarily close to \(1\)?

\paragraph{Supporting answers.}
Mendel--Naor arXiv:0803.1697 explicitly cites Lee--Naor--Peres as
\texttt{LNP-markov-convex}.  On PDF p. 3 it says that Lee--Naor--Peres asked
whether the Banach converse is true and answers it positively.  Theorem
\texttt{convexity-coincide} in that paper states that a Banach space is
\(p\)-convex if and only if it is Markov \(p\)-convex.  The later Theorem
\texttt{renorming} gives the quantitative equivalent renorming from a
finite Markov \(p\)-convexity constant.

On PDF p. 4, the supporting paper also answers the general-metric analogue
negatively.  Its Theorem \texttt{doubling} constructs a metric space
\(X\) which is not Markov \(p\)-convex for any finite \(p\), yet
\[
  \lim_{n\to\infty} c_X(B_n)=\infty,
\]
indeed with exponential lower growth for a doubling example.  Therefore
nontrivial Markov convexity is not forced by the failure of binary trees to
embed with distortion arbitrarily close to \(1\), answering Problem 2
negatively.

\paragraph{Why this is not new.}
The supporting authors explicitly knew they were answering the Lee--Naor--Peres
questions: the source paper is cited as \texttt{LNP-markov-convex}, the
Banach converse is stated as a question from that paper and answered
positively, and the arbitrary-metric analogue is stated as a question from that
paper and answered negatively.

\paragraph{Scope.}
This packet records already-known literature answers to Problems 1 and 2 only.
It does not address the broad unique-obstruction questions for planar graphs,
hyperbolic-plane subsets, or products of trees in Problem 3, nor the
lamplighter asymptotic and \(L_1\)-embedding questions in Problem 4.

\paragraph{References.}
\begin{itemize}
\item J. R. Lee, A. Naor, and Y. Peres, \emph{Trees and Markov convexity},
  arXiv:0706.0545.
\item M. Mendel and A. Naor, \emph{Markov convexity and local rigidity of
  distorted metrics}, arXiv:0803.1697.
\end{itemize}

\end{document}
