\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{The Schur--\(c_0\) problem for \(X_{\mathcal F}\) is answered by the rapid Farah family}
\author{Literature-status note}
\date{2026-06-18}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.

\paragraph{Source problem.}
Borodulin-Nadzieja and Farkas, \emph{Analytic P-ideals and Banach spaces}, arXiv:1905.13484, ask in the section ``Schur Property'', Problem labeled \texttt{schur-c0}:
\[
\text{Is there a family }\mathcal F\subseteq[\omega]^{<\omega}
\text{ such that }X_{\mathcal F}\text{ does not have the Schur property}
\]
\[
\text{and }X_{\mathcal F}\text{ does not contain a copy of }c_0?
\]

\paragraph{Supporting answer.}
Borodulin-Nadzieja, Farkas, Jachimek, and Pelczar-Barwacz, \emph{The Zoo of combinatorial Banach spaces}, arXiv:2404.01733, explicitly studies the same implication chain for combinatorial Banach spaces:
\[
\text{Schur property}\Rightarrow \ell_1\text{-saturation}\Rightarrow \text{no copies of }c_0.
\]
In the introduction they state that none of these implications can be reversed. In Subsection ``The rapid Farah family'' they define a family \(\mathrm{rFh}\), note that the block intervals \((I_n)\) witness that \(X_{\mathrm{rFh}}\) does not have the Schur property, and prove in Theorem \texttt{elel} that \(X_{\mathrm{rFh}}\) is \(\ell_1\)-saturated.

\paragraph{Why this answers the source problem.}
Take \(\mathcal F=\mathrm{rFh}\). The supporting paper gives directly that \(X_{\mathcal F}\) is not Schur. It also proves \(X_{\mathcal F}\) is \(\ell_1\)-saturated. Since a copy of \(c_0\) has subspaces containing no copy of \(\ell_1\) (indeed \(c_0\) itself contains no \(\ell_1\)), an \(\ell_1\)-saturated space cannot contain \(c_0\). Therefore \(X_{\mathrm{rFh}}\) is exactly the family requested in the 2019 problem.

\paragraph{Provenance and scope.}
This is a later-paper answer, not a new result from this run. The 2024 paper cites the 2019 paper as the source of the \(X_{\mathcal F}\) framework and explicitly frames the rapid Farah construction as a non-reversal of the Schur-to-\(\ell_1\)-saturation implication. The packet answers the existence question only; broader classification or characterization questions for arbitrary \(\mathcal F\) remain outside this status note.

\paragraph{References.}
\begin{itemize}
\item P. Borodulin-Nadzieja and B. Farkas, \emph{Analytic P-ideals and Banach spaces}, arXiv:1905.13484.
\item P. Borodulin-Nadzieja, B. Farkas, S. Jachimek, and A. Pelczar-Barwacz, \emph{The Zoo of combinatorial Banach spaces}, arXiv:2404.01733.
\end{itemize}

\end{document}
