\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Status note for arXiv:1602.00473, Question 3.11}
\author{fa\_banach\_001, agent\_lane\_15}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet.  The source question is
already answered in a later paper by Candeloro--Di Piazza--Musial--Sambucini;
no new proof is claimed here.

\section*{Source question}

The source paper is D. Candeloro, L. Di Piazza, K. Musial, and
A. R. Sambucini, \emph{Gauge integrals and selections of weakly compact valued
multifunctions}, J. Math. Anal. Appl. 441 (1) (2016), 293--308, DOI
\href{https://doi.org/10.1016/j.jmaa.2016.04.009}{10.1016/j.jmaa.2016.04.009},
arXiv:1602.00473.

In Section 3, Question 3.11 asks whether there exists at least one
variationally Henstock integrable selection of a \(cwk(X)\)-valued
variationally Henstock integrable multifunction.
Immediately after the question the authors say that the answer was not known
for an arbitrary Banach space, while it was known under the Radon--Nikodym
property.

\section*{Answering theorem}

The answer source is D. Candeloro, L. Di Piazza, K. Musial, and
A. R. Sambucini, \emph{Relations among Gauge and Pettis integrals for
\(cwk(X)\)-valued multifunctions}, Annali di Matematica Pura ed Applicata
197 (1) (2018), 171--183, DOI
\href{https://doi.org/10.1007/s10231-017-0674-z}{10.1007/s10231-017-0674-z},
available locally as arXiv:1912.01845.

The supporting paper's introduction states that its Theorem 4.1 solves the
existence problem for variationally Henstock integrable selections of
\(cwk(X)\)-valued variationally Henstock integrable multifunctions, citing
the source as Question 3.11.  In Section 4 it then says it examines
Question 3.11, removes the Radon--Nikodym-property hypothesis from the earlier
partial theorem, and gives a complete answer.

Theorem 4.1 states: if \(X\) is any Banach space and
\(\Gamma:[0,1]\to cwk(X)\) is variationally Henstock integrable, then
\(\mathcal S_{vH}(\Gamma)\neq\emptyset\), and every strongly measurable
selection of \(\Gamma\) is variationally Henstock integrable.  Therefore
Question 3.11 has an affirmative answer in arbitrary Banach spaces.

\section*{Provenance check}

Crossref metadata for the supporting paper records the source paper as a
reference by DOI
\href{https://doi.org/10.1016/j.jmaa.2016.04.009}{10.1016/j.jmaa.2016.04.009}.
The supporting paper also names the source question explicitly, so this is an
exact later answer rather than an agent-identified reformulation.

\section*{Conclusion}

The target arXiv:1602.00473 is not viable for a new proof or counterexample
on Question 3.11.  The question is already answered affirmatively by Theorem
4.1 of arXiv:1912.01845 / Annali di Matematica Pura ed Applicata 197 (2018).

\begin{thebibliography}{9}

\bibitem{CDMS2016}
D. Candeloro, L. Di Piazza, K. Musial, and A. R. Sambucini,
\emph{Gauge integrals and selections of weakly compact valued multifunctions},
J. Math. Anal. Appl. 441 (1) (2016), 293--308.

\bibitem{CDMS2018}
D. Candeloro, L. Di Piazza, K. Musial, and A. R. Sambucini,
\emph{Relations among Gauge and Pettis integrals for \(cwk(X)\)-valued
multifunctions},
Annali di Matematica Pura ed Applicata 197 (1) (2018), 171--183.

\end{thebibliography}

\end{document}
