\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Two Roe Rigidity Questions}
\author{Run \texttt{fa\_banach\_001}, lane 11}
\date{19 July 2026}

\begin{document}
\emergencystretch=3em
\maketitle

\section*{Status}

\textbf{literature\_already\_answered.}
This is a lightweight status packet, not a new proof claim by the run.  Both
questions on page 18 of the source paper are consequences of later general
rigidity theorems.

\section*{Source Questions}

The source is Bruno M. Braga, Yeong Chyuan Chung, and Kang Li,
\emph{Coarse Baum--Connes conjecture and rigidity for Roe algebras},
arXiv:1907.10237, J. Funct. Anal. 279 (2020), 108728 \cite{BCL}.
On page 18, Question 5.5 asks:
\begin{quote}
There is a finitely generated group $\Gamma$ which contains an expander $X$
with large girth isometrically in its Cayley graph.  Thus $\Gamma$ does not
satisfy the coarse Baum--Connes conjecture with coefficients, and the sparse
subspace $X$ yields a noncompact ghost projection.  Is $\Gamma$ Roe rigid?
\end{quote}
On the same page, Question 5.8 asks:
\begin{quote}
Let $X$ be a uniformly locally finite metric space which admits a coarse
embedding into a Hilbert space.  Is $X$ necessarily uniform Roe bijectively
rigid?
\end{quote}

\section*{Identification}

For Question 5.5, Diego Martinez and Federico Vigolo prove in Theorem A of
\emph{C*-Rigidity of bounded geometry metric spaces}, arXiv:2501.03128,
page 2 \cite{MV}, that if uniformly locally finite metric spaces $X$ and $Y$
have isomorphic Roe algebras, then $X$ and $Y$ are coarsely equivalent.  A
Cayley graph of a finitely generated group is uniformly locally finite.
Therefore every such $\Gamma$, including the group in Question 5.5, is Roe
rigid.  Martinez--Vigolo cite the source paper as reference [6] and describe
their theorem as the complete solution of this C*-rigidity problem.

For Question 5.8, Alessandro Vignati proves in Theorem A of
\emph{The rigidity problem for uniform Roe algebras}, arXiv:2602.01998,
page 3 \cite{Vig}, that if the uniform Roe algebras of uniformly locally finite
metric spaces $X$ and $Y$ are isomorphic, then $X$ and $Y$ are bijectively
coarsely equivalent.  Thus every uniformly locally finite $X$ is uniform Roe
bijectively rigid.  Question 5.8 has a positive answer, with no coarse Hilbert
embedding assumption needed.

\section*{Scope and Search Evidence}

The run's lightweight registry, solution, attempt, and proof-gap indexes were
searched for arXiv:1907.10237 and the two rigidity phrases.  No exact prior
record was found.  The decisive later sources are arXiv:2501.03128, whose
Theorem A solves Roe rigidity generally and whose bibliography cites the
source, and arXiv:2602.01998, whose abstract, introduction, and Theorem A state
the unconditional solution of uniform Roe bijective rigidity.  No part of
Questions 5.5 or 5.8 remains open after these theorems.

\begin{thebibliography}{9}
\bibitem{BCL}
Bruno M. Braga, Yeong Chyuan Chung, and Kang Li,
\emph{Coarse Baum--Connes conjecture and rigidity for Roe algebras},
J. Funct. Anal. 279 (2020), 108728; arXiv:1907.10237.

\bibitem{MV}
Diego Martinez and Federico Vigolo,
\emph{C*-Rigidity of bounded geometry metric spaces},
Publ. Math. IHES 141 (2025), 333--348; arXiv:2501.03128.

\bibitem{Vig}
Alessandro Vignati,
\emph{The rigidity problem for uniform Roe algebras},
arXiv:2602.01998, 2026.
\end{thebibliography}

\end{document}
