\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for arXiv:2202.01745}
\author{Run fa\_banach\_001, lane 2}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Already answered in the literature.} This packet records that the model
questions surfaced by O'Loughlin's 2022/2023 paper on symmetric matrix
representations of truncated Toeplitz operators are answered by a separate later
paper by the same author, arXiv:2607.14019.

\section*{Source Question}

The source paper is Ryan O'Loughlin, \emph{Symmetric matrix representations of
truncated Toeplitz operators on finite dimensional spaces}, arXiv:2202.01745,
later published in \emph{Linear Algebra and its Applications} 666 (2023),
11--28 \cite{oloughlin2023}.

In its introduction, the source recalls the finite-dimensional model question:
\[
\text{Is every symmetric matrix unitarily equivalent to a direct sum of TTOs?}
\]
After giving a negative answer to a modified-Clark-basis formulation, the source
poses the refined Section 3 conjecture labelled \texttt{newconj}: if a complex
symmetric matrix \(M\) is unitarily equivalent to a truncated Toeplitz operator,
does there exist an inner function \(u\) and a \(C_\theta\)-real basis for
\(K_u\) such that \(M\) is the matrix representation of a TTO with respect to
that basis?

\section*{Supporting Answer}

The supporting paper is Ryan O'Loughlin, \emph{Semialgebraic Dimension and
Truncated Toeplitz Models for Complex Symmetric Matrices}, arXiv:2607.14019,
submitted 2026-07-15 \cite{oloughlin2026}. Its abstract and introduction state
that it resolves the finite-dimensional model question negatively. More
precisely, Corollary 4.2 proves that, for every \(n\geq 10\), not every
\(n\times n\) symmetric matrix is unitarily equivalent to a direct sum of
truncated Toeplitz operators.

The same supporting paper also treats the refined representation question. In
Section 5 it restates the source's refined conjecture as Conjecture 5.1 and then
proves the following theorem: if \(B\) is a finite Blaschke product, \(A\) is a
TTO on \(K_B\), and \(M\in\mathcal{CS}_n\) is unitarily equivalent to \(A\), then
there exists a \(C_B\)-real orthonormal basis \(v_1,\ldots,v_n\) of \(K_B\) such
that \(M=[A]_{v_1,\ldots,v_n}\).

\section*{Scope}

The broad direct-sum model question is answered negatively in dimensions
\(n\geq 10\). The refined single-TTO representation question is answered
positively in finite dimensions when the unitary equivalence to a TTO is already
known to exist. This is a literature-status packet only; it should not be counted
as an original proof, partial result, or counterexample produced by the run.

\begin{thebibliography}{9}

\bibitem{oloughlin2023}
R. O'Loughlin,
\emph{Symmetric matrix representations of truncated Toeplitz operators on finite
dimensional spaces},
Linear Algebra Appl. 666 (2023), 11--28; arXiv:2202.01745.

\bibitem{oloughlin2026}
R. O'Loughlin,
\emph{Semialgebraic Dimension and Truncated Toeplitz Models for Complex
Symmetric Matrices},
arXiv:2607.14019, submitted 2026-07-15.

\end{thebibliography}

\end{document}
