\documentclass[11pt]{article}

\usepackage[margin=1.03in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\definecolor{darkblue}{RGB}{27,67,114}
\hypersetup{colorlinks=true,linkcolor=darkblue,citecolor=darkblue,urlcolor=darkblue}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\Pcal}{\mathcal P}
\newcommand{\Bcal}{\mathcal B}
\newcommand{\N}{\mathbb N}
\newcommand{\Q}{\mathbb Q}
\newcommand{\R}{\mathbb R}
\newcommand{\ellTwo}{\ell_2}
\newcommand{\Span}{\operatorname{span}}
\newcommand{\clspan}{\overline{\operatorname{span}}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\id}{\operatorname{id}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\Ball}{B}
\newcommand{\Haus}{d_{\mathrm H}}
\newcommand{\Proj}{\operatorname{P}}
\newcommand{\equiviso}{\equiv}
\newcommand{\eps}{\varepsilon}
\newcommand{\SigmaTwo}{\boldsymbol{\Sigma}^{0}_{2}}
\newcommand{\DeltaTwo}{\boldsymbol{\Delta}^{0}_{2}}

\title{Audit of a Fixed-Representative Reduction\\
\large and a Continuous Realization of All Pseudonorm Codes}
\author{Research note on Questions 1 and 2 of C\'uth--Dole\v{z}al--Doucha--Kurka}
\date{21 June 2026}

\begin{document}
\maketitle

\begin{abstract}
C\'uth, Dole\v{z}al, Doucha and Kurka asked whether every infinite-dimensional
pseudonorm code can be converted continuously into a genuine norm code for the
same Banach space, and whether one can at least obtain a
$\SigmaTwo$ reduction to an admissibly topologized space of closed subspaces.
This note audits a proposed fixed-subsequence argument and finds a genuine flaw:
it tests only rational linear independence, whereas membership in $\Bcal$
requires real linear independence after extension to real $c_{00}$.  An explicit
irrational-slope counterexample is given, followed by the corrected fixed-stratum
theorem.

A literature search through the date above did not locate a published or arXiv
resolution of either stated question.  The main result of the note is a direct
construction of continuous maps
$\chi_n:\Pcal\to C(Q)$, for one fixed compact metric space $Q$, satisfying
\[
 \left\|\sum_{n=1}^N a_n\chi_n(\mu)\right\|_\infty
 =\mu\left(\sum_{n=1}^N a_ne_n\right)
 \qquad(\mu\in\Pcal,\ a_n\in\R).
\]
This extends the continuous realization theorem in the source paper from
$\Bcal$ to all pseudonorms.  It yields a $\SigmaTwo$ reduction from all of
$\Pcal$ to $SB(X)$ for every isometrically universal separable Banach space
$X$ and every admissible topology, and therefore gives a positive answer to
Question 2.  The construction preserves all null relations, so it does not by
itself answer Question 1.  The argument appears not to be in the searched
literature and should be independently checked before being treated as a
published result.
\end{abstract}

\section{Source problem and conclusions}

Let $V=c_{00}(\Q)$ with its canonical Hamel basis $(e_n)_{n\in\N}$.  The space
$\Pcal$ consists of all pseudonorms on $V$, with the pointwise topology inherited
from $\R^V$.  Every $\mu\in\Pcal$ has a unique extension to a real pseudonorm on
$c_{00}(\R)$.  Let $X_\mu$ be the completion of $c_{00}(\R)/\ker\mu$.  The
subspace $\Pcal_\infty$ consists of codes with $X_\mu$ infinite-dimensional, and
$\Bcal\subseteq\Pcal_\infty$ consists of those $\mu$ whose real extension is a
norm.  Equivalently, the vectors $[e_n]_\mu$ are linearly independent over
$\R$ in $X_\mu$.

The source paper asks:
\begin{enumerate}[label=\textbf{Q\arabic*.},leftmargin=2.8em]
\item Is there a continuous map $\Phi:\Pcal_\infty\to\Bcal$ such that
      $X_{\Phi(\mu)}\equiviso X_\mu$ for all $\mu$?
\item Given an isometrically universal separable Banach space $X$ and an
      admissible topology $\tau$ on $SB(X)$, is there a $\SigmaTwo$ map
      $\Phi:\Pcal_\infty\to(SB(X),\tau)$ such that
      $\Phi(\mu)\equiviso X_\mu$ for all $\mu$?
\end{enumerate}

The conclusions of this audit are as follows.
\begin{enumerate}[leftmargin=2.3em]
\item The submitted fixed-representative statement is false as written, because
      rational independence does not imply real independence.
\item The same proof is correct after replacing rational independence by real
      independence.
\item No resolution of Question 1 was located in the literature search described
      in \cref{sec:literature}; Question 1 also remains unresolved by this note.
\item \Cref{thm:realization,cor:q2} give a positive answer to Question 2, in the
      stronger form of a $\SigmaTwo$ reduction defined on all of $\Pcal$.
\end{enumerate}

\section{Audit of the fixed-representative argument}

Fix a strictly increasing sequence $s=(s_j)_{j\geq 1}$ in $\N$.  The proposed
argument assumed that
\[
 \mu\left(\sum_{j=1}^m q_je_{s_j}\right)>0
 \quad\text{for every nonzero }(q_1,\dots,q_m)\in\Q^m,
 \tag{2.1}\label{eq:rational-ind}
\]
and inferred that the pullback along $e_j\mapsto e_{s_j}$ belongs to $\Bcal$.
That inference is invalid.

\begin{proposition}[Irrational-slope counterexample]\label{prop:irrational}
There is $\mu\in\Pcal_\infty$ such that \eqref{eq:rational-ind} holds for
$s_j=j$, the coordinate vectors have dense span in $X_\mu$, but $\mu\notin\Bcal$.
Consequently the fixed-representative theorem in the submitted packet is false
as stated.
\end{proposition}

\begin{proof}
Fix an irrational number $\alpha$, for instance $\alpha=\sqrt2$, and define on
real $c_{00}$
\[
 \mu(x)=|x_1-\alpha x_2|+\sum_{n=3}^{\infty}|x_n|.
 \tag{2.2}\label{eq:irrational-mu}
\]
Restricting \eqref{eq:irrational-mu} to $V$ gives an element of $\Pcal$.  If
$x\in V\setminus\{0\}$ and $\mu(x)=0$, then $x_n=0$ for $n\geq3$ and
$x_1=\alpha x_2$.  Since $x_1,x_2\in\Q$ and $\alpha\notin\Q$, this forces
$x_1=x_2=0$, a contradiction.  Thus the restriction is positive on every
nonzero rational vector.

On real $c_{00}$, however,
\[
 \mu(\alpha e_1+e_2)=0.
\]
Hence the real extension is not a norm and $\mu\notin\Bcal$.  The quotient map
\[
 c_{00}\longrightarrow c_{00},\qquad
 x\longmapsto (x_1-\alpha x_2,x_3,x_4,\ldots)
\]
identifies $X_\mu$ isometrically with $\ell_1$, so $\mu\in\Pcal_\infty$.
Finally, the images of the coordinate vectors span the canonical dense copy of
$c_{00}/\ker\mu$ in its completion.
\end{proof}

The correct hypothesis is real linear independence.  It is useful to record it
in a quantitative finite-dimensional form.  Put $\Pcal_s^{\mathrm{ind}}$ equal
to the set of all $\mu\in\Pcal_\infty$ such that
\begin{align}
 &\inf_{\|a\|_2=1}
   \mu\left(\sum_{j=1}^m a_je_{s_j}\right)>0
   \quad\text{for every }m\in\N,                                    
   \tag{2.3}\label{eq:real-ind}\\
 &\clspan\{[e_{s_j}]_\mu:j\in\N\}=X_\mu.                           
   \tag{2.4}\label{eq:dense}
\end{align}
Condition \eqref{eq:real-ind} is equivalent to real linear independence of every
finite initial segment.  The strict lower bound follows from compactness of the
Euclidean unit sphere.

\begin{theorem}[Corrected fixed-stratum theorem]\label{thm:fixed}
For every strictly increasing $s=(s_j)$, the formula
\[
 \Phi_s(\mu)\left(\sum_{j=1}^m q_je_j\right)
 =\mu\left(\sum_{j=1}^m q_je_{s_j}\right),\qquad q_j\in\Q,
 \tag{2.5}\label{eq:fixed-map}
\]
defines a continuous map
$\Phi_s:\Pcal_s^{\mathrm{ind}}\to\Bcal$.  Moreover,
$X_{\Phi_s(\mu)}\equiviso X_\mu$ for every
$\mu\in\Pcal_s^{\mathrm{ind}}$.
\end{theorem}

\begin{proof}
Let $T_s:c_{00}\to c_{00}$ be the real-linear map $T_se_j=e_{s_j}$.
The real extension of \eqref{eq:fixed-map} is
\[
 \Phi_s(\mu)(x)=\mu(T_sx).
\]
By \eqref{eq:real-ind}, $T_sx$ is not $\mu$-null when $x\neq0$; hence
$\Phi_s(\mu)$ is a norm and lies in $\Bcal$.

For $v\in V$, the coordinate function
$\mu\mapsto\Phi_s(\mu)(v)=\mu(T_sv)$ is continuous in the pointwise topology of
$\Pcal$.  This proves continuity of $\Phi_s$.

The map $e_j\mapsto[e_{s_j}]_\mu$ is an isometry from
$(c_{00},\Phi_s(\mu))$ into $X_\mu$.  Its range has dense span by
\eqref{eq:dense}, so it extends to a surjective linear isometry
$X_{\Phi_s(\mu)}\to X_\mu$.
\end{proof}

\begin{corollary}\label{cor:fixed-zero}
Let $A\subseteq\N$ have infinite complement
$S=\{s_1<s_2<\cdots\}$.  On the stratum where $[e_i]_\mu=0$ for $i\in A$ and
$([e_{s_j}]_\mu)_j$ is real-linearly independent, Question 1 has a positive
answer via $\Phi_s$.
\end{corollary}

\begin{proof}
Every finitely supported vector is, modulo the null coordinates indexed by $A$,
a finite linear combination of the $e_{s_j}$.  Thus \eqref{eq:dense} holds, and
\cref{thm:fixed} applies.
\end{proof}

\section{Literature check}\label{sec:literature}

The published source paper~\cite{CDDK} proves a $\SigmaTwo$ reduction
$\Pcal_\infty\to\Bcal$, a continuous realization theorem on $\Bcal$, and a
$\boldsymbol\Sigma^0_3$ reduction $\Pcal\to SB(X)$.  It explicitly leaves open
both Questions 1 and 2, and also states that it is open whether its continuous
realization theorem extends from $\Bcal$ to all of $\Pcal$.

The search for a later resolution used the exact wording of both questions,
combinations of the symbols $\Pcal_\infty$, $\Bcal$, $SB(X)$ and
``admissible topology'', the arXiv record and versions of the source paper, the
2024 sequel~\cite{CDDK2}, the citation trail visible through the publisher and
general scholarly search, and a 2026 quotient-encoding preprint that cites the
source~\cite{Kania}.  The cited papers visible in that trail through June 2026
do not advertise a solution of these questions.  A 2025 thesis surveying the
coding comparison~\cite{Kaplan} still records the
$\boldsymbol\Sigma^0_3$ map from $\Pcal$ to $SB(X)$ as the available general
result.  No exact published or arXiv answer was located.

This is necessarily an absence-of-evidence statement rather than a proof of
novelty.  The construction below should therefore be viewed as a candidate new
solution of Question 2 pending expert verification.

\section{A continuously varying compact dual ball}

The main idea is to place the dual balls of all $X_\mu$ inside one compact
Hilbert cube, prove Hausdorff continuity, and use Hilbert-space metric projection
to pull the varying canonical function spaces back to one fixed $C(Q)$.

Fix positive numbers $w_n=2^{-n}$ and set
\[
 Q=\{z=(z_n)\in\ellTwo: |z_n|\leq w_n\text{ for all }n\}.
 \tag{4.1}\label{eq:Q}
\]
Since $(w_n)\in\ellTwo$, $Q$ is compact in the norm topology of $\ellTwo$.
For $\mu\in\Pcal$ put
\[
 d_n(\mu)=1+\mu(e_n),\qquad
 u_n^\mu=\frac{[e_n]_\mu}{d_n(\mu)}\in X_\mu.
 \tag{4.2}\label{eq:normalized}
\]
Then $\|u_n^\mu\|<1$.  For $N\in\N$ and $a=(a_1,\ldots,a_N)\in\R^N$, define
\[
 p_{\mu,N}(a)
 =\left\|\sum_{n=1}^N a_nu_n^\mu\right\|
 =\mu\left(\sum_{n=1}^N\frac{a_n}{d_n(\mu)}e_n\right).
 \tag{4.3}\label{eq:pmun}
\]

\begin{lemma}[Continuity of real finite-dimensional evaluations]
\label{lem:finite-eval}
For every $N$, the map
\[
 \Pcal\times\R^N\longrightarrow\R,
 \qquad
 (\mu,a)\longmapsto\mu\left(\sum_{n=1}^N a_ne_n\right)
\]
is continuous.  Consequently, if $\mu_j\to\mu$ in $\Pcal$, then
$p_{\mu_j,N}\to p_{\mu,N}$ uniformly on every compact subset of $\R^N$.
\end{lemma}

\begin{proof}
It is enough to use sequences.  Suppose $\mu_j\to\mu$ and $a^{(j)}\to a$ in
$\R^N$.  The numbers $\mu_j(e_n)$, $j\in\N$ and $n\leq N$, are uniformly
bounded.  Hence there is $M<\infty$ such that
\[
 \mu_j\left(\sum_{n=1}^N b_ne_n\right)\leq M\|b\|_1
 \quad(j\in\N,\ b\in\R^N).
 \tag{4.4}\label{eq:Lipschitz}
\]
The same estimate holds for $\mu$ after increasing $M$ if needed.  Thus
\[
 |\mu_j(a^{(j)})-\mu_j(a)|\leq M\|a^{(j)}-a\|_1\longrightarrow0.
\]
To prove $\mu_j(a)\to\mu(a)$, approximate $a$ by a rational vector $q$ and use
\[
 |\mu_j(a)-\mu(a)|
 \leq \mu_j(a-q)+|\mu_j(q)-\mu(q)|+\mu(a-q),
\]
where the middle term tends to zero by the defining topology of $\Pcal$ and the
other two terms are bounded by \eqref{eq:Lipschitz}.  This proves joint
continuity.  The final assertion follows by applying uniform continuity on the
compact product of a convergent sequence (together with its limit) and the given
compact subset of $\R^N$, also taking into account the continuous denominators
in \eqref{eq:pmun}.
\end{proof}

For $\mu\in\Pcal$ and $N\in\N$, let
\[
 D_{\mu,N}=
 \{t\in\R^N: |\langle a,t\rangle|\leq p_{\mu,N}(a)
                 \text{ for every }a\in\R^N\}.
 \tag{4.5}\label{eq:Dmun}
\]

\begin{lemma}[Finite polar balls]\label{lem:finite-polar}
Each $D_{\mu,N}$ is a nonempty compact convex symmetric subset of
$[-1,1]^N$.  Its support function is
\[
 h_{D_{\mu,N}}(a)=\sup_{t\in D_{\mu,N}}\langle a,t\rangle
 =p_{\mu,N}(a).
 \tag{4.6}\label{eq:support}
\]
Moreover, $\mu\mapsto D_{\mu,N}$ is continuous for the Euclidean Hausdorff
metric.
\end{lemma}

\begin{proof}
All structural properties follow immediately from \eqref{eq:Dmun}; the coordinate
bound follows by testing $a=e_n$ and observing that
$p_{\mu,N}(e_n)=\mu(e_n)/(1+\mu(e_n))\leq1$.

The inequality $h_{D_{\mu,N}}\leq p_{\mu,N}$ is part of the definition.  For the
reverse inequality, fix $a\in\R^N$.  Hahn--Banach, applied to the seminorm
$p_{\mu,N}$, gives a linear functional $\ell$ on $\R^N$ with
$|\ell(b)|\leq p_{\mu,N}(b)$ for all $b$ and $\ell(a)=p_{\mu,N}(a)$.  Writing
$\ell(b)=\langle b,t\rangle$ gives $t\in D_{\mu,N}$ and proves
\eqref{eq:support}.

For compact convex subsets of Euclidean space,
\[
 \Haus(A,B)=\sup_{\|a\|_2\leq1}|h_A(a)-h_B(a)|.
 \tag{4.7}\label{eq:haus-support}
\]
By \cref{lem:finite-eval}, the right-hand side for
$A=D_{\mu_j,N}$ and $B=D_{\mu,N}$ tends to zero whenever $\mu_j\to\mu$.
\end{proof}

Define the compact convex set
\[
 K_\mu=\left\{z\in Q:
 \left|\sum_{n=1}^N a_n\frac{z_n}{w_n}\right|
 \leq p_{\mu,N}(a)
 \text{ for every }N\in\N\text{ and }a\in\R^N\right\}.
 \tag{4.8}\label{eq:Kmu}
\]
It is nonempty because $0\in K_\mu$.

\begin{lemma}[Dual-ball representation]\label{lem:dual-rep}
Let $\Ball_{X_\mu^*}$ be the closed dual unit ball.  Then
\[
 K_\mu=
 \left\{\bigl(w_nf(u_n^\mu)\bigr)_{n\geq1}:
             f\in\Ball_{X_\mu^*}\right\}.
 \tag{4.9}\label{eq:dual-rep}
\]
If $\pi_N:\ellTwo\to\R^N$ denotes the first-coordinate projection and
$W_N=\operatorname{diag}(w_1,\ldots,w_N)$, then
\[
 \pi_N(K_\mu)=W_ND_{\mu,N}.
 \tag{4.10}\label{eq:finite-proj}
\]
\end{lemma}

\begin{proof}
If $f\in\Ball_{X_\mu^*}$ and $z_n=w_nf(u_n^\mu)$, then $z\in Q$ and every
inequality in \eqref{eq:Kmu} follows from
\[
 \left|f\left(\sum_{n=1}^N a_nu_n^\mu\right)\right|
 \leq p_{\mu,N}(a).
\]
Conversely, if $z\in K_\mu$, define on the algebraic span of the $u_n^\mu$
\[
 f_z\left(\sum_{n=1}^N a_nu_n^\mu\right)
 =\sum_{n=1}^N a_n\frac{z_n}{w_n}.
 \tag{4.11}\label{eq:fz}
\]
The inequalities in \eqref{eq:Kmu} show both that \eqref{eq:fz} is well-defined
and that $\|f_z\|\leq1$.  Since the $u_n^\mu$ have dense linear span in
$X_\mu$, $f_z$ extends continuously to an element of $\Ball_{X_\mu^*}$.
This proves \eqref{eq:dual-rep}.

The inclusion $\pi_N(K_\mu)\subseteq W_ND_{\mu,N}$ is immediate.  Conversely,
$t\in D_{\mu,N}$ defines a norm-one functional on
$\Span\{u_1^\mu,\ldots,u_N^\mu\}$ by
$\sum a_nu_n^\mu\mapsto\sum a_nt_n$.  Hahn--Banach extends it to
$X_\mu$, and \eqref{eq:dual-rep} supplies an element of $K_\mu$ whose first
$N$ coordinates are $W_Nt$.
\end{proof}

\begin{proposition}[Hausdorff continuity of the dual balls]
\label{prop:hausdorff}
The map $\mu\mapsto K_\mu$ from $\Pcal$ into the nonempty compact subsets of
$Q$ is continuous for the Hausdorff metric inherited from $\ellTwo$.
\end{proposition}

\begin{proof}
Set
\[
 r_N=\left(\sum_{n>N}w_n^2\right)^{1/2}\longrightarrow0.
\]
For any $\mu,\nu\in\Pcal$, \eqref{eq:finite-proj} gives
\[
 \Haus(K_\mu,K_\nu)
 \leq \Haus(W_ND_{\mu,N},W_ND_{\nu,N})+2r_N.
 \tag{4.12}\label{eq:tail-estimate}
\]
Indeed, given $z\in K_\mu$, choose $y\in K_\nu$ whose first $N$ coordinates
are within the finite-dimensional Hausdorff distance of $\pi_Nz$.  Both tails
have $\ellTwo$ norm at most $r_N$, yielding \eqref{eq:tail-estimate}; the reverse
direction is identical.

If $\mu_j\to\mu$, then for every fixed $N$ the first term on the right of
\eqref{eq:tail-estimate} tends to zero by \cref{lem:finite-polar}.  Taking
$\limsup_j$ and then $N\to\infty$ proves the result.
\end{proof}

\section{Metric projection and the continuous realization theorem}

For a nonempty closed convex subset $K$ of $\ellTwo$, let $\Proj_K$ denote the
Hilbert-space metric projection onto $K$.

\begin{lemma}[Continuous dependence of metric projections]
\label{lem:projection}
If $K_j,K$ are nonempty compact convex subsets of $Q$ and
$\Haus(K_j,K)\to0$, then
\[
 \sup_{z\in Q}\|\Proj_{K_j}z-\Proj_Kz\|_2\longrightarrow0.
 \tag{5.1}\label{eq:projection-uniform}
\]
\end{lemma}

\begin{proof}
First suppose $z_j\to z$ in $Q$ and put $p_j=\Proj_{K_j}z_j$.  Compactness of
$Q$ gives convergent subsequences of $(p_j)$.  If $p_{j_k}\to p$, Hausdorff
convergence implies $p\in K$.  For every $y\in K$, choose $y_{j_k}\in K_{j_k}$
with $y_{j_k}\to y$.  The minimizing property gives
\[
 \|z_{j_k}-p_{j_k}\|_2\leq\|z_{j_k}-y_{j_k}\|_2.
\]
Passing to the limit shows $\|z-p\|_2\leq\|z-y\|_2$ for all $y\in K$.
Uniqueness of Hilbert-space projection yields $p=\Proj_Kz$.  Thus
$\Proj_{K_j}z_j\to\Proj_Kz$.

If \eqref{eq:projection-uniform} failed, there would be $z_j\in Q$ and
$\eps>0$ with
$\|\Proj_{K_j}z_j-\Proj_Kz_j\|_2\geq\eps$.  Passing to a subsequence, compactness
of $Q$ gives $z_j\to z$, and the preceding sequential continuity applied both
to $K_j$ and to the constant sequence $K$ gives a contradiction.
\end{proof}

For $\mu\in\Pcal$, abbreviate
\[
 P_\mu=\Proj_{K_\mu}|_Q:Q\longrightarrow K_\mu.
\]
Since $P_\mu$ fixes every point of $K_\mu$, it maps $Q$ onto $K_\mu$.

\begin{theorem}[Continuous realization of all pseudonorms]
\label{thm:realization}
There is a fixed compact metric space $Q$ and continuous maps
\[
 \chi_n:\Pcal\longrightarrow C(Q),\qquad n\in\N,
\]
such that for every $\mu\in\Pcal$, every $N\in\N$ and every
$a_1,\ldots,a_N\in\R$,
\[
 \left\|\sum_{n=1}^N a_n\chi_n(\mu)\right\|_{C(Q)}
 =\mu\left(\sum_{n=1}^N a_ne_n\right).
 \tag{5.2}\label{eq:main-identity}
\]
One may take $Q$ as in \eqref{eq:Q} and
\[
 \chi_n(\mu)(z)
 =d_n(\mu)\frac{(P_\mu z)_n}{w_n},
 \qquad z\in Q.
 \tag{5.3}\label{eq:chi}
\]
\end{theorem}

\begin{proof}
For fixed $\mu$ and $n$, formula \eqref{eq:chi} defines a continuous function on
$Q$.  If $\mu_j\to\mu$, then \cref{prop:hausdorff,lem:projection} give
$P_{\mu_j}\to P_\mu$ uniformly on $Q$, while
$d_n(\mu_j)\to d_n(\mu)$.  Hence
$\chi_n(\mu_j)\to\chi_n(\mu)$ in the supremum norm, proving continuity of
$\chi_n$.

Because $P_\mu(Q)=K_\mu$, \cref{lem:dual-rep} gives
\begin{align*}
 \left\|\sum_{n=1}^N a_n\chi_n(\mu)\right\|_\infty
 &=\sup_{y\in K_\mu}
   \left|\sum_{n=1}^N a_nd_n(\mu)\frac{y_n}{w_n}\right|\\
 &=\sup_{f\in\Ball_{X_\mu^*}}
   \left|f\left(\sum_{n=1}^N a_n[e_n]_\mu\right)\right|\\
 &=\left\|\sum_{n=1}^N a_n[e_n]_\mu\right\|_{X_\mu}
 =\mu\left(\sum_{n=1}^N a_ne_n\right),
\end{align*}
where the penultimate equality is the usual dual formula for the norm.  This is
\eqref{eq:main-identity}.
\end{proof}

\begin{remark}
The source paper proves the analogue of \cref{thm:realization} on $\Bcal$ and
explicitly asks whether it extends to $\Pcal$.  Thus \cref{thm:realization}
settles that intermediate problem as well.  Conceptually, $K_\mu$ is a weighted
copy of the weak-star compact dual unit ball, and $P_\mu$ is a continuously
varying surjection from one fixed compact space onto $K_\mu$.
\end{remark}

\section{Positive answer to Question 2}

Let $X$ be an isometrically universal separable Banach space.  Since $C(Q)$ is
separable, fix a linear isometric embedding $J:C(Q)\to X$.  Define
\[
 F(\mu)=\clspan\{J\chi_n(\mu):n\in\N\}\in SB(X).
 \tag{6.1}\label{eq:Fmu}
\]

\begin{corollary}[Question 2, with a stronger domain]\label{cor:q2}
For every admissible topology $\tau$ on $SB(X)$, the map
\[
 F:\Pcal\longrightarrow(SB(X),\tau)
\]
is $\SigmaTwo$-measurable and satisfies $F(\mu)\equiviso X_\mu$ for every
$\mu\in\Pcal$.  Its restriction to $\Pcal_\infty$ takes values in
$SB_\infty(X)$ and gives a positive answer to Question 2.
\end{corollary}

\begin{proof}
By \eqref{eq:main-identity}, the linear map
$e_n\mapsto J\chi_n(\mu)$ has exactly the pseudonorm $\mu$.  It therefore
factors through $c_{00}/\ker\mu$ and extends to a surjective linear isometry
$X_\mu\to F(\mu)$.

For an open set $U\subseteq X$, write
$E^+(U)=\{Y\in SB(X):Y\cap U\neq\varnothing\}$.  Rational finite linear
combinations of the $J\chi_n(\mu)$ are dense in $F(\mu)$, so
\[
 F^{-1}(E^+(U))
 =\bigcup_{q\in V}
   \left\{\mu\in\Pcal:
      \sum_n q_nJ\chi_n(\mu)\in U\right\}.
 \tag{6.2}\label{eq:hit-open}
\]
Every set on the right is open, hence the inverse image in
\eqref{eq:hit-open} is open.

By definition, an admissible topology has a subbasis whose members are
countable unions of sets $E^+(U)\setminus E^+(V)$ with $U,V$ open in $X$.
The inverse image of such a difference is the difference of two open subsets of
the Polish space $\Pcal$.  This is an $F_\sigma$ set: every open subset of a
metrizable space is $F_\sigma$, and intersecting an $F_\sigma$ set with a closed
set preserves that class.  Therefore inverse images of
subbasic open sets are $\boldsymbol\Sigma^0_2$.  Since the target topology is
second countable, every open set is a countable union of finite intersections
of subbasic sets, and $\boldsymbol\Sigma^0_2$ is closed under these operations.
Thus $F$ is $\SigmaTwo$-measurable.
\end{proof}

\begin{remark}
The conclusion is stronger than Question 2 in two ways: the map is defined on
all pseudonorms, including finite-dimensional and zero codes, and the hit-open
sets in \eqref{eq:hit-open} have open inverse image.  The loss to
$\boldsymbol\Sigma^0_2$ occurs only when passing from the lower hit topology to
an arbitrary admissible topology.
\end{remark}

\section{What remains for Question 1}

The realization theorem deliberately preserves null relations.  Indeed,
\eqref{eq:main-identity} gives
\[
 \sum_{n=1}^N a_n\chi_n(\mu)=0
 \quad\Longleftrightarrow\quad
 \mu\left(\sum_{n=1}^N a_ne_n\right)=0.
 \tag{7.1}\label{eq:null-relations}
\]
Thus, when $\mu\notin\Bcal$, the displayed continuous generating sequence is
not linearly independent.  To answer Question 1 one must additionally replace
it, continuously in $\mu$, by a real-linearly independent dense sequence in the
same Banach space.  Neither the metric-projection construction nor the corrected
fixed-stratum theorem performs that global selection.

The following observation rules out the most rigid possible repair.

\begin{proposition}[No fixed real-linear pullback solves Question 1]
\label{prop:no-fixed}
There is no fixed real-linear map $T:c_{00}(\R)\to c_{00}(\R)$ such that
\[
 \Phi_T(\mu)(v)=\mu(Tv),\qquad v\in V,
\]
belongs to $\Bcal$ and codes a space isometric to $X_\mu$ for every
$\mu\in\Pcal_\infty$.
\end{proposition}

\begin{proof}
If $T$ is not injective, choose $0\neq v\in c_{00}(\R)$ with $Tv=0$; then the
real extension of $\Phi_T(\mu)$ has the nonzero null vector $v$ for every $\mu$.
Suppose $T$ is injective and choose $0\neq v\in c_{00}(\R)$.  Put $y=Tv\neq0$.
Choose a real-linear automorphism $A$ of $c_{00}$ with $Ay=e_1$, and define
\[
 \mu(x)=\sum_{n=2}^{\infty}|(Ax)_n|.
\]
Then $\ker\mu=\R y$, while $X_\mu$ is infinite-dimensional (indeed, isometric
to $\ell_1$ after a coordinate identification).  Hence
$\Phi_T(\mu)(v)=\mu(y)=0$, so $\Phi_T(\mu)\notin\Bcal$.
\end{proof}

A recursive construction would require continuous choices outside varying
finite-dimensional spans.  This resembles a zero-avoiding continuous-selection
problem.  General selection theory does not provide such avoidance on arbitrary
infinite-dimensional parameter spaces without additional hypotheses.  This is
consistent with, but of course does not prove, the continued difficulty of
Question 1.

\section{Final status}

The fixed-representative packet contains a correct idea but an incorrect
independence test.  After replacing rational independence by real independence,
its theorem is valid on the stated fixed strata.  The global norm-code problem
(Question 1) remains open in this investigation.

The compact-dual-ball and metric-projection construction gives a candidate
continuous realization of every pseudonorm in one fixed separable Banach space.
Subject to independent verification, it supplies a full positive solution of
Question 2 and improves
the previously stated $\boldsymbol\Sigma^0_3$ reduction from $\Pcal$ to
$SB(X)$ to $\boldsymbol\Sigma^0_2$.  Because this appears to be a new argument,
independent expert checking is especially important; the most delicate points
are the Hausdorff continuity in \cref{prop:hausdorff} and the uniform projection
continuity in \cref{lem:projection}.

\begin{thebibliography}{9}

\bibitem{CDDK}
M.~C\'uth, M.~Dole\v{z}al, M.~Doucha and O.~Kurka,
\emph{Polish spaces of Banach spaces},
Forum of Mathematics, Sigma \textbf{10} (2022), e26.
\href{https://doi.org/10.1017/fms.2022.16}{doi:10.1017/fms.2022.16};
\href{https://arxiv.org/abs/1912.03994}{arXiv:1912.03994}.

\bibitem{CDDK2}
M.~C\'uth, M.~Dole\v{z}al, M.~Doucha and O.~Kurka,
\emph{Polish spaces of Banach spaces: complexity of isometry and isomorphism
classes},
J. Inst. Math. Jussieu \textbf{23} (2024), 1919--1957.
\href{https://doi.org/10.1017/S1474748023000440}{doi:10.1017/S1474748023000440};
\href{https://arxiv.org/abs/2204.06834}{arXiv:2204.06834}.

\bibitem{Kaplan}
A.~Kaplan,
\emph{Descriptive Complexities in Polish Spaces of Separable Banach Spaces},
M.S. thesis, Middle East Technical University, August 2025.

\bibitem{Kania}
T.~Kania,
\emph{Polish spaces for countable and separable structures through quotient
encodings},
arXiv:2604.15843, 2026.

\bibitem{GSR}
G.~Godefroy and J.~Saint-Raymond,
\emph{Descriptive complexity of some isomorphism classes of Banach spaces},
J. Funct. Anal. \textbf{275} (2018), 1008--1022.

\bibitem{Kechris}
A.~S. Kechris,
\emph{Classical Descriptive Set Theory},
Graduate Texts in Mathematics 156, Springer, 1995.

\bibitem{RepovsSemenov}
D.~Repov\v{s} and P.~V. Semenov,
\emph{Continuous selections of multivalued mappings},
in: Recent Progress in General Topology III, Atlantis Press, 2014, 423--461;
\href{https://arxiv.org/abs/1401.2257}{arXiv:1401.2257}.

\end{thebibliography}

\end{document}
