\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\setlength{\emergencystretch}{3em}

\newcommand{\B}{\mathcal{B}}
\newcommand{\K}{\mathcal{K}}

\begin{document}

\begin{center}
{\Large Literature status: the $\B(\ell^p)$ amenability question}\\[0.4em]
{\large arXiv:math/0401122 answered by arXiv:0907.3984}\\[0.6em]
\textbf{Status: literature\_already\_answered, not an original run proof}
\end{center}

\section*{Source question}

The source paper is Narutaka Ozawa, \emph{A note on non-amenability of
$\B(\ell_p)$ for $p=1,2$}, arXiv:math/0401122, later published in
\emph{International Journal of Mathematics} 15 (2004), 557--565.
In the introduction, after recalling the known $p=1,2,\infty$ cases, Ozawa
records the remaining case:
\begin{quote}
``It is left open whether $\B(\ell_p)$ is amenable or not for
$p\in(1,\infty)\setminus\{2\}$.'' \cite[p.~1]{Ozawa2004}
\end{quote}

The queue hit also sees a later remark in Ozawa's proof discussion: the same
strategy would produce almost invariant vectors in
$\ell_q\widehat{\otimes}\ell_p$, but Ozawa does not know whether the unit ball
of this projective tensor product uniformly embeds into Hilbert space, and
notes that nontrivial cotype was not known there. That is a method-side
obstruction, not the main amenability question identified above.

\section*{Supporting answer}

The decisive later paper is Volker Runde, \emph{$\B(\ell^p)$ is never
amenable}, arXiv:0907.3984, published in \emph{Journal of the American
Mathematical Society} 23 (2010), 1175--1185. Runde explicitly cites Ozawa's
paper and states that Daws and Runde had investigated whether $\B(\ell^p)$ is
amenable for $p\in(1,\infty)\setminus\{2\}$ \cite[Introduction]{Runde2010}.

Runde's final argument gives, for $p\in(1,\infty)$, non-amenability of
$\ell^\infty(\K(E))$ for every infinite-dimensional $\mathcal L^p$-space
$E$, then non-amenability of $\B(\ell^p(E))$ for every $\mathcal L^p$-space
$E$ \cite[Proposition 4.1 and Theorem 4.2]{Runde2010}. Applying the corollary
with $E=\ell^p$ yields that $\B(\ell^p)$ is not amenable for every
$p\in(1,\infty)$ \cite[Corollary 4.3 and following paragraph]{Runde2010}.
Together with the earlier $p=1,2,\infty$ results cited there, this answers the
open range from Ozawa's introduction.

\section*{Scope and limitations}

This packet records a known literature answer to the main open problem in the
source introduction. It should not be counted as a new solution, partial
solution, or counterexample produced by this run.

No claim is made here that Runde resolves the separate tensor-product
uniform-embedding or cotype question mentioned in Ozawa's remark. Runde instead
bypasses that specific obstruction through the Daws--Runde transference route
and a modification of Ozawa's method.

\section*{Search and citation evidence}

The local run indexes had no existing row for arXiv:math/0401122. Local source
inspection found Ozawa's open statement in the introduction and the separate
tensor-product remark near the end of the proof section. A bounded web and
local-source search for phrases including
\texttt{B(ell\^{}p) amenable}, \texttt{B(ell\^{}p) is never amenable}, and
\texttt{Daws Runde Ozawa} found arXiv:0907.3984. The supporting paper's
abstract, introduction, final theorem/corollary, and bibliography identify the
answer as the same problem and cite Ozawa's paper.

\begin{thebibliography}{9}

\bibitem{Ozawa2004}
N. Ozawa,
\emph{A note on non-amenability of $\B(\ell_p)$ for $p=1,2$},
arXiv:math/0401122; Internat. J. Math. 15 (2004), 557--565.
\url{https://arxiv.org/abs/math/0401122}

\bibitem{Runde2010}
V. Runde,
\emph{$\B(\ell^p)$ is never amenable},
arXiv:0907.3984; J. Amer. Math. Soc. 23 (2010), 1175--1185.
\url{https://arxiv.org/abs/0907.3984}

\bibitem{DawsRunde2008}
M. Daws and V. Runde,
\emph{Can $\B(\ell^p)$ ever be amenable?},
Studia Math. 188 (2008), 151--174; erratum Studia Math. 195 (2009),
297--298.

\end{thebibliography}

\end{document}
