\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Scoped literature answer for the polyhedral k-smoothness question}
\author{Codex agent lane 17}
\date{July 18, 2026}

\newcommand{\X}{\mathbb X}
\newcommand{\Y}{\mathbb Y}
\newcommand{\R}{\mathbb R}
\newcommand{\Lin}{\mathbb L}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\spanop}{\operatorname{span}}
\newcommand{\rank}{\operatorname{rank}}

\begin{document}
\maketitle

\section*{Status}

This is a literature-implied answer for a scoped subcase of the final
question in Mal--Dey--Paul \cite{MDP}.  It does not answer the arbitrary
Banach-space question.  It records that the later work of
Sain--Sohel--Paul \cite{SSP} answers the explicitly suggested real
finite-dimensional polyhedral case
\[
  \X=\ell_\infty^n,\qquad \Y=\ell_1^n,\qquad n\geq 3.
\]

\section*{Source question}

The source paper arXiv:2007.12628 ends the section on
\(k\)-smoothness of operators defined on Banach spaces with the question:
given Banach spaces \(\X,\Y\) and \(T\in S_{\Lin(\X,\Y)}\), what are
necessary and sufficient conditions for \(T\) to be a multi-smooth point
of finite order?  The same question specifically suggests considering
\(\X=\ell_\infty^n\), \(\Y=\ell_1^n\), \(n\geq 3\).

\section*{Supporting theorem}

Sain--Sohel--Paul \cite{SSP} introduce an index of smoothness \(i_R(T)\)
for an operator \(T\) relative to a subset \(R\subset S_\X\).  Their
Definition 1.2 defines this index by taking the dimension of an explicitly
described finite-dimensional span of coefficient vectors.  Proposition
1.7 proves that the index is independent of the auxiliary bases used in
the definition.  Theorem 1.8 then proves that, under the standard
reflexive/M-ideal hypotheses appearing there,
\[
  T\text{ is }k\text{-smooth}\quad\Longleftrightarrow\quad
  i_{M_T}(T)=k.
\]
In finite dimensions the compact operators are all operators, so the
M-ideal and distance hypotheses become trivial.  Section II of
\cite{SSP}, restricted there to real finite-dimensional polyhedral
Banach spaces, gives a three-step finite procedure for determining
\(i_{M_T}(T)\) for any \(T\in S_{\Lin(\X,\Y)}\).  The final remark states
that the order problem for operators between finite-dimensional
polyhedral Banach spaces is thereby completely solvable in a
computationally effective way.

\section*{Concrete consequence for \(\ell_\infty^n\to\ell_1^n\)}

Let \(T\in S_{\Lin(\ell_\infty^n,\ell_1^n)}\) over the real field.  Put
\[
  R=M_T\cap \Ext(B_{\ell_\infty^n})
    =\{\sigma\in\{\pm1\}^n:\|T\sigma\|_1=1\}.
\]
Choose a basis \(v_1,\ldots,v_r\) of \(\spanop R\).  For
\(y\in S_{\ell_1^n}\), the extreme support functionals in
\((\ell_1^n)^*=\ell_\infty^n\) are the sign vectors
\[
  \Ext J(y)=
  \{\varepsilon\in\{\pm1\}^n:
      \varepsilon_i=\operatorname{sign}(y_i)\text{ whenever }y_i\neq0\}.
\]
Let \(\eta_1,\ldots,\eta_s\) be a basis for the span of all
\(\Ext J(Tv)\), \(v\in R\).  For every \(v\in R\) and
\(\varepsilon\in\Ext J(Tv)\), write
\[
  v=\sum_{i=1}^r \alpha_i v_i,\qquad
  \varepsilon=\sum_{j=1}^s \beta_j \eta_j,
\]
and form the coefficient vector
\[
  z(v,\varepsilon)=(\alpha_i\beta_j)_{1\leq i\leq r,\;1\leq j\leq s}
  \in \R^{rs}.
\]
Then the Sain--Sohel--Paul index specializes to
\[
  i_{M_T}(T)=
  \rank\,\spanop\{z(v,\varepsilon):
          v\in R,\ \varepsilon\in\Ext J(Tv)\}.
\]
Consequently,
\[
  T\text{ is }k\text{-smooth}
  \quad\Longleftrightarrow\quad
  \rank\,\spanop\{z(v,\varepsilon)\}=k.
\]
This gives the necessary and sufficient condition requested in the
source's suggested \(\ell_\infty^n\)-to-\(\ell_1^n\) case.

\section*{Scope limitation}

The broad question for arbitrary Banach spaces remains outside this
packet.  The present identification is a scoped literature implication:
the supporting paper cites arXiv:2007.12628 and solves the finite
polyhedral operator-order problem, but it does not present itself as a
full solution of the final arbitrary-space question from the source
paper.

\begin{thebibliography}{9}

\bibitem{MDP}
A. Mal, S. Dey, and K. Paul,
\emph{Characterization of \(k\)-smoothness of operators defined between
infinite-dimensional spaces},
arXiv:2007.12628; Linear Multilinear Algebra 70 (2022), no. 18,
3477--3489.

\bibitem{SSP}
D. Sain, S. Sohel, and K. Paul,
\emph{On \(k\)-smoothness of operators between Banach spaces},
arXiv:2407.19455; Bull. Sci. Math. 196 (2024), 103486.

\end{thebibliography}

\end{document}
