\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\C}{\mathbb C}
\newcommand{\ellone}{\ell_1}
\newcommand{\Ideal}{\mathrm{Ideal}}
\newcommand{\dist}{\mathrm{dist}}

\title{Dedekind Finiteness Is Not Open In The Free-Monoid Quotient Coding}
\author{agent\_super\_01}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Source And Question}

The source paper is Tomasz Kania, \emph{Polish spaces for countable and
separable structures through quotient encodings}, arXiv:2604.15843.
In Section 12, under ``Dedekind finiteness for Banach algebras'', the paper
asks whether the closed set of Dedekind finite Banach-algebra quotients is
non-open in the Wijsman topology, or whether natural subclasses exhibit sharper
completeness phenomena.

This packet answers the non-openness part for the standard unital
Banach-algebra quotient generator used in the paper:
\[
        A=\ell_1(S),
\]
where \(S\) is the free monoid on countably many generators.

\section*{Definitions}

A unital Banach algebra \(B\) is Dedekind finite, or directly finite, if
\[
        ab=1 \quad\Longrightarrow\quad ba=1
\]
for all \(a,b\in B\).  Otherwise \(B\) is Dedekind infinite.

For a closed ideal \(K\subset A\), the Wijsman topology is the topology of
pointwise convergence of quotient norms:
\[
        K_i\to K
        \quad\Longleftrightarrow\quad
        \dist(x,K_i)=\|x+K_i\|_{A/K_i}\to \|x+K\|_{A/K}
        \quad(x\in A).
\]

\section*{Proof Intuition}

Dedekind infiniteness can be hidden arbitrarily far out in the free generating
sequence.  Put a one-sided inverse pair on the generators \(s_{2n-1},s_{2n}\)
and send all other generators to zero.  Each quotient is Dedekind infinite.
But every fixed finite word only uses finitely many generators, so for large
\(n\) the quotient cannot see the one-sided inverse pair on that finite part;
there it agrees with the scalar quotient.  Finite-support approximation then
upgrades this agreement to Wijsman convergence on all of \(\ell_1(S)\).

\begin{theorem}
Let \(S\) be the free monoid on generators \(s_1,s_2,\ldots\), and let
\(A=\ell_1(S)\) be the standard unital free Banach-algebra quotient generator.
In \(\Ideal(A)\) with the Wijsman topology, the class of Dedekind finite
proper quotients is not open.
\end{theorem}

\begin{proof}
Let \(1\in S\) denote the empty word.  Define the augmentation character
\(\chi:A\to\C\) by
\[
        \chi(1)=1,\qquad \chi(w)=0\quad(w\ne 1),
\]
extended linearly and continuously.  This is a contractive unital algebra
homomorphism, and \(K_\infty:=\ker\chi\) gives the scalar quotient
\(A/K_\infty\cong\C\), which is Dedekind finite.

Let \(H=\ell_2(\N_0)\).  Let \(R e_j=e_{j+1}\) be the forward unilateral
shift and let \(L e_0=0,\ L e_{j+1}=e_j\) be the backward shift.  Then
\[
        LR=I,\qquad RL=I-p_0,
\]
where \(p_0\) is the rank-one projection onto \(\C e_0\).

For each \(n\ge 1\), define a contractive unital homomorphism
\(\pi_n:A\to B(H)\) by assigning
\[
        \pi_n(s_{2n-1})=L,\qquad
        \pi_n(s_{2n})=R,\qquad
        \pi_n(s_j)=0\quad(j\notin\{2n-1,2n\}),
\]
and extending by the universal \(\ell_1\)-free-monoid construction.  Put
\(K_n=\ker\pi_n\).  In \(A/K_n\), the cosets of \(s_{2n-1}\) and \(s_{2n}\)
satisfy
\[
        (s_{2n-1}+K_n)(s_{2n}+K_n)=1+K_n,
\]
but
\[
        (s_{2n}+K_n)(s_{2n-1}+K_n)\ne 1+K_n,
\]
because \(\pi_n(s_{2n}s_{2n-1}-1)=RL-I=-p_0\ne0\).  Thus every quotient
\(A/K_n\) is Dedekind infinite.

It remains to prove \(K_n\to K_\infty\) in the Wijsman topology.  First take
an element \(y\in A\) with finite support, and suppose all non-empty words in
its support use only generators among \(s_1,\ldots,s_m\).  If \(2n-1>m\), then
\(\pi_n(w)=0\) for every non-empty word \(w\) in the support of \(y\), whence
\[
        \pi_n(y)=\chi(y)I.
\]
Since \(y-\chi(y)1\in K_n\), we get
\[
        \dist(y,K_n)\le |\chi(y)|.
\]
Conversely, \(\pi_n\) is contractive and vanishes on \(K_n\), so for every
\(k\in K_n\),
\[
        |\chi(y)|=\|\pi_n(y)\|=\|\pi_n(y-k)\|\le \|y-k\|.
\]
Hence \(\dist(y,K_n)=|\chi(y)|\) for all sufficiently large \(n\).  The same
identity holds for \(K_\infty\): \(\dist(y,K_\infty)=|\chi(y)|\), because
\(\chi\) is a norm-one quotient map onto \(\C\).

Now let \(x\in A\) be arbitrary and choose finite-support \(y\) with
\(\|x-y\|<\varepsilon\).  Distance to a closed set is 1-Lipschitz in the
point, so for all sufficiently large \(n\),
\[
\begin{aligned}
|\dist(x,K_n)-\dist(x,K_\infty)|
&\le |\dist(x,K_n)-\dist(y,K_n)| \\
&\quad + |\dist(y,K_n)-\dist(y,K_\infty)|
      + |\dist(y,K_\infty)-\dist(x,K_\infty)| \\
&\le 2\varepsilon .
\end{aligned}
\]
As \(\varepsilon>0\) is arbitrary, \(\dist(x,K_n)\to\dist(x,K_\infty)\) for
every \(x\in A\).  Thus \(K_n\to K_\infty\) Wijsman.

We have exhibited a Dedekind finite quotient \(A/K_\infty\) that is a Wijsman
limit of Dedekind infinite quotients \(A/K_n\).  Therefore the Dedekind finite
class is not open.
\end{proof}

\section*{Verification Notes}

The proof uses only the standard free-monoid generator from the source paper
and the elementary unilateral-shift one-sided inverse \(LR=I\), \(RL\ne I\).
The Wijsman convergence proof is pointwise on quotient norms, first for
finite-support elements and then by density of finitely supported elements in
\(\ell_1(S)\).

\section*{Limitations And Novelty Check}

Cheap run indexes were searched for arXiv:2604.15843, Dedekind finiteness,
Banach-algebra quotient coding, and related stable-rank/operator-algebra
keywords.  No prior packet for this source question was found.

This is a partial result for the paper's list of open questions.  It answers
the non-openness question for the standard unital Banach-algebra quotient
generator \(A=\ell_1(S)\).  It does not prove an optimal completeness rank, and
it does not address every possible quotient generator or every admissible
hyperspace topology.

\section*{References}

\begin{itemize}
\item T. Kania, \emph{Polish spaces for countable and separable structures
through quotient encodings}, arXiv:2604.15843.
\end{itemize}

\section*{Human Review Recommendation}

Check that the source's intended ``present coding'' for Banach algebras includes
the standard unital free-monoid generator \(A=\ell_1(S)\), and verify the
quotient-norm convergence calculation.  If accepted, this should be recorded as
a scoped partial answer to the Dedekind-finiteness item in Section 12.

\end{document}
