\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\newtheorem*{theorem}{Literature Answer}

\title{Literature Answer to the Kadison--Singer Problem-Family in arXiv:0510024}
\author{FA/Banach run packet}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet. It records that the central
Kadison--Singer problem-family surveyed in arXiv:0510024 was answered
positively by Marcus--Spielman--Srivastava in arXiv:1306.3969. It is not an
original proof from this run.

\section*{Original Problem Evidence}

Casazza--Fickus--Tremain--Weber \cite{CFTW} present the Kadison--Singer
problem and its equivalent formulations in operator theory, frame theory,
Hilbert-space theory, Banach-space theory, harmonic analysis,
time-frequency analysis, and engineering. The introduction states that the
paper reduces these problems to equivalent forms of Kadison--Singer. The
source explicitly includes Anderson paving, Weaver's conjectures, the
Feichtinger conjecture, the \(R_\varepsilon\)-conjecture, and the
Bourgain--Tzafriri conjecture among the central formulations.

\section*{Supporting Answer Evidence}

Marcus--Spielman--Srivastava \cite{MSS} prove two results known to imply a
positive solution to Kadison--Singer. First, they prove Weaver's
\(KS_2\) conjecture. Second, they prove Anderson's paving conjecture in the
Casazza--Edidin--Kalra--Paulsen formulation and give explicit paving bounds.
Their history and introduction identify the same equivalent conjectures
surveyed by \cite{CFTW}, including Weaver \(KS_r\), Anderson paving,
Bourgain--Tzafriri, Feichtinger, and the \(R_\varepsilon\)-conjecture.

The post-solution survey \cite{C2014} records the consequence in the language
of the 2005 survey: the Marcus--Spielman--Srivastava theorem proves Weaver's
conjecture and therefore yields the Kadison--Singer solution and its standard
equivalent consequences.

\begin{theorem}
The central Kadison--Singer/Weaver/paving/Feichtinger/Bourgain--Tzafriri
open-problem family surveyed in arXiv:0510024 has a positive answer in the
later literature.
\end{theorem}

\begin{proof}
The 2005 source records the equivalence between the Kadison--Singer problem
and several finite-dimensional partition formulations, in particular Anderson
paving and Weaver-type vector partition conjectures. Marcus--Spielman--
Srivastava prove Weaver \(KS_2\), which Weaver had shown sufficient for
Kadison--Singer, and they also prove Anderson paving directly with explicit
bounds. These two theorems give the positive Kadison--Singer solution and hence
settle the equivalent conjectures in the scope of the 2005 survey.
\end{proof}

\section*{Limitations}

This packet only records the later literature answer to the central
problem-family of arXiv:0510024. It does not claim new proof, improved paving
constants, or a classification of every special operator class and uniform
paving variant discussed in the survey. It also does not address unrelated
Banach-space generalizations of Feichtinger-type conjectures.

\section*{Verification Notes}

The lane-15 queue selected arXiv:0510024. The cheap run indexes had no exact
previous packet for this source. Searches for \texttt{Kadison-Singer},
\texttt{Paving}, \texttt{Weaver}, \texttt{Feichtinger},
\texttt{Bourgain-Tzafriri}, and \texttt{Anderson} identified nearby later
Kadison--Singer sources, especially arXiv:1306.3969 and arXiv:1407.4768. A web
check on 2026-07-03 confirmed the arXiv record for arXiv:1306.3969.

\begin{thebibliography}{9}

\bibitem{CFTW}
P. G. Casazza, M. Fickus, J. C. Tremain, and E. Weber,
\emph{The Kadison--Singer Problem in Mathematics and Engineering: A Detailed
Account}, arXiv:math/0510024.

\bibitem{MSS}
A. W. Marcus, D. A. Spielman, and N. Srivastava,
\emph{Interlacing Families II: Mixed Characteristic Polynomials and the
Kadison--Singer Problem}, arXiv:1306.3969.

\bibitem{C2014}
P. G. Casazza,
\emph{Consequences of the Marcus/Spielman/Srivastava Solution of the
Kadison--Singer Problem}, arXiv:1407.4768.

\end{thebibliography}

\end{document}
