\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\C}{\mathcal C}
\newcommand{\K}{\mathcal K}
\newcommand{\Z}{\mathbb Z}

\begin{document}

\section*{Human Review: The Metrizable \texorpdfstring{$C(K)$}{C(K)} Case of \texorpdfstring{$\gamma^*=1$}{gamma-star equals one}}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 15 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears to give a correct affirmative answer to the parenthesized metrizable version of Problem 7.3 in the source paper, namely that
\[
  \gamma^*(\C(\K))=1
\]
for compact metrizable spaces \(\K\). It does not claim to settle the full nonmetrizable case.

The main idea is to decompose \(\K\) into its Cantor--Bendixson perfect kernel \(P\) and the scattered remainder \(\K\setminus P\). On the perfect part, \(P\) is compact metrizable and perfect, so \(\C(P)\) is separable and octahedral. The source paper's theorem for separable octahedral spaces then gives \(\gamma^*(\C(P))=1\). Thus, for every small \(\eta>0\), there is a subgroup
\[
  D_P\subseteq \C(P)
\]
which is \(2\)-separated and \((1+\eta)\)-dense.

The proof then uses the Dugundji extension theorem to choose a norm-one extension operator
\[
  E:\C(P)\longrightarrow \C(\K),
  \qquad (Ed)|_P=d.
\]
The remaining subgroup is
\[
  H=\{h\in \C(\K): h|_P=0 \text{ and } h(\K)\subseteq 2\Z\},
\]
and the proposed packing subgroup is
\[
  D=E[D_P]+H.
\]

The separation argument is straightforward and correct. If the \(D_P\)-component is nonzero, restriction to \(P\) detects norm at least \(2\). If the \(D_P\)-component vanishes but the \(H\)-component is nonzero, then the function takes a nonzero even-integer value, hence has norm at least \(2\).

The density argument also appears correct. Given \(f\in \C(\K)\), first approximate \(f|_P\) by some \(d\in D_P\), and then subtract the extension \(Ed\). The remaining function
\[
  g=f-Ed
\]
is already small on \(P\). Therefore the set where \(|g|\) is still too large lies inside \(\K\setminus P\). This remainder is locally compact, metrizable and scattered, hence zero-dimensional. Consequently, the relevant compact subset of \(\K\setminus P\) has a compact clopen neighbourhood \(U\subseteq \K\setminus P\).

On this compact zero-dimensional set \(U\), the proof applies exactly the even-integer approximation used in Theorem 4.4 of the source paper: take a finite clopen partition on which \(g\) has small oscillation, and on each clopen piece choose a nearest even integer to a representative value. This gives a continuous \(2\Z\)-valued approximation on \(U\), which can be extended by zero outside \(U\). Since \(U\) is clopen and disjoint from \(P\), the extension belongs to \(H\). This completes the \((1+\varepsilon)\)-density of \(D\).

\section*{Review Outcome}

Archive this packet as an apparently correct full solution to the metrizable case of the \(C(K)\) problem. The proof is a clean gluing argument: the perfect kernel is handled by the source paper's separable-octahedral result, while the scattered remainder is handled by the source paper's zero-dimensional even-integer construction. The only points that should be cited carefully in a polished version are the zero-dimensionality of the locally compact metrizable scattered remainder and the use of Theorem 4.4 for the compact clopen neighbourhood \(U\).

\end{document}
