\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Literature-implied theorem}

\begin{document}

\begin{center}
{\Large Literature-Implied Answer to the Near-Tight Feichtinger Partition Exponent}\\[0.5em]
{\normalsize Source: Bownik--Casazza--Marcus--Speegle, arXiv:1508.07353.}\\
{\normalsize Support: Ravichandran--Srivastava, arXiv:1706.03737.}
\end{center}

\paragraph{Status.}
\texttt{literature\_implied\_answer}.  The supporting paper does not explicitly
state that it is answering Remark 4.9 of arXiv:1508.07353; the answer follows
by combining the source paper's fixed-condition-number Riesz partition theorem
with the later asymptotically optimal paving theorem.

\paragraph{Source question.}
In Section 4 of arXiv:1508.07353, Theorem 4.8 proves that if
$(\phi_i)_{i\in I}$ is a unit-norm Bessel sequence with Bessel bound $B$, then
for every $\varepsilon>0$ it can be partitioned into
$O(B\varepsilon^{-4})$ Riesz sequences with bounds $1-\varepsilon$ and
$1+\varepsilon$.  The following Remark 4.9 says that it is open whether this
$\varepsilon$-dependence is optimal, notes that the linear dependence on $B$ is
optimal, and records a lower bound $\Omega(\varepsilon^{-2})$ as
$\varepsilon\to0$ from Casazza--Edidin--Kalra--Paulsen.

\paragraph{Supporting theorem.}
Ravichandran--Srivastava, arXiv:1706.03737, Theorem 1 proves that for
zero-diagonal Hermitian contractions $A^{(1)},\ldots,A^{(k)}$ and
$\varepsilon>0$, there is a common paving into at most
$18k\varepsilon^{-2}$ blocks with
\[
  \lambda_{\max}(P_X A^{(j)} P_X)<\varepsilon
\]
for every block $X$ and every $j$.  Applying this to $(A,-A)$ gives
two-sided paving of every zero-diagonal Hermitian contraction into
$O(\varepsilon^{-2})$ blocks.  Their abstract also records the consequence that
zero-diagonal contractions are $(O(\varepsilon^{-2}),\varepsilon)$ paved.

\begin{theorem}
Let $(\phi_i)_{i\in I}$ be a unit-norm Bessel sequence in a separable Hilbert
space with Bessel bound $B$.  For every $0<\varepsilon<1$ there is a partition
of $I$ into at most $C B\varepsilon^{-2}$ sets, where $C$ is universal, such
that each subfamily is a Riesz sequence with bounds
$1-\varepsilon$ and $1+\varepsilon$.
\end{theorem}

\begin{proof}
It is enough to discuss finite families; the infinite separable case follows
from the same pinball/compactness passage used in Section 4 of the source
paper.

By Theorem 4.7 of arXiv:1508.07353, the unit-norm Bessel sequence can first be
partitioned into at most $C_0 B$ Riesz sequences with fixed universal Riesz
bounds
\[
  a\sum |c_i|^2 \leq \left\|\sum c_i\phi_i\right\|^2
  \leq b\sum |c_i|^2,
\]
where $0<a\leq 1\leq b<\infty$ are absolute constants.

Fix one piece and let $G=(\langle\phi_j,\phi_i\rangle)_{i,j}$ be its Gram
matrix on the corresponding coefficient space.  Since the vectors have norm
one, $G$ has diagonal entries equal to $1$.  The Riesz bounds say that the
spectrum of $G$ is contained in $[a,b]$.  Hence
\[
  A:=G-I
\]
is zero diagonal and Hermitian, and $\|A\|\leq K:=\max\{1-a,b-1\}$, where $K$
is universal.

Apply Ravichandran--Srivastava two-sided paving to $A/K$ with tolerance
$\varepsilon/K$; equivalently apply their Theorem 1 to the two contractions
$A/K$ and $-A/K$.  This refines the fixed Riesz piece into at most
$C_1K^2\varepsilon^{-2}=O(\varepsilon^{-2})$ subpieces such that for every
refined block $J$,
\[
  \|P_J A P_J\|\leq \varepsilon .
\]
Therefore the corresponding compressed Gram matrix satisfies
\[
  (1-\varepsilon)I_J \leq P_JGP_J \leq (1+\varepsilon)I_J,
\]
which is exactly the statement that $(\phi_i)_{i\in J}$ is a Riesz sequence
with bounds $1-\varepsilon$ and $1+\varepsilon$.

Multiplying the initial $O(B)$ pieces by the $O(\varepsilon^{-2})$ refinement
inside each piece gives the claimed $O(B\varepsilon^{-2})$ partition size.
\end{proof}

\paragraph{Scope and optimality.}
This answers the exponent gap in Remark 4.9 up to universal constants.  The
supporting result supplies the missing $\varepsilon^{-2}$ paving exponent.  The
source paper already notes that the linear dependence on $B$ is optimal, and
that $\Omega(\varepsilon^{-2})$ blocks are necessary as $\varepsilon\to0$.

\paragraph{References.}
\begin{itemize}
\item M. Bownik, P. G. Casazza, A. W. Marcus, D. Speegle,
\emph{Improved bounds in Weaver and Feichtinger Conjectures},
arXiv:1508.07353.
\item M. Ravichandran, N. Srivastava,
\emph{Asymptotically Optimal Multi-Paving},
arXiv:1706.03737.
\item P. Casazza, D. Edidin, D. Kalra, V. Paulsen,
\emph{Projections and the Kadison--Singer problem},
Oper. Matrices 1 (2007), 391--408.
\end{itemize}

\end{document}

