\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\newcommand{\ellp}{\ell_p}

\title{Literature Status for a Schlumprecht Ergodicity Question in arXiv:math/0511170}
\author{Run fa\_banach\_001, lane 7}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Status}

This note records a literature-implied answer to a concrete question in
Ferenczi, arXiv:math/0511170, and a partial later-literature answer to the
broader ergodicity conjecture stated there.

\section*{Source Signals}

In the introduction, the source paper states the conjecture that every
separable Banach space is either isomorphic to $\ell_2$ or ergodic.

Later, after proving that $E_0$ Borel reduces to permutative equivalence on
block bases of Schlumprecht's space $S$, the source says:
\begin{quote}
It is however still unknown if $S$ is ergodic.
\end{quote}

\section*{Supporting Result}

The later paper Cuellar Carrera, arXiv:1611.05500, proves that every separable
non-near-Hilbert Banach space is ergodic. Equivalently, a non-ergodic separable
Banach space must be near Hilbert. This narrows the broad conjecture from
arXiv:math/0511170 to the near-Hilbert case.

The same later paper proves that the Schlumprecht-type spaces $S_{p,r}$ and
their duals are not near Hilbert, and explicitly concludes that they are
ergodic. Since Schlumprecht's original space is $S_{1,\infty}$, this gives a
positive answer to the source paper's concrete question: Schlumprecht's space
$S$ is ergodic.

\section*{Scope}

This packet is not a new theorem. It records an already-known later implication.
The broad conjecture that $\ell_2$ is the only non-ergodic separable Banach
space remains open in the near-Hilbert range. The Schlumprecht-space question
from the source paper is settled positively by the later theorem.

\section*{References}

\begin{enumerate}
\item V. Ferenczi, \emph{On the number of non permutatively equivalent
sequences in a Banach space}, arXiv:math/0511170.
\item W. Cuellar Carrera, \emph{Non-ergodic Banach spaces are near Hilbert},
arXiv:1611.05500.
\end{enumerate}

\end{document}
