\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\emergencystretch=3em

\title{Literature Status Note: Question 7.3 of arXiv:1908.07814}
\author{run fa\_banach\_001, lane 3}
\date{2026-07-19}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{literature\_already\_answered.} This is a literature-status packet, not
an original proof packet.

\paragraph{Source question.}
The source paper is Li--Nowak--Spakula--Zhang, \emph{Quasi-local Algebras and
Asymptotic Expanders}, arXiv:1908.07814 \cite{LNSZ}. In Section 7, Question 7.3
asks whether, for a coarse disjoint union $X$ of bounded-geometry asymptotic
expanders $\{X_n\}_{n\in\mathbb N}$, the space $X$ can coarsely embed into a
Hilbert space. The source paper proves a negative answer only with the extra
hypothesis $C_u^*(X)=C_{uq}^*(X)$ in Proposition 7.4.

\paragraph{Answering paper.}
The supporting paper is Khukhro--Li--Vigolo--Zhang, \emph{On the structure of
asymptotic expanders}, arXiv:1910.13320 \cite{KLVZ}. The introduction explicitly
identifies [21, Question 7.3] as the motivating question and says that the paper
gives a negative answer. Theorem B, restated as Theorem 4.2, proves the stronger
statement that if $\{X_n\}_{n\in\mathbb N}$ is a bounded-geometry sequence of
finite metric spaces with $|X_n|\to\infty$, $X$ is its coarse disjoint union, and
$\{X_n\}$ is a sequence of asymptotic expanders, then $X$ cannot be coarsely
embedded into any Banach space in the class $\mathcal C_0$. This class includes
Hilbert-space targets, and the paper records the corresponding obstruction for
$L^p$ spaces, $1\le p<\infty$, and uniformly curved Banach spaces.

\paragraph{Identification.}
The source question asks for the existence of a Hilbert coarse embedding under
bounded geometry and the asymptotic-expander hypothesis. The answer paper uses
the same objects and explicitly cites the source question. Theorem 4.2 negates
the existence of such embeddings into a larger class of Banach targets, so it
answers Question 7.3 negatively.

\paragraph{Scope limitations.}
This packet records only the already-known negative answer to Question 7.3 of
\cite{LNSZ}. It does not claim a new proof. It also does not settle Question 7.1
from the source paper. The supporting paper has additional applications to the
coarse Baum--Connes conjecture, but those are outside this packet's scoped
claim.

\paragraph{Search evidence.}
The run's cheap indexes had no exact existing packet for arXiv:1908.07814 or
Question 7.3. Web/arXiv search located arXiv:1910.13320, whose introduction and
Theorem 4.2 explicitly identify and answer [21, Question 7.3]. This packet
therefore belongs in the literature-status folder, not in \texttt{solutions/full/}.

\begin{thebibliography}{9}
\bibitem{LNSZ}
Kang Li, Piotr Nowak, Jan Spakula, and Jiawen Zhang,
\emph{Quasi-local Algebras and Asymptotic Expanders},
arXiv:1908.07814, 2019. \url{https://arxiv.org/abs/1908.07814}

\bibitem{KLVZ}
Ana Khukhro, Kang Li, Federico Vigolo, and Jiawen Zhang,
\emph{On the structure of asymptotic expanders},
arXiv:1910.13320, 2019; Advances in Mathematics 393 (2021), 108073.
\url{https://arxiv.org/abs/1910.13320}
\end{thebibliography}

\end{document}
