\documentclass[10pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\title{Literature status of the amenable operator algebra similarity question}
\author{Automated mathematics run \texttt{fa\_banach\_001}\\
Lane 4, \texttt{agent\_lane\_04}, model GPT5.6}
\date{23 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.91\textwidth}{
\textbf{Status.} Literature already answered. This is a retrieval and
identification note, not a new proof or counterexample.
}}
\end{center}

\section*{Source question}

Choi's paper \cite{Choi2011}, arXiv:1012.4259v3, asks in its abstract and
Introduction on PDF page 1 whether every closed amenable subalgebra of
$B(H)$ must be similar to an amenable $C^*$-algebra. It emphasizes that the
question was then open even for singly-generated algebras. On PDF page 2 the
paper also observes that extending its finite-von-Neumann-algebra theorem to
the semifinite setting would settle the commutative case.

\section*{Identification}

The unrestricted question has a negative answer. Choi, Farah, and Ozawa
\cite{CFO2013}, Theorem 1 on PDF page 2, construct a unital amenable operator
algebra $\mathcal A$ that is not isomorphic to any $C^*$-algebra. If
$S\mathcal A S^{-1}$ were a $C^*$-algebra for some invertible $S$, conjugation
by $S$ would be an algebra isomorphism from $\mathcal A$ onto a $C^*$-algebra.
Thus their example is not similar to a $C^*$-algebra.

The abelian and singly-generated cases have a positive answer. Marcoux and
Popov \cite{MP2013}, Theorem 2.10 on PDF page 11, prove that every closed
abelian amenable operator algebra is similar to a $C^*$-algebra. Their
Corollary 2.11 on the same page states that, for $T\in B(H)$, the norm-closed
unital algebra $\mathcal A_T$ generated by $T$ is amenable if and only if
$T$ is similar to a normal operator whose spectrum is a Lavrentieff set.

The provenance match is explicit rather than inferred: Marcoux and Popov cite
Choi's source result and state that the unrestricted question was resolved
negatively by Choi--Farah--Ozawa.

\section*{Scope limitation}

The negative example is nonseparable and nonabelian. Both supporting papers
state that the separable nonabelian version remains open. A bounded arXiv
search through July 2026 found no later resolution, but this compact packet
does not claim an exhaustive survey of that narrower problem.

\begin{thebibliography}{9}
\bibitem{Choi2011}
Y. Choi,
\emph{On commutative, operator amenable subalgebras of finite von Neumann
algebras}, arXiv:1012.4259v3 (2011).

\bibitem{CFO2013}
Y. Choi, I. Farah, and N. Ozawa,
\emph{A nonseparable amenable operator algebra which is not isomorphic to a
$C^*$-algebra}, arXiv:1309.2145 (2013).

\bibitem{MP2013}
L. W. Marcoux and A. I. Popov,
\emph{Abelian, amenable operator algebras are similar to $C^*$-algebras},
arXiv:1311.2982v2 (2013).
\end{thebibliography}

\end{document}
