\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath,amssymb}

\title{Literature-Implied Partial Answer to a Block-Minimal/Meager-Isomorphism Problem}
\author{Run \texttt{fa\_banach\_001}, lane 17}
\date{June 19, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{literature\_implied\_answer (partial local-block-minimal variant).}
This is not a full solution of the source problem.

\section*{Source Problem}

The source paper is V. Ferenczi and G. Godefroy,
\emph{Tightness of Banach spaces and Baire category}, arXiv:1111.6444.
At the end of Section 4, after Example T concerning $T^*$, the authors ask:
\begin{quote}
Find a space $X$ which embeds as a block-subspace of all its block-subspaces,
but such that $\mathrm{Is}$ is meager.
\end{quote}
Here $\mathrm{Is}$ denotes the isomorphism relation on the Polish space $b(X)$
of block-subspaces.

\section*{Supporting Result}

The supporting paper is V. Ferenczi and C. Rosendal,
\emph{Banach spaces without minimal subspaces}, arXiv:0711.1350.  In Section
6, Example \texttt{OdellSchlumprecht}, they prove:
\begin{quote}
There exists a reflexive, tight, locally block minimal Banach space.
\end{quote}

\section*{Identification}

The source paper proves in Proposition 3.3 that if $X$ is tight, then the
embeddability relation $\mathrm{Emb}$ is meager in $b(X)^2$.  Since
\[
  \mathrm{Is}\subseteq \mathrm{Emb},
\]
the isomorphism relation $\mathrm{Is}$ is also meager for every tight space.
Combining this with arXiv:0711.1350 gives a reflexive Banach space whose basis
is locally block minimal and whose block-subspace isomorphism relation is
meager.

Thus the natural local-block-minimal weakening of the source problem has a
positive answer in the literature.

\section*{Limitations}

This is an agent-identified implication rather than an explicit answer by the
supporting authors to arXiv:1111.6444.  It does not give a space which embeds
as a block-subspace of all its block-subspaces.  Local block minimality is a
finite-dimensional block finite-representability condition, weaker than
block-minimality.  The exact source problem therefore remains open from this
packet's point of view.

\section*{Search Evidence}

The local run indexes were searched for arXiv:1111.6444, the source title,
\texttt{block-minimal}, \texttt{block minimal}, \texttt{locally block minimal},
\texttt{Is is meager}, and the exact problem sentence.  No existing packet for
this implication was found.  Bounded web searches for the exact
block-minimal/meager problem and close variants did not reveal a later exact
solution.

\begin{thebibliography}{9}
\bibitem{FG}
V. Ferenczi and G. Godefroy,
\emph{Tightness of Banach spaces and Baire category},
arXiv:1111.6444.

\bibitem{FR}
V. Ferenczi and C. Rosendal,
\emph{Banach spaces without minimal subspaces},
arXiv:0711.1350.
\end{thebibliography}

\end{document}
