\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}

\title{Literature Status: Almost Complete Coarse Embeddability}
\author{Run \texttt{fa\_banach\_001} -- agent \texttt{agent\_lane\_00}}
\date{21 July 2026}

\begin{document}
\maketitle

\textbf{Status:} \texttt{literature\_already\_answered}.

\section*{Source question}
Braga and Ch\'avez-Dom\'inguez ask in Question 4.3 of
\cite{source} whether almost complete coarse embeddability is strictly weaker
than almost complete $\mathbb R$-isomorphic embeddability.  Equivalently, do
there exist operator spaces $X,Y$ such that $X$ almost completely coarsely
embeds into $Y$, while $X$ does not almost completely
$\mathbb R$-isomorphically embed into $Y$?

\section*{Identification}
Braga, Ch\'avez-Dom\'inguez, and Sinclair explicitly state that their main
conceptual result answers this question \cite[Introduction and Theorem
1.4]{answer}.  They construct operator spaces $X,Y$ such that $X$ almost
completely isometrically embeds into $Y$, but $X$ does not even
$\mathbb R$-isomorphically embed into $Y$ as a Banach space.

An almost complete isometric embedding is in particular an almost complete
coarse embedding, with common control functions $\rho(t)=\omega(t)=t$.
Moreover, if there is no real-linear Banach-space embedding $X\to Y$, then
there cannot be a sequence of real-linear maps whose $n$th amplifications are
uniformly isomorphic embeddings.  Theorem 1.4 therefore gives an affirmative,
strictly stronger answer to the exact source question.

\section*{Scope and provenance}
The supporting authors knew they were answering Question 4.3 and cite the
source paper at the point of the claim.  This packet records a literature
answer, not a new proof.  Their example uses a nonseparable Hilbertian
operator space; the source question is existential and imposes no separability
condition, so the answer is complete.  The supporting paper separately proves
a positive linearization statement for separable domains under the stronger
almost-complete-isometric hypothesis.

\begin{thebibliography}{9}
\bibitem{source}
B. M. Braga and J. A. Ch\'avez-Dom\'inguez,
\emph{Completely coarse maps are $\mathbb R$-linear},
Proc. Amer. Math. Soc. 149 (2021), 1139--1149;
\href{https://arxiv.org/abs/2006.00948}{arXiv:2006.00948}.

\bibitem{answer}
B. M. Braga, J. A. Ch\'avez-Dom\'inguez, and T. Sinclair,
\emph{Lipschitz geometry of operator spaces and Lipschitz-free operator
spaces}, Math. Ann. 388 (2024), 1053--1090;
\href{https://arxiv.org/abs/2104.02714}{arXiv:2104.02714}.
\end{thebibliography}

\end{document}

