\documentclass[11pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlength{\emergencystretch}{3em}

\title{Problem 3 in Moslehian's complemented subspace survey is answered}
\author{Agent lane 16}
\date{2026-06-29}

\begin{document}
\maketitle

\textbf{Status.} \texttt{literature\_already\_answered}.  This packet records a
later explicit counterexample to one of the open problems listed in Mohammad
Sal Moslehian's survey \cite{Moslehian}.

\textbf{Source question.}  In Section 12, ``Some interesting problems,'' Problem
3 asks:
\[
\begin{gathered}
\text{Is every complemented vector subspace of } C(S)\\
\text{isomorphic to some } C(S_1)\text{?}
\end{gathered}
\]
The problem appears on PDF page 10 of \cite{Moslehian}.  In modern terminology,
this asks whether the class of \(C(K)\)-spaces is closed under complemented
subspaces.

\textbf{Supporting answer.}  Plebanek and Salguero Alarcon \cite{PSA} explicitly
formulate the complemented subspace problem for \(C\)-spaces as Problem 1.1 and
then give a negative answer.  Their abstract states that they construct a
compact space \(L\) and a \(1\)-complemented subspace of \(C(L)\) which is not
isomorphic to a space of continuous functions.  Their Theorem 1.1 gives the
precise construction: there are compacta \(K,L\), a continuous surjection
\(\theta:L\to K\), and a closed subspace \(X\subset C(L)\) such that
\[
  C(L)\simeq \theta^\circ[C(K)]\oplus X,
\]
both summands are \(1\)-complemented in \(C(L)\), and \(X\) is not a
\(C\)-space.

\textbf{Identification.}  This is exactly a negative answer to Moslehian's
Problem 3.  The supporting paper does not merely imply the answer indirectly:
it names the complemented subspace problem for \(C\)-spaces and presents its
main theorem as a counterexample.

\textbf{Scope limitations.}  The source survey lists seven broad problems.  This
packet clears only Problem 3.  It does not claim answers to the general
complemented subspace classification problem, the injective-space question, the
von Neumann algebra question, or the prime-space question.

\textbf{Search evidence.}  The run's cheap indexes were searched for
arXiv:0501048, arXiv:2111.13860, the source title, and phrases around
complemented subspaces of \(C(K)\)-spaces.  No prior packet for this
source/supporting-pair answer was present.  A web search for the same phrases
located arXiv:2111.13860 as the direct later counterexample.

\begin{thebibliography}{9}
\bibitem{Moslehian}
M. S. Moslehian,
\emph{A Survey on the Complemented Subspace Problem},
arXiv:math/0501048, 2005.
\url{https://arxiv.org/abs/math/0501048}

\bibitem{PSA}
G. Plebanek and A. Salguero Alarcon,
\emph{The complemented subspace problem for \(C(K)\)-spaces: A counterexample},
arXiv:2111.13860, 2021.
\url{https://arxiv.org/abs/2111.13860}
\end{thebibliography}

\end{document}
