\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathrsfs}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newcommand{\Sph}{\mathscr S}
\newcommand{\SE}{S_E}
\newcommand{\SEp}{S_{E^{(p)}}}
\newcommand{\Lip}{\Lambda}
\newcommand{\R}{\mathbb R}

\begin{document}

\begin{center}
{\Large Literature-implied full answer}\\[3pt]
{\large The \(p\)-convexification Mazur map restriction \(p\ge 3\)}
\end{center}

\paragraph{Status.}
\textbf{literature\_implied\_answer (full source question).}

\paragraph{Source question.}
In Section 4 of Javier Alejandro Chavez-Dominguez,
\emph{Uniform homeomorphisms between spheres of unitarily invariant ideals},
arXiv:2305.07169, the theorem labelled
\begin{center}
\texttt{thm-homeomorphism-convexification}
\end{center}
proves that for \(3\le p<\infty\), and every \(1\)-symmetric sequence space
\(E\), the map
\[
G_p(x)=u|x|^p,\qquad x=u|x|,
\]
is a uniform homeomorphism from \(\Sph(\SEp)\) onto \(\Sph(\SE)\).  The
remark immediately after the theorem says that it is not known whether the
restriction \(p\ge 3\) is needed, and suspects it is not.  The restriction
enters through the second inequality in Lemma \texttt{lemma-sum}, whose proof
uses Joci\'c's Theorem 3.1.

\paragraph{Supporting theorem.}
In Section 11 of A. B. Aleksandrov and V. V. Peller,
\emph{Functions of operators under perturbations of class \(S_p\)},
arXiv:0908.3623, Theorem \texttt{sigmaq} proves the following pointwise
singular-value estimate.  If \(0<\alpha<1\), \(f\in \Lip_\alpha(\R)\),
\(A,B\) are bounded self-adjoint operators, and \(Q\) is bounded, then
\[
s_j\!\left(\left|f(A)Q-Qf(B)\right|^{1/\alpha}\right)
\le C_\alpha \|f\|_{\Lip_\alpha(\R)}^{1/\alpha}
   \|Q\|^{(1-\alpha)/\alpha} s_j(AQ-QB),
\qquad j\ge0.
\]
This is stronger than an estimate in a particular Schatten norm: it is
coordinatewise domination of singular values.

\paragraph{Identification.}
Fix \(p>1\), put \(\alpha=1/p\), and set
\[
f(t)=\operatorname{sign}(t)|t|^{1/p}.
\]
Then \(f\in\Lip_{1/p}(\R)\).  For \(x,y\in \SEp^+\) and \(b\in S_\infty\),
apply Theorem \texttt{sigmaq} with
\[
A=x^p,\qquad B=-y^p,\qquad Q=b.
\]
Since \(f(x^p)=x\) and \(f(-y^p)=-y\), the left hand side becomes
\(xb+by\), while
\[
AQ-QB=x^p b+b y^p.
\]
Therefore, for all \(j\ge0\),
\[
s_j\!\left(|xb+by|^p\right)
\le K_p \|b\|_\infty^{p-1}s_j(x^pb+by^p),
\]
where \(K_p=C_{1/p}\|f\|_{\Lip_{1/p}}^p\).

Because \(E\) is \(1\)-symmetric, its norm is monotone under coordinatewise
domination of singular-value sequences.  Hence
\[
\big\||xb+by|^p\big\|_{\SE}
\le K_p\|b\|_\infty^{p-1}\|x^pb+by^p\|_{\SE}.
\]
Using the definition of \(p\)-convexification,
\(\|T\|_{\SEp}^p=\||T|^p\|_{\SE}\), this gives
\[
\|xb+by\|_{\SEp}
\le K_p^{1/p}\|b\|_\infty^{1-1/p}
     \|x^pb+by^p\|_{\SE}^{1/p}.
\]
This is exactly the second, formerly \(p\ge3\)-restricted, inequality in
Lemma \texttt{lemma-sum}, now valid for every \(p>1\).

\paragraph{Conclusion.}
The rest of the Section 4 proof in arXiv:2305.07169 uses this reverse
anticommutator estimate to obtain the inverse uniform-continuity estimates
for the generalized Mazur map.  The forward uniform continuity of \(G_p\) is
already proved there for all \(p\ge1\).  Replacing the cited Joci\'c step by
the Aleksandrov--Peller singular-value estimate removes the only stated
\(p\ge3\) obstruction.  Consequently, for every \(1<p<\infty\) and every
\(1\)-symmetric sequence space \(E\), the map
\[
G_p:\Sph(\SEp)\longrightarrow \Sph(\SE)
\]
is a uniform homeomorphism, with moduli depending only on \(p\).

\paragraph{Provenance and search evidence.}
This is a literature-implied answer, not an independent new theorem: the
supporting theorem is from arXiv:0908.3623 and predates the source paper.
The supporting paper does not explicitly identify Chavez-Dominguez's later
question.  The implication appears only after the substitution
\(A=x^p\), \(B=-y^p\), \(Q=b\), and after observing that pointwise
singular-value domination passes through arbitrary \(1\)-symmetric sequence
norms.  The run indexes already contained only the weaker arXiv:0907.3049
operator-norm subcase packet; no prior full packet for this
arXiv:2305.07169 question was present.

\paragraph{Scope limitations.}
No part of the original question remains open under the hypotheses stated in
Theorem \texttt{thm-homeomorphism-convexification}.  Human review should
check only the transfer from singular-value domination to the general
\(S_E\)-norm and the claim that Section 4 has no additional \(p\ge3\)
dependencies beyond Lemma \texttt{lemma-sum}.

\paragraph{References.}
\begin{itemize}
\item J. A. Chavez-Dominguez, \emph{Uniform homeomorphisms between spheres
of unitarily invariant ideals}, arXiv:2305.07169.
\item A. B. Aleksandrov and V. V. Peller, \emph{Functions of operators under
perturbations of class \(S_p\)}, arXiv:0908.3623, Section 11,
Theorem \texttt{sigmaq}.
\end{itemize}

\end{document}
