\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1.05in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\setlist{nosep}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\FBL}[2]{\operatorname{FBL}^{(#1)}[#2]}
\newcommand{\FVL}[1]{\operatorname{FVL}[#1]}
\newcommand{\Id}{\operatorname{Id}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\eps}{\varepsilon}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\abs}[1]{\lvert #1\rvert}
\newcommand{\norm}[1]{\lVert #1\rVert}
\newcommand{\pair}[2]{\langle #1,#2\rangle}

\title{Order Continuity for Closed Subspaces of Free \\[-1mm]
\(p\)-Convex Banach Lattices:\\
The Complemented Case and a Finite-\(p\) Counterexample}
\author{Independent research note}
\date{June 22, 2026}

\begin{document}
\maketitle

\begin{abstract}
We first verify a supplied partial argument: if a bounded operator
\(T:F\to E\) has a bounded left inverse, then the induced lattice
homomorphism
\(\wh T:\FBL{p}{F}\to\FBL{p}{E}\) is order continuous for every
\(1\le p\le\infty\).  The proof is correct, but this is essentially the
complemented-range part of the original proof of Oikhberg--Taylor--Tradacete--
Troitsky, the part explicitly retained in their corrigendum.

We then answer the remaining finite-\(p\) closed-subspace question negatively.
Let \(F\) be the closed span of the Rademacher functions in \(L_1[0,1]\).
Thus \(F\) is isomorphic to \(\ell_2\).  For every \(1\le p<\infty\), the
canonical lattice homomorphism
\[
  \FBL{p}{F}\longrightarrow \FBL{p}{L_1[0,1]}
\]
is not order continuous.  The same pair \(F\subset L_1[0,1]\) works
simultaneously for all finite \(p\).  Combined with the theorem of
Azouzi--Dhifaoui for \(p=\infty\), this gives a sharp finite-versus-infinite
\(p\) dichotomy.  The counterexample and proof below are independent and
have not been peer reviewed; a literature search through the date above did
not locate a prior finite-\(p\) resolution.
\end{abstract}

\section{Background and statement of the answer}

All Banach spaces and Banach lattices are real.  For a Banach space \(X\)
and \(1\le p\le\infty\), write \(\FBL{p}{X}\) for the free \(p\)-convex
Banach lattice generated by \(X\), with canonical generator map
\(x\mapsto\delta_x^X\).  If \(A:X\to Y\) is bounded, its canonical extension
is denoted by
\[
  \wh A:\FBL{p}{X}\longrightarrow\FBL{p}{Y}.
\]
In the standard functional representation,
\[
  (\wh A f)(y^*)=f(A^*y^*) \qquad (y^*\in Y^*),                 \tag{1.1}
\]
and the construction is functorial:
\[
  \widehat{BA}=\wh B\,\wh A.                                  \tag{1.2}
\]

Oikhberg, Taylor, Tradacete and Troitsky originally claimed that, whenever
\(F\) is a closed subspace of \(E\), the inclusion-induced map
\(\FBL{p}{F}\to\FBL{p}{E}\) is order continuous for every \(p\)
\cite[Theorem~3.4]{OTTT}.  The proof used an order-density assertion that
fails in infinite dimensions.  Azouzi and Dhifaoui proved that the inclusion
result remains true for \(p=\infty\), and left the finite-\(p\) case open
\cite[Theorem~11]{AD}.  The subsequent corrigendum says explicitly that the
old proof works only for complemented subspaces \cite{Corr}.

For definiteness, throughout the construction we use the Rademacher system
\[
  r_n(t)=(-1)^{\lfloor 2^{n+1}t\rfloor}\qquad(0\le t<1,\ n\ge0),
\]
with arbitrary values at the dyadic endpoints.  Thus the \(r_n\)'s are
independent \(\{-1,1\}\)-valued functions and are pairwise orthogonal in
\(L_2[0,1]\).

The principal result of this note is the following.

\begin{theorem}\label{thm:main}
Let \((r_n)_{n\ge0}\) be the Rademacher functions on \([0,1]\), let
\[
  E=L_1[0,1],
  \qquad
  F=\overline{\operatorname{span}}\{r_n:n\ge0\}^{\,L_1},
\]
and let \(\iota:F\hookrightarrow E\) be the inclusion.  Then \(F\) is a
closed subspace isomorphic to \(\ell_2\), and for every
\(1\le p<\infty\) the lattice homomorphism
\[
  \wh\iota:\FBL{p}{F}\longrightarrow\FBL{p}{E}
\]
is not order continuous.
\end{theorem}

Thus the answer for arbitrary closed subspaces is positive at
\(p=\infty\) and negative at every finite \(p\).

\section{Finite-\texorpdfstring{\(p\)}{p} preliminaries}

Fix \(1\le p<\infty\).  We use the concrete norm formula for
\(\FBL{p}{X}\): if \(f\) is a positively homogeneous function on \(X^*\),
then
\begin{equation}\label{eq:norm}
 \norm{f}_{\FBL{p}{X}}
 =\sup\left\{
   \left(\sum_{j=1}^m \abs{f(x_j^*)}^p\right)^{1/p}:
   \sup_{x\in B_X}
   \left(\sum_{j=1}^m\abs{x_j^*(x)}^p\right)^{1/p}\le1
 \right\}.
\end{equation}
The free lattice \(\FBL{p}{X}\) is the norm-closed sublattice generated by
\(\{\delta_x^X:x\in X\}\), where
\(\delta_x^X(x^*)=x^*(x)\).  In particular,
\begin{equation}\label{eq:evaluation}
  \abs{f(x^*)}\le \norm{f}_{\FBL{p}{X}}\norm{x^*}
  \qquad(f\in\FBL{p}{X},\ x^*\in X^*).
\end{equation}
Indeed, for \(x^*\ne0\), the one-element family
\(x^*/\norm{x^*}\) is admissible in \eqref{eq:norm}.

We shall repeatedly use the following elementary order criterion.  If
\((x_\alpha)\) is a decreasing net in a vector lattice with \(x_\alpha\ge0\),
then \(x_\alpha\downarrow0\) exactly when there is no nonzero positive
common lower bound.  Consequently, to disprove order continuity of a positive
operator it suffices to find \(x_n\downarrow0\) whose images have a nonzero
positive common lower bound.

\section{Verification of the complemented-range argument}

The supplied partial proof is correct.  We record it in operator form because
it also fixes the orientation of all functorial identities.

\begin{theorem}\label{thm:leftinverse}
Let \(1\le p\le\infty\), and let \(T:F\to E\) be bounded.  Suppose that
there is a bounded operator \(R:E\to F\) such that
\(RT=\Id_F\).  Then
\[
  \wh T:\FBL{p}{F}\longrightarrow\FBL{p}{E}
\]
is order continuous.
\end{theorem}

\begin{proof}
Let \(f_\alpha\downarrow0\) in \(\FBL{p}{F}_+\), and suppose that
\(0\le h\le\wh T f_\alpha\) for every \(\alpha\), where
\(h\in\FBL{p}{E}\).  We prove \(h=0\).

Assume otherwise and choose \(x^*\in E^*\) with \(h(x^*)>0\).  Put
\(y^*=T^*x^*\).  Then \(y^*\ne0\), since otherwise
\[
  0<h(x^*)\le (\wh T f_\alpha)(x^*)=f_\alpha(0)=0.
\]
Set \(d=x^*-R^*y^*\).  Since \(RT=\Id_F\), one has
\(d(Tu)=0\) for every \(u\in F\).  Choose \(u_0\in F\) such that
\(y^*(u_0)=1\), and define
\[
  Se=e+d(e)Tu_0 \qquad(e\in E).
\]
Then \(S\) is bounded, \(ST=T\), and
\[
  S^*R^*y^*=x^*.
\]
Indeed, for \(e\in E\),
\[
  (S^*R^*y^*)(e)
   =y^*(Re+d(e)RTu_0)
   =(R^*y^*)(e)+d(e)=x^*(e).
\]
By functoriality,
\[
  \wh S\,\wh T=\widehat{ST}=\wh T,
  \qquad
  \wh R\,\wh T=\widehat{RT}=\Id_{\FBL{p}{F}}.
\]
Therefore
\[
  0\le \wh R\,\wh S h
  \le \wh R\,\wh S\,\wh T f_\alpha
  =\wh R\,\wh T f_\alpha=f_\alpha
\]
for every \(\alpha\).  But
\[
  (\wh R\,\wh S h)(y^*)=h(S^*R^*y^*)=h(x^*)>0,
\]
so \(\wh R\,\wh S h\) is a nonzero positive common lower bound for
\((f_\alpha)\), a contradiction.
\end{proof}

\begin{remark}\label{rem:duplicate}
The hypothesis in Theorem~\ref{thm:leftinverse} says precisely that \(T\) is
an isomorphic embedding with complemented range.  Factoring \(T\) through
its range shows that this is the complemented-subspace case of the original
theorem.  The original paper already proved that case, and its corrigendum
explicitly states that this is the part of the proof that remains valid.
Thus the supplied argument is mathematically sound, but it is not a new
subcase of the literature \cite{Corr}.
\end{remark}

\section{A decreasing source sequence with infimum zero}

Let
\[
  H=\ell_2(\N_0),
  \qquad \N_0=\{0,1,2,\ldots\},
\]
with unit vector basis \((e_n)_{n\ge0}\).  We first choose a single slowly
decaying sequence that will work for every finite \(p\).

For \(j\ge1\), set
\[
  m_j=2^{j^2},
  \qquad
  M_j=\sum_{i=1}^j m_i,
  \qquad
  I_j=\{M_{j-1}+1,\ldots,M_j\},
\]
where \(M_0=0\).  Define
\begin{equation}\label{eq:sndef}
  s_n=\frac1j \qquad(n\in I_j).
\end{equation}
Then \((s_n)\) is non-increasing and tends to zero.  Moreover, for every
finite \(q\),
\begin{equation}\label{eq:blockgrowth}
  \frac1j\,m_j^{1/q}\longrightarrow\infty.
\end{equation}
Set
\begin{equation}\label{eq:unfn}
  u_0=e_0,
  \qquad
  u_n=e_0+s_ne_n\quad(n\ge1),
  \qquad
  f_n=\bigwedge_{k=0}^n\abs{\delta_{u_k}^H}
       \in\FBL{p}{H}_+.
\end{equation}

We need one density observation.

\begin{lemma}\label{lem:finite-density}
The union of the vector sublattices generated by
\(\delta_{e_0}^H,\ldots,\delta_{e_N}^H\), \(N\ge0\), is norm dense in
\(\FBL{p}{H}\).
\end{lemma}

\begin{proof}
The finitely supported vectors are dense in \(H\), and
\(x\mapsto\delta_x^H\) is an isometry.  Hence the closed sublattice generated
by \(\{\delta_x^H:x\in c_{00}\}\) contains every \(\delta_x^H\),
\(x\in H\), and is therefore all of \(\FBL{p}{H}\).  Every lattice
expression involving finitely many finitely supported vectors is contained in
the sublattice generated by \(e_0,\ldots,e_N\) for some \(N\).
\end{proof}

\begin{proposition}\label{prop:source-zero}
For every \(1\le p<\infty\), the sequence in \eqref{eq:unfn} satisfies
\[
  f_n\downarrow0 \quad\text{in }\FBL{p}{H}.
\]
\end{proposition}

\begin{proof}
The sequence is decreasing and positive.  Suppose that
\(0\le g\le f_n\) for every \(n\).  We prove \(g=0\).

Assume \(g\ne0\).  By positive homogeneity and
\eqref{eq:evaluation}, choose \(x^*\in H^*\) with
\(\norm{x^*}=1\) and
\[
  \eta:=g(x^*)>0.
\]
Write
\[
  a=x^*(e_0),\qquad b_n=x^*(e_n)\quad(n\ge1).
\]
Since \(g\le f_0=\abs{\delta_{e_0}^H}\), we have \(a\ne0\).
By Lemma~\ref{lem:finite-density}, choose \(N\) and an element \(\phi\)
of the sublattice generated by
\(\delta_{e_0}^H,\ldots,\delta_{e_N}^H\) such that
\begin{equation}\label{eq:approxphi}
  \norm{g-\phi}_{\FBL{p}{H}}<\frac{\eta}{4}.
\end{equation}
Then \eqref{eq:evaluation} gives
\begin{equation}\label{eq:phipos}
  \phi(x^*)>\frac{3\eta}{4}.
\end{equation}

For \(n>N\), define
\[
  d_n=b_n+\frac{a}{s_n},
  \qquad
  y_n^*=x^*-d_ne_n^*.
\]
Here \(e_n^*\) is the \(n\)-th coordinate functional.  We have
\[
  y_n^*(u_n)=a+s_n(b_n-d_n)=0.
\]
Thus
\begin{equation}\label{eq:gyzero}
  g(y_n^*)=0,
  \qquad
  \phi(y_n^*)=\phi(x^*)
  \quad(n>N),
\end{equation}
because \(g\le f_n\), while \(\phi\) depends only on the first
\(N+1\) coordinates.

Put
\[
  w_n=\frac1{\abs{d_n}}
      =\frac{s_n}{\abs{a+s_nb_n}}.
\]
Since \(b_n\to0\), after increasing \(N\) we may assume that
\begin{equation}\label{eq:wcompare}
  c s_n\le w_n\le C s_n \qquad(n>N)
\end{equation}
for constants \(c,C>0\) independent of \(n\).

Choose a block \(I_j\subset\{n>N\}\).  We now select nonnegative weights
\((\lambda_n)_{n\in I_j}\).  If \(p\ge2\), set
\[
  \lambda_n=w_n.
\]
Then \(\abs{\lambda_nd_n}=1\), and for every \(x=(x_k)\in H\),
\begin{equation}\label{eq:diaglargep}
  \left(\sum_{n\in I_j}\abs{\lambda_nd_nx_n}^p\right)^{1/p}
  \le \left(\sum_{n\in I_j}\abs{x_n}^2\right)^{1/2}
  \le\norm{x}.
\end{equation}
Moreover, by \eqref{eq:wcompare} and \eqref{eq:blockgrowth},
\[
  L_j:=\left(\sum_{n\in I_j}\lambda_n^p\right)^{1/p}
  \ge \frac{c}{j}m_j^{1/p}\longrightarrow\infty.
\]

If \(1\le p<2\), set
\[
  \alpha_j=m_j^{\,1/2-1/p},
  \qquad
  \lambda_n=\alpha_jw_n\quad(n\in I_j).
\]
Since
\(\norm{z}_{\ell_p^{m_j}}\le m_j^{1/p-1/2}\norm{z}_{\ell_2^{m_j}}\),
we again have
\begin{equation}\label{eq:diagsmallp}
  \left(\sum_{n\in I_j}\abs{\lambda_nd_nx_n}^p\right)^{1/p}
  =\alpha_j\left(\sum_{n\in I_j}\abs{x_n}^p\right)^{1/p}
  \le\norm{x}.
\end{equation}
This time
\[
  L_j:=\left(\sum_{n\in I_j}\lambda_n^p\right)^{1/p}
  \ge \frac{c}{j}\,m_j^{1/2}\longrightarrow\infty.
\]
Thus, in both cases, \(L_j\to\infty\) and the diagonal estimate
\begin{equation}\label{eq:diagall}
  \left(\sum_{n\in I_j}\abs{\lambda_nd_nx_n}^p\right)^{1/p}
  \le\norm{x}
\end{equation}
holds.

For \(x\in H\), Minkowski's inequality and \(\norm{x^*}=1\) now give
\[
 \begin{aligned}
  \left(\sum_{n\in I_j}\abs{\lambda_ny_n^*(x)}^p\right)^{1/p}
  &\le
  L_j\abs{x^*(x)}
   +\left(\sum_{n\in I_j}\abs{\lambda_nd_nx_n}^p\right)^{1/p}\\
  &\le (L_j+1)\norm{x}.
 \end{aligned}
\]
Hence the finite family
\[
  \left(\frac{\lambda_n}{L_j+1}y_n^*\right)_{n\in I_j}
\]
is admissible in \eqref{eq:norm}.  Using \eqref{eq:gyzero} and positive
homogeneity, we obtain
\[
 \begin{aligned}
  \norm{g-\phi}_{\FBL{p}{H}}
  &\ge
  \left(
    \sum_{n\in I_j}
    \abs{(g-\phi)\left(\frac{\lambda_n}{L_j+1}y_n^*\right)}^p
  \right)^{1/p}\\
  &=\phi(x^*)\frac{L_j}{L_j+1}.
 \end{aligned}
\]
Letting \(j\to\infty\), the right-hand side tends to \(\phi(x^*)\),
which is larger than \(3\eta/4\) by \eqref{eq:phipos}.  This contradicts
\eqref{eq:approxphi}.  Therefore \(g=0\), and \(f_n\downarrow0\).
\end{proof}

\section{The images acquire a nonzero lower bound in \texorpdfstring{\(L_1\)}{L1}}

We first record the ambient norm estimate that makes the construction work.

\begin{lemma}\label{lem:rademacher-join}
Let \(J\subset\N_0\) be finite and nonempty.  For every
\(1\le p<\infty\),
\[
  \norm{\bigvee_{k\in J}\abs{\delta_{r_k}^{L_1}}}_{\FBL{p}{L_1[0,1]}}
  \le1.
\]
\end{lemma}

\begin{proof}
Let \(\varphi_1,\ldots,\varphi_m\in L_\infty[0,1]\) be admissible in
\eqref{eq:norm}; equivalently, the operator
\[
  A:L_1[0,1]\longrightarrow\ell_p^m,
  \qquad
  Ax=\left(\int_0^1x(t)\varphi_j(t)\,dt\right)_{j=1}^m,
\]
has norm at most one.  Its adjoint has norm at most one, and finite-dimensional
duality therefore gives
\begin{equation}\label{eq:pointwise-lp}
  \left(\sum_{j=1}^m\abs{\varphi_j(t)}^p\right)^{1/p}\le1
  \quad\text{for almost every }t.
\end{equation}
For completeness, one obtains a common null set by testing \(A^*\) on a
countable dense subset of the unit ball of the conjugate finite-dimensional
space.

Since \(\abs{r_k}=1\) almost everywhere, Minkowski's integral inequality and
\eqref{eq:pointwise-lp} yield
\[
 \begin{aligned}
  &\left(
    \sum_{j=1}^m
    \left(\max_{k\in J}\abs{\int_0^1 r_k(t)\varphi_j(t)\,dt}\right)^p
  \right)^{1/p}\\
  &\qquad\le
  \left(\sum_{j=1}^m\left(\int_0^1\abs{\varphi_j(t)}\,dt\right)^p\right)^{1/p}\\
  &\qquad\le
  \int_0^1
  \left(\sum_{j=1}^m\abs{\varphi_j(t)}^p\right)^{1/p}\,dt
  \le1.
 \end{aligned}
\]
Taking the supremum over admissible families proves the claim.
\end{proof}

Let
\[
  T:H\longrightarrow L_1[0,1],
  \qquad
  T(x_0,x_1,\ldots)=\sum_{n=0}^\infty x_nr_n.
\]
Khintchine's inequality implies that \(T\) is an isomorphic embedding.
Consequently,
\[
  F=T(H)=\overline{\operatorname{span}}\{r_n:n\ge0\}^{\,L_1}
\]
is closed and isomorphic to \(\ell_2\).  For the vectors from
\eqref{eq:unfn}, put
\[
  v_0=Tu_0=r_0,
  \qquad
  v_n=Tu_n=r_0+s_nr_n \quad(n\ge1).
\]
For fixed finite \(p\), define
\begin{equation}\label{eq:Gn}
  G_n=\bigwedge_{k=0}^n\abs{\delta_{v_k}^{L_1}}
  \in\FBL{p}{L_1[0,1]}_+.
\end{equation}
By functoriality,
\begin{equation}\label{eq:imagefn}
  G_n=\wh T f_n.
\end{equation}

\begin{proposition}\label{prop:ambient-limit}
For every \(1\le p<\infty\), the sequence \((G_n)\) converges in norm to
an element \(h_p\in\FBL{p}{L_1[0,1]}_+\) such that
\[
  0<h_p\le G_n\qquad(n\ge0).
\]
More precisely,
\[
  \norm{G_n-G_m}_{\FBL{p}{L_1}}\le s_{n+1}
  \qquad(m>n).
\]
\end{proposition}

\begin{proof}
For \(m>n\), the scalar lattice identity
\[
 a-\bigl(a\wedge b_{n+1}\wedge\cdots\wedge b_m\bigr)
 =\bigvee_{k=n+1}^m(a-b_k)^+
\]
applied pointwise gives
\[
  G_n-G_m
  =\bigvee_{k=n+1}^m
      \left(G_n-\abs{\delta_{v_k}^{L_1}}\right)^+.
\]
Since \(G_n\le\abs{\delta_{v_0}^{L_1}}\), the standard lattice inequality
\(\bigl\lvert\abs{x}-\abs{y}\bigr\rvert\le\abs{x-y}\) yields
\[
 \begin{aligned}
  0\le G_n-G_m
  &\le\bigvee_{k=n+1}^m
      \bigl\lvert
       \abs{\delta_{v_0}^{L_1}}-\abs{\delta_{v_k}^{L_1}}
      \bigr\rvert\\
  &\le\bigvee_{k=n+1}^m
      \abs{\delta_{v_0-v_k}^{L_1}}\\
  &=\bigvee_{k=n+1}^m s_k\abs{\delta_{r_k}^{L_1}}\\
  &\le s_{n+1}\bigvee_{k=n+1}^m\abs{\delta_{r_k}^{L_1}}.
 \end{aligned}
\]
Lemma~\ref{lem:rademacher-join} proves the norm estimate.  Thus \((G_n)\)
is norm Cauchy; let its limit be \(h_p\).  The positive cone is closed and
\(G_m\le G_n\) for \(m>n\), so \(0\le h_p\le G_n\) for every \(n\).

Finally, regard \(r_0\) as an element of \(L_\infty=L_1^*\).  Pairwise
orthogonality of the Rademacher functions in \(L_2\) gives
\[
  \pair{r_0}{v_0}=1,
  \qquad
  \pair{r_0}{v_k}=1+s_k\int_0^1r_0r_k=1 \quad(k\ge1).
\]
Hence \(G_n(r_0)=1\) for every \(n\).  Evaluation at \(r_0\) is continuous
by \eqref{eq:evaluation}, so \(h_p(r_0)=1\), and therefore \(h_p>0\).
\end{proof}

\section{Proof of the counterexample and the sharp dichotomy}

\begin{proof}[Proof of Theorem~\ref{thm:main}]
Let \(U:H\to F\) be the operator \(T\) viewed as a map onto its range.
Since \(U\) is an isomorphism of Banach spaces, functoriality shows that
\[
  \wh U:\FBL{p}{H}\longrightarrow\FBL{p}{F}
\]
is a lattice isomorphism, with inverse \(\widehat{U^{-1}}\).  Set
\[
  g_n=\wh U f_n\in\FBL{p}{F}.
\]
Proposition~\ref{prop:source-zero} gives \(g_n\downarrow0\).  Since
\(T=\iota U\), equations \eqref{eq:imagefn} and \eqref{eq:Gn} give
\[
  \wh\iota g_n=\wh\iota\,\wh U f_n=\wh T f_n=G_n.
\]
By Proposition~\ref{prop:ambient-limit}, the sequence \((G_n)\) has the
nonzero positive common lower bound \(h_p\).  Therefore \(\wh\iota\) is not
order continuous.

The spaces \(E\) and \(F\), and the sequence \((s_n)\), were chosen
independently of \(p\).  Hence the same closed Hilbertian subspace
\(F\subset L_1[0,1]\) works simultaneously for every finite \(p\).
\end{proof}

\begin{corollary}[Sharp finite-versus-infinite dichotomy]\label{cor:sharp}
For the Rademacher subspace \(F\subset L_1[0,1]\), the inclusion-induced map
\[
  \FBL{p}{F}\longrightarrow\FBL{p}{L_1[0,1]}
\]
is not order continuous for \(1\le p<\infty\), whereas it is order
continuous for \(p=\infty\).
\end{corollary}

\begin{proof}
The finite-\(p\) assertion is Theorem~\ref{thm:main}.  The
\(p=\infty\) assertion is the closed-range embedding theorem of
Azouzi--Dhifaoui \cite[Theorem~11]{AD}.
\end{proof}

\begin{remark}
The mechanism is worth emphasizing.  In the source Hilbert space, the
perturbations \(s_ne_n\) are distributed over very large coordinate blocks.
Finite-\(p\) admissible families can amplify those blocks enough to force the
only common lower bound of \((f_n)\) to be zero.  After the Rademacher
embedding into \(L_1\), finite joins of the perturbation directions have
uniformly bounded free-lattice norm.  The image sequence therefore converges
in norm to a nonzero lower bound.  This mismatch is exactly the failure of
regularity.
\end{remark}

\section{Literature status}

The relevant chronology is as follows.
\begin{itemize}
\item Oikhberg--Taylor--Tradacete--Troitsky, Theorem 3.4, asserted order
continuity for every closed subspace and every \(p\).  Its complemented
subspace argument is valid \cite{OTTT,Corr}.
\item Azouzi--Dhifaoui identified the order-density gap, proved the full
closed-range embedding result for \(p=\infty\), and stated that the other
values of \(p\) remained open \cite{AD}.
\item The corrigendum of Oikhberg--Taylor--Tradacete--Troitsky, published on
June 19, 2026, says that the proof of Theorem 3.4 works only when the
subspace is complemented and that the claim had not been used elsewhere in
the literature \cite{Corr}.
\end{itemize}

Exact-title, theorem-number, citation, and arXiv searches through June 22,
2026 did not locate a published or posted finite-\(p\) proof or counterexample.
Accordingly, the finite-\(p\) construction above should be treated as an
independent, unrefereed argument rather than as a certified novelty claim.

\begin{thebibliography}{9}

\bibitem{AD}
Y.~Azouzi and W.~Dhifaoui,
\emph{Order denseness in free Banach lattices},
arXiv:2508.11648v1, 2025.

\bibitem{ART}
A.~Avil\'es, J.~Rodr\'iguez, and P.~Tradacete,
\emph{The free Banach lattice generated by a Banach space},
J. Funct. Anal. \textbf{274} (2018), no.~10, 2955--2977.

\bibitem{JSLTT}
H.~Jard\'on-S\'anchez, N.~J. Laustsen, M.~A. Taylor, P.~Tradacete,
and V.~G. Troitsky,
\emph{Free Banach lattices under convexity conditions},
Rev. R. Acad. Cienc. Exactas F\'is. Nat. Ser. A Mat. RACSAM
\textbf{116} (2022), article 15.

\bibitem{OTTT}
T.~Oikhberg, M.~A. Taylor, P.~Tradacete, and V.~G. Troitsky,
\emph{Free Banach lattices},
J. Eur. Math. Soc. \textbf{28} (2026), no.~10, 4387--4514;
DOI 10.4171/JEMS/1552.

\bibitem{Corr}
T.~Oikhberg, M.~A. Taylor, P.~Tradacete, and V.~G. Troitsky,
\emph{Corrigendum to ``Free Banach lattices''},
J. Eur. Math. Soc. \textbf{28} (2026), no.~10, 4515--4518;
DOI 10.4171/JEMS/1802.

\end{thebibliography}

\end{document}
