\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

\newcommand{\ellq}{\ell_q}
\newcommand{\N}{\mathbb N}

\title{An Asplund Ostrovskii quojection without Banach subspaces}
\author{arXiv automatic math run \texttt{fa\_banach\_001}}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Source problem}

The source paper is J. Kakol and A. Leiderman,
\emph{Asplund locally convex spaces and the finest locally convex topology},
arXiv:2412.11510.  In Section 4, after proving their quojection criterion for
the Asplund property, they ask:

\begin{quote}
Does there exist a quojection Frechet lcs \(E\) which is Asplund not being a
countable product of Banach spaces and yet \(E\) contains no
infinite-dimensional Banach subspaces?
\end{quote}

We prove that the answer is affirmative.  In fact, Ostrovskii's original
quojection without infinite-dimensional Banach subspaces already has an
Asplund defining spectrum.

\section*{Background}

We use three standard facts about Banach-space Asplundness.

\begin{enumerate}
\item A separable Banach space is Asplund if and only if its dual is separable.
\item The class of Asplund Banach spaces is a three-space class: if \(Y\) and
      \(X/Y\) are Asplund, then \(X\) is Asplund.
\item Separability is also a three-space property for Banach spaces.
\end{enumerate}

We also use the following theorem from the source paper.

\begin{theorem}[Kakol--Leiderman]
\label{thm:KL}
Let \(E=s\hbox{-}\operatorname{proj}(E_n,P_n)\) be a quojection, i.e. a strict
projective limit of Banach spaces.  Then \(E\) is Asplund if and only if every
Banach space \(E_n\) is Asplund.
\end{theorem}

Ostrovskii's 1994 construction uses the following Bellenot--James space.  Let
\(1<q<\infty\), let \(Z\) be a separable Banach space, and let
\((Z_i)_{i=0}^\infty\) be an increasing sequence of finite-dimensional
subspaces with \(Z_0=\{0\}\) and dense union in \(Z\).  For finitely supported
sequences \(z=(z_i)\), \(z_i\in Z_i\), define
\[
2\|z\|_{J,q}^{q}
 =
\sup
\left\{
\sum_{i=1}^{k-1}\|z_{\eta(i)}-z_{\eta(i+1)}\|^{q}
 +
\|z_{\eta(k)}\|^{q}
\right\},
\]
where the supremum is taken over all finite increasing sequences
\(0\le \eta(1)<\cdots<\eta(k)\).  Let \(J(q,Z)\) denote any completion
obtained in this way.

Ostrovskii records the key identity
\[
J(q,Z)^{**}/J(q,Z)\cong Z
\]
isometrically.

\section*{The Asplund check}

\begin{lemma}
\label{lem:J-asplund}
Let \(Z\) be a separable Asplund Banach space and \(1<q<\infty\).  For every
Bellenot--James space \(X\in J(q,Z)\), both \(X\) and \(X^{**}\) are Asplund.
\end{lemma}

\begin{proof}
The space \(X\) is separable, because it is the completion of the finitely
supported sequences over a countable sequence of finite-dimensional spaces.
By Ostrovskii's quoted form of Bellenot's theorem,
\[
X^{**}/X \cong Z .
\]
Since both \(X\) and \(Z\) are separable, the middle space \(X^{**}\) is
separable by the three-space property of separability.

Now \(X^{**}\) is the dual of \(X^*\).  A Banach space whose dual is separable
is separable, hence \(X^*\) is separable.  Since \(X\) is separable with
separable dual, \(X\) is Asplund.

Finally, \(X\) is an Asplund subspace of \(X^{**}\) and
\(X^{**}/X\cong Z\) is Asplund.  By the three-space property for Asplund
Banach spaces, \(X^{**}\) is Asplund.
\end{proof}

\section*{The construction}

\begin{theorem}
\label{thm:main}
There exists a quojection Frechet locally convex space \(E\) which is Asplund,
is not isomorphic to a countable product of Banach spaces, and contains no
infinite-dimensional Banach subspace.
\end{theorem}

\begin{proof}
Choose a strictly decreasing sequence \(q(1)>q(2)>\cdots\) in \((1,\infty)\).
Ostrovskii defines Banach spaces \(F_n\) recursively as follows.  Put
\[
F_1=\ell_{q(1)}.
\]
For \(n\ge 2\), choose \(X\in J(q(n),F_{n-1})\) and set
\[
F_n=X^{**}.
\]
The quotient identity \(X^{**}/X\cong F_{n-1}\) gives a quotient map
\[
R_{n-1}:F_n\longrightarrow F_{n-1}.
\]
Thus \((F_n,R_n)\) is a projective sequence with surjective bonding maps.

Ostrovskii proves that these \(F_n\) satisfy the Metafune--Moscatelli
criterion:
\[
j\ne k
\quad\Longrightarrow\quad
F_j\text{ and }F_k\text{ have no isomorphic infinite-dimensional subspaces}.
\]
Therefore the projective limit
\[
E=\operatorname{proj}(F_n,R_n)
\]
is a twisted quojection, i.e. it is not isomorphic to a countable product of
Banach spaces, and it contains no infinite-dimensional Banach subspaces.

It remains only to check the Asplund property.  The space \(F_1=\ell_{q(1)}\)
is reflexive, hence separable Asplund.  If \(F_{n-1}\) is separable Asplund,
then Lemma~\ref{lem:J-asplund} applied to \(Z=F_{n-1}\) gives that
\(F_n=X^{**}\) is Asplund; it is also separable by the proof of the lemma.
Induction shows that every \(F_n\) is Asplund.

By Theorem~\ref{thm:KL}, the quojection \(E\) is Asplund.  This \(E\) has all
three required properties.
\end{proof}

\section*{Relation to the source paper}

The source paper already points out that Ostrovskii's mechanism would solve
the problem if the Banach spaces in the defining sequence could be chosen
Asplund.  The observation above is that no new construction is needed:
Ostrovskii's recursively defined spaces are Asplund by a short induction using
\(X^{**}/X\cong Z\), separability, and the three-space property for Asplund
Banach spaces.

\section*{Novelty and literature check}

Local run indexes were searched for arXiv:2412.11510, the source title,
Asplund spaces, finest locally convex topology, quojection, Ostrovskii, and the
exact final problem phrase.  No existing packet or attempt for this target was
found.

Web searches on 2026-06-19 for the source title, the final quojection problem,
and Ostrovskii's \emph{Quojections without Banach subspaces} found the two
papers used here, but no explicit published answer to the Asplund-strengthened
question.

\section*{References}

\begin{itemize}
\item J. Kakol and A. Leiderman, \emph{Asplund locally convex spaces and the
finest locally convex topology}, arXiv:2412.11510.
\item M. I. Ostrovskii, \emph{Quojections without Banach subspaces},
arXiv:math/9403209; Bull. Polish Acad. Sci. \textbf{44} (1996), 143--146.
\item R. Eyland and B. Sharp, \emph{A factor theorem for locally convex
differentiability spaces}, Bull. Austral. Math. Soc. \textbf{43} (1991),
101--113.
\item J. Lindenstrauss and L. Tzafriri, \emph{Classical Banach Spaces I:
Sequence Spaces}, Springer, 1977.
\end{itemize}

\section*{Human review recommendation}

The main point for review is Lemma~\ref{lem:J-asplund}.  It uses only standard
permanence facts, but it is the step not spelled out in either source paper.
The rest of the argument is exactly Ostrovskii's projective-spectrum criterion
combined with Kakol--Leiderman's quojection-Asplund theorem.

\end{document}

