\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Status Note: Symplectic Codimension-One Compact Perturbations}
\author{fa\_banach\_001 / agent\_super\_00}
\date{June 30, 2026}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_already\_answered}. This is a compact literature-status
note, not a new proof packet.

\section*{Source Question}

The source paper is J. M. F. Castillo, W. Cuellar, M. Gonzalez Ortiz, and
R. Pino, \emph{Symplectic forms on Banach spaces}, arXiv:2204.01703. In the
published numbering quoted by the later paper, the relevant source result is
Proposition 8.11. In the arXiv PDF it appears on page 20.

It states that if $\mathcal H$ is a real infinite-dimensional Hilbert space and
$\omega$ is a symplectic structure on $\mathcal H$, then there do not exist
bounded bilinear maps $\Omega$ and $\kappa$ on $X=\mathbb R\oplus\mathcal H$
such that $\kappa$ is compact, $\Omega$ extends $\omega$, and
$\Omega+\kappa$ is symplectic on $X$. Immediately after the proof, the source
asks whether this proposition holds for general Banach spaces.

\section*{Supporting Answer}

The supporting paper is H. Li and C. Zhu, \emph{Skew-adjoint linear relations
between Banach spaces}, arXiv:2404.08445. Its Introduction, page 4, explicitly
quotes the source question after Proposition 8.11 and says that the paper will
solve the problem by generalizing mod-2 kernel stability to real Banach
spaces. The relevant general stability statements are Theorems 1.3 and 1.4.

The direct answer is Corollary 1.5, page 5. It states that if $(X,\omega)$ and
$(X\oplus\mathbb R^n,\widetilde\omega)$ are real symplectic Banach spaces and
$L_{\widetilde\omega|X}-L_\omega$ is compact, then, in the strong symplectic
case, $n$ must be even. Setting $n=1$ rules out the codimension-one compact
perturbation scenario in the source question.

\section*{Conclusion and Scope}

The source question is already answered in the later literature. Proposition
8.11 does extend to general Banach spaces in the strong symplectic setting:
a strong real symplectic Banach space cannot become a codimension-one strong
real symplectic Banach extension by a compact perturbation of the restricted
symplectic operator. The supporting paper proves a stronger parity theorem for
skew-adjoint Fredholm relations; this packet records the explicit source-to-
supporting-paper identification.

\section*{Local Evidence}

The packet contains the original arXiv PDF as \texttt{source\_paper.pdf} and
the supporting answer as \texttt{supporting\_paper\_2404.08445.pdf}. Cheap
run-index search for the arXiv id, title keywords, symplectic Banach spaces,
Proposition 8.11, and compact perturbation found no prior solution packet for
this source target.

\begin{thebibliography}{9}

\bibitem{CCGP}
J. M. F. Castillo, W. Cuellar, M. Gonzalez Ortiz, and R. Pino,
\emph{Symplectic forms on Banach spaces}, arXiv:2204.01703.

\bibitem{LZ}
H. Li and C. Zhu,
\emph{Skew-adjoint linear relations between Banach spaces}, arXiv:2404.08445.

\end{thebibliography}

\end{document}
