\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}

\title{Literature status note for arXiv:1508.01961}
\author{agent\_lane\_12}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet.  It records that one
open question quoted in Braga's paper is already answered negatively
in later literature, and that a second Borelness clause is also
answered negatively.  It does not claim a new proof.

\section*{Source questions}

Braga's Introduction asks the Bossard question:
\[
\text{If } X\in \mathrm{SB} \text{ has Borel isomorphism class }
\langle X\rangle,\text{ must }X\cong \ell_2?
\]
The source identifies this as Bossard, Problem 2.9.

In the subsection on unconditional bases, the source also asks whether
\(\mathrm{UB}\), the class of separable Banach spaces with an
unconditional basis, is Borel or complete analytic, and asks analogous
questions for
\[
S=\{X\in\mathrm{SB}:X\text{ has a Schauder basis}\}.
\]

\section*{Answer identification}

Kurka's later paper \emph{The isomorphism class of \(c_0\) is not
Borel}, arXiv:1711.03328, explicitly says in its Introduction that
Bossard's question had been answered negatively, citing Godefroy's
Theorem 6.2.  The same paragraph records that the isomorphism classes
of \(\ell_p\), \(1<p<\infty\), are Borel.  Thus taking any
\(p\ne 2\) gives a separable Banach space not isomorphic to \(\ell_2\)
whose isomorphism class is Borel.  This is a negative literature
answer to the source question.

Kurka's Theorem 3 further states that the class of spaces with an
unconditional basis is analytic but not Borel.  Therefore the source
question ``Is \(\mathrm{UB}\) Borel?'' is answered negatively in the
same supporting paper.

\section*{Scope limitations}

This packet does not settle the exact descriptive complexity of all
remaining classes in Braga's table.  In particular, it does not answer
whether \(\mathrm{UB}\) is complete analytic, and it does not answer
whether the class \(S\) of spaces with a Schauder basis is Borel or
complete analytic.  Kurka explicitly notes that the Borelness of the
Schauder-basis class was not known at the time of that paper.

\section*{References}

\begin{thebibliography}{9}

\bibitem{Braga}
B. de Mendonca Braga,
\emph{On the complexity of some inevitable classes of separable Banach spaces},
arXiv:1508.01961.

\bibitem{Kurka}
O. Kurka,
\emph{The isomorphism class of \(c_0\) is not Borel},
arXiv:1711.03328; Israel J. Math. 231 (2019), 243--268.

\bibitem{GodefroySome}
G. Godefroy,
\emph{The complexity of the isomorphism class of some Banach spaces},
J. Nonlinear Convex Anal. 18 (2017), no. 2, 231--240.

\bibitem{GodefroyLp}
G. Godefroy,
\emph{The isomorphism classes of \(\ell_p\) are Borel},
Houston J. Math. 43 (2017), no. 3, 947--951.

\end{thebibliography}

\end{document}
