\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Theorem}

\title{Literature-Implied Partial Answer to Yun's \(L_r\)-to-\(L_s\) Question}
\author{FA/Banach run packet}
\date{June 16, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{Result type:} literature implied answer (partial subcase).

\textbf{Source question:} Longyun Ding, \emph{Borel reducibility and
H\"older\((\alpha)\) embeddability between Banach spaces}, arXiv:0912.1912,
Section 7.

\textbf{Supporting theorem:} Assaf Naor, \emph{Discrete Riesz transforms and
sharp metric \(X_p\) inequalities}, arXiv:1601.03332.

\section*{Source Question}

In the final remarks of arXiv:0912.1912, after noting that little is known for
\(r\ge 2\), Yun asks:
\[
\text{For } r,s\ge 2,\ r\le s,\text{ does } L_r \text{ finitely Lipschitz
embed into } L_s?
\]
The same displayed question also asks whether this would imply, or accompany,
\[
E(L_r,p)\le_B E(L_s,p).
\]

\section*{Identification}

Yun proves earlier in the same paper that, for Banach spaces \(X,U\) and
\(\alpha>0\), \(X\) finitely H\"older\((\alpha)\)-embeds into \(U\) if and only
if \(X\) H\"older\((\alpha)\)-embeds into an ultrapower \((U)_{\mathcal U}\).

Naor proves sharp metric \(X_p\) inequalities. One consequence, stated in the
abstract of arXiv:1601.03332, is that for \(2<q<p<\infty\), the maximal
\(\theta\in(0,1]\) for which \(L_q\) admits a bi-\(\theta\)-H\"older embedding
into \(L_p\) is exactly \(q/p\). In particular, no bi-Lipschitz embedding
\(L_q\to L_p\) exists when \(2<q<p<\infty\).

\section*{Formal Consequence}

\begin{theorem}
For \(2<r<s<\infty\), \(L_r\) does not finitely Lipschitz embed into \(L_s\).
Consequently, the finite-Lipschitz part of Yun's Section 7 question has a
negative answer in the strict super-Hilbertian range.
\end{theorem}

\begin{proof}
Suppose that \(L_r\) finitely Lipschitz embeds into \(L_s\) for some
\(2<r<s<\infty\). By Yun's ultraproduct characterization with \(\alpha=1\),
there is a bi-Lipschitz embedding
\[
L_r \longrightarrow (L_s)_{\mathcal U}
\]
for a free ultrafilter \(\mathcal U\).

An ultrapower of an \(L_s\)-space is again an abstract \(L_s\)-space. Naor's
sharp \(X_p\) inequality applies to \(L_s\)-spaces and bounds the possible
bi-H\"older exponent of an embedding of \(L_r\) into such a target by \(r/s\).
Since \(r/s<1\), exponent \(1\) is impossible. This contradicts the
bi-Lipschitz embedding above.
\end{proof}

\section*{Scope and Remaining Questions}

This is not a full answer to Yun's final questions. The endpoint \(r=s\) is
trivial, and the Hilbertian source case \(r=2\) is outside the negative
argument. The packet does not settle the Borel reducibility assertion
\(E(L_r,p)\le_B E(L_s,p)\), nor Yun's separate question about finite
H\"older\((p/q)\) self-embeddings of \(L_r\) and \(E(L_r,p)\le_B E(L_r,q)\).

The supporting paper does not explicitly cite Yun's question; this is an
agent-identified implication, so the packet belongs under
\texttt{literature\_implied\_answers/}, not
\texttt{literature\_already\_answered/}.

\section*{Verification}

Stored files:
\[
\texttt{source\_paper.pdf},\qquad
\texttt{supporting\_paper\_1601.03332.pdf}.
\]
Cheap-index search before packaging found no exact prior packet for
arXiv:0912.1912. Local corpus and web searches for the exact \(E(L_r,p)\),
\(E(\ell_r,p)\), finite Lipschitz, and H\"older-embeddability phrases found no
existing run packet for this target. The decisive later theorem was identified
through the metric \(X_p\) / snowflake literature.

\begin{thebibliography}{9}

\bibitem{Yun2009}
L. Yun,
\emph{Borel reducibility and H\"older\((\alpha)\) embeddability between Banach
spaces},
arXiv:0912.1912.
\url{https://arxiv.org/abs/0912.1912}

\bibitem{Naor2016}
A. Naor,
\emph{Discrete Riesz transforms and sharp metric \(X_p\) inequalities},
Ann. of Math. (2) 184 (2016), no. 3, 991--1016;
arXiv:1601.03332.
\url{https://arxiv.org/abs/1601.03332}

\end{thebibliography}

\end{document}
