\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\begin{center}
{\Large Literature-implied partial answer to a point-finite ball covering question}

\vspace{0.4em}
{\large Source arXiv:1212.2817; supporting arXiv:2007.05242}
\end{center}

\section*{Source question}

Fonf, Levin, and Zanco, \emph{Covering \(L^p\) spaces by balls}
(arXiv:1212.2817), ask in Question 1.1:
\begin{quote}
\emph{Which infinite-dimensional Banach spaces admit point-finite coverings by
balls, each of positive radius?}
\end{quote}
Their main theorem gives a negative answer for separable infinite-dimensional
Banach spaces that are both uniformly rotund and uniformly smooth; in
particular, for separable infinite-dimensional \(L^p(\mu)\), \(1<p<\infty\).

\section*{Supporting theorem}

De Bernardi, \emph{A note on point-finite coverings by balls}
(arXiv:2007.05242), explicitly cites the Fonf--Levin--Zanco paper and states
that Klee's problem about point-finite coverings by balls of
\(\ell_p(\Gamma)\), \(1<p<\infty\), remained open in the nonseparable case.
Theorem 3.6 of that paper proves the following strengthened negative result:
if \(X\) is infinite-dimensional, uniformly rotund and uniformly smooth, and
\[
\operatorname{dens}(X)<2^{\aleph_0},
\]
then \(X\) admits no point-finite covering by open or closed balls, each of
positive radius.  The same theorem also proves that any cover of such an
\(X\) by open balls is not point-finite.

\section*{Status}

This is a literature-implied partial answer to Question 1.1 of arXiv:1212.2817.
It extends the source paper's separable uniformly rotund/smooth obstruction to
all density-below-continuum uniformly rotund/smooth spaces.  It does not solve
the full classification problem: arXiv:2007.05242 explicitly leaves open
whether the density restriction can be removed, even for Hilbert spaces.

\section*{Search evidence}

The local run indexes had no existing packet for arXiv:1212.2817.  Web search
for the exact source question and for ``point-finite coverings by balls''
returned arXiv:2007.05242 as the direct later development, and the parsed
source of arXiv:2007.05242 contains the explicit citations and theorem stated
above.

\section*{References}

V. P. Fonf, M. Levin, and C. Zanco, \emph{Covering \(L^p\) spaces by balls},
arXiv:1212.2817.

C. A. De Bernardi, \emph{A note on point-finite coverings by balls},
arXiv:2007.05242.

\end{document}
