\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\begin{document}

\begin{center}
{\Large A scalar-valued positive subcase of the Akemann--Shell--Weaver projection problem}
\end{center}

\paragraph{Source.}
The source paper is C.~A.~Akemann, G.~C.~Shell, and N.~Weaver,
\emph{Locally nonconical convexity}, arXiv:0005194.  Near the end of
Section 4 the authors ask:
\[
\begin{gathered}
\text{Let } Q \text{ be a closed, bounded, strictly convex subset of a Hilbert space } X\\
\text{and let } T:X\to\mathbb R^n \text{ be a bounded linear map.}\\
\text{Is } T|_Q:Q\to T(Q) \text{ necessarily open?}
\end{gathered}
\]
The following proves the scalar case \(n=1\).  The proof does not use
closedness, strict convexity, or the Hilbert structure.

\begin{theorem}
Let \(Q\) be a bounded convex subset of a normed linear space \(X\), and let
\(T:X\to\mathbb R\) be a linear map.  Then the restriction
\[
        f=T|_Q:Q\longrightarrow T(Q)
\]
is open, where \(Q\) and \(T(Q)\) carry their relative norm topologies.
\end{theorem}

\begin{proof}
Fix \(q\in Q\) and put \(y=Tq\).  Let \(U\) be a relative neighborhood of
\(q\) in \(Q\).  It is enough to consider neighborhoods of the form
\[
        U_\varepsilon=Q\cap B(q,\varepsilon).
\]
Since \(Q\) is bounded, choose \(D>0\) such that
\(\|x-q\|\le D\) for every \(x\in Q\).  Fix
\(\alpha\in(0,1]\) with \(\alpha D<\varepsilon\).

For every \(x\in Q\), convexity gives
\[
        q+\alpha(x-q)=(1-\alpha)q+\alpha x\in Q
\]
and the norm estimate gives this point in \(U_\varepsilon\).  Applying \(T\)
therefore yields
\[
        (1-\alpha)y+\alpha T(Q)\subseteq T(U_\varepsilon).
\]
The set \(T(Q)\) is a convex subset of \(\mathbb R\), hence an interval
possibly open, closed, half-open, degenerate, or unbounded only if \(Q\) is
unbounded.  Because \(Q\) is bounded, this interval is bounded.  For every
point \(y\) of an interval \(I\), the homothetic interval
\((1-\alpha)y+\alpha I\) is a relative neighborhood of \(y\) in \(I\):
if \(y\) is an endpoint it contains a one-sided relative interval, if \(y\)
is interior it contains a two-sided interval, and if \(I=\{y\}\) this is
trivial.  Thus \(T(U_\varepsilon)\) is a relative neighborhood of \(y\) in
\(T(Q)\).  Since \(q\) and \(\varepsilon\) were arbitrary, \(f\) is open.
\end{proof}

\begin{corollary}
The Akemann--Shell--Weaver open problem has an affirmative answer when
\(n=1\).  In this scalar case the hypotheses that \(Q\) be closed, strictly
convex, and Hilbert-space-valued are unnecessary; bounded convexity is
sufficient.
\end{corollary}

\begin{remark}[Finite-dimensional reduction]
The same first paragraph proves a useful local criterion for arbitrary
finite-dimensional targets.  Let \(C=T(Q)\), \(y=Tq\), and
\(\varepsilon>0\).  If \(D=\sup_{x\in Q}\|x-q\|\) and
\(\alpha D<\varepsilon\), then
\[
        (1-\alpha)y+\alpha C\subseteq T(Q\cap B(q,\varepsilon)).
\]
Consequently \(T|_Q\) is open at \(q\) whenever, for some such
\(\alpha>0\), the homothetic copy \((1-\alpha)y+\alpha C\) is a relative
neighborhood of \(y\) in \(C\).  In particular the remaining obstruction for
\(n\ge2\) can only occur at image points where \(T(Q)\) has a genuinely
non-conical local boundary, such as a cusp.
\end{remark}

\paragraph{Bounded novelty check.}
The run indexes were searched for arXiv id \(0005194\), for the exact
phrases ``closed, bounded, strictly convex'', ``\(T|_Q\)'', and
``cofinite-dimensional kernel'', and for title/author keywords from the
source paper.  No prior run packet or attempt was found for this target.
A bounded local parsed-source search and exact-phrase web search found the
source problem but no separate later explicit answer.  This packet therefore
records a partial positive subcase, not a claimed full answer to the
\(n\ge2\) problem.

\end{document}
