\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Two Answered Problems from\\
\emph{J-class operators and hypercyclicity}}
\author{Run fa\_banach\_001, agent\_lane\_06}
\date{June 28, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet for two specific questions from
Costakis--Manoussos, \emph{J-class operators and hypercyclicity},
arXiv:0704.3354 \cite{CM}.  It does not settle all five open problems in the
source paper.

\section*{Source Questions}

In Section 6, page 19 of the source PDF, the authors ask:

\begin{quote}
\textbf{Problem 2.} Does every non-separable and infinite dimensional Banach
space support a \(J\)-class operator?
\end{quote}

They then ask:

\begin{quote}
\textbf{Problem 3.} Is there a spectral description of the closure of the set of
\(J\)-class operators acting on a Hilbert space?
\end{quote}

\section*{Supporting Answer to Problem 2}

Nasseri, \emph{On the existence of J-class operators on Banach spaces},
arXiv:1009.3461 \cite{Nasseri}, explicitly answers the Costakis--Manoussos
non-separable-space question in the negative.  The abstract states that the paper
answers the question negatively, and Theorem 1.1 states that there exists a
non-separable complex Banach space \(X\) on which the \(J\)-set of every operator
has empty interior for every nonzero vector.  Consequently \(X\) supports no
\(J\)-class operator.

This is a direct negative answer to Problem 2.

\section*{Supporting Answer to Problem 3}

Tian--Hou, \emph{Limits of J-class operators}, arXiv:1010.3386 \cite{TH},
explicitly addresses the third Costakis--Manoussos problem.  Its abstract says
that it gives the spectral description of the closure of the set of
\(J\)-class operators on a separable Hilbert space.  In Section 1 it repeats the
question, and Theorem 2.10 gives the announced formula:
\[
\begin{aligned}
\overline{J(H)}=\{T\in B(H):\;&
[\sigma_{\mathrm{lre}}(T)\cup\rho^{(+)}_{\mathrm{s-F}}(T)]
      \cap\partial\mathbb D\neq\varnothing,\\
&\overline{\mathbb D}\cap\rho^{(-)}_{\mathrm{s-F}}(T)=\varnothing,\\
&\text{no component of }\sigma(T)\text{ is contained in }\mathbb D\}.
\end{aligned}
\]

This is a direct literature answer to Problem 3.

\section*{Scope Limitations}

Problems 1, 4, and 5 from the same source open-problems section are not answered
by this packet.  A bounded direct attack checked the natural direct-sum route for
Problem 4, but individual hypercyclicity of summands is not enough because
\(J\)-sets of direct sums require common return times.  No promoted proof or
counterexample was obtained for Problems 1, 4, or 5.

\section*{Search Notes}

The run indexes had no exact packet for arXiv:0704.3354.  They did contain a
nearby triage entry for arXiv:1009.3461, recording that Nasseri answers the
non-separable \(J\)-class existence question in the negative.  Local source search
also found arXiv:1010.3386, whose abstract and introduction explicitly identify
Problem 3 from Costakis--Manoussos and whose Theorem 2.10 supplies the spectral
description.

\begin{thebibliography}{9}
\bibitem{CM}
G. Costakis and A. Manoussos, \emph{J-class operators and hypercyclicity},
arXiv:0704.3354.

\bibitem{Nasseri}
A. B. Nasseri, \emph{On the existence of J-class operators on Banach spaces},
arXiv:1009.3461.

\bibitem{TH}
G. Tian and B. Hou, \emph{Limits of J-class operators}, arXiv:1010.3386.
\end{thebibliography}

\end{document}
