\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Literature Answer}

\title{Literature Answer to the Continuous-Parameter Besov Katznelson--Tzafriri Question from arXiv:2204.13411}
\author{FA/Banach run packet}
\date{2026-06-21}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet. It records that the
continuous-parameter Besov-calculus question noted in Batty--Seifert
\cite{BSsurvey} is answered by the companion/later paper
Batty--Seifert \cite{BScontinuous}. It is not an original proof from this run.

\section*{Original Source Signal}

In Section 5.1 of \cite{BSsurvey}, after discussing the analytic Besov algebra
\(\mathcal B(\mathbb C_+)\) and the corresponding calculus for negative
generators of bounded \(C_0\)-semigroups, the authors write that the results in
the discrete Besov section are analogous to the semigroup Besov-calculus
results except for Theorem 2.7. They then state that one can formulate a
continuous-parameter version of that theorem, but that they had not determined
whether it is true.

The discrete theorem in question says that if \(T\) is power-bounded, has a
bounded \(\mathcal B(\mathbb D)\)-calculus, and \(f\in \mathcal B(\mathbb D)\)
vanishes on \(\sigma(T)\cap\mathbb T\), then
\[
  \lim_{n\to\infty}\|T^n f(T)\|=0.
\]

\section*{Supporting Answer}

The paper \cite{BScontinuous} has exactly the title
\emph{A continuous-parameter Katznelson--Tzafriri theorem for algebras of
analytic functions}. Its abstract states that it proves a continuous-parameter
version of the recent Besov-calculus Katznelson--Tzafriri theorem for
power-bounded operators. Its introduction cites the survey \cite{BSsurvey} and
says that the authors subsequently proved the corresponding
continuous-parameter result.

The principal Besov statement is Theorem 1.2 of \cite{BScontinuous}:

\begin{theorem}
Let \(-A\) be the generator of a bounded \(C_0\)-semigroup \((T(t))_{t\ge 0}\)
on a Banach space and suppose that \(A\) has a bounded
\(\mathcal B(\mathbb C_+)\)-calculus. If \(f\in \mathcal B(\mathbb C_+)\)
vanishes on \(\sigma(A)\cap i\mathbb R\) and
\[
  \lim_{\substack{z\in \mathbb C_+\\ |z|\to\infty}} f(z)=0,
\]
then
\[
  \lim_{t\to\infty}\|T(t)f(A)\|=0.
\]
\end{theorem}

Theorem 2.1 of \cite{BScontinuous} gives a larger-algebra version: if
\(\mathcal A\) is a Banach algebra with
\(\mathcal B(\mathbb C_+)\subseteq \mathcal A\subseteq H^\infty(\mathbb C_+)\),
\(-A\) generates a bounded \(C_0\)-semigroup and has a bounded
\(\mathcal A\)-calculus, and \(f\) lies in the closure of Laplace transforms in
\(\mathcal A\) while vanishing on \(\sigma(A)\cap i\mathbb R\), then the same
operator-norm decay follows.

\section*{Scope and Identification}

This answers the exact unresolved continuous-parameter analogue signalled in
\cite{BSsurvey}. The vanishing-at-infinity hypothesis in Theorem 1.2 is part of
the correct continuous-parameter formulation for unbounded generators; the
supporting paper explains that without it constant functions would give
counterexamples when the semigroup is bounded but not exponentially stable.

The answer source is separate from the survey source. It also explicitly knows
the surrounding problem context: it cites the survey as \cite{BSsurvey}, cites
the discrete Besov theorem as \cite{BSdiscrete}, and states that it proves the
corresponding continuous-parameter theorem.

\section*{Verification Notes}

Local source inspection used:
\begin{itemize}
\item \texttt{data/parsed/arxiv\_sources/2204.13411/source.tex}, lines
701--704, for the source signal.
\item \texttt{data/parsed/arxiv\_sources/2204.13416/source.tex}, lines
129--130 and 155--166, for the abstract/intro match and Theorem 1.2.
\item \texttt{data/parsed/arxiv\_sources/2204.13416/source.tex}, lines
210--214 and 335--341, for the larger-algebra theorem and its proof conclusion.
\end{itemize}
Web search for the exact supporting title also returned arXiv:2204.13416 with
the same abstract. No local registry row for this exact target existed before
this packet.

\begin{thebibliography}{9}

\bibitem{BSsurvey}
C. Batty and D. Seifert,
\emph{Some developments around the Katznelson--Tzafriri theorem},
arXiv:2204.13411; Acta Sci. Math. (Szeged) 88 (2022), 53--84.

\bibitem{BScontinuous}
C. Batty and D. Seifert,
\emph{A continuous-parameter Katznelson--Tzafriri theorem for algebras of
analytic functions},
arXiv:2204.13416; Studia Math. 270 (2023), 229--239.

\bibitem{BSdiscrete}
C. Batty and D. Seifert,
\emph{A Katznelson--Tzafriri theorem for analytic Besov functions of
operators},
arXiv:2201.12076.

\end{thebibliography}

\end{document}
