\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Discrete Supports for fsJN-Sequences}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \textbf{literature\_already\_answered} packet.  It records that a
later paper explicitly answers one of the open questions extracted from
arXiv:2009.07552.  It is not a new proof packet.

\section*{Source Question}

The source paper is:

\begin{quote}
Jerzy K\k{a}kol, Damian Sobota, and Lyubomyr Zdomskyy,
\emph{The Josefson--Nissenzweig theorem, Grothendieck property, and finitely
supported measures on compact spaces}, arXiv:2009.07552.
\end{quote}

In Question 4.23, on page 24 of the source PDF, the authors ask:

\begin{quote}
Does every space \(X\) with the fsJNP admit an fsJN-sequence
\(\langle\mu_n:n\in\omega\rangle\) such that
\(\bigcup_n \operatorname{supp}(\mu_n)\) is a discrete subspace of \(X\)?
\end{quote}

Here fsJNP means the finitely supported Josefson--Nissenzweig property, and an
fsJN-sequence is a weak-star null normalized sequence of finitely supported
measures.

\section*{Supporting Answer}

The supporting paper is:

\begin{quote}
Witold Marciszewski, Damian Sobota, and Lyubomyr Zdomskyy,
\emph{On sequences of finitely supported measures related to the
Josefson--Nissenzweig theorem}, arXiv:2303.03809.
\end{quote}

Theorem 1.2 of the supporting paper, on page 2, states that if a Tychonoff
space \(X\) carries a finitely supported JN-sequence
\(\langle\mu_n:n\in\omega\rangle\), then there exists a finitely supported
JN-sequence \(\langle\nu_n:n\in\omega\rangle\) on \(X\) such that:
\[
  \bigcup_{n\in\omega}\operatorname{supp}(\nu_n)
  \subseteq
  \bigcup_{n\in\omega}\operatorname{supp}(\mu_n),
\]
\[
  \operatorname{supp}(\nu_n)\cap\operatorname{supp}(\nu_k)=\varnothing
  \quad(n\neq k),
\]
and
\[
  \bigcup_{n\in\omega}\operatorname{supp}(\nu_n)
  \text{ is a discrete subset of }X.
\]

The proof is given by combining Theorem 4.3, which produces disjoint supports,
with Theorem 5.4, which refines a disjointly supported sequence so that the
union of supports is discrete.

\section*{Identification}

The source question asks for exactly the existence of an fsJN-sequence with
discrete union of supports under the hypothesis that \(X\) has the fsJNP.
Theorem 1.2 of arXiv:2303.03809 proves this for every Tychonoff space \(X\),
and hence gives a positive answer to Question 4.23 of arXiv:2009.07552.

The supporting arXiv record also notes substantial text overlap with
arXiv:2009.07552, and two of the three supporting authors are coauthors of the
source paper, so this is best classified as an already-known later answer
rather than as a newly discovered proof.

\section*{Scope Limitations}

This packet answers only the discrete-support question, Question 4.23, from
the source paper.  It does not address the source paper's questions about
Boolean subalgebras with the \(\ell_1\)-Grothendieck property, long
\(\tau\)-simple extension systems, or de la Vega systems.

\section*{Search Evidence}

Local cheap indexes for arXiv:2009.07552, fsJNP, finitely supported
Josefson--Nissenzweig sequences, discrete supports, and the Grothendieck
keywords had no prior exact packet at reservation time.  External search on
2026-06-14 for the exact phrase around ``fsJNP'' and ``discrete subspace''
returned arXiv:2303.03809 as the direct answer source.

\begin{thebibliography}{9}

\bibitem{KSZ2009}
J. K\k{a}kol, D. Sobota, and L. Zdomskyy,
\emph{The Josefson--Nissenzweig theorem, Grothendieck property, and finitely
supported measures on compact spaces}, arXiv:2009.07552.

\bibitem{MSZ2303}
W. Marciszewski, D. Sobota, and L. Zdomskyy,
\emph{On sequences of finitely supported measures related to the
Josefson--Nissenzweig theorem}, arXiv:2303.03809.

\end{thebibliography}

\end{document}
