\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature Status Note: Uniform Algebras and the Complex Mazur--Ulam Property}
\author{fa\_banach\_001 / agent\_lane\_07}
\date{June 20, 2026}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{literature\_implied\_answer (partial subcase).}
The complex-target reading of the uniform-algebra Mazur--Ulam conjecture in
arXiv:2101.01994 is answered positively by the later paper arXiv:2107.01515.
The full real-target Mazur--Ulam property remains open in the supporting paper.

\paragraph{Original source.}
O. Hatori, S. Oi, and R. Shindo Togashi,
\emph{Tingley's problems on uniform algebras}, arXiv:2101.01994.
The source proves that a surjective isometry between the unit spheres of two
uniform algebras extends to a surjective real-linear isometry.  In Section 8
(``Remarks''), the authors then conjecture that a uniform algebra satisfies the
Mazur--Ulam property, meaning that the target should be allowed to be an
arbitrary Banach space rather than another uniform algebra.

\paragraph{Supporting source.}
O. Hatori, \emph{The Mazur--Ulam property for uniform algebras},
arXiv:2107.01515.
The introduction explicitly recalls the arXiv:2101.01994 theorem and states
that the new paper proves the complex Mazur--Ulam property for uniform
algebras.  The decisive statement is Theorem 4.2: every uniform algebra
satisfies the complex Mazur--Ulam property.  Equivalently, if \(A\) is a
uniform algebra and \(T:S(A)\to S(E)\) is a surjective isometry onto the unit
sphere of an arbitrary complex Banach space \(E\), then the homogeneous
extension of \(T\) is a surjective real-linear isometry \(A\to E\).

\paragraph{Identification.}
This is an implication rather than a same-paper answer.  The original paper
asked for the Mazur--Ulam property after proving the uniform-algebra-to-uniform-
algebra Tingley theorem.  The later paper proves exactly the arbitrary-complex-
target version.  Thus the natural complex Banach-space form of the conjecture
is settled positively in the literature.

\paragraph{Remaining scope.}
The later paper does not claim the full real-target Mazur--Ulam property.
Indeed its final remarks say that it merely proves the complex Mazur--Ulam
property and still conjectures the Mazur--Ulam property for uniform algebras,
more generally for closed subalgebras of \(C_0(Y,\mathbb C)\).

There is also a visible reason the same proof does not directly cover the real
form of a complex uniform algebra.  In Hatori's real-space sufficient condition
one needs
\[
  M_{p,\alpha}=\{a\in S(B):p(a)=\alpha\}
\]
for real face representatives \(p\) and all \(-1\leq\alpha\leq 1\).  For the
real Banach space underlying a complex uniform algebra, the natural real face
functionals are \(p=\operatorname{Re}(\gamma\delta_x)\).  Taking \(p=\operatorname{Re}\delta_x\)
and a sphere element \(f\) with \(f(x)=i\), one has \(p(f)=0\), but
\[
  \operatorname{dist}(f,\{g\in S(A):g(x)=1\})\geq |i-1|=\sqrt2>1.
\]
Hence \(f\notin M_{p,0}\).  The real criterion in arXiv:2107.01515 therefore
does not automatically settle the remaining real-target conjecture.

\paragraph{Evidence checked.}
Local arXiv sources and PDFs were checked for arXiv:2101.01994 and
arXiv:2107.01515.  Cheap run indexes showed no prior exact packet for
arXiv:2101.01994.  Web search for the source title together with
``Mazur--Ulam property'' led to arXiv:2107.01515, whose title and theorem
statements match the complex-target subcase.

\end{document}

