\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature-Implied Partial Subcase for arXiv:0902.3422}
\author{fa\_banach\_001 lane 3}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature\_implied\_answer (partial subcase).

This note records a known-literature implication answering only the unconditional-basis subcase of a question from Lopez Perez~\cite{Lopez2009}. It is not a full answer to the unrestricted question.

\section*{Source Question}

The source is arXiv:0902.3422, ``Banach spaces with many boundedly complete basic sequences failing PCP'' by Gines Lopez Perez~\cite{Lopez2009}. Remark 2.7(iii), page 8 of the arXiv PDF, asks whether a Banach space must satisfy the convex point of continuity property (CPCP) whenever every semi-normalized basic sequence has a boundedly complete subsequence.

\section*{Supporting Literature}

The supporting source is arXiv:2302.11287, ``Fixed point property, unconditional basis and Banach spaces containing no copies of \(c_0\)'' by Cleon S. Barroso~\cite{Barroso2023}. Remark 4.15, page 11 of the arXiv PDF, records that if a Banach space \(X\) has an unconditional basis and fails CPCP, then \(X\) contains a \(c_0\)-sequence; the remark cites Schachermayer~\cite[Corollary 2.11]{Schachermayer1987}.

\section*{Identification}

Let \(X\) be a Banach space with an unconditional basis and suppose every semi-normalized basic sequence in \(X\) has a boundedly complete subsequence. If \(X\) failed CPCP, the implication recorded in Barroso's Remark 4.15 would give a basic sequence in \(X\) equivalent to the unit vector basis of \(c_0\). No subsequence of the \(c_0\) basis is boundedly complete: the scalar choice \(a_n=1\) has uniformly bounded partial sums in \(c_0\) but the series does not converge in norm. This contradicts the source sequential property. Hence \(X\) satisfies CPCP.

\section*{Scope and Search Notes}

This answers only the unconditional-basis subcase of the source question. The unrestricted implication remains open from this packet's bounded pass: the local run indexes had no exact prior entry for arXiv:0902.3422; local source search found the same source question and nearby CPCP/bounded-completeness material, including Barroso's Remark 4.15; web searches for exact phrases such as ``boundedly complete subsequence'' with ``convex point of continuity property'' did not reveal a full published answer.

\section*{References}

\begin{thebibliography}{9}

\bibitem{Lopez2009}
G. Lopez Perez,
\emph{Banach spaces with many boundedly complete basic sequences failing PCP},
arXiv:0902.3422, 2009.

\bibitem{Barroso2023}
C. S. Barroso,
\emph{Fixed point property, unconditional basis and Banach spaces containing no copies of \(c_0\)},
arXiv:2302.11287, 2023.

\bibitem{Schachermayer1987}
W. Schachermayer,
\emph{The Radon-Nikodym property and Krein-Milman property are equivalent for strongly regular sets},
Transactions of the American Mathematical Society 303 (1987), 673--687.

\end{thebibliography}

\end{document}
