\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newcommand{\F}{\mathcal F}
\newcommand{\N}{\mathbb N}

\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}

\title{A literature-implied negative answer for the BAP clause in Cuth--Doucha's totally disconnected question}
\author{fa\_banach\_001, lane 19}
\date{June 20, 2026}

\begin{document}
\maketitle

\section*{Source question}

Cuth and Doucha ask at the end of \emph{Lipschitz-free spaces over
ultrametric spaces} \cite{cuth-doucha}:
\begin{quote}
Does the Lipschitz-free space over a totally disconnected compact metric space
have the BAP? Is it a dual space?
\end{quote}
This note records that the first clause has a negative answer by a later
Cantor-metric theorem of Talimdjioski \cite{talimdjioski}.

\section*{Supporting literature theorem}

Let \(K=2^\N\) be the Cantor set and let \(\mathcal M\) be the space of all
metrics on \(K\) which induce the usual product topology. Talimdjioski defines
\[
\mathcal A_f=\{d\in\mathcal M:\F(K,d)\text{ fails the approximation property}\}.
\]
The theorem labeled \texttt{afmeagerdense} in \cite{talimdjioski} states that
\(\mathcal A_f\) is dense and meager in \(\mathcal M\). In particular,
\(\mathcal A_f\neq\varnothing\).

\section*{Consequence for the source question}

\begin{corollary}
There exists a totally disconnected compact metric space \(M\) such that
\(\F(M)\) does not have the bounded approximation property.
\end{corollary}

\begin{proof}
Choose \(d\in\mathcal A_f\). Then \(M=(K,d)\) is compact and totally
disconnected, since \(d\) induces the usual Cantor topology. By the definition
of \(\mathcal A_f\), the Lipschitz-free space \(\F(K,d)\) fails the
approximation property. Since BAP implies AP for Banach spaces, \(\F(K,d)\)
cannot have BAP.
\end{proof}

\section*{Scope}

This answers the BAP clause of the Cuth--Doucha/Godefroy question negatively.
It does not settle the separate clause asking whether every free space over a
totally disconnected compact metric space is a dual space. Indeed,
\cite[Corollary labeled \texttt{cor:dualmapresidual}]{talimdjioski} proves a
residual set of compatible Cantor metrics for which \(\F(K,d)\) is the dual of
\(\operatorname{lip}_0(K,d)\) and both spaces have MAP. Thus the later paper
contains both positive generic information and negative existence information;
the latter is the part used here.

\begin{thebibliography}{9}

\bibitem{cuth-doucha}
M. Cuth and M. Doucha,
\emph{Lipschitz-free spaces over ultrametric spaces},
arXiv:1411.2434.

\bibitem{talimdjioski}
F. Talimdjioski,
\emph{Lipschitz-free spaces over Cantor sets and approximation properties},
arXiv:2305.07591.

\end{thebibliography}

\end{document}
