\documentclass[11pt]{article}
\usepackage[margin=0.78in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}

\title{Literature Status: Sharp CHS-to-Operator Lower Constant}
\author{Run \texttt{fa\_banach\_001}}
\date{19 July 2026}

\begin{document}
\maketitle
\small

\textbf{Status.} \texttt{literature\_already\_answered}.

\textbf{Source question.} Bouthat, Ch\'avez, and Garcia,
\emph{Hunter's positivity theorem and random vector norms},
arXiv:2403.10314, Problem~5 on PDF page~59, asks: ``Find a sharp lower
bound in Theorem~10.5.'' For even $d$, that theorem concerns Hermitian
matrices and
\[
  \|A\|_d^d=h_d(\lambda_1(A),\ldots,\lambda_n(A)),
  \qquad \|A\|_{\mathrm{op}}=\max_i|\lambda_i(A)|.
\]

\textbf{Supporting answer.} Brazitikos and Pandis,
\emph{Sharp inequalities for symmetric polynomials, Hunter's conjecture,
and moments of exponential random variables}, arXiv:2512.12254, Section~6,
Theorem~6.1, Lemmas~6.2--6.3, and Corollary~6.4 (starting on PDF page~37),
compute the exact minimum of $h_{2k}$ on the $\ell_\infty$-sphere. Their
introduction (PDF page~5) explicitly states that Section~6 answers the sharp
matrix-norm lower-constant question.

\textbf{Identification.} Let $d=2k$, $n\ge2$, and let $\tau_{n,k}\in(-1,0)$
be the unique root of
\[
  h_{2k-1}(\underbrace{\tau_{n,k},\ldots,\tau_{n,k}}_{n\text{ copies}},1)=0.
\]
The supporting result gives
\[
  \min_{\|x\|_\infty=1}h_{2k}(x)
  =\binom{n+2k-1}{2k}|\tau_{n,k}|^{2k}.
\]
Therefore the sharp constant sought in Problem~5 is
\[
  \boxed{C_{n,2k}=\binom{n+2k-1}{2k}^{1/(2k)}|\tau_{n,k}|},
  \qquad C_{n,2k}\|A\|_{\mathrm{op}}\le \|A\|_{2k}.
\]
Equality is realized, up to scale, global sign, and permutation, by a
Hermitian matrix whose eigenvalue vector is
$(\tau_{n,k},\ldots,\tau_{n,k},1)$, with $n-1$ copies of $\tau_{n,k}$.

\textbf{Indexing note.} The displayed statement of Theorem~6.1 writes
$n-1$ copies in the odd-degree root equation. Lemmas~6.2--6.3,
Corollary~6.4, and the stationarity calculation use the correct equation with
$n$ copies; the extremizing vector itself has $n-1$ copies. For instance,
$n=2$, $k=1$ requires the root of $2t+1$.

\textbf{Scope.} This resolves Problem~5 only and is recorded as literature
retrieval, not as a new result of the run. The other problems in the source
paper are not addressed here.

\begin{thebibliography}{9}
\bibitem{BCG}
L. Bouthat, A. Ch\'avez, and S. R. Garcia,
\emph{Hunter's positivity theorem and random vector norms},
arXiv:2403.10314 (2024),
\url{https://arxiv.org/abs/2403.10314}.

\bibitem{BP}
S. Brazitikos and C. Pandis,
\emph{Sharp inequalities for symmetric polynomials, Hunter's conjecture,
and moments of exponential random variables},
arXiv:2512.12254 (2025),
\url{https://arxiv.org/abs/2512.12254}.
\end{thebibliography}

\end{document}
