\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=29mm]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{microtype}
\usepackage{booktabs,tabularx,array}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\setlist[itemize]{topsep=0.25em,itemsep=0.15em,leftmargin=1.45em}
\setlist[enumerate]{topsep=0.25em,itemsep=0.15em,leftmargin=1.6em}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{question}[theorem]{Question}

\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\conv}{\operatorname{conv}}
\newcommand{\diam}{\operatorname{diam}}
\newcommand{\ext}{\operatorname{ext}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\co}{\operatorname{co}}
\newcommand{\clco}{\overline{\operatorname{co}}}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\newcommand{\abs}[1]{\left\lvert #1\right\rvert}
\newcommand{\pair}[2]{\left\langle #1,#2\right\rangle}
\newcommand{\sourceNorm}[1]{\left\lvert #1\right\rvert_{\eps}}
\newcommand{\newnorm}[1]{\left\lvert\!\left\lvert\!\left\lvert #1\right\rvert\!\right\rvert\!\right\rvert}

\title{LASQ versus the Diameter Two Property\\
\large Verification of the fixed-$\eps$ obstruction, further obstructions, and quantitative partial progress}
\author{Research note prepared from the supplied source paper and partial proof}
\date{21 June 2026}

\begin{document}
\maketitle

\begin{abstract}
Rodr\'iguez and Rueda Zoca asked whether a locally almost square (LASQ) Banach space can fail the diameter two property (D2P).  The supplied partial proof concerns the fixed-$\eps$ renorming used in their construction of spaces with the slice-D2P but with arbitrarily small relatively weakly open subsets.  That proof is correct.  We sharpen it in three ways: a symmetric ``leakage'' inequality is obtained; every tree generator, not only the root, is shown to be quantitatively strongly extreme; and the actual norm on the whole space constructed in the proof of their Theorem~1.2 is shown not to be LASQ.

A literature search through 21 June 2026 did not locate a proof or counterexample for the general LASQ-versus-D2P question.  We therefore examine two later natural candidates.  The 2024 renorming of $L_\infty[0,1]$ by Cobollo et al. and the 2026 dual LD2P-without-D2P example of Haller--Kaasik--Ostrak both contain explicit strongly extreme sphere points and hence are not LASQ.  Finally, we prove a finite-rank estimate: if $X$ is LASQ and a basic relatively weakly open subset of $B_X$ is determined by an operator of rank $r$, then its diameter is at least $2/(r+1)$.  This does not settle the problem, but it isolates the remaining obstruction: LASQ supplies almost square directions at one point, while D2P requires such directions to be simultaneously small under finitely many functionals.
\end{abstract}

\tableofcontents

\section{The question and the outcome of this investigation}

For a real Banach space $X$, write $B_X$ and $S_X$ for its closed unit ball and unit sphere.  We use the following equivalent $\eps$-form of local almost squareness:
\[
 X \text{ is LASQ}
 \quad\Longleftrightarrow\quad
 \forall x\in S_X\ \forall\eps>0\ \exists y\in S_X:
 \norm{x\pm y}\le 1+\eps.
\]
The diameter two property (D2P) means that every non-empty relatively weakly open subset of $B_X$ has diameter two.  LASQ always implies the slice diameter two property (also called LD2P), whereas weak almost squareness implies D2P; see \cite{ALL2016}.  The question raised in \cite{RodriguezRueda2023} is:

\begin{question}[Rodr\'iguez--Rueda Zoca]
Does there exist a LASQ Banach space which fails the D2P?
\end{question}

The conclusions reached here are as follows.
\begin{enumerate}
\item The supplied fixed-$\eps$ obstruction is valid, and its quantitative estimate can be improved.
\item The entire norm constructed in the proof of \cite[Theorem~1.2]{RodriguezRueda2023}, not merely its $c_0$ core, is not LASQ.
\item No full resolution of the general question was found in the literature search described in \cref{sec:literature}.
\item Two later constructions which at first sight are plausible sources of a counterexample are also not LASQ.
\item A general finite-rank lower bound, \cref{thm:finite-rank}, gives some positive information but falls short of diameter two.
\end{enumerate}

A point $p\in S_X$ is \emph{strongly extreme} if
\[
 \norm{p+y_n}\longrightarrow 1,
 \qquad
 \norm{p-y_n}\longrightarrow 1
 \quad\Longrightarrow\quad
 \norm{y_n}\longrightarrow 0.
\]
Plainly, a LASQ space has no strongly extreme point in its unit sphere.

\section{The fixed-$\eps$ construction from the source paper}
\label{sec:source}

We retain the notation of \cite[Section~3]{RodriguezRueda2023}.  Let $\N^{<\omega}$ be the Baire tree and let
\[
 Z=c(\N^{<\omega})\oplus_\infty c_0,
 \qquad
 \norm{(x,y)}_Z=\max\{\norm{x}_\infty,\norm{y}_\infty\}.
\]
For $\alpha\in\N^{<\omega}$ put
\[
 x_\alpha(\beta)=
 \begin{cases}
  1,&\beta\preceq\alpha,\\
 -1,&\text{otherwise},
 \end{cases}
 \qquad
 A=\{x_\alpha:\alpha\in\N^{<\omega}\}.
\]
Every $x_\alpha$ is $\{\pm1\}$-valued and $\lim x_\alpha=-1$.  Fix $0<\eps<1$ and set
\begin{equation}
\label{eq:source-ball}
 B_\eps=\clco\Bigl(
 (A\times\{0\})\cup(-A\times\{0\})\cup
 \bigl((1-\eps)B_Z+\eps B_{c_0(\N^{<\omega})}\times\{0\}\bigr)
 \Bigr).
\end{equation}
Let $\sourceNorm{\cdot}$ be the Minkowski functional of $B_\eps$.  The source proof gives
\begin{equation}
\label{eq:norm-comparison}
 (1-\eps)B_Z\subset B_\eps\subset B_Z,
 \qquad
 \norm{z}_Z\le\sourceNorm{z}\le\frac{1}{1-\eps}\norm{z}_Z.
\end{equation}
Let $P_2(x,y)=y$ and $L(x,y)=\lim x$.

\subsection{A symmetric leakage estimate}

The partial proof used the one-sided estimate
\[
 \norm{P_2w}_\infty\le \frac{1-\eps}{\eps}\bigl(1+L(w)\bigr).
\]
It is correct.  In fact, the following symmetric inequality is available.

\begin{lemma}[Leakage inequality]
\label{lem:leakage}
For every $w\in B_\eps$,
\begin{equation}
\label{eq:symmetric-leakage}
 \eps\norm{P_2w}_\infty+(1-\eps)\abs{L(w)}\le 1-\eps.
\end{equation}
Consequently,
\begin{equation}
\label{eq:one-sided-leakage}
 \norm{P_2w}_\infty
 \le \frac{1-\eps}{\eps}\bigl(1+L(w)\bigr)
 \quad\text{and}\quad
 \norm{P_2w}_\infty
 \le \frac{1-\eps}{\eps}\bigl(1-L(w)\bigr).
\end{equation}
\end{lemma}

\begin{proof}
The left side of \eqref{eq:symmetric-leakage} is a continuous convex function of $w$.  It is therefore enough to check the three generating pieces in \eqref{eq:source-ball}.

If $w=(\pm x_\alpha,0)$, then $P_2w=0$ and $\abs{L(w)}=1$, so equality holds.  If
\[
 w=(1-\eps)u+\eps(v,0),
 \qquad u\in B_Z,\quad v\in B_{c_0(\N^{<\omega})},
\]
then $\norm{P_2w}_\infty\le1-\eps$ and $\abs{L(w)}\le1-\eps$.  Hence
\[
 \eps\norm{P_2w}_\infty+(1-\eps)\abs{L(w)}
 \le \eps(1-\eps)+(1-\eps)^2=1-\eps.
\]
The closed convex hull is therefore contained in the sublevel set.  The two estimates in \eqref{eq:one-sided-leakage} follow from $1-\abs{t}\le1\pm t$.
\end{proof}

The geometric meaning is simple: the only generators which can carry a second $c_0$ coordinate have $\abs{L}\le1-\eps$.  Thus approaching either face $L=\pm1$ forces the second coordinate to vanish quantitatively.

\subsection{All tree generators are strongly extreme}

\begin{theorem}[Quantitative strong extremity]
\label{thm:tree-strong}
For every $\alpha\in\N^{<\omega}$, the points
\[
 p_\alpha=(x_\alpha,0)
 \quad\text{and}\quad
 -p_\alpha
\]
are strongly extreme points of $B_\eps$.  More precisely, if $y=(u,v)\in Z$ and
\begin{equation}
\label{eq:delta-assumption}
 \sourceNorm{p_\alpha+y}\le1+\delta,
 \qquad
 \sourceNorm{p_\alpha-y}\le1+\delta
\end{equation}
for some $\delta\ge0$, then
\begin{equation}
\label{eq:strong-modulus}
 \sourceNorm{y}
 \le C_\eps\delta,
 \qquad
 C_\eps=\max\left\{\frac1{1-\eps},\frac1\eps\right\}.
\end{equation}
\end{theorem}

\begin{proof}
Because $B_\eps\subset B_Z$, \eqref{eq:delta-assumption} implies
\[
 \norm{x_\alpha\pm u}_\infty\le1+\delta.
\]
Every coordinate of $x_\alpha$ has modulus one.  For a scalar $a\in\{\pm1\}$,
\[
 \max\{\abs{a+t},\abs{a-t}\}=1+\abs{t}.
\]
It follows coordinatewise that
\begin{equation}
\label{eq:u-small}
 \norm{u}_\infty\le\delta,
 \qquad
 \abs{\lim u}\le\delta.
\end{equation}

Put $\ell=\lim u$ and
\[
 q_+=\frac{p_\alpha+y}{1+\delta},
 \qquad
 q_-=\frac{p_\alpha-y}{1+\delta}.
\]
Both points lie in $B_\eps$.  Applying the first inequality in \eqref{eq:one-sided-leakage} to $q_+$ and $q_-$ gives, respectively,
\[
 \norm{v}_\infty
 \le \frac{1-\eps}{\eps}(\delta+\ell),
 \qquad
 \norm{v}_\infty
 \le \frac{1-\eps}{\eps}(\delta-\ell).
\]
Therefore
\begin{equation}
\label{eq:v-small}
 \norm{v}_\infty
 \le\frac{1-\eps}{\eps}(\delta-\abs{\ell})
 \le\frac{1-\eps}{\eps}\delta.
\end{equation}
Combining \eqref{eq:u-small}, \eqref{eq:v-small}, and \eqref{eq:norm-comparison},
\[
 \sourceNorm{y}
 \le\frac1{1-\eps}\max\left\{\delta,\frac{1-\eps}{\eps}\delta\right\}
 =C_\eps\delta.
\]
This proves the quantitative estimate and hence strong extremity.  The assertion for $-p_\alpha$ follows by symmetry.
\end{proof}

\begin{corollary}
\label{cor:partial-correct}
The partial result supplied with the problem is correct.  Its factor $2/\eps$ can be replaced by $1/\eps$, and its conclusion holds at every tree point $\pm(x_\alpha,0)$.
\end{corollary}

\begin{proof}
If $\sourceNorm{p_\alpha\pm y_n}\to1$, then
\[
 \delta_n=\max\{\sourceNorm{p_\alpha+y_n},\sourceNorm{p_\alpha-y_n}\}-1
\]
is non-negative by the triangle inequality and tends to zero.  Apply \eqref{eq:strong-modulus}.  Since LASQ would require vectors of norm tending to one at every sphere point, the space is not LASQ.
\end{proof}

\section{The full norm used in the source theorem is not LASQ}
\label{sec:full-source}

The source proof first constructs the preceding norm on a space isomorphic to $c_0$.  For a general space containing a complemented copy of $c_0$, it then writes $X=E\oplus W$ and equips $X$ with an $\ell_\infty$-sum norm.  The following elementary fact closes the gap between the core obstruction and the full construction.

\begin{lemma}[$\ell_\infty$ sums]
\label{lem:linfty-lasq}
For non-zero Banach spaces $X$ and $Y$,
\[
 X\oplus_\infty Y\text{ is LASQ}
 \quad\Longleftrightarrow\quad
 X\text{ is LASQ or }Y\text{ is LASQ}.
\]
\end{lemma}

\begin{proof}
Suppose first that $X$ is LASQ.  Given $(x,y)\in S_{X\oplus_\infty Y}$, choose $u_n\in S_X$ with
\[
 \norm{x/\norm{x}\pm u_n}\to1
\]
when $x\ne0$; if $x=0$, take any $u_n\in S_X$.  Convexity gives
\[
 \limsup_n\norm{x\pm u_n}\le1.
\]
Consequently,
\[
 \norm{(x,y)\pm(u_n,0)}
 =\max\{\norm{x\pm u_n},\norm{y}\}\longrightarrow1.
\]
The same argument applies if $Y$ is LASQ.

Conversely, suppose $X\oplus_\infty Y$ is LASQ and take $x\in S_X$, $y\in S_Y$.  There are $(u_n,v_n)\in B_{X\oplus_\infty Y}$ such that
\[
 \max\{\norm{u_n},\norm{v_n}\}\to1
\]
and
\[
 \max\{\norm{x\pm u_n},\norm{y\pm v_n}\}\to1.
\]
After passing to a subsequence, either $\norm{u_n}\to1$ or $\norm{v_n}\to1$.  In the first case $x$ has an LASQ sequence in $X$; in the second case $y$ has one in $Y$.  If neither summand were LASQ, choosing $x$ and $y$ to be bad sphere points would give a contradiction.
\end{proof}

\begin{theorem}
\label{thm:full-source-not-lasq}
The particular equivalent norm on $X$ constructed in the proof of \cite[Theorem~1.2]{RodriguezRueda2023} is not LASQ for any fixed $0<\eps<1$.
\end{theorem}

\begin{proof}
The $c_0$ summand $E$ is equipped with the fixed-$\eps$ norm of \cref{sec:source}, so it is not LASQ by \cref{thm:tree-strong}.  If the complementary summand $W$ is non-zero, the source proof chooses on $W$ an equivalent norm whose unit ball has slices of arbitrarily small diameter.  Such a space cannot be LASQ, because LASQ implies the slice-D2P.  The final norm is the $\ell_\infty$-sum of these two norms, so \cref{lem:linfty-lasq} applies.  If $W=\{0\}$, the conclusion is already \cref{thm:tree-strong}.
\end{proof}

\begin{remark}
The conclusion concerns the explicit norm built in the proof of the theorem.  It does not say that every norm satisfying properties (i)--(iii) of \cite[Theorem~1.2]{RodriguezRueda2023} must fail LASQ.
\end{remark}

\section{Two later candidate constructions are also not LASQ}
\label{sec:candidates}

\subsection{A general saturation obstruction in supremum norms}

\begin{lemma}[Supremum-norm saturation]
\label{lem:sup-saturation}
Let $E$ be a subspace of $\ell_\infty(\Gamma)$ or $L_\infty(\mu)$, and let $\newnorm{\cdot}$ be an equivalent norm satisfying
\begin{equation}
\label{eq:sup-equivalence}
 \norm{z}_\infty\le\newnorm{z}\le C\norm{z}_\infty
 \qquad(z\in E).
\end{equation}
If $u\in S_{(E,\newnorm{\cdot})}$ is $\{\pm1\}$-valued pointwise (or almost everywhere), then $u$ is strongly extreme.  Quantitatively,
\[
 \newnorm{u\pm z}\le1+\delta
 \quad\Longrightarrow\quad
 \newnorm{z}\le C\delta.
\]
\end{lemma}

\begin{proof}
The left inequality in \eqref{eq:sup-equivalence} yields $\norm{u\pm z}_\infty\le1+\delta$.  Pointwise,
\[
 \max\{\abs{u(t)+z(t)},\abs{u(t)-z(t)}\}=1+\abs{z(t)},
\]
so $\norm{z}_\infty\le\delta$.  The right inequality in \eqref{eq:sup-equivalence} finishes the proof.
\end{proof}

\subsection{The 2024 $L_\infty$ renorming}

Cobollo, Isert, L\'opez-P\'erez, Mart\'in, Perreau, Quero, Quilis, Rodr\'iguez-Vidanes and Rueda Zoca constructed in \cite{CobolloEtAl2024} an equivalent norm on $L_\infty[0,1]$ whose unit ball has relatively weakly open subsets of arbitrarily small diameter and a weakly dense set of Daugavet points.  Their unit ball has the form
\[
 \mathcal B_\eps=\clco\Bigl(
 (2K_0-\mathbf1)\cup(-2K_0+\mathbf1)
 \cup\bigl((1-\eps)B_{L_\infty}+\eps B_{\ker E_0}\bigr)
 \Bigr),
\]
with
\[
 (1-\eps)B_{L_\infty}\subset\mathcal B_\eps\subset B_{L_\infty}.
\]
Their tree functions $u_\alpha=2h_\alpha-\mathbf1$ belong to the new unit sphere and are $\{\pm1\}$-valued almost everywhere.

\begin{corollary}
\label{cor:cobollo-not-lasq}
For every fixed $0<\eps<1$, the norm of \cite[Theorem~1.3]{CobolloEtAl2024} is not LASQ.  Every tree function $u_\alpha$ is strongly extreme, with
\[
 \newnorm{g}\le\frac{\delta}{1-\eps}
 \quad\text{whenever}\quad
 \newnorm{u_\alpha\pm g}\le1+\delta.
\]
\end{corollary}

\begin{proof}
The norm comparison is exactly \eqref{eq:sup-equivalence} with $C=(1-\eps)^{-1}$.  Apply \cref{lem:sup-saturation}.
\end{proof}

The cited paper proves that the same $u_\alpha$ are preserved extreme Daugavet points.  Strong extremity is a different and stronger local obstruction for the present purpose; it appears to follow immediately from the ambient $L_\infty$ saturation but was not used there.

\subsection{The 2026 dual LD2P-without-D2P example}

Haller, Kaasik and Ostrak constructed a metric space $M$ for which $\Lip_0(M)$ has the LD2P but fails even the weak-star D2P \cite[Example~5.2]{HallerKaasikOstrak2026}.  Its points are
\[
 M=\{x_i,y_i,u_j^i,v_j^i:i\in\{1,2,3\},\ j\in\N\}.
\]
The pairs at distance one are
\[
 y_1x_2,\quad y_2x_3,\quad y_3x_1,
\]
and, for each $i,j$, the three edges in the path
\[
 x_i-u_j^i-v_j^i-y_i.
\]
Every other pair of distinct points has distance two.  Take $x_1$ as base point.

The distance-one graph is bipartite, with colour classes
\[
 \mathcal C_0=\{x_i,v_j^i\},
 \qquad
 \mathcal C_1=\{y_i,u_j^i\}.
\]
Define $f\in\Lip_0(M)$ by $f=0$ on $\mathcal C_0$ and $f=1$ on $\mathcal C_1$.

\begin{proposition}
\label{prop:lip-strong}
The function $f$ is a strongly extreme point of $B_{\Lip_0(M)}$.  More precisely,
\[
 \norm{f\pm g}_{\Lip}\le1+\delta
 \quad\Longrightarrow\quad
 \norm{g}_{\Lip}\le3\delta.
\]
Consequently the space in \cite[Example~5.2]{HallerKaasikOstrak2026} is not LASQ.
\end{proposition}

\begin{proof}
The function $f$ changes by exactly one across every distance-one edge, hence $\norm{f}_{\Lip}=1$.  If $p,q$ form such an edge and $a=g(p)-g(q)$, the two assumptions give
\[
 \abs{1+a}\le1+\delta,
 \qquad
 \abs{1-a}\le1+\delta,
\]
after possibly reversing the orientation.  Thus $\abs{a}\le\delta$.

The distance-one graph has graph diameter six.  Hence any two vertices can be joined by at most six unit edges, and therefore
\[
 \abs{g(p)-g(q)}\le6\delta
 \qquad(p,q\in M).
\]
On a distance-one pair the Lipschitz quotient is at most $\delta$; on every other pair the metric distance is two, so the quotient is at most $3\delta$.  This proves the estimate.
\end{proof}

Thus the most recent explicit dual example separating LD2P from D2P does not answer the LASQ question either.

\section{The weakly-null-net route to D2P}
\label{sec:net}

The central missing ingredient can be formulated cleanly.  Say that $X$ has the \emph{net-LASQ property} if for every $x\in S_X$ there is a weakly null net $(y_\gamma)$ in $X$ such that
\[
 \norm{y_\gamma}\to1,
 \qquad
 \norm{x\pm y_\gamma}\to1.
\]

\begin{proposition}
\label{prop:net-implies-d2p}
Every Banach space with the net-LASQ property has the D2P.
\end{proposition}

\begin{proof}
Let $U\subset B_X$ be non-empty and relatively weakly open.  Since a net-LASQ space is infinite-dimensional, $S_X$ is weakly dense in $B_X$; choose $x\in U\cap S_X$.  There are $f_1,\dots,f_n\in X^*$ and $\rho>0$ such that
\[
 W=\{z\in B_X:\abs{f_i(z-x)}<\rho\ (i=1,\dots,n)\}\subset U.
\]
Let $(y_\gamma)$ be a net as above and set
\[
 \eta_\gamma=
 \max\{\norm{x+y_\gamma},\norm{x-y_\gamma},1\}-1.
\]
Then $\eta_\gamma\to0$ and
\[
 z_\gamma^\pm=\frac{x\pm y_\gamma}{1+\eta_\gamma}\in B_X.
\]
Since $y_\gamma\to0$ weakly,
\[
 f_i(z_\gamma^\pm-x)
 =\frac{\pm f_i(y_\gamma)-\eta_\gamma f_i(x)}{1+\eta_\gamma}
 \longrightarrow0.
\]
Thus $z_\gamma^\pm\in W$ eventually, while
\[
 \norm{z_\gamma^+-z_\gamma^-}
 =\frac{2\norm{y_\gamma}}{1+\eta_\gamma}\longrightarrow2.
\]
Hence $\diam U=2$.
\end{proof}

Ciaci proved that positive LASQ Banach lattices have the net-LASQ property, and consequently the D2P \cite{Ciaci2023}.  The same paper explicitly asks whether ordinary LASQ implies this net property.  A positive solution of that stronger question would settle the original LASQ-versus-D2P problem positively.

\section{A finite-rank lower bound for weakly open sets}
\label{sec:finite-rank}

The next result is independent of the special constructions above.  It quantifies what LASQ alone forces inside a weak neighborhood described by finitely many functionals.

\begin{lemma}[Almost diametral pairs over extreme quotient points]
\label{lem:extreme-lifting}
Let $X$ be LASQ, let $T:X\to F$ be a finite-rank operator, and put
\[
 K=\overline{T(B_X)}\subset F.
\]
If $v\in\ext K$, then for every $\eta>0$ there are $a,b\in B_X$ such that
\[
 \norm{Ta-v}<\eta,
 \qquad
 \norm{Tb-v}<\eta,
 \qquad
 \norm{a-b}>2-\eta.
\]
\end{lemma}

\begin{proof}
If $T=0$ there is nothing to prove, so assume $K$ is non-trivial.  Since $K$ is symmetric, $0$ is not an extreme point.  Choose $z_k\in B_X$ with $Tz_k\to v$.  We claim that $\norm{z_k}\to1$.  Otherwise, after passing to a subsequence, $\norm{z_k}\le c<1$.  Then $v\in cK$, so $v=cw+(1-c)0$ for some $w\in K$, contradicting extremality.

Put $x_k=z_k/\norm{z_k}\in S_X$, so $Tx_k\to v$.  By LASQ choose $y_k\in S_X$ and numbers $\eps_k\downarrow0$ such that
\[
 \norm{x_k\pm y_k}\le1+\eps_k.
\]
After passing to a subsequence, $Ty_k\to h\in F$.  Set
\[
 a_k=\frac{x_k+y_k}{1+\eps_k},
 \qquad
 b_k=\frac{x_k-y_k}{1+\eps_k}.
\]
Then $a_k,b_k\in B_X$, $\norm{a_k-b_k}=2/(1+\eps_k)\to2$, and
\[
 Ta_k\to v+h,
 \qquad
 Tb_k\to v-h.
\]
Both limits belong to $K$.  Since $v$ is their midpoint and is extreme, $h=0$.  The assertion follows for large $k$.
\end{proof}

\begin{theorem}[Finite-rank diameter estimate]
\label{thm:finite-rank}
Let $X$ be LASQ, let $T:X\to F$ have rank $r<\infty$, and let $V\subset T(X)$ be open.  If
\[
 U=B_X\cap T^{-1}(V)
e\varnothing,
\]
then
\begin{equation}
\label{eq:rank-bound}
 \diam U\ge\frac{2}{r+1}.
\end{equation}
For $r=0$, the right conclusion is understood as $\diam U=2$.
\end{theorem}

\begin{proof}
Assume $r\ge1$ and put $K=\overline{T(B_X)}$.  Choose $x_0\in U$ and set $c=Tx_0\in V\cap K$.  By the finite-dimensional Minkowski--Carath\'eodory theorem, there are extreme points $v_1,\dots,v_m$ of $K$ and coefficients $\lambda_i\ge0$ such that
\[
 c=\sum_{i=1}^m\lambda_i v_i,
 \qquad
 \sum_{i=1}^m\lambda_i=1,
 \qquad
 m\le r+1.
\]
Choose $j$ with $\lambda_j=\max_i\lambda_i$, so $\lambda_j\ge1/(r+1)$.

Fix $\eta>0$.  By \cref{lem:extreme-lifting}, choose $a_j,b_j\in B_X$ with $Ta_j,Tb_j$ as close to $v_j$ as desired and $\norm{a_j-b_j}>2-\eta$.  For $i\ne j$, choose $c_i\in B_X$ with $Tc_i$ as close to $v_i$ as desired.  Define
\[
 a=\lambda_j a_j+\sum_{i\ne j}\lambda_i c_i,
 \qquad
 b=\lambda_j b_j+\sum_{i\ne j}\lambda_i c_i.
\]
Both points belong to $B_X$.  Because $V$ is open and $Ta,Tb$ can be made arbitrarily close to $c$, the choices can be made so that $a,b\in U$.  Finally,
\[
 \norm{a-b}=\lambda_j\norm{a_j-b_j}
 >\lambda_j(2-\eta).
\]
Letting $\eta\downarrow0$ gives \eqref{eq:rank-bound}.
\end{proof}

\begin{corollary}
If a basic relatively weakly open subset of $B_X$ is described using $r$ linearly independent functionals, then an LASQ space forces its diameter to be at least $2/(r+1)$.
\end{corollary}

\begin{remark}
This estimate is compatible with the source construction.  Its weakly open sets of small diameter use an increasing number of tree-coordinate constraints.  The bound tends to zero as the number of independent functionals grows, so it cannot by itself prove D2P.
\end{remark}

\section{Literature search and current status}
\label{sec:literature}

The literature search covered the exact problem statement, the terms LASQ, WASQ, D2P, slice-D2P/LD2P, recent work on ultrapowers, Banach lattices, Lipschitz-free spaces, spaces of Lipschitz functions, and the renormings most closely related to the source construction.  The following are the most relevant checkpoints.

\begin{center}
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{0.23\textwidth}X>{\raggedright\arraybackslash}p{0.25\textwidth}@{}}
\toprule
Source & Result & Relevance here\\
\midrule
Rodr\'iguez--Rueda Zoca (2023) \cite{RodriguezRueda2023} & Poses the LASQ-without-D2P question and constructs the fixed-$\eps$ near-square renorming. & The explicit norm is ruled out in \cref{sec:source,sec:full-source}.\\
Ciaci (2023) \cite{Ciaci2023} & Positive LASQ Banach lattices have a weakly null LASQ net and hence D2P. & Gives the strongest general positive mechanism currently found; asks whether the net conclusion holds for every LASQ space.\\
Rueda Zoca (2025) \cite{RuedaZoca2025} & LASQ yields strong uniform slice-D2P consequences in ultrapowers. & Strengthens the slice conclusion, but does not establish D2P.\\
Haller--Kaasik--Ostrak (2023) and Kaasik (2026) \cite{HKO2023,KaasikThesis2026} & For Lipschitz-free spaces, LASQ is equivalent to the underlying complete metric space being a length space, and hence to Daugavet/D2P behaviour. & The problem has a positive answer in this special class.\\
Haller--Kaasik--Ostrak (2026) \cite{HallerKaasikOstrak2026} & Constructs a dual space $\Lip_0(M)$ with LD2P but not D2P. & The explicit checkerboard point in \cref{prop:lip-strong} shows this example is not LASQ.\\
Cobollo et al. (2024) \cite{CobolloEtAl2024} & Renorms $L_\infty$ with arbitrarily small weakly open subsets and many Daugavet points. & Its $\{\pm1\}$ tree points are strongly extreme; see \cref{cor:cobollo-not-lasq}.\\
\bottomrule
\end{tabularx}
\end{center}

No article, preprint, thesis, or survey located in this search states a general proof that LASQ implies D2P or gives a LASQ counterexample to D2P.  The most recent sources surveyed continue to record only special classes and stronger auxiliary hypotheses.  This is necessarily a literature-search conclusion rather than a proof of non-existence of an unindexed result.

\section{Strategies tested and the remaining bottleneck}
\label{sec:strategies}

Several natural ways of turning the source's ``almost LASQ'' norms into an exact LASQ norm do not produce a counterexample.

\paragraph{Letting $\eps\downarrow0$ on the same space.}
If one takes the closed convex hull of the union of source balls $B_{\eps_n}$ with $\eps_n\downarrow0$, then the inclusions $(1-\eps_n)B_Z\subset B_{\eps_n}\subset B_Z$ force the resulting ball to be exactly $B_Z$.  The limiting space $c(\N^{<\omega})\oplus_\infty c_0$ is ASQ because of its $c_0$ summand, and therefore has the D2P.

\paragraph{Ultraproducts of the fixed-$\eps_n$ norms.}
The source spaces are $(r,s)$-SQ for all $r,s<(1-\eps_n)/(1+\eps_n)$.  When $\eps_n\to0$, these constants tend to one, and the standard ultraproduct argument upgrades the limit to ASQ.  Again the D2P is recovered rather than destroyed.

\paragraph{Direct sums.}
A $c_0$-sum creates tail directions and is ASQ.  An $\ell_\infty$-sum is LASQ only when at least one factor is LASQ, by \cref{lem:linfty-lasq}; if that factor has D2P, the usual product weak neighborhoods retain diameter two.  Other standard absolute sums do not bypass the same compatibility constraints; see \cite{Hardtke2018}.

\paragraph{Finite-dimensional images.}
The proof of \cref{thm:finite-rank} shows that over an extreme point of the finite-dimensional image $\overline{T(B_X)}$, LASQ directions must become small under $T$.  At an interior image point, however, a non-zero symmetric segment can remain inside the image.  Carath\'eodory decomposition then loses a factor of at most $r+1$.  Eliminating that loss would amount to finding one almost-square direction which is small under all the defining functionals, precisely the net-LASQ issue of \cref{sec:net}.

Thus the fixed-$\eps$ leakage mechanism is now well understood, but no construction found here simultaneously achieves the following two incompatible-looking requirements:
\begin{itemize}
\item at every sphere point, a norm-one almost-square direction; and
\item in one finite-codimensional weak neighborhood, a uniform obstruction to all almost diametral pairs.
\end{itemize}

\section{Conclusion}

The supplied partial proof is mathematically sound.  The fixed-$\eps$ source ball has a sharper symmetric leakage inequality, and all of its tree generators are quantitatively strongly extreme.  This also rules out the complete norm actually used in the source proof of Theorem~1.2.  Two prominent later LD2P-without-D2P constructions are ruled out by similarly explicit strong-extremity arguments.

The general LASQ-versus-D2P question was not resolved by the literature search or by the additional arguments developed here.  The finite-rank bound $2/(r+1)$ is a rigorous partial result, while the weakly-null-net formulation identifies a clean sufficient condition whose validity for arbitrary LASQ spaces remains the central bottleneck.

\begin{thebibliography}{99}

\bibitem{ALL2016}
T.~A. Abrahamsen, J.~Langemets and V.~Lima,
\emph{Almost square Banach spaces},
J. Math. Anal. Appl. \textbf{434} (2016), 1549--1565.
\href{https://doi.org/10.1016/j.jmaa.2015.10.013}{doi:10.1016/j.jmaa.2015.10.013}.

\bibitem{Ciaci2023}
S.~Ciaci,
\emph{Locally almost square Banach lattices},
Rev. R. Acad. Cienc. Exactas F\'is. Nat. Ser. A Mat. RACSAM \textbf{117} (2023), article 97.
\href{https://doi.org/10.1007/s13398-023-01434-6}{doi:10.1007/s13398-023-01434-6}.

\bibitem{CobolloEtAl2024}
C.~Cobollo, D.~Isert, G.~L\'opez-P\'erez, M.~Mart\'in, Y.~Perreau, A.~Quero,
A.~Quilis, D.~L. Rodr\'iguez-Vidanes and A.~Rueda Zoca,
\emph{Banach spaces with small weakly open subsets of the unit ball and massive sets of Daugavet and $\Delta$-points},
Rev. R. Acad. Cienc. Exactas F\'is. Nat. Ser. A Mat. RACSAM \textbf{118} (2024), article 96.
\href{https://doi.org/10.1007/s13398-024-01596-x}{doi:10.1007/s13398-024-01596-x}.

\bibitem{Hardtke2018}
J.-D. Hardtke,
\emph{Summands in locally almost square and locally octahedral spaces},
Acta Comment. Univ. Tartu. Math. \textbf{22} (2018), 149--162.
\href{https://doi.org/10.12697/ACUTM.2018.22.13}{doi:10.12697/ACUTM.2018.22.13}.

\bibitem{HKO2023}
R.~Haller, J.~K. Kaasik and A.~Ostrak,
\emph{The Lipschitz-free space over a length space is locally almost square but never almost square},
Mediterr. J. Math. \textbf{20} (2023), article 39.
\href{https://doi.org/10.1007/s00009-022-02228-9}{doi:10.1007/s00009-022-02228-9}.

\bibitem{HallerKaasikOstrak2026}
R.~Haller, J.~K. Kaasik and A.~Ostrak,
\emph{The local diameter two property and the diameter two property in spaces of Lipschitz functions},
J. Math. Anal. Appl. \textbf{556} (2026), article 130178.
\href{https://doi.org/10.1016/j.jmaa.2025.130178}{doi:10.1016/j.jmaa.2025.130178}.

\bibitem{KaasikThesis2026}
J.~K. Kaasik,
\emph{Diameter two properties and almost square properties in Lipschitz-free spaces and spaces of Lipschitz functions},
Dissertationes Mathematicae Universitatis Tartuensis 146, University of Tartu Press, 2026.

\bibitem{RodriguezRueda2023}
J.~Rodr\'iguez and A.~Rueda Zoca,
\emph{On weakly almost square Banach spaces},
Proc. Edinb. Math. Soc. \textbf{66} (2023), 979--997.
\href{https://doi.org/10.1017/S0013091523000536}{doi:10.1017/S0013091523000536}.

\bibitem{RuedaZoca2025}
A.~Rueda Zoca,
\emph{Slice diameter two property in ultrapowers},
Bull. Malays. Math. Sci. Soc. \textbf{48} (2025), article 62.
\href{https://doi.org/10.1007/s40840-025-01847-z}{doi:10.1007/s40840-025-01847-z}.

\end{thebibliography}

\end{document}
