\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\title{Literature-Implied Answer: Weak-Star Sigma-Discrete Boundaries}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_01}}
\date{2026-06-23}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature-implied negative answer to a boundary subquestion in
arXiv:2502.17001.

\section*{Source Question}

In arXiv:2502.17001, ``Polyhedrality for twisted sums with
$C(\omega^\alpha)$'', Castillo and Salguero Alarcon explain in Section
\emph{Boundaries} that a previous conclusion about twisted sums with
$c_0(\kappa)$ is uncertain because they do not know whether the existence of a
weak-star $\sigma$-discrete boundary implies that a Banach space is
isomorphically polyhedral.

\section*{Supporting Literature}

In arXiv:1804.02899, ``Topology, isomorphic smoothness and polyhedrality in
Banach spaces'', Smith recalls the necessary condition that a polyhedral or LFC
norm forces the space to be Asplund and $c_0$-saturated.  Immediately after
this discussion, Smith cites Bible's thesis, Remark 3.4.4, for a space
\[
  Z=\ell_1 \oplus \ell_1(S_{\ell_\infty})
\]
which is neither Asplund nor $c_0$-saturated, and hence is not isomorphically
polyhedral, but which nevertheless admits an equivalent norm with a relatively
weak-star-discrete boundary.

\section*{Identification}

A relatively weak-star-discrete boundary is a weak-star
$\sigma$-discrete boundary, taking the countable union to have one piece.
Isomorphic polyhedrality is invariant under equivalent renorming.  Therefore
Bible's example, as reported by Smith, gives a negative answer to the implication
question:
\[
  \text{weak-star $\sigma$-discrete boundary}
  \;\nRightarrow\;
  \text{isomorphically polyhedral}.
\]

\section*{Scope}

This packet does not settle the full 3-space problem for isomorphic
polyhedrality.  It only clears the narrower boundary implication used in the
source paper to explain why a previous coda was uncertain.

\section*{Evidence}

The source and supporting PDFs were not locally available in
\texttt{data/raw/arxiv} at packet creation time.  The packet includes the parsed
TeX sources \texttt{source\_2502.17001.tex} and
\texttt{supporting\_source\_1804.02899.tex}.  The relevant source locations are
parsed line 275 of arXiv:2502.17001 and parsed line 168 of arXiv:1804.02899.

\end{document}
