\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newcommand{\LP}{\mathcal{LP}}

\title{Literature-Implied Answer for arXiv:math/0502081}
\author{run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_06}}
\date{2026-06-29}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature-implied answer, negative for the no-\(\ell_1\)
\(\mathcal L_\infty\)/non-\(\LP\) subquestion.

\section*{Source Question}

In Section 4 of Castillo--Moreno--Suarez, \emph{On
Lindenstrauss-Pelczynski spaces}, arXiv:math/0502081, after the corollary that
twisted sums of \(C(K)\)-spaces are \(\LP\)-spaces, the authors state:
\[
\text{``We do not know if there exist }\mathcal L_\infty\text{-spaces not
containing }\ell_1\text{ which are not }\LP\text{ spaces.''}
\]
In the parsed source this is the paragraph around lines 817--819 of
\texttt{data/parsed/arxiv\_sources/0502081/source.tex}.

\section*{Supporting Literature}

Castillo--Papini, \emph{On isomorphically polyhedral
\(\mathcal L_\infty\)-spaces}, arXiv:1601.02035, proves in its final section:
\[
\text{There is an isomorphically polyhedral }\mathcal L_\infty\text{-space
that is not an }\LP\text{-space.}
\]
The proof constructs, for a subspace \(H\subset c_0\), an exact sequence
\[
0\longrightarrow C(\omega^\omega)\longrightarrow \Omega_H
\longrightarrow c_0\longrightarrow 0
\]
and shows that \(\Omega_H\) is not an \(\LP\)-space.

\section*{Identification}

The constructed space \(\Omega_H\) is an \(\mathcal L_\infty\)-space and is
not \(\LP\) by arXiv:1601.02035. It remains only to check the ``not containing
\(\ell_1\)'' clause from the source question. The kernel \(C(\omega^\omega)\)
contains no copy of \(\ell_1\): its compact space is countable and scattered,
so its dual is separable, whereas any Banach space containing \(\ell_1\) has
nonseparable dual. The quotient \(c_0\) contains no copy of \(\ell_1\).
Finally, containing no copy of \(\ell_1\) is a three-space property: if
\(0\to Y\to X\to Z\to 0\) has \(Y\) and \(Z\) with no \(\ell_1\), then an
\(\ell_1\)-copy in \(X\) either maps isomorphically into \(Z\), or a block
basis is mapped arbitrarily close to \(Y\), yielding an \(\ell_1\)-copy in
\(Y\).

Thus \(\Omega_H\) is an \(\mathcal L_\infty\)-space containing no
\(\ell_1\), but it is not a Lindenstrauss--Pelczynski space. This gives a
negative answer to the source subquestion.

\section*{Scope and Limitations}

This is not a solution of the later quotient questions in Section 5 of
arXiv:math/0502081. In particular, it does not decide whether quotients of two
\(\LP\)-spaces are \(\LP\), whether \(\ell_\infty/C[0,1]\) is \(\LP\), or
whether the \(c_0(\Gamma)\)-extension property holds for all \(\LP\) ranges.

The relation is an agent-identified implication. The supporting paper cites
the source paper and proves the needed example, but does not explicitly state
that it is resolving this particular sentence from arXiv:math/0502081.

\section*{References}

\begin{enumerate}
\item J. M. F. Castillo, Y. Moreno, J. Suarez, \emph{On
Lindenstrauss-Pelczynski spaces}, arXiv:math/0502081.
\item J. M. F. Castillo and P. L. Papini, \emph{On isomorphically polyhedral
\(\mathcal L_\infty\)-spaces}, arXiv:1601.02035.
\end{enumerate}

\end{document}
