\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Lp}{L^p}
\newcommand{\Ktilde}{\widetilde{\mathcal K}}

\title{Literature-Implied Partial Boundary for arXiv:1304.7575}
\author{FA/Banach run fa\_banach\_001}
\date{June 15, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_implied\_answer (partial characterization /
negative boundary example)} packet. It does not claim a new proof, and it does
not claim a complete classification of all Banach spaces satisfying the
stochastic convolution hypothesis $(H_p)$ in van Neerven--Veraar--Weis
\cite{NVWsurvey}. It records that the later paper
van Neerven--Veraar--Weis \cite{NVWrbounded} gives a substantial positive
criterion, an equivalence reducing the Banach-lattice case to deterministic
$\ell^1$-boundedness, and a counterexample showing that UMD type 2 is not
sufficient.

\section*{Source Problem}

In the stochastic maximal $\Lp$-regularity section of \cite{NVWsurvey}, the
authors formulate Hypothesis $(H_p)$ as an $R$-boundedness condition for a
family of stochastic convolution operators. They prove that if $X$ is
isomorphic to a closed subspace of an $L^q(\mathcal O)$ space with
$q\in[2,\infty)$, then $(H_p)$ holds for all $p\in(2,\infty)$; the same result
holds for $p=q=2$. Immediately after this theorem they write that it is open
to describe the class of Banach spaces $X$ to which the theorem can be
extended. They also record a sufficient Banach-function-space condition from
earlier work.

\section*{Later Literature}

The later paper \cite{NVWrbounded} studies the $R$-boundedness of the same
stochastic convolution families. Its Theorem 7.1 states that, for Banach
spaces of type 2 and $p\in[2,\infty)$, several $R$-boundedness formulations
for stochastic convolution families are equivalent. In the Banach lattice case
these are also equivalent to $\ell^1$-boundedness of an associated deterministic
convolution family on $L^{p/2}(\R_+;X^2)$, where $X^2$ is the
2-concavification of $X$.

Theorem 7.2 of \cite{NVWrbounded} gives the positive criterion: if $X$ is a
Banach lattice with type 2 and the dual of $X^2$ is an HL lattice, then for
every Hilbert space $H$ and every $p\in(2,\infty)$ the family
\[
  \{S_k^H : k^2\in \Ktilde\}
\]
is $R$-bounded from
\[
  L^p_{\mathcal F}(\R_+\times\Omega;\gamma(H,X))
  \quad\hbox{to}\quad
  L^p(\R_+\times\Omega;X).
\]
The following corollary applies this result to the kernel class used in the
stochastic maximal regularity argument.

\section*{Negative Boundary}

Section 8 of \cite{NVWrbounded} explicitly says that it had been open whether
this $R$-boundedness holds for all UMD Banach spaces with type 2, and in
particular for all UMD Banach lattices with type 2. The paper answers this
negatively.

\begin{theorem}[van Neerven--Veraar--Weis, Theorem 8.2]
For every $1<p<\infty$, the deterministic family
$\{T_k:k\in\Ktilde\}$ fails to be $\ell^1$-bounded on
$L^p(\R_+;\ell^1(\ell^2))$. Consequently, for every $2<p<\infty$ the
stochastic convolution family $\{S_k^H:k^2\in\Ktilde\}$ fails to be
$R$-bounded from
\[
  L^p_{\mathcal F}(\R_+\times\Omega;\gamma(H,\ell^2(\ell^4)))
  \quad\hbox{to}\quad
  L^p(\R_+\times\Omega;\ell^2(\ell^4)).
\]
\end{theorem}

Thus the broad source question cannot be answered by the condition ``UMD and
type 2'' alone. Even within UMD Banach lattices of type 2, the space
$\ell^2(\ell^4)$ is outside the stochastic convolution class considered in
the theorem.

\section*{Conclusion}

For the source problem asking for the class of Banach spaces to which the
$L^q$ stochastic maximal regularity theorem extends, \cite{NVWrbounded}
provides the following literature-implied partial answer:
\begin{enumerate}
  \item in Banach lattices the question is equivalent to a deterministic
  $\ell^1$-boundedness problem on the 2-concavification;
  \item Banach lattices of type 2 whose 2-concavification has dual an HL
  lattice give a positive class;
  \item UMD type 2 is not sufficient, because $X=\ell^2(\ell^4)$ is a
  counterexample.
\end{enumerate}
The full classification requested in \cite{NVWsurvey} remains broader than
this packet.

\section*{Search Evidence}

The run indexes were searched for \texttt{1304.7575}, \texttt{Hypothesis
(H\_p)}, \texttt{stochastic maximal regularity}, \texttt{R-bounded stochastic
convolution}, \texttt{ell\^{}1-boundedness}, \texttt{UMD type 2}, and
\texttt{ell\^{}2(ell\^{}4)}. Existing packets covered adjacent stochastic
Weiss and UMD-lattice themes but not this source problem. A web/arXiv check on
June 15, 2026 identified \cite{NVWrbounded} as the direct follow-up source.

\section*{Human Review Recommendation}

Review as a provenance/status packet. The key points to check are whether a
later paper gives a full intrinsic classification of all Banach spaces
satisfying $(H_p)$, and whether theorem numbering differs in the published
versions of the two arXiv papers.

\begin{thebibliography}{9}

\bibitem{NVWsurvey}
J. van Neerven, M. Veraar, and L. Weis,
\emph{Stochastic integration in Banach spaces -- a survey},
arXiv:1304.7575.

\bibitem{NVWrbounded}
J. van Neerven, M. Veraar, and L. Weis,
\emph{On the R-boundedness of stochastic convolution operators},
arXiv:1404.3353.

\end{thebibliography}

\end{document}
