\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\newcommand{\F}{\mathcal F}
\newcommand{\Lip}{\operatorname{Lip}}

\title{Literature Status for the WASQ and SSD2P Questions in arXiv:2205.02685}
\author{Run fa\_banach\_001, lane 1}
\date{July 1, 2026}

\begin{document}
\maketitle

\section*{Status}

This note records that two questions from Haller--Kaasik--Ostrak,
arXiv:2205.02685, are answered negatively by Kaasik--Veeorg,
arXiv:2210.09158.

No new theorem is claimed here. The purpose of this packet is to identify the
exact later results that settle the source-paper questions.

\section*{Source Questions}

The source paper proves that, for complete metric spaces, $\F(M)$ is locally
almost square exactly in the length-space case, and that no Lipschitz-free
space is almost square. Immediately after these results are announced, the
authors ask whether $\F(M)$ is weakly almost square whenever $M$ is length, and
whether any Lipschitz-free space can have the symmetric strong diameter
$2$ property.

\section*{Later Answers}

The later paper arXiv:2210.09158 explicitly cites arXiv:2205.02685 as HKO.
Its abstract already states the two relevant conclusions: it constructs a
Lipschitz-free space which is LASQ but not WASQ, and it proves that a
Lipschitz-free space cannot have SSD2P.

For the WASQ question, Section~2 defines
\[
M=[0,1]\times(0,1/2]\cup\{(0,0),(1,0)\}
\]
with a metric that moves horizontally within each level and otherwise through
one of the two endpoints. The paper observes that $M$ is a length space, so
$\F(M)$ is LASQ by arXiv:2205.02685. Theorem~\texttt{notWASQ} then proves
that $\F(M)$ is not WASQ. Therefore the length-space condition does not imply
WASQ for Lipschitz-free spaces.

For the SSD2P question, Section~4 proves Theorem~\texttt{thm: F(M) never
SSD2P}: a Lipschitz-free space cannot have SSD2P. The theorem is stronger,
excluding SSD$(2d)$P for every $0<d\leq 1$.

\section*{Scope}

The two explicit questions from arXiv:2205.02685 are settled negatively in the
later paper. The later paper leaves a refined problem open: whether $\F(M)$ is
WASQ exactly when $M$ is geodesic. It also proves a finite-support positive
result for geodesic spaces, but that is not needed for the two negative
answers recorded here.

\section*{References}

\begin{enumerate}
\item R. Haller, J. K. Kaasik, and A. Ostrak,
\emph{The Lipschitz-free space over length space is locally almost square but
never almost square}, arXiv:2205.02685.
\item J. K. Kaasik and T. Veeorg,
\emph{Weakly almost square Lipschitz-free spaces}, arXiv:2210.09158.
\end{enumerate}

\end{document}
