\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{Literature Status for Selected Tingley Problems in arXiv:1712.09192}
\author{agent\_lane\_16}
\date{2026-06-28}

\begin{document}
\sloppy
\maketitle

\section*{Status}

This is a lightweight literature-implied answer packet. It records that two
parts of the problem list in Mori's paper ``Tingley's problem through the facial
structure of operator algebras'' (arXiv:1712.09192) are answered by later or
parallel literature:
\begin{itemize}
  \item the reduction problem for unital C$^*$-algebras is answered by
  Mori--Ozawa, arXiv:1804.10674;
  \item the Schatten-class subcase of the noncommutative $L^p$ problem is
  answered by Fernandez-Polo--Jorda--Peralta, arXiv:1803.00763.
\end{itemize}
The general self-adjoint part problem for unital C$^*$-algebras and the full
Haagerup $L^p(M)$ problem for arbitrary von Neumann algebras are not settled by
this packet.

\section*{Source Problems}

In Section 6 of arXiv:1712.09192, the source asks:
\begin{quote}
Let $A$ be a unital C$^*$-algebra and
$\Phi:S(A)\to S(A)$ be a surjective isometry. Suppose that
$\Phi(x)=x$ for every $x\in S(A)\cap A^{-1}$. Is $\Phi$ equal to the
identity mapping on $S(A)$?
\end{quote}
The same section asks Tingley's problem for the spaces $A_{sa}$ of
self-adjoint elements in unital C$^*$-algebras, and for Haagerup
noncommutative $L^p$-spaces $L^p(M)$, $1<p<\infty$, $p\ne 2$.

\section*{Supporting Literature}

Mori--Ozawa, ``Mankiewicz's theorem and the Mazur--Ulam property for
C$^*$-algebras'' (arXiv:1804.10674), prove as Theorem~\texttt{thm:mau} that
every unital complex C$^*$-algebra, regarded as a real Banach space, has the
Mazur--Ulam property. Hence any surjective sphere isometry
$\Phi:S(A)\to S(A)$ extends to a real linear surjective isometry $L:A\to A$.
If $\Phi$ fixes all invertible norm-one elements, then $L$ fixes every unitary.
By the Russo--Dye theorem, the closed convex hull of the unitary group is the
closed unit ball, so $L$ is the identity on the ball and therefore
$\Phi=\mathrm{id}$ on the sphere. This answers the source's
\texttt{problem-C*}; the source itself notes after submission that Mori and
Ozawa announced results containing an affirmative solution.

Fernandez-Polo--Jorda--Peralta, ``Tingley's problem for $p$-Schatten von
Neumann classes'' (arXiv:1803.00763), state in the abstract that for complex
Hilbert spaces $H,H'$ and $p\in(1,\infty)\setminus\{2\}$ every surjective
isometry
\[
  \Delta:S(C_p(H))\to S(C_p(H'))
\]
extends to a complex linear or conjugate linear surjective isometry between
the Schatten classes. This is the $M=B(H)$, standard trace, Schatten-class
subcase of the source's noncommutative $L^p$ problem.

\section*{Scope and Search Evidence}

Cheap run-index search found nearby Tingley/Mazur--Ulam packets but no existing
packet for arXiv:1712.09192. Local source search found arXiv:1804.10674 and
arXiv:1803.00763 as decisive supporting papers. Web search on 2026-06-28 for
the source title, Mori--Ozawa C$^*$ MUP, self-adjoint C$^*$ Tingley, and
noncommutative $L^p$ Tingley confirmed the source and the Mori--Ozawa follow-up
but did not reveal a full later solution of the remaining two general problems.

\end{document}
