\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\title{A Literature-Implied Partial Answer to Fremlin's Problem DU}
\author{Run fa\_banach\_001, lane 3}
\date{June 23, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a literature-implied partial answer to Fremlin's Problem DU as recorded
in Aviles--Plebanek--Rodriguez, arXiv:1001.4896 \cite{APR2010}. The supporting
result is due to Dodos--Kanellopoulos, arXiv:0805.2031 \cite{DK2008}. The
identification is agent-made: the supporting paper studies Fremlin's filling
families over the Cantor set, but the source paper still records the arbitrary
uncountable-set version as open.

\section*{Source Problem}

The source paper defines an \(\varepsilon\)-filling family on a set \(S\) to be
a hereditary family \(\mathcal F\subset [S]^{<\omega}\) such that for every
finite \(H\subset S\) there is \(F\in\mathcal F\) with
\[
  F\subset H,\qquad |F|\ge \varepsilon |H|.
\]
It calls \(\mathcal F\) compact when \(\{1_F:F\in\mathcal F\}\) is compact in
\(2^S\), and records Fremlin's Problem DU:

\begin{quote}
Are there compact \(\varepsilon\)-filling families on uncountable sets?
\end{quote}

\section*{Supporting Theorem}

Dodos--Kanellopoulos prove that if \(\mathcal F\) is an
\(\varepsilon\)-filling family over the Cantor set \(\mathcal C\) and
\(\mathcal F\) is \(C\)-measurable in \([\mathcal C]^{<\omega}\), then for
every perfect \(P\subset\mathcal C\) there is a perfect \(Q\subset P\) such
that
\[
  [Q]^{<\omega}\subset \mathcal F.
\]
In particular, they note that every \(C\)-measurable
\(\varepsilon\)-filling family over \(\mathcal C\) is not compact.

\section*{Implication}

There is no compact \(\varepsilon\)-filling family on any set \(S\) with
\(|S|\ge\mathfrak c\).

Indeed, suppose \(\mathcal F\subset [S]^{<\omega}\) is compact and
\(\varepsilon\)-filling. Choose \(T\subset S\) with \(|T|=\mathfrak c\). The
restriction
\[
  \mathcal F_T=\{F\in\mathcal F:F\subset T\}
\]
is compact in \(2^T\), hereditary, and \(\varepsilon\)-filling over \(T\).
Transport \(\mathcal F_T\) by a bijection between \(T\) and the Cantor set
\(\mathcal C\). This gives a compact \(\varepsilon\)-filling family
\(\mathcal G\subset[\mathcal C]^{<\omega}\).

Compactness in \(2^{\mathcal C}\) makes \(\mathcal G\) \(C\)-measurable in
\([\mathcal C]^{<\omega}\). By Dodos--Kanellopoulos, there is a perfect
infinite \(Q\subset\mathcal C\) such that \([Q]^{<\omega}\subset\mathcal G\).
But then the net of finite subsets of \(Q\), directed by inclusion, converges
pointwise in \(2^{\mathcal C}\) to the infinite set \(Q\). Since \(\mathcal G\)
is compact, hence closed in \(2^{\mathcal C}\), it would contain \(Q\), a
contradiction to \(\mathcal G\subset[\mathcal C]^{<\omega}\).

\section*{Scope}

This gives a negative answer to Problem DU for all sets of cardinality at least
\(\mathfrak c\). In particular, under the Continuum Hypothesis, every
uncountable set has cardinality at least \(\mathfrak c\), so Problem DU has a
negative answer under CH.

The arbitrary ZFC problem remains open for possible uncountable sets of
cardinality strictly below \(\mathfrak c\). This packet therefore belongs in
the literature-implied partial-answer bucket, not in full solutions.

\section*{References}

\begin{thebibliography}{9}

\bibitem{APR2010}
A.~Aviles, G.~Plebanek, and J.~Rodriguez,
\emph{The McShane integral in weakly compactly generated spaces},
arXiv:1001.4896.

\bibitem{DK2008}
P.~Dodos and V.~Kanellopoulos,
\emph{On filling families of finite subsets of the Cantor set},
arXiv:0805.2031.

\end{thebibliography}

\end{document}
