\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\hypersetup{hidelinks}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\om}{\omega}
\newcommand{\cWG}{\mathcal{W G}}

\title{Nonconcave moduli in the Whitney-Glaeser theorem}
\author{arXiv automatic math run \texttt{fa\_banach\_001}}
\date{2026-06-18}

\begin{document}
\maketitle

\section*{Source and target}

The source paper is Johanis, Krystof, and Zajicek,
\emph{On Whitney-type extension theorems on Banach spaces for
\(C^{1,\omega}\), \(C^{1,+}\), \(C_{\mathrm{loc}}^{1,+}\), and
\(C_{\mathrm B}^{1,+}\)-smooth functions}, arXiv:2305.19995
\cite{JKZ2305}.  Its Theorem~\texttt{t:ext\_C1om} proves a
Whitney-Glaeser extension theorem for concave finite moduli \(\omega\).  In
Remark~\texttt{r:moduli\_nonconc}, the authors explain that the theorem also
holds for some nonconcave moduli: it is enough that there are a concave
modulus \(\psi\) and a constant \(K>0\) such that
\[
        \psi\leq \omega\leq K\psi .
\]
They then ask whether this condition is necessary.

\section*{Result}

The answer is yes, for the sufficiency direction with the derivative
interpolation conclusion of Theorem~\texttt{t:ext\_C1om}.  Thus the sufficient
condition in Remark~\texttt{r:moduli\_nonconc}(b) is also necessary.

\begin{theorem}
\label{thm:main}
Let \(\omega\in\mathcal M\) be a nonzero finite modulus.  Consider the
following one-dimensional Whitney-Glaeser principle \(P_\omega(\R)\): for
every \(E\subset\R\), every \(f:E\to\R\), and every \(G:E\to\R\) satisfying
condition \(\mathcal{W G}\omega\), there is \(F\in C^{1,\omega}(\R)\) such
that \(F=f\) and \(F'=G\) on \(E\).

Then \(P_\omega(\R)\) holds if and only if there are a concave modulus
\(\psi\in\mathcal M\) and a constant \(K>0\) such that
\[
        \psi\leq \omega\leq K\psi .
\]
Consequently, the source theorem can hold with derivative interpolation on its
Banach-space class only under this same condition, since that class contains
the line.
\end{theorem}

\section*{Proof Intuition}

To force a lower bound on any possible extension modulus, put a very sparse
Whitney datum on a line.  At dyadic scale \(2^k\), use two points distance
\(2^k\) apart, set both function values equal to zero, and prescribe derivative
values whose jump is exactly \(\omega(2^k)\).  The pairs are placed so far
apart that all cross-pair Whitney inequalities are harmless.

If an extension \(F\in C^{1,\omega}\) interpolates these derivatives, the
minimal modulus \(m\) of \(F'\) satisfies
\[
        m(2^k)\geq \omega(2^k)\quad(k\in\mathbb Z),
        \qquad     m\leq C\omega .
\]
The modulus \(m\) is subadditive.  Stechkin's concavification lemma then
produces a concave \(\theta\) with \(m\leq\theta\leq2m\).  The dyadic lower
bound and concavity imply \(\theta(t)\geq \frac12\omega(t)\) for every
\(t>0\), while \(\theta\leq2C\omega\).  A rescaling of \(\theta\) is the
desired concave modulus comparable to \(\omega\).

\section*{Proof}

The sufficiency direction is exactly the observation made in the source paper:
if \(f\) satisfies \(\mathcal{W G}\omega\) and
\(\psi\leq\omega\leq K\psi\) with \(\psi\) concave, then \(f\) satisfies
\(\mathcal{W G}\psi\), after increasing the Whitney constant.  The concave
case of Theorem~\texttt{t:ext\_C1om} gives an extension
\(F\in C^{1,\psi}(X)\subset C^{1,\omega}(X)\), with \(DF=G\) on \(E\).

It remains to prove necessity.  Suppose \(P_\omega(\R)\) holds.  The source paper
already observes in Remark~\texttt{r:moduli\_nonconc}(a) that this implies
that \(\omega\) dominates a nonzero concave modulus.  In particular
\(\omega(t)>0\) for every \(t>0\).

Set \(r_k=2^k\), \(k\in\mathbb Z\).  We first choose pair locations
\[
        a_k<b_k,\qquad b_k-a_k=r_k ,
\]
with the following separation property: there is \(M\geq1\) such that whenever
\(k\neq j\), \(u\in\{a_k,b_k\}\), and \(v\in\{a_j,b_j\}\),
\[
\label{eq:sep}
        \max\{\omega(r_k),\omega(r_j)\}\leq
        M\,\omega(|u-v|).
\tag{1}
\]
This is immediate by induction.  If \(\omega\) is unbounded, take \(M=1\) and
place each new pair far enough from the finitely many old pairs.  If
\(\omega\) is bounded, let \(L=\sup_{t\geq0}\omega(t)\), choose \(d_0>0\), and
take \(M\geq L/\omega(d_0)\); placing distinct pairs at distance at least
\(d_0\) gives \eqref{eq:sep}.

Let \(X=\R\), let
\[
        E=\{a_k,b_k:k\in\mathbb Z\},
\]
and define
\[
        f\equiv0,\qquad
        G(a_k)=0,\qquad
        G(b_k)=\omega(r_k)
\]
where \(G(x)\in X^*\cong\R\).  We claim that this datum satisfies
\(\mathcal{W G}\omega\).  If \(x,y\) are the two points of the same dyadic
pair, then \(|x-y|=r_k\) and the required estimates hold with constant
\(\max\{M,1\}\).  If \(x,y\) belong to different pairs, \eqref{eq:sep} gives
\[
        |G(x)-G(y)|\leq M\omega(|x-y|)
\]
and also
\[
        |f(y)-f(x)-G(x)(y-x)|
        = |G(x)|\,|y-x|
        \leq M\omega(|x-y|)\,|x-y|.
\]
Thus \(f\) satisfies \(\mathcal{W G}\omega\) on \(E\).

By \(P_\omega(\R)\), there exists \(F\in C^{1,\omega}(\R)\) such that
\[
        F=f,\qquad F'=G\quad\text{on }E .
\]
Let \(m\) be the minimal modulus of continuity of \(F'\):
\[
        m(t)=\sup\{|F'(s)-F'(u)|: |s-u|\leq t\}.
\]
Since \(F'\) is uniformly continuous on the convex set \(\R\), \(m\) is a
finite subadditive modulus.  Also, because \(F\in C^{1,\omega}(\R)\), there is
\(C>0\) such that
\[
        m(t)\leq C\omega(t)\qquad(t\geq0).
\]
On the other hand, for each \(k\in\mathbb Z\),
\[
        m(r_k)\geq |F'(b_k)-F'(a_k)|=\omega(r_k).
\]

By Stechkin's concavification lemma, as quoted in Lemma~\texttt{l:Steckin}(iii)
of the source paper, there is a concave modulus \(\theta\) such that
\[
        m\leq\theta\leq2m .
\]
Hence \(\theta\leq2C\omega\).  For the reverse estimate, fix \(t>0\) and
choose \(k\in\mathbb Z\) with \(r_k\leq t<r_{k+1}=2r_k\).  Since
\(\theta\) is concave, nondecreasing, and \(\theta(0)=0\),
\[
        \theta(t)\geq \frac{t}{r_{k+1}}\theta(r_{k+1})
        \geq \frac{1}{2}\omega(r_{k+1})
        \geq \frac{1}{2}\omega(t).
\]
Therefore
\[
        \frac{1}{2}\omega\leq\theta\leq2C\omega .
\]
Putting \(\psi=(2C)^{-1}\theta\), we get a concave modulus with
\[
        \psi\leq\omega\leq4C\,\psi .
\]
This proves the necessity and hence the theorem.

\section*{Scope and verification notes}

This packet answers only Remark~\texttt{r:moduli\_nonconc}; it does not address
the paper's other open remarks on relaxing the smoothness assumption on \(X\),
removing the extra hypotheses in Corollary~\texttt{c:extC1+-quasic}, or
extensions from bounded convex sets in nonsuperreflexive spaces.

The proof uses only one-dimensional data, the derivative-interpolation part of
the Whitney-Glaeser conclusion, and the same Stechkin concavification lemma
already used in the source paper.  Local index search found no existing packet
or attempt for arXiv:2305.19995.  Local parsed-source search found only the
original open remark.  Web search on 2026-06-18 found the source paper and the
later arXiv:2507.09384 follow-up, but no answer to this nonconcave-modulus
question.

\begin{thebibliography}{9}

\bibitem{JKZ2305}
M. Johanis, V. Krystof, and L. Zajicek.
\newblock \emph{On Whitney-type extension theorems on Banach spaces for
\(C^{1,\omega}\), \(C^{1,+}\), \(C_{\mathrm{loc}}^{1,+}\), and
\(C_{\mathrm B}^{1,+}\)-smooth functions}.
\newblock arXiv:2305.19995, 2023.

\end{thebibliography}

\end{document}
