\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\emergencystretch=2em

\title{Literature Status for arXiv:1006.1546: Intersection-Body Fixed Points}
\author{Run fa\_banach\_001, agent\_lane\_03}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet.  It records that the
fixed-point question for the intersection body operator quoted in
Kim--Yaskin--Zvavitch, \emph{The geometry of \(p\)-convex intersection
bodies}, arXiv:1006.1546, is answered by Milman--Shabelman--Yehudayoff,
\emph{Fixed and Periodic Points of the Intersection Body Operator},
arXiv:2408.08171.

\section*{Source Question}

On PDF page 2 of arXiv:1006.1546, the authors recall a question about the
intersection body operator \(I\), citing Lutwak and Gardner.  Since a Euclidean
ball is mapped by \(I\) to a Euclidean ball, they ask whether there are other
fixed points of \(I\).  They note that Fish--Nazarov--Ryabogin--Zvavitch had
proved only a local uniqueness result in a sufficiently small Banach--Mazur
neighborhood of the ball, and that the general question was still open.

The same paragraph then asks whether \(IK\) must be closer to the Euclidean
ball than \(K\).  That second, distance-improvement question is answered
negatively in arXiv:1006.1546 itself; it is not the literature-status claim of
this packet.

\section*{Supporting Answer}

The abstract of arXiv:2408.08171 states that, when \(n\geq 3\),
\[
  I^2K=cK \quad\text{if and only if}\quad K
  \text{ is a centered ellipsoid},
\]
and hence
\[
  IK=cK \quad\text{if and only if}\quad K
  \text{ is a centered Euclidean ball}.
\]
On PDF page 2, Theorem~1.1 gives the \(I^2\) classification and
Corollary~1.2 gives the fixed-point classification for \(I\).  The authors
explicitly say that Corollary~1.2 provides a complete answer to Gardner's
fixed-point question and to the Fish--Nazarov--Ryabogin--Zvavitch question
about fixed points of \(I:\mathcal S_n\to\mathcal S_n\) when \(n\geq 3\).

\section*{Scope}

This answers the fixed-point branch quoted in the source paper for star bodies
in dimensions \(n\geq 3\).  The two-dimensional case is exceptional: the later
paper notes that \(I^2K=4K\) for every origin-symmetric star body in
\(\mathbb R^2\), and \(IK=2K\) for bodies invariant under a quarter-turn.  The
source paper's separate question about whether \(IK\) improves Banach--Mazur
distance to the Euclidean ball is a same-paper negative result and is not
counted here as a separate literature answer.

\section*{Search Evidence}

The lane-3 queue selected arXiv:1006.1546.  Cheap run indexes were searched for
the arXiv id, \texttt{2408.08171}, \texttt{intersection body fixed points},
\texttt{p-convex intersection bodies}, \texttt{Lutwak}, and \texttt{Gardner};
no duplicate packet for this source relation was found.  Local corpus search
and targeted web search for \texttt{fixed points intersection body operator}
identified arXiv:2408.08171 as the decisive later source.

{\raggedright
\begin{thebibliography}{9}

\bibitem{KYZ10}
J.~Kim, V.~Yaskin, and A.~Zvavitch,
\emph{The geometry of \(p\)-convex intersection bodies},
arXiv:1006.1546.

\bibitem{MSY24}
E.~Milman, S.~Shabelman, and A.~Yehudayoff,
\emph{Fixed and Periodic Points of the Intersection Body Operator},
arXiv:2408.08171.

\end{thebibliography}
}

\end{document}
