\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newcommand{\Cu}{\mathrm{C}^*_u}
\newcommand{\K}{\mathcal K}
\newcommand{\elltwo}{\ell_2}

\title{Literature-Implied Answer To A C*-Case Isometry Rigidity Question}
\author{Run fa\_banach\_001}
\date{Updated 2026-07-03}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature-implied answer, partial C*-subcase, with the strengthened conclusion of bijective coarse equivalence.

\textbf{Source question:} Bruno M. Braga, \emph{On Banach algebras of band-dominated operators and their order structure}, arXiv:2003.11567.  The relevant questions appear in Section 7, ``Open questions'', as Problem 7.1 (source TeX label \texttt{Prob2}) and the following C*-case Problem 7.2 (source TeX label \texttt{ProblemIsometryRig}).

\textbf{Supporting theorems:} Florent P. Baudier, Bruno M. Braga, Ilijas Farah, Ana Khukhro, Alessandro Vignati, and Rufus Willett, \emph{Uniform Roe algebras of uniformly locally finite metric spaces are rigid}, arXiv:2106.11391, proved that $*$-isomorphism of uniform Roe algebras implies coarse equivalence.  Alessandro Vignati, \emph{The rigidity problem for uniform Roe algebras}, arXiv:2602.01998, strengthens this as Theorem~\texttt{thmi:main}: if $X$ and $Y$ are uniformly locally finite metric spaces and $\Cu(X)$ and $\Cu(Y)$ are $*$-isomorphic, then $X$ and $Y$ are bijectively coarsely equivalent.

\section*{Source Question}

Problem 7.1 of arXiv:2003.11567 asks whether, for uniformly locally finite metric spaces $(\mathbb N,d)$ and $(\mathbb N,\partial)$ and strictly convex Banach spaces with $1$-symmetric bases, a Banach-space isometry
\[
  B_u(d,\mathcal E) \cong B_u(\partial,\mathcal F)
\]
forces the two metric spaces to be coarsely equivalent.  The paper explicitly notes that this is open even in the Hilbert case $E=\ell_2$ with its standard basis.  The subsequent Problem 7.2 asks, for uniformly locally finite metric spaces $X,Y$, whether the following two hypotheses imply coarse equivalence:
\[
  \Cu(X) \text{ and } \Cu(Y) \text{ are isometric as Banach spaces,}
\]
and
\[
  \Cu(X) \text{ and } \Cu(Y) \text{ are isomorphic as ordered Banach spaces.}
\]

\section*{Identification}

Under the standard complex-linear reading of ``isometric as Banach spaces'', the C*-case has a positive answer.  Indeed, let
\[
  T:\Cu(X)\to \Cu(Y)
\]
be a surjective complex-linear isometry.  Kadison's theorem on isometries of C*-algebras says that $u=T(1)$ is a unitary and
\[
  J(a)=u^*T(a)
\]
is a unital Jordan $*$-isomorphism.

The uniform Roe algebra $\Cu(Y)$ contains $\K(\elltwo(Y))$ as an essential simple ideal.  Therefore $\Cu(Y)$ is prime: every nonzero closed ideal intersects $\K(\elltwo(Y))$ nontrivially, hence contains $\K(\elltwo(Y))$, so two nonzero closed ideals cannot have zero product.  A standard structure theorem for Jordan $*$-homomorphisms then implies that a Jordan $*$-isomorphism onto a prime C*-algebra is either a $*$-isomorphism or a $*$-anti-isomorphism.

If $J$ is multiplicative, $J:\Cu(X)\to \Cu(Y)$ is already a $*$-isomorphism.  If $J$ is anti-multiplicative, compose it with the transpose anti-automorphism
\[
  \tau_Y([a_{yz}])=[a_{zy}]
\]
of $\Cu(Y)$.  This transpose preserves finite propagation and hence preserves the norm closure defining $\Cu(Y)$.  Thus $\tau_Y\circ J$ is a $*$-isomorphism from $\Cu(X)$ onto $\Cu(Y)$.

In either case, $\Cu(X)$ and $\Cu(Y)$ are $*$-isomorphic.  Theorem~\texttt{thmi:main} of Vignati's 2026 paper then gives that $X$ and $Y$ are bijectively coarsely equivalent.  The earlier theorem of Baudier--Braga--Farah--Khukhro--Vignati--Willett already gave coarse equivalence; the later theorem upgrades the conclusion to the bijective form.

\section*{Conclusion And Scope}

The C*-subcase of Problem 7.1 has a positive literature-implied answer:
\[
  \begin{gathered}
  \Cu(X)\cong \Cu(Y)\quad\text{isometrically as complex Banach spaces}\\
  \Longrightarrow\quad
  X \text{ and } Y \text{ are bijectively coarsely equivalent.}
  \end{gathered}
\]
Consequently, Problem 7.2 has a positive answer, and its additional ordered Banach space isomorphism hypothesis is not needed in the C*-case.

This does not settle the full Problem 7.1 for arbitrary strictly convex Banach spaces with $1$-symmetric bases.  The argument uses Kadison's C*-algebraic isometry theorem and the later unconditional rigidity theorem for uniform Roe C*-algebras.

\section*{Search Evidence}

The relation is agent-identified rather than explicitly advertised by the supporting papers as an answer to the exact source problem.  The cheap run indexes were searched for arXiv:2003.11567, arXiv:2602.01998, the paper titles, ``band-dominated operators'', ``uniform Roe'', ``isometric as Banach spaces'', ``bijective coarse equivalence'', and ``order structure''.  The prior version of this packet used arXiv:2106.11391 for coarse equivalence; the present update adds arXiv:2602.01998, whose abstract and Theorem~\texttt{thmi:main} provide the strengthened bijective rigidity conclusion after the Kadison/Jordan reduction.

\begin{thebibliography}{9}

\bibitem{Braga2021}
B. M. Braga,
\emph{On Banach algebras of band-dominated operators and their order structure},
J. Funct. Anal. 280 (2021), no. 9, Paper No. 108958; arXiv:2003.11567.

\bibitem{BBFKVW2022}
F. P. Baudier, B. M. Braga, I. Farah, A. Khukhro, A. Vignati, and R. Willett,
\emph{Uniform Roe algebras of uniformly locally finite metric spaces are rigid},
Invent. Math. 230 (2022), 1071--1100; arXiv:2106.11391.

\bibitem{Vignati2026}
A. Vignati,
\emph{The rigidity problem for uniform Roe algebras},
arXiv:2602.01998, 2026.

\bibitem{Kadison1951}
R. V. Kadison,
\emph{Isometries of operator algebras},
Ann. of Math. (2) 54 (1951), 325--338.

\end{thebibliography}

\end{document}
