\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\R}{\mathbb R}
\newcommand{\ellp}{\ell_p^2}
\newcommand{\norm}[1]{\left\|#1\right\|}

\title{A Partial Result on the Davis-Wielandt Index}
\author{fa\_banach\_001, agent\_lane\_17}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Source Question}

Bhunia, Sain and Paul introduced the Davis-Wielandt index
\[
  \eta_{dw}(X)=\inf\{dw(T): T\in S_{\mathcal L(X)}\}
\]
of a normed linear space \(X\). At the end of arXiv:2006.15323 they ask for
separate complete characterizations of the properties
\[
  \eta_{dw}(X)=1
  \qquad\text{and}\qquad
  \eta_{dw}(X)=\sqrt{n(X)^2+1},
\]
where \(n(X)\) is the numerical index.

\section*{Result}

We record a concrete family for the first property.

\begin{theorem}
Let \(X=(\R^2,\norm{\cdot}_p)=\ell_p^2\) be real. If \(2\le p\le 8\), then
\[
  \eta_{dw}(X)=1.
\]
\end{theorem}

\section*{Proof Intuition}

The Davis-Wielandt index is always at least \(1\). Thus it is enough to find
one norm-one operator whose Davis-Wielandt radius is \(1\). On \(\ell_p^2\),
the natural candidate is the rank-one nilpotent \(T(a,b)=(0,a)\). At the
point \((1,0)\), \(T\) attains its norm and the unique norming functional
annihilates \(T(1,0)\), exactly as for a skew-symmetric Hilbert-space
operator. The only issue is to control all other unit vectors; this reduces
to a one-variable inequality with a sharp endpoint at \(p=8\).

\section*{Scalar Inequality}

\begin{lemma}
For \(1\le r\le 4\) and \(0\le s\le 1\),
\[
  s(1-s^r)^{2-1/r}+s^2\le 1.
\]
\end{lemma}

\begin{proof}
If \(1\le r\le 2\), then \(s^r\ge s^2\), hence
\[
  (1-s^r)^{2-1/r}\le 1-s^r\le 1-s^2,
\]
because \(2-1/r\ge 1\). Multiplying by \(s\le 1\) gives the result.

It remains to consider \(2\le r\le 4\). Put \(a=1/r\), so
\(a\in[1/4,1/2]\), and set \(y=s^r\). The desired inequality is
\[
  H_a(y):=1-y^{2a}-y^a(1-y)^{2-a}\ge 0.
\]
We first note that \(H_a(y)\) is increasing in \(a\) on
\([1/4,1/2]\). Indeed,
\[
  \frac{\partial H_a(y)}{\partial a}
  =2y^{2a}\log(1/y)
   -y^a(1-y)^{2-a}\log\frac{y}{1-y}.
\]
For \(0<y\le 1/2\) this is non-negative. For \(1/2<y<1\), write
\(\rho=(1-y)/y\in(0,1)\). Since \(2a\le 1\) and \(2-a\ge 3/2\),
\[
\frac{\partial H_a(y)}{\partial a}
\ge
\frac{2\log(1+\rho)-\rho^{3/2}\log(1/\rho)}{(1+\rho)^2}.
\]
Now \(2\log(1+\rho)\ge \rho\), while
\(\rho^{3/2}\log(1/\rho)\le \rho\), since
\(\sqrt{\rho}\log(1/\rho)\le 2/e<1\). Hence the derivative is non-negative.

It is therefore enough to prove the endpoint \(a=1/4\):
\[
  y^{1/4}(1-y)^{7/4}+y^{1/2}\le 1.
\]
Writing \(v=y^{1/4}\), this is equivalent to
\[
  v(1-v^4)^{7/4}\le 1-v^2.
\]
After raising to the fourth power and putting \(u=v^2\), it suffices to show
\[
  P(u):=u^2(1-u)^3(1+u)^7\le 1,\qquad 0\le u\le 1.
\]
The logarithmic derivative of \(P\) is
\[
  \frac{2}{u}-\frac{3}{1-u}+\frac{7}{1+u}
  =
  \frac{2+4u-12u^2}{u(1-u)(1+u)}.
\]
Thus the only interior maximum occurs at \(u=(1+\sqrt 7)/6\), and direct
substitution gives \(P(u)<0.619<1\). Since \(P(0)=P(1)=0\), the endpoint case
and the lemma follow.
\end{proof}

\section*{Proof of the Theorem}

Let \(T:\ell_p^2\to\ell_p^2\) be
\[
  T(a,b)=(0,a).
\]
Clearly \(\norm{T}=1\). Since \(p>1\), each non-zero point of \(\ell_p^2\)
has a unique norming functional. If \(x=(a,b)\in S_{\ell_p^2}\), then
\[
  x^\#=(\operatorname{sgn}(a)|a|^{p-1},
        \operatorname{sgn}(b)|b|^{p-1})\in S_{(\ell_p^2)^*}
\]
is the unique element of \(\mathcal J(x)\). Therefore
\[
  |x^\#(Tx)|^2+\norm{Tx}^4
  =
  |a|^2|b|^{2p-2}+|a|^4.
\]
Put \(s=|a|^2\) and \(r=p/2\). Since \(2\le p\le 8\), we have
\(1\le r\le 4\), and since \(|a|^p+|b|^p=1\),
\[
  |a|^2|b|^{2p-2}+|a|^4
  =
  s(1-s^r)^{2-1/r}+s^2
  \le 1
\]
by the lemma. Hence \(dw(T)\le 1\). At \(x=(1,0)\), the unique norming
functional is \(x^\#=(1,0)\), and
\[
  |x^\#(Tx)|^2+\norm{Tx}^4=0+1=1,
\]
so \(dw(T)=1\).

The source paper proves \(\eta_{dw}(X)\ge 1\) for every normed space \(X\).
Since \(T\in S_{\mathcal L(X)}\) and \(dw(T)=1\), we conclude
\[
  \eta_{dw}(\ell_p^2)=1.
\]
\end{document}
