\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}

\newcommand{\SSing}{\mathcal{SS}}
\newcommand{\LLop}{\mathcal{L}}
\newcommand{\Sch}{\mathcal{S}}
\newcommand{\Bell}{\mathcal{B}}
\newcommand{\ellp}{\ell_p}

\begin{document}

\begin{center}
{\Large Literature status: the strictly singular Borel converse}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:0908.1113}
\end{center}

\section*{Source question}

Beanland's paper \emph{An Ordinal Index on the Space of Strictly Singular
Operators} proves that if \(X\) and \(Y\) are separable Banach spaces and
\(\Bell(\SSing(X,Y))\) is Borel in \(\Bell(\LLop(X,Y))\), then there is a
countable ordinal \(\xi\) such that
\[
  \SSing_\xi(X,Y)=\SSing(X,Y).
\]
In Section 4.5, ``Future Research and Concluding Remarks'', the paper asks
whether the converse holds:

\begin{quote}
Suppose \(X\) and \(Y\) are separable Banach spaces and there is an
\(\xi<\omega_1\) such that
\(\SSing_\xi(X,Y)=\SSing(X,Y)\).  Is
\(\Bell(\SSing(X,Y))\) a Borel subset of \(\Bell(\LLop(X,Y))\)?
\end{quote}

The source states that this problem was communicated by S. Argyros and
conjectures a positive answer.

\section*{Supporting literature status}

Beanland and Dodos' later paper \emph{On strictly singular operators between
separable Banach spaces}, arXiv:1006.2672, explicitly restates this conjecture.
In its introduction it says that the conjecture appears in \cite[\S 4.5]{Beanland}
and that its second main result answers the question negatively.

The relevant theorem is Theorem 4 of \cite{BeanlandDodos}:

\begin{theorem}[Beanland--Dodos, arXiv:1006.2672, Theorem 4]
For every \(1\le p<\infty\) there is a Banach space \(Y_p\) with an
unconditional basis such that:
\begin{enumerate}
\item \(\SSing(\ell_p,Y_p)\) is a complete coanalytic, in particular non-Borel,
subset of \(\LLop(\ell_p,Y_p)\).
\item If \(T:\ell_p\to Y_p\) is strictly singular, then \(\varrho(T)\le 2\).
\end{enumerate}
\end{theorem}

\section*{Why this answers the source question}

Definition 1 of \cite{BeanlandDodos} is the same Schreier refinement used in
the source paper: \(T\) is \(\Sch_\xi\)-strictly singular if every normalized
basic sequence and every \(\varepsilon>0\) admit a non-empty
\(F\in\Sch_\xi\) and a unit vector in the corresponding finite span on which
\(T\) has norm at most \(\varepsilon\).  The rank is
\[
  \varrho(T)=\inf\{\xi:T\text{ is }\Sch_\xi\text{-strictly singular}\}.
\]
Thus \(\varrho(T)\le 2\) for every strictly singular \(T:\ell_p\to Y_p\)
implies
\[
  \SSing_2(\ell_p,Y_p)=\SSing(\ell_p,Y_p).
\]
At the same time, Theorem 4 says that \(\SSing(\ell_p,Y_p)\) is complete
coanalytic and therefore not Borel.  This gives separable spaces \(X=\ell_p\)
and \(Y=Y_p\) for which the Schreier index is bounded by \(2\), but the
strictly singular set is non-Borel.  The answer to the source question is
therefore negative.

\section*{Verification notes and limitations}

This packet records a known literature answer, not a new proof.  The
supporting paper explicitly identifies the source conjecture by citing
\cite[\S 4.5]{Beanland}.  The statement in arXiv:1006.2672 is formulated for
\(\LLop(\ell_p,Y_p)\) as a standard Borel space.  Since the source paper uses
the operator unit ball \(\Bell(\LLop(X,Y))\), one can restrict the complete
coanalytic example to suitable norm balls, or equivalently rescale operators;
the non-Borel obstruction is not removed by the unit-ball formulation.

The result does not classify all bounded-index pairs \((X,Y)\).  It only
settles the general converse question negatively.

\section*{Human review recommendation}

Treat arXiv:0908.1113 Section 4.5 as already answered negatively by
arXiv:1006.2672.  This packet should prevent duplicate work on the same
question, but it should not be counted as an original proof from this run.

\begin{thebibliography}{9}

\bibitem{Beanland}
K. Beanland,
\emph{An Ordinal Index on the Space of Strictly Singular Operators},
arXiv:0908.1113.

\bibitem{BeanlandDodos}
K. Beanland and P. Dodos,
\emph{On strictly singular operators between separable Banach spaces},
arXiv:1006.2672.

\end{thebibliography}

\end{document}

