\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Fix}{\operatorname{Fix}}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\dist}{\operatorname{d}}

\begin{document}

\section*{Human Review: Uniform H\"older nonexpansive maps on decomposable balls}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears correct and the method is sound. The key point is that a
previous packet in the run had already produced the required uniformly
Lipschitzian fixed-point-free map with null minimal displacement on \(B_X\) for
every decomposable Banach space
\[
  X=Y\oplus Z,
\]
where both summands are infinite-dimensional. Once this input is available, the
present argument is a clean scaling step which converts uniformly Lipschitzian
dynamics into uniformly \(\alpha\)-H\"older nonexpansive dynamics.

There is also a bibliographic typo in the packet: the source paper is listed as
being by Cleon S. Barroso and Valdir Ferreira, whereas the paper
\emph{H\"older-contractive mappings, nonlinear extension problem and fixed point
free results} is authored only by Cleon S. Barroso.

\section*{Scaling Argument}

Starting with \(U:B_X\to B_X\) such that
\[
  \Fix(U)=\varnothing,\qquad
  \dist(U,B_X)=0,\qquad
  M:=\sup_{n\geq1}\Lip(U^n)<\infty,
\]
the proof compresses the dynamics into a small ball \(rB_X\). The scaled map is
\[
  S(z)=rU(z/r),\qquad z\in rB_X.
\]
It has the same fixed-point-free and null-minimal-displacement properties, and
its iterates remain uniformly Lipschitzian.

The map on the whole unit ball is then
\[
  V=S R_r,
\]
where \(R_r:B_X\to rB_X\) is the radial retraction. Since \(R_r\) is
\(2\)-Lipschitz and \(S(rB_X)\subseteq rB_X\), one obtains
\[
  V^n=S^nR_r
\]
and therefore
\[
  \|V^n x-V^n y\|
  \leq
  \min\{2M\|x-y\|,2r\}.
\]
Choosing \(r\) sufficiently small gives
\[
  \min\{2M d,2r\}\leq d^\alpha
  \qquad(0\leq d\leq2),
\]
which is exactly the uniformly \(\alpha\)-H\"older nonexpansive estimate
\[
  \|V^n x-V^n y\|\leq \|x-y\|^\alpha
  \qquad(n\geq1).
\]

\section*{Scope of the Result}

The automatic packet correctly observes that the result applies to spaces
isomorphic to Hilbert space and to spaces with an unconditional basis, because
these are decomposable in the required sense.

However, the packet missed one important consequence: the James space case is
also covered. The James space is decomposable, and therefore it falls under the
same theorem. Thus the argument should be recorded not only as answering the
Hilbert-isomorphic and reflexive-unconditional-basis cases, but also as giving
the corresponding affirmative answer for James space.

\section*{Review Outcome}

Archive this packet as an apparently correct solution for all decomposable
Banach spaces covered by the input uniformly Lipschitzian construction. In
particular, it gives affirmative answers in the Hilbert-isomorphic case, the
unconditional-basis case, and the James-space case. The remaining genuinely
unresolved part, from the perspective of this packet, is the arbitrary reflexive
case without an available decomposable uniformly Lipschitzian construction.

\end{document}
