\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,mathrsfs}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\geometry{margin=1in}

\newcommand{\C}{\mathscr C}
\newcommand{\conv}{\operatorname{conv}}

\title{Literature Status: Order-Reversing Operators on Convex Functions}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_05}}
\date{2026-06-18}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet for the self-map branch
of the open problem in Iusem--Reem--Svaiter, arXiv:1212.1120. It is not a new
solution produced by this run.

\section*{Source Question}

In Section 3 of arXiv:1212.1120, after characterizing fully order reversing
maps
\[
  S:\C(X)\to \C_{w^*}(X^*),
\]
Iusem--Reem--Svaiter write that the characterization of fully order reversing
operators
\[
  S:\C(X)\to\C(X)
\]
and, in the nonreflexive case, \(S:\C(X)\to\C(X^*)\), is left as an open
problem. Here \(\C(X)\) denotes the proper lower semicontinuous convex
functions on the Banach space \(X\).

\section*{Answering Paper}

Cheng--Luo, \emph{On order preserving and order reversing mappings defined on
cones of convex functions}, arXiv:1708.06548, explicitly quote this
Iusem--Reem--Svaiter question in their introduction. Their Theorem 1.5 states
that a fully order reversing self-map
\[
  S:\conv(X)\to\conv(X)
\]
exists if and only if \(X\) is reflexive and linearly isomorphic to its dual
\(X^*\). Their Theorem 1.6 gives the normal form: for every such \(S\), there
are a linear isomorphism \(U:X\to X^*\), vectors
\(x_0^*,\varphi_0\in X^*\), a scalar \(\alpha>0\), and \(r_0\in\mathbb R\)
such that
\[
  (Sf)(x)=\alpha\,(\mathcal F f)(Ux+x_0^*)+\langle\varphi_0,x\rangle+r_0,
  \qquad x\in X,
\]
where \(\mathcal F\) is the Fenchel transform.

\section*{Scope}

The later paper explicitly knows it is addressing the Iusem--Reem--Svaiter
open problem: it cites the source, quotes the problem passage, and says that
the resulting theorems resolve the self-map existence and representation
questions. This packet records that identification so the run does not treat
the self-map branch of arXiv:1212.1120 as a fresh open target.

\section*{References}

\begin{itemize}
\item A. N. Iusem, D. Reem, and B. F. Svaiter, \emph{Order preserving and order
reversing operators on the class of convex functions in Banach spaces},
arXiv:1212.1120; J. Funct. Anal. 268 (2015), 73--92.
\item L. Cheng and S. Luo, \emph{On order preserving and order reversing
mappings defined on cones of convex functions}, arXiv:1708.06548.
\end{itemize}

\end{document}
