\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Naor--Young and the Heisenberg \(L_1\) Compression Exponent}
\author{Run \texttt{fa\_banach\_001}, lane 2}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Literature-implied answer, scoped to the main logarithmic exponent.}
This packet is not a new proof.  It records that later work of Naor--Young
identifies the exponent-level answer to the compression-rate question raised
by Cheeger--Kleiner--Naor, while leaving the exact lower-order compression
profile open.

\section*{Source Signal}

The source paper is J. Cheeger, B. Kleiner, and A. Naor,
\emph{Compression bounds for Lipschitz maps from the Heisenberg group to
\(L_1\)}, arXiv:0910.2026 \cite{CKN}.  Theorem 1.1
(\emph{Quantitative central collapse}) gives a universal
\(\delta>0\) such that every \(1\)-Lipschitz \(L_1\)-valued map on a
Heisenberg ball has central pairs with collapse factor at most
\[
  \frac{1}{(\log(1/\varepsilon))^\delta}.
\]
Immediately after the theorem, the authors record that a crude estimate from
their proof is \(\delta=2^{-60}\), and that obtaining the best possible
\(\delta\) remains an open question.

In the compression-rate subsection, Corollary 1.6 states that for every
\(1\)-Lipschitz map \(f:\mathbb H(\mathbb Z)\to L_1\), with respect to a word
metric,
\[
  \omega_f(t)\lesssim \frac{t}{(1+\log t)^\delta}\qquad (t\ge 1),
\]
where \(\omega_f\) is the compression rate.  The following remark asks for the
correct exponent in this Heisenberg-to-\(L_1\) compression gap.

\section*{Supporting Theorem}

The supporting paper is A. Naor and R. Young,
\emph{Foliated corona decompositions}, arXiv:2004.12522 \cite{NY}.  In
Theorem 1.10, item (5), the subgroup \(H\) used in their construction is a
copy of the three-dimensional integer Heisenberg group \(\mathbb H_{\mathbb Z}\).
They construct a Lipschitz map \(f:\mathbb H_{\mathbb Z}\to\ell_1\) whose
compression satisfies
\[
  \omega_f(s)\gtrsim
  \frac{s}{\sqrt[4]{\log s}\,(\log\log s)^2}
  \qquad (s\ge 3).
\]

The same paper's Remark 23 states that the lower-order factor cannot simply
be deleted: there is no Lipschitz map
\(f:\mathbb H_{\mathbb Z}\to\ell_1\), for the word metric, whose compression
rate satisfies
\[
  \omega_f(s)\gtrsim \frac{s}{\sqrt[4]{\log s}}
  \qquad (s\ge 2).
\]

\section*{Identification}

Together, these statements pin down the principal logarithmic exponent in the
\(\mathbb H_{\mathbb Z}\to L_1\) compression problem as \(1/4\), modulo
lower-order factors.  The lower-bound construction gives compression at
\[
  s/((\log s)^{1/4}(\log\log s)^2),
\]
and the endpoint obstruction rules out a uniform compression lower bound of
order \(s/(\log s)^{1/4}\) with no unbounded lower-order loss.  Equivalently,
for every \(\eta>0\), the lower-bound construction gives
\(\omega_f(s)\gtrsim_\eta s/(\log s)^{1/4+\eta}\) eventually, while the
exact \(1/4\) endpoint cannot be attained without some lower-order loss.

This is an agent-identified implication of the later Naor--Young theorem and
remark rather than a statement that the supporting authors explicitly framed
as an answer to this exact sentence of arXiv:0910.2026.

\section*{Scope Limitations}

This packet does not claim that every form of the central-collapse theorem in
\cite{CKN} has an optimal exponent proved in the same formulation.  It records
the compression-rate consequence for the discrete Heisenberg group.  It also
does not give a full characterization of all possible lower-order compression
rates: Naor--Young explicitly state after Remark 23 that obtaining such a
characterization would require additional work.

Local run indexes were searched for arXiv:0910.2026, the source title,
Heisenberg \(L_1\) compression, central collapse, Naor--Young, arXiv:2004.12522,
and \(\sqrt[4]{\log}\).  Nearby packets already record the finite-ball
distortion consequence \(c_1(\mathcal B_n)\asymp(\log n)^{1/4}\), but no exact
prior packet for this compression-rate signal was found.

\section*{Human Review Recommendation}

Accept as a scoped literature-implied answer: the main logarithmic compression
exponent is \(1/4\) up to necessary lower-order loss.  Do not count this as an
original solve, and do not mark the full lower-order compression-profile
problem closed.

\begin{thebibliography}{9}
\bibitem{CKN}
J. Cheeger, B. Kleiner, and A. Naor.
\emph{Compression bounds for Lipschitz maps from the Heisenberg group to
\(L_1\)}. arXiv:0910.2026, 2009.

\bibitem{NY}
A. Naor and R. Young.
\emph{Foliated corona decompositions}. arXiv:2004.12522, 2020.
\end{thebibliography}

\end{document}
