\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}

\title{Literature status: the unbounded Davies--Gaffney--Grigor'yan question for Hodge Laplacians}
\author{fa\_banach\_001, agent\_lane\_08}
\date{2026-07-18}

\begin{document}
\maketitle

\paragraph{Status.}
This packet records a \texttt{literature\_already\_answered} identification.
It is not an original proof from the run.

\paragraph{Original question.}
Bobo Hua and Xin Luo, \emph{Davies--Gaffney--Grigor'yan lemma on simplicial complexes},
arXiv:1702.00529, prove a Davies--Gaffney--Grigor'yan estimate for heat kernels of
bounded discrete Hodge Laplacians on simplicial complexes.  Their Remark 1.1
on page 3 says: ``It will be interesting to know whether it holds for unbounded
cases.''  Here ``it'' is Theorem 1.2, the DGG lemma for bounded Hodge
Laplacians.

\paragraph{Answering paper.}
Philipp Bartmann and Matthias Keller, \emph{The heat equation and independence
of the spectrum of the Hodge Laplacian on $\ell^p$}, arXiv:2602.18597, explicitly
answers this question.  The introduction says that the paper establishes a DGG
estimate for the heat semigroup kernel and that this answers the question in
Hua--Luo concerning unbounded operators.  In Section 5.2, immediately before
Theorem 5.1, the authors state that their weighted-simplicial-complex DGG
estimate answers Hua--Luo Remark 1.1.

\paragraph{Why this answers the question.}
Bartmann--Keller first prove Theorem 2.2, a DGG estimate for general positive
magnetic Schrodinger operators on graphs associated with a positive closable
quadratic form and an intrinsic metric of finite jump size.  They then use the
signed-Schrodinger representation of discrete Hodge Laplacians on weighted
simplicial complexes.  The resulting Theorem 5.1 gives, for each
$\circ\in\{+,-,H\}$ and all $\omega,\eta\in\ell^2$,
\[
  |\langle e^{-t\Delta^\circ_2}\omega,\eta\rangle|
  \leq
  \exp\!\left(
    -\lambda^\circ_2 t
    -\frac{t}{s^2}\zeta\!\left(\frac{s\,d^\circ(\operatorname{supp}\omega,
    \operatorname{supp}\eta)}{t}\right)
  \right)\|\omega\|_2\|\eta\|_2,
\]
with the corresponding pointwise heat-kernel bound.  The theorem is stated for
the unbounded Dirichlet Hodge Laplacians arising from the closed forms, so it
removes exactly the boundedness restriction singled out in Hua--Luo Remark 1.1.

\paragraph{Scope.}
The answer covers the DGG estimate for the unbounded Hodge Laplacians in the
weighted simplicial-complex framework used by Bartmann--Keller, via their
magnetic Schrodinger operator reduction.  This packet makes no separate claim
about other open directions in $\ell^p$ Hodge theory.

\paragraph{Evidence used.}
The source question was checked against arXiv:1702.00529 and the supporting
answer against arXiv:2602.18597.  Cheap run indexes had no previous record for
either arXiv id at the time of packaging.

\begin{thebibliography}{9}
\bibitem{HL}
B. Hua and X. Luo, \emph{Davies--Gaffney--Grigor'yan lemma on simplicial complexes},
arXiv:1702.00529; Math. Z. 290 (2018), 1041--1053.

\bibitem{BK}
P. Bartmann and M. Keller, \emph{The heat equation and independence of the spectrum
of the Hodge Laplacian on $\ell^p$}, arXiv:2602.18597.
\end{thebibliography}

\end{document}
