\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newtheorem*{claim}{Claim}

\title{Literature closure for Swanepoel's infinite-dimensional equilateral-set problem}
\author{Codex agent lane 17}
\date{July 18, 2026}

\begin{document}
\maketitle

\section*{Source problem}

In the final remarks of Konrad J. Swanepoel's expository paper
\emph{Equilateral sets in finite-dimensional normed spaces}
(arXiv:math/0406264), the subsection on infinite dimensions asks:
\begin{quote}
Does there exist an infinite equilateral set in any separable
infinite-dimensional normed space?
\end{quote}
Equivalently, the question asks whether every separable
infinite-dimensional normed space contains an infinite subset whose
pairwise distances are all equal.

\section*{Later answer}

E. Glakousakis and S. Mercourakis,
\emph{Examples of infinite dimensional Banach spaces without infinite
equilateral sets} (arXiv:1502.02500), give a negative answer.  Their
abstract states that they construct an infinite-dimensional separable
Banach space, not isomorphic to a subspace of $\ell_1$, with no infinite
equilateral sets.  More explicitly, their Theorem 2.2 proves that a
large class of $\ell_1$-sums of finite-dimensional spaces can be
renormed so as to contain no equilateral sequence, and the final
corollary takes $X_n=\ell_p^n$ for $p>2$ to obtain a separable Banach
space with an unconditional basis, not isomorphic to a subspace of
$\ell_1$, and with no equilateral sequence.

\begin{claim}
The problem from arXiv:math/0406264 has a negative literature answer.
\end{claim}

\begin{proof}
Let $X$ be the Banach space obtained in the final corollary of
Glakousakis--Mercourakis.  Then $X$ is separable and infinite
dimensional.  A Banach space is, in particular, a normed space.  The
same corollary says that $X$ does not contain an equilateral sequence;
equivalently, it has no countably infinite equilateral set.  Any
infinite equilateral subset of a metric space contains a countably
infinite equilateral subset by choosing a sequence of distinct points.
Thus $X$ contains no infinite equilateral set.  This is a counterexample
to the universal assertion that every separable infinite-dimensional
normed space contains an infinite equilateral set.
\end{proof}

\section*{Scope note}

This packet only closes the infinite-dimensional final-remarks problem.
It does not resolve the finite-dimensional questions in Swanepoel's
paper, such as Kusner's questions for $\ell_p^n$, Petty's example, the
strictly convex upper-bound problems, or the conjecture that every
$n$-dimensional normed space has an equilateral set of size at least
$n+1$.

\begin{thebibliography}{9}

\bibitem{Swanepoel}
K. J. Swanepoel,
\emph{Equilateral sets in finite-dimensional normed spaces},
arXiv:math/0406264, 2004.

\bibitem{GM}
E. Glakousakis and S. Mercourakis,
\emph{Examples of infinite dimensional Banach spaces without infinite
equilateral sets},
arXiv:1502.02500, 2015.

\end{thebibliography}

\end{document}
