\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Status Note: The Converse for Locally Finite Metric Universality}
\author{fa\_banach\_001 lane 7}
\date{June 16, 2026}

\begin{document}
\maketitle

\paragraph{Status.}
This is a \texttt{literature\_already\_answered} packet.  The source question
from Baudier--Lancien \cite{BL} is explicitly answered in Baudier's later paper
\cite{B09}, using an argument credited there to G. Schechtman.

\paragraph{Source question.}
Baudier--Lancien prove in Section 2, the theorem labeled \texttt{main} in
\cite{BL}, that
there is a universal constant \(C>1\) such that whenever a Banach space \(X\)
uniformly contains the spaces \(\ell_\infty^n\), every locally finite metric
space \(M\) admits a metric embedding \(M \buildrel C \over \hookrightarrow X\).
After their Proposition/Lemma showing that pointwise embeddability of all
locally finite metric spaces is equivalent to uniformly bounded distortion,
they ask in the final remark whether the converse of that theorem is true:
if every locally finite metric space metrically embeds into a Banach space
\(X\), must \(X\) uniformly contain the \(\ell_\infty^n\)'s?

\paragraph{Later answer.}
Baudier \cite{B09}, Section 4, first proves a proper-metric-space converse:
for \(p=\infty\), Schechtman's argument gives that \(X\) has no nontrivial
cotype if and only if all proper metric spaces admit suitable coarse
bi-Lipschitz embeddings into \(X\) with universal constants.  The proof uses
finite grids
\[
  N_k = k^{-1}\mathbb Z^n \cap k B_{\ell_\infty^n},
\]
passes to an ultrapower of \(X\), applies the Heinrich--Mankiewicz
differentiability principle to obtain linear copies of \(\ell_\infty^n\), and
then uses finite representability to return to \(X\).

Most importantly for the source question, the final remark of \cite{B09}
states the exact locally finite consequence: the converse of Baudier--Lancien's
Theorem 2.1 holds, namely a Banach space \(X\) uniformly contains the
\(\ell_\infty^n\)'s if and only if every locally finite metric space
Lipschitz embeds into \(X\).

\paragraph{Scope and classification.}
This completely answers the converse question in \cite{BL} for the same
Lipschitz/metric embedding notion used there.  Since the supporting paper
explicitly identifies the Baudier--Lancien theorem and states the converse,
this packet is classified as \texttt{literature\_already\_answered}, not as a
new full solution from the run.

\begin{thebibliography}{9}
\bibitem{BL}
F. Baudier and G. Lancien,
\emph{Embeddings of locally finite metric spaces into Banach spaces},
Proc. Amer. Math. Soc. 136 (2008), 1029--1033;
arXiv:math/0702266.

\bibitem{B09}
F. Baudier,
\emph{Embeddings of proper metric spaces into Banach spaces},
Houston J. Math. 38 (2012), no. 1, 209--223;
arXiv:0906.3696.
\end{thebibliography}

\end{document}
