\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer: Countable Compact Free Spaces Have MAP}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-19}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.  The second closing question in
arXiv:1201.0847 has a negative answer in later literature.

\paragraph{Source question.}
In Godefroy--Ozawa, \emph{Free Banach spaces and the approximation properties},
arXiv:1201.0847, the authors close the paper with several questions.  Question
2 asks:
\[
  \text{Is there a countable compact space }K
  \text{ such that }\mathfrak F(K)\text{ fails (AP)?}
\]

\paragraph{Later answer.}
Dalet, \emph{Free Spaces over Countable Compact Metric Spaces},
arXiv:1307.0735, proves in Theorem 3.1 that if \(K\) is a countable compact
metric space, then \(\mathcal F(K)\) has the metric approximation property
(MAP).  Since MAP implies AP, there is no countable compact metric space
\(K\) for which \(\mathcal F(K)\) fails AP.  The introduction of
arXiv:1307.0735 explicitly states that this gives a negative answer to
Question 2 in Godefroy--Ozawa.

\paragraph{Adjacent uniformly-discrete subcase.}
The first closing question in arXiv:1201.0847 is Kalton's problem asking
whether \(\mathfrak F(M)\) has BAP for every uniformly discrete metric space
\(M\).  This packet does not solve that problem.  It records one nearby known
positive subcase: Dalet, \emph{Free spaces over some proper metric spaces},
arXiv:1404.3939, Theorem 2.6 proves MAP for countable proper metric spaces.
In particular, every proper uniformly discrete metric space is locally finite
and countable, so this covers the proper/locally finite uniformly-discrete
case.  The arbitrary uniformly-discrete problem remains open; for example,
Cuth--Kalenda, arXiv:2604.01875, still describe it as a major open problem
while proving that uniformly-discrete free spaces are \(3\)-Schur.

\paragraph{Why this is not new.}
The decisive source arXiv:1307.0735 explicitly identifies the Godefroy--Ozawa
question and states that its theorem answers it.  The additional proper-metric
paper is included only as duplicate-prevention context for the adjacent
uniformly-discrete BAP question.

\paragraph{References.}
\begin{itemize}
\item G. Godefroy and N. Ozawa, \emph{Free Banach spaces and the approximation properties}, arXiv:1201.0847.
\item A. Dalet, \emph{Free Spaces over Countable Compact Metric Spaces}, arXiv:1307.0735.
\item A. Dalet, \emph{Free spaces over some proper metric spaces}, arXiv:1404.3939.
\item M. Cuth and O. F. K. Kalenda, \emph{Lipschitz-free spaces over uniformly discrete metric spaces are \(3\)-Schur}, arXiv:2604.01875.
\end{itemize}

\end{document}
