\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\ellone}{\ell^1}
\newcommand{\ellinf}{\ell^\infty}
\newcommand{\one}{\mathbf 1}

\begin{document}

\section*{Human Review: rank-one map \(\ell^1\to\ell^\infty\)}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Not independently checked in detail by the human reviewer;
excluded from the survey.

\noindent Verdict: Excluded from the main survey.

\section*{Human Comments}

The packet claims to identify a local error in the source paper.  The paper
states that the rank-one operator
\[
  T:\ellone\to\ellinf,
  \qquad
  T(x)=\left(\sum_{k=1}^\infty x_k\right)\one,
  \qquad
  \one=(1,1,\ldots),
\]
is not disjoint weak-star Dunford-Pettis.  The automatic packet argues that
this assertion is false.

Indeed, write
\[
  \sigma(x)=\sum_{k=1}^\infty x_k.
\]
Then
\[
  T(x)=\sigma(x)\one.
\]
If \((x_n)\) is a norm-bounded disjoint sequence in \(\ellone\), then
\((\sigma(x_n))\) is bounded.  If
\[
  f_n\overset{w^*}{\longrightarrow}0
  \quad\text{in }(\ellinf)',
\]
then, since \(\one\in\ellinf\),
\[
  f_n(\one)\longrightarrow 0.
\]
Therefore
\[
  f_n(Tx_n)
  =
  f_n(\sigma(x_n)\one)
  =
  \sigma(x_n)f_n(\one)
  \longrightarrow 0.
\]
This would be exactly the definition of a disjoint weak-star
Dunford-Pettis operator, and hence would refute the displayed assertion in
the source paper.

The alleged mistake in the source paper appears to come from an incorrect handling
of weak-star null sequences in \((\ell^\infty)'\).  In particular, one cannot
generally represent arbitrary elements of \((\ell^\infty)'\) by countable
coordinate sums, and any weak-star null sequence in \((\ell^\infty)'\) must
vanish on the constant vector \(\one\).

\section*{Short Version}

The automatic packet gives a short argument that the rank-one map factors
through the constant vector \(\one\), and that weak-star null functionals on
\((\ell^\infty)'\) vanish on \(\one\).  If correct, this would show that the
operator is disjoint weak-star Dunford-Pettis, contrary to the assertion in
the source paper.

\section*{Literature and Follow-Up}

This should be treated, at most, as a possible local correction to a printed
example, not as a substantive new mathematical discovery.  The surrounding
paper also shows some signs of technical unreliability, so this packet is
best understood as an example-checking case rather than as progress on an
open problem.

\section*{Review Outcome}

Exclude this packet from the main survey of successful mathematical
discoveries.  It may be retained as a cautionary example of a possible local
paper-error detection, but the argument has not been independently checked in
detail by the human reviewer, and in any case the mathematical contribution
would be too small and too local to count as a main survey example.

\end{document}
