\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newcommand{\R}{\mathbb{R}}
\newcommand{\op}{\operatorname{op}}
\newcommand{\DD}{\Delta_{\hbar}}
\newcommand{\Dh}{D_{\hbar}}
\newcommand{\Lp}{L^p}

\title{Quantum Riesz Transform Boundedness via Quantum Euclidean Singular Integrals}
\author{Run \texttt{fa\_banach\_001}, lane 6}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Literature-implied answer.}  The Riesz transform conjecture in
Lafleche's \emph{On Quantum Sobolev Inequalities} follows from the
Calderon--Zygmund theory for quantum Euclidean spaces of Gonzalez-Perez,
Junge, and Parcet, after identifying the Weyl phase-space algebra with the
Heisenberg--Weyl instance of \(\mathcal R_\Theta\).

\section*{Source Question}

The source paper is Laurent Lafleche, \emph{On Quantum Sobolev Inequalities},
arXiv:2210.03013, J. Funct. Anal. 286 (2024), 110400.  In the subsection
"Boundedness of Riesz transforms in the quantum phase space", the paper proves
boundedness for the split Schur multipliers
\((-\Delta_{\hbar,\xi})^{-1/2}D_{\hbar,\xi}\) and, by Fourier conjugation,
\((-\Delta_{\hbar,x})^{-1/2}D_{\hbar,x}\).  It then states that it is not clear
whether these split expressions are equivalent to
\[
  \|(-\DD)^{1/2}A\|_{\Lp}
\]
when \(p\ne 2\), and conjectures more precisely that
\[
  (-\DD)^{-1/2}\Dh:\Lp\longrightarrow(\Lp)^{2d}
\]
is bounded for every \(1<p<\infty\), with norm independent of \(\hbar\).

\section*{Supporting Theorem}

The supporting paper is A. M. Gonzalez-Perez, M. Junge, and J. Parcet,
\emph{Singular integrals in quantum Euclidean spaces}, arXiv:1705.01081,
Memoirs Amer. Math. Soc. 272 (2021), no. 1334.  It defines quantum Euclidean
spaces \(\mathcal R_\Theta\), notes that the choice
\[
  \Theta = 2\pi\hbar\, I_m\otimes
  \begin{pmatrix}0&1\\ -1&0\end{pmatrix}
\]
yields the Heisenberg--Weyl algebra, and proves quantum
Calderon--Zygmund extrapolation: if a kernel operator on \(\mathcal R_\Theta\)
has the \(L_2\) cancellation estimate and the required quantum kernel
smoothness, then it is completely bounded on \(L_p(\mathcal R_\Theta)\) for
all \(1<p<\infty\).  The paper also emphasizes that the convolution-kernel
case, equivalently quantum Fourier multipliers, is easier and is covered by
the same framework.

\section*{Implication}

Let \(n=2d\).  Under Weyl quantization in Lafleche's notation,
\[
  D_{\hbar,j}\op_f=\op_{\partial_{z_j}f},
  \qquad
  (-\DD)^s\op_f=\op_{(-\Delta_z)^s f}.
\]
Thus on the Fourier side in the phase-space variable \(z\), the \(j\)-th
component
\[
  R_{\hbar,j}=D_{\hbar,j}(-\DD)^{-1/2}
\]
has multiplier
\[
  m_j(\eta)=c\,\frac{i\eta_j}{|\eta|},
  \qquad \eta\ne 0,
\]
up to the harmless Fourier-normalization constant \(c\).  This is exactly the
classical Riesz transform symbol, now acting as a scalar quantum Fourier
multiplier on the quantum Euclidean space \(\mathcal R_{\Theta_\hbar}\).

Equivalently, its principal-value kernel is transported from the classical
Calderon--Zygmund kernel
\[
  K_j(z)=c_n\,\frac{z_j}{|z|^{n+1}}.
\]
The normal homomorphism \(\pi_\Theta\) used in the supporting paper transports
the Euclidean distance-to-the-diagonal and its differential estimates into
\(\mathcal R_\Theta\).  Consequently \(K_j\) satisfies the supporting paper's
quantum Calderon--Zygmund hypotheses with constants depending only on \(n\)
and the normalization of \(K_j\), not on the deformation matrix \(\Theta\).
The \(L_2\) norm is the Plancherel multiplier norm \(\|m_j\|_\infty\), also
independent of \(\Theta\).  Hence for each \(1<p<\infty\),
\[
  \|R_{\hbar,j}A\|_{\Lp}\le C_{p,n}\|A\|_{\Lp},
  \qquad j=1,\ldots,n,
\]
with \(C_{p,n}\) independent of \(\hbar\).

\section*{Vector-Valued Bound}

The source appendix gives the needed finite-dimensional vector comparison for
operator columns.  If \(B=(B_1,\ldots,B_n)\), then for \(p\ge2\),
\[
  \|B\|_{S^p(\ell^2)}
  \le \Big(\sum_{j=1}^n \|B_j\|_{S^p}^2\Big)^{1/2},
\]
whereas for \(1\le p\le2\),
\[
  \|B\|_{S^p(\ell^2)}
  \le \Big(\sum_{j=1}^n \|B_j\|_{S^p}^p\Big)^{1/p}.
\]
Applying these inequalities to \(B_j=R_{\hbar,j}A\) gives
\[
  \|(-\DD)^{-1/2}\Dh A\|_{(\Lp)^n}
  \le C_{p,n}'\|A\|_{\Lp},
\]
where \(C_{p,n}'\) is independent of \(\hbar\).  This is the conjectured
boundedness.

The same scalar estimates also give the reverse norm comparison.  Indeed, on
the dense Weyl-Schwartz core,
\[
  R_{\hbar,j}=D_{\hbar,j}(-\DD)^{-1/2},
\]
and the Fourier multiplier identity
\[
  (-\DD)^{1/2}A=-\sum_{j=1}^n R_{\hbar,j}D_{\hbar,j} A
\]
holds on the dense Schwartz/Weyl core and extends by density.  Therefore
\[
  \|(-\DD)^{1/2}A\|_{\Lp}
  \le C_{p,n}''\|\Dh A\|_{(\Lp)^n},
\]
again with no \(\hbar\)-dependence.  Thus the first-order quantum Bessel and
Sobolev seminorms are equivalent for fixed \(d\) and \(1<p<\infty\), with
constants independent of \(\hbar\).

\section*{Scope and Search}

This is a literature-implied answer, not a new theorem.  The supporting paper
predates the source question and does not appear to explicitly state that it
answers Lafleche's conjecture.  The implication uses the standard
identification of the source's Weyl/Schatten phase-space model with the
Heisenberg--Weyl quantum Euclidean space.  Constants are allowed to depend on
\(p\) and \(d\); no dimension-free assertion is claimed.

Local run indexes were searched for arXiv:2210.03013, the title, quantum
Sobolev phrases, Riesz transform phrases, and Junge--Parcet/Gonzalez-Perez
keywords.  Web searches on 2026-07-18 checked arXiv and EMS pages for
arXiv:2210.03013, arXiv:1705.01081, arXiv:1407.2475, and close phrase
searches.  No existing run packet or explicit later answer to this exact
conjecture was found.

\begin{thebibliography}{9}
\bibitem{Lafleche}
L. Lafleche.
\emph{On Quantum Sobolev Inequalities}.
J. Funct. Anal. 286 (2024), 110400. arXiv:2210.03013.

\bibitem{GPJP}
A. M. Gonzalez-Perez, M. Junge, and J. Parcet.
\emph{Singular integrals in quantum Euclidean spaces}.
Memoirs Amer. Math. Soc. 272 (2021), no. 1334. arXiv:1705.01081.

\bibitem{JMP}
M. Junge, T. Mei, and J. Parcet.
\emph{Noncommutative Riesz transforms -- dimension free bounds and Fourier multipliers}.
J. Eur. Math. Soc. 20 (2018), 529--595. arXiv:1407.2475.
\end{thebibliography}

\end{document}
