\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\eps}{\varepsilon}

\title{Strengthened Versions of a Uniform Property \texorpdfstring{$(S)$}{(S)} Modulus Question}
\author{Follow-up note to the scalar counterexample packet}
\date{June 8, 2026}

\begin{document}
\maketitle

\section*{Source and Question}

This note follows up on the scalar counterexample packet for Open
Problem (3) in:
\begin{quote}
William B. Johnson and Tomasz Kania, \emph{Uniform Property (S)},
arXiv:2602.09106.
\end{quote}
The printed question asks whether \(U(d,a)\) is always bounded above by
a constant multiple of \(da\).  The scalar packet shows that, as printed,
the answer is no: in the real one-dimensional space \(\R\), for every
\(0<d<2\) the admissible pair in the infimum is forced to be the
antipodal pair.

The purpose of this note is to record what happens after adding natural
extra hypotheses such as infinite-dimensionality or the existence of
small-distance pairs in the unit sphere.

\section*{Definitions}

For a normed space \(X\), Johnson and Kania define
\[
  U_X(x,y;a)
  =
  \sup_{\norm{z}\le a}
  \left|\,\norm{x+z}-\norm{y+z}\,\right|
  \qquad (x,y\in S_X,\ a>0),
\]
and
\[
  U_X(d;a)
  =
  \inf_{\substack{x,y\in S_X\\ \norm{x-y}\ge d}}
  U_X(x,y;a)
  \qquad (0<d<2,\ a>0).
\]

\section*{Main Boundary Found}

\begin{theorem}
Let \(X\) be a non-superreflexive Banach space.  Then
\[
  U_X(d;a)\le 2ad
  \qquad (0<d\le 2,\ a>0).
\]
Consequently, the infinite-dimensional strengthened version of the
printed question is true for all non-superreflexive Banach spaces.
\end{theorem}

\begin{proof}
Johnson and Kania prove, as Theorem C of the source paper, that every
non-superreflexive Banach space satisfies
\[
  U_X(d;a)
  \le
  \left(\frac{4a}{2+d}\wedge 1\right)d
  \qquad (0<d\le 2,\ a>0).
\]
If \(a\le (2+d)/4\), then
\[
  \left(\frac{4a}{2+d}\right)d
  \le 2ad,
\]
because \(2+d\ge 2\).  If \(a\ge (2+d)/4\), then \(a\ge 1/2\), so the
trivial estimate \(U_X(d;a)\le d\) gives \(U_X(d;a)\le d\le 2ad\).
\end{proof}

\begin{corollary}
Any counterexample to the infinite-dimensional strengthened question
must be superreflexive.
\end{corollary}

\section*{The Flat-Face Mechanism}

The source proof of Theorem C passes through almost-isometric
\(\ell_\infty^2\) geometry, equivalently a long line segment in the
unit sphere after passing to an ultrapower.  The elementary estimate
behind that mechanism is the following.

\begin{lemma}[Spherical segment estimate]
Suppose the unit sphere of \(X\) contains a line segment \([v,w]\) with
\(\norm{v-w}=L>0\).  Then for every \(0<d\le L\) and every \(a>0\),
\[
  U_X(d;a)\le \frac{4a}{L+d}\,d
  \le \frac{4}{L}ad.
\]
In particular, if \(L=2\), then \(U_X(d;a)\le 2ad\) for every
\(0<d\le 2\) and \(a>0\).
\end{lemma}

\begin{proof}
Parametrize the segment by
\[
  p(s)=(1-s)v+sw,\qquad 0\le s\le 1.
\]
For \(0<d\le L\), put
\[
  x=p\!\left(\frac{1-d/L}{2}\right),
  \qquad
  y=p\!\left(\frac{1+d/L}{2}\right).
\]
Then \(x,y\in S_X\) and \(\norm{x-y}=d\).  Moreover
\[
  y=tx+(1-t)w,
  \qquad
  t=\frac{L-d}{L+d}.
\]
Fix \(z\in X\) with \(\norm{z}\le a\).  By interchanging \(x\) and \(y\)
if necessary, assume \(\norm{x+z}\le \norm{y+z}\).  Convexity gives
\[
\begin{aligned}
  \norm{y+z}
  &\le t\norm{x+z}+(1-t)\norm{w+z} \\
  &\le t\norm{x+z}+(1-t)(1+a)       \\
  &=\norm{x+z}+(1-t)(1+a-\norm{x+z}).
\end{aligned}
\]
Since \(\norm{x+z}\ge 1-a\), the final factor is at most \(2a\).
Also \(1-t=2d/(L+d)\).  Hence
\[
  \norm{y+z}-\norm{x+z}
  \le
  \frac{4ad}{L+d}.
\]
Taking the supremum over \(\norm{z}\le a\), and then using this
particular admissible pair in the infimum defining \(U_X(d;a)\), proves
the result.
\end{proof}

\begin{remark}
This lemma shows that merely having pairs at each small distance is not
the decisive sufficient condition.  What gives the estimate is a
controlled family of pairs lying on a spherical segment.
\end{remark}

\section*{The Hilbert Case}

\begin{proposition}
If \(H\) is a real Hilbert space with \(\dim H\ge 2\), then
\[
  U_H(d;a)\le 2ad
  \qquad (0<d<2,\ a>0).
\]
\end{proposition}

\begin{proof}
Choose \(x,y\in S_H\) with \(\norm{x-y}=d\).  For every \(z\in H\),
\[
  \norm{x+z}^2-\norm{y+z}^2
  =
  2\langle x-y,z\rangle.
\]
If \(a\le 1/2\) and \(\norm{z}\le a\), then
\[
  \norm{x+z}+\norm{y+z}
  \ge 2(1-a)\ge 1,
\]
and therefore
\[
\begin{aligned}
  \left|\norm{x+z}-\norm{y+z}\right|
  &=
  \frac{2|\langle x-y,z\rangle|}
       {\norm{x+z}+\norm{y+z}}       \\
  &\le 2ad.
\end{aligned}
\]
Taking the supremum over such \(z\) gives \(U_H(x,y;a)\le 2ad\), hence
\(U_H(d;a)\le 2ad\).  If \(a\ge 1/2\), then the trivial estimate
\[
  \left|\norm{x+z}-\norm{y+z}\right|\le \norm{x-y}=d
\]
gives \(U_H(d;a)\le d\le 2ad\).
\end{proof}

\section*{A Permanence Observation}

\begin{proposition}
Let \(1\le p\le \infty\), and suppose \(Y\) satisfies
\[
  U_Y(d;a)\le Cda
  \qquad (0<d<2,\ a>0).
\]
Then every absolute sum \(X=Y\oplus_p Z\) satisfies the same estimate.
\end{proposition}

\begin{proof}
It suffices to use admissible pairs inside the copy of \(Y\).  Let
\(x,y\in S_Y\), and view them as \((x,0),(y,0)\in S_X\).  For a
perturbation \((u,v)\in X\), with \(1\le p<\infty\),
\[
  \norm{(x,0)+(u,v)}_p
  =
  \left(\norm{x+u}^p+\norm{v}^p\right)^{1/p}.
\]
For fixed \(r\ge 0\), the scalar map
\[
  s\mapsto (s^p+r^p)^{1/p}
\]
is \(1\)-Lipschitz on \([0,\infty)\).  Hence
\[
\begin{aligned}
&\left|
  \norm{(x,0)+(u,v)}_p-\norm{(y,0)+(u,v)}_p
  \right|        \\
&\qquad\le
  \left|\norm{x+u}-\norm{y+u}\right|.
\end{aligned}
\]
The case \(p=\infty\) is identical, using the \(1\)-Lipschitz map
\(s\mapsto \max\{s,r\}\).  Taking suprema over perturbations of norm at
most \(a\), and then infima over \(x,y\in S_Y\), gives the claim.
\end{proof}

\section*{Remaining Target}

This follow-up does not settle the connected-sphere strengthening.  It
also does not settle the infinite-dimensional strengthening in the
superreflexive case.  The reductions above show that a counterexample,
if one exists, cannot be one-dimensional, non-superreflexive, Hilbert, a
space with a diameter-two spherical segment, or an absolute
\(\ell_p\)-sum containing a good summand.

Thus any remaining infinite-dimensional counterexample must be
superreflexive and must avoid both the flat-face mechanism and the
Hilbert-type estimate.  Numerical probes in the accompanying scratch
script \texttt{lp2\_modulus\_probe.py} did not suggest an
\(\ell_p^2\) counterexample: balanced pairs can be hostile for large
\(p\), but near-axis pairs become flat and appear to drive the infimum
down.

\section*{Recommendation for the Original Packet}

The original scalar packet should remain labeled as a literal
counterexample to the printed question.  Its limitation statement can be
made sharper: the infinite-dimensional variant is already resolved
positively for all non-superreflexive spaces by Johnson--Kania's
Theorem C, so only the superreflexive infinite-dimensional direction
remains open from this follow-up.

\end{document}
