\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature-implied partial answer to a convex-transitive Banach--Mazur question}
\author{Run fa\_banach\_001}
\date{2026-06-28}

\begin{document}
\maketitle

\paragraph{Status.}
This is a \textbf{literature-implied partial answer}, not a new proof packet.

\paragraph{Source question.}
Randrianantoanina's \emph{A note on Banach--Mazur problem}
(arXiv:math/0110202) proves that a real Banach space of dimension at least
three with an almost transitive isometry group and a 1-complemented hyperplane
is Hilbert.  In the introduction, after discussing the complex convex
transitive reflection-vector theorem, the paper asks whether this theorem can
be generalized to convex transitive spaces.  In source lines 330--331:
\[
\text{``We do not know whether Theorem 1 can be generalized for convex transitive spaces.''}
\]

\paragraph{Supporting theorem.}
Talponen's \emph{Convex-transitive characterizations of Hilbert spaces}
(arXiv:0705.2526) explicitly identifies the question as Randrianantoanina's
Question \((\mathbf Q_{\mathrm R})\): whether every real convex-transitive
Banach space containing a 1-codimensional 1-complemented subspace is Hilbert.
The paper then proves affirmative subcases.

First, Theorem 3.2 says that if \(X\) is weakly locally uniformly rotund,
has a big point, and for every \(\varepsilon>0\) has a 1-codimensional
\((1+\varepsilon)\)-complemented subspace, then \(X\) is Hilbert.  A convex
transitive space has every sphere point big, so this applies to the source
projection hypothesis under the additional weak-LUR assumption.

Second, Theorem 5.4 says that if \(X\) is convex-transitive, admits a
one-dimensional bicontractive projection, and has a weak-LUR point on the unit
sphere, then \(X\) is Hilbert.  This is a sharper weak-geometry subcase, but
the bicontractive line projection is stronger than merely having a
1-complemented hyperplane.

\paragraph{Scope.}
The general convex-transitive variant of Randrianantoanina's theorem remains
open here.  The supporting paper supplies substantial partial affirmative
answers under weak-LUR or bicontractive projection hypotheses; it does not
settle the unrestricted convex-transitive case.

\paragraph{Novelty check.}
The run registry had no existing packet for arXiv:0110202 or arXiv:0705.2526.
It did contain a separate rotation-problem packet for the \(\ell_p\) and
subspace-of-quotient-of-\(\ell_p\) classes, which is disjoint from this
Flinn/bicontractive-projection subcase.  Web and local searches for
``1-complemented hyperplane convex transitive'', ``Flinn element convex
transitive'', and the source title found Talponen's paper as the relevant
later partial answer, with no full answer to the unrestricted question.

\begin{thebibliography}{9}
\bibitem{Randrianantoanina2002}
B. Randrianantoanina,
\emph{A note on Banach--Mazur problem},
Glasgow Math. J. 44 (2002), 159--165; arXiv:math/0110202.

\bibitem{Talponen2007}
J. Talponen,
\emph{Convex-transitive characterizations of Hilbert spaces},
arXiv:0705.2526.
\end{thebibliography}

\end{document}
