\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\LDTP}{\mathrm{LD2P}}
\newcommand{\DTP}{\mathrm{D2P}}
\newcommand{\SDTP}{\mathrm{SD2P}}
\newcommand{\cnull}{c_0}

\begin{document}

\begin{center}
{\Large Literature status: separations among diameter 2 properties}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:1304.7068}
\end{center}

\section*{Source question}

Abrahamsen, Lima, and Nygaard's paper \emph{Remarks on diameter 2 properties},
arXiv:1304.7068, defines in Definition 1.1 three properties of a Banach space
\(X\): the local diameter 2 property, where every slice of \(B_X\) has
diameter 2; the diameter 2 property, where every non-empty relatively weakly
open subset of \(B_X\) has diameter 2; and the strong diameter 2 property,
where every finite convex combination of slices of \(B_X\) has diameter 2.

Immediately after the definition, the authors say that they do not know
whether any of the reverse implications hold. In Section 4, ``Some concluding
remarks and questions'', they again say that they do not know whether the
three diameter 2 properties are really different and conjecture that they are
not equal. Item (c) asks whether Theorem 3.2, the stability of the local and
ordinary diameter 2 properties under \(\ell_p\)-sums for all
\(1\leq p\leq \infty\), is true for the strong diameter 2 property.

\section*{Supporting answers}

Becerra Guerrero, Lopez-Perez, and Rueda Zoca's paper \emph{Big slices versus
big relatively weakly open subsets in Banach spaces}, arXiv:1304.4397, gives
the first separation. The introduction says that the paper proves the
existence of a Banach space satisfying the slice diameter 2 property and
failing the diameter 2 property, answering negatively an open problem stated
in Abrahamsen--Lima--Nygaard. In that paper's notation, ``SD2P'' means the
slice diameter 2 property, i.e. \(\LDTP\), not the strong diameter 2 property.
The decisive result is Theorem 2.4 and Corollary 2.5: every Banach space
containing an isomorphic copy of \(\cnull\) admits an equivalent norm for
which every slice of the new unit ball has diameter 2, while there are
non-empty relatively weakly open subsets of the new unit ball with arbitrarily
small diameter. Thus \(\LDTP\) does not imply \(\DTP\).

The same supporting paper records the second separation: the strong diameter
2 property is strictly stronger than \(\DTP\). It cites the theorem of
Acosta, Becerra Guerrero, and Lopez-Perez that
\[
  \cnull \oplus_2 \cnull
\]
has \(\DTP\) but fails the strong diameter 2 property. This also answers the
literal form of source item (c) negatively, since \(\cnull\) has the strong
diameter 2 property but its \(\ell_2\)-sum with itself fails strong D2P.

For the broader stability landscape, Haller, Langemets, and Nadel's paper
\emph{Stability of average roughness, octahedrality, and strong diameter two
properties of Banach spaces with respect to absolute sums}, arXiv:1702.03140,
gives a full absolute-sum criterion. Their Theorem 3.3 states that if \(X\)
and \(Y\) have the strong diameter 2 property and \(N\) is an absolute
normalized norm on \(\mathbb R^2\), then \(X\oplus_N Y\) has the strong
diameter 2 property if and only if \((\mathbb R^2,N)\) has the positive strong
diameter 2 property.

\section*{Status}

The main separation question from arXiv:1304.7068 is already answered in the
literature:
\[
  \SDTP \Longrightarrow \DTP \Longrightarrow \LDTP,
\]
but neither reverse implication holds. The \(\LDTP\)-versus-\(\DTP\)
separation is explicitly presented in arXiv:1304.4397 as answering the
Abrahamsen--Lima--Nygaard open problem. The \(\DTP\)-versus-strong-D2P
separation is recorded there via the example \(\cnull\oplus_2\cnull\), and
the later absolute-sum theorem of Haller--Langemets--Nadel explains the
general strong-D2P stability criterion.

This is an already-known literature answer, not a new result from the run.
The packet does not answer the remaining concluding questions in
arXiv:1304.7068, namely items (a), (b), (d), and (e), except for the overlap
with absolute-sum stability described above.

\section*{References}

\sloppy
\begin{itemize}
\item T. A. Abrahamsen, V. Lima, O. Nygaard, \emph{Remarks on diameter 2
properties}, arXiv:1304.7068; J. Convex Anal. 20 (2013), 439--452.
\item J. Becerra Guerrero, G. Lopez-Perez, A. Rueda Zoca, \emph{Big slices
versus big relatively weakly open subsets in Banach spaces}, arXiv:1304.4397;
J. Math. Anal. Appl. 428 (2015), 855--865.
\item R. Haller, J. Langemets, R. Nadel, \emph{Stability of average roughness,
octahedrality, and strong diameter two properties of Banach spaces with
respect to absolute sums}, arXiv:1702.03140.
\end{itemize}

\end{document}
