\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathrsfs}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: Dales Question (II) for \(c_0\oplus\ell_\infty\)}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 15 June 2026

\noindent Status: Verified.

\noindent Verdict: The proof appears essentially correct. It gives a positive answer to the stated subquestion for
\[
E=c_0\oplus\ell_\infty,
\]
namely that every finitely-generated maximal left ideal of \(\mathcal B(E)\) is fixed.

\section*{Human Comments}

The proof has a clear structure. The main new step is the following implication: if \(L\) is a non-fixed maximal left ideal of \(\mathcal B(c_0\oplus\ell_\infty)\) and \(L\) contains a bounded-below operator, then
\[
\mathcal K_1\subseteq L,
\]
where
\[
\mathcal K_1=
\left\{
\begin{pmatrix}
A&B\\
C&D
\end{pmatrix}\in\mathcal B(c_0\oplus\ell_\infty): A\in\mathcal K(c_0)
\right\}.
\]
This is then combined with Proposition 7.8 of the source paper, which states that \(\mathcal K_1\) is not contained in any finitely-generated maximal left ideal of \(\mathcal B(c_0\oplus\ell_\infty)\).

The block argument looks sound. Since \(L\) is non-fixed, the strong dichotomy in the source paper gives
\[
\mathcal E(E)\subseteq L,
\]
where \(\mathcal E(E)\) is the ideal of inessential operators. The required block inclusions are justified as follows. Compact operators on \(c_0\) are inessential. Every operator \(\ell_\infty\to c_0\) is strictly singular, because \(c_0\) contains no copy of \(\ell_\infty\), and hence is inessential. The converse off-diagonal direction \(c_0\to\ell_\infty\) is also inessential by the standard symmetry property for inessential operators, exactly as used in the proof of Theorem 7.7 of the source paper via Gonzalez. Finally, weakly compact operators on \(\ell_\infty\) are inessential.

Now let
\[
R=
\begin{pmatrix}
R_{11}&R_{12}\\
R_{21}&R_{22}
\end{pmatrix}\in L
\]
be bounded below. Restricting \(R\) to the \(\ell_\infty\)-summand gives the column operator
\[
y\mapsto (R_{12}y,R_{22}y),
\qquad
\ell_\infty\to c_0\oplus\ell_\infty,
\]
which is bounded below and hence upper semi-Fredholm. Since \(R_{12}:\ell_\infty\to c_0\) is strictly singular, stability of upper semi-Fredholm operators under strictly singular perturbations implies that \(R_{22}\) is upper semi-Fredholm.

Choosing a finite-rank projection \(Q\) onto \(\ker R_{22}\), the restriction of \(R_{22}\) to \(\ker Q\) is an isomorphism onto its closed range. Since \(\ell_\infty\) is injective, the inverse on this range extends to an operator \(S\in\mathcal B(\ell_\infty)\), giving
\[
SR_{22}=I_{\ell_\infty}-Q.
\]
Multiplying \(R\) on the left by the lower-right block operator with entry \(S\) then produces
\[
\begin{pmatrix}
0&0\\
SR_{21}&I_{\ell_\infty}-Q
\end{pmatrix}\in L.
\]
The lower-left block \(SR_{21}\) is inessential, and \(Q\) is finite-rank. Since these corresponding block operators already belong to \(L\), it follows that
\[
\begin{pmatrix}
0&0\\
0&I_{\ell_\infty}
\end{pmatrix}\in L.
\]
This forces all lower-right blocks into \(L\), and together with the inessential upper-left compact and off-diagonal blocks gives \(\mathcal K_1\subseteq L\).

It remains to explain why a non-fixed finitely-generated maximal left ideal contains such a bounded-below operator. If
\[
L=\mathscr L_\Gamma,\qquad \Gamma=\{T_1,\ldots,T_n\},
\]
then the dichotomy theorem gives \(\mathcal F(E)\subseteq L\). Corollary 4.7 of the source paper then implies that
\[
\Psi_\Gamma:E\to E^n,\qquad
\Psi_\Gamma x=(T_1x,\ldots,T_nx),
\]
is bounded below. Since \(E^n\cong E\), choose an isomorphism \(A:E^n\to E\). Then
\[
R=A\Psi_\Gamma
\]
is bounded below. Moreover \(R\in L\), because writing \(A\) coordinatewise as
\[
A(y_1,\ldots,y_n)=A_1y_1+\cdots+A_ny_n
\]
gives
\[
A\Psi_\Gamma=A_1T_1+\cdots+A_nT_n\in\mathscr L_\Gamma=L.
\]

Thus a non-fixed finitely-generated maximal left ideal would contain a bounded-below operator, hence would contain \(\mathcal K_1\), contradicting Proposition 7.8. The conclusion follows.

\section*{Review Outcome}

Accepted as an essentially correct proof of the \(c_0\oplus\ell_\infty\) subcase. The result should be viewed as a corollary-style completion of this specific open subquestion using the machinery already developed in the source paper, rather than as a solution to the broader remaining \(C(K)\) cases.

\end{document}
