\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\LDTP}{\mathrm{LD2P}}
\newcommand{\DTP}{\mathrm{D2P}}
\newcommand{\cnull}{c_0}

\begin{document}

\begin{center}
{\Large Literature status: local diameter 2 property versus diameter 2 property}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:1206.3539}
\end{center}

\section*{Source question}

Abrahamsen, Lima, and Nygaard's paper \emph{Almost isometric ideals in Banach
spaces} defines, in Section 3, the local diameter 2 property and the diameter
2 property as follows. A Banach space \(X\) has the local diameter 2 property
if every slice of \(B_X\) has diameter 2, and it has the diameter 2 property
if every non-empty relatively weakly open subset of \(B_X\) has diameter 2.
Immediately after Definition 3.1, on page 7 of the PDF, the authors state
that they do not know whether these two properties are really different.

\section*{Supporting answer}

Becerra Guerrero, Lopez-Perez, and Rueda Zoca's paper \emph{Big slices versus
big relatively weakly open subsets in Banach spaces}, arXiv:1304.4397, answers
this question negatively. In the introduction, on page 2 of the PDF, they say
that the aim of the note is to prove the existence of a Banach space satisfying
the slice diameter 2 property and failing the diameter 2 property, answering
the open problem negatively.

There is one notation warning. In arXiv:1304.4397, ``SD2P'' denotes the
slice diameter 2 property. This is the same condition as the local diameter 2
property in arXiv:1206.3539. It is not the modern strong diameter 2 property.

The decisive statement is Theorem 2.4, followed by Corollary 2.5, on page 10:
every Banach space containing an isomorphic copy of \(\cnull\) can be
equivalently renormed so that every slice of the new unit ball has diameter
2, while the new unit ball has non-empty relatively weakly open subsets of
arbitrarily small diameter. Consequently, the renormed space has \(\LDTP\)
and fails \(\DTP\).

\section*{Status}

The answer to the arXiv:1206.3539 uncertainty is therefore:
\[
  \LDTP \not\Longleftrightarrow \DTP.
\]
More precisely, \(\DTP\) implies \(\LDTP\), but the converse fails, even
within equivalent renormings of any Banach space containing an isomorphic copy
of \(\cnull\).

This is an already-known literature answer, not a new result from the run.
The supporting paper explicitly records that it is answering the equivalence
problem between slice/local D2P and D2P. The link to the exact
arXiv:1206.3539 passage is by matching the definitions and the same question;
the supporting paper cites the earlier Abrahamsen--Lima--Nygaard source for
the problem.

\section*{Queue-signal note}

The two deterministic signals that reserved arXiv:1206.3539 are same-paper
false positives. The introduction asks for an analogue of a theorem and then
proves it in the same paper. Later, the authors say they know no explicit
reference for bidual-to-space inheritance of D2P, and then prove a stronger
ai-ideal inheritance result in the same section. Neither passage should be
counted as a promoted result.

\section*{References}

\sloppy
\begin{itemize}
\item T. A. Abrahamsen, V. Lima, O. Nygaard, \emph{Almost isometric ideals in
Banach spaces}, arXiv:1206.3539.
\item J. Becerra Guerrero, G. Lopez-Perez, A. Rueda Zoca, \emph{Big slices
versus big relatively weakly open subsets in Banach spaces}, arXiv:1304.4397;
J. Math. Anal. Appl. 428 (2015), 855--865.
\end{itemize}

\end{document}
