\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\N}{\mathbb N}

\title{Literature-Implied Answer to the Measure-Algebra Question in arXiv:1209.4294}
\author{Run \texttt{fa\_banach\_001}, lane 3}
\date{June 26, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{literature\_implied\_answer (full answer to Question 6.8 subquestion).}

\section*{Source Question}

The source paper is P. Koszmider,
\emph{Universal objects and associations between classes of Banach spaces and
classes of compact spaces}, arXiv:1209.4294.

On page 18, Question 6.8 asks:

\begin{quote}
Suppose that $K$ is the Stone space of the measure algebra, i.e. the Boolean
algebra of Borel subsets of $[0,1]$ modulo Lebesgue null sets.  Is it consistent
that $C(K)$ does not isometrically embed into $\ell_\infty/c_0$?
\end{quote}

The surrounding paragraph recalls that Dow--Hart proved the corresponding
Stone space may consistently fail to be a continuous image of $\N^*$, and then
asks whether the Banach-space isometric embedding can also consistently fail.

\section*{Supporting Literature}

The supporting paper is C. Brech and P. Koszmider,
\emph{An isometrically universal Banach space induced by a non-universal Boolean
algebra}, arXiv:1505.04776.

On page 2, its introduction says that Dow--Hart proved under OCA that the
measure algebra $M$ does not embed into $\wp(\N)/\mathrm{Fin}$, while it is
well known that
\[
  C(K_M)\equiv L_\infty
  \quad\text{isometrically embeds into}\quad
  C(K_{\wp(\N)/\mathrm{Fin}})\equiv \ell_\infty/c_0,
\]
citing Amir--Arbel.

\section*{Conclusion}

This gives a negative answer in ZFC to Question 6.8 of arXiv:1209.4294.
The consistency failure asked for there cannot occur, because the relevant
isometric embedding always exists:
\[
  C(K_M) \hookrightarrow \ell_\infty/c_0
\]
linearly and isometrically.

\section*{Scope}

This packet answers only the measure-algebra isometric-embedding subquestion.
It does not answer the broader ZFC equivalence questions from the same survey
about universal Banach spaces, isometrically universal Banach spaces, and
universal compact spaces.

\section*{Search Notes}

The run indexes were searched for arXiv:1209.4294, \texttt{measure algebra},
\texttt{L\_infty}, and \texttt{l\_infty/c\_0}. No prior packet for this
subquestion was found. The decisive supporting statement was found by local
source search in arXiv:1505.04776.

\begin{thebibliography}{9}

\bibitem{Koszmider2012}
P. Koszmider,
\emph{Universal objects and associations between classes of Banach spaces and
classes of compact spaces}, arXiv:1209.4294.

\bibitem{BrechKoszmider2015}
C. Brech and P. Koszmider,
\emph{An isometrically universal Banach space induced by a non-universal
Boolean algebra}, arXiv:1505.04776.

\bibitem{AmirArbel}
D. Amir and B. Arbel,
\emph{Continuous functions spaces with the separable complementation property},
Israel J. Math. 29 (1978), 294--306.

\end{thebibliography}

\end{document}
