\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature-Implied Status for Question CIC}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_18}}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

\textbf{Literature-implied answer, human verification recommended.}

The source problem is Question CIC in Cwikel and Rochberg, \emph{Nigel Kalton and complex interpolation of compact operators}, arXiv:1410.4527. A recent preprint of Pustylnik, \emph{A new approach to interpolation of compact linear operators}, arXiv:2605.00530, appears to imply an affirmative answer.

\section*{Source Question}

For Banach couples \((X_0,X_1)\) and \((Y_0,Y_1)\), Cwikel and Rochberg write
\[
(X_0,X_1)\blacktriangleright(Y_0,Y_1)
\]
when every linear operator \(T:X_0+X_1\to Y_0+Y_1\) that is compact \(X_0\to Y_0\) and bounded \(X_1\to Y_1\) is compact
\[
[X_0,X_1]_\theta\to [Y_0,Y_1]_\theta
\]
for every \(0<\theta<1\). Their Question CIC asks whether this property holds for all Banach couples.

\section*{Supporting Paper}

The relevant source passages in arXiv:2605.00530 are:
\begin{itemize}
\item lines 270--284: the paper distinguishes two-sided compactness from one-sided compactness and says one-sided compactness requires condition (2);
\item lines 336--344: condition (2) is the estimate
\[
\|T\|_{A\to B}\le W(\|T\|_{A_0\to B_0},\|T\|_{A_1\to B_1}),
\]
with \(W(\alpha,\beta)\to0\) as \(\beta\to0\) for bounded \(\alpha\), and the complex interpolation functor is explicitly covered with \(W(\alpha,\beta)=\alpha^{1-\theta}\beta^\theta\);
\item lines 346--349: the Main Theorem concludes compactness of the interpolated embedding under these hypotheses;
\item lines 598--610: the paper passes from embedding operators to arbitrary linear operators via image spaces.
\end{itemize}

\section*{Identification}

Question CIC is the one-sided compactness problem for the complex interpolation functor. Pustylnik's one-sided theorem applies once condition (2) holds, and the paper explicitly states that condition (2) holds for the complex functor. The final image-space reduction then converts the embedding theorem into the corresponding statement for arbitrary operators. Thus, if arXiv:2605.00530 is correct as stated, it gives a full affirmative answer to Question CIC.

\section*{Caveat}

This is not presented in arXiv:2605.00530 as an explicit answer to Cwikel--Rochberg's Question CIC, and the supporting paper is a recent broad preprint about a famously difficult problem. This packet should therefore be treated as a literature-implied claimed answer pending human review of the proof.

\begin{thebibliography}{9}
\bibitem{CR1410}
M. Cwikel and R. Rochberg,
\emph{Nigel Kalton and complex interpolation of compact operators},
arXiv:1410.4527, 2014.

\bibitem{P2605}
E. Pustylnik,
\emph{A new approach to interpolation of compact linear operators},
arXiv:2605.00530, 2026.
\end{thebibliography}

\end{document}
