\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=0.78in]{geometry}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{microtype}

\title{The Lorentz endpoint problem for elliptic canceling operators\\
\large Exact positive answer in later literature}
\author{Literature-status note for \texttt{fa\_banach\_001}}
\date{21 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.9\textwidth}{\textbf{Status: literature already answered.}
Stolyarov's endpoint Hardy--Littlewood--Sobolev theorem gives the estimate in
Spector's Open Problem 7.3 for every elliptic canceling operator. This is not
an original result of the run.}}
\end{center}

\section*{Original question}

Spector asks in Open Problem 7.3, page 19 of arXiv:1903.09292 \cite{Spector}:
if $d\geq 3$ and the first-order homogeneous constant-coefficient operator
\[
 A(D):C_c^\infty(\mathbb R^d;V)\longrightarrow
 C_c^\infty(\mathbb R^d;E)
\]
is elliptic and canceling, must there be a constant $C$ such that
\[
 \|u\|_{L^{d/(d-1),1}(\mathbb R^d;V)}
 \leq C\|A(D)u\|_{L^1(\mathbb R^d;E)}
 \qquad(u\in C_c^\infty(\mathbb R^d;V))?
\]
The source identifies this as, in particular, Van Schaftingen's Open
Problem 8.3.

\section*{Exact later answer}

For an elliptic homogeneous operator $A$ of order $m$, Stolyarov associates
the smooth Fourier-restriction field
\[
 \Omega(\zeta)=\operatorname{Im}\mathbb A(\zeta),
 \qquad \zeta\in S^{d-1}.
\]
Canceling means precisely
$\bigcap_{\zeta\in S^{d-1}}\Omega(\zeta)=\{0\}$.
Corollary 1.7 of arXiv:2010.05297 \cite{Stolyarov}, obtained from the stronger
Theorem 1.1, proves the optimal Lorentz endpoint embedding.  In the elliptic
differential-operator case its stated consequence is
\[
 \|\nabla^{m-1}u\|_{L^{d/(d-1),1}}
 \lesssim \|A(D)u\|_{L^1}.
\]
Taking $m=1$ makes $\nabla^{m-1}u=u$ and gives exactly Spector's requested
inequality (indeed in every $d\geq2$ where the formulation applies).

The supporting paper also states immediately after Corollary 1.7 that, for
the rational field $\Omega$ coming from an elliptic differential operator and
$\alpha=1$, the corollary solves Van Schaftingen's Open Problem 8.3. Thus the
problem-number cross-reference and the formula both match the source question.

\begin{thebibliography}{9}
\bibitem{Spector}
D. Spector,
\emph{New Directions in Harmonic Analysis on $L^1$},
arXiv:1903.09292 (2019), Open Problem 7.3.

\bibitem{Stolyarov}
D. M. Stolyarov,
\emph{Hardy--Littlewood--Sobolev inequality for $p=1$},
arXiv:2010.05297v3 (2021), Theorem 1.1 and Corollary 1.7;
Sb. Math. 213 (2022), 844--889.
\end{thebibliography}

\end{document}
