\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Scope note}
\newcommand{\ellp}{\ell_p}
\title{A literature-implied answer to Tokarev's singleton-spectrum problem}
\author{Automated mathematical discovery run \texttt{fa\_banach\_001}, lane 7}
\date{21 July 2026}

\begin{document}
\maketitle

\paragraph{Source question.}
Tokarev \cite{Tokarev} defines the $\ell_p$-spectrum of an infinite-dimensional
Banach space $X$ by
\[
  S(X)=\{p:\ell_p\text{ is finitely representable in }X\}.
\]
His Problem~2 asks whether there is a non-superreflexive Banach space $X$
with $S(X)=\{2\}$.  This is stated as a weaker companion to Problem~1,
which asks for a non-superreflexive space with the hereditary approximation
property (HAP).

\paragraph{Later input.}
Johnson and Szankowski \cite[p.~1999, immediately after Question~3]{JS}
recall that there exist nonreflexive Banach spaces of type $2-\varepsilon$
and cotype $2+\varepsilon$ for every $\varepsilon>0$, citing the construction
of Pisier and Xu \cite{PX}.  The following standard argument identifies this
as a positive answer to Tokarev's Problem~2.

\begin{theorem}
Let $X$ be an infinite-dimensional Banach space such that
\begin{enumerate}
  \item $X$ has type $r$ for every $1\le r<2$, and
  \item $X$ has cotype $s$ for every $2<s<\infty$.
\end{enumerate}
Then $S(X)=\{2\}$.  Consequently, any nonreflexive Pisier--Xu space recalled
in \cite{JS} is a non-superreflexive positive example for Tokarev's
Problem~2.
\end{theorem}

\begin{proof}
Dvoretzky's theorem says that $\ell_2$ is finitely representable in every
infinite-dimensional Banach space, so $2\in S(X)$.

Suppose first that $1\le p<2$ and $\ell_p$ were finitely representable in
$X$.  Choose $r$ with $p<r<2$.  A type-$r$ inequality is a uniform
finite-dimensional inequality, so it passes to every space finitely
representable in $X$.  Hence $\ell_p$ would have type $r$.  This is
impossible: the supremal type exponent of $\ell_p$ is $p$.

Now suppose that $2<p<\infty$ and $\ell_p$ were finitely representable in
$X$.  Choose $s$ with $2<s<p$.  Cotype-$s$ inequalities likewise pass under
finite representability, so $\ell_p$ would have cotype $s$.  This contradicts
the fact that the infimal cotype exponent of $\ell_p$ is $p$.  Finally,
$\ell_\infty$ cannot be finitely representable in $X$, because $X$ has (for
example) cotype $3$, while $\ell_\infty$ has no finite cotype.  Thus no
exponent other than $2$ belongs to $S(X)$.

Johnson--Szankowski's cited example is nonreflexive.  Since every
superreflexive space is reflexive, it is non-superreflexive, completing the
identification.
\end{proof}

\begin{remark}
This settles only Tokarev's Problem~2.  The HAP question remains genuinely
stronger.  Johnson--Szankowski ask whether every HAP space is reflexive and
explicitly state that this problem remains open \cite[p.~1988]{JS}.
\end{remark}

\paragraph{Verification and novelty status.}
The implication from the near-Hilbert type/cotype profile to $S(X)=\{2\}$ is
an elementary finite-representability argument.  The existence input is from
the cited literature, so this packet is classified as a
\emph{literature-implied answer}, not as a new construction.  Cheap run
indexes contained no packet for arXiv:math/0206108, and bounded searches for
the HAP/nonreflexivity question found no later exact primary-source solution.

\begin{thebibliography}{9}
\bibitem{Tokarev}
E.~Tokarev,
\emph{An example of a Banach Space with a Subsymmetric Basis, which has the
Hereditarily Approximation Property}, arXiv:math/0206108 (2002).

\bibitem{JS}
W.~B. Johnson and A.~Szankowski,
\emph{Hereditary approximation property},
Ann. of Math. (2) \textbf{176} (2012), 1987--2001.

\bibitem{PX}
G.~Pisier and Q.~H. Xu,
\emph{Random series in the real interpolation spaces between the spaces
$v_p$}, in \emph{Geometrical Aspects of Functional Analysis (1985/86)},
Lecture Notes in Math. 1267, Springer, 1987, 185--209.
\end{thebibliography}

\end{document}

