\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\diag}{\operatorname{diag}}

\title{Sharpness of the \(k/4\) Triangle Constant for Contractions}
\author{FA/Banach run packet}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Source Question}

Bourin and Lee \cite[Corollary 4.4]{BL} prove that, for contractions
\(A_1,\ldots,A_k\in M_n\), \(k>1\),
\[
  \left|\sum_{j=1}^k A_j\right|
  \leq \frac{k}{4}I+\sum_{j=1}^k |A_j|.
\]
They prove that the constant \(k/4\) is sharp for even \(k\), and conjecture
that it is also sharp for odd \(k>1\).  The abstract singles out the case
\(k=3\), where the conjectured optimal constant is \(3/4\).

\section*{Result}

\begin{theorem}
For every integer \(k>1\), the constant \(k/4\) in the Bourin--Lee triangle
inequality is optimal.  More precisely, over complex matrices, there are
rank-one contractions \(A_0,\ldots,A_{k-1}\in M_2(\C)\) such that any inequality
\[
  \left|\sum_{j=0}^{k-1} A_j\right|
  \leq c I+\sum_{j=0}^{k-1}|A_j|
\]
forces \(c\geq k/4\).
\end{theorem}

\begin{proof}
Let \(e_1,e_2\) be the standard basis of \(\C^2\), let
\(\zeta=\exp(2\pi i/k)\), and put
\[
  v_j=\frac{1}{2}e_1+\frac{\sqrt3}{2}\zeta^j e_2,\qquad
  u=e_1,\qquad
  A_j=uv_j^*
\]
for \(j=0,\ldots,k-1\).  Each \(v_j\) is a unit vector, so each \(A_j\) is a
rank-one contraction.  Moreover
\[
  A_j^*A_j=v_jv_j^*,
  \qquad
  |A_j|=v_jv_j^*.
\]
Since \(k>1\), \(\sum_{j=0}^{k-1}\zeta^j=0\).  Hence
\[
  \sum_{j=0}^{k-1}A_j
  =
  u\left(\sum_{j=0}^{k-1}v_j\right)^*
  =\frac{k}{2}e_1e_1^*,
\]
and therefore
\[
  \left|\sum_{j=0}^{k-1}A_j\right|
  =\frac{k}{2}e_1e_1^*.
\]
On the other hand, the off-diagonal terms in \(\sum_j v_jv_j^*\) vanish by the
same roots-of-unity identity, giving
\[
  \sum_{j=0}^{k-1}|A_j|
  =
  \sum_{j=0}^{k-1}v_jv_j^*
  =
  \begin{pmatrix}
    k/4 & 0\\
    0 & 3k/4
  \end{pmatrix}.
\]
If the displayed inequality with constant \(c\) holds for this family, then
taking the quadratic form at \(e_1\) gives
\[
  \frac{k}{2}
  \leq c+\frac{k}{4}.
\]
Thus \(c\geq k/4\).  Since the Bourin--Lee corollary proves the inequality with
\(c=k/4\), the constant is optimal.
\end{proof}

\begin{corollary}
The odd-\(k\) conjecture in \cite{BL} is true. In particular, for three
contractions the constant \(3/4\) cannot be decreased.
\end{corollary}

\section*{Real Matrices}

For odd \(k\geq3\), the same argument has a real \(3\times3\) version.  Let
\[
  v_j=\frac{1}{2}e_1+\frac{\sqrt3}{2}
  \left(\cos \frac{2\pi j}{k}\,e_2+\sin \frac{2\pi j}{k}\,e_3\right),
  \qquad
  A_j=e_1v_j^T.
\]
The vertices of the regular \(k\)-gon have zero sum, and
\[
  \sum_{j=0}^{k-1} |A_j|
  =
  \diag(k/4,3k/8,3k/8),\qquad
  \left|\sum_{j=0}^{k-1}A_j\right|=\frac{k}{2}e_1e_1^T.
\]
Evaluating at \(e_1\) again forces \(c\geq k/4\).

\section*{Scope}

This packet settles the optimality of the additive constant in the triangle
inequality for contractions.  It does not address separate sharpness questions
for other eigenvalue inequalities in \cite{BL}.

\begin{thebibliography}{9}

\bibitem{BL}
J.-C. Bourin and E.-Y. Lee,
\emph{Diagonal and off-diagonal blocks of positive definite partitioned matrices},
arXiv:2307.02034; Linear Algebra Appl. 684 (2024), 87--100.

\end{thebibliography}

\end{document}
