\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{claim}{Claim}

\begin{document}

\begin{center}
{\Large Literature-implied partial answer for arXiv:2206.10279}\\[3pt]
{\large The skein free space is not Dirac-witnessed Plichko}
\end{center}

\paragraph{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.

\paragraph{Source question.}
The source is P. Hajek and A. Quilis, \emph{A complete metric space without
non-trivial separable Lipschitz retracts}, arXiv:2206.10279 \cite{HQ22}.
In the Introduction, parsed source lines 110--115, the authors recall the
Plichko property and the Separable Complementation Property (SCP), state that
they do not know examples of Lipschitz-free spaces over metric spaces failing
to be Plichko, and ask in particular whether the Lipschitz-free space over
their constructed metric space is Plichko, or even has the SCP.

\paragraph{Supporting theorem.}
The supporting paper is A. J. Guirao, V. Montesinos, and A. Quilis,
\emph{On projectional skeletons and the Plichko property in Lipschitz-free
Banach spaces}, arXiv:2305.08543 \cite{GMQ23}.  Theorem 2.1 of
\cite{GMQ23} says, among other equivalent conditions, that for a complete
pointed metric space \(M\) and \(\lambda\geq 1\), the free space
\(\mathcal F(M)\) is \(\lambda\)-Plichko witnessed by a subset of
\(\delta(M)\) if and only if for every \(p\in M\) and every
\(r<1/\lambda\), the ball
\[
        B\bigl(p,r\,d(p,0)\bigr)
\]
is separable.

\begin{claim}
Let \(M=\operatorname{Sk}(\omega_1)\) be the skein metric space constructed in
\cite{HQ22}, pointed at the initial anchor \(A\).  Then \(\mathcal F(M)\) is
not \(\lambda\)-Plichko witnessed by Dirac measures for any finite
\(\lambda\geq 1\).
\end{claim}

\begin{proof}
Let \(B\) be the other initial anchor of the \(0\)-skein.  In the construction
of \cite{HQ22}, \(d(A,B)=1/2\), and the first successor stage attaches the
threading space \(\operatorname{Th}(A,B)\).  This threading space contains,
for every \(\gamma\in\Delta\), a thread \(T_\gamma(A,B)\) of width \(1/2\);
different such threads meet exactly in the two anchors \(A,B\).  The set
\(\Delta\) is uncountable.

We first note that \(B\) is not isolated inside any \(T_\gamma(A,B)\).  Indeed,
in the real model \(T_\gamma\subset[0,1]\), the complement is the union of the
gaps \(G_i^\gamma=(q_{n_i},q_{n_i}+\gamma_i)\), each lying strictly inside
\((0,1)\), and Proposition 2.6 of \cite{HQ22} identifies these gaps as the
components of the complement.  If a terminal interval \((1-\varepsilon,1)\)
were disjoint from \(T_\gamma\), connectedness of that interval would force it
to lie in a single complementary component whose right endpoint is \(1\), which
is impossible.

Fix \(\lambda\geq 1\).  Choose \(r>0\) with
\[
        r<\min\{1/\lambda,1/4\},
\]
and put \(\rho=r\,d(B,A)=r/2\).  For each \(\gamma\in\Delta\), choose a
non-anchor point \(x_\gamma\in T_\gamma(A,B)\) such that
\[
        0<d(x_\gamma,B)<\rho .
\]
Split these choices into the countably many annuli
\[
        \frac{\rho}{n+1}\leq d(x_\gamma,B)<\frac{\rho}{n},
        \qquad n=1,2,\ldots .
\]
Since \(\Delta\) is uncountable, one annulus contains \(x_\gamma\)'s for an
uncountable set \(\Delta_0\subset\Delta\).  If \(\gamma\neq\eta\) are in
\(\Delta_0\), the attachment formula for distinct threads in
\(\operatorname{Th}(A,B)\) gives
\[
 d(x_\gamma,x_\eta)
 =\min\{d(x_\gamma,A)+d(A,x_\eta),\,
        d(x_\gamma,B)+d(B,x_\eta)\}.
\]
The second term is at least \(2\rho/(n+1)\).  The first term is bounded below
by \(2(1/2-\rho)>0\), because \(d(A,B)=1/2\) and \(d(x_\gamma,B)<\rho<1/8\).
Thus the set \(\{x_\gamma:\gamma\in\Delta_0\}\) is uncountable and uniformly
separated, while it is contained in \(B(B,\rho)=B(B,r\,d(B,A))\).  Therefore
this ball is nonseparable.

The local separability condition in Theorem 2.1 of \cite{GMQ23} fails for the
point \(p=B\) and the above \(r<1/\lambda\).  Hence \(\mathcal F(M)\) is not
\(\lambda\)-Plichko witnessed by a subset of \(\delta(M)\).  Since
\(\lambda\geq 1\) was arbitrary, no finite Dirac-witnessed Plichko constant is
possible.
\end{proof}

\paragraph{Scope and limitations.}
This is not a full answer to the source question.  It rules out only Plichko
witnesses supported on Dirac measures.  It does not rule out a Plichko witness
using molecules or more general vectors in \(\mathcal F(M)\), and it does not
decide whether \(\mathcal F(M)\) has the SCP.

\paragraph{Search and provenance.}
The relation above is not stated as an answer to arXiv:2206.10279 in
\cite{GMQ23}; it is an agent-identified implication of Theorem 2.1 combined
with the local geometry of the skein construction.  Web searches for
``Lipschitz-free spaces fail to be Plichko'', ``F(ell\_infty) Plichko SCP'',
and close variants found the 2023 supporting paper, which still states that
the unrestricted Plichko and SCP questions remain open.

\begin{thebibliography}{9}

\bibitem{HQ22}
P. Hajek and A. Quilis,
\emph{A complete metric space without non-trivial separable Lipschitz
retracts}, arXiv:2206.10279, 2022.

\bibitem{GMQ23}
A. J. Guirao, V. Montesinos, and A. Quilis,
\emph{On projectional skeletons and the Plichko property in Lipschitz-free
Banach spaces}, arXiv:2305.08543, 2023.

\end{thebibliography}

\end{document}
