\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}
\begin{document}

\begin{center}
{\Large\bfseries BFU is not a three-space property}\par
\vspace{0.4em}
{\small Source question: arXiv:0804.2832 \qquad Supporting theorem: arXiv:1612.05948}
\end{center}

\textbf{Status.} Full negative answer implied by later literature; no new
mathematical result is claimed here.

\textbf{Source question.} Burshteyn defines a Banach space $X$ to be BFU
when every norm-bounded subset of $X^*$ is Fréchet--Urysohn in
$\sigma(X^*,X)$.  In Section~6, ``Open Problems,'' p.~89, he asks whether
this is a three-space property: if a closed subspace $Y$ and $X/Y$ are BFU,
must $X$ be BFU?

This is the standard property that $X$ has a weak-star angelic dual ball.

\textbf{Counterexample from a later theorem.} Martínez-Cervantes proves in
Theorem~4 of \emph{Banach spaces with weak*-sequential dual ball} that the
Johnson--Lindenstrauss space $JL_2$ has weak-star sequential order exactly
$2$.  The proof records both
\[
 JL_2/c_0\cong \ell_2(\Gamma)
 \quad\text{and}\quad
 JL_2\text{ does not have weak-star angelic dual}.
\]
Consequently the exact sequence
\[
 0\longrightarrow c_0\longrightarrow JL_2
   \longrightarrow \ell_2(\Gamma)\longrightarrow 0
\]
has BFU kernel and quotient: $c_0$ is separable, and $\ell_2(\Gamma)$ is
reflexive.  Its middle space is not BFU.  Hence the BFU property is not a
three-space property.

\textbf{Provenance.} The supporting paper does not cite or name the 2008
question.  The answer is therefore a direct identification of a later
theorem with the source problem, rather than an explicit literature answer.

\end{document}

