\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\newcommand{\Gen}{\operatorname{Gen}}
\newcommand{\dens}{\operatorname{dens}}
\newcommand{\ellTwo}{\ell_2}

\title{An ALUR Universality Reduction for Generating Operators}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_14}}
\date{2026-06-29}

\begin{document}
\maketitle

\section*{Source Question}

Kadets, Martin, Meri, and Quero ask in arXiv:2306.02645, after their
Proposition 4.4, whether for a cardinal $\Gamma$ there is a Banach space
$Y$ with $\dens(Y)=\Gamma$ such that
\[
  \Gen(X,Y)\neq\varnothing
\]
for every Banach space $X$ satisfying $\dens(X)\leq \Gamma$.
Here $\Gen(X,Y)$ denotes the norm-one generating operators from $X$ to $Y$.

\section*{Definitions Used}

A Banach space is ALUR, or average locally uniformly rotund, when every point
of its unit sphere is a denting point of its unit ball.  The source paper
records the standard equivalence and proves the following corollary
(\texttt{cor:domain-LUR} in the source): if $X$ is ALUR, then every
generating operator $G\colon X\to Y$ is an isometric embedding.

\section*{Proof Intuition}

The density-character question is phrased in terms of generating operators,
which are a priori weaker than isometric embeddings.  However, the weakening
disappears on ALUR domains.  On such spaces, the source paper's denting-point
criterion forces a generating operator to preserve the norm at every unit
vector, hence to be an isometry.  Therefore any single range space $Y$ that
works for all domains of density at most $\Gamma$ must already be isometrically
universal for the ALUR members of that class.

\begin{theorem}[ALUR universality reduction]
Let $\Gamma$ be a cardinal and let $Y$ be a Banach space such that
$\Gen(X,Y)\neq\varnothing$ for every Banach space $X$ with
$\dens(X)\leq\Gamma$.  Then every ALUR Banach space $X$ with
$\dens(X)\leq\Gamma$ embeds linearly isometrically into $Y$.
\end{theorem}

\begin{proof}
Fix an ALUR Banach space $X$ with $\dens(X)\leq\Gamma$.  By the assumed
property of $Y$, there is a generating operator $G\in\Gen(X,Y)$.  By
Corollary \texttt{cor:domain-LUR} of the source paper, every generating
operator whose domain is ALUR is an isometric embedding.  Hence $G$ is a
linear isometry from $X$ into $Y$.
\end{proof}

\begin{corollary}
If a Banach space $Y$ of density $\Gamma$ answers the source question
positively, then $Y$ contains an isometric copy of $\ell_2(\kappa)$ for every
cardinal $\kappa\leq\Gamma$.
\end{corollary}

\begin{proof}
Hilbert spaces are uniformly convex, hence ALUR, and
$\dens(\ell_2(\kappa))=\kappa$ for infinite $\kappa$.
\end{proof}

\section*{Verification Notes}

The proof uses only the source paper's own Corollary
\texttt{cor:domain-LUR} and the exact density-character question stated
after Proposition 4.4.  No additional set-theoretic assumption is used.

This is a necessary condition, not a positive or negative solution of the
source question.  It says that any positive answer must be at least as strong
as isometric universality on the ALUR subcategory, so non-isometric generating
operators cannot bypass isometric universality for ALUR domains.

\section*{Novelty and Duplicate Check}

The run's lightweight indexes were searched for \texttt{2306.02645},
\texttt{generating operators}, \texttt{Gen(X,Y)}, density-character wording,
and universal-space keywords.  The only exact hit was the prior attempt
\texttt{2306.02645\_density\_character\_generating\_operators\_no\_promotion.md}.
That attempt records the invalid universal compact-space shortcut and does
not contain the ALUR universality reduction stated here.

\section*{Limitations}

The result does not prove that such a range space $Y$ exists, nor does it
prove nonexistence in ZFC.  It also does not reduce the question to
isometric universality for all Banach spaces, only for the ALUR subclass.

\section*{Reference}

V. Kadets, M. Martin, J. Meri, and A. Quero, \emph{Generating operators
between Banach spaces}, arXiv:2306.02645.

\end{document}

