\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.7em}

\newtheorem*{claim}{Claim}

\begin{document}

\begin{center}
{\Large Literature-Already-Answered Packet}\\[0.25em]
{\large Vector-valued dimension-free Hardy--Littlewood maximal bounds on the Heisenberg group}\\[0.35em]
\textbf{Status:} literature already answered, not a new automatic-discovery result
\end{center}

\section*{Source question}

The source paper is arXiv:1703.08327, Deleaval--Kriegler,
\emph{Dimension free bounds for the vector-valued Hardy--Littlewood maximal
operator}.
It proves dimension-free Fefferman--Stein inequalities on Euclidean spaces and
for Grushin maximal operators. In the final paragraph, the authors point to the
centered Hardy--Littlewood maximal operator on the Heisenberg group and say
that they do not know whether this operator admits dimension-free
\(\ell^q\)-valued or UMD Banach lattice-valued estimates.

\section*{Later answer}

The later paper is arXiv:2503.15291, Ganguly--Ghosh,
\emph{Dimension free estimates for the vector-valued Hardy--Littlewood maximal
function on the Heisenberg group}.
The supporting TeX source is included at
\[
\texttt{source\_tex/supporting\_2503.15291.tex}.
\]

Ganguly--Ghosh explicitly cite the Heisenberg-group analogue left open by
Deleaval--Kriegler as the motivating open problem. They work on
\(\mathbb H^n\) and define the centered Hardy--Littlewood maximal operator
using Koranyi balls.

\begin{claim}
For every \(1<p,q<\infty\), the centered Hardy--Littlewood maximal operator on
\(\mathbb H^n\) satisfies the Fefferman--Stein inequality
\[
\left\|\left(\sum_j |\mathcal M f_j|^q\right)^{1/q}\right\|_{L^p(\mathbb H^n)}
\le C(p,q)
\left\|\left(\sum_j |f_j|^q\right)^{1/q}\right\|_{L^p(\mathbb H^n)},
\]
where \(C(p,q)\) is independent of \(n\).
\end{claim}

This is Theorem 1.1 of arXiv:2503.15291.

\begin{claim}
If \(Z\) is a UMD Banach lattice and \(1<p<\infty\), then the corresponding
UMD-lattice-valued centered Hardy--Littlewood maximal operator on
\(\mathbb H^n\) is bounded on \(L^p(\mathbb H^n;Z)\) with a constant
\(C(p,Z)\) independent of \(n\).
\end{claim}

This is Theorem 1.2 of arXiv:2503.15291.

\section*{Metric variant}

The source question cites earlier Heisenberg maximal-function papers rather
than pinning the question to only one Heisenberg ball model. Ganguly--Ghosh's
main results are stated for Koranyi balls. Their concluding remarks also state
the same dimension-free \(\ell^q\) and UMD-lattice-valued estimates for
Hardy--Littlewood maximal averages over Carnot--Caratheodory balls.

\section*{Classification}

This packet records a later-literature resolution of the source paper's
explicit ``we do not know'' signal. It should not be counted as a new proof by
this run.

\end{document}
