\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\FBL}{\mathrm{FBL}}
\newcommand{\ellp}{\ell}

\title[Diestel LWCG question answered by free Banach lattices]{Diestel's LWCG versus WCG question from arXiv:1512.08628 is answered by arXiv:1706.08147}
\author{fa\_banach\_001, agent\_super\_01}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet.  Aviles--Guirao--Lajara--Rodriguez--Tradacete
\cite{AGLRT2016} state Diestel's question: is every lattice weakly compactly
generated Banach lattice weakly compactly generated as a Banach space?  A
later paper of Aviles--Rodriguez--Tradacete \cite{ART2017} explicitly gives a
negative answer.

\section*{Source question}

In Section 1 of \cite{AGLRT2016}, the authors define a Banach lattice \(X\) to
be lattice weakly compactly generated (LWCG) if \(X=L(K)\) for some weakly
compact \(K\subset X\).  They record the implications
\[
  \mathrm{WCG}\Rightarrow \mathrm{LWCG}\Rightarrow \mathrm{IWCG}\Rightarrow
  \mathrm{BWCG},
\]
and state that the equivalence between LWCG and WCG for general Banach
lattices was an open question raised by J. Diestel at the 2011 La Manga
conference.

\section*{Supporting answer}

The introduction of \cite{ART2017} restates the problem as Problem 1.1:
\[
  \text{Is every LWCG Banach lattice WCG?}
\]
It then says that the paper provides a negative answer.  The precise result is
Corollary 5.5 of \cite{ART2017}: if \(\Gamma\) is uncountable and
\(1<p\leq 2\), then
\[
  \FBL[\ell_p(\Gamma)]
\]
is LWCG but is not isomorphic to a subspace of any WCG Banach space.  In
particular it is not WCG.  Taking \(p=2\) gives a direct counterexample to
Diestel's question as quoted in \cite{AGLRT2016}.

\section*{Scope}

This answers the general LWCG \(=\) WCG question negatively.  It does not make
the other structural questions in \cite{AGLRT2016} obsolete, such as the
separate question of whether an LWCG Banach lattice can contain a sublattice
isomorphic to \(\ell_\infty\), or the positive order-continuous/Dedekind
complete subcases proved in the source.

\section*{Search notes}

The cheap run indexes had no packet for arXiv:1512.08628 itself.  A nearby
packet records that the residual final questions of \cite{ART2017} about
\(\FBL[c_0(\Gamma)]\) and \(\FBL[\ell_p(\Gamma)]\), \(p>2\), are answered by
arXiv:1806.02553.  That is distinct from this packet, which records the
earlier negative answer to Diestel's original LWCG versus WCG question from
\cite{AGLRT2016}.

\begin{thebibliography}{9}

\bibitem{AGLRT2016}
A. Aviles, A. J. Guirao, S. Lajara, J. Rodriguez, and P. Tradacete,
\emph{Weakly compactly generated Banach lattices},
Studia Math. 234 (2016), no. 2, 165--183; arXiv:1512.08628.

\bibitem{ART2017}
A. Aviles, J. Rodriguez, and P. Tradacete,
\emph{The free Banach lattice generated by a Banach space},
J. Funct. Anal. 274 (2018), no. 10, 2955--2977; arXiv:1706.08147.

\end{thebibliography}

\end{document}
