\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Status Note for arXiv:1903.01761}
\author{run fa\_banach\_001, agent\_lane\_14}
\date{2026-06-29}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer} (partial subcases/status update). This is
not an original proof and not a full answer to the unrestricted Daugavet
tensor-product question.

\paragraph{Source/open-problem metadata.}
Abraham Rueda Zoca, Pedro Tradacete, and Ignacio Villanueva, ``Daugavet
property in tensor product spaces,'' arXiv:1903.01761. In the introduction,
Question~1 asks whether, whenever Banach spaces \(X\) and \(Y\) both have the
Daugavet property, the tensor products
\[
  X\widehat{\otimes}_{\varepsilon}Y
  \quad\text{and}\quad
  X\widehat{\otimes}_{\pi}Y
\]
also have the Daugavet property.

\paragraph{Supporting projective WODP metadata.}
Miguel Martin and Abraham Rueda Zoca, ``Daugavet property in projective
symmetric tensor products of Banach spaces,'' arXiv:2010.15936; Banach
J. Math. Anal. 16 (2022), article 35. Section~5 introduces the weak operator
Daugavet property (WODP). Theorem~5.4, labelled \texttt{theorem:WODP} in the
source, proves that if \(X\) and \(Y\) have WODP, then
\[
  X\widehat{\otimes}_{\pi}Y
\]
has WODP. Since WODP implies the Daugavet property, this gives a positive
projective-tensor subcase of the source question under the stronger WODP
hypothesis.

\paragraph{Supporting injective WODP metadata.}
Abraham Rueda Zoca, ``Weak operator Daugavet property and weakly open sets in
tensor product spaces,'' arXiv:2407.21585. Theorem \texttt{theo:daugainjective}
proves that if \(X^*\) and \(Y^*\) have WODP, then
\[
  X\widehat{\otimes}_{\varepsilon}Y
\]
has the Daugavet property. Remark \texttt{remark:mejoratrada} explicitly says
that this improves the \(L_1(\mu)\widehat{\otimes}_{\varepsilon}L_1(\nu)\)
case proved as Theorem~1.1 in arXiv:1903.01761.

\paragraph{Supporting transfinite projective metadata.}
Antonio Aviles, Johann Langemets, Miguel Martin, and Abraham Rueda Zoca,
``Transfinite Daugavet property,'' arXiv:2604.14102. In the section
``Tensor products,'' Theorem \texttt{theo:tensorprolargeDP} proves that for an
infinite cardinal \(\kappa\), if \(X\) and \(Y\) are injective Banach spaces
with the \(\kappa\)-Daugavet property, then
\[
  X\widehat{\otimes}_{\pi}Y
\]
has the \(\kappa\)-Daugavet property; the same is proved for the
\(\kappa\)-perfect Daugavet property.

\paragraph{Identification.}
The 2022 WODP theorem directly answers the projective half of the source
question for WODP factors. The 2024 WODP theorem directly answers the
injective half when both dual spaces have WODP, and the supporting paper
explicitly identifies this as an improvement of the 1903 \(L_1\)-space theorem.
The 2026 theorem gives a further projective-tensor subcase for injective spaces
with a transfinite strengthening of the Daugavet property. These are genuine
positive pieces around Question~1, but they do not remove the stronger
hypotheses.

\paragraph{Scope limitations.}
The unrestricted problem remains open in this packet: no checked supporting
source proves that \(X\widehat{\otimes}_{\pi}Y\) or
\(X\widehat{\otimes}_{\varepsilon}Y\) has the Daugavet property for arbitrary
Daugavet spaces \(X,Y\). This packet also does not settle whether every
Daugavet space has WODP or ODP.

\paragraph{Search evidence.}
The run indexes were searched for \texttt{1903.01761},
\texttt{Daugavet property}, \texttt{projective tensor},
\texttt{injective tensor}, \texttt{WODP}, and
\texttt{weak operator Daugavet}. No existing packet covered this target. Local
source search then identified arXiv:2010.15936, arXiv:2407.21585, and
arXiv:2604.14102 as the decisive later literature for these scoped positive
answers.

\begin{thebibliography}{9}
\bibitem{RTV2019}
A. Rueda Zoca, P. Tradacete, and I. Villanueva,
``Daugavet property in tensor product spaces,''
J. Inst. Math. Jussieu 20 (2021), 1409--1428; arXiv:1903.01761.

\bibitem{MR2022}
M. Martin and A. Rueda Zoca,
``Daugavet property in projective symmetric tensor products of Banach
spaces,'' Banach J. Math. Anal. 16 (2022), article 35; arXiv:2010.15936.

\bibitem{RZ2024}
A. Rueda Zoca,
``Weak operator Daugavet property and weakly open sets in tensor product
spaces,'' arXiv:2407.21585.

\bibitem{ALMRZ2026}
A. Aviles, J. Langemets, M. Martin, and A. Rueda Zoca,
``Transfinite Daugavet property,'' arXiv:2604.14102.
\end{thebibliography}

\end{document}
