\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note:\\The 3D Heisenberg \(L_1\) Distortion Conjecture}
\author{fa\_banach\_001, agent\_lane\_07}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature\_already\_answered.}
The \(L_1\)-distortion conjecture in Lafforgue--Naor,
\emph{Vertical versus horizontal Poincaré inequalities on the Heisenberg
group}, arXiv:1212.2107, is answered negatively by Naor--Young,
\emph{Foliated corona decompositions}, arXiv:2004.12522.

\section*{Source Question}

In Section 4, Lafforgue--Naor ask whether the endpoint \(p=1\)
vertical-versus-horizontal inequality holds for smooth compactly supported
real-valued functions on the real 3-dimensional Heisenberg group. They
reformulate this as an isoperimetric question and state Conjecture 4.4:
\[
  c_1(B_n,d_W)\asymp \sqrt{\log n}
  \qquad(n\ge 2),
\]
where \(B_n\) is the radius \(n\) word ball in the discrete 3-dimensional
Heisenberg group.

\section*{Supporting Answer}

The supporting paper is Assaf Naor and Robert Young,
\emph{Foliated corona decompositions}, arXiv:2004.12522. Its introduction
explicitly says that the asymptotic evaluation of
\(c_{\ell_1}(\mathcal B_n)\) had been asked in the Lafforgue--Naor line of
references and that most of those references conjectured the
\(\sqrt{\log n}\) behavior.

The decisive statement is Theorem 1.6:
\[
  c_{\ell_1}(\mathcal B_n)\asymp \sqrt[4]{\log n}
  \qquad\text{for every integer } n\ge 2.
\]
Here \(\mathcal B_n\) is the word ball in the same discrete
3-dimensional Heisenberg group.

\section*{Conclusion}

Naor--Young's two-sided estimate gives the exact exponent \(1/4\). Therefore
the Lafforgue--Naor conjectural conclusion
\[
  c_1(B_n,d_W)\asymp \sqrt{\log n}
\]
is false for the 3-dimensional Heisenberg group. Consequently the endpoint
Question 4.1, the isoperimetric Question 4.2, and the coarse total vertical
perimeter Conjecture 4.3 cannot all hold in a form that implies Conjecture 4.4
as stated.

\section*{Scope}

This is a literature answer rather than a new proof from the run. It concerns
the 3-dimensional Heisenberg group. Naor--Young also stress that the
5-dimensional Heisenberg group has \(L_1\)-distortion of order
\(\sqrt{\log n}\), so the dimension is essential.

\begin{thebibliography}{9}
\bibitem{LN}
V. Lafforgue and A. Naor,
\emph{Vertical versus horizontal Poincaré inequalities on the Heisenberg
group},
Israel J. Math. 203 (2014), 309--339; arXiv:1212.2107.

\bibitem{NY}
A. Naor and R. Young,
\emph{Foliated corona decompositions},
arXiv:2004.12522.
\end{thebibliography}

\end{document}
