\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for arXiv:0705.0411: Finite-Space Maximal Negative Type}
\author{Run fa\_banach\_001, agent\_lane\_01}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet. It records that the
finite-metric-space endpoint question raised by Doust--Weston,
\emph{Enhanced negative type for finite metric trees}, arXiv:0705.0411v2, was
answered by Li--Weston, \emph{Strict \(p\)-negative type of a metric space},
arXiv:0901.0695v3.

\section*{Source Question}

In the Introduction and Synopsis of arXiv:0705.0411v2, page 3, Doust--Weston
explain that their infinite necklace tree \((Y,d)\) has strict
\(1\)-negative type but does not have \(p\)-negative type for any \(p>1\).
Thus, for general metric spaces, the maximal \(p\)-negative type can be
strict. They then ask:
\[
\text{Can the maximal \(p\)-negative type of a finite metric space be strict?}
\]

\section*{Supporting Answer}

Li--Weston, arXiv:0901.0695v3, explicitly builds on the enhanced negative
type method of Doust--Weston. Its abstract states that one of the paper's main
results is that the supremal \(p\)-negative type of a finite metric space
cannot be strict.

The exact answer appears in Section 4, titled ``Supremal \(p\)-negative type
of a finite metric space cannot be strict''. The paper first proves
Theorem~4.1: for a finite metric space \((X,d)\), strict \(p\)-negative type
is equivalent to positivity of the \(p\)-negative type gap
\(\Gamma_X^p\). Corollary~4.2 then shows that strict \(p\)-negative type at
\(p\) persists to an interval \([p,p+\zeta)\). Consequently Corollary~4.3,
on page 9, states:
\[
\text{The supremal \(p\)-negative type of a finite metric space cannot be strict.}
\]
This gives a negative answer to the source question: no finite metric space
has a strict endpoint for its maximal/supremal \(p\)-negative type.

\section*{Scope}

This is not a new proof produced by the run. It records an already-known
literature answer to the finite-metric-space strict-endpoint question in
arXiv:0705.0411v2. The answer is exact for finite metric spaces, hence also
covers finite metric trees as a subclass. It does not address unrelated open
problems about metric type, cotype, generalized roundness in other classes,
or non-commutative \(L_p\)-space analogues.

\section*{Search Evidence}

The lane-1 queue selected arXiv:0705.0411. Cheap run indexes were searched
using the arXiv id and the core phrases ``enhanced negative type'', ``finite
metric trees'', ``negative type'', ``metric trees'', and ``finite trees''; no
duplicate packet was found. A local corpus search for the core phrase
``maximal p-negative type'' identified arXiv:0901.0695v3. The supporting paper
explicitly cites Doust--Weston, identifies its refinement of enhanced negative
type, and states the finite-space non-strict endpoint result in its abstract,
Section 4, and Corollary~4.3.

\begin{thebibliography}{9}
\bibitem{DW07}
I.~Doust and A.~Weston,
\emph{Enhanced negative type for finite metric trees},
arXiv:0705.0411v2.

\bibitem{LW09}
H.~Li and A.~Weston,
\emph{Strict \(p\)-negative type of a metric space},
arXiv:0901.0695v3.
\end{thebibliography}

\end{document}
