\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\title{Literature Status: Fatou-Version Isometry Question for Symmetric Operator Spaces}
\author{fa\_banach\_001 lane 6}
\date{2026-07-18}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{literature\_already\_answered}, with the scope caveat that the later theorem is stated for strongly symmetric operator spaces having the Fatou property.

\paragraph{Original source.}
Huang and Sukochev, \emph{Hermitian operators and isometries on symmetric operator spaces}, arXiv:2101.03667; later JEMS 26 (2024), 3287--3325.  The extracted target is the remark after Example 4.12, near source lines 2496--2502, which asks whether Theorem \verb|th:iso| remains true under the weaker hypothesis that the symmetric operator spaces have Fatou norms only.  The original theorem classifies surjective isometries under order-continuity assumptions.

\paragraph{Supporting answer.}
Fang, Guo, Huang, and Sukochev, \emph{Isometric Structure in Noncommutative Symmetric Spaces}, arXiv:2512.20972.  In the introduction, immediately before Theorem \verb|11212|, the authors write that a goal of the paper is to treat the case where the norm on \(E(\mathcal M,\tau)\) is not necessarily order continuous.  Theorem \verb|11212| states that if \(\mathcal M_1,\mathcal M_2\) are atomless \(\sigma\)-finite von Neumann algebras, or \(\sigma\)-finite atomic von Neumann algebras whose atoms have the same trace, and \(E(\mathcal M_1,\tau_1)\), \(F(\mathcal M_2,\tau_2)\) are strongly symmetric operator spaces having the Fatou property and not proportional to \(L_2\), then every surjective isometry has the same elementary Jordan form as in the Huang--Sukochev theorem, with \(\sigma(F,F^\times)\)-convergent sums in the semifinite case and a finite-trace simplification.

\paragraph{Identification.}
This is a separate later paper, not a same-paper answer.  It cites the Huang--Sukochev JEMS paper as the order-continuous case, explicitly positions itself as handling the non-order-continuous case, and proves the corresponding elementary-isometry theorem under Fatou-property hypotheses.  Therefore the 2101.03667 remark is no longer a new-proof target in the standard strong-symmetric/Fatou-property formulation.

\paragraph{Limitations.}
The later statement uses ``Fatou property'' and ``strongly symmetric'' language.  This packet records a full literature answer for that formulation and does not separately settle any possible convention in which a bare ``Fatou norm'' assumption is strictly weaker than the hypotheses of Theorem \verb|11212|.

\paragraph{Evidence searched.}
Local cheap indexes had no prior packet for arXiv:2101.03667 or arXiv:2512.20972.  The local parsed source for arXiv:2512.20972 contains the explicit answer statement at source lines 391--412.  Web search for the title and keywords located the same arXiv preprint and public metadata for the original JEMS article.

\begin{thebibliography}{9}
\bibitem{HS}
J. Huang and F. Sukochev,
\emph{Hermitian operators and isometries on symmetric operator spaces},
arXiv:2101.03667; J. Eur. Math. Soc. 26 (2024), 3287--3325.

\bibitem{FGHS}
K. Fang, T. Guo, J. Huang, and F. Sukochev,
\emph{Isometric Structure in Noncommutative Symmetric Spaces},
arXiv:2512.20972.
\end{thebibliography}

\end{document}

