\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Sz}{\operatorname{Sz}}
\newcommand{\cC}{\mathcal{C}}

\title{Literature Status: Same-Szlenk Basis Embeddings}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 28, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \textbf{literature\_already\_answered} packet for the
basis-embedding subquestion in arXiv:0706.0656.  It records an already-known
answer from a later paper, not a new proof from the run.

\section*{Source Question}

The source paper is:
\begin{quote}
Edward Odell, Thomas Schlumprecht, and Andras Zsak,
\emph{Banach spaces of bounded Szlenk index}, arXiv:0706.0656.
\end{quote}

In the open-problems paragraph on page 4 of the source PDF, the authors ask:
\begin{quote}
Is it true that, given \(\alpha\leq \omega_1\), every space in
\(\cC_{\omega^\alpha}\) embeds into a space with a basis of the same class?
\end{quote}
Here \(\cC_\xi\) denotes the class of separable reflexive Banach spaces
\(X\) such that both \(\Sz(X)\) and \(\Sz(X^*)\) are bounded by \(\xi\).

\section*{Supporting Answer}

The supporting paper is:
\begin{quote}
Edward Odell and Thomas Schlumprecht,
\emph{On Zippin's Embedding Theorem of Banach spaces into Banach spaces with
bases}, arXiv:1408.3311.
\end{quote}

The Main Theorem of the supporting paper, on page 2, states that if \(X\) has
separable dual, then \(X\) embeds into a space \(W\) with a shrinking basis
such that
\[
  \Sz(W)=\Sz(X).
\]
It also states that if \(X\) is reflexive, then \(W\) is reflexive and
\[
  \Sz(W^*)=\Sz(X^*).
\]
The same page says that these parts of the Main Theorem answer a question
posed by Pe{\l}czy\'nski and sharpen the earlier Odell--Schlumprecht--Zsak
bounded-Szlenk embedding results.

\section*{Identification}

Let \(X\in \cC_{\omega^\alpha}\).  Then \(X\) is separable and reflexive, and
\[
  \Sz(X)\leq \omega^\alpha,
  \qquad
  \Sz(X^*)\leq \omega^\alpha .
\]
Applying the supporting Main Theorem gives a reflexive space \(W\) with a
basis such that \(X\) embeds into \(W\), \(\Sz(W)=\Sz(X)\), and
\(\Sz(W^*)=\Sz(X^*)\).  Hence \(W\in\cC_{\omega^\alpha}\).  This is exactly
the same-class basis embedding requested in the source question.

The supporting authors explicitly frame their theorem as answering the
Pe{\l}czy\'nski embedding question and as sharpening the earlier bounded
Szlenk-index results, so this packet is classified as an already-known later
answer.

\section*{Scope Limitations}

This packet answers only the first sentence of the second source problem: the
existence of a same-class basis superspace for each individual
\(X\in\cC_{\omega^\alpha}\).  It does not settle the source paper's
universal-element questions for \(\cC_{\omega^{\alpha\cdot\omega}}\) or for
\(\cC_{\omega^\alpha}\).

\section*{Search Evidence}

Cheap run indexes for arXiv:0706.0656, bounded Szlenk index, same-class
basis embeddings, and Szlenk universality had no prior exact packet.
Local later-source search found arXiv:1408.3311 and its Main Theorem.
External web search on June 28, 2026 for the exact Szlenk-universality
phrases returned arXiv:0706.0656 and the related sequel arXiv:0809.3626, but
no newer contradiction to the arXiv:1408.3311 same-Szlenk basis theorem.

\begin{thebibliography}{9}

\bibitem{OSZ0706}
E. Odell, T. Schlumprecht, and A. Zsak,
\emph{Banach spaces of bounded Szlenk index}, arXiv:0706.0656.

\bibitem{OS1408}
E. Odell and T. Schlumprecht,
\emph{On Zippin's Embedding Theorem of Banach spaces into Banach spaces with
bases}, arXiv:1408.3311.

\end{thebibliography}

\end{document}
