\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status for arXiv:1708.07333}
\author{Agent lane 8 note}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Status}

The open norm-attainment-set question extracted from Sain's
\emph{On extreme contractions and the norm attainment set of a bounded linear
operator} \cite{SainExtreme} is already answered in a later paper by Sain,
\emph{On the norm attainment set of a bounded linear operator and
semi-inner-products in normed spaces} \cite{SainSIP}.  This packet is therefore
classified as \texttt{literature\_already\_answered}, not as an original run
result.

\section*{Source Question}

In arXiv:1708.07333, Remark 2.1 on PDF page 3 says that, in view of the
Hilbert-space theorem just proved there, for a bounded linear operator
\(T\) between general Banach spaces \(X,Y\), obtaining a complete
characterization of \(M_T\) appears much more difficult and, to the author's
knowledge, remains open.

\section*{Supporting Answer}

The later arXiv:1802.10439 explicitly identifies the same problem.  Its
abstract states that it obtains a complete characterization of the norm
attainment set of a bounded linear operator between any two real normed
spaces, and says this answers the open question from Sain's earlier paper
on the norm attainment set.  The introduction restates the question:
find a necessary and sufficient condition for \(x\in S_X\) to satisfy
\(x\in M_T\), where \(T\) is a bounded linear operator defined on a Banach
space \(X\).  It then says the result gives a complete solution without
requiring completeness, finite dimensionality, or identical domain and range.

The decisive statement is Theorem 2.3 of \cite{SainSIP}: if \(X,Y\) are real
normed spaces, \(T\in\mathcal L(X,Y)\), and \(z\in S_X\), then \(z\in M_T\)
if and only if for every \(x\in X\) there exist semi-inner-products
\([\, ,\,]_X\) and \([\, ,\,]_Y\) on \(X\) and \(Y\) such that
\[
  [Tx,Tz]_Y=\|T\|^2 [x,z]_X.
\]

\section*{Scope}

This answers the real-normed-space version of the source question.  The source
paper's ambient notation allows real or complex scalars, while the supporting
Theorem 2.3 is stated for real normed spaces.  A complex version should be
checked separately before recording a full complex-scalar closure.

\section*{Evidence}

The support is explicit rather than agent-inferred: the supporting abstract
and introduction both say that the open question is answered, and Theorem 2.3
is the advertised characterization.  Local run-index search found no existing
packet for arXiv:1708.07333 or arXiv:1802.10439 before this packet was created.

\begin{thebibliography}{9}

\bibitem{SainExtreme}
D. Sain,
\emph{On extreme contractions and the norm attainment set of a bounded linear
operator},
arXiv:1708.07333.

\bibitem{SainSIP}
D. Sain,
\emph{On the norm attainment set of a bounded linear operator and
semi-inner-products in normed spaces},
arXiv:1802.10439.

\end{thebibliography}

\end{document}
