\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: Nearly isometric does not imply almost Lipschitz}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 18 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears correct.  The construction is a clever exploitation of the
main difference between nearly isometric embeddability and almost Lipschitz
embeddability: in the nearly isometric definition, the embedding is allowed to
depend on the requested compression function \(\rho\).  The target space can
therefore be made large enough to contain a separate component adapted to
each admissible compression.

By contrast, the almost Lipschitz condition is more global.  In the present
example \(X=\mathbb N_0\), all nonzero distances are at least \(1\).  Choosing
an admissible function \(\varphi\) which is bounded below by a positive
constant on \([1,\infty)\) turns an almost Lipschitz embedding into an
ordinary bi-Lipschitz embedding of the integer ray.  Thus it is enough to
construct a target \(Y\) which satisfies every individual nearly isometric
compression request, but which contains no bi-Lipschitz copy of
\(\mathbb N_0\).

\section*{Construction}

For each admissible compression \(\rho\), the proof chooses a concave,
nondecreasing, unbounded function \(g_\rho\) such that
\[
  \rho(t)\leq g_\rho(t)\leq t,
  \qquad
  \frac{g_\rho(t)}{t}\to0.
\]
The \(\rho\)-component is a copy of \(\mathbb N_0\) with metric
\[
  d_\rho(m,n)=g_\rho(|m-n|).
\]
Then \(Y\) is the wedge, or bouquet, of all these components at their common
basepoint.

This immediately gives nearly isometric embeddability.  Given a requested
pair \((\rho,\omega)\), map \(n\in\mathbb N_0\) to \(n\) inside the
\(\rho\)-component.  On integer distances \(k\geq1\), one has
\[
  \rho(k)\leq g_\rho(k)\leq k=\omega(k),
\]
so the required inequalities hold.

\section*{No Bi-Lipschitz Ray}

The obstruction to almost Lipschitz embeddability is that \(Y\) contains no
bi-Lipschitz copy of the usual ray.  Suppose, for contradiction, that
\[
  F:\mathbb N_0\to Y
\]
is bi-Lipschitz.  Let
\[
  R_n=d_Y(F(n),o)
\]
be the distance from the common basepoint.  The lower Lipschitz estimate gives
linear growth:
\[
  R_n\geq cn-R_0.
\]
On the other hand, consecutive points satisfy
\[
  d_Y(F(n+1),F(n))\leq C.
\]
If \(F(n)\) and \(F(n+1)\) were in different bouquet components, their
distance would be
\[
  R_n+R_{n+1},
\]
which is eventually larger than \(C\).  Hence, after some point, consecutive
terms must lie in the same component.  Therefore the whole tail of the ray is
trapped in a single component \(Y_{\rho_0}\).

Inside this component, distances are measured by
\[
  g_{\rho_0}(|a_m-a_n|).
\]
The upper Lipschitz bound on consecutive points implies that the underlying
integer jumps \(|a_{n+1}-a_n|\) are uniformly bounded.  Thus
\[
  |a_m-a_n|\leq B|m-n|.
\]
But \(g_{\rho_0}\) is sublinear, so
\[
  \frac{g_{\rho_0}(B|m-n|)}{|m-n|}\to0.
\]
This contradicts the lower linear bound required by a bi-Lipschitz embedding.

\section*{Review Outcome}

Approve this packet as an apparently correct counterexample to the source
problem.  The key idea is exactly the dependence of the nearly isometric
embedding on \(\rho\): the bouquet can accommodate every requested sublinear
compression separately, while the almost Lipschitz condition, in this
discrete setting, would force a genuine bi-Lipschitz ray, which the bouquet is
designed to exclude.

\end{document}
