\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Fix}{\operatorname{Fix}}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\dist}{\operatorname{d}}

\begin{document}

\section*{Human Review: Decomposable-space tube construction}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears to be correct. Although it does not solve the full problem
for arbitrary infinite-dimensional Banach spaces, I would regard the argument
as both quite ingenious and quite general. The only structural assumption is a
decomposition
\[
  X=Y\oplus Z
\]
with both \(Y\) and \(Z\) infinite-dimensional. Since Banach spaces which do
not admit such decompositions are rather special and exotic from the usual
fixed-point-theoretic point of view, this covers a large and natural class of
spaces.

\section*{Idea of the Construction}

The proof uses the decomposition \(X=Y\oplus Z\) as a system of base and fibre
coordinates. The \(Y\)-coordinate is first retracted onto a small sphere
\[
  aS_Y.
\]
Over each base point \(y\in aS_Y\), the construction places a small fibre in
the \(Z\)-direction of radius
\[
  r(y)>0.
\]
The radius function is Lipschitz, positive everywhere, and has infimum zero.
This is the essential device: positivity prevents fixed points, while the
vanishing infimum gives null minimal displacement.

The map then acts by flipping the sign in the \(Z\)-fibre:
\[
  y+r(y)z \longmapsto y-r(y)z.
\]
After the first iterate, the base point and radius are fixed, and the dynamics
alternate between the two fibre signs. This gives
\[
  T^2=S,\qquad T^3=T,
\]
so the iterates are uniformly Lipschitz.

\section*{Technical Points Checked}

The auxiliary estimates appear sound. The radial clipping map is
\(2\)-Lipschitz, and the variable-radius sphere selection lemma gives the
needed Lipschitz control for
\[
  H(r,q)=rR_Z(\kappa_Z(q/r)).
\]
This is what ensures that the fibre selection remains Lipschitz even though
the radius varies with the base point.

The use of infinite-dimensionality is also clear. It is needed to invoke the
Benyamini--Sternfeld Lipschitz retractions
\[
  R_Y:B_Y\to S_Y,\qquad R_Z:B_Z\to S_Z,
\]
and to build a positive Lipschitz gauge on \(S_Y\) whose infimum is zero.

\section*{Review Outcome}

Archive this packet as an apparently correct partial solution to Q2. It gives
an affirmative answer for every decomposable Banach space with two
infinite-dimensional complemented summands. It should not be described as a
full solution to the arbitrary Banach-space problem, but it is a strong and
conceptually useful partial result.

\end{document}
