\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Weighted Semi-Greedy Bases}
\author{Run \texttt{fa\_banach\_001}, lane 14}
\date{2026-06-29}

\begin{document}
\maketitle

\noindent\textbf{Status.} \texttt{literature\_already\_answered}.

\section*{Original Question}

The source paper is Dilworth, Kutzarova, Temlyakov, and Wallis,
\emph{Weight-almost greedy bases}, arXiv:1803.02932 \cite{DKTW}.
Question 4.12, on PDF page 18, asks:
\begin{quote}
Does the analogous result hold for semi-greediness?
\end{quote}
The preceding Corollary 4.11 proves that, if a basis has no subsequence
equivalent to the unit vector basis of \(c_0\), then it is \(w\)-almost greedy
for some weight \(w\) if and only if it is almost greedy. The question asks for
the corresponding statement with \(w\)-semi-greediness and semi-greediness.
The source gives only the finite-cotype partial answer in Corollary 4.16.

\section*{Supporting Answer}

The later paper Berna, \emph{Characterization of weight-semi-greedy bases},
arXiv:1902.10986 \cite{Berna}, explicitly addresses this weighted
semi-greedy question. Its abstract says that it proves the same
characterization from \cite{DKTW} while removing the finite-cotype condition.

The decisive statement is Theorem 1.11, on PDF page 4. It states that if
\(\mathcal B\) is a Schauder basis in a Banach space, then:
\begin{itemize}
\item \(w\)-semi-greediness implies quasi-greediness and
  \(w\)-super-democracy;
\item quasi-greediness together with \(w\)-super-democracy implies
  \(w\)-semi-greediness.
\end{itemize}
Together with the standard weighted characterization of \(w\)-almost greedy
bases by quasi-greediness and weighted democracy/super-democracy, this removes
the finite-cotype hypothesis from the partial answer in Corollary 4.16 of
\cite{DKTW}.

\section*{Conclusion}

The extracted target from \cite{DKTW} is already answered by \cite{Berna}.
This packet records the duplicate status; it is not a new proof packet.

\begin{thebibliography}{9}
\bibitem{DKTW}
S. J. Dilworth, D. Kutzarova, V. N. Temlyakov, and B. Wallis,
\emph{Weight-almost greedy bases},
arXiv:1803.02932, 2018.

\bibitem{Berna}
P. M. Berna,
\emph{Characterization of weight-semi-greedy bases},
arXiv:1902.10986, 2019.
\end{thebibliography}

\end{document}
