\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature Status for arXiv:1804.01705 Question 6.2}
\author{arxiv\_automatic\_math run fa\_banach\_001}
\date{2026-06-14}

\begin{document}
\maketitle

\section*{Status}

\textbf{Result type:} literature\_already\_answered.

\textbf{Verdict:} Question 6.2 of arXiv:1804.01705 has an affirmative answer in later literature.

\section*{Original Question}

The source paper is:
\begin{quote}
Rainis Haller, Jaan Kristjan Langemets, and Mart Poldvere,
\emph{Symmetric strong diameter two property}, arXiv:1804.01705.
\end{quote}

In Section 6, Question 6.2, PDF page 16, the paper asks:
\begin{quote}
Does there exist a dual Banach space with the weak-star symmetric strong
diameter two property and without the symmetric strong diameter two property?
\end{quote}

\section*{Supporting Answer}

The supporting paper is:
\begin{quote}
Rainis Haller, Jaan Kristjan Kaasik, and Andre Ostrak,
\emph{Separating diameter two properties from their weak-star counterparts in
spaces of Lipschitz functions}, arXiv:2404.11430.
\end{quote}

The supporting paper explicitly identifies the same question. In the
introduction, PDF page 2, it states that it had remained open whether SSD2P
and \(w^\ast\)-SSD2P are equivalent for dual spaces, citing
\([6,\) Question 6.2\(]\). On PDF page 3 it says that its observation
establishes that \(w^\ast\)-SSD2P differs from SSD2P in spaces of Lipschitz
functions, thereby answering \([6,\) Question 6.2\(]\).

The decisive statement appears in Section 3, PDF page 6: the authors state
that they show there exist spaces of Lipschitz functions, hence dual Banach
spaces, with \(w^\ast\)-SSD2P but without SSD2P, and that these are the first
known examples answering \([6,\) Question 6.2\(]\). More concretely, for the
metric space \(M\) from Haller--Oja--Poldvere Example 2.7, they use the known
SLTP characterization to obtain \(w^\ast\)-SSD2P for \(\mathrm{Lip}_0(M)\),
then prove that \(\mathrm{Lip}_0(M)\) does not have SSD2P.

\section*{Scope And Limitations}

This is an already-known literature answer, not a new proof produced in this
run. It clears exactly the 2018 question asking for a dual Banach space with
\(w^\ast\)-SSD2P but without SSD2P.

It does not settle the separate question posed later in arXiv:2404.11430 asking
whether there is a Banach space \(X\) with SSD2P such that \(X^{**}\) lacks
SSD2P.

\section*{Run Evidence}

The run's lightweight indexes were searched for arXiv ids 1804.01705 and
2404.11430 and for the key phrases \(w^\ast\)-SSD2P, SSD2P, and symmetric
strong diameter two property. No existing durable packet for this exact source
question was found.

\section*{References}

\begin{thebibliography}{9}
\bibitem{HLP2018}
R. Haller, J. K. Langemets, and M. Poldvere,
\emph{Symmetric strong diameter two property}, arXiv:1804.01705.

\bibitem{HKO2024}
R. Haller, J. K. Kaasik, and A. Ostrak,
\emph{Separating diameter two properties from their weak-star counterparts in
spaces of Lipschitz functions}, arXiv:2404.11430.
\end{thebibliography}

\end{document}
