\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\ellTwo}{\ell_2}

\title{Literature Status: Superreflexive Spaces with \texorpdfstring{$\Delta$}{Delta}-Points}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_12}}
\date{2026-06-14}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet.  It records that Question~6.1
from Abrahamsen--Lima--Martiny--Perreau, \emph{Asymptotic geometry and
delta-points}, arXiv:2203.14528, is answered by the later paper
Abrahamsen--Aliaga--Lima--Martiny--Perreau--Prochazka--Veeorg,
\emph{Delta-points and their implications for the geometry of Banach spaces},
arXiv:2303.00511.

\section*{Source Question}

The source paper asks:
\[
\text{Do all superreflexive Banach spaces fail to contain } \Delta
\text{-points?}
\]
In the parsed source this is Question~\texttt{quest:delta\_SR}, at
\texttt{source.tex:2164--2169}.  The paper also reformulates the issue via
almost $\Delta$-points and asks in particular about renormings of $\ellTwo$ at
\texttt{source.tex:2450--2464}.

\section*{Supporting Answer}

The supporting paper explicitly says in its introduction that Corollary~6.10
of the source paper showed finite-dimensional spaces have no $\Delta$-points
and that Question~6.1 asked whether the same holds for superreflexive spaces.
It then states that Section~3 answers this question negatively.

Section~3 defines an equivalent norm on $\ellTwo$ and lets
\[
Y=(\ellTwo,\vert\!\vert\!\vert\cdot\vert\!\vert\!\vert).
\]
Theorem~3.1 states that both $e_1\in S_Y$ and $e_1^*\in S_{Y^*}$ are super
$\Delta$-points, and neither is a Daugavet point.

Since $Y$ is an equivalent renorming of $\ellTwo$, it is superreflexive.  A
super $\Delta$-point is in particular a $\Delta$-point.  Therefore the answer
to the source question is negative.

\section*{Scope}

This packet does not claim a new proof.  It also does not settle the
Daugavet-point variant: the supporting theorem explicitly says the constructed
points are not Daugavet points, and the supporting paper notes that the
existence of a reflexive or superreflexive space with a Daugavet point remains
open.

\section*{References}

\begin{itemize}
\item T. A. Abrahamsen, V. Lima, A. Martiny, and Y. Perreau,
\emph{Asymptotic geometry and delta-points}, arXiv:2203.14528; Banach J.
Math. Anal. 16 (2022), Paper No. 57.
\item T. A. Abrahamsen, R. J. Aliaga, V. Lima, A. Martiny, Y. Perreau,
A. Prochazka, and T. Veeorg, \emph{Delta-points and their implications for
the geometry of Banach spaces}, arXiv:2303.00511.
\end{itemize}

\end{document}
