\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\title{Literature status: the superreflexive\\non-summing lineability problem}
\author{Automated Math Discovery Run \texttt{fa\_banach\_001}\\Model: GPT5.6}
\date{22 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.88\linewidth}{\textbf{Status: literature already answered.}
Kitson--Timoney (2011), Theorem~4.1, explicitly answers the problem and
proves a stronger simultaneous spaceability theorem.}}
\end{center}

\section*{Source question}

Botelho, Diniz, and Pellegrino quote as Problem~1.1 the following question
of Puglisi and Seoane-Sep\'{u}lveda \cite{BDP}: if $E$ is an
infinite-dimensional superreflexive Banach space and $p\geq1$, is
\[
  \mathcal L(E;F)\setminus\Pi_p(E;F)
\]
lineable for every infinite-dimensional Banach space $F$? Their Theorem~2.1
answers this when either $E$ contains a complemented infinite-dimensional
subspace with an unconditional basis or $F$ contains an unconditional basic
sequence. Their Remark~2.2 leaves precisely the case where both structural
conditions fail.

The source location is arXiv:0811.0092v5, Introduction, Problem~1.1 and
Section~2, Theorem~2.1 and the following remark (PDF pages 1--4).

\section*{Decisive later theorem}

Kitson and Timoney explicitly write that their Section~4 improves the earlier
results and answers the original problem \cite{KT}. Their Theorem~4.1 states:
if $X$ and $Y$ are infinite-dimensional Banach spaces and $X$ is
superreflexive, then
\[
  \mathcal K(X,Y)\setminus
  \bigcup_{1\leq p<\infty}\Pi_p(X,Y)
\]
is spaceable as a subset of $\mathcal K(X,Y)$.

This is Theorem~4.1 on accepted-manuscript pages 7--8 (published article
pages 680--686, DOI below).

\section*{Why this settles the source question}

Spaceability is stronger than lineability. Theorem~4.1 supplies a closed
infinite-dimensional subspace $W\subset\mathcal K(E,F)$ such that every
nonzero $T\in W$ fails to be absolutely $p$-summing for \emph{every} finite
$p$. For each fixed $p\geq1$,
\[
  W\setminus\{0\}
  \subseteq \mathcal K(E,F)\setminus\Pi_p(E,F)
  \subseteq \mathcal L(E,F)\setminus\Pi_p(E,F).
\]
Thus the answer is affirmative for all pairs $(E,F)$ in the source problem,
including its simultaneous pathological case. No part of that problem
remains open. The supporting authors knew they were answering it; this is
not merely an agent-identified implication.

\section*{Evidence and local artifacts}

The original paper is stored locally as \texttt{source\_paper.pdf}. The
accepted supporting manuscript was inspected through Trinity College
Dublin's repository. Direct automated downloads returned an anti-bot HTML
challenge rather than a PDF, so no false \texttt{.pdf} artifact is retained;
the stable DOI, repository link, and exact theorem location are recorded in
\texttt{supporting\_paper\_access.md}.

\begin{thebibliography}{9}
\bibitem{BDP}
G. Botelho, D. Diniz, and D. Pellegrino,
\emph{Lineability of the set of bounded linear non-absolutely summing
operators}, J. Math. Anal. Appl. 357 (2009), 171--175;
arXiv:0811.0092v5.
\url{https://arxiv.org/abs/0811.0092}

\bibitem{KT}
D. Kitson and R. M. Timoney,
\emph{Operator ranges and spaceability},
J. Math. Anal. Appl. 378 (2011), 680--686.
\url{https://doi.org/10.1016/j.jmaa.2010.12.061}
\end{thebibliography}

\end{document}
