\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\Hol}{\operatorname{Hol}}
\newcommand{\Harm}{\operatorname{Harm}}

\title{Partial Result: A Positive-Area Support Criterion for the Harmonic Bergman Question}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_super\_01}}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Status}

This is a partial positive answer to Question 2 in Han--Qiu--Wang,
\emph{Complete weighted Bergman spaces have bounded point evaluations},
arXiv:2111.07575. The source asks whether completeness of a weighted harmonic
Bergman space $B^p(\Omega,\mu)$ implies locally uniformly bounded point
evaluations. The source proves this when $\operatorname{int}\operatorname{supp}\mu$
is nonempty. The result below replaces that assumption by the weaker condition
that $\operatorname{supp}\mu$ has positive planar Lebesgue measure.

\section*{Theorem}

\begin{theorem}
Let $\Omega\subset\C$ be a domain, let $\mu$ be a positive Radon measure on
$\Omega$, and let $1\leq p<\infty$. Define
\[
  B^p(\Omega,\mu)
  =
  \left\{f\in \Harm(\Omega):
    \int_\Omega |f|^p\,d\mu<\infty
  \right\}
\]
with its natural $L^p(\mu)$ norm. Suppose that $B^p(\Omega,\mu)$ is a Banach
space and that $\supp\mu$ has positive two-dimensional Lebesgue measure. Then
$B^p(\Omega,\mu)$ has locally uniformly bounded point evaluations: for every
compact set $K\subset\Omega$ there is a constant $C_K$ such that
\[
  \sup_{z\in K}|f(z)|
  \leq C_K\left(\int_\Omega |f|^p\,d\mu\right)^{1/p}
  \qquad (f\in B^p(\Omega,\mu)).
\]
\end{theorem}

\begin{proof}
Choose a compact set $E\subset \supp\mu$ with positive planar Lebesgue
measure. This is possible by inner regularity of planar Lebesgue measure,
using that $\Omega$ is sigma-compact.

Fix a compact set $K\subset\Omega$. Since $\Omega$ is a domain, there is a
relatively compact subdomain $S\Subset\Omega$ such that $K\cup E\subset S$.
Let $h^\infty(S)$ be the Banach space of bounded harmonic functions on $S$
with the supremum norm, and consider the restriction map
\[
  R_S:B^p(\Omega,\mu)\longrightarrow h^\infty(S),
  \qquad R_S f=f|_S .
\]
This map is well-defined because every harmonic function on $\Omega$ is
bounded on relatively compact subdomains.

We show that $R_S$ has closed graph. Let $f_n\to f$ in $B^p(\Omega,\mu)$ and
$f_n|_S\to g$ in $h^\infty(S)$. Since $\overline S$ is compact and $\mu$ is
Radon, $\mu(S)<\infty$. Therefore $f_n|_S\to f|_S$ in $L^p(S,\mu)$ and also
$f_n|_S\to g$ in $L^p(S,\mu)$. Hence $f|_S-g=0$ $\mu$-almost everywhere on
$S$.

The function $f|_S-g$ is harmonic on $S$. By continuity and the definition of
support, a continuous function that vanishes $\mu$-almost everywhere on $S$
vanishes on $\supp\mu\cap S$. In particular, $f|_S-g$ vanishes on $E$.
Since $E$ has positive planar measure and a nonzero harmonic function has a
zero set of planar measure zero, it follows that $f|_S-g\equiv 0$ on $S$.
Thus the graph of $R_S$ is closed.

The closed graph theorem gives a constant $C_S$ such that
\[
  \|f\|_{h^\infty(S)}\leq C_S\|f\|_{B^p(\Omega,\mu)} .
\]
Since $K\subset S$, this implies the desired estimate with $C_K=C_S$.
\end{proof}

\section*{Comment}

The condition $|\supp\mu|>0$ is strictly weaker than
$\operatorname{int}\supp\mu\neq\emptyset$: a fat Cantor set of positive area
inside $\Omega$ has empty interior but is still a uniqueness set for harmonic
functions. Thus the theorem expands the source's stated partial result for
the harmonic question, but it does not settle the remaining zero-area
uniqueness-set cases.

\section*{References}

\begin{itemize}
\item Y. Han, Y. Qiu, and Z. Wang, \emph{Complete weighted Bergman spaces have
bounded point evaluations}, arXiv:2111.07575.
\end{itemize}

\end{document}
