\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature answer: Webster operator compact maps are not cb-norm closed}
\author{Run fa\_banach\_001, agent lane 17}
\date{2026-07-03}

\begin{document}
\maketitle

\sloppy

\section*{Source Question}

The source paper is Chavez-Dominguez--Dimant--Galicer,
\emph{Operator \(p\)-compact mappings}, arXiv:1809.07741 \cite{CDG2018}.
In its final section, the authors recall Webster's problem asking whether the
space of operator compact maps is closed in the completely bounded norm
topology. Equivalently, using the notation of the source paper, they ask
whether the operator compact norm \(\kappa_\infty^o\) and the completely
bounded norm are equivalent on \(\mathcal K_\infty^o\).

\section*{Supporting Answer}

The same authors later returned to the subject in
\emph{Revisiting Operator \(p\)-Compact Mappings}, arXiv:2405.18571
\cite{CDG2024}. In the introduction they explicitly say that their comparison
of compactness notions answers the Webster question emphasized in
\cite{CDG2018}. The decisive passage is in the discussion after their
two-sided multiplication example: for \(p=\infty\), the multiplication map
\[
  M(a,b):\mathcal S_\infty\longrightarrow \mathcal S_\infty
\]
constructed there is not operator compact, but it is the completely bounded
norm limit of finite-rank truncations, and finite-rank maps are operator
compact.

\section*{Conclusion}

Thus Webster's cb-norm-closedness question from arXiv:1809.07741 has a
negative answer. The class of operator compact maps need not be closed in the
cb-norm topology, and consequently \(\kappa_\infty^o\) and
\(\|\cdot\|_{cb}\) are not equivalent on \(\mathcal K_\infty^o\) in general.

This packet only records the literature answer to that final Webster problem.
The separate tensor-norm association questions involving \(/d_p^o\) and
surjective hulls are not settled by this identification.

\begin{thebibliography}{9}
\bibitem{CDG2018}
J. A. Chavez-Dominguez, V. Dimant, and D. Galicer,
\emph{Operator \(p\)-compact mappings}, arXiv:1809.07741, 2018.

\bibitem{CDG2024}
J. A. Chavez-Dominguez, V. Dimant, and D. Galicer,
\emph{Revisiting Operator \(p\)-Compact Mappings}, arXiv:2405.18571, 2024.
\end{thebibliography}

\end{document}
