\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

\newcommand{\F}{\mathcal F}
\newcommand{\Lip}{\operatorname{Lip}_0}

\title[Geodesic Free Spaces and Net-LASQ]{A Net-Level Geodesic Lipschitz-Free Subcase of Question 2.3 in arXiv:2210.13306}
\author{agent\_lane\_19}
\date{June 20, 2026}

\begin{document}

\begin{abstract}
Ciaci asked whether every locally almost square Banach space satisfies the
weakly-null-net conclusion proved in his paper for positive locally almost
square Banach lattices.  We prove a partial positive result: if \(M\) is a
geodesic metric space, then the Lipschitz-free space \(\F(M)\) satisfies that
net conclusion at every point of its unit sphere.  The proof combines the
finite-support geodesic theorem of Kaasik--Veeorg with a simple density lemma
showing that pointwise weakly-null square sequences on a dense subset of the
sphere promote to weakly-null square nets on the whole sphere.
\end{abstract}

\maketitle

\section{Source Question}

In \cite{Ciaci2022}, a Banach space \(X\) is called locally almost square
(LASQ) if, for every \(y\in S_X\) and every \(\varepsilon>0\), there exists
\(x\in S_X\) such that
\[
  \|y+x\|\le 1+\varepsilon
  \quad\text{and}\quad
  \|y-x\|\le 1+\varepsilon .
\]
Ciaci proves that a positive LASQ Banach lattice has the following stronger
net conclusion: for every \(y\in S_X\), there is a weakly null net
\((x_\alpha)\) such that
\[
  \|x_\alpha\|\to 1,\qquad
  \|y+x_\alpha\|\to 1,\qquad
  \|y-x_\alpha\|\to 1 .
\]
Question 2.3 of \cite{Ciaci2022} asks whether the same conclusion follows from
LASQ alone, without the lattice and positivity hypotheses.

\section{Idea of the Proof}

The only new mechanism is that nets are stable under sphere-density in a way
that sequences need not be.  Suppose a dense set \(D\subset S_X\) consists of
points at which weakly-null square sequences already exist.  Given a target
\(y\), a weak neighborhood \(U\) of zero, and a tolerance \(\varepsilon\),
choose \(z\in D\) close to \(y\).  Then move far enough along the sequence
attached to \(z\) so that the chosen vector lies in \(U\) and is almost square
with \(z\).  It is automatically almost square with \(y\), up to the small
error \(\|y-z\|\).  Directing these choices by weak neighborhoods and
tolerances gives the desired weakly null net.

Kaasik and Veeorg prove in \cite{KaasikVeeorg2022} that for a geodesic metric
space \(M\), every finite-support \(y\in S_{\F(M)}\) has such a weakly-null
square sequence.  Since finite-support elements are dense in \(\F(M)\), the
density lemma promotes their result to all \(y\in S_{\F(M)}\), at the net
level.

\section{The Density Lemma}

\begin{definition}
Let \(X\) be a Banach space.  A point \(y\in S_X\) has the
\emph{weakly-null-net square property} if there is a weakly null net
\((x_\alpha)\subset B_X\) such that
\[
  \|x_\alpha\|\to 1,\qquad
  \|y+x_\alpha\|\to 1,\qquad
  \|y-x_\alpha\|\to 1 .
\]
\end{definition}

\begin{lemma}[Density promotion]
\label{lem:density}
Let \(D\subset S_X\) be norm dense.  Assume that every \(z\in D\) has a
weakly null sequence \((x_n^z)\subset B_X\) satisfying
\[
  \|x_n^z\|\to 1,\qquad
  \|z+x_n^z\|\to 1,\qquad
  \|z-x_n^z\|\to 1 .
\]
Then every \(y\in S_X\) has the weakly-null-net square property.
\end{lemma}

\begin{proof}
Fix \(y\in S_X\).  It is enough to show the following local selection
property: for every \(\varepsilon>0\) and every weak neighborhood \(U\) of
zero, there exists \(x\in U\cap B_X\) such that
\[
  \|x\|>1-\varepsilon,\qquad
  \|y+x\|<1+\varepsilon,\qquad
  \|y-x\|<1+\varepsilon .
\]
Indeed, after choosing one such \(x_{\varepsilon,U}\) for every pair
\((\varepsilon,U)\), ordered by decreasing \(\varepsilon\) and shrinking
neighborhoods, the resulting net is weakly null and has the required norm
limits.

Let \(\varepsilon>0\) and let \(U\) be a weak neighborhood of zero.  Choose
\(\eta>0\) with \(3\eta<\varepsilon\), and choose \(z\in D\) such that
\(\|y-z\|<\eta\).  Since the sequence attached to \(z\) is weakly null and
has the square limits at \(z\), there is \(n\) such that \(x:=x_n^z\in U\),
\(\|x\|>1-\eta\), and
\[
  \|z+x\|<1+\eta,\qquad
  \|z-x\|<1+\eta .
\]
Therefore
\[
  \|y\pm x\|\le \|y-z\|+\|z\pm x\| < \eta+(1+\eta)<1+\varepsilon
\]
and \(\|x\|>1-\varepsilon\).  This proves the local selection property.

Finally, the two upper estimates force the lower limits of
\(\|y\pm x_{\varepsilon,U}\|\) to be \(1\): if both upper bounds are at most
\(1+\varepsilon\), then
\[
  2=\|(y+x_{\varepsilon,U})+(y-x_{\varepsilon,U})\|
    \le \|y+x_{\varepsilon,U}\|+\|y-x_{\varepsilon,U}\|,
\]
so each of the two norms is at least \(1-\varepsilon\) once the other is at
most \(1+\varepsilon\).
\end{proof}

\section{Application to Geodesic Lipschitz-Free Spaces}

\begin{theorem}
\label{thm:geodesic-free-net}
Let \(M\) be a geodesic metric space.  Then for every \(y\in S_{\F(M)}\) there
exists a weakly null net \((\mu_\alpha)\subset B_{\F(M)}\) such that
\[
  \|\mu_\alpha\|\to 1,\qquad
  \|y+\mu_\alpha\|\to 1,\qquad
  \|y-\mu_\alpha\|\to 1 .
\]
\end{theorem}

\begin{proof}
Let
\[
  D=\{z\in S_{\F(M)}:\ z \text{ has finite support}\}.
\]
The linear span of the evaluation vectors \(\delta_p\), \(p\in M\), is dense
in \(\F(M)\).  Hence \(D\) is norm dense in \(S_{\F(M)}\).

By \cite[Proposition in Section 3]{KaasikVeeorg2022}, if \(M\) is geodesic and
\(z\in S_{\F(M)}\) has finite support, then there is a weakly null sequence
\((\mu_n)\subset B_{\F(M)}\) such that
\[
  \|\mu_n\|\to 1,\qquad
  \|z+\mu_n\|\to 1,\qquad
  \|z-\mu_n\|\to 1 .
\]
Thus every point of the dense set \(D\) satisfies the hypothesis of
Lemma~\ref{lem:density}.  Applying that lemma with \(X=\F(M)\) gives the
desired weakly null net for every \(y\in S_{\F(M)}\).
\end{proof}

\begin{corollary}
In the class of Lipschitz-free spaces over geodesic metric spaces, Question 2.3
of \cite{Ciaci2022} has a positive answer.
\end{corollary}

\section{Limitations and Verification Notes}

This packet does not prove the full arbitrary-LASQ statement asked in
\cite{Ciaci2022}.  It also does not settle the length but non-geodesic
Lipschitz-free examples from \cite{KaasikVeeorg2022}; those examples separate
LASQ from WASQ, and the sequence obstruction in that paper does not by itself
rule out weakly null nets.

The proof above uses only:
\begin{enumerate}
\item the standard density of finite-support elements in a Lipschitz-free
space;
\item the finite-support geodesic weakly-null sequence theorem from
\cite{KaasikVeeorg2022}; and
\item the elementary density-promotion Lemma~\ref{lem:density}.
\end{enumerate}
No computational verification is required.

\begin{thebibliography}{9}

\bibitem{Ciaci2022}
S.~Ciaci,
\emph{Locally almost square Banach lattices},
arXiv:2210.13306, 2022.

\bibitem{KaasikVeeorg2022}
J.~K. Kaasik and T.~Veeorg,
\emph{Weakly almost square Lipschitz-free spaces},
arXiv:2210.09158, 2022.

\end{thebibliography}

\end{document}
