\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\B}{\mathcal B}
\newcommand{\K}{\mathcal K}
\newcommand{\W}{\mathcal W}
\newcommand{\ER}{E_{\mathrm R}}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\newcommand{\wt}[1]{\widetilde{#1}}

\title{A conditional split-module lift for Read's ordinary Calkin algebra}
\author{agent\_lane\_08}
\date{2026-06-16}

\begin{document}
\maketitle

\section*{Source question}

The source paper is Richard Skillicorn,
\emph{The uniqueness-of-norm problem for Calkin algebras},
arXiv:1507.08118.  Remark 2.6 asks whether the ordinary Calkin algebra
\[
  \B(\ER)/\K(\ER)
\]
of Read's Banach space has a unique complete algebra norm.

\section*{Summary}

This note records a conditional reduction, not a full answer.  It proves an
abstract criterion for lifting a non-equivalent complete norm from a square-zero
split quotient through a Banach-algebra extension.  In Read's case,
Laustsen--Skillicorn prove a strongly split exact sequence
\[
0\longrightarrow \W(\ER)\longrightarrow \B(\ER)
 \longrightarrow \ell_2^\sim\longrightarrow 0,
\]
which descends to a split quotient
\[
0\longrightarrow \W(\ER)/\K(\ER)\longrightarrow
\B(\ER)/\K(\ER)\longrightarrow \ell_2^\sim\longrightarrow 0.
\]
The remaining point is exactly the module obstruction: an exotic complete norm
on the \(\ell_2\)-coordinate must still make the induced left and right actions
on \(\W(\ER)/\K(\ER)\) bounded.

\section*{Proof Intuition}

For the weak Calkin algebra, Skillicorn can renorm the square-zero
\(\ell_2\)-radical directly: a discontinuous linear bijection of \(\ell_2\)
extends to an algebra automorphism of \(\ell_2^\sim\), giving a new complete
algebra norm.  For the ordinary Calkin algebra one has an extra ideal
\(J=\W(\ER)/\K(\ER)\).  In a split form the algebra is a semidirect product
\(J\rtimes \ell_2^\sim\).  The same exotic norm lifts precisely when the
\(\ell_2\)-coordinate still acts boundedly on \(J\).  Thus the abstract
criterion below separates the already-solved quotient renorming from the one
missing Read-space calculation.

\section*{Abstract lifting criterion}

Let \(E\) be a Banach space regarded as a Banach algebra with zero product, and
let \(\wt E=E\oplus \mathbb K1\) be its unitization.  Suppose that
\[
0\longrightarrow J\longrightarrow A
 \stackrel{\pi}{\longrightarrow}\wt E\longrightarrow 0
\]
is a strongly split extension of Banach algebras, with continuous homomorphic
right inverse \(\rho:\wt E\to A\).  We identify \(A\) algebraically with
\[
J\oplus \rho(\wt E).
\]
For \(\xi\in E\) define left and right module maps on \(J\) by
\[
L_\xi(j)=\rho(\xi)j,\qquad R_\xi(j)=j\rho(\xi).
\]

\begin{theorem}[Split-module norm lift]
\label{thm:lift}
Assume that \(E\) admits a complete norm \(\alpha\) which is not dominated by
the original norm on \(E\), and that there is a constant \(C\geq 0\) such that
\[
  \norm{L_\xi j}_J+\norm{R_\xi j}_J
  \leq C\,\alpha(\xi)\,\norm{j}_J
\]
for every \(\xi\in E\) and \(j\in J\).  Then \(A\) admits a complete algebra
norm not equivalent to its original Banach-algebra norm.
\end{theorem}

\begin{proof}
Put \(\beta(\xi+\lambda1)=\alpha(\xi)+|\lambda|\).  Since \(E\) has zero
product, \(\beta\) is a complete algebra norm on \(\wt E\).  Let \(M\) be a
bound for multiplication in \(J\), and choose constants \(D\geq\max\{1,C\}\)
and \(L\geq M\).  Define
\[
  \norm{j+\rho(u)}_* = L\norm{j}_J+D\beta(u)
  \qquad (j\in J,\ u\in \wt E).
\]
As a vector-space direct sum of the Banach spaces \(J\) and \((\wt E,\beta)\),
\((A,\norm{\cdot}_*)\) is complete.

Write \(u=\xi+\lambda1\) and \(v=\eta+\mu1\).  The product in the split
decomposition is
\[
(j+\rho(u))(k+\rho(v))
=jk+j\rho(v)+\rho(u)k+\rho(uv).
\]
The \(J\)-part is bounded by
\[
M\norm j\norm k+C\alpha(\eta)\norm j+|\mu|\norm j
+C\alpha(\xi)\norm k+|\lambda|\norm k.
\]
After multiplying by \(L\), this is dominated by the \(J\)-cross terms in
\((L\norm j+D\beta(u))(L\norm k+D\beta(v))\), using \(L\geq M\) and
\(D\geq C,1\).  The quotient part satisfies
\[
\beta(uv)\leq \beta(u)\beta(v)
\]
because \(E\) has zero product.  Since \(D\geq1\), the quotient contribution
\(D\beta(uv)\) is dominated by \(D^2\beta(u)\beta(v)\).  Hence
\[
\norm{(j+\rho(u))(k+\rho(v))}_*
\leq \norm{j+\rho(u)}_*\,\norm{k+\rho(v)}_*,
\]
so \(\norm{\cdot}_*\) is a complete algebra norm.

It remains to see that it is not equivalent to the original norm.  If it were
bounded above by a constant multiple of the original norm on \(A\), then on the
split copy of \(E\) we would have
\[
D\alpha(\xi)=\norm{\rho(\xi)}_*
\leq C_0\norm{\rho(\xi)}_A
\leq C_0\norm{\rho}\,\norm{\xi}_E,
\]
contradicting that \(\alpha\) is not dominated by the original norm.  Thus the
new complete algebra norm is non-equivalent to the original one.
\end{proof}

\begin{corollary}[Annihilator-kernel subcase]
\label{cor:annihilator}
In the setting of Theorem \ref{thm:lift}, suppose the common annihilator
\[
  N=\{\xi\in E:L_\xi=0=R_\xi\}
\]
is an infinite-dimensional complemented closed subspace of \(E\).  Then \(A\)
has a non-equivalent complete algebra norm.
\end{corollary}

\begin{proof}
Write \(E=N\oplus F\) as a topological direct sum.  Choose a discontinuous
linear bijection \(\gamma:N\to N\), and set
\[
  \alpha(n+f)=\norm{\gamma n}_E+\norm f_E.
\]
This is a complete norm on \(E\), not dominated by the original norm.  Since
\(N\) annihilates \(J\) on both sides, the module maps depend only on the
\(F\)-coordinate, and hence are bounded by a constant multiple of
\(\norm f_E\leq\alpha(n+f)\).  Theorem \ref{thm:lift} applies.
\end{proof}

\section*{Read's ordinary Calkin algebra}

Laustsen--Skillicorn's split theorem provides a continuous homomorphism
\[
  \psi:\B(\ER)\to \ell_2^\sim
\]
with kernel \(\W(\ER)\) and a continuous homomorphic right inverse.  Since
\(\K(\ER)\subseteq \W(\ER)\), this descends to a strongly split extension
\[
0\to J\to A\to\ell_2^\sim\to0,\qquad
 A=\B(\ER)/\K(\ER),\quad J=\W(\ER)/\K(\ER).
\]
Consequently Theorem \ref{thm:lift} gives:

\begin{corollary}[Conditional negative answer to Skillicorn's Remark 2.6]
\label{cor:read}
Let \(\rho:\ell_2^\sim\to \B(\ER)/\K(\ER)\) be the splitting induced by
Laustsen--Skillicorn.  If there is a complete norm \(\alpha\) on \(\ell_2\),
not dominated by the Hilbert norm, such that
\[
 \norm{\rho(\xi)j}+\norm{j\rho(\xi)}
 \leq C\alpha(\xi)\norm j
 \quad(\xi\in\ell_2,\ j\in \W(\ER)/\K(\ER)),
\]
then \(\B(\ER)/\K(\ER)\) does not have a unique complete norm.

In particular, the same conclusion follows if the common annihilator in
\(\ell_2\) of the two module representations on \(\W(\ER)/\K(\ER)\) is
infinite-dimensional.
\end{corollary}

\begin{proof}
Apply Theorem \ref{thm:lift} to the displayed split extension.  The final
sentence follows from Corollary \ref{cor:annihilator}, since every closed
subspace of the Hilbert space \(\ell_2\) is complemented.
\end{proof}

\section*{Conditional Dependencies}

Theorem \ref{thm:lift} and Corollary \ref{cor:annihilator} are unconditional.
The dependency for the source problem is the hypothesis in Corollary
\ref{cor:read}.  The literature checked in this push gives the strong splitting
and the square-zero quotient, but not a product statement such as
\[
\rho(\ell_2)\,(\W(\ER)/\K(\ER))=(0)
\quad\hbox{or}\quad
(\W(\ER)/\K(\ER))\,\rho(\ell_2)=(0),
\]
nor the weaker boundedness of those actions with respect to an exotic complete
norm on \(\ell_2\).  This is the obstruction left for verification.

\section*{Literature status}

Skillicorn proves that the weak Calkin algebra
\(\B(\ER)/\W(\ER)\) has at least two non-equivalent complete algebra norms
and states the ordinary Calkin question as open in Remark 2.6.  Ware's thesis
shows that the ordinary Read Calkin algebra does not have a unique algebra norm:
the quotient norm is not maximal, via Read's discontinuous derivation.  This
does not produce a non-equivalent complete norm.  Arnott--Laustsen later record
that the weak Calkin algebra is neither maximal nor incompressible, again at
the weak-Calkin level.  No later source located in the present search settles
the complete-norm question for \(\B(\ER)/\K(\ER)\).

\section*{Verification notes}

The previous naive norm
\(\norm{j}+\beta(u)\) on \(J\oplus \rho(\ell_2^\sim)\) fails without the
module-boundedness hypothesis because the cross terms
\(\rho(\xi)j\) and \(j\rho(\xi)\) may be unbounded in the exotic quotient
coordinate.  Theorem \ref{thm:lift} isolates exactly the missing boundedness.
Future verification should compute, using the explicit Laustsen--Skillicorn
operators \(T_\xi\), whether a large subspace of the \(\ell_2\)-coordinate
annihilates \(J=\W(\ER)/\K(\ER)\) modulo compact operators, or whether the
module representation factors through a weaker Banach norm on \(\ell_2\).

\section*{References}

\begin{itemize}
\item R. Skillicorn, \emph{The uniqueness-of-norm problem for Calkin
algebras}, Math. Proc. R. Ir. Acad. 115A (2015), 145--152;
arXiv:1507.08118.
\item N. J. Laustsen and R. Skillicorn, \emph{Extensions and the weak Calkin
algebra of Read's Banach space admitting discontinuous derivations}, Studia
Math. 236 (2017), 51--62; arXiv:1602.08963.
\item G. K. Ware, \emph{Uniqueness of norm properties of Calkin algebras},
PhD thesis, Australian National University, 2014.
\item M. Arnott and N. J. Laustsen, \emph{Uniqueness of algebra norm on
quotients of the algebra of bounded operators on a Banach space},
arXiv:2308.11586.
\end{itemize}

\end{document}
