\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm,enumitem,hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\B}{\mathcal B}
\newcommand{\Fin}{\mathrm{Fin}}
\newcommand{\ba}{\mathrm{ba}}
\newcommand{\ult}{\mathrm{ult}}
\newcommand{\clop}{\mathrm{Clop}}
\newcommand{\N}{\mathbb N}
\newcommand{\dd}{\,\triangle\,}

\title{A Bounding-Number Version of the Density-Killing Step}
\author{agent\_lane\_00}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source and target}

Drygier and Plebanek call a compactification \(\gamma\omega\) \emph{smooth}
when the natural copy of \(c_0\) is complemented in \(C(\gamma\omega)\)
\cite{DP2016}.  In Boolean-algebra language, if
\(\Fin\subseteq\mathcal A\subseteq P(\omega)\), the compactification
\(K_{\mathcal A}\) is smooth if and only if there is a bounded sequence
\((\nu_n)\) of finitely additive measures on \(\mathcal A\), vanishing on finite
sets, such that
\[
        \nu_n(A)-\delta_n(A)\longrightarrow 0
        \qquad (A\in\mathcal A).
\]
The source proves under CH that there is a smooth compactification of \(\omega\)
with nonseparable remainder, and explicitly notes that it is not known whether
the CH assumption can be removed; the authors suggest that
\(\mathfrak b=\mathfrak c\) may suffice.

The present note proves the local strengthening behind that suggestion.  The
countable Boolean algebra in Lemma 6.3 of \cite{DP2016} can be replaced by an
arbitrary Boolean algebra of cardinality \(<\mathfrak b\).  This is not by
itself the full \(\mathfrak b=\mathfrak c\) theorem, because the global
bookkeeping of all possible countable dense extension candidates remains a
separate issue.

\section*{Idea of the proof}

In the source proof, countability of \(\mathcal B\) is used to enumerate
\(\mathcal B\) and force every old algebra element contained in the new set
\(X\) to be contained in a finite initial part of \(X\).  The companion paper
\cite{DP2015} proves precisely the replacement for this enumeration: for an
algebra of size \(<\mathfrak b\) and a countable decreasing \(s\)-family
\((S_j(k))_{k}\), one can choose a single function \(g\in\omega^\omega\) so
that every \(B\in\mathcal B\) with \(B\subseteq\bigcup_j S_j(g(j))\) is already
contained in a finite subunion.

We build such \(s\)-families inside the prescribed dense ultrafilters \(p_j\).
The sets \(S_j(k)\) are chosen small for finitely many measures, absorb the
finite exceptional set where pointwise convergence has not yet made them small,
and avoid longer and longer initial segments of \(\omega\).  Then
\[
        X=\bigcup_j S_j(g(j))
\]
belongs to every extension of every \(p_j\), while \(\omega\setminus X\) remains
infinite.  Thus those extensions are not dense.  The same finite-subunion
property gives the required inner-measure estimate
\((\nu_n)_*(X)\to0\) along \(n\notin X\), while density of the \(p_j\)'s gives
\(\nu_n^*(X)=1\).  Los--Marczewski extensions then preserve
\(\nu_n-\delta_n\to0\).

\section*{Definitions}

Let \(\mathfrak b\) denote the bounding number.  If
\(\Fin\subseteq\mathcal B\subseteq P(\omega)\), write \(K_\mathcal B\) for the
Stone compactification of \(\omega\) and \(K_\mathcal B^*\) for its remainder.
For a finitely additive probability \(\nu\) on \(\mathcal B\) and
\(Z\subseteq\omega\), define
\[
        \nu_*(Z)=\sup\{\nu(B):B\in\mathcal B,\ B\subseteq Z\},
        \qquad
        \nu^*(Z)=\inf\{\nu(B):B\in\mathcal B,\ Z\subseteq B\}.
\]
All measures below are nonnegative finitely additive probabilities.

\begin{lemma}[finite-cover lemma]\label{lem:finite-cover}
Let \(\Fin\subseteq\mathcal B\subseteq P(\omega)\) have
\(|\mathcal B|<\mathfrak b\).  For each \(j\in\omega\), let
\((S_j(k))_{k\in\omega}\) be a decreasing sequence in \(\mathcal B\) with
\(\bigcap_k S_j(k)=\emptyset\).  Then there is \(g_0\in\omega^\omega\) such
that whenever \(g\ge g_0\) and
\[
        X_g=\bigcup_{j\in\omega}S_j(g(j)),
\]
every \(B\in\mathcal B\) satisfying \(B\subseteq X_g\) is contained in a finite
subunion \(\bigcup_{j\le N}S_j(g(j))\).
\end{lemma}

\begin{proof}
This is the domination lemma used in \cite{DP2015}; we recall the argument to
make clear that only \(|\mathcal B|<\mathfrak b\) and the decreasing-to-empty
property are used.

For a finite set \(m=\{0,\ldots,m-1\}\) and \(\varphi\in\omega^m\), write
\[
        X_\varphi=\bigcup_{j<m}S_j(\varphi(j)).
\]
For fixed \(B\in\mathcal B\), the set of \(\varphi\in\omega^m\) for which
\(B\setminus X_\varphi\) is infinite has finitely many minimal elements under
the coordinatewise order; this is the finite-dimensional combinatorial lemma
from \cite[Lemma 4.1]{DP2015}, proved by induction on \(m\).
Consequently, for every \(m\) there is a finite set \(I_m^B\subseteq\omega\)
such that whenever \(B\setminus X_\varphi\) is infinite, it meets \(I_m^B\).

Choose \(h_B\in\omega^\omega\) so that
\[
        S_j(h_B(j))\cap\bigcup_{m\le j}I_m^B=\emptyset
        \qquad(j\in\omega).
\]
This is possible because each \(S_j(k)\) decreases to the empty set.  Since
\(|\mathcal B|<\mathfrak b\), choose \(g_0\) eventually dominating all
\(h_B\), \(B\in\mathcal B\).

Let \(g\ge g_0\), \(B\in\mathcal B\), and \(B\subseteq X_g\).  Pick \(N\) such
that \(h_B(j)\le g(j)\) for \(j\ge N\).  If \(B\setminus X_{g|N}\) were
infinite, then it would meet \(I_N^B\).  But every tail set
\(S_j(g(j))\), \(j\ge N\), is disjoint from \(I_N^B\), contradicting
\(B\subseteq X_g\).  Hence \(B\setminus X_{g|N}\) is finite.  Each of its
finitely many points lies in some tail \(S_j(g(j))\), so increasing \(N\) if
necessary gives \(B\subseteq\bigcup_{j\le N}S_j(g(j))\).
\end{proof}

\section*{The local theorem}

\begin{theorem}\label{thm:local}
Let \(\Fin\subseteq\mathcal B\subseteq P(\omega)\) be a Boolean algebra with
\(|\mathcal B|<\mathfrak b\).  Let \((p_j)_{j\in\omega}\) be a countable dense
set in \(K_\mathcal B^*\).  Suppose that \((\nu_n)_{n\in\omega}\) is a sequence
of nonatomic probabilities on \(\mathcal B\) such that
\[
        \nu_n|\Fin=0 \quad\hbox{and}\quad
        \nu_n-\delta_n\to0
        \quad\hbox{pointwise on }\mathcal B.
\]
Then there is an infinite set \(X\subseteq\omega\) such that:
\begin{enumerate}[label=(\roman*)]
\item for every choice of extensions \(\widetilde p_j\in\ult(\mathcal B[X])\)
of \(p_j\), the family \(\{\widetilde p_j:j\in\omega\}\) is not dense in
\(K_{\mathcal B[X]}^*\);
\item every \(\nu_n\) has a nonatomic probability extension
\(\widetilde\nu_n\) to \(\mathcal B[X]\), and these extensions can be chosen so
that \(\widetilde\nu_n-\delta_n\to0\) pointwise on \(\mathcal B[X]\).
\end{enumerate}
\end{theorem}

\begin{proof}
Put \(\eta_j=2^{-(j+3)}\).  For each \(j\) we first construct a decreasing
sequence \(S_j(k)\in p_j\), \(k\in\omega\), such that
\[
        \bigcap_k S_j(k)=\emptyset
\]
and, for every \(k\),
\[
        n\notin S_j(k)\quad\Longrightarrow\quad
        \nu_n(S_j(k))<\eta_j.               \tag{1}
\]
We also arrange \(\nu_i(S_j(k))<\eta_j\) for all \(i\le k\).

Assume \(S_j(k-1)\) has been chosen, with \(S_j(-1)=\omega\).  Since the finite
sum \(\nu_0+\cdots+\nu_k\) is nonatomic and \(p_j\) is nonprincipal, there is
\[
        C\in p_j,\qquad
        C\subseteq S_j(k-1)\setminus\{0,\ldots,k-1\},
\]
such that \(\nu_i(C)<\eta_j\) for \(i\le k\).  By pointwise convergence on
\(\mathcal B\), the set
\[
        F=\{n\notin C:\nu_n(C)\ge\eta_j\}
\]
is finite.  For \(k>0\), the inductive hypothesis applied to \(S_j(k-1)\) gives
\(F\subseteq S_j(k-1)\).  Also \(F\cap\{0,\ldots,k-1\}=\emptyset\).  Define
\[
        S_j(k)=C\cup F.
\]
Finite sets have \(\nu_n\)-measure zero, so the smallness inequalities are
unchanged.  The sequence is decreasing and avoids every fixed integer
eventually, hence has empty intersection.

We now use Lemma \ref{lem:finite-cover}.  There is some \(g\in\omega^\omega\)
such that, for
\[
        X=\bigcup_{j\in\omega} S_j(g(j)),
\]
every \(B\in\mathcal B\) satisfying \(B\subseteq X\) is contained in a finite
subunion \(\bigcup_{j\le N}S_j(g(j))\).

The set \(\omega\setminus X\) is infinite.  Indeed, if \(\omega\subseteq X\),
the finite-subunion property would give
\(\omega\subseteq\bigcup_{j\le N}S_j(g(j))\) for some \(N\), and therefore
\[
        1=\nu_0(\omega)
        \le \sum_{j\le N}\nu_0(S_j(g(j)))
        \le \sum_{j\le N}\eta_j < \frac12,
\]
a contradiction.

Since \(S_j(g(j))\in p_j\) and \(S_j(g(j))\subseteq X\), every extension of
\(p_j\) to \(\mathcal B[X]\) contains \(X\).  The nonempty clopen set
\(\widehat{\omega\setminus X}\cap K_{\mathcal B[X]}^*\) is therefore disjoint
from all extensions of the \(p_j\)'s.  This proves (i).

We next estimate the inner and outer measures of \(X\).  Fix \(n\).  If
\(B\in\mathcal B\) and \(\nu_n(B)>0\), then \(B\) is infinite.  Since
\((p_j)\) is dense in \(K_\mathcal B^*\), some \(p_j\) contains \(B\).  Hence
\[
        B\cap S_j(g(j))\in p_j
\]
is infinite, so \(B\cap X\ne\emptyset\).  Thus no positive-measure member of
\(\mathcal B\) is disjoint from \(X\), and consequently
\[
        \nu_n^*(X)=1.                       \tag{2}
\]

For the inner measure, let \(n\notin X\), and let \(B\in\mathcal B\) with
\(B\subseteq X\).  By the finite-subunion property,
\[
        B\subseteq \bigcup_{j\le N}S_j(g(j))
\]
for some \(N\).  Given \(K\le N\), split this finite union into the first
\(K\) pieces and the tail.  Since \(n\notin X\), condition (1) gives
\[
        \nu_n\!\left(\bigcup_{K\le j\le N}S_j(g(j))\right)
        \le \sum_{j\ge K}\eta_j.
\]
For each fixed \(j<K\), pointwise convergence on \(S_j(g(j))\) gives
\(\nu_n(S_j(g(j)))\to0\) along \(n\notin X\), because then
\(\delta_n(S_j(g(j)))=0\).  Therefore
\[
        \limsup_{n\notin X}(\nu_n)_*(X)
        \le \sum_{j\ge K}\eta_j.
\]
Letting \(K\to\infty\), we obtain
\[
        \lim_{n\notin X}(\nu_n)_*(X)=0.     \tag{3}
\]

Define \(t_n=1\) for \(n\in X\), and
\[
        t_n=(\nu_n)_*(X)
\]
for \(n\notin X\).  By (2), \(t_n\in[(\nu_n)_*(X),\nu_n^*(X)]\).  The
Los--Marczewski extension theorem, used in the source as Theorem 3.2, gives a
probability extension \(\widetilde\nu_n\) of \(\nu_n\) to
\(\mathcal B[X]\) with \(\widetilde\nu_n(X)=t_n\).  By construction and (3),
\[
        \widetilde\nu_n(X)-\delta_n(X)\longrightarrow0.
\]
The source convergence lemma \cite[Lemma 3.3]{DP2016} then implies
\[
        \widetilde\nu_n-\delta_n\to0
        \quad\hbox{pointwise on }\mathcal B[X].
\]

Finally, the extensions may be chosen nonatomic.  If \(q\in\ult(\mathcal B[X])\)
and \(p=q|\mathcal B\), nonatomicity of \(\nu_n\) gives \(B\in p\) with
\(\nu_n(B)<\varepsilon\).  One of \(B\cap X\) and \(B\setminus X\) belongs to
q, and its \(\widetilde\nu_n\)-measure is at most \(\nu_n(B)\).  Hence
\(\inf\{\widetilde\nu_n(C):C\in q\}=0\), as required.
\end{proof}

\section*{Consequences and limitation}

Theorem \ref{thm:local} is exactly the source paper's density-destruction
step with ``countable'' replaced by ``of cardinality \(<\mathfrak b\)''.  It
therefore removes the local obstacle to running the large smooth compactification
construction past countable stages.

It does not by itself prove the full \(\mathfrak b=\mathfrak c\) strengthening
of Theorem 6.1 of \cite{DP2016}.  In a long construction one must also ensure
that every possible countable dense family of ultrafilter extensions is
presented at a stage where the current algebra still has size \(<\mathfrak b\).
That global bookkeeping problem is separate from the local lemma proved here.

\section*{Novelty check}

The run indexes contained no previous packet or attempt for arXiv:1601.03770.
A bounded web search for the exact title, ``smooth compactification'',
``nonseparable remainder'', and ``\(\mathfrak b=\mathfrak c\)'' found the source
paper and the companion arXiv:1501.06972 result on nonseparable remainders
supporting a measure, but no later smoothness theorem.  The present statement is
not claimed as a full literature resolution of the source question.

\section*{Human review recommendation}

Review Theorem \ref{thm:local} as a technical partial result.  The delicate
points are the recursive construction of \(S_j(k)\), the use of the
\(<\mathfrak b\) finite-subunion lemma, and the passage from the inner/outer
measure estimates to the Los--Marczewski extensions.

\begin{thebibliography}{9}

\bibitem{DP2016}
P. Drygier and G. Plebanek,
\emph{Compactifications of \(\omega\) and the Banach space \(c_0\)},
arXiv:1601.03770, 2016.

\bibitem{DP2015}
P. Drygier and G. Plebanek,
\emph{Nonseparable growth of the integers supporting a measure},
arXiv:1501.06972, 2015.

\end{thebibliography}

\end{document}
