\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\BLip}{\operatorname{BLip}}
\newcommand{\Blin}{\operatorname{Blin}}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\F}{\mathcal F}
\newcommand{\eps}{\varepsilon}

\title{Partial Positive Results for Complementing Bilinear Maps in Two-Lipschitz Spaces}
\author{Run fa\_banach\_001, agent\_lane\_04}
\date{2026-06-29}

\begin{document}
\maketitle

\section*{Source Question}

Mandal's paper \cite{mandal} asks in Question~1:
\[
\text{Is } \Blin(X,Y;E)\text{ complemented in }\BLip_0(X,Y;E)?
\]
The paper proves a norm-one positive answer when the codomain $E$ is a dual
Banach space and states that the general case remains open. This note records
two partial extensions.

\section*{Definitions}

For real normed spaces $X,Y$ and a Banach space $E$, a map
$T:X\times Y\to E$ belongs to $\BLip_0(X,Y;E)$ if it vanishes on the coordinate
axes and
\[
\|T(x,y)-T(x',y)-T(x,y')+T(x',y')\|
   \leq C\|x-x'\|\,\|y-y'\|
\]
for all $x,x'\in X$ and $y,y'\in Y$. The least such $C$ is denoted
$\BLip(T)$. The closed subspace $\Blin(X,Y;E)$ consists of bounded bilinear
maps, with the usual bilinear norm.

\section*{Idea of the Proof}

Mandal's projection is built from a vector-valued invariant mean. The dual-space
hypothesis is only used to guarantee that the scalar invariant mean applied
coordinatewise lands back in $E$, rather than merely in $E^{**}$. Thus the same
formula works whenever the canonical copy of $E$ is complemented in $E^{**}$.

There is also a different operator-theoretic route. The source paper recalls
the two-Lipschitz linearization
\[
\BLip_0(X,Y;E)\cong
L\bigl(\F(X)\widehat\otimes_\pi \F(Y),E\bigr).
\]
Under this identification, bilinear maps are precisely the operators that
factor through the tensor of the barycenter maps
\[
\beta_X\otimes\beta_Y:
\F(X)\widehat\otimes_\pi\F(Y)\longrightarrow X\widehat\otimes_\pi Y.
\]
If those barycenter quotient maps have bounded linear right inverses, the
tensor quotient splits and hence precomposition gives a projection for every
codomain $E$.

\begin{theorem}[codomains complemented in the bidual]
Let $X,Y$ be real normed spaces and let $E$ be a Banach space. Suppose that the
canonical copy $\kappa_E(E)$ is complemented in $E^{**}$ by a projection
$R:E^{**}\to \kappa_E(E)$ with $\|R\|\leq C$. Then
$\Blin(X,Y;E)$ is complemented in $\BLip_0(X,Y;E)$ by a projection of norm at
most $C$.
\end{theorem}

\begin{proof}
Let $G=X\times Y$ be the additive amenable group. Choose a scalar invariant
mean $m$ on $\ell_\infty(G)$. For $f\in \ell_\infty(G,E)$ define
$\widetilde M f\in E^{**}$ by
\[
\langle \widetilde M f,e^*\rangle
 = m\bigl((\langle e^*,f(g)\rangle)_{g\in G}\bigr)
 \qquad(e^*\in E^*).
\]
Then $\widetilde M$ has norm one, is translation invariant, and sends the
constant function $g\mapsto e$ to $\kappa_E(e)$. Set
\[
M=\kappa_E^{-1}R\widetilde M:\ell_\infty(G,E)\longrightarrow E.
\]
This is an $E$-valued translation-invariant mean with $\|M\|\leq C$ and
$M(\widehat e)=e$ for constant functions.

For $T\in\BLip_0(X,Y;E)$ and $w\in X,z\in Y$, put
\[
\phi_T^{w,z}(x,y)=T(w+x,z+y)-T(w+x,y)-T(x,z+y)+T(x,y).
\]
As in Mandal's Lemma~2.1, $\phi_T^{w,z}\in\ell_\infty(G,E)$ and
\[
\|\phi_T^{w,z}\|_\infty\leq \BLip(T)\|w\|\,\|z\|.
\]
Define
\[
P(T)(w,z)=M(\phi_T^{w,z}).
\]
The additivity identities for the functions $\phi_T^{w,z}$ are exactly those
used in \cite[Theorem~2.3]{mandal}; translation invariance and linearity of
$M$ imply that $P(T)$ is additive in each variable. The preceding bound gives
continuity, so the standard rational-scalar argument makes $P(T)$ bilinear.
Moreover
\[
\|P(T)(w,z)\|\leq C\,\BLip(T)\|w\|\,\|z\|,
\]
hence $\|P\|\leq C$.

If $T$ is already bilinear, then
$\phi_T^{w,z}$ is the constant function with value $T(w,z)$, so
$P(T)(w,z)=M(\widehat{T(w,z)})=T(w,z)$. Therefore $P$ is a bounded linear
projection from $\BLip_0(X,Y;E)$ onto $\Blin(X,Y;E)$.
\end{proof}

\begin{corollary}
Question~1 has an affirmative answer whenever $E$ is complemented in its
bidual. Equivalently, by Lindenstrauss' characterization quoted in
\cite{kania}, this includes Banach spaces isomorphic to complemented subspaces
of dual Banach spaces.
\end{corollary}

\begin{theorem}[split barycenter maps]
Let $X,Y$ be Banach spaces. Suppose the barycenter maps
$\beta_X:\F(X)\to X$ and $\beta_Y:\F(Y)\to Y$ admit bounded linear right
inverses $s_X:X\to\F(X)$ and $s_Y:Y\to\F(Y)$. Then for every Banach space
$E$, the subspace $\Blin(X,Y;E)$ is complemented in $\BLip_0(X,Y;E)$. The
projection can be chosen with norm at most $\|s_X\|\,\|s_Y\|$.
\end{theorem}

\begin{proof}
Let $Z=\F(X)\widehat\otimes_\pi\F(Y)$ and
$W=X\widehat\otimes_\pi Y$. The two-Lipschitz linearization identifies
$\BLip_0(X,Y;E)$ isometrically with $L(Z,E)$.

Let
\[
q=\beta_X\otimes\beta_Y:Z\to W,\qquad
s=s_X\otimes s_Y:W\to Z.
\]
Then $qs=I_W$, and $\|s\|\leq\|s_X\|\,\|s_Y\|$. Hence
\[
\pi=sq:Z\to Z
\]
is a bounded projection onto $s(W)$.

Under the linearization, a two-Lipschitz map is bilinear precisely when its
linearization factors through $q$; this is the content of Mandal's
Proposition~4.3, equivalently the vanishing on
$\ker\beta_X\widehat\otimes_\pi\F(Y)+
\F(X)\widehat\otimes_\pi\ker\beta_Y$.
Define, for $A\in L(Z,E)$,
\[
\Pi(A)=A\pi=Asq.
\]
Then $\Pi(A)$ factors through $q$, so it corresponds to a bilinear map. If
$A=Bq$ already factors through $q$, then
\[
\Pi(A)=Bqsq=Bq=A.
\]
Thus $\Pi$ is a projection onto the bilinear subspace and
$\|\Pi\|\leq\|s\|\leq\|s_X\|\,\|s_Y\|$.
\end{proof}

\begin{remark}
The second theorem gives an all-codomain positive answer for every pair
$(X,Y)$ whose free-space barycenter quotients split linearly. In particular,
finite-dimensional $X$ and $Y$ satisfy this hypothesis by choosing a basis and
lifting basis vectors to their Dirac masses. The theorem is not claimed to
cover arbitrary Banach spaces.
\end{remark}

\section*{Limitations and Novelty Check}

These results do not settle Mandal's unrestricted question. They leave open
the case where $E$ is not complemented in $E^{**}$ and the free-space
barycenter maps for the domains do not split.

Local index searches for arXiv:2512.05640, ``two-Lipschitz'', ``BLip\_0'',
``Blin'', and ``vector-valued invariant mean'' found no existing run packet
for this paper. Web searches for the exact title, for ``BLip\_0(X,Y;E)'', and
for ``Blin(X,Y;E)'' found the source paper and the one-variable predecessor
arXiv:2506.09324, but no later complete answer. The bidual-complemented
codomain result relies on known invariant-mean theory, especially Kania
\cite{kania}; the present contribution is the direct application to Mandal's
Question~1 and the split-domain operator reformulation above.

\section*{References}

\begin{thebibliography}{9}
\bibitem{mandal}
A. Mandal,
\emph{Projection from space of two-Lipschitz operators onto the space of
Bilinear maps},
arXiv:2512.05640, 2025.

\bibitem{kania}
T. Kania,
\emph{Vector-valued invariant means revisited once again},
arXiv:1607.03387, 2016.

\bibitem{godefroykalton}
G. Godefroy and N. J. Kalton,
\emph{Lipschitz-free Banach spaces},
Studia Math. 159 (2003), 121--141.
\end{thebibliography}

\end{document}
