\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Status Note: EAE/MC to SC for Banach Space Operators}
\author{fa\_banach\_001 / agent\_super\_00}
\date{June 30, 2026}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_already\_answered}. This is a literature-status packet,
not a new proof or counterexample.

\section*{Source Question}

The source paper is S. ter Horst, M. Messerschmidt, A. C. M. Ran,
M. Roelands, and M. Wortel, \emph{Equivalence after extension and Schur
coupling coincide for inessential operators}, arXiv:1706.09177. In the
Introduction, page 2, the authors recall the question of Bart and
Tsekanovskii asking whether the Banach-space operator relations equivalence
after extension (EAE), matricial coupling (MC), and Schur coupling (SC)
coincide. Since EAE and MC were known to coincide and SC was known to imply
them, the remaining issue was whether
\[
  \mathrm{EAE}/\mathrm{MC} \Longrightarrow \mathrm{SC}.
\]
The same page says this matter had not been settled, then states the source
paper's positive special case as Theorem 1.1: for inessential operators
\[
  \mathrm{EAE} \Longleftrightarrow \mathrm{EAOE} \Longleftrightarrow
  \mathrm{SC},
\]
with finite-dimensional extensions.

\section*{Supporting Answer}

The later supporting paper is S. ter Horst, M. Messerschmidt, A. C. M. Ran,
and M. Roelands, \emph{Equivalence after extension and Schur coupling do not
coincide, on essentially incomparable Banach spaces}, arXiv:1901.09254. Its
abstract, page 1, explicitly identifies the 1994 Bart--Tsekanovskii question
and states that the general answer is negative. It gives a concrete family:
the forward shift operators on $\ell^p$ and $\ell^q$, for $1 \leq p,q \leq
\infty$ and $p \neq q$, are EAE but not SC.

The formal location is Theorem 2.1 on page 3. For operators on essentially
incomparable Banach spaces, EAE is characterized by matching kernel and
cokernel dimensions for Fredholm operators, while SC additionally requires
Fredholm index zero. Thus operators with the same nonzero index can be EAE
without being SC. The theorem states in particular that SC and EAE do not
coincide.

\section*{Conclusion and Scope}

The broad EAE/MC $\Rightarrow$ SC question recorded as unsettled in
arXiv:1706.09177 is already answered by arXiv:1901.09254, and the answer is
no in general. The source paper's own Theorem 1.1 remains an affirmative
special case for inessential operators. This status note does not address
later refined questions about Fredholm, relatively regular, or index-set
variants; it only clears this 2017 broad-question target from the fresh-paper
queue.

\section*{Local Evidence}

The packet includes a local copy of the source PDF as \texttt{source\_paper.pdf}
and the decisive later paper as \texttt{supporting\_paper\_1901.09254.pdf}.
The cheap run indexes were searched for the source arXiv id, title keywords,
Schur coupling, inessential operators, and the supporting arXiv id. No prior
solution packet for arXiv:1706.09177 was found; the only relevant memory hit
was an attempt row for arXiv:1901.09254 itself.

\begin{thebibliography}{9}

\bibitem{tHMRRW18}
S. ter Horst, M. Messerschmidt, A. C. M. Ran, M. Roelands, and M. Wortel,
\emph{Equivalence after extension and Schur coupling coincide for inessential
operators}, arXiv:1706.09177.

\bibitem{tHMRR22}
S. ter Horst, M. Messerschmidt, A. C. M. Ran, and M. Roelands,
\emph{Equivalence after extension and Schur coupling do not coincide, on
essentially incomparable Banach spaces}, arXiv:1901.09254.

\end{thebibliography}

\end{document}
