\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\CR}{\operatorname{CR}}
\newcommand{\DR}{\operatorname{DR}}
\newcommand{\N}{\mathbb N}
\newcommand{\eps}{\varepsilon}
\newcommand{\directlim}{\varinjlim}
\newcommand{\Sphere}{S}

\title{Expanders Give a Negative Answer to the\\
Finite-Complexity-Rate Inductive-Limit Question}
\author{}
\date{June 21, 2026}
\hypersetup{
  pdftitle={Expanders Give a Negative Answer to the Finite-Complexity-Rate Inductive-Limit Question},
  pdfsubject={A counterexample to the finite-complexity-rate inductive-limit question}
}

\begin{document}
\maketitle

\begin{abstract}
Tian and Yu asked whether every countable discrete group is an inductive limit of groups with finite complexity rates.  We first verify the supplied direct-union reduction: under injective bonding maps, the question is equivalent to asking whether every finitely generated group has finite complexity rate.  We then give a counterexample.

The key observation is quantitative.  If a finitely generated group coarsely contains a bounded-degree expander sequence, then every family of maps used in the definition of complexity rate has unit-scale variation at least a constant multiple of $1/p$ in the target $\ell^{2p}$.  This follows from the $L_q$ Poincar\'e inequality for expanders with constant $O(q)$.  Hence such a group has decay rate exactly $1$, or equivalently infinite complexity rate.  Osajda constructed finitely presented groups---indeed fundamental groups of closed aspherical manifolds---that coarsely contain expanders.  One of these groups is therefore a finitely presented counterexample.

Finally, finite presentability shows that the same example cannot be a filtered colimit of finite-complexity-rate groups even when arbitrary, non-injective bonding homomorphisms are allowed.  Thus the answer to the question is negative under both standard interpretations of ``inductive limit.''
\end{abstract}

\section{The question and the rate condition}

Tian and Yu prove the strong Novikov conjecture for countable groups with finite complexity rate and ask:
\begin{quote}
``It is natural to ask whether every countable discrete group is an inductive limit of groups with finite complexity rates.''
\end{quote}
Their rate condition is Definition~1.4 of \cite{TianYu2026}; Definition~1.3 there only defines the iterated logarithms.

For the present argument, only the following consequence of the definition is needed.  If $\CR(\Gamma)<\infty$, then there are a finite tuple
\[
  \mathbf a=(a_0,a_1,\ldots,a_k)>1,
  \qquad a_0\ge 1,\quad a_j\ge 0,
\]
in the lexicographic order used in \cite{TianYu2026}, a constant $C>0$, numbers $N_p>0$, and maps
\[
  \phi_p:\Gamma\longrightarrow \Sphere\bigl(\ell^{2p}(\N)\bigr)
  \qquad (p\in\N)
\]
such that
\begin{align}
 d(x,y)\le 1
 &\Longrightarrow
 \|\phi_p(x)-\phi_p(y)\|_{2p}
 \le \eps_p,
 \label{eq:variation}\tag{1.1}\\
 d(x,y)\ge N_p
 &\Longrightarrow
 \|\phi_p(x)-\phi_p(y)\|_{2p}\ge 1,
 \label{eq:separation}\tag{1.2}
\end{align}
where
\[
 \eps_p=
 \frac{C}{p^{a_0}(\log p)^{a_1}\cdots(\log_k p)^{a_k}}.
\]
The truncated convention for the iterated logarithms at small values of $p$ is irrelevant here.  Since $\mathbf a>1$ lexicographically,
\begin{equation}
  p\eps_p\longrightarrow 0.
  \label{eq:pepszero}\tag{1.3}
\end{equation}
Indeed, either $a_0>1$, or $a_0=1$ and the first nonzero logarithmic exponent is positive.

The definition is independent of the chosen left-invariant proper metric on $\Gamma$ \cite{TianYu2026}.  For finitely generated groups we therefore use a word metric.

\section{Audit of the supplied partial result}

\begin{lemma}[Subgroup heredity]\label{lem:subgroup}
If a countable group $\Gamma$ has finite complexity rate, then every subgroup $\Lambda\leq \Gamma$ has finite complexity rate.
\end{lemma}

\begin{proof}
Restrict a left-invariant proper metric on $\Gamma$ to $\Lambda$.  It remains left-invariant and proper.  Restricting each witness $\phi_p$ preserves both the variation estimate and the large-scale separation estimate.  Metric independence of the definition then gives the intrinsic assertion for $\Lambda$.
\end{proof}

\begin{proposition}[Direct-union reduction]\label{prop:directunion}
For a countable group $\Gamma$, the following are equivalent.
\begin{enumerate}
  \item $\Gamma$ is a directed union of subgroups with finite complexity rate.
  \item Every finitely generated subgroup of $\Gamma$ has finite complexity rate.
\end{enumerate}
\end{proposition}

\begin{proof}
Suppose $\Gamma=\bigcup_{i\in I}\Gamma_i$, with $I$ directed and all $\Gamma_i$ of finite complexity rate.  A finite generating set of a subgroup $H\leq\Gamma$ is contained in one stage, so $H$ is a subgroup of that stage and Lemma~\ref{lem:subgroup} applies.

Conversely, the finitely generated subgroups of $\Gamma$, ordered by inclusion, form a directed set: $H_1$ and $H_2$ are contained in $\langle H_1\cup H_2\rangle$.  Their union is $\Gamma$.
\end{proof}

Thus the main reduction in the supplied packet is correct.  Its additional observation about non-injective systems is also correct: a filtered colimit of torsion-free groups is torsion-free.  If the class of an element $g_i$ has finite order in the colimit, then a later image of $g_i$ has finite order; torsion-freeness of that later stage forces the image, and hence the colimit class, to be trivial.  In particular, torsion groups cannot be obtained as filtered colimits of free groups.

\section{The expander obstruction}

We use spectral expanders.  Let $X=(V,E)$ be a finite connected $d$-regular graph, and let $A_X$ be the normalized adjacency operator.  We say that a sequence $(X_n)$ is a spectral expander sequence with gap $\sigma>0$ if $|V(X_n)|\to\infty$ and
\[
  1-\lambda_2(A_{X_n})\ge \sigma
\]
for every $n$.

We say that $(X_n)$ \emph{coarsely embeds into} a finitely generated group $\Gamma$ if there are maps $\iota_n:V(X_n)\to\Gamma$ and nondecreasing functions $\rho_-,\rho_+:[0,\infty)\to[0,\infty)$, independent of $n$, such that $\rho_-(t)\to\infty$ and
\begin{equation}
 \rho_-\bigl(d_{X_n}(u,v)\bigr)
 \le d_\Gamma\bigl(\iota_n(u),\iota_n(v)\bigr)
 \le \rho_+\bigl(d_{X_n}(u,v)\bigr).
 \label{eq:coarseembed}\tag{3.1}
\end{equation}

The analytic input is the following form of Matou\v{s}ek's extrapolated Poincar\'e inequality.  It is Corollary~4.5 of Naor--Silberman \cite{NaorSilberman2011}; see also Matou\v{s}ek \cite{Matou\v{s}ek1997}.

\begin{lemma}[$L_q$ Poincar\'e inequality]\label{lem:poincare}
Let $X=(V,E)$ be a finite $d$-regular graph whose normalized adjacency operator has spectral gap at least $\sigma>0$.  For every $q\ge 2$ and every map $f:V\to\ell^q$,
\begin{equation}
 \left(
   \frac{1}{|V|^2}\sum_{u,v\in V}\|f(u)-f(v)\|_q^q
 \right)^{1/q}
 \le
 \frac{2q}{\sqrt\sigma}
 \left(
   \frac{1}{d|V|}\sum_{u\in V}\sum_{v\sim u}
        \|f(u)-f(v)\|_q^q
 \right)^{1/q}.
 \label{eq:poincare}\tag{3.2}
\end{equation}
\end{lemma}

\begin{theorem}[Expanders force the critical $1/p$ rate]\label{thm:expanderobstruction}
Let $\Gamma$ be finitely generated.  Suppose a $d$-regular spectral expander sequence with gap $\sigma>0$ coarsely embeds into $\Gamma$.  Let
\[
  \phi_p:\Gamma\to \Sphere\bigl(\ell^{2p}(\N)\bigr)
\]
be any maps satisfying \eqref{eq:variation} and \eqref{eq:separation}, with unit-scale variations $\eps_p$.  Then there is a constant $c>0$, independent of $p$, such that
\begin{equation}
  p\eps_p\ge c \qquad\text{for every }p\in\N.
  \label{eq:lowerbound}\tag{3.3}
\end{equation}
Consequently, $\CR(\Gamma)=\infty$ (equivalently, $\DR(\Gamma)=1$ in the notation of \cite{TianYu2026}).
\end{theorem}

\begin{proof}
Let
\[
  L=\max\bigl\{1,\lceil\rho_+(1)\rceil\bigr\}.
\]
Because the word metric on $\Gamma$ is geodesic, \eqref{eq:variation} implies
\begin{equation}
 d_\Gamma(x,y)\le L
 \quad\Longrightarrow\quad
 \|\phi_p(x)-\phi_p(y)\|_{2p}\le L\eps_p.
 \label{eq:Lvariation}\tag{3.4}
\end{equation}

Fix $p$ and put $q=2p$.  Choose an integer $R_p\ge1$ such that $\rho_-(R_p)\ge N_p$.  Since the degrees of the graphs are bounded, the cardinality of every radius-$(R_p-1)$ ball is at most
\[
  B_p=1+d\sum_{j=0}^{R_p-2}(d-1)^j,
\]
with the empty sum interpreted as zero.  Choose $n$ so large that $|V(X_n)|\ge 2B_p$.  Then at least half of the ordered pairs $(u,v)\in V(X_n)^2$ satisfy $d_{X_n}(u,v)\ge R_p$.

Set $f=\phi_p\circ\iota_n$.  For every such far pair, \eqref{eq:coarseembed} and \eqref{eq:separation} give
\[
  \|f(u)-f(v)\|_q\ge1.
\]
Therefore
\begin{equation}
 \left(
   \frac{1}{|V(X_n)|^2}
   \sum_{u,v\in V(X_n)}\|f(u)-f(v)\|_q^q
 \right)^{1/q}
 \ge 2^{-1/q}.
 \label{eq:loweraverage}\tag{3.5}
\end{equation}
If $u\sim v$, then \eqref{eq:coarseembed} gives
$d_\Gamma(\iota_n(u),\iota_n(v))\le\rho_+(1)\le L$, so \eqref{eq:Lvariation} yields
\[
  \|f(u)-f(v)\|_q\le L\eps_p.
\]
Applying Lemma~\ref{lem:poincare} and \eqref{eq:loweraverage},
\[
  2^{-1/q}
  \le \frac{2q}{\sqrt\sigma}L\eps_p.
\]
Since $q=2p$ and $2^{-1/(2p)}\ge2^{-1/2}$,
\[
  p\eps_p
  \ge \frac{\sqrt\sigma}{4L}2^{-1/(2p)}
  \ge \frac{\sqrt\sigma}{4\sqrt2\,L}.
\]
This proves \eqref{eq:lowerbound}.

If $\CR(\Gamma)<\infty$, the defining variations satisfy \eqref{eq:pepszero}, contradicting \eqref{eq:lowerbound}.  Hence $\CR(\Gamma)=\infty$.  Tian and Yu show that every countable group has decay rate at least $1$, so the decay rate here is exactly $1$.
\end{proof}

\section{A finitely presented counterexample and arbitrary filtered colimits}

Osajda constructed finitely generated groups whose Cayley graphs contain isometrically embedded expander sequences \cite[Theorem~3.2 and Corollary~3.3]{Osajda2020}.  His construction applies to fixed-degree regular expander families; for such families, combinatorial expansion and Cheeger's inequality give the uniform normalized spectral gap required in Theorem~\ref{thm:expanderobstruction}.  More strongly, he obtained the following consequence of Sapir's asphericity-preserving Higman embedding construction:
\begin{quote}
There exist closed aspherical manifolds of dimension at least four whose fundamental groups contain coarsely embedded expanders \cite[Corollary~3.5]{Osajda2020}.
\end{quote}
A fundamental group of a closed manifold is finitely presented.  Combining this with Theorem~\ref{thm:expanderobstruction} gives:

\begin{corollary}\label{cor:fpbad}
There exists a finitely presented group $G$ with $\CR(G)=\infty$.
\end{corollary}

For injective inductive limits, Proposition~\ref{prop:directunion} already makes $G$ a counterexample.  Finite presentability also handles arbitrary bonding homomorphisms.

\begin{lemma}[A finitely presented colimit is a retract of a stage]\label{lem:retract}
Let $(G_i,\alpha_{ij})$ be a directed system of groups and let
\[
  G\cong\directlim_i G_i.
\]
If $G$ is finitely presented, then for some $i$ there is a homomorphism
$s:G\to G_i$ such that the canonical map $\lambda_i:G_i\to G$ satisfies
$\lambda_i\circ s=\operatorname{id}_G$.  In particular, $G$ is isomorphic to a subgroup of $G_i$.
\end{lemma}

\begin{proof}
Write
\[
  G=\langle x_1,\ldots,x_m\mid r_1,\ldots,r_k\rangle.
\]
Choose representatives of the finitely many generators in stages of the system, and then pass to one common later stage $G_i$.  Each word $r_j$ in those representatives maps to the identity in the colimit.  Equality in a filtered colimit is witnessed at a later stage, so after passing to a common later stage $G_{i'}$, all finitely many relators are simultaneously trivial.  Sending $x_l$ to its chosen representative in $G_{i'}$ therefore defines a homomorphism $s:G\to G_{i'}$.  The composite $\lambda_{i'}\circ s$ fixes every generator $x_l$, hence is the identity.  Thus $s$ is injective.
\end{proof}

\begin{theorem}[Negative answer under both interpretations]\label{thm:negative}
The question of Tian and Yu has a negative answer.
\begin{enumerate}
  \item There is a countable, finitely presented group that is not a directed union of groups with finite complexity rates.
  \item The same group is not a filtered colimit of groups with finite complexity rates, even if the bonding homomorphisms are arbitrary and need not be injective.
\end{enumerate}
\end{theorem}

\begin{proof}
Let $G$ be the finitely presented group from Corollary~\ref{cor:fpbad}.

For the first assertion, if $G$ were a directed union of finite-complexity-rate subgroups, its finite generating set would lie in one stage.  That stage would contain all of $G$, so $G$ itself would have finite complexity rate, a contradiction.

For the second assertion, suppose $G\cong\directlim_i G_i$ with every $G_i$ of finite complexity rate.  By Lemma~\ref{lem:retract}, $G$ embeds in one $G_i$.  Subgroup heredity, Lemma~\ref{lem:subgroup}, would then imply $\CR(G)<\infty$, again a contradiction.
\end{proof}

\section{Literature status}

The exact notion of complexity rate was introduced only in May 2026.  Searches by the paper title, arXiv identifier, the phrase ``finite complexity rate,'' and the inductive-limit question did not locate a later paper or note explicitly answering the question as of June 21, 2026.  The counterexample above is a synthesis of two older ingredients: the linear-in-$q$ Poincar\'e bound for $L_q$ targets and the existence of finitely presented groups coarsely containing expanders.  No claim of priority beyond that synthesis is made here.

\begin{thebibliography}{9}

\bibitem{Matou\v{s}ek1997}
Ji\v{r}\'i Matou\v{s}ek,
\newblock On embedding expanders into $\ell_p$ spaces,
\newblock \emph{Israel Journal of Mathematics} \textbf{102} (1997), 189--197.

\bibitem{NaorSilberman2011}
Assaf Naor and Lior Silberman,
\newblock Poincar\'e inequalities, embeddings, and wild groups,
\newblock \emph{Compositio Mathematica} \textbf{147} (2011), no.~5, 1546--1572.

\bibitem{Osajda2020}
Damian Osajda,
\newblock Small cancellation labellings of some infinite graphs and applications,
\newblock \emph{Acta Mathematica} \textbf{225} (2020), no.~1, 159--191.

\bibitem{TianYu2026}
Geng Tian and Guoliang Yu,
\newblock Embedding complexity into Banach spaces and the strong Novikov conjecture,
\newblock arXiv:2605.12930v1, 2026.

\end{thebibliography}

\end{document}
