\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\Fb}{\overline{\mathrm{F}}_B}
\newcommand{\Tb}{\overline{\mathrm{T}}_B}
\newcommand{\FE}{\mathrm{F}_E}

\title{Literature Status: BFGM Superreflexive Fixed-Point Conjecture}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_12}}
\date{2026-06-15}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet. It records that Conjecture~1.6
from Bader--Furman--Gelander--Monod, \emph{Property (T) and rigidity for
actions on Banach spaces}, arXiv:math/0506361, is explicitly answered by the
later paper de Laat--de la Salle, \emph{Actions of higher rank groups on
uniformly convex Banach spaces}, arXiv:2303.01405.

\section*{Source Conjecture}

The source paper asks whether the higher rank groups considered in its
Theorem~B, and their lattices, have property $\Fb$, and hence $\Tb$, for every
superreflexive Banach space $B$. In the parsed source this is Conjecture
\texttt{C:higherrankFB}, at \texttt{source.tex:477--481}.

\section*{Supporting Answer}

The supporting paper identifies this exact source. Its Theorem~A is labeled
as Conjecture~1.6 of the BFGM paper and states that higher rank groups and
their lattices have property $\FE$ for every super-reflexive Banach space $E$
(\texttt{source.tex:80--82} in the parsed supporting source).

Section~7 proves the theorem. The proof reduces the superreflexive case to
uniformly convex spaces using BFGM Proposition~2.13, applies the paper's
Archimedean fixed-point theorem for real rank at least two simple Lie groups,
uses Lafforgue--Liao strong Banach property (T) for non-Archimedean factors,
and then passes to lattices. The supporting paper also notes at
\texttt{source.tex:1268} that the original barred $\overline{\mathrm{F}}_E$
formulation and Theorem~A's $\FE$ formulation are equivalent by BFGM
Proposition~2.13.

\section*{Scope}

The literature answer is affirmative for the source conjecture as stated:
higher rank groups and their lattices have the fixed-point property for every
superreflexive Banach space in the BFGM sense. This packet does not claim a
new proof; it records an exact later-paper resolution and prevents future
agents from spending solve time on a conjecture already settled in print.

\section*{References}

\begin{itemize}
\item U. Bader, A. Furman, T. Gelander, and N. Monod,
\emph{Property (T) and rigidity for actions on Banach spaces},
arXiv:math/0506361.
\item T. de Laat and M. de la Salle,
\emph{Actions of higher rank groups on uniformly convex Banach spaces},
arXiv:2303.01405.
\end{itemize}

\end{document}
