\documentclass[11pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem*{theorem*}{Literature-implied subcase}

\begin{document}

\title{Nets in Separable \texorpdfstring{\(\mathcal L_\infty\)}{L-infinity} Spaces}
\author{Run fa\_banach\_001}
\date{2026-06-15}
\maketitle

\noindent
\textbf{Status.} \texttt{literature\_implied\_answer (partial subcase)}.
This is not a new proof and not a full solution of Kalton's question. It
records that a later theorem of Hajek--Medina gives a positive Schauder-basis
answer for nets in separable infinite-dimensional \(\mathcal L_\infty\)-spaces.

\section*{Source Question}

Hajek--Medina, \emph{Schauder bases in Lipschitz free spaces over nets in
Banach spaces}, arXiv:2112.03095, recall Kalton's question whether
Lipschitz free spaces over separable uniformly discrete metric spaces have the
bounded approximation property. They note that it suffices to consider the
case where the metric space is a net \(N\) in a Banach space \(X\), that
Kalton proved a positive answer when \(X\) has separable dual or is a
separable dual space, and that the case of a general separable Banach space
\(X\) remains open.

The same source paper proves stronger Schauder-basis conclusions in several
special cases, including finite-dimensional spaces and Banach spaces with a
Schauder basis containing \(c_0\), or with a \(c_0\)-like FDD.

\section*{Supporting Literature}

Hajek--Medina, \emph{Schauder bases in Lipschitz free spaces over nets of
\(\mathcal L_\infty\)-spaces}, arXiv:2202.08032, explicitly says that it is
motivated by the same Kalton question and studies the retractional structure
of nets in \(\mathcal L_\infty\)-spaces. Its introduction states that, as a
corollary of the construction, the Lipschitz free space \(\mathcal F(N)\) over
a net in any separable \(\mathcal L_\infty\)-space has a Schauder basis.

The decisive statements are the paper's \emph{Main Theorem} and the immediate
corollary:
\begin{quote}
  a net in any separable infinite-dimensional \(\mathcal L_\infty\)-space has
  a retractional basis; hence, if \(N\) is such a net, then
  \(\mathcal F(N)\) has a Schauder basis.
\end{quote}
The first implication from a retractional basis to a Schauder basis is also
recorded in the same paper via the cited retractional-basis theorem.

\begin{theorem*}
Let \(X\) be a separable infinite-dimensional \(\mathcal L_\infty\)-space and
let \(N\) be a net in \(X\). Then \(\mathcal F(N)\) has a Schauder basis.
In particular, \(\mathcal F(N)\) has the bounded approximation property.
\end{theorem*}

\begin{proof}
The theorem and corollary in arXiv:2202.08032 give the Schauder basis directly.
The bounded approximation property follows because the partial-sum projections
associated to a Schauder basis are finite-rank operators and are uniformly
bounded by the basis constant.
\end{proof}

\section*{Scope}

This is a proper subcase of the source target, not a solution of the general
separable Banach-space case. The packet records a positive answer for nets in
separable infinite-dimensional \(\mathcal L_\infty\)-spaces. Finite-dimensional
and \(c_0\)/\(c_0\)-like FDD cases are already handled by the source paper
arXiv:2112.03095 itself.

\section*{Search and Provenance Notes}

The run indexes were searched for arXiv:2112.03095, the source title, free
spaces over nets, Schauder bases, retractional bases, and the BAP question.
No prior packet or attempt for this exact target or this
\(\mathcal L_\infty\)-subcase was found. External search found the decisive
later paper arXiv:2202.08032, along with adjacent but nondecisive papers on
retractional-basis obstructions and Lipschitz-free spaces over nets.

The supporting paper is by the same authors and explicitly says it is
motivated by the Kalton/net BAP problem and extends their previous net-basis
work. This packet classifies the relation as an agent-identified
literature-implied partial subcase because the general separable Banach-space
problem remains open.

\begin{thebibliography}{9}

\bibitem{HM2021}
P. Hajek and R. Medina,
\emph{Schauder bases in Lipschitz free spaces over nets in Banach spaces},
arXiv:2112.03095.

\bibitem{HM2022}
P. Hajek and R. Medina,
\emph{Schauder bases in Lipschitz free spaces over nets of
\(\mathcal L_\infty\)-spaces},
arXiv:2202.08032.

\end{thebibliography}

\end{document}
