\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{microtype}
\raggedright

\newtheorem*{claim}{Claim}

\begin{document}

\begin{center}
{\Large Literature-implied answer for arXiv:1001.2026}\\[4pt]
{\large Spanning unimodular eigenvectors need not be perfectly spanning}
\end{center}

\paragraph{Status.}
\textbf{literature\_implied\_answer}.  This is not a new proof produced by the
run.  It is a direct identification of a later counterexample theorem with one
of the open questions in Sophie Grivaux, \emph{A new class of frequently
hypercyclic operators}, arXiv:1001.2026.

\paragraph{Source question.}
In Section 6, ``Open questions and remarks'', subsection ``Hypercyclic
operators with spanning unimodular eigenvectors'', Grivaux asks:
\begin{quote}
If $T$ is a hypercyclic operator on $X$ whose eigenvectors associated to
eigenvalues of modulus $1$ span a dense subspace of $X$, is it true that the
unimodular eigenvectors of $T$ are perfectly spanning?
\end{quote}
This is Question 2 in the source paper's notation.

\paragraph{Supporting literature.}
Quentin Menet, \emph{Linear chaos and frequent hypercyclicity},
arXiv:1410.7173, Theorem~1.2, constructs a chaotic operator $T$ on $\ell^1$
which is neither $\mathcal U$-frequently hypercyclic nor distributionally
chaotic; in particular, $T$ is chaotic and not frequently hypercyclic.  The
same introduction recalls the standard identity, for complex vector spaces,
that periodic points are spanned by eigenvectors associated to roots of unity.

\paragraph{Identification.}
Menet's operator is chaotic, so it is hypercyclic and has a dense set of
periodic points.  Since periodic points lie in the span of root-of-unity
eigenvectors, the eigenvectors associated to eigenvalues of modulus $1$ span a
dense subspace of $\ell^1$.

If these unimodular eigenvectors were perfectly spanning, Grivaux's main
Theorem~1.1 in arXiv:1001.2026 would imply that $T$ is frequently
hypercyclic.  This contradicts Menet's Theorem~1.2.  Therefore Menet's
operator is a negative example to Grivaux's Question 2.

\begin{claim}
There exists a bounded hypercyclic operator on a complex Banach space whose
unimodular eigenvectors span a dense subspace, but whose unimodular
eigenvectors are not perfectly spanning.
\end{claim}

\paragraph{Scope and limitations.}
The chaotic-implies-frequently-hypercyclic question quoted immediately before
Grivaux's Question~2 is explicitly answered negatively by Menet and is already
recorded in this run in the packet
\texttt{1005.1416\_chaotic\_not\_fhc\_answered\_by\_1410.7173}.  The present
packet records the additional implied answer to Grivaux's ``perfectly
spanning'' question.

This packet does not answer the related question in Grivaux's final section
asking for an operator whose full unimodular point spectrum is countable and
whose corresponding eigenspaces span densely.  The argument above uses only
the dense root-of-unity eigenspaces forced by dense periodic points, and does
not verify the full unimodular point spectrum of Menet's operator.

\paragraph{Search evidence.}
The run's cheap indexes had no direct packet for arXiv:1001.2026 or this
perfectly-spanning implication.  They did contain the adjacent
arXiv:1005.1416/arXiv:1410.7173 chaotic-not-frequently-hypercyclic packet.
Local source search and web/arXiv search were then used for the key phrases
``spanning unimodular eigenvectors'', ``perfectly spanning'', and
``chaotic operator frequently hypercyclic''.

\begin{thebibliography}{9}
\bibitem{Grivaux1001}
S. Grivaux,
\emph{A new class of frequently hypercyclic operators},
arXiv:1001.2026; Indiana Univ. Math. J. 60 (2011), 1177--1201.

\bibitem{Menet1410}
Q. Menet,
\emph{Linear chaos and frequent hypercyclicity},
arXiv:1410.7173.
\end{thebibliography}

\end{document}
