\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\newcommand{\Fp}{\mathcal F_p}
\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}

\title{Literature Status for Two Questions in arXiv:1905.07201}
\author{Run fa\_banach\_001, lane 7}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Status}

This note records that two open-problem signals in
Albiac--Ansorena--Cudeiro--Doucha, arXiv:1905.07201, are settled by the later
paper Albiac--Ansorena--Cuth--Doucha, arXiv:2006.08018.

The Schauder-basis question is explicitly answered by the later paper. The
Euclidean subset complementability question is answered by direct specialization
of a later complementability result.

\section*{Source Questions}

In Section 6 of arXiv:1905.07201, the authors ask:
\begin{quote}
Does $\Fp([0,1]^d)$ have a Schauder basis for each $d\in\N$ and each
$p\in(0,1]$?
\end{quote}
The later paper arXiv:2006.08018 identifies this as Question 6.5 of
arXiv:1905.07201.

The same source section also asks:
\begin{quote}
Let $\mathcal M\subset \R^d$ and $p\in(0,1]$. Is $\Fp(\mathcal M)$
isomorphic to a complemented subspace of $\Fp(\R^d)$?
\end{quote}

\section*{Later Answer}

The abstract of arXiv:2006.08018 states that the authors prove
$\Fp(\R^d)$ admits a Schauder basis for every $p\in(0,1]$, and that they give
explicit formulas for bases of both $\Fp(\R^d)$ and its isomorphic space
$\Fp([0,1]^d)$. The introduction then says explicitly that this answers
arXiv:1905.07201, Question 6.5, in the positive.

The theorem-level statement is arXiv:2006.08018, Theorem 2.9:
\[
  \text{for every }0<p\leq 1\text{ and }d\in\N,\quad
  \Fp([0,1]^d)\text{ has a Schauder basis.}
\]
This directly resolves the basis question.

For the complementability question, the same later paper records that for every
$d\in\N$ there is a constant $C=C(p,d)$ such that, whenever
$\mathcal M\subset \mathcal N\subset \R^d$, the space $\Fp(\mathcal M)$ is
$C$-complemented in $\Fp(\mathcal N)$. Taking $\mathcal N=\R^d$ yields a
positive answer to the source question: $\Fp(\mathcal M)$ is isomorphic to a
complemented subspace of $\Fp(\R^d)$ for every $\mathcal M\subset\R^d$ and
$p\in(0,1]$.

\section*{Scope}

No new theorem is claimed in this packet. The purpose is only to clear these
two target-queue signals and record the exact later source that answers them.
The neighboring questions in arXiv:1905.07201 about the metric approximation
property, isometric copies of $\ell_p$, and metric quotients are not resolved
here.

\section*{References}

\begin{enumerate}
\item F. Albiac, J. L. Ansorena, J. Cudeiro, and M. Doucha,
\emph{Embeddability of $\ell_p$ and bases in Lipschitz free $p$-spaces for
$0<p\leq 1$}, arXiv:1905.07201.
\item F. Albiac, J. L. Ansorena, M. Cuth, and M. Doucha,
\emph{Structure of the Lipschitz free $p$-spaces $\mathcal F_p(\mathbb Z^d)$
and $\mathcal F_p(\mathbb R^d)$ for $0<p\leq 1$}, arXiv:2006.08018.
\end{enumerate}

\end{document}
