\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{A literature-implied negative answer for unconditional frames in \(C_r^*(F_2)\)}
\author{Run \texttt{fa\_banach\_001}, lane 10}
\date{2026-06-18}

\begin{document}
\maketitle

\paragraph{Status.}
This packet records a \emph{literature-implied answer}, not a new proof packet.
It gives a negative answer to a narrow question in Remark 2.2 of Rui Liu and
Zhong-Jin Ruan, \emph{Cb-frames for operator spaces}, arXiv:1601.06218: whether
there is any unconditional frame for \(C_r^*(F_2)\).  It does not settle the
broader cb-basis problem for separable C*-algebras or weakly amenable reduced
group C*-algebras.

\paragraph{Source question.}
Liu--Ruan construct a cb-frame for \(C_r^*(F_2)\) and observe in Remark 2.2 that
their particular frame is not unconditional.  The remark ends with the statement
that, at that moment, it was not known whether there is any unconditional frame
for \(C_r^*(F_2)\).

\paragraph{Supporting theorem.}
Samir Kabbaj and Rafik Karkri, \emph{Structure of Banach spaces and besselian
Schauder frames}, arXiv:2411.00777, prove that an unconditional Schauder frame
is Besselian and that a Banach space with a Besselian frame has
Pe\l czy\'nski's property (u).  They then state as a corollary that
\(C([0,1])\) has no Besselian frame and consequently no unconditional frame.

\paragraph{Identification.}
Let \(a\) be a free generator of \(F_2\), and let \(H=\langle a\rangle\cong
\mathbb Z\).  The canonical Fourier projection
\[
  E_H\left(\sum_{s\in F_2} c_s\lambda_s\right)
  =
  \sum_{s\in H} c_s\lambda_s
\]
extends to the standard contractive conditional expectation from
\(C_r^*(F_2)\) onto \(C_r^*(H)\).  Hence \(C_r^*(H)\) is a complemented Banach
subspace of \(C_r^*(F_2)\).  Since \(C_r^*(H)\cong C(\mathbb T)\), and
\(C(\mathbb T)\) is isomorphic to \(C([0,1])\) by the classical Milutin theorem,
the supporting result rules out unconditional frames for \(C_r^*(H)\).

Unconditional frames pass to complemented subspaces: applying a bounded
projection to the frame vectors and restricting the coefficient functionals
gives an unconditional frame for the complemented subspace.  Therefore, if
\(C_r^*(F_2)\) had an unconditional frame, \(C_r^*(H)\cong C(\mathbb T)\) would
also have one, contradicting the preceding paragraph.

\paragraph{Conclusion.}
\[
  C_r^*(F_2) \text{ has no unconditional frame.}
\]
Thus the unconditional-frame question in Liu--Ruan Remark 2.2 has a negative
answer by later Banach-frame structure results.

\paragraph{Provenance and scope.}
The implication is agent-identified.  The supporting paper does not appear to
explicitly cite the Liu--Ruan question.  The conclusion concerns ordinary
Banach-space unconditional frames, matching the norm-unconditional convergence
used in Liu--Ruan's remark; it does not decide whether weakly amenable reduced
group C*-algebras have cb-bases.

\paragraph{References.}
\begin{itemize}
  \item R. Liu and Z.-J. Ruan, \emph{Cb-frames for operator spaces},
  arXiv:1601.06218.
  \item S. Kabbaj and R. Karkri, \emph{Structure of Banach spaces and besselian
  Schauder frames}, arXiv:2411.00777.
\end{itemize}

\end{document}
