\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Lop}{\mathcal L}
\newcommand{\K}{\mathcal K}
\newcommand{\Cal}{\mathcal C\!al}
\newcommand{\Ad}{\operatorname{Ad}}
\newcommand{\Homeo}{\operatorname{Homeo}}

\begin{document}

\section*{Human Review: automorphism-map noninjectivity}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Reviewed for survey inclusion, but not independently checked
in detail by the human reviewer; excluded for the time being.

\noindent Verdict: Exclude from the verified successful examples at this stage.

\section*{Human Comments}

The proposed counterexample is an elementary observation about the literal
formulation of the question.  It argues as follows.  If \(X\) is a Banach
space and \(P\) is a nonzero finite-rank projection, then
\[
  U=I+P
\]
is invertible, and conjugation
\[
  \Ad_U(T)=UTU^{-1}
\]
defines an automorphism of \(\Lop(X)\).  Since \(U-I=P\) is compact, this
automorphism induces the identity map on the Calkin algebra
\[
  \Cal(X)=\Lop(X)/\K(X).
\]
The packet further argues that \(\Ad_U\) need not be the identity
automorphism of \(\Lop(X)\).  Thus, if this elementary calculation is
accepted, then the literal map from automorphisms of \(\Lop(X)\) to the
induced automorphisms of the Calkin algebra would not be injective.

However, I do not think this should be included as a successful project
example for the time being.  The source manuscript itself raises several
reliability concerns.  It appears to claim a large number of substantial
results at once, including realization, rigidity, ideal classification, and
new reflexive Calkin-algebra examples.  Some parts of the manuscript also
look internally suspicious.  For example, the running header refers to
``Strongly Singular Kirchhoff-Type Equations'', which is unrelated to the
paper title and content.  More substantively, the paper appears to pass from
finite direct sums of copies of \(C(K)\) to matrix algebras \(M_m(C(K))\) by
using a linear identification, even though these are not isomorphic as Banach
algebras for \(m>1\) since the former is commutative and the latter is not.
There is also a claim involving \(\ell_2\) with pointwise multiplication as a
Calkin algebra, which is problematic since such an algebra is not unital.

There is a second issue with the formulation of the relevant open question.
The remark asks about injectivity of a natural map to \(\Homeo(K)\), but it
also phrases the issue in terms of possible non-inner automorphisms in the
kernel.  The candidate counterexample only supplies an inner automorphism,
coming from conjugation by an invertible compact perturbation of the
identity.  Therefore it answers the literal wording, but probably not the
more meaningful intended question if inner automorphisms were supposed to be
ignored.

\section*{Short Version}

The finite-rank conjugation argument is a possible elementary objection to
the literal wording: inner automorphisms implemented by invertible compact
perturbations of the identity should be invisible in the Calkin algebra.  But
the argument has not been independently checked in detail by the human
reviewer, the source paper appears unreliable enough, and the intended
question may differ enough from the literal wording that this packet should
be excluded for now.

\section*{Literature and Follow-Up}

This example should not be used as evidence of mathematical progress unless
the source manuscript is independently validated or the authors clarify that
the literal inner-automorphism obstruction is genuinely relevant to their
intended question.  If the intended problem concerns outer automorphisms or
automorphisms modulo inner automorphisms, then the present packet does not
address it.

\section*{Review Outcome}

Exclude this packet from the verified successful examples for the time being.
It may be retained as a cautionary case: the automatic system found a
possible elementary objection to the literal wording, but the argument has
not been independently checked in detail by the human reviewer, and the
surrounding source and likely intended question make it unsuitable for
inclusion as a positive mathematical-discovery example.

\end{document}
