\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\dens}{\operatorname{dens}}

\title{Literature Status: Maximal Separated Sets in Super-Reflexive Spaces}
\author{fa\_banach\_001}
\date{2026-06-23}

\begin{document}
\maketitle

\paragraph{Status.}
This is a literature-already-answered identification.  The source question
from Kania--Kochanek, arXiv:1503.08166, Remark 3.7, is explicitly answered by
Hajek--Kania--Russo, arXiv:1803.11501.

\paragraph{Source question.}
Kania and Kochanek study cardinal sizes of subsets of unit spheres whose
mutual distances are strictly larger than one.  Their Theorem A proves, among
other things, that nonseparable quasi-reflexive spaces have uncountable
$(1+)$-separated subsets and that nonseparable super-reflexive spaces have
uncountable $(1+\varepsilon)$-separated subsets for some $\varepsilon>0$.
In Remark 3.7 they give a reflexive space of density $\omega_\omega$ for
which the supremum in $\mathsf{eo}(X)$ is not attained at the density of
$X$, and then ask what happens in the super-reflexive case.

\paragraph{Supporting answer.}
Hajek--Kania--Russo, arXiv:1803.11501, Theorem B, proves the maximal-density
super-reflexive statement: if $X$ is super-reflexive, then there exist
$\varepsilon>0$ and a symmetrically $(1+\varepsilon)$-separated subset of
$S_X$ of cardinality $\dens X$.  The introduction explicitly says that this
answers the question raised in Kania--Kochanek, Remark 3.7.  The same theorem
also strengthens the quasi-reflexive part of the source paper by showing that
every infinite-dimensional quasi-reflexive space has a symmetrically
$(1+)$-separated subset of $S_X$ with cardinality $\dens X$, and gives a
uniform $(1+\varepsilon)$ version for cardinals of uncountable cofinality.

\paragraph{Scope.}
This packet does not claim a solution of the fully general nonseparable
Kottman problem for arbitrary Banach spaces.  It records only the exact
super-reflexive Remark 3.7 answer and the associated quasi-reflexive
maximal-density strengthening.

\paragraph{References.}
\begin{itemize}
\item T. Kania and T. Kochanek, \emph{Uncountable sets of unit vectors that
are separated by more than 1}, arXiv:1503.08166, Studia Math. 232 (2016),
19--44.
\item P. Hajek, T. Kania, and A. Russo, \emph{Separated sets and Auerbach
systems in Banach spaces}, arXiv:1803.11501, Trans. Amer. Math. Soc. 373
(2020), 3113--3145.
\end{itemize}

\end{document}

