\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\newcommand{\BM}{d_{\mathrm{BM}}}
\newcommand{\ellone}{\ell_1^4}
\newcommand{\ellinf}{\ell_\infty^4}
\newcommand{\Ha}{H_\alpha}
\newcommand{\Hap}{H'_\alpha}

\title{A Literature-Implied Upper Bound for \texorpdfstring{\(\Hap(\ell_1^4)\)}{H'alpha(ell1^4)}}
\author{Run \texttt{fa\_banach\_001}, lane 9}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-implied partial-subcase note for
Mercourakis--Vassiliadis, arXiv:1902.05593.  It records an implication of a
later Banach--Mazur distance theorem of Kobos--Varivoda, arXiv:2305.06427.
It is not an original full solution of the source paper's open-problem list.

\section*{Source Question}

Mercourakis and Vassiliadis conclude with open problems.  Item 1(a) asks for
better upper and lower bounds for
\[
  \Hap(\ell_p^n)\quad\text{and}\quad \Ha(\ell_p^n)
\]
for \(n\ge 4\) and \(1\le p<2\).  The subcase recorded here is the strict
antipodal number of \(\ell_1^4\).

\section*{Supporting Literature}

Kobos and Varivoda prove in Theorem 3.1 of \cite{KV} that the Banach--Mazur
distance between the four-dimensional cube \(C_4\) and its polar
cross-polytope \(C_4^*\) is exactly \(2\).  In Banach-space notation,
\[
  \BM(\ellinf,\ellone)=2.
\]

\section*{Identification}

We claim that the supporting theorem implies
\[
  \Hap(\ellone) < 16,
\]
and hence, since \(\Hap\) is integer-valued,
\[
  \Hap(\ellone) \le 15.
\]

Indeed, suppose toward a contradiction that
\(\Hap(\ellone)=16=2^4\).  Then there is a strict bounded separated antipodal
set \(S\subset S_{\ellone}\) with \(16\) points and separation constant
\(d>1\) in the sense of the source paper.

The renorming theorem quoted in the introduction of \cite{MV} says that such
a set becomes equilateral under an equivalent norm \(|||\cdot|||\), and the
Banach--Mazur distance from the original norm is at most \(2/d\).  Thus
\[
  \BM\bigl((\mathbb R^4,\|\cdot\|_1),(\mathbb R^4,|||\cdot|||)\bigr)
  \le \frac{2}{d}<2.
\]
Since an equilateral set in a four-dimensional normed space has at most
\(2^4\) points, with equality only for \(\ell_\infty^4\), the renormed space
is linearly isometric to \(\ellinf\).  Consequently
\[
  \BM(\ellone,\ellinf)<2,
\]
contradicting Kobos--Varivoda's equality \(\BM(\ellone,\ellinf)=2\).

\section*{Scope}

This only improves the upper bound in the single endpoint subcase
\((p,n)=(1,4)\) for the strict antipodal Hadwiger number.  It does not
determine the exact value of \(\Hap(\ell_1^4)\), does not decide
\(\Ha(\ell_1^4)\), and does not address the remaining \(1<p<2\) cases.
The relation appears to be an agent-identified implication rather than a
claim explicitly made by Kobos--Varivoda.

\section*{Search Notes}

Cheap run-index searches for \texttt{1902.05593}, antipodal Hadwiger,
Hadwiger numbers, and finite-dimensional Banach keywords found no existing
packet for this source paper.  Targeted web searches for antipodal Hadwiger
phrases found the source paper, while searches for Banach--Mazur distance
between \(\ell_1^4\) and \(\ell_\infty^4\) found Kobos--Varivoda's later
paper.  No direct later paper stating this exact \(\Hap(\ell_1^4)\) corollary
was found in this bounded search.

\begin{thebibliography}{9}

\bibitem{MV}
S. K. Mercourakis and G. Vassiliadis,
\emph{Antipodal Hadwiger numbers of finite-dimensional Banach spaces},
arXiv:1902.05593, 2019.

\bibitem{KV}
T. Kobos and M. Varivoda,
\emph{On the Banach--Mazur Distance in Small Dimensions},
arXiv:2305.06427, 2023.

\end{thebibliography}

\end{document}
