\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\ellTwo}{\ell_2}

\begin{document}

\section*{Human Review: Finite-codimensional quasicomplement counterexample}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 18 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct as a literal counterexample.

\section*{Human Comments}

The proposed solution appears correct as an answer to Problem 2.1 exactly as
stated in Barbosa--Raposo--Ribeiro's paper.  The example is
\[
  X=\ell_2\oplus_2 \mathbb R,
  \qquad
  Y=\ell_2\oplus\{0\},
  \qquad
  F=\{0\}\oplus\mathbb R.
\]
Then \(Y\) is closed, infinite-dimensional, and quasicomplemented.  In fact,
it is \(1\)-complemented, so the example is very elementary.

The obstruction is finite codimension.  Since
\[
  X=Y\oplus F,
\]
any subspace \(Z\) which is disjoint from \(Y\) and contains \(F\) must equal
\(F\).  Indeed, if \(z\in Z\), write \(z=y+f\) with \(y\in Y\) and
\(f\in F\).  Since \(F\subset Z\), one has \(y=z-f\in Z\cap Y=\{0\}\), so
\(z=f\in F\).  Hence \(Z=F\), and therefore
\[
  \dim Z/F=0,
\]
not infinity.

\section*{Interpretation}

Mathematically, the argument is correct.  However, this seems likely to be a
minor issue in the formulation of the question rather than a substantial
counterexample to the intended problem.  The example is simply a
finite-codimensional complemented subspace, and the obstruction comes from the
fact that the chosen finite-dimensional \(F\) already exhausts the quotient
\(X/Y\).  There is then no room left for a quasicomplement \(Z\) containing
\(F\) with infinite-dimensional quotient \(Z/F\).

This strongly suggests that the intended question was probably meant in the
setting of infinite codimension, which is also the setting emphasized by the
paper's later positive results.

\section*{Literature Check}

A preliminary online check did not find a later answer to this exact point.
OpenAlex reports no citing works for arXiv:2403.05806, a direct OpenAlex
citing-works query returned no results, and OpenCitations returned an empty
citation list for the arXiv DOI.  Targeted searches for the terminology
around total \(\alpha\)-quasicomplementation, finite codimension, and
Problem 2.1 did not reveal another source discussing this example.

\section*{Review Outcome}

The packet should be recorded as a correct literal counterexample, but with
the caveat that it probably identifies a missing hypothesis or intended
restriction in the question.  I would not present it as a deep mathematical
contribution; rather, it is a semantic warning about finite-codimensional
cases.

\end{document}
