\documentclass[11pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\begin{document}

\title{Relative Expanders and Ostrovskii's Bounded-Geometry Question}
\author{Run fa\_banach\_001}
\date{2026-06-28}
\maketitle

\noindent
\textbf{Status.}
\texttt{literature\_implied\_answer (bounded-geometry version; group version remains open)}.
This note records an existing literature answer, not a new theorem.

\section*{Source Question}

In \emph{Coarse embeddability into Banach spaces}, arXiv:0802.3666,
Ostrovskii asks whether a metric space with bounded geometry that is not
coarsely embeddable into Hilbert space must contain an expander-like
substructure. Immediately afterward he quotes the more specific
Gromov--Kasparov problem: if a finitely presented group has Cayley graph not
coarsely embeddable into \(\ell_2\), must that Cayley graph weakly contain a
family of expanders?

\section*{Supporting Literature}

Arzhantseva--Tessera, \emph{Relative expanders}, arXiv:1402.1481, construct a
finitely generated group \(G\) and finite-index normal subgroups
\((N_n)\) such that, for every finite generating set \(S\), the finite Cayley
graphs
\[
  (G/N_n,S)
\]
do not coarsely embed into any \(L^p\)-space for \(1\le p<\infty\), and more
generally not into any uniformly curved Banach space, yet admit no weakly
embedded expander.

\section*{Identification}

The coarse disjoint union of the graphs \((G/N_n,S)\) is a bounded-geometry
metric space. Since the sequence does not coarsely embed into any \(L^p\),
it does not coarsely embed into Hilbert space. Since the sequence admits no
weakly embedded expander, it gives a negative answer to Ostrovskii's broader
bounded-geometry question: non-embeddability into Hilbert does not force a
weakly embedded expander.

\section*{Scope}

This does not settle the narrower group formulation printed by Ostrovskii.
Arzhantseva--Tessera themselves explicitly leave open the problem of
constructing a finitely generated group whose Cayley graph does not coarsely
embed into Hilbert space and yet has no weakly embedded expander. Ostrovskii's
quoted problem asks the even narrower finitely presented version. Thus this
packet records only the bounded-geometry metric-space answer.

The separate question in Ostrovskii's Section 5 asking whether
\(\ell_2\) coarsely embeds into every infinite-dimensional Banach space is
already covered in the run registry by the Baudier--Lancien--Schlumprecht
answer, arXiv:1705.06797.

\section*{Provenance}

The supporting paper does not appear to cite arXiv:0802.3666 as the source of
the bounded-geometry question; the relation is therefore recorded as a
literature-implied answer. It is not a new counterexample from this run.

\end{document}
