\documentclass[10pt]{article}
\usepackage[margin=0.85in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Answer: Sharp Log-Concave Empirical Covariance Rate}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-07-19}

\begin{document}
\maketitle
\vspace{-1.2em}

\paragraph{Status.}
\texttt{literature\_implied\_answer}.  The precise covariance conjecture in
arXiv:1005.0816 is proved by the later arXiv:1012.0294.  The identification is
agent-made: the supporting paper does not explicitly say that it answers
Mendelson's conjecture.

\paragraph{Source conjecture.}
On printed page 47, near the end of the section
``From a bounded diameter to concentration,''
Mendelson asks for the optimal empirical covariance rate for independent
samples \(X_1,\ldots,X_N\) from an isotropic log-concave measure on
\(\mathbb R^n\).  Equation (6.6), labelled \texttt{sampling} in the source,
conjectures that for every
\(N\gtrsim n\), with high probability or in expectation,
\[
 \sup_{\theta\in S^{n-1}}
 \left|\frac1N\sum_{i=1}^N\langle\theta,X_i\rangle^2-1\right|
 \le C\sqrt{\frac nN}.
\]

\paragraph{Supporting theorem.}
Theorem~1 on printed page 2 (source label \texttt{raz}) of
Adamczak--Litvak--Pajor--Tomczak-Jaegermann proves that if \(n\le N\), the
vectors are independent,
their one-dimensional marginals have a uniform \(\psi_1\) bound, and their
Euclidean norms satisfy the paper's boundedness condition, then with
probability at least \(1-2e^{-c\sqrt n}\),
\[
 \sup_{\theta\in S^{n-1}}
 \left|\frac1N\sum_{i=1}^N
 \bigl(|\langle X_i,\theta\rangle|^2
       -\mathbb E|\langle X_i,\theta\rangle|^2\bigr)\right|
 \le C(\psi+K)^2\sqrt{\frac nN}.
\]
Example~2 immediately after the theorem states that isotropic log-concave
vectors satisfy both hypotheses with absolute constants, by Borell's and
Paouris' estimates.  Isotropy turns the expectation in the summand into \(1\).
The result therefore proves the conjectured high-probability estimate, for the
slightly larger range \(N\ge n\).

\paragraph{Scope and provenance.}
This identifies an existing proof and is not a new result.  It resolves the
specific equation \texttt{(sampling)}; the surrounding informal program of
extending other Gaussian results is outside the scope of the packet.  The
supporting paper describes its result as removing the logarithmic loss and
obtaining the Gaussian order for arbitrary \(N\), but it does not explicitly
name the source conjecture, so the conservative provenance is
\texttt{literature\_implied\_answer}.

\begin{thebibliography}{9}
\bibitem{Mendelson}
S. Mendelson,
\emph{Empirical processes with bounded \(\psi_1\) diameter},
Geom. Funct. Anal. 20 (2010), 988--1027;
\href{https://arxiv.org/abs/1005.0816}{arXiv:1005.0816}.

\bibitem{ALPT}
R. Adamczak, A. E. Litvak, A. Pajor, and N. Tomczak-Jaegermann,
\emph{Sharp bounds on the rate of convergence of the empirical covariance
matrix},
\href{https://arxiv.org/abs/1012.0294}{arXiv:1012.0294}.
\end{thebibliography}

\end{document}
