\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\dd}{\,d}
\newcommand{\id}{\mathrm{id}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\bary}{\operatorname{bar}}

\title{A Growth Obstruction to Free-Gibbs Barycenter Centering}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_08}}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source And Extracted Question}

The source is Charles-Philippe Diez, \emph{A sharp symmetrized free
transport-entropy inequality for the semicircular law}, arXiv:2410.02715.
In Remark 9 and the following conjecture, the paper asks whether, for every
continuous function \(f:\R\to\R\) satisfying the one-dimensional free Gibbs
growth condition
\[
        f(x)-2\log |x|\longrightarrow +\infty
        \qquad (|x|\to\infty),
\]
there exists \(\lambda\in\R\) such that the free Gibbs measure associated with
\(f+\lambda \id\) has barycenter zero.

\section*{Result}

As stated with only the displayed logarithmic growth condition, the conjecture
is false. The obstruction is simple: logarithmic confinement is stable under
translations, but not under arbitrary linear tilts. A non-centered translate of
a logarithmically confined potential gives an admissible potential for
\(\lambda=0\), while every nonzero linear tilt destroys confinement in one
direction.

\section*{Idea Of The Proof}

Start with an even admissible potential \(V\). By uniqueness, its free Gibbs
measure is symmetric and has barycenter zero. Translate the potential:
\(f_a(x)=V(x-a)\). Translation invariance of the logarithmic energy makes the
new equilibrium measure the translate of the old one, so its barycenter is
\(a\). If \(V\) grows only logarithmically, adding \(\lambda x\) with
\(\lambda\ne0\) makes the variational functional unbounded above by translating
any fixed compactly supported trial measure far in the favorable direction.
Thus \(\lambda=0\) gives the wrong barycenter and \(\lambda\ne0\) gives no free
Gibbs measure.

\begin{theorem}[Counterexample to the printed conjecture]
Let \(c>1\), \(a\ne0\), and
\[
        V(x)=c\log(1+x^2),\qquad f_a(x)=V(x-a).
\]
Then \(f_a\) is continuous and satisfies
\[
        f_a(x)-2\log |x|\to+\infty .
\]
However, there is no \(\lambda\in\R\) such that the free Gibbs measure
associated with \(f_a+\lambda x\) exists and has barycenter zero.
\end{theorem}

\begin{proof}
First,
\[
f_a(x)-2\log |x|
=c\log(1+(x-a)^2)-2\log |x|
=(2c-2)\log |x|+o(\log |x|),
\]
which tends to \(+\infty\) because \(c>1\).

Let \(\nu_V\) be the equilibrium measure for \(V\), i.e. the unique maximizer
of
\[
        \mu\mapsto \chi(\mu)-\int V\,\dd\mu .
\]
Since \(V\) is even, uniqueness implies that \(\nu_V\) is symmetric. Hence
\(\int x\,\dd\nu_V(x)=0\). Let \(\tau_a(x)=x+a\). The free entropy is invariant
under translations, and
\[
        \int f_a\,\dd((\tau_a)_\#\mu)
        =\int V\,\dd\mu .
\]
Therefore the unique maximizer for \(f_a\) is
\(\nu_{f_a}=(\tau_a)_\#\nu_V\). Its barycenter is \(a\), so \(\lambda=0\) does
not center it.

It remains to show that no nonzero \(\lambda\) is admissible. Let
\(\mu_0=\nu_V\), and write \(\mu_t=(\tau_t)_\#\mu_0\). The measure \(\mu_0\) is
compactly supported under the standard one-dimensional logarithmic confinement
hypothesis, and translation leaves \(\chi\) invariant. For \(\lambda>0\),
\[
\chi(\mu_t)-\int (f_a(x)+\lambda x)\,\dd\mu_t(x)
=\chi(\mu_0)-\int V(y+t-a)\,\dd\mu_0(y)-\lambda\int(y+t)\,\dd\mu_0(y).
\]
As \(t\to-\infty\), the middle integral is \(O(\log |t|)\), while
\(-\lambda t\to+\infty\). Thus the variational functional is unbounded above.
Hence no maximizer, and therefore no free Gibbs measure, exists for
\(f_a+\lambda x\).

The case \(\lambda<0\) is identical, sending \(t\to+\infty\). Consequently no
real \(\lambda\) gives an existing centered free Gibbs measure.
\end{proof}

\section*{Corrected Positive Statement}

The obstruction above disappears if the potential is assumed to be
superlinear in both directions. This is the natural hypothesis in the preceding
argument of the source when linear tilts are introduced.

\begin{proposition}[Superlinear repair]
Suppose \(f:\R\to\R\) is continuous and
\[
        \frac{f(x)}{|x|}\longrightarrow+\infty\qquad (|x|\to\infty),
\]
and suppose that for every \(\lambda\in\R\) the potential
\(f+\lambda\id\) has a unique free Gibbs equilibrium measure \(\nu_\lambda\).
Then there exists \(\lambda_0\in\R\) such that
\[
        \int x\,\dd\nu_{\lambda_0}(x)=0.
\]
\end{proposition}

\begin{proof}
Let
\[
        P(\lambda)=\eta(f+\lambda\id)
        =\sup_\mu\left\{\chi(\mu)-\int f\,\dd\mu
        -\lambda\int x\,\dd\mu(x)\right\}.
\]
As a supremum of affine functions of \(\lambda\), \(P\) is convex. The
superlinear hypothesis implies coercivity: taking any compactly supported
trial measure and translating it near a point where \(-\lambda x-f(x)\) is
large gives
\[
        P(\lambda)\geq C+\sup_x\{-\lambda x-f(x)\}-o(1),
\]
and the right-hand side tends to \(+\infty\) as \(|\lambda|\to\infty\). Hence
\(P\) attains a minimum at some \(\lambda_0\).

By the standard envelope theorem for a convex supremum with a unique maximizer
(equivalently, Danskin's theorem),
\[
        P'(\lambda)=-\int x\,\dd\nu_\lambda(x)
\]
at every \(\lambda\). Since \(\lambda_0\) minimizes \(P\), \(P'(\lambda_0)=0\),
which gives the desired barycenter identity.
\end{proof}

\section*{Verification And Limitations}

The counterexample uses only standard facts recalled in the source: existence
and uniqueness of the one-dimensional equilibrium measure under the logarithmic
growth hypothesis, uniqueness of the free Gibbs maximizer, and translation
invariance of the logarithmic energy/free entropy.

The negative result is a literal reading of the printed conjecture under
\(f(x)-2\log|x|\to+\infty\). It does not refute the intended centering statement
when \(f\) is assumed to grow faster than every linear function, or more simply
when \(f(x)/|x|\to+\infty\). The proposition records that corrected form.

\section*{Novelty Check}

The run indexes were searched for arXiv:2410.02715 and for phrases involving
free Gibbs measures, barycenter zero, linear tilts, free pressure, and
Blaschke--Santalo. No existing run packet was found. Web searches on
2026-07-03 for exact phrases such as ``free Gibbs measure barycenter zero
\(f+\lambda\)'' and ``free Blaschke-Santalo barycenter zero lambda free Gibbs''
found the source paper but no separate answer.

\section*{References}

\begin{itemize}
\item C.-P. Diez, \emph{A sharp symmetrized free transport-entropy inequality
for the semicircular law}, arXiv:2410.02715.
\item E. B. Saff and V. Totik, \emph{Logarithmic Potentials with External
Fields}, Springer, 1997. Used through the standard one-dimensional equilibrium
existence and uniqueness facts cited in the source.
\item F. Hiai, \emph{Free analog of pressure and its Legendre transform},
Commun. Math. Phys. 255 (2005), 229--252. Used for the free pressure
variational viewpoint cited in the source.
\end{itemize}

\end{document}
