\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newcommand{\BPBp}{\mathrm{BPBp}}
\newcommand{\ot}{\widehat{\otimes}_{\varepsilon}}

\title{Historical strong partial packet: state-norming units}
\author{Run \texttt{fa\_banach\_001}, lane 5}
\date{Archived inside the full packet on 2026-06-19}

\begin{document}
\maketitle

\section*{Historical Status}

This note records the intermediate strong partial result obtained after the
unital \(C(K)\)-subspace packet and before the final all-nonzero-\(E\)
qualitative theorem.  It is superseded by the parent full packet, but remains
the same-modulus refinement.

\section*{Theorem}

\begin{theorem}
Let \(E\) be a Banach space and suppose that there is \(e\in S_E\) such that
\[
 K_e=\{e^\ast\in B_{E^\ast}: e^\ast(e)=1\}
\]
norms \(E\).  Let \(X\) and \(Y\) be Banach spaces.  If \((X,E\ot Y)\) has the
BPBp with function \(\eta\), then \((X,Y)\) has the BPBp with the same function
\(\eta\).
\end{theorem}

\section*{Proof}

The set \(K_e\) is weak-star compact, and the map
\[
 \Gamma:E\to C(K_e),\qquad \Gamma(a)(e^\ast)=e^\ast(a),
\]
is an isometry because \(K_e\) norms \(E\).  Moreover \(\Gamma(e)=1_{K_e}\).
Thus, by injectivity of the injective tensor norm,
\[
 E\ot Y\hookrightarrow C(K_e)\ot Y\subset C(K_e,Y)
\]
isometrically.

Fix \(\varepsilon>0\).  Given \(T\in S_{\mathcal L(X,Y)}\) and \(x_0\in S_X\)
with \(\|Tx_0\|>1-\eta(\varepsilon)\), define \(J(y)=e\otimes y\) and
\(\widetilde T=J\circ T\).  The map \(J:Y\to E\ot Y\) is an isometry.
Applying BPBp for \((X,E\ot Y)\), choose \(\widetilde S\) and \(x_1\in S_X\)
with
\[
 \|\widetilde S\|=\|\widetilde Sx_1\|=1,\qquad
 \|\widetilde S-\widetilde T\|<\varepsilon,\qquad
 \|x_1-x_0\|<\varepsilon .
\]
The continuous \(Y\)-valued function \(\widetilde Sx_1\) on compact \(K_e\)
attains its norm at some \(e_1^\ast\in K_e\).  Let
\[
 S=(e_1^\ast\otimes \mathrm{Id}_Y)\circ \widetilde S.
\]
Then \(\|S\|\leq 1\), and
\[
 \|Sx_1\|=\|(\widetilde Sx_1)(e_1^\ast)\|=1.
\]
Since \(e_1^\ast(e)=1\), evaluation fixes \(J(Y)\), so
\[
 \|S-T\|\leq\|\widetilde S-\widetilde T\|<\varepsilon .
\]
Hence \((X,Y)\) has the BPBp with the same modulus.

\section*{Supersession Note}

The final packet proves qualitative BPBp descent for every nonzero \(E\).  The
argument there evaluates over the whole dual ball \(B_{E^\ast}\) and rotates a
scalar whose modulus is close to one, causing a factor-two modulus loss.  The
state-norming-unit hypothesis removes that loss.

\end{document}
