\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\bwr}{\wr}
\newcommand{\alp}{\alpha}

\title{Literature Status: \(L_p\) Compression of \(\Z \bwr \Z\)}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-23}

\begin{document}
\sloppy
\maketitle

\paragraph{Status.}
\textbf{Literature already answered.} This packet records a later literature
answer to a question in Naor--Peres, \emph{Embeddings of discrete groups and
the speed of random walks}, arXiv:0708.0853.

\paragraph{Source question.}
The source paper asks in Question 7.9, page 21:
\[
\text{Evaluate } \alpha_p^*(\Z \bwr \Z) \text{ for } 1<p<2.
\]
Here \(\alpha_p^*(G)\) denotes the \(L_p\)-compression exponent of the finitely
generated group \(G\) equipped with a word metric.

\paragraph{Supporting answer.}
Naor--Peres, arXiv:0904.4728, gives the exact value. Its abstract and
introduction state
\[
\alpha_p^*(\Z \bwr \Z)=
\max\left\{\frac{p}{2p-1},\frac23\right\}
\qquad (1\le p<\infty).
\]
For the range \(1<p<2\) asked in the source question,
\[
\frac{p}{2p-1}>\frac23,
\]
with equality only at \(p=2\). Hence the answer to Question 7.9 is
\[
\boxed{\alpha_p^*(\Z \bwr \Z)=\frac{p}{2p-1}\quad\text{for }1<p<2.}
\]

\paragraph{Provenance.}
The supporting paper explicitly says that the computation of
\(\alpha_p^*(\Z \bwr \Z)\) answers a question posed in the earlier
Naor--Peres paper. This packet is therefore a literature-status record, not a
new proof or original partial result.

\paragraph{Scope limitations.}
Only Question 7.9 is covered here. The other questions in the source paper's
discussion section, including questions about amenable groups, \(L_1\)
compression, hyperbolic groups, and edge Markov type, are not addressed by this
packet.

\begin{thebibliography}{9}

\bibitem{NP2007}
A. Naor and Y. Peres,
\emph{Embeddings of discrete groups and the speed of random walks},
arXiv:0708.0853.

\bibitem{NP2009}
A. Naor and Y. Peres,
\emph{\(L_p\) compression, traveling salesmen, and stable walks},
arXiv:0904.4728; Duke Math. J. 157 (2011), no. 1, 53--108.

\end{thebibliography}

\end{document}
