\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newcommand{\ellone}{\ell_1}
\newcommand{\czero}{c_0}
\newcommand{\omegaord}{\omega}
\newcommand{\perpann}{\perp}

\title{A Literature-Implied Variant of Remark 13.8 in Argyros--Manoussakis--Pelczar}
\author{run fa\_banach\_001, lane 2}
\date{2026-07-18}

\begin{document}
\maketitle

\paragraph{Status.}
This is a \emph{literature-implied answer to a strengthened variant}, not a full solution of the source problem.  The supporting theorem is Causey's dualization theorem for the Bourgain $\czero$ index.

\paragraph{Source problem.}
Argyros, Manoussakis, and Pelczar ask in Remark 13.8 of \cite{AMP} whether the following is true.  Let $X$ be reflexive and suppose every subspace of $X^*$ has Bourgain $\czero$-index greater than $\omegaord^\xi$.  Must there be a subspace $Y\subset X$ such that every subspace of $X/Y$ has Bourgain $\ellone$-index greater than $\omegaord^\xi$?

\paragraph{Supporting theorem.}
Causey's Theorem 5.2 in \cite{Causey} says, in particular, that if a dual space $W=E^*$ has Bourgain $\czero$-index greater than $\omegaord^\xi$, then any predual $E$ has Bourgain $\ellone$-index greater than $\omegaord^\xi$; see also the quantitative paragraph following that theorem.

\paragraph{Literature-implied variant.}
Let $X$ be reflexive and let $Y\subset X$ be closed.  Put $W=Y^\perp\subset X^*$.  Assume that every quotient of $W$ has Bourgain $\czero$-index greater than $\omegaord^\xi$.  Then every subspace of $X/Y$ has Bourgain $\ellone$-index greater than $\omegaord^\xi$.

\paragraph{Proof.}
Let $Q=X/Y$.  Since $X$ is reflexive, $Q$ is reflexive and $Q^*$ is canonically isometric to $Y^\perp=W$.  Let $Z\subset Q$ be an infinite-dimensional closed subspace.  Its annihilator in $Q^*$ is
\[
  Z^\perp=\{w\in W: w(z)=0\ \text{for all }z\in Z\},
\]
and the usual duality identification gives
\[
  Z^*\cong Q^*/Z^\perp \cong W/Z^\perp .
\]
By the quotient-hereditary hypothesis on $W$, this quotient has Bourgain $\czero$-index greater than $\omegaord^\xi$.  It is a dual space with predual $Z$, so Causey's dualization theorem applies and yields that $Z$ has Bourgain $\ellone$-index greater than $\omegaord^\xi$.  Since $Z\subset Q$ was arbitrary, $Q=X/Y$ has the desired hereditary $\ellone$-index conclusion.

In particular, if every quotient of $X^*$ has Bourgain $\czero$-index greater than $\omegaord^\xi$, the same proof with $Y=0$ gives the desired conclusion for $X$ itself.

\paragraph{Remaining gap for the original question.}
The original hypothesis is hereditary for subspaces of $X^*$, whereas the proof above needs quotient-heredity for an annihilator subspace $Y^\perp$.  A subspace $Z$ of $X/Y$ produces a quotient $Z^*\cong Y^\perp/Z^\perp$, not merely a subspace of $X^*$.  Thus the unresolved core is the stabilization step: find, from the source hypothesis, an annihilator $Y^\perp\subset X^*$ all of whose quotients still have Bourgain $\czero$-index greater than $\omegaord^\xi$.  Causey's subspace/quotient estimates in Theorem 8.1 are relevant, but they do not alone prove this stabilization.

\paragraph{Bounded search note.}
The run indexes contained no prior packet for arXiv:0907.4317 or this final problem.  Local and web searches for the exact problem phrases and for ``dualization of the Bourgain $c_0$ index'' located \cite{Causey}.  No searched source explicitly claimed to resolve Remark 13.8 under the original subspace-hereditary hypothesis.

\begin{thebibliography}{9}
\bibitem{AMP}
S. A. Argyros, A. Manoussakis, and A. M. Pelczar,
\emph{On the hereditary proximity to $\ell_1$},
J. Funct. Anal. 261 (2011), 1145--1203; arXiv:0907.4317.

\bibitem{Causey}
R. M. Causey,
\emph{Proximity to $\ell_p$ and $c_0$ in Banach spaces},
J. Funct. Anal. 269 (2015), 3952--4005; arXiv:1502.05753.
\end{thebibliography}

\end{document}
