\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\F}{\mathcal F}

\begin{document}

\section*{Human Review: separable-dual wording loophole}

\noindent Packet identifier:
\texttt{2509.00722\_separable\_free\_space\_dual\_embedding}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Manually checked.

\noindent Verdict: Rejected as a substantive solution to the intended problem.
This is a wording loophole rather than a mathematical resolution.

\section*{Human Comments}

The proposed solution in \texttt{solution\_packet.pdf} should not be accepted
as a full solution of Problem 3.12 in Smith's paper.  The argument it gives is
mathematically correct as a literal Banach-space observation: if \(Y\) is
separable, then a countable norming family in \(Y^*\) gives an isometric
embedding
\[
  Y \hookrightarrow \ell_\infty=(\ell_1)^*.
\]
Since \(\F(M)\) is separable whenever \(M\) is separable, this gives
\(\F(M)\hookrightarrow(\ell_1)^*\) for every separable metric space \(M\).

However, this cannot be the intended mathematical content of Problem 3.12.
The paper explicitly defines \(X\hookrightarrow Y\) to mean linear isomorphism
to a subspace, so the automatic packet is exploiting a literal reading of the
notation.  But the surrounding context makes that reading vacuous.  Theorem
1.3 constructs countable complete discrete metric spaces \(M\) for which
\(\F(M)\) fails the bounded approximation property and consequently is not
isomorphic to any dual Banach space.  Immediately after related remarks about
complete separable p1u spaces, the author says that G. Lancien suggested
Problem 3.12 as something Theorem 1.3 leaves open.

Under the packet's reading, none of the hypotheses or preceding discussion
matter: every separable Banach space embeds into the dual of the separable
space \(\ell_1\).  Thus the question would have a one-line affirmative answer
for all separable \(M\), independent of p1u, completeness, the Radon--Nikodym
property, approximation properties, or the issue of being isomorphic to a
dual.  This is strong evidence that the intended question involved a stronger
duality requirement, or that the printed problem is missing a qualifier.

Possible intended variants include asking whether \(\F(M)\) is itself
isomorphic to a dual space with separable predual, whether it embeds into a
separable dual in a weak-star meaningful way, or whether some related
complemented or canonical dual structure exists.  The automatic packet does
not address any such substantive variant.

\section*{Short Version}

The \(\ell_\infty=(\ell_1)^*\) embedding is correct, but it makes Problem
3.12 completely trivial for every separable Banach space.  The source context
is about whether certain Lipschitz-free spaces are, or meaningfully sit in,
dual spaces.  Therefore this packet should be treated as a wording observation,
not as a mathematical solution of the intended problem.

\section*{Review Outcome}

Reject this candidate as a successful full solution.  At most, archive it as a
cautionary example: the automatic system found a literal loophole in the
printed wording, but the surrounding paper makes clear that the intended
question is a nontrivial duality question not answered by the universal
\(\ell_\infty\) embedding.

\end{document}
