\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\newtheorem*{question}{Source question}
\newtheorem*{theorem}{Later theorem (Eklund--Lindstr\"om--Mleczko)}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}
\renewcommand{\thesection}{\arabic{section}.}

\title{Literature Status: The Proposed Hyperbolic\
Dirichlet-Spectrum Annulus Is Too Large}
\author{Run \texttt{fa\_banach\_001} --- lane 1}
\date{22 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\textbf{Status: full negative answer implied by later literature.}
For the admissible constant weight $h\equiv1$, the proposed annulus has outer
radius $1/\mu>1$.  A later theorem gives
$r_{\mathcal D}(C_\varphi)=1$, so that annulus cannot be the spectrum.
}}
\end{center}

\section{Original question}

Chalendar, Gallardo-Guti\'errez, and Partington study the classical Dirichlet
space
\[
 \mathcal D=\left\{f\in H(\mathbb D):
 |f(0)|^2+\int_{\mathbb D}|f'(z)|^2\,dA(z)<\infty\right\}
\]
and weighted composition operators $W_{h,\varphi}=hC_\varphi$.
Their final remark after Theorem~3.3 asks the following
question on arXiv PDF page~13~\cite{source}.

\begin{question}
Let $\varphi$ be a hyperbolic automorphism with attractive and repelling
fixed points $a,b\in\partial\mathbb D$, conjugate to
\[
 \psi(z)=\frac{(1+\mu)z+(1-\mu)}{(1-\mu)z+(1+\mu)},
 \qquad 0<\mu<1.
\]
If $h\in\mathcal M(\mathcal D)$ is continuous at $a,b$ and
$W_{h,\varphi}$ is invertible, must
\[
 \sigma(W_{h,\varphi})=
 \left\{z:\min\{|h(a)|,|h(b)|\}\mu\le |z|
 \le\frac{\max\{|h(a)|,|h(b)|\}}{\mu}\right\}?
\]
\end{question}

Theorem~3.3 of the source proves only containment in this annulus.

\section{Decisive later result}

Eklund, Lindstr\"om, and Mleczko subsequently sharpened that bound.  Their
Theorem~5.2 (arXiv PDF page~14) states the following for hyperbolic
automorphisms~\cite{later}.

\begin{theorem}
If $hC_\varphi$ is invertible on $\mathcal D$ and
$h\in A(\mathbb D)$, then
\[
 r_{\mathcal D}(hC_\varphi)=\max\{|h(a)|,|h(b)|\},
\]
and
\[
 \sigma_{\mathcal D}(hC_\varphi)\subseteq
 \left\{\lambda:\min\{|h(a)|,|h(b)|\}\le |\lambda|
 \le\max\{|h(a)|,|h(b)|\}\right\}.
\]
\end{theorem}

The disc-algebra assumption is more than enough for the constant multiplier
used below.

\section{Counterexample to the proposed equality}

Set $h\equiv1$.  Then $h\in\mathcal M(\mathcal D)\cap A(\mathbb D)$, it is
continuous at $a,b$ and bounded away from zero, and $C_\varphi$ is invertible
with inverse $C_{\varphi^{-1}}$.  The later theorem gives
\[
 r_{\mathcal D}(C_\varphi)=1.
\]
If the equality proposed in the source question held, however, then
\[
 \sigma(C_\varphi)=\{z:\mu\le |z|\le1/\mu\},
\]
whose spectral radius is $1/\mu>1$.  This contradicts the later theorem.
Therefore the answer to the source question is \emph{no}.

This is a complete answer to the literal question, but it does not compute
the exact spectrum for general $h$.  The later paper leaves that sharper
problem open when $|h(a)|\ne|h(b)|$.

\section{Provenance}

The implication above is a direct specialization of a separate later
theorem, not a new result.  The 2016 paper describes its contribution as an
improvement of the 2015 hyperbolic estimate and records the resulting sharper
spectral-radius formula; the present note identifies that formula as a
negative answer to the earlier annulus-equality question.

\begin{thebibliography}{9}
\bibitem{source}
I. Chalendar, E. A. Gallardo-Guti\'errez, and J. R. Partington,
\emph{Weighted composition operators on the Dirichlet space: boundedness and
spectral properties}, Math. Ann. \textbf{363} (2015), 1265--1279;
arXiv:1503.01130.

\bibitem{later}
T. Eklund, M. Lindstr\"om, and P. Mleczko,
\emph{Spectral properties of weighted composition operators on the Bloch and
Dirichlet spaces}, Studia Math. \textbf{232} (2016), 95--112;
arXiv:1602.05805, Theorem~5.2.
\end{thebibliography}

\end{document}
