\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Sj}{\mathcal{S}_2}

\begin{document}

\begin{center}
{\Large Literature status: the \(j=2\) Santaló / many-body Blaschke--Santaló case}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:2203.14815}
\end{center}

\section*{Source question}

Kalantzopoulos and Saroglou's paper \emph{On a \(j\)-Santaló Conjecture}
formulates, for \(2\leq j\leq k\), a sharp product-volume conjecture for
tuples of symmetric convex bodies satisfying an \(\mathcal{E}_j\)-polarity
condition.  In the case \(j=2\), this condition is
\[
  \mathcal{S}_2(x_1,\ldots,x_k)
  =\sum_{1\leq i<\ell\leq k}\langle x_i,x_\ell\rangle
  \leq {k\choose 2}
  \qquad (x_i\in K_i),
\]
and the conjectured conclusion is
\[
  \prod_{i=1}^k |K_i|\leq |B_2^n|^k.
\]
The source also records the functional version and notes that for \(j=2\) it
is the Kolesnikov--Werner many-function Blaschke--Santaló conjecture.

\section*{Supporting literature}

Chen, Li, Xi, and Xu's later paper \emph{The many-body
Blaschke--Santaló type inequality via optimal transport}, arXiv:2606.30579,
explicitly identifies the \(j=2\) geometric problem as the many-body
Blaschke--Santaló inequality proposed by Kalantzopoulos and Saroglou.  Its
abstract says that the authors prove the sharp inequality and, using the
geometric--functional equivalence of Kalantzopoulos and Saroglou, establish
the Kolesnikov--Werner functional version.

\section*{The literature answer}

\begin{theorem}[Chen--Li--Xi--Xu, Theorem 1.1]
Let \(n\geq 1\), \(k\geq 2\), and let
\(K_1,\ldots,K_k\subset \R^n\) be origin-symmetric measurable sets of finite
volume.  If
\[
  \mathcal{S}_2(x_1,\ldots,x_k)\leq {k\choose 2}
  \qquad\text{for all }x_i\in K_i,
\]
then
\[
  \prod_{i=1}^k |K_i|\leq |B^n|^k.
\]
The paper also characterizes the equality cases.
\end{theorem}

This proves the \(j=2\) case of the geometric \(j\)-Santaló conjecture from
arXiv:2203.14815, since \(B_j^n=B_2^n\) for \(j=2\) and
\(\mathcal{E}_2=\mathcal{S}_2/{k\choose 2}\).  It is slightly stronger than
the convex-body formulation because the supporting theorem allows measurable
sets of finite volume.

By the geometric--functional equivalence proved in arXiv:2203.14815,
Proposition 4.1, the same supporting paper obtains the functional many-body
Blaschke--Santaló inequality.  This is recorded as Theorem 1.2 of
arXiv:2606.30579 and answers the Kolesnikov--Werner \(j=2\) functional
conjecture.

\section*{Scope and limitations}

This is a literature-status packet, not an original proof from the run.  The
supporting authors explicitly know the relation: they name the inequality as
the one proposed by Kalantzopoulos--Saroglou and cite their
geometric--functional equivalence.

The scope is the \(j=2\) pairwise-interaction case only.  The higher
\(j>2\) conjectures in arXiv:2203.14815 remain outside this packet, except
for the classes already proved in the source paper itself, such as \(j=k\)
and the unconditional cases.

\section*{Verification notes}

Before packaging, the run lightweight indexes were searched for
arXiv:2203.14815, Santaló/Santalo keywords, the title phrase, Kolesnikov--
Werner, many-function Blaschke--Santaló, and related convex-geometric terms.
No existing exact packet for this target was found.

Web search on 2026-07-03 found arXiv:2606.30579, posted June 29, 2026.  The
arXiv page and supporting PDF state Theorems 1.1 and 1.2 and explicitly
identify the source problem and functional consequence.

\section*{Human review recommendation}

Record the \(j=2\) component of arXiv:2203.14815 as already answered by
arXiv:2606.30579.  Keep the higher \(j\)-Santaló conjectures separate.

\begin{thebibliography}{9}

\bibitem{KS}
P. Kalantzopoulos and C. Saroglou,
\emph{On a \(j\)-Santaló Conjecture},
arXiv:2203.14815.

\bibitem{CLXX}
S. Chen, Y. Li, D. Xi, and Z.-F. Xu,
\emph{The many-body Blaschke--Santaló type inequality via optimal transport},
arXiv:2606.30579.

\bibitem{KW}
A. V. Kolesnikov and E. M. Werner,
\emph{Blaschke--Santaló inequality for many functions and geodesic
barycenters of measures},
arXiv:2010.00135.

\end{thebibliography}

\end{document}
