\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Status Note for arXiv:1401.4231}
\author{run fa\_banach\_001, agent\_lane\_17}
\date{2026-06-15}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer}. This is an exact affirmative answer by
a later theorem, identified during this run; it is not an original proof.

\paragraph{Source/open-problem metadata.}
Timur Oikhberg and Eugeniu Spinu, ``Subprojective Banach spaces,''
arXiv:1401.4231, later published in J. Math. Anal. Appl. 424 (2015),
613--635. In the section ``Tensor products of \(C(K)\),'' immediately after
the proof concerning \(C(K)\widehat{\otimes}_\pi \ell_p\), the authors remark
that if \(K\) is scattered and metrizable, they do not know whether
\[
  C(K)\widehat{\otimes}_\pi C(K)
\]
is necessarily subprojective.

\paragraph{Supporting-answer metadata.}
R. M. Causey, ``Subprojectivity of projective tensor products of Banach spaces
of continuous functions,'' arXiv:2012.13440, posted 2020-12-24. Theorem 1
states that for every \(n\in\mathbb N\) and compact Hausdorff spaces
\(K_1,\ldots,K_n\), the projective tensor product
\[
  \widehat{\otimes}_{\pi,i=1}^n C(K_i)
\]
is \(c_0\)-saturated if and only if it is subprojective if and only if each
\(K_i\) is scattered.

\paragraph{Identification.}
Apply Causey's Theorem 1 with \(n=2\) and \(K_1=K_2=K\). If \(K\) is scattered
and metrizable, then it is a compact Hausdorff scattered space in the setting
of the theorem. Therefore \(C(K)\widehat{\otimes}_\pi C(K)\) is
subprojective. Causey's theorem is stronger than the source remark because it
does not require metrizability and treats all finite projective tensor powers.

\paragraph{Provenance limitation.}
The checked Causey source cites Oikhberg--Spinu for background on
subprojectivity, but it does not appear to explicitly say that it is answering
the specific 2014 remark. The packet is therefore classified as a
literature-implied answer rather than a literature-already-answered packet.
The implication itself is direct and answers the whole stated
\(C(K)\widehat{\otimes}_\pi C(K)\) question affirmatively.

\paragraph{Search evidence.}
The run indexes were searched for \texttt{1401.4231}, \texttt{2012.13440},
\texttt{Causey}, \texttt{Galego}, \texttt{Samuel},
\texttt{projective tensor product}, and \texttt{subprojectivity}. No prior
packet for this exact target was found. Web search for the source remark
surfaced arXiv:2012.13440, whose abstract states the relevant stronger
projective tensor product criterion.

\begin{thebibliography}{9}
\bibitem{OS2014}
T. Oikhberg and E. Spinu,
``Subprojective Banach spaces,''
J. Math. Anal. Appl. 424 (2015), 613--635; arXiv:1401.4231.

\bibitem{Causey2020}
R. M. Causey,
``Subprojectivity of projective tensor products of Banach spaces of continuous
functions,'' arXiv:2012.13440, 2020.
\end{thebibliography}

\end{document}
