\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Finite-dimensional subcase of the positive commutator problem}
\author{Literature-implied status note}
\date{2026-06-18}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.

\paragraph{Source problem.}
Madou, Remizov, and Vafadar, \emph{Open problems in one-parameter operator semigroups theory}, arXiv:2410.00416, Problem ``Positive commutator problem'' asks:
if \(E\) is a Banach lattice and \(C:E\to E\) is a positive quasinilpotent compact operator, do there exist positive operators \(A,B:E\to E\) such that
\[
  C=AB-BA
\]
with one of \(A\) and \(B\) compact?

\paragraph{Supporting theorem.}
Drnovsek and Kandic, \emph{Positive operators as commutators of positive operators}, arXiv:1707.00882, Corollary 3.2, prove that a positive matrix \(C\) can be written as a commutator of positive matrices \(A\) and \(B\) if and only if \(C\) is nilpotent. Moreover, their construction can choose \(A\) diagonal and \(B\) permutation-similar to a strictly upper triangular matrix.

\paragraph{Identification.}
Let \(E\) be a finite-dimensional Banach lattice. Then \(E\) is lattice isomorphic to \(\mathbb{R}^n\) with its coordinate order, so positive operators on \(E\) correspond to positive matrices. Every operator on \(E\) is compact. Finally, in finite dimension quasinilpotence is equivalent to nilpotence. Therefore, if \(C:E\to E\) is positive, quasinilpotent, and compact, then \(C\) is a positive nilpotent matrix in lattice coordinates. By Drnovsek--Kandic Corollary 3.2, \(C=AB-BA\) for positive matrices \(A,B\), and since the space is finite-dimensional one of them is automatically compact.

\paragraph{Scope and provenance.}
This answers only the finite-dimensional Banach-lattice subcase of the source problem. The supporting paper predates arXiv:2410.00416 and does not present itself as answering that later problem; the relation is an agent-identified specialization. The general infinite-dimensional compact/quasinilpotent Banach-lattice problem is not settled by this packet.

\paragraph{References.}
\begin{itemize}
\item K. R. Madou, I. Remizov, and R. Vafadar, \emph{Open problems in one-parameter operator semigroups theory}, arXiv:2410.00416.
\item R. Drnovsek and M. Kandic, \emph{Positive operators as commutators of positive operators}, arXiv:1707.00882; Studia Math. 245 (2019), 185--200.
\end{itemize}

\end{document}
