\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status: Abelian WAP Groups}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-23}

\begin{document}
\sloppy
\maketitle

\paragraph{Status.}
\textbf{Literature already answered.} This packet records that a question
from Megrelishvili, \emph{Fragmentability and representations of flows},
arXiv:math/0411112, has a later negative literature answer.

\paragraph{Source question.}
In Section ``Reflexive representations of (semi)groups'' of the source paper
(page 13 of the source PDF), after recalling that the additive group of
\(L_4[0,1]\) is WAP but not unitarily representable, Megrelishvili asks:
\begin{quote}
Is every abelian Hausdorff topological group, for example the additive group
of a Banach space, WAP?
\end{quote}
Here WAP for a topological group means that the universal WAP/semitopological
compactification is an embedding, equivalently that WAP functions induce the
topology; this is the standard reflexive-representability condition for
topological groups.

\paragraph{Supporting answer.}
Ben Yaacov--Berenstein--Ferri,
\emph{Reflexive representability and stable metrics}, arXiv:0901.1003,
explicitly recall the Megrelishvili and Glasner--Megrelishvili problem asking
whether there exists an abelian group that is not reflexively representable.
Their Section 4 then proves:
\[
\text{The additive group of the Banach space \(c_0\) is not reflexively
representable.}
\]
This is Theorem 4.1 on page 8 of the supporting PDF.

\paragraph{Identification.}
The additive group of \(c_0\), with its norm topology, is an abelian Hausdorff
topological group. If it were WAP in the sense of the source question, then its
topology would be induced by WAP functions, hence it would be reflexively
representable. Theorem 4.1 of Ben Yaacov--Berenstein--Ferri says this is
impossible. Thus \(c_0\) gives a negative answer to Megrelishvili's abelian
WAP question.

\paragraph{Provenance and search evidence.}
This is an explicit literature answer, not an original counterexample from the
run: the supporting paper states that it is addressing the abelian
non-reflexively-representable problem and gives \(c_0\) as the example. The
local run indexes were searched for \texttt{0411112}, \texttt{0901.1003},
\texttt{every abelian Hausdorff}, \texttt{c\_0 reflexively representable}, and
nearby WAP/reflexive-representability keywords; no existing durable packet for
this exact source/supporting-paper pair was found.

\paragraph{Scope limitations.}
This packet only records the negative answer to the abelian Hausdorff WAP
question. It does not settle the source paper's other fragmentability,
Asplund-representation, or flow-representation questions.

\begin{thebibliography}{9}

\bibitem{Meg0411112}
M. Megrelishvili,
\emph{Fragmentability and representations of flows},
arXiv:math/0411112.

\bibitem{BBF09011003}
I. Ben Yaacov, A. Berenstein, and S. Ferri,
\emph{Reflexive representability and stable metrics},
arXiv:0901.1003; Math. Z. 267 (2011), 129--138.

\end{thebibliography}

\end{document}
