\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\title{Resistance Conjecture Quoted in arXiv:2509.04155 Answered by arXiv:2602.05477}
\author{Run fa\_banach\_001, agent\_lane\_14}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet:
\[
\texttt{literature\_already\_answered}
\]
for the resistance conjecture as quoted in Riku Anttila, ``An Approach to
Sub-Gaussian Heat Kernel Estimates via Analysis on Metric Spaces'',
arXiv:2509.04155.

\section*{Source Question}

In Section 7, arXiv:2509.04155 discusses the resistance conjecture of
Grigor'yan, Hu, and Lau and states it as Conjecture 4.15. In the notation of
that paper:

\begin{quote}
The strongly local regular Dirichlet form
\((\mathcal E,\mathcal F)\) on \(L^2(X,\mu)\) satisfies the heat kernel
estimates if and only if \((\mathcal E,\mathcal F)\) satisfies both the
Poincare inequality and the upper capacity estimate.
\end{quote}

The surrounding text explains that the conjecture asks whether the cutoff
energy condition in Theorem 6.4 can be replaced by the upper capacity estimate.

\section*{Supporting Answer}

Sylvester Eriksson-Bique, ``On the Resistance Conjecture'',
arXiv:2602.05477, explicitly states in the abstract that it gives an
affirmative answer to the resistance conjecture. Its Theorem 1.1 proves the
equivalence, for metric measure Dirichlet spaces, of:
\begin{enumerate}
\item parabolic Harnack inequality \({\rm PHI}(\beta)\);
\item heat-kernel estimates \({\rm HKE}(\beta)\) together with volume doubling;
\item volume doubling, elliptic Harnack inequality, and a two-sided capacity
bound;
\item volume doubling, Poincare inequality \({\rm PI}(\beta)\), and the
capacity upper bound \({\rm Cap}_2(\beta)\).
\end{enumerate}
The paper further explains that its key step is proving that volume doubling,
Poincare, and upper capacity imply the cutoff Sobolev inequality.

Thus the later paper supplies the advertised replacement of cutoff Sobolev by
upper capacity bounds, in the standard volume-doubling formulation. The
supporting paper also cites arXiv:2509.04155 and describes Anttila's work as
a closely related earlier approach with partial results.

\section*{Scope}

This packet records a literature answer only; it is not a new proof. It does
not settle the sharper question isolated in the existing attempt for
arXiv:2602.05477, namely whether upper capacity plus a separated-ball lower
capacity condition and volume doubling imply the Poincare inequality itself.

\section*{Search Evidence}

Cheap run indexes showed no exact prior packet for arXiv:2509.04155. They did
show an arXiv:2602.05477 attempt noting that the later paper solves the
headline resistance conjecture and leaves a sharper capacity-to-Poincare
question open. Local source inspection matched the Conjecture 4.15 discussion
in arXiv:2509.04155 with the explicit affirmative-answer language and Theorem
1.1 of arXiv:2602.05477.

\begin{thebibliography}{9}
\bibitem{Anttila2509}
Riku Anttila, \emph{An Approach to Sub-Gaussian Heat Kernel Estimates via
Analysis on Metric Spaces}, arXiv:2509.04155.

\bibitem{ErikssonBique2602}
Sylvester Eriksson-Bique, \emph{On the Resistance Conjecture},
arXiv:2602.05477.
\end{thebibliography}

\end{document}
