\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: bidual stability of uniform property (S)}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 10 June 2026

\noindent Status: Manually checked.

\noindent Verdict: Correct.

\section*{Human Comments}

The solution is correct. Once the idea is mentioned, the argument is quite
easy to spot: choose \(X=L_1[0,1]\), so that the underlying measure is
atomless and the positive results of the paper apply to \(X\). Thus \(X\) has
uniform property (S).

The obstruction appears only after passing to the bidual. Since
\[
  X^{**}=(L_\infty[0,1])^*,
\]
one can represent \(L_\infty[0,1]\) as \(C(K)\) for its Stone space \(K\), and
therefore
\[
  X^{**}\simeq C(K)^*=M(K).
\]
Equivalently, by the representation theory of abstract AL-spaces, this space
may be viewed as an \(L_1(\nu)\)-space for a measure \(\nu\) with atoms. In
the Stone representation, the atoms are visible as Dirac measures.

The key point is that once the bidual contains at least two atoms, uniform
property (S) cannot hold. The packet exhibits two Dirac measures
\(\delta_s,\delta_t\) and then chooses
\[
  u=\frac34\delta_s+\frac14\delta_t,\qquad
  v=\frac14\delta_s+\frac34\delta_t.
\]
For sufficiently small perturbations, the two atomic coefficients stay
positive, and the total variation norms of \(u+z\) and \(v+z\) remain equal.
This gives
\[
  U_{X^{**}}(u,v;1/8)=0
  \qquad\text{while}\qquad
  \|u-v\|=1,
\]
so \(X^{**}\) fails uniform property (S).

\section*{Short Version}

The example is \(X=L_1[0,1]\). The space \(X\) has uniform property (S)
because the measure is atomless. But \(X^{**}\) can be represented as a
measure space with atoms, and the presence of two atoms gives a direct
two-coordinate obstruction to uniform property (S).

\section*{Further Question}

The proof uses two atoms. It would be interesting to understand whether the
paper's positive results, or some variant of them, extend to the case where
the representing measure has exactly one atom. The present packet does not
settle that one-atom case; it only shows that two atoms are already enough to
destroy uniform property (S).

\section*{Author Follow-Up}

After reaching out to the authors, they indicated that they had already come
up with the same example for a new version that has not yet been published.
This should therefore be recorded as a correct rediscovery/check rather than
as a novel contribution.

\section*{Review Outcome}

Archive this packet as a correct negative answer to bidual stability of
uniform property (S), with the side note that the one-atom case remains a
natural follow-up question. Also record that the same example was already
known to the authors for a forthcoming version, so this should not be counted
as an independent novel contribution.

\end{document}
