\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Quasi-Greedy Bases in \(\ell_p\), \(0<p<1\), Are Democratic}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 16, 2026}

\begin{document}
\maketitle

\section*{Original Problem}

The source paper is Fernando Albiac, Jose L. Ansorena, and Przemyslaw
Wojtaszczyk, \emph{On certain subspaces of \(\ell_p\) for \(0<p\le 1\) and
their applications to conditional quasi-greedy bases in \(p\)-Banach spaces},
arXiv:1912.08449; later published in \emph{Math. Ann.} 379 (2021),
no. 1--2, 465--502.

After Proposition 4.7, the paper remarks that the known examples of
quasi-greedy bases in \(\ell_p\), \(0<p<1\), are democratic, and asks:
\[
\text{Is every quasi-greedy basis in }\ell_p\text{ for }0<p<1\text{ democratic?}
\]
In the parsed local source this appears at
\texttt{data/parsed/arxiv\_sources/1912.08449/source.tex}, lines 731--735.

\section*{Answer Source}

The direct answer source is Fernando Albiac, Jose L. Ansorena, and
Przemyslaw Wojtaszczyk, \emph{Quasi-greedy bases in the spaces \(\ell_p\)
\((0<p<1)\) are democratic}, arXiv:2004.05206; later published in
\emph{J. Funct. Anal.} 280 (2021), no. 7, 108871.

Its abstract states that the paper proves all quasi-greedy bases in
\(\ell_p\), \(0<p<1\), are democratic and have fundamental function of the
same order as \(m^{1/p}\). The main theorem makes the statement precise:
if \(\mathcal X\) is a quasi-greedy basis of \(\ell_p\), \(0<p<1\), then
\[
\varphi_l[\mathcal X,\ell_p](m)\approx m^{1/p}\approx
\varphi_u[\mathcal X,\ell_p](m),\quad m\in\mathbb N.
\]
In particular, \(\mathcal X\) is democratic. In the parsed local source these
are lines 125 and 266--271 of
\texttt{data/parsed/arxiv\_sources/2004.05206/source.tex}.

The introduction of arXiv:2004.05206 also points back to arXiv:1912.08449 as
the recent paper whose examples motivated the conjectural pattern; see line
264 and the bibliography entry at lines 781--788.

\section*{Corroborating Later Source}

The later paper Fernando Albiac, Jose L. Ansorena, and Glenier Bello,
\emph{Democracy of quasi-greedy bases in \(p\)-Banach spaces with applications
to the efficiency of the TGA in the Hardy spaces \(H_p(\mathbb D^d)\)},
arXiv:2208.09342, cites the 2021 JFA article by title in its abstract and
bibliography. This paper uses the ell\(_p\) result as established literature
while solving a further Hardy-space question raised in that 2021 work.

\section*{Conclusion}

The question from arXiv:1912.08449 is already answered in the later
literature. The answer is positive:
\[
\boxed{\text{Every quasi-greedy basis in }\ell_p,\ 0<p<1,\text{ is democratic.}}
\]

\section*{Search Bounds}

Before making this packet, the run registry, solution index, attempt index,
and proof-gap index were searched for arXiv:1912.08449, arXiv:2004.05206,
arXiv:2208.09342, and quasi-greedy democracy terms. No packet for this exact
source question was found. A nearby existing packet records the distinct
Hardy-space Question 3.8 from arXiv:2004.05206, answered by arXiv:2208.09342;
this packet is only for the earlier \(\ell_p\) question in arXiv:1912.08449.

\section*{Limitations}

This packet records an already-known literature answer, not an original proof
produced by the run. It does not claim any resolution of the separate
\(q\)-envelope question for \(\mathcal L_p\)-spaces that appears later in
arXiv:1912.08449.

\section*{Human Review Recommendation}

Check that the source question on lines 731--735 of arXiv:1912.08449 is the
same \(\ell_p\), \(0<p<1\), democracy question, and that Theorem 1 of
arXiv:2004.05206 gives the stated positive answer.

\begin{thebibliography}{9}
\bibitem{AAW2020}
F. Albiac, J. L. Ansorena, and P. Wojtaszczyk,
\emph{On certain subspaces of \(\ell_p\) for \(0<p\le 1\) and their
applications to conditional quasi-greedy bases in \(p\)-Banach spaces},
Math. Ann. 379 (2021), no. 1--2, 465--502; arXiv:1912.08449.

\bibitem{AAW2021}
F. Albiac, J. L. Ansorena, and P. Wojtaszczyk,
\emph{Quasi-greedy bases in the spaces \(\ell_p\) \((0<p<1)\) are democratic},
J. Funct. Anal. 280 (2021), no. 7, 108871; arXiv:2004.05206.

\bibitem{AAB2022}
F. Albiac, J. L. Ansorena, and G. Bello,
\emph{Democracy of quasi-greedy bases in \(p\)-Banach spaces with applications
to the efficiency of the TGA in the Hardy spaces \(H_p(\mathbb D^d)\)},
arXiv:2208.09342.
\end{thebibliography}

\end{document}
