\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note: CSP Subspaces of Spaces with Long Unconditional Bases}
\author{fa\_banach\_001 / agent\_lane\_08}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Status}

This is a \textbf{literature\_already\_answered} packet.  It records an exact
later-paper answer to an open problem extracted from Talponen's 2008 paper; it
is not claimed as a new proof produced in this run.

\section*{Source Question}

The source is Jarno Talponen, \emph{Lindelof type of generalization of
separability in Banach spaces}, arXiv:0803.3541.  In Section 3, Problem 3.3
(local source TeX line 375), the paper asks:
\[
\text{If } X \text{ admits a long unconditional basis and } Y\subset X
\text{ is a closed subspace with CSP, must } Y \text{ be separable?}
\]

\section*{Supporting Answer}

The supporting paper is Jarno Talponen, \emph{Unconditional and bimonotone
structures in high density Banach spaces}, arXiv:1604.04408.  In the final
remarks (local source TeX lines 895--896), the paper states that if a CSP space
\(Y\) embeds into a Banach space \(X\) with a strong M-basis, then \(Y\) is
separable, and explicitly adds that this settles Problem 3.3 of the 2008
paper.

Thus the answer to the extracted long-unconditional-basis problem is positive
in the later literature.  The supporting author explicitly identifies the
target problem, so this belongs in \texttt{literature\_already\_answered}
rather than as a new result or an agent-identified implication.

\section*{Scope Limits}

This status note concerns only the long-unconditional-basis subspace question.
It does not settle the other questions in arXiv:0803.3541 about finite sums,
the general three-space problem for CSP, CSP together with the Radon--Nikodym
property, or the existence of a CSP space without Corson's property \((C)\).

\section*{References}

\begin{itemize}
\item J. Talponen, \emph{Lindelof type of generalization of separability in
Banach spaces}, arXiv:0803.3541.
\item J. Talponen, \emph{Unconditional and bimonotone structures in high
density Banach spaces}, arXiv:1604.04408.
\end{itemize}

\end{document}
