\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: Very Smooth Operator Converse Counterexample}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Verified.

\noindent Verdict: The proof is correct. The example does show that the converse question after Corollary 14 in Rao's paper is not true in general.

\section*{Human Comments}

The proposed counterexample is elementary and convincing. Let
\[
X=\ell_1,\qquad Y=\mathbb K,
\]
and let \(T\in \mathcal K(\ell_1,\mathbb K)\) be the scalar-valued operator represented by the sequence
\[
a=(a_n)\in \ell_\infty,\qquad
a_1=1,\qquad a_n=1-\frac1n \quad (n\geq 2).
\]
Since the range is one-dimensional, \(T\) is compact. Also
\[
\|T\|=\|a\|_\infty=1.
\]

The operator \(T\) attains its norm only at \(e_1\), up to scalar multiples. Indeed, if \(\|x\|_1=1\) and \(|Tx|=1\), then
\[
1=|Tx|
\leq \sum_{n=1}^\infty a_n |x_n|
\leq \sum_{n=1}^\infty |x_n|
=1.
\]
Since \(a_n<1\) for every \(n\geq 2\), equality forces \(x_n=0\) for all \(n\geq 2\). Hence \(x=\lambda e_1\), with \(|\lambda|=1\). Thus the norm-attaining vector is unique up to scalars.

Moreover,
\[
T(e_1)=1\in \mathbb K,
\]
and every unit vector in the one-dimensional space \(\mathbb K\) is very smooth. Therefore the hypotheses suggested by Rao's converse question are satisfied.

However, \(T\) is not a very smooth point of \(\mathcal K(\ell_1,\mathbb K)\). In fact,
\[
\mathcal K(\ell_1,\mathbb K)=\mathcal L(\ell_1,\mathbb K)=(\ell_1)^*=\ell_\infty
\]
isometrically, and \(T\) corresponds to the sequence \(a\). This sequence is not a smooth point of \(\ell_\infty\). The coordinate functional
\[
\delta_1(b)=b_1
\]
has norm one and satisfies
\[
\delta_1(a)=1.
\]
On the other hand, if \(\mathcal U\) is a free ultrafilter on \(\mathbb N\), then
\[
L_{\mathcal U}(b)=\lim_{\mathcal U} b_n
\]
defines a norm-one functional on \(\ell_\infty\), and since \(a_n\to 1\), one has
\[
L_{\mathcal U}(a)=1.
\]
The two norming functionals are distinct; for instance,
\[
\delta_1(e_1)=1,\qquad L_{\mathcal U}(e_1)=0.
\]
Thus \(a\) is not a smooth point of \(\ell_\infty\). Consequently \(T\) is not even smooth as a point of \(\mathcal K(\ell_1,\mathbb K)\), and therefore it cannot be very smooth.

\section*{Short Version}

The example satisfies the proposed converse hypotheses: \(T\) is compact, it attains its norm at a unique unit vector up to scalars, and \(T(e_1)\) is very smooth in the scalar range. Nevertheless, \(T\) corresponds to a nonsmooth point of \(\ell_\infty\), because the sequence
\[
(1,1/2,2/3,3/4,\ldots)
\]
is normed both by first-coordinate evaluation and by free-ultrafilter limits. Hence \(T\) is not very smooth.

\section*{Review Outcome}

This should be classified as a correct counterexample. It proves that the converse question after Corollary 14 is false in general.

\end{document}
