\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}

\newcommand{\as}{asymptotically symmetric}
\newcommand{\ellp}{\ell_p}
\newcommand{\cnull}{c_0}
\newcommand{\Xkm}{\mathfrak{X}^{1/2}_{0,1}}

\begin{document}

\begin{center}
{\Large Literature status: Problem 2 on asymptotically symmetric spaces}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:math/0508035}
\end{center}

\section*{Source problem}

Junge, Kutzarova, and Odell introduced asymptotically symmetric Banach spaces
and asked:
\begin{quote}
If \(X\) is infinite dimensional and asymptotically symmetric, must \(X\)
contain an asymptotic \(\ellp\) subspace for some \(p\)?
\end{quote}
This is Problem 2 in arXiv:math/0508035.

\section*{Later literature}

Kutzarova and Motakis later wrote \emph{Asymptotically symmetric spaces with
hereditarily non-unique spreading models}, arXiv:1902.10098.  In the
introduction they cite the Junge--Kutzarova--Odell problem in the slightly
stronger form asking whether every \as{} Banach space contains an
infinite-dimensional asymptotic-\(\ellp\) or asymptotic-\(\cnull\) subspace.
They state that they solve this problem in the negative direction by a
variation \(\Xkm\) of the Argyros--Beanland--Motakis space
\(\mathfrak{X}_{0,1}\).

\section*{The literature answer}

\begin{theorem}
Problem 2 of arXiv:math/0508035 has a negative answer.
\end{theorem}

\begin{proof}
Let \(X=\Xkm\) be the space constructed in arXiv:1902.10098.  The conclusion
section of that paper proves that \(X\) is asymptotically symmetric.

The same paper proves that every block subspace of \(X\) admits both a
normalized block sequence generating an \(\ell_1\) spreading model and a
normalized block sequence generating a \(\cnull\) spreading model.  It also
recalls the standard obstruction: if a Banach space is asymptotic-\(\ellp\)
or asymptotic-\(\cnull\), then every spreading model generated by a normalized
weakly null sequence in that space must be equivalent to the corresponding
unit vector basis.

Therefore no infinite-dimensional subspace of \(X\) can be
asymptotic-\(\ellp\) for any \(1\le p<\infty\).  If such a subspace were
asymptotic-\(\ellp\), its weakly-null spreading models would all have to be
\(\ellp\)-type; but the Kutzarova--Motakis hereditary property supplies both
\(\ell_1\) and \(\cnull\) spreading models in every subspace.  The same
argument also rules out asymptotic-\(\cnull\) subspaces.

Thus \(X\) is an infinite-dimensional asymptotically symmetric Banach space
with no asymptotic-\(\ellp\) subspace.  This is exactly a counterexample to
the conclusion asked for in the 2005 problem.
\end{proof}

\section*{Verification notes}

The implication used above is stronger than the original problem requires:
arXiv:1902.10098 rules out asymptotic-\(\ellp\) and asymptotic-\(\cnull\)
subspaces, while the source problem asks only for an asymptotic-\(\ellp\)
subspace.  The supporting paper also proves reflexivity of \(\Xkm\), so there
is no finite-dimensional or nonseparable edge case involved.

This packet is a literature-status identification, not a new proof.  It
answers Problem 2 of arXiv:math/0508035.  It does not address Problem 1 of the
same source paper on infinite-dimensional subspaces of noncommutative
\(L_p(N)\), nor the separate final question in arXiv:1902.10098 about whether
every asymptotically symmetric Banach space admits an \(\ellp\) or \(\cnull\)
spreading model.

The run lightweight indexes were searched for arXiv:0508035, the source title,
``asymptotically symmetric'', ``spreading model'', and the author names before
promotion.  No existing exact packet or attempt for this problem was found.

\section*{Human review recommendation}

Treat Junge--Kutzarova--Odell Problem 2 as already answered negatively by
Kutzarova--Motakis arXiv:1902.10098.

\begin{thebibliography}{9}

\bibitem{JKO}
M. Junge, D. Kutzarova, and E. Odell,
\emph{On asymptotically symmetric Banach spaces},
Studia Math. 173 (2006), no. 3, 203--231; arXiv:math/0508035.

\bibitem{KM}
D. Kutzarova and P. Motakis,
\emph{Asymptotically symmetric spaces with hereditarily non-unique spreading
models},
arXiv:1902.10098.

\end{thebibliography}

\end{document}
