\documentclass[11pt]{amsart}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{microtype}
\usepackage[margin=1.08in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{question}[theorem]{Question}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\ol}{\overline}
\newcommand{\conv}{\operatorname{conv}}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\BS}{\mathrm{BS}}
\newcommand{\wBS}{\mathrm{wBS}}
\newcommand{\treeBS}{\mathrm{tree\text{-}BS}}
\newcommand{\Def}{\mathop{\mathrm{Def}}}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\newcommand{\abs}[1]{\left\lvert #1\right\rvert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\angles}[1]{\left\langle #1\right\rangle}

\setlist[itemize]{leftmargin=2em,itemsep=0.25em,topsep=0.35em}
\setlist[enumerate]{leftmargin=2.2em,itemsep=0.3em,topsep=0.35em}
\emergencystretch=3em

\title[Braga's weak $p$--Banach--Saks problem]{Braga's weak $p$--Banach--Saks problem for weakly sequentially continuous coarse embeddings:\\audit, modulus transfer, and current status}
\author{Research note prepared from the supplied solver output}
\date{June 21, 2026}

\begin{document}
\begin{abstract}
Braga asked whether the weak $p$--Banach--Saks property passes from a Banach space $Y$ to a Banach space $X$ whenever $X$ admits a weakly sequentially continuous coarse Lipschitz embedding into $Y$.  We audit a supplied partial proof and find it correct, apart from a misnumbered citation and two minor omitted justifications.  The proof gives permanence under the stronger hypothesis that $Y$ has the tree-$p$--Banach--Saks property.

We place that argument in a more general modulus-transfer statement.  If $Y$ has tree-$p$--Banach--Saks constant $C$ and $f:X\to Y$ is a weakly sequentially continuous coarse embedding, then, for every scale $r$ with $\rho_f(r)>0$, every normalized weakly null tree in $X$ has a branch satisfying
\[
 \rho_f\!\left(r\norm{\sum_{j=1}^k x_{n_1,\ldots,n_j}}\right)
 \le C\,\omega_f(r)k^{1/p}.
\]
For coarse Lipschitz embeddings this yields tree-$p$--Banach--Saks permanence with an explicit sharp-at-infinity constant.  We also give a direct positive answer under the original weak $p$--Banach--Saks target assumption when the embedding has controlled additive defect.

A literature search through June 21, 2026 found no published proof or counterexample to Braga's question.  The original problem therefore appears to remain open.  The central obstruction is genuine: weak $p$--Banach--Saks controls one weakly null sequence, whereas the nonlinear telescoping argument creates a weakly null tree, and Braga constructed reflexive weak $p$--Banach--Saks spaces with no tree-$q$--Banach--Saks property for any $q>1$.
\end{abstract}
\maketitle

\section{The problem and a result ledger}

For a map $f:X\to Y$ between Banach spaces, write
\begin{align*}
 \omega_f(t)&=\sup\set{\norm{f(x)-f(y)}: \norm{x-y}\le t},\\
 \rho_f(t)&=\inf\set{\norm{f(x)-f(y)}: \norm{x-y}\ge t}.
\end{align*}
The map is a \emph{coarse embedding} if $\omega_f(t)<\infty$ for every $t$ and $\rho_f(t)\to\infty$ as $t\to\infty$.  It is a \emph{coarse Lipschitz embedding} if there are $a,b>0$ and $A\ge0$ such that
\begin{equation}\label{eq:affine-control}
 a\norm{x-y}-A\le \norm{f(x)-f(y)}\le b\norm{x-y}+A
 \qquad(x,y\in X).
\end{equation}
It is \emph{weakly sequentially continuous} if $x_n\rightharpoonup x$ implies $f(x_n)\rightharpoonup f(x)$.

Braga's Problem~8.6 asks the following \cite[Problem~8.6]{BragaJIMJ}.

\begin{question}[Braga]\label{q:Braga}
Let $1<p<\infty$.  Suppose that $Y$ has the weak $p$--Banach--Saks property and that there is a weakly sequentially continuous coarse Lipschitz embedding $f:X\to Y$.  Must $X$ have the weak $p$--Banach--Saks property?
\end{question}

The conclusions established in this note are as follows.
\begin{enumerate}[label=\textup{(\roman*)}]
 \item The supplied partial proof is valid: tree-$p$--Banach--Saks in $Y$ implies tree-$p$--Banach--Saks in $X$ under such an embedding; see Corollary~\ref{cor:CL-tree-transfer}.
 \item The argument admits the scale-sensitive form in Theorem~\ref{thm:modulus-transfer}, valid for arbitrary coarse embeddings and for $1<p\le\infty$.
 \item Under the original weak $p$--Banach--Saks assumption on $Y$, a positive answer follows if the nonlinear embedding is sufficiently additive at suitable large scales; see Theorem~\ref{thm:defect-criterion}.  In particular it follows for embeddings with bounded Cauchy defect; see Corollary~\ref{cor:bounded-defect}.
 \item No complete proof or counterexample to Question~\ref{q:Braga} was located in the literature.  The tree-versus-sequence gap prevents the supplied argument from settling the original question.
\end{enumerate}

\section{Banach--Saks definitions and the tree gap}

\begin{definition}
Let $1<p\le\infty$ and use $k^{1/\infty}=1$.
\begin{enumerate}[label=\textup{(\roman*)}]
 \item A Banach space $Z$ has the \emph{weak $p$--Banach--Saks property with constant $C$} if for every weakly null sequence $(z_n)\subset B_Z$ and every $k\in\N$ there is an infinite $M\subset\N$ such that
 \[
  \norm{\sum_{j=1}^k z_{n_j}}\le Ck^{1/p}
  \quad\text{whenever }n_1<\cdots<n_k\text{ belong to }M.
 \]
 \item A family $(z_s)_{s\in[\N]^{\le k}}$ is a \emph{weakly null tree} if, for every node $s$ of length less than $k$, the successor sequence $(z_{s\frown n})_{n>\max s}$ is weakly null.
 \item The space $Z$ has the \emph{tree-$p$--Banach--Saks property with constant $C$} if every normalized weakly null tree $(z_s)_{s\in[\N]^{\le k}}\subset S_Z$ has a branch $n_1<\cdots<n_k$ for which
 \[
  \norm{\sum_{j=1}^k z_{(n_1,\ldots,n_j)}}\le Ck^{1/p}.
 \]
\end{enumerate}
\end{definition}

The tree property implies the weak property by applying it to the tree whose value at $(n_1,\ldots,n_j)$ is the $n_j$th term of a weakly null sequence \cite[Remark~6.4]{BragaJIMJ}.  The converse is false in a very strong form: for every $1<p<\infty$, Braga constructed a separable reflexive space with the weak (indeed alternating) $p$--Banach--Saks property but without tree-$q$--Banach--Saks for any $1<q<\infty$ \cite[Theorem~7.1]{BragaJIMJ}.  Later work places tree-$p$--Banach--Saks among a hierarchy of asymptotic and Hamming concentration properties and records strict inclusions even among reflexive spaces \cite{FovelleHamming,CauseyFovelleLancien}.

We use the signed form of the tree property.

\begin{proposition}[Braga's signed stabilization]\label{prop:signed-tree}
If $Z$ has tree-$p$--Banach--Saks constant $C$, then for every normalized weakly null tree $(z_s)_{s\in[\N]^{\le k}}$ there is an infinite $M\subset\N$ such that
\[
 \norm{\sum_{j=1}^k \eps_j z_{(n_1,\ldots,n_j)}}\le Ck^{1/p}
\]
for every $(n_1,\ldots,n_k)\in[M]^k$ and every choice $\eps_j\in\{-1,1\}$.
\end{proposition}

This is Proposition~6.3 of \cite{BragaJIMJ}, not Proposition~6.5 as stated in the supplied packet.  It follows by applying the tree property to the finitely many levelwise sign changes and then using Ramsey stabilization.

\begin{lemma}[Convexity of the sign cube]\label{lem:sign-cube}
Let $e_1,\ldots,e_k$ belong to a normed space and let $t_1,\ldots,t_k\in[-1,1]$.  Then
\[
 \sum_{j=1}^k t_j e_j\in
 \conv\set{\sum_{j=1}^k\eps_j e_j:\eps_j\in\{-1,1\}}.
\]
Consequently, if all signed sums on the right have norm at most $K$, then $\norm{\sum_jt_je_j}\le K$.
\end{lemma}

\begin{proof}
Choose independent signs $\eps_j$ with $\mathbb E\eps_j=t_j$.  Then
$\sum_jt_je_j=\mathbb E\sum_j\eps_je_j$, a convex combination of the sign vectors.
\end{proof}

\section{Audit of the supplied partial proof}

The supplied argument has the right architecture.  Given a normalized weakly null tree $(x_s)$ in $X$, set
\[
 u_s=\sum_{t\preceq s}x_t,
 \qquad
 y_s=f(u_s)-f(u_{s^-}).
\]
For a fixed predecessor $s$, one has $u_s+x_{s\frown n}\rightharpoonup u_s$, so weak sequential continuity makes $(y_{s\frown n})_n$ weakly null.  Coarse Lipschitz control makes the increments semi-normalized after a harmless change of scale.  Normalize the increments, use Proposition~\ref{prop:signed-tree}, return to the unequal increment lengths by Lemma~\ref{lem:sign-cube}, and telescope.

There are only three corrections or additions to make.
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item The cited signed result is Braga's Proposition~6.3.
 \item If $y_{s\frown n}\rightharpoonup0$ and $\inf_n\norm{y_{s\frown n}}>0$, then $y_{s\frown n}/\norm{y_{s\frown n}}\rightharpoonup0$: for every $y^*\in Y^*$, the numerator tends to zero while the denominator stays bounded away from zero.
 \item The rescaled map $x\mapsto m^{-1}(f(mx)-f(0))$ is still weakly sequentially continuous because scalar multiplication and translation preserve weak convergence.
\end{enumerate}
No other gap occurs.  The next theorem gives a cleaner proof and retains the full compression and expansion moduli.

\section{A general modulus-transfer theorem}

\begin{theorem}[Modulus transfer]\label{thm:modulus-transfer}
Let $1<p\le\infty$.  Suppose that $Y$ has tree-$p$--Banach--Saks constant $C$ and that $f:X\to Y$ is a weakly sequentially continuous coarse embedding.  Fix $r>0$ such that $\rho_f(r)>0$.  Then every normalized weakly null tree $(x_s)_{s\in[\N]^{\le k}}$ in $X$ has a branch $n_1<\cdots<n_k$ satisfying
\begin{equation}\label{eq:master-transfer}
 \rho_f\!\left(
  r\norm{\sum_{j=1}^k x_{(n_1,\ldots,n_j)}}
 \right)
 \le C\,\omega_f(r)k^{1/p}.
\end{equation}
The convention is $k^{1/\infty}=1$.
\end{theorem}

\begin{proof}
Translation does not change $\rho_f$ or $\omega_f$, so assume $f(0)=0$.  For a nonempty node $s$, let
\[
 u_s=\sum_{t\preceq s}x_t,\qquad u_\emptyset=0,
 \qquad y_s=f(ru_s)-f(ru_{s^-}).
\]
For every fixed predecessor $s$, the sequence $u_s+x_{s\frown n}$ converges weakly to $u_s$.  Hence $(y_{s\frown n})_n$ is weakly null.  Since adjacent partial sums are exactly distance $r$ apart after scaling,
\begin{equation}\label{eq:increment-window}
 0<\rho_f(r)\le\norm{y_s}\le\omega_f(r)<\infty.
\end{equation}
It follows from the lower bound in \eqref{eq:increment-window} that
$e_s=y_s/\norm{y_s}$ is a normalized weakly null tree.

Apply Proposition~\ref{prop:signed-tree} to $(e_s)$.  On the resulting branch put
\[
 t_j=\frac{\norm{y_{(n_1,\ldots,n_j)}}}{\omega_f(r)}\in[0,1].
\]
Lemma~\ref{lem:sign-cube} gives
\begin{align*}
 \norm{\sum_{j=1}^k y_{(n_1,\ldots,n_j)}}
 &=\omega_f(r)\norm{\sum_{j=1}^k t_j e_{(n_1,\ldots,n_j)}}\\
 &\le C\,\omega_f(r)k^{1/p}.
\end{align*}
The sum on the left telescopes to
\[
 f\!\left(r\sum_{j=1}^k x_{(n_1,\ldots,n_j)}\right)-f(0).
\]
The definition of the compression modulus now yields \eqref{eq:master-transfer}.
\end{proof}

The theorem can be read as an inverse-compression estimate.  With the generalized inverse
\[
 \rho_f^{-1,+}(s)=\sup\set{t\ge0:\rho_f(t)\le s},
\]
Equation~\eqref{eq:master-transfer} gives
\begin{equation}\label{eq:inverse-compression}
 \norm{\sum_{j=1}^k x_{(n_1,\ldots,n_j)}}
 \le \frac1r\,\rho_f^{-1,+}\!\left(C\omega_f(r)k^{1/p}\right).
\end{equation}
This is meaningful without any affine hypothesis.

\begin{corollary}[Coarse Lipschitz permanence]\label{cor:CL-tree-transfer}
Let $1<p<\infty$.  Assume that $Y$ has tree-$p$--Banach--Saks constant $C$, and let $f:X\to Y$ be weakly sequentially continuous and satisfy \eqref{eq:affine-control}.  Then $X$ has the tree-$p$--Banach--Saks property.  More precisely, for every $r>A/a$, every normalized weakly null tree in $X$ has a branch with
\begin{equation}\label{eq:CL-constant}
 \norm{\sum_{j=1}^k x_{(n_1,\ldots,n_j)}}
 \le \frac{C(br+A)+A}{ar}\,k^{1/p}.
\end{equation}
Consequently, for every $\eta>0$, $X$ has tree-$p$--Banach--Saks constant at most
\[
 \frac{bC}{a}+\eta.
\]
In particular, $X$ has the weak $p$--Banach--Saks property.
\end{corollary}

\begin{proof}
The affine bounds give $\omega_f(r)\le br+A$ and, directly on the endpoint of the selected branch,
\[
 ar\norm{\sum_jx_{(n_1,\ldots,n_j)}}-A
 \le \norm{f(r\sum_jx_{(n_1,\ldots,n_j)})-f(0)}.
\]
Combine this with the proof of Theorem~\ref{thm:modulus-transfer} and use $k^{1/p}\ge1$.  Letting $r\to\infty$ gives the limiting constant.  Tree-$p$--Banach--Saks implies weak $p$--Banach--Saks.
\end{proof}

In the symmetric notation used in the supplied packet,
\[
 L^{-1}\norm{x-y}-A\le\norm{f(x)-f(y)}\le L\norm{x-y}+A,
\]
Corollary~\ref{cor:CL-tree-transfer} gives constants arbitrarily close to $L^2C$.

\begin{corollary}[Power compression]\label{cor:power-compression}
Under the hypotheses of Theorem~\ref{thm:modulus-transfer}, suppose additionally that
\[
 \rho_f(t)\ge c t^\alpha-d\qquad(t\ge0)
\]
for some $c>0$, $d\ge0$, and $\alpha>0$.  Then, for every $r$ with $\rho_f(r)>0$, the selected branch satisfies
\[
 \norm{\sum_{j=1}^k x_{(n_1,\ldots,n_j)}}
 \le
 \frac{(C\omega_f(r)+d)^{1/\alpha}}{r c^{1/\alpha}}
 k^{1/(\alpha p)}.
\]
Thus, if $\alpha p>1$, the space $X$ has tree-$(\alpha p)$--Banach--Saks.
\end{corollary}

\begin{proof}
Insert the power lower bound in \eqref{eq:master-transfer} and use
$C\omega_f(r)k^{1/p}+d\le(C\omega_f(r)+d)k^{1/p}$.
\end{proof}

\begin{remark}[The endpoint case]
For $p=\infty$, Theorem~\ref{thm:modulus-transfer} gives
\[
 \rho_f\!\left(r\norm{\sum_jx_{(n_1,\ldots,n_j)}}\right)
 \le C\omega_f(r).
\]
Since $\rho_f(t)\to\infty$, the branch sums are uniformly bounded independently of the height.  Hence tree-$\infty$--Banach--Saks passes under weakly sequentially continuous coarse embeddings.  This is the tree formulation of the endpoint phenomenon in Braga's Theorem~6.11; tree-$\infty$ and upper $\ell_\infty$ tree estimates coincide in this setting \cite{BragaJIMJ,FovelleHamming}.
\end{remark}

\section{A direct weak p theorem from additive defect}

The tree proof cannot use weak $p$--Banach--Saks directly because its increments have different predecessors.  There is, however, a complementary route: apply weak $p$--Banach--Saks to the single sequence $f(r x_n)$ and quantify the failure of $f$ to commute with finite sums.

After translating $f$, put $\widetilde f=f-f(0)$.  For $k\in\N$ and $r>0$, define the $k$-term additive defect on the unit ball by
\begin{equation}\label{eq:defect-definition}
 \Def_f(k,r)=
 \sup_{x_1,\ldots,x_k\in B_X}
 \norm{
  \widetilde f\!\left(r\sum_{j=1}^k x_j\right)
  -\sum_{j=1}^k\widetilde f(rx_j)
 }.
\end{equation}

\begin{theorem}[A defect criterion]\label{thm:defect-criterion}
Let $1<p<\infty$.  Suppose that $Y$ has weak $p$--Banach--Saks constant $C$, and let $f:X\to Y$ be weakly sequentially continuous and satisfy \eqref{eq:affine-control}.  Assume that there are $D\ge0$ and scales $r_k\ge1$ such that
\begin{equation}\label{eq:defect-assumption}
 \frac{\Def_f(k,r_k)}{r_k}\le Dk^{1/p}
 \qquad(k\in\N).
\end{equation}
Then $X$ has the weak $p$--Banach--Saks property, with constant at most
\begin{equation}\label{eq:defect-constant}
 \frac{C(b+A)+D+A}{a}.
\end{equation}
\end{theorem}

\begin{proof}
Let $(x_n)\subset B_X$ be weakly null and fix $k$.  Define
\[
 g_k(x)=\frac{\widetilde f(r_kx)}{r_k}.
\]
Then $g_k$ is weakly sequentially continuous, $g_k(0)=0$, and
\[
 \norm{g_k(x_n)}\le b+\frac{A}{r_k}\le b+A.
\]
The sequence $(g_k(x_n))$ is weakly null in $Y$.  The weak $p$--Banach--Saks property of $Y$ supplies an infinite $M\subset\N$ such that
\begin{equation}\label{eq:image-sequence-bound}
 \norm{\sum_{j=1}^k g_k(x_{n_j})}
 \le C(b+A)k^{1/p}
 \qquad(n_1<\cdots<n_k\text{ in }M).
\end{equation}
For such indices, \eqref{eq:defect-assumption} and \eqref{eq:image-sequence-bound} imply
\[
 \norm{g_k(\sum_{j=1}^k x_{n_j})}
 \le \bigl(C(b+A)+D\bigr)k^{1/p}.
\]
The lower affine estimate for $g_k$ is
\[
 a\norm{x-y}-\frac{A}{r_k}
 \le\norm{g_k(x)-g_k(y)}.
\]
Taking $x=\sum_jx_{n_j}$ and $y=0$, and using $A/r_k\le A k^{1/p}$, gives \eqref{eq:defect-constant}.
\end{proof}

A simple concrete hypothesis implies the defect condition.

\begin{corollary}[Bounded Cauchy defect]\label{cor:bounded-defect}
Under the hypotheses on $p,Y$, and $f$ in Theorem~\ref{thm:defect-criterion}, assume
\begin{equation}\label{eq:cauchy-defect}
 D_0:=\sup_{u,v\in X}
 \norm{f(u+v)-f(u)-f(v)+f(0)}<\infty.
\end{equation}
Then $X$ has the weak $p$--Banach--Saks property.
\end{corollary}

\begin{proof}
An induction gives $\Def_f(k,r)\le(k-1)D_0$ for every $k$ and $r$.  Taking $r_k=k$ yields
\[
 \frac{\Def_f(k,r_k)}{r_k}\le D_0\le D_0k^{1/p},
\]
so Theorem~\ref{thm:defect-criterion} applies.
\end{proof}

A genuinely asymptotic version is also enough.  Define the local binary defect
\[
 \delta_f(R)=\sup_{\norm{u},\norm{v}\le R}
 \norm{f(u+v)-f(u)-f(v)+f(0)}.
\]

\begin{corollary}[Sublinear additive defect]\label{cor:sublinear-defect}
Under the hypotheses on $p,Y$, and $f$ in Theorem~\ref{thm:defect-criterion}, suppose
\[
 \lim_{R\to\infty}\frac{\delta_f(R)}{R}=0.
\]
Then $X$ has the weak $p$--Banach--Saks property.
\end{corollary}

\begin{proof}
For $x_1,\ldots,x_k\in B_X$, iterative addition at scale $r$ only evaluates the binary defect on vectors of norm at most $kr$.  Hence
\[
 \Def_f(k,r)\le(k-1)\delta_f(kr).
\]
For each $k\ge2$, choose $R_k\ge k$ so large that
\[
 \frac{\delta_f(R_k)}{R_k}\le\frac{k^{1/p}}{k(k-1)},
\]
and put $r_k=R_k/k\ge1$.  Then
\[
 \frac{\Def_f(k,r_k)}{r_k}
 \le k(k-1)\frac{\delta_f(R_k)}{R_k}
 \le k^{1/p}.
\]
Take $r_1=1$ and apply Theorem~\ref{thm:defect-criterion}.
\end{proof}

\begin{remark}
Condition \eqref{eq:cauchy-defect} says that the translated map $\widetilde f$ is a quasi-homomorphism of the additive Banach groups; by classical Hyers--Ulam stability, such maps are close to additive maps under mild regularity.  Theorem~\ref{thm:defect-criterion} and Corollary~\ref{cor:sublinear-defect} are more flexible: they only ask for finite-sum additivity after division by scales that may depend on $k$.  Thus they isolate a precise analytic quantity whose control would settle Question~\ref{q:Braga} for a given embedding.
\end{remark}

\section{Why the original argument stops at trees}

Let $(x_s)$ be a weakly null tree in $X$ and define increments
\begin{equation}\label{eq:increment-tree-again}
 y_s=f\!\left(r\sum_{t\preceq s}x_t\right)
      -f\!\left(r\sum_{t\prec s}x_t\right).
\end{equation}
Weak sequential continuity says that the successors of each fixed node form a weakly null sequence.  It does \emph{not} say that an enumeration of all $y_s$ is weakly null: the predecessor changes while one enumerates the tree.  Weak $p$--Banach--Saks can be applied separately at each node, but those local subsequences need not produce one branch on which the sum of increments is small.

Several standard-looking reductions therefore fail at exactly the same point.
\begin{itemize}
 \item Enumerating tree nodes loses weak nullity because the base point of the increment moves.
 \item Applying weak $p$--Banach--Saks to the sequence $f(rx_n)-f(0)$ controls $\sum_j f(rx_{n_j})$, whereas coarse lower bounds concern $f(r\sum_jx_{n_j})$; their difference is the additive defect in \eqref{eq:defect-definition}.
 \item Hamming-cube or Hamming-graph averaging requires a concentration property stronger than weak $p$--Banach--Saks.  Tree-$p$--Banach--Saks yields such concentration in reflexive or quasi-reflexive settings, but weak $p$ alone does not currently do so \cite{FovelleHamming}.
 \item Passing to ultrapowers turns the levels of a weakly null tree into an asymptotic sequence, but weak $p$--Banach--Saks is not known to have the required ultrapower stability; tree properties are designed precisely to retain this asymptotic information.
\end{itemize}

The bad-tree example in Braga's Theorem~7.1 shows that this is not a cosmetic distinction.  Any complete positive proof must exploit the additional ``gradient'' or cocycle relations enjoyed by \eqref{eq:increment-tree-again}, rather than merely treating it as an arbitrary weakly null tree.  Conversely, a counterexample should combine a weak $p$--Banach--Saks target having bad weakly null trees with a weakly sequentially continuous coarse Lipschitz embedding whose increment tree realizes that bad behavior.

\section{Counterexample routes checked}

This section records the most concrete routes examined, both to delimit the result and to make the remaining task reproducible.

\subsection*{The Kalton--Peck source candidate}
The reflexive Kalton--Peck space $Z_p$ fails the weak $p$--Banach--Saks property.  Causey, Fovelle, and Lancien also show that $Z_p$ fails the Hamming concentration properties indexed by $p$ \cite[Propositions~5.6--5.7]{CauseyFovelleLancien}.  Hence $Z_p$ cannot coarse Lipschitz embed into targets carrying the corresponding tree/Hamming concentration.  This does not exclude a weak $p$--Banach--Saks target with bad tree structure, so $Z_p$ remains a natural possible source for a counterexample; no suitable weakly sequentially continuous embedding was found.

\subsection*{Braga's Baire-sum target candidate}
The well-founded-tree construction in \cite[Theorem~7.1]{BragaJIMJ} gives a separable reflexive target $Y_p$ with weak $p$--Banach--Saks but with arbitrarily bad finite weakly null trees.  It is therefore a natural target candidate.  A counterexample would follow, for example, from a weakly sequentially continuous coarse Lipschitz embedding of $\ell_q$ into $Y_p$ for some $1<q<p$, since the unit vector basis shows that $\ell_q$ fails weak $p$--Banach--Saks.  Natural support-sorting and branch-selection maps are not stable under changes in early coordinates and no coarse Lipschitz, weakly sequentially continuous construction was obtained.

\subsection*{Averaging and cube identities}
The increment tree is a discrete gradient: endpoint values are independent of the order in which coordinates are added, and increments satisfy square-cocycle identities.  Averaging over permutations or over finite blocks makes certain convex combinations of endpoint images small, using weak $p$--Banach--Saks locally.  Coarse lower estimates, however, apply to individual endpoints and do not pass from a small convex average to a small member without additional geometry of $Y$.  This route therefore does not close the gap under the present hypothesis.

These failures are not counterexamples to the desired statement.  They identify the two plausible fronts for further work: prove a branch estimate for gradient trees in every weak $p$--Banach--Saks space, or construct a WSC coarse Lipschitz map into a bad-tree weak $p$ target.

\section{Literature status as of June 21, 2026}

The source article appeared in the \emph{Journal of the Institute of Mathematics of Jussieu} in 2021 and states Question~\ref{q:Braga} explicitly \cite{BragaJIMJ}.  Searches were made for the exact problem number, the exact weak-$p$ phrase, combinations with ``weakly sequentially continuous'' and ``coarse Lipschitz'', and forward citations of the source.  The later papers most closely connected to the problem develop tree-$p$--Banach--Saks and Hamming concentration properties \cite{FovelleHamming}, study the strict hierarchy of asymptotic properties and note that $Z_p$ fails weak $p$--Banach--Saks \cite{CauseyFovelleLancien}, and construct concentration examples beyond asymptotic smoothness \cite{FovelleSmoothness}.  A 2025 monograph surveys the current nonlinear/asymptotic geometry program broadly \cite{BaudierLancienBook}.

No located paper states a proof or a counterexample to Question~\ref{q:Braga}, and no located later source claims that Problem~8.6 has been resolved.  On that evidence, the problem appears open.  This is necessarily a literature-search conclusion rather than a proof of nonexistence: an unpublished or differently phrased result could have been missed.

\section{Conclusion}

The supplied partial result is correct and can be sharpened to the exact modulus estimate \eqref{eq:master-transfer}.  In particular, tree-$p$--Banach--Saks is stable under weakly sequentially continuous coarse Lipschitz embeddings, with constants governed by the asymptotic slope ratio of the embedding.  The original weak-$p$ question is also positive for maps with controlled finite-sum defect.

The unresolved core is now quite narrow.  Weak $p$--Banach--Saks must somehow control the special gradient trees generated by a single weakly sequentially continuous coarse Lipschitz map, even though it cannot control arbitrary weakly null trees.  Alternatively, those gradient relations must be realized inside one of the known weak-$p$, bad-tree spaces to produce a counterexample.

\begin{thebibliography}{99}

\bibitem{BaudierLancienBook}
F.~P. Baudier and G. Lancien,
\emph{Asymptotic and nonlinear geometries of Banach spaces and their interactions},
arXiv:2512.00817, 2025.

\bibitem{Beauzamy}
B. Beauzamy,
Banach--Saks properties and spreading models,
\emph{Math. Scand.} \textbf{44} (1979), no.~2, 357--384.

\bibitem{BragaWSC}
B. de Mendon\c{c}a Braga,
Nonlinear weakly sequentially continuous embeddings between Banach spaces,
\emph{Int. Math. Res. Not. IMRN} (2020), no.~18, 5506--5533.

\bibitem{BragaJIMJ}
B. de Mendon\c{c}a Braga,
On asymptotic uniform smoothness and nonlinear geometry of Banach spaces,
\emph{J. Inst. Math. Jussieu} \textbf{20} (2021), no.~1, 65--102;
arXiv:1808.03254.

\bibitem{CauseyFovelleLancien}
R.~M. Causey, A. Fovelle, and G. Lancien,
Asymptotic smoothness in Banach spaces, three-space properties and coarse Lipschitz geometry,
arXiv:2110.06710, version 2, 2022.

\bibitem{FovelleHamming}
A. Fovelle,
Hamming graphs and concentration properties in Banach spaces,
arXiv:2106.04297, version 3, 2023.

\bibitem{FovelleSmoothness}
A. Fovelle,
Asymptotic smoothness, concentration properties in Banach spaces and applications,
arXiv:2311.15900, version 2, 2024.

\end{thebibliography}

\end{document}
