\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{enumitem}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\lip}{\operatorname{lip}}
\newcommand{\diam}{\operatorname{diam}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\R}{\mathbb R}
\newcommand{\F}{\mathcal F}
\newcommand{\eps}{\varepsilon}

\title{A Local-Slope ACUG Transfer Theorem for the Graph Embedding Question}
\author{Agent lane 19}
\date{June 20, 2026}

\begin{document}
\maketitle

\section*{Source Question}

The source paper is M. Jung, C. Petitjean, A. Prochazka, A. Quilis,
\emph{Affine Approximation in Finite Nagata Dimension and Applications to
Lipschitz-free spaces}, arXiv:2606.11723.
Question 1 on page 34 asks:
\begin{quote}
Let \(M\) be a compact metric space admitting a superreflexive ACUG structure.
Does \(M\) admit a bi-Lipschitz embedding into a compact quasiconvex metric
space that also carries a superreflexive ACUG structure?
\end{quote}

The same paper constructs, for every metric space \(M\) and every
\(\eps>0\), a graph space \(G_\eps(M)\) into which \(M\) embeds isometrically
and which is compact when \(M\) is compact and \((1+\eps)\)-quasiconvex.
The issue is whether ACUG structure transfers to \(G_\eps(M)\).

\section*{Proof Intuition}

An ACUG structure controls approximants along rectifiable curves already
present in \(M\).  The graph \(G_\eps(M)\), however, adds many new intervals
\([x,y]\) between points of \(M\).  On a short new edge, the derivative of any
extension must at least see the secant quotient
\[
   \frac{|g(x)-g(y)|}{d(x,y)}.
\]
Thus ordinary upper-gradient control on \(M\) is not enough by itself: it may
say nothing about secants between nearby points not joined by curves inside
\(M\).

The following theorem proves that this is the only obstruction for the graph
method.  If the ACUG approximants also come with a linear continuous majorant
for small secants, then one extends approximants over the new graph edges,
uses the secant majorant on short edges, and uses an ordinary one-dimensional
derivative on long edges.  The resulting majorant is continuous on the graph
and remains superreflexive because only finite Hilbert sums of the original
superreflexive model are added.

\begin{definition}[local-slope ACUG]
Let \(M\) be compact and \(X\) a Banach space.  We say that \(M\) has a
local-slope ACUG \(X\)-structure if there is \(C_0\geq 1\) such that for every
\(\eta>0\) there are a linear subspace \(H_\eta\subset \Lip(M)\) and a linear
map
\[
   \Lambda_\eta:H_\eta\longrightarrow C(M,X^*)
\]
with the following properties.
\begin{enumerate}[label=(\roman*)]
\item For every \(f\in \Lip(M)\) with \(\Lip(f)\leq 1\), there is
      \(g\in H_\eta\) such that
      \[
        \Lip(g)\le C_0,\qquad \|f-g\|_\infty\le \eta,\qquad
        \|\Lambda_\eta g\|_\infty\le C_0 .
      \]
\item For every \(g\in H_\eta\), the function
      \(x\mapsto \|\Lambda_\eta g(x)\|\) is an upper gradient of \(g\) on
      \(M\).
\item For every \(g\in H_\eta\) and all \(x,y\in M\) with
      \(0<d(x,y)\le \eta\),
      \[
        \frac{|g(x)-g(y)|}{d(x,y)}
        \le
        \max\{\|\Lambda_\eta g(x)\|,\|\Lambda_\eta g(y)\|\}.
      \]
\end{enumerate}
\end{definition}

\begin{theorem}
Let \(M\) be a compact metric space with a local-slope ACUG \(X\)-structure,
where \(X\) is superreflexive.  Then for every \(\eps>0\), the graph space
\(G_\eps(M)\) of Jung--Petitjean--Prochazka--Quilis admits an ACUG structure
modeled on a superreflexive Banach space.  Consequently \(M\) embeds
isometrically into a compact \((1+\eps)\)-quasiconvex metric space carrying a
superreflexive ACUG structure.
\end{theorem}

\begin{proof}
Fix \(\eps>0\), and let \(G=G_\eps(M)\).  By Proposition 5.1 of the source
paper, \(G\) is compact, \((1+\eps)\)-quasiconvex, and contains an isometric
copy of \(M\).

It remains to prove that \(G\) has an ACUG structure.  Let
\(\alpha>0\) be an approximation tolerance.  Choose
\(\eta>0\) so small that \((2C_0+4)\eta<\alpha\), and take
\((H,\Lambda)=(H_\eta,\Lambda_\eta)\) from the local-slope ACUG structure of
\(M\).  We construct a subspace \(\widetilde H\subset\Lip(G)\) and a linear
operator
\[
   \Psi:\widetilde H\longrightarrow C(G,Y^*)
       \quad\text{where}\quad
   Y^*=(X^*\oplus X^*\oplus \R)_2 .
\]
The predual model \(Y=(X\oplus X\oplus\R)_2\) is superreflexive because
finite Hilbert sums preserve superreflexivity.

The elements of \(\widetilde H\) are functions \(u\in\Lip(G)\) satisfying the
following linear conditions.  First \(u|_M\in H\).  On each edge
\([x,y]\subset G\setminus M\) with \(d(x,y)\le \eta\), \(u\) is the fixed
linear smoothing of the endpoint data \(u(x),u(y)\): it is constant in small
endpoint collars, is \(C^1\) on the edge interior, and
\[
   |u'(p)|\le 4\,\frac{|u(x)-u(y)|}{d(x,y)}
   \quad(p\in (x,y)).
\]
The smoothing is chosen once and for all.  Its derivative is supported in the
middle half of the edge.  On each edge with \(d(x,y)>\eta\), \(u\) is \(C^1\)
on the edge interior and is constant on endpoint collars of length \(\eta/4\).
These requirements define a linear subspace.

For \(h=u|_M\), define \(\Psi u\) as follows.  On \(M\), set
\[
   \Psi u(x)=(4\Lambda h(x),\,4\Lambda h(x),\,0).
\]
On a short edge \([x,y]\), set the third coordinate to \(0\).  The first two
coordinates are a fixed continuous interpolation which equals
\((4\Lambda h(x),4\Lambda h(x))\) near \(x\), equals
\((4\Lambda h(x),4\Lambda h(y))\) on the middle half of the edge, and equals
\((4\Lambda h(y),4\Lambda h(y))\) near \(y\).  On a long edge, use the same
endpoint interpolation in the first two coordinates and put the actual
one-dimensional derivative \(u'\) in the third coordinate.  The endpoint
collars make \(u'\to0\) at vertices.  Since \(\Lambda h\) is continuous on
compact \(M\), the resulting \(\Psi u\) is continuous on \(G\).  The definition
is linear in \(u\).

We next check upper-gradient domination.  On portions of curves lying in
\(M\), the norm of \(\Psi u\) dominates
\(\|\Lambda h\|\), hence dominates variation by the local-slope ACUG
hypothesis.  On a long edge, the third coordinate is \(u'\), so the norm of
\(\Psi u\) dominates the one-dimensional metric derivative of \(u\).  On a
short edge, \(u'\) is supported where
\[
   \Psi u=(4\Lambda h(x),4\Lambda h(y),0),
\]
and therefore
\[
   \|\Psi u\|
   \ge 4\max\{\|\Lambda h(x)\|,\|\Lambda h(y)\|\}
   \ge 4\,\frac{|h(x)-h(y)|}{d(x,y)}
   \ge |u'|.
\]
Thus the pointwise local Lipschitz constant of \(u\) on \(G\) is bounded by
\(\|\Psi u\|\).  By the standard local-Lipschitz-constant upper-gradient
lemma used in the source paper, \(\|\Psi u\|\) is an upper gradient of \(u\).

It remains to verify approximation.  Let \(F\in\Lip(G)\) with \(\Lip(F)\le1\).
Choose \(h\in H\) such that \(\Lip(h)\le C_0\),
\(\|F|_M-h\|_\infty\le\eta\), and
\(\|\Lambda h\|_\infty\le C_0\).  Extend \(h\) to a function
\(\widetilde h\in\widetilde H\) as follows.

On each short edge \([x,y]\) with \(d(x,y)\le\eta\), use the fixed smoothing of
the endpoint values \(h(x),h(y)\).  Then every point of the edge is within
\(\eta/2\) of an endpoint, and the preceding derivative bound gives
\[
   |\widetilde h(p)-F(p)|\le (2C_0+2)\eta .
\]
On each long edge, keep \(\widetilde h=h(x)\) and \(\widetilde h=h(y)\) on
the endpoint collars, choose a partition of the middle with mesh between
\(\eta/4\) and \(\eta/2\), prescribe the values of \(F\) at the partition
points, and smooth linearly between consecutive values.  Exactly as in the
proof of Proposition 5.1's purely unrectifiable case in the source paper, this
gives
\[
   \|\widetilde h-F\|_\infty\le 4\eta,\qquad
   \Lip(\widetilde h)\le 8+2C_0 .
\]
Increasing the structural constant once, independent of \(\alpha\), we have
\[
   \Lip(\widetilde h)\le C',\qquad
   \|\Psi\widetilde h\|_\infty\le C',\qquad
   \|\widetilde h-F\|_\infty\le \alpha .
\]
This is precisely an ACUG \(Y\)-structure on \(G\).
\end{proof}

\section*{Verification and Scope}

The theorem is a partial answer to the source question.  It proves the graph
embedding conclusion under a stronger hypothesis than ordinary ACUG.  The
strengthening is not cosmetic: it controls the small secants that become
derivatives on the new edges of \(G_\eps(M)\).

The full source question would follow if every compact superreflexive ACUG
space admitted this local-slope upgrade, perhaps after changing the
approximating subspaces.  No proof of that upgrade is claimed here.

\section*{Novelty Check}

Local repository indexes contained only one previous attempt for arXiv:2606.11723,
which triaged the broad ACUG embedding question and did not promote a result.
Web searches on June 20, 2026 for exact ACUG embedding phrases found the source
paper arXiv:2606.11723 and the background paper Aliaga--Pernecka--Quero
arXiv:2411.15107, but no later answer to Question 1.

\section*{References}

\begin{itemize}
\item M. Jung, C. Petitjean, A. Prochazka, A. Quilis,
\emph{Affine Approximation in Finite Nagata Dimension and Applications to
Lipschitz-free spaces}, arXiv:2606.11723.
\item R. J. Aliaga, E. Pernecka, A. Quero,
\emph{Pelczynski's property (V*) in Lipschitz-free spaces}, arXiv:2411.15107.
\end{itemize}

\end{document}
