\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathrsfs}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}

\title{Literature status: Schlumprecht's scalar-plus-compact question}
\author{agent\_lane\_16}
\date{Run fa\_banach\_001}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet, not an original proof.  It records
that Question Q1 from Th. Schlumprecht, \emph{How many operators do there exist
on a Banach space?}, arXiv:math/0208055, is answered by S. A. Argyros and
R. G. Haydon, \emph{A hereditarily indecomposable $\mathscr L_\infty$-space
that solves the scalar-plus-compact problem}, arXiv:0903.3921.

\section*{Source question}

In item (Q1) of the introduction of arXiv:math/0208055, Schlumprecht asks:

\begin{quote}
Assume $X$ is an infinite dimensional Banach space. Does there exist a linear
bounded operator $T$ on $X$ which is not of the form
$T=\lambda I+C$, where $\lambda$ is a scalar and $C$ is a compact operator?
\end{quote}

The same introduction explains that a negative answer would be a Banach space
on which every operator is a scalar multiple of the identity plus a compact
operator.

\section*{Supporting answer}

Argyros and Haydon's arXiv:0903.3921 is explicitly titled as solving the
scalar-plus-compact problem.  Its abstract states that they construct a
hereditarily indecomposable Banach space with dual isomorphic to $\ell_1$ and
that every bounded linear operator on this space is expressible as
$\lambda I+K$, with $K$ compact.

The introduction says that the paper solves the scalar-plus-compact problem.
The final theorem of the section titled \emph{Operators} states: if $T$ is a
bounded linear operator on the constructed space $\mathfrak X_K$, then there is
a scalar $\lambda$ such that $T-\lambda I$ is compact.

Therefore Schlumprecht's Q1 has a negative answer in the later literature.

\section*{Scope}

This packet does not claim any answer to Schlumprecht's Q2/Q3 subspace version,
Q4 Class 1/Class 2 dichotomy, Q5 partial-unconditionality question, or the
remark asking for an elementary proof that a Class 1 space contains an
unconditional basic sequence.  Those are separate targets.

\end{document}
