\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Theorem}

\title{Literature Status for arXiv:0404401 Final Remark (A)}
\author{FA/Banach run packet}
\date{June 16, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{Result type:} literature already answered.

\textbf{Source question:} Piotr W. Nowak, \emph{Coarse embeddings of metric
spaces into Banach spaces}, arXiv:math/0404401, final remark (A).

\textbf{Supporting answer:} Manor Mendel and Assaf Naor, \emph{Metric cotype},
arXiv:math/0506201.

\section*{Source Question}

Nowak proves that \(L_p(\mu)\) admits a coarse embedding into Hilbert space for
\(0<p<2\). In final remark (A), after recalling the Aharoni--Maurey--Mityagin
uniform non-embedding theorem for \(L_p\), \(p>2\), he asks whether the same
phenomenon has a coarse-uniform analogue:
\[
\text{Does } L_p(\mu) \text{ admit a coarse uniform embedding into Hilbert
space if } p>2?
\]

\section*{Supporting Literature}

Mendel--Naor introduce metric cotype and prove that, for Banach spaces, it
coincides with classical Rademacher cotype. Their Theorem 1.6 states that if
\(X\) has nontrivial type and \(Y\) coarsely embeds into \(X\), then
\(q_Y\le q_X\). In particular,
\[
L_p \text{ embeds coarsely into } L_q
\quad\Longleftrightarrow\quad
p\le q \text{ or } q\le p\le 2 .
\]
The later corollary in the same paper gives the corresponding statement for
both uniform and coarse embeddings.

Taking \(q=2\) gives a negative answer for \(p>2\): the conditions
\(p\le 2\) and \(2\le p\le 2\) both fail. Thus \(L_p\) does not coarsely embed
into Hilbert space for \(p>2\). Since a coarse-uniform embedding is stronger
than a coarse embedding, Nowak's coarse-uniform question has a negative answer
in this standard infinite-dimensional \(L_p\) setting.

\section*{Formal Statement}

\begin{theorem}
Final remark (A) of Nowak, arXiv:math/0404401, is answered negatively in the
later literature for the standard infinite-dimensional \(L_p\) spaces. For
\(p>2\), \(L_p\) does not admit a coarse embedding, hence does not admit a
coarse-uniform embedding, into a Hilbert space.
\end{theorem}

\begin{proof}
Apply Mendel--Naor's coarse embedding classification with \(q=2\). For
\(p>2\), neither \(p\le 2\) nor \(2\le p\le 2\) holds, so their theorem rules
out a coarse embedding \(L_p\to L_2\). A Hilbert target is an \(L_2\)-space up
to linear isometry. Therefore \(L_p\), \(p>2\), does not coarsely embed into
Hilbert space. Any coarse-uniform embedding would in particular be a coarse
embedding, so it is also impossible.
\end{proof}

\section*{Scope and Caveat}

The source writes \(L_p(\mu)\). The supporting theorem is stated for the
standard \(L_p\)-scale and covers the intended infinite-dimensional examples,
including \(L_p[0,1]\) and \(\ell_p\). If \(L_p(\mu)\) is read literally to
include finite-dimensional measure spaces, those finite-dimensional cases
embed into Hilbert space after changing constants and are a trivial exception
outside the intended question.

This packet records a known literature answer rather than a new proof. The
supporting paper explicitly notes that Johnson--Randrianarivony had already
resolved the \(p>2\) Hilbert case negatively and then proves the stronger
classification above.

\section*{Verification}

Stored files:
\[
\texttt{source\_paper.pdf},\qquad
\texttt{supporting\_paper\_0506201.pdf}.
\]
The source question appears in the parsed TeX
\[
\texttt{data/parsed/arxiv\_sources/0404401/source.tex}
\]
around final remark (A). The supporting classification appears in
\[
\texttt{data/parsed/arxiv\_sources/0506201/source.tex}
\]
as Theorem \texttt{thm:coarse} and the later corollary proving that \(L_p\)
embeds uniformly or coarsely into \(L_q\) iff \(p\le q\) or \(q\le p\le 2\).

Cheap-index search before packaging found no prior exact packet for
arXiv:0404401 or this \(L_p\), \(p>2\), Hilbert coarse-embedding question.

\begin{thebibliography}{9}

\bibitem{Nowak2004}
P. W. Nowak,
\emph{Coarse embeddings of metric spaces into Banach spaces},
arXiv:math/0404401.
\url{https://arxiv.org/abs/math/0404401}

\bibitem{MendelNaor2005}
M. Mendel and A. Naor,
\emph{Metric cotype},
arXiv:math/0506201.
\url{https://arxiv.org/abs/math/0506201}

\bibitem{JR2004}
W. B. Johnson and N. L. Randrianarivony,
\emph{\(\ell_p\) (\(p>2\)) does not coarsely embed into a Hilbert space},
Proc. Amer. Math. Soc. 134 (2006), no. 4, 1045--1050.

\end{thebibliography}

\end{document}

