\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\emergencystretch=3em

\title{Literature Status Note for arXiv:2510.12540}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-07-03}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_already\_answered}, scoped to the source paper's
conjectured strict upper bound for the two-variable universal commuting
dilation constant. This note is not a new proof from this run.

\section*{Source Question}

The source paper is M. Gerhold, M. Scherer, and O. M. Shalit,
\emph{Empirical bounds for commuting dilations of free unitaries and the
universal commuting dilation constant}, arXiv:2510.12540.

On page 1, the source identifies the open problem of determining the universal
commuting dilation constant \(C_2\), the least constant \(c\) such that every
pair of contractions dilates to commuting normal operators of norm at most
\(c\). The source gives numerical evidence for
\[
  C_2 \leq 2\sqrt{\frac{2}{3}} < 2 .
\]
On page 3, after deriving this inequality semi-rigorously from an empirical
random-unitary limit, the source explicitly states that this inequality is
conjectured to hold.

\section*{Supporting Answer}

The supporting paper is I. Thompson, arXiv:2606.12506. Its title is
\emph{On the universal commuting dilation constant}.

The abstract on page 1 states that the paper gives a positive answer to the
question whether \(C_2<2\). Page 2, Theorem A, proves that for every pair of
contractions \(T_1,T_2\) there is a dilation to commuting normal contractions
with scale
\[
  \frac{2}{\sqrt{\varphi}},
\]
where \(\varphi\) is the golden ratio. Equivalently,
\[
  C_2 \leq \frac{2}{\sqrt{\varphi}} .
\]
The same page explicitly discusses the 2025 empirical approach and says that
the new upper bound is stronger than the suggested bound
\(C_2 \leq 2\sqrt{2/3}\).

Since \(\varphi=(1+\sqrt5)/2\), one has
\[
  \frac{2}{\sqrt{\varphi}} \approx 1.5724
  < 2\sqrt{\frac{2}{3}} \approx 1.6330 .
\]
Thus the supporting theorem proves the source's conjectured inequality and in
particular proves \(C_2<2\).

\section*{Why This Is Literature, Not A New Result}

The supporting paper explicitly cites and discusses the 2025 empirical approach
and states that its main upper bound is stronger than the suggested
\(2\sqrt{2/3}\) bound. The identification is therefore a direct later-literature
answer, not an agent-derived implication.

\section*{Scope Limitations}

This packet does not claim the exact value of \(C_2\). It also does not prove
the source's empirical random-matrix limit
\(\lim_{N\to\infty} c(U^{(N)},u_0)=\sqrt2\). Finally, it does not determine
the exact value of \(C_d\) for every \(d\); the supporting paper improves
general bounds but does not settle all constants.

\section*{Search And Verification Notes}

The run indexes were searched for the source arXiv id, title terms, and core
keywords including \texttt{commuting dilations}, \texttt{free unitaries},
\texttt{universal commuting dilation constant}, and \texttt{C\_2}. No prior
packet for arXiv:2510.12540 was found. Web search found arXiv:2606.12506,
posted June 2026, with the stronger Theorem A bound.

\section*{Local Files}

\begin{itemize}[leftmargin=2em]
  \item Source PDF: \texttt{source\_paper.pdf}.
  \item Supporting PDF: \texttt{supporting\_paper\_2606.12506.pdf}.
  \item Ledger record:
    \texttt{2510.12540\_c2\_bound\_answered\_by\_2606.12506.json}.
\end{itemize}

\begin{thebibliography}{9}
\bibitem{GerholdSchererShalit2025}
M. Gerhold, M. Scherer, and O. M. Shalit,
\emph{Empirical bounds for commuting dilations of free unitaries and the
universal commuting dilation constant},
arXiv:2510.12540.

\bibitem{Thompson2026}
I. Thompson,
\emph{On the universal commuting dilation constant},
arXiv:2606.12506.
\end{thebibliography}

\end{document}
