\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for arXiv:1302.4618: The \(4M-4\) Conjecture}
\author{Run fa\_banach\_001, agent\_lane\_03}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet.  It records that the
\(4M-4\) conjecture posed by Bandeira--Cahill--Mixon--Nelson in
\emph{Saving phase: Injectivity and stability for phase retrieval},
arXiv:1302.4618, has already been settled in later literature: the generic
sufficiency half was proved by Conca--Edidin--Hering--Vinzant
\cite{CEHV13}, and the proposed necessity half was disproved by Vinzant
\cite{Vinzant15}.

\section*{Source Question}

On PDF page 7 of arXiv:1302.4618, after a dimension-counting discussion of
rank-at-most-two Hermitian matrices, the authors pose the following
\(4M-4\) conjecture.  Let
\[
  \Phi=\{\varphi_n\}_{n=1}^N\subseteq \mathbb{C}^M,\qquad
  \mathcal A:\mathbb{C}^M/\mathbb T\to\mathbb R^N,\qquad
  (\mathcal A(x))(n)=|\langle x,\varphi_n\rangle|^2 .
\]
If \(M\geq 2\), then:
\begin{enumerate}
\item[(a)] if \(N<4M-4\), then \(\mathcal A\) is not injective;
\item[(b)] if \(N\geq 4M-4\), then \(\mathcal A\) is injective for generic
\(\Phi\).
\end{enumerate}
The source paper proves this conjecture only for \(M=2\) and \(M=3\).

\section*{Supporting Answers}

The first later paper, arXiv:1312.0158, explicitly identifies the same
conjecture.  Its Theorem~1.1 states that if \(N\geq 4M-4\), then for a generic
frame \(\Phi\), the map \(\mathcal A_\Phi\) is injective.  The introduction
states that this proves part (b) of the \(4M-4\) conjecture from
\cite{BCMN13}.  Thus the generic sufficiency half of the source conjecture is
answered positively.

The second later paper, arXiv:1502.04656, explicitly gives a counterexample to
the proposed necessity half.  Its abstract presents a complex frame of eleven
vectors in four-dimensional complex space and proves that it defines injective
measurements; the same paragraph says this disproves the conjecture of
Bandeira--Cahill--Mixon--Nelson.  In Section~II the paper displays the
eleven-vector frame in \(\mathbb C^4\) and states that it provides a
counterexample to Conjecture~2 of \cite{BCMN13}.  Since \(4M-4=12\) when
\(M=4\), this is an injective example with \(N=11<12\), contradicting part
(a).

\section*{Scope}

Together these papers settle the \(4M-4\) conjecture as stated in
arXiv:1302.4618: part (b) is true, while part (a) is false.  This packet does
not claim a complete classification of the exact minimum number of complex
measurements in all dimensions.  It also does not address the source paper's
separate stability questions, quantitative Lipschitz bounds, or refinements
connected to Wright's conjecture.

\section*{Search Evidence}

The lane-3 queue selected arXiv:1302.4618.  The cheap run indexes were searched
for the arXiv id, title words, ``phase retrieval'', ``4M-4'', and nearby
author names; no duplicate packet for this source was found.  Targeted searches
for phrases including ``4M-4 Conjecture phase retrieval'', ``Saving phase
4M-4 conjecture'', ``generic 4M-4 phase retrieval Conca Edidin Hering
Vinzant'', and ``small frame certificate injectivity 4M-4'' identified
arXiv:1312.0158 and arXiv:1502.04656 as the decisive later sources.

\begin{thebibliography}{9}

\bibitem{BCMN13}
A.~S. Bandeira, J.~Cahill, D.~G. Mixon, and A.~A. Nelson,
\emph{Saving phase: Injectivity and stability for phase retrieval},
arXiv:1302.4618.

\bibitem{CEHV13}
A.~Conca, D.~Edidin, M.~Hering, and C.~Vinzant,
\emph{An algebraic characterization of injectivity in phase retrieval},
arXiv:1312.0158.

\bibitem{Vinzant15}
C.~Vinzant,
\emph{A small frame and a certificate of its injectivity},
arXiv:1502.04656.

\end{thebibliography}

\end{document}
