\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\geometry{margin=1in}

\title{Literature-Implied Answer: Fully \((2;2,\ldots,2)\)-Summing \(L_\infty\) Multilinear Forms}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_09}}
\date{2026-06-15}

\begin{document}
\maketitle

\section*{Source Question}

The source paper is Daniel M. Pellegrino, \emph{Cotype and nonlinear absolutely
summing mappings}, arXiv:math/0307311.  In Section 4, after defining
\(r\)-fully absolutely summing multilinear mappings, the author asks whether
every scalar \(n\)-linear mapping on \(\mathcal L_\infty\) spaces is fully
\((2;2,\ldots,2)\)-summing.  The question appears on page 10 of the source
PDF.

In the source notation, the case \(r=n\) is called ``fully'' summing, while the
subsequent corollary gives an \(f(2)\)-fully conclusion.  Thus the source paper
only gives the all-indices answer in the bilinear case; for \(n\geq 3\), the
natural question is the full multiple-array assertion.

\section*{Supporting Theorem}

The supporting paper is Geraldo Botelho, Carsten Michels, and Daniel
Pellegrino, \emph{New inclusion and coincidence theorems for summing
multilinear mappings}, arXiv:0810.0947.

Section 4 of the supporting paper defines multiple
\((q;p_1,\ldots,p_n)\)-summing mappings by summing over all indices
\((j_1,\ldots,j_n)\).  This is the same all-indices condition as the source
paper's fully summing notion.  In Section 4.3, Corollary 4.10, page 9, the
supporting paper proves:
\[
  \mathcal L(E_1,\ldots,E_n;F)
  =
  \mathcal L_{ms,r}(E_1,\ldots,E_n;F)
  \qquad (2\leq r\leq\infty)
\]
whenever \(E_1,\ldots,E_n\) are \(\mathcal L_\infty\)-spaces and \(F\) has
cotype \(2\).

\section*{Identification}

The scalar field \(\mathbb K\) has cotype \(2\).  Applying Corollary 4.10 with
\(F=\mathbb K\) and \(r=2\) gives
\[
  \mathcal L(E_1,\ldots,E_n;\mathbb K)
  =
  \mathcal L_{ms,2}(E_1,\ldots,E_n;\mathbb K),
\]
that is, every scalar-valued continuous \(n\)-linear form on
\(\mathcal L_\infty\) domains is multiple \((2;2,\ldots,2)\)-summing.  Under
the notation match above, this is precisely the fully \((2;2,\ldots,2)\)
answer requested in the source question.

\section*{Provenance and Scope}

This packet records a literature-implied answer, not an original proof.  The
supporting paper does not explicitly present Corollary 4.10 as resolving the
source sentence, but it cites the source paper and proves a stronger
coincidence theorem whose scalar \(r=2\) case answers the question.  No broader
claim is made about optimal constants, other exponents, or unrelated nonlinear
summability problems.

\section*{References}

\begin{itemize}
\item D. M. Pellegrino, \emph{Cotype and nonlinear absolutely summing
mappings}, arXiv:math/0307311.
\item G. Botelho, C. Michels, and D. Pellegrino, \emph{New inclusion and
coincidence theorems for summing multilinear mappings}, arXiv:0810.0947.
\end{itemize}

\end{document}
