\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for arXiv:1012.5595: A ZFC Non-Gruenhage Compact Space with \((*)\)}
\author{Run fa\_banach\_001, agent\_lane\_13}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet.  It records that
Problem~6.2 of Orihuela--Troyanski--Smith,
\emph{Strictly convex norms and topology}, arXiv:1012.5595, was answered by
Richard J. Smith, \emph{Tree Duplicates, \(G_\delta\)-diagonals and
Gruenhage spaces}, arXiv:1102.0982.

\section*{Source Question}

Section~6 of arXiv:1012.5595 lists several unresolved problems.  The second
one, labelled \texttt{zfcstarnon-gru}, asks:
\[
\text{Is there in ZFC an example of a non-Gruenhage compact space with } (*)?
\]
The preceding text explains that the source paper constructs such a compact
scattered non-Gruenhage space with \((*)\) under the continuum hypothesis, but
leaves the ZFC version open.

\section*{Supporting Answer}

The abstract of arXiv:1102.0982 says that the paper gives a ZFC example of a
locally compact, scattered, Hausdorff, non-Gruenhage space \(D\) having a
\(G_\delta\)-diagonal, and explicitly says that this answers a question posed
by Orihuela, Troyanski, and Smith in their work on strictly convex norms.

In the introduction, Smith recalls two topological facts needed to convert
this locally compact example into the compact example asked for in
Problem~6.2: every space with a \(G_\delta\)-diagonal has \((*)\), and if
\(L\) is locally compact and has \((*)\), then the one-point compactification
\(L\cup\{\infty\}\) also has \((*)\).  The main theorem proves that the
\(\Lambda\)-duplicate has a \(G_\delta\)-diagonal but is not Gruenhage.  The
following corollary then states that the one-point compactification \(K\) of
that space \(D\) is a scattered compact non-Gruenhage space with \((*)\).

This is exactly the ZFC example requested in Problem~6.2 of arXiv:1012.5595.

\section*{Scope}

This packet records only the answer to Problem~6.2.  It does not address the
other problems in Section~6 of arXiv:1012.5595, including the non-scattered
strictly convex dual norm problem, the preservation of \((*)\) under
continuous or perfect images, or the Gateaux-norm problem for the
Ostaszewski and HMVZ compact \(O\)-spaces.

\section*{Search Evidence}

The lane-13 sparse queue selected arXiv:1012.5595.  Cheap run indexes were
searched for the arXiv id, title words, \texttt{strictly convex norms},
\texttt{property (*)}, \texttt{non-Gruenhage}, and
\texttt{G\_delta-diagonal}; no duplicate packet for this source was found.
Targeted local and web searches for the source problem phrase
\texttt{non-Gruenhage compact space with (*)} identified arXiv:1102.0982 as
the decisive later paper.  Its abstract, theorem, and corollary explicitly
match the source problem.

\begin{thebibliography}{9}
\bibitem{OTS10}
J.~Orihuela, S.~Troyanski, and R.~J. Smith,
\emph{Strictly convex norms and topology},
arXiv:1012.5595.

\bibitem{Smith11}
R.~J. Smith,
\emph{Tree Duplicates, \(G_\delta\)-diagonals and Gruenhage spaces},
arXiv:1102.0982.
\end{thebibliography}

\end{document}
