\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\newcommand{\GammaG}{\Gamma}
\newcommand{\SL}{\operatorname{SL}}
\newcommand{\QQ}{\mathbb Q}

\title{A Literature-Implied Negative Answer to the Higher Property (T) Converse}
\author{Run fa\_banach\_001}
\date{2026-07-19}

\begin{document}
\maketitle

\section{Status}

This is a lightweight \emph{literature-implied answer}, not an original proof.
The source paper is
\[
\text{U. Bader and P. W. Nowak, \emph{Cohomology of deformations},
arXiv:1401.5362.}
\]
In Section 5.1, ``Higher property (T) and reduced cohomology'', Definition 5.1
defines property \((T_n)\) for a group of type \(F_{n+1}\) by requiring that
\[
  H^{n+1}(\GammaG,\pi)
\]
is reduced for every unitary representation \(\pi\).  Immediately after the
definition, the paper asks whether the converse to the trivial implication is
true: does this reducedness condition imply
\[
  H^{n+1}(\GammaG,\pi)=0
\]
for every unitary representation \(\pi\)?

\section{Supporting Literature}

The supporting paper is U. Bader and R. Sauer,
\emph{Higher Kazhdan property and unitary cohomology of arithmetic groups},
arXiv:2308.06517v3.
Its introduction explicitly says that the higher analogues of the
Delorme--Guichardet equivalent criteria are not equivalent.  Its Definition 1.1
uses different notation: \( [T_n]\) is vanishing of \(H^j\) for every unitary
representation and \(1\leq j\leq n\), while \((T_n)\) is the corresponding
vanishing condition for unitary representations without invariant vectors.

The decisive passage is Remark 3.10.  It states that, for \(n>1\), having
\[
  H^k(\GammaG,U)\ \text{reduced for every }k\leq n
  \text{ and every unitary }U
\]
does not guarantee Bader--Sauer's vanishing property \((T_n)\), and gives
\(\SL_{n+1}(\QQ_p)\) and its lattices as examples with reduced cohomology
groups in all degrees.

\section{Identification}

Take \(m\geq 1\) in the Bader--Nowak question and set \(k=m+1\geq 2\).  Let
\(\GammaG\) be a suitable lattice in \(\SL_{k+1}(\QQ_p)\), for instance a
torsion-free cocompact lattice when one wants a discrete group with a finite
\(K(\GammaG,1)\).  Bader--Sauer's Remark 3.10 gives that
\[
  H^j(\GammaG,U)
\]
is reduced for every degree \(j\) and every unitary \(U\).  In particular,
\(\GammaG\) satisfies the Bader--Nowak property \((T_m)\), since the relevant
degree is \(m+1=k\).

On the other hand, the same Bader--Sauer discussion says these examples do not
satisfy the corresponding degree-\(k\) vanishing property.  Garland's theorem,
as stated in the supporting paper for \(\SL_r(\QQ_p)\), gives vanishing through
degree \(r-2\).  For \(r=k+1\), this is vanishing through degree \(k-1\), so the
first possible failure of vanishing is exactly degree \(k\).  Thus there is a
unitary representation \(U\) with
\[
  H^k(\GammaG,U)\neq 0,
\]
while \(H^k(\GammaG,U)\) is reduced.

This is precisely a counterexample to the source converse for \(m=k-1\):
reducedness of \(H^{m+1}\) for every unitary representation does not force
vanishing of \(H^{m+1}\) for every unitary representation.

\section{Scope}

The implication is negative in every genuinely higher degree \(m\geq 1\).  The
case \(m=0\) is different: it is the ordinary Delorme--Guichardet theorem for
Kazhdan's property (T), and remains positive.

The supporting authors do not present the passage as a direct answer to the
question in arXiv:1401.5362.  This packet records the consequence after matching
definitions and the degree shift.

\section{References}

\begin{itemize}[leftmargin=*]
\item U. Bader and P. W. Nowak, \emph{Cohomology of deformations},
arXiv:1401.5362.
\item U. Bader and R. Sauer, \emph{Higher Kazhdan property and unitary
cohomology of arithmetic groups}, arXiv:2308.06517v3.
\item H. Garland, \emph{p-adic curvature and the cohomology of discrete
subgroups of p-adic groups}, Annals of Mathematics 97 (1973), as quoted in the
supporting paper.
\end{itemize}

\end{document}
