\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}

\newcommand{\ga}{\gamma}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

\title{Literature-Implied Subcase for arXiv:math/0611724}
\author{FA/Banach run fa\_banach\_001}
\date{June 15, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_implied\_answer (partial subcase /
reformulated resolvent condition)} packet. It does not claim a new proof, and
it does not claim a complete answer to the exact finite-cotype formulation in
Haak--van Neerven \cite{HaakNeerven2006}. It records that a later theorem of
Abreu--Haak--van Neerven \cite{AbreuHaakNeerven2012} proves the central
invariant-measure equivalence under Pisier property $(\alpha)$.

\section*{Source Conjecture}

In the final section of \cite{HaakNeerven2006}, after proving that existence
of an invariant measure implies uniform $\ga$-radonification of the sector
resolvent family
\[
  \{\sqrt{\lambda}R(\lambda,A)B:\lambda\in S_\vartheta\},
\]
Haak--van Neerven formulate the stochastic Weiss conjecture. In their displayed
formulation, $E$ has finite cotype, $-A$ is injective and sectorial of angle
less than $\pi/2$, and $-A$ admits a bounded $H^\infty$ calculus. The conjecture
asks for equivalence of:
\begin{enumerate}
  \item the stochastic Cauchy problem admits an invariant measure;
  \item $(-A)^{-1/2}B$ is $\ga$-radonifying;
  \item the sector family $\{\sqrt{\lambda}R(\lambda,A)B\}$ is uniformly
  $\ga$-radonifying for some/every sector angle $0<\vartheta<\pi/2$.
\end{enumerate}
The authors note that the implication from (2) to (1) is known, and that the
remaining hard direction is from the resolvent condition to
$(-A)^{-1/2}B\in\ga(H,E)$, or directly to invariant measure.

\section*{Supporting Theorem}

The later paper \cite{AbreuHaakNeerven2012} explicitly cites
\cite{HaakNeerven2006} and states in its abstract that it solves the stochastic
Weiss conjecture proposed there. Its main theorem assumes that $E$ has
Pisier property $(\alpha)$ and that $-A$ admits a bounded $H^\infty$ calculus
of angle less than $\pi/2$. It proves the equivalence of invariant measure,
$(-A)^{-1/2}B\in\ga(H,E)$, a $\ga(L^2(\R_+,d\lambda/\lambda;H),E)$ resolvent
condition, and a dyadic Gaussian resolvent condition.

\section*{Idea of the Identification}

The source conjecture's central analytic content is the equivalence between
existence of an invariant measure and the half-power condition
$(-A)^{-1/2}B\in\ga(H,E)$. The later theorem proves exactly this equivalence
under property $(\alpha)$, and it supplies a precise stochastic-resolvent
condition in place of the original uniform family condition. Property
$(\alpha)$ includes Hilbert spaces and $L^p$ spaces, and the supporting paper
recalls Pisier's theorem that a Banach lattice has property $(\alpha)$ if and
only if it has finite cotype. Thus the literature theorem answers a substantial
finite-cotype lattice/Hilbert subcase of the 2006 programme.

\begin{theorem}
Let $E$ have property $(\alpha)$. Suppose $-A$ is injective, sectorial of angle
less than $\pi/2$, has dense range, and admits a bounded $H^\infty$ calculus
of angle less than $\pi/2$ on $E$. Let $B:H\to E_{-1}$ be bounded. Then the
stochastic Cauchy problem admits an invariant measure on $E$ if and only if
$(-A)^{-1/2}B\in\ga(H,E)$.
\end{theorem}

\begin{proof}
This is the implication between assertions (1) and (2) in
Theorem 1.1 of Abreu--Haak--van Neerven \cite{AbreuHaakNeerven2012}. The same
theorem also proves equivalence with the supporting paper's
$\ga(L^2(d\lambda/\lambda))$ and dyadic Gaussian resolvent conditions.
\end{proof}

\section*{Limitations}

This packet is deliberately scoped. The original displayed conjecture in
\cite{HaakNeerven2006} assumes finite cotype and uses uniform
$\ga$-radonification of the whole sector resolvent family. The supporting
paper assumes property $(\alpha)$ and formulates the resolvent side through
Gaussian square-function/dyadic conditions. Therefore the packet should not be
counted as a full answer to the exact finite-cotype uniform-family statement.
The apparent remaining territory is the finite-cotype case without property
$(\alpha)$, and the precise relationship between the original uniform-family
condition and the later dyadic/Gaussian condition outside the supporting
paper's hypotheses.

\section*{Search Evidence}

The run indexes were searched for \texttt{0611724}, \texttt{gamma-radonifying},
\texttt{stochastic Weiss}, \texttt{Weiss conjecture}, \texttt{admissibility},
and \texttt{analytic semigroup}. No prior packet or attempt for this target
was found. Local source comparison identified arXiv:1206.3656 as the decisive
supporting paper. Web/arXiv searches on June 15, 2026 for stochastic Weiss
conjecture, finite cotype, property $(\alpha)$, and gamma-radonifying variants
found the original arXiv source and arXiv:1206.3656, but no later primary
source removing the property $(\alpha)$ restriction.

\section*{Human Review Recommendation}

Review as a provenance/status packet. The main points to check are whether a
later source has closed the finite-cotype gap, and whether the published
version of \cite{AbreuHaakNeerven2012} labels the main theorem differently
from the arXiv source. This should not be counted as an original proof or a
full solution of the 2006 conjecture as displayed.

\begin{thebibliography}{9}

\bibitem{HaakNeerven2006}
B. H. Haak and J. van Neerven,
\emph{Uniformly gamma-radonifying families of operators and the stochastic
Weiss conjecture},
arXiv:math/0611724.

\bibitem{AbreuHaakNeerven2012}
J. Abreu, B. Haak, and J. van Neerven,
\emph{The stochastic Weiss conjecture for bounded analytic semigroups},
arXiv:1206.3656.

\end{thebibliography}

\end{document}
