\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}

\newcommand{\B}{\mathcal B}
\newcommand{\K}{\mathcal K}
\newcommand{\F}{\mathcal F}
\newcommand{\Lop}{\mathcal L}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\HH}{H}
\newcommand{\eps}{\varepsilon}
\newcommand{\dens}{\operatorname{dens}}

\title{A SHAI Subcase for the First Limit Bourgain--Rosenthal--Schechtman Space}
\author{Run \texttt{fa\_banach\_001}, lane 14}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

This packet records a partial result for Johnson--Phillips--Schechtman's
Problem~\ref{source-problem} from \cite{JPS}.  The source asks whether every
complemented subspace of \(L^p\), and in particular the
Bourgain--Rosenthal--Schechtman examples, has the SHAI property.  We prove the
first limit BRS/Rosenthal subcase.

\begin{theorem}[Main result]
\label{main}
Let \(1<p<\infty\).  The centered first limit
Bourgain--Rosenthal--Schechtman space \(R_\omega^{p,0}\) has the SHAI property.
Consequently the non-centered first limit space
\[
  R_\omega^p \cong \mathbb K \oplus R_\omega^{p,0}
\]
also has the SHAI property.
\end{theorem}

This is a partial answer only: it does not settle arbitrary complemented
subspaces of \(L^p\), the unconditional-basis version, or all countable BRS
spaces \(R_\alpha^p\).

\section*{Source Question}

In \cite[Problem 2.7]{JPS}, Johnson--Phillips--Schechtman ask:

\begin{quote}
\label{source-problem}
Suppose \(p\in(1,\infty)\setminus\{2\}\) and let \(X\) be a complemented
subspace of \(L^p\). Does \(X\) have the SHAI property? What if, in addition,
\(X\) has an unconditional basis? What if, in addition, \(X\) is one of the
\(\aleph_1\) spaces constructed in \cite{BRS}?
\end{quote}

\section*{Proof Intuition}

The Johnson--Phillips--Schechtman proof for \(L^p\), \(1<p<\infty\), uses a
finite-dimensional decomposition with continuum many almost-disjoint
coordinate subspaces, each isomorphic to the whole space.  In the first limit
BRS space the natural blocks are
\[
  H_n=L_p^0(\{0,1\}^n),
\]
and a copy of \(H_m\) generally sits inside a later block \(H_k\), \(k\ge m\),
rather than as a whole block.  This is still enough.  For every infinite
set \(A=\{a_1<a_2<\cdots\}\), embed \(H_m\) into \(H_{a_m}\) by ignoring the
last \(a_m-m\) Bernoulli coordinates.  The resulting range is a complemented
isometric copy of the whole first-limit BRS space.

Taking a continuum almost-disjoint family of infinite sets \(A\) gives
continuum many self-copy projections \(P_A\).  If \(A\cap B\) is finite, then
\(P_AP_B\) has finite-dimensional range, hence is finite rank.  In any
nonzero quotient of \(\Lop(X)\), finite-rank operators vanish, so the images of
the \(P_A\)'s become pairwise orthogonal nonzero idempotents with uniformly
bounded finite sums.  A lower \(s\)-estimate inherited from \(L^p\) makes the
associated decomposition in the quotient target boundedly complete, and the
usual density contradiction follows.

\section*{Preliminaries}

We use the concrete first-limit realization from \cite{Sampedro}: let
\(\Omega_n=\{0,1\}^n\) with uniform probability and set
\[
  H_n=L_p^0(\Omega_n).
\]
On the product probability space \(\Omega=\prod_{n=1}^\infty \Omega_n\), let
\(J_n:H_n\to L^p(\Omega)\) be the \(n\)-th coordinate lifting.  Then
\[
  X:=R_\omega^{p,0}
     = \overline{\operatorname{span}}\{J_n(H_n):n\in\N\}.
\]
Each \(H_n\) is finite dimensional.  The coordinate projection onto any
subcollection of the exterior blocks is the restriction of a conditional
expectation, hence has norm at most one.

We shall use the following standard estimate in the same way as
\cite[Section 1]{JPS}.  Since \(X\) is a subspace of an \(L^p\)-space, its
canonical unconditional finite-dimensional decomposition has a disjoint lower
\(s\)-estimate for some finite \(s\), for instance \(s=\max\{p,2\}\): there is
\(C_s<\infty\) such that whenever \(z_1,\ldots,z_m\in X\) have disjoint
exterior block supports,
\[
  \Big(\sum_{j=1}^m \|z_j\|^s\Big)^{1/s}
     \le C_s\Big\|\sum_{j=1}^m z_j\Big\|.
\]

\section*{Block-Finite Self-Copies}

\begin{lemma}[Almost-disjoint complemented self-copies]
\label{copy-lemma}
There is a family \(\mathcal A\subset[\N]^\omega\) of cardinality continuum and
norm-one projections \(P_A\in\Lop(X)\), \(A\in\mathcal A\), such that:
\begin{enumerate}
\item \(P_A X\) is isometric to \(X\);
\item if \(A\ne B\), then \(P_AP_B\) is finite rank;
\item for every finite \(\mathcal F\subset\mathcal A\) there are finite-rank
operators \(R_A\), \(A\in\mathcal F\), such that
\[
  \Phi(P_A)=\Phi(P_A-R_A)
\]
for every homomorphism \(\Phi\) whose kernel contains the finite-rank
operators, and
\[
  \Big\|\sum_{A\in\mathcal F}(P_A-R_A)\Big\|\le 1.
\]
\end{enumerate}
\end{lemma}

\begin{proof}
Fix a continuum-sized almost-disjoint family
\(\mathcal A\subset[\N]^\omega\).  For \(A=\{a_1<a_2<\cdots\}\), we have
\(a_m\ge m\).  Let
\(\rho_{m,A}:\Omega_{a_m}\to\Omega_m\) be the projection onto the first
\(m\) Bernoulli coordinates.  Pullback by \(\rho_{m,A}\) gives an isometric
embedding
\[
  u_{m,A}:H_m\longrightarrow H_{a_m}.
\]
The conditional expectation from \(L^p(\Omega_{a_m})\) onto the sigma algebra
generated by those first \(m\) coordinates restricts to a norm-one projection
from \(H_{a_m}\) onto \(u_{m,A}H_m\).

Define \(U_A:X\to X\) on finite sums by
\[
  U_A\Big(\sum_m J_m x_m\Big)=\sum_m J_{a_m}u_{m,A}x_m.
\]
The summands remain independent and preserve their individual distributions,
so \(U_A\) extends to an isometry.  Define \(V_A:X\to X\) by first projecting
onto the exterior blocks \(a_m\), then applying the above conditional
expectation inside \(H_{a_m}\), and finally identifying \(u_{m,A}H_m\) with
\(H_m\).  This is the restriction of a conditional expectation/factor map on
the product probability space, so \(\|V_A\|\le1\), and \(V_AU_A=I_X\).
Put \(P_A=U_AV_A\).  Then \(P_A\) is a norm-one projection and \(P_AX=U_AX\)
is isometric to \(X\).

If \(A\ne B\), then \(A\cap B\) is finite.  The operator \(P_AP_B\) can be
nonzero only on exterior blocks indexed by \(A\cap B\).  Each such block is
finite dimensional, hence \(P_AP_B\) is finite rank.

Now let \(\mathcal F\subset\mathcal A\) be finite and let
\[
  S=\bigcup_{\substack{A,B\in\mathcal F\\ A\ne B}} (A\cap B).
\]
For \(A\in\mathcal F\), let \(P_A^S\) be the same projection as \(P_A\), but
with all target exterior blocks in \(S\) deleted.  Then \(P_A-P_A^S\) has range
contained in the finite-dimensional sum of the blocks \(H_k\), \(k\in S\), so
it is finite rank.  The remaining target block supports \(A\setminus S\),
\(A\in\mathcal F\), are pairwise disjoint.  Therefore
\(\sum_{A\in\mathcal F}P_A^S\) is again a coordinatewise conditional
expectation onto mutually disjoint Bernoulli factors, and its norm is at most
one.  Taking \(R_A=P_A-P_A^S\) proves the last assertion.
\end{proof}

\begin{lemma}[Lower-estimate transfer for the self-copy projections]
\label{lower-lemma}
Let \(Q_1,\ldots,Q_m\) be projections obtained from finitely many \(P_A\)'s by
deleting a common finite set of exterior target blocks as in the proof of
Lemma~\ref{copy-lemma}, so that the ranges of the \(Q_j\)'s have pairwise
disjoint exterior block supports and \(\|\sum_j Q_j\|\le1\).  If
\(T_1,\ldots,T_m\in\Lop(X)\), then
\[
  \Big\|\sum_{j=1}^m T_jQ_j\Big\|
  \le C_s\Big(\sum_{j=1}^m \|T_j\|^{s'}\Big)^{1/s'},
  \qquad \frac1s+\frac1{s'}=1.
\]
\end{lemma}

\begin{proof}
For \(\|x\|\le1\), the vectors \(Q_jx\) have disjoint exterior block supports.
Thus
\[
\begin{aligned}
\Big\|\sum_j T_jQ_jx\Big\|
&\le \sum_j \|T_j\|\,\|Q_jx\|  \\
&\le \Big(\sum_j\|T_j\|^{s'}\Big)^{1/s'}
     \Big(\sum_j\|Q_jx\|^s\Big)^{1/s}  \\
&\le C_s\Big(\sum_j\|T_j\|^{s'}\Big)^{1/s'}
     \Big\|\sum_j Q_jx\Big\|  \\
&\le C_s\Big(\sum_j\|T_j\|^{s'}\Big)^{1/s'}.
\end{aligned}
\]
\end{proof}

\section*{Proof of Theorem \ref{main}}

Assume toward contradiction that \(Y\ne0\) and that
\[
  \Phi:\Lop(X)\longrightarrow \Lop(Y)
\]
is a surjective non-injective algebra homomorphism.  By automatic continuity
\cite{JPS,Dales}, \(\Phi\) is continuous.  Its nonzero kernel is a closed
two-sided ideal in \(\Lop(X)\), hence contains the finite-rank operators.

For \(A\in\mathcal A\), put \(E_A=\Phi(P_A)\).  Each \(E_A\) is a nonzero
idempotent.  Indeed, if \(E_A=0\), then
\[
  I_X=V_AP_AU_A
\]
would imply \(\Phi(I_X)=0\), impossible because \(Y\ne0\).  If \(A\ne B\),
then \(P_AP_B\) is finite rank by Lemma~\ref{copy-lemma}, so
\[
  E_AE_B=0=E_BE_A.
\]
Moreover, for each finite \(\mathcal F\subset\mathcal A\), Lemma~\ref{copy-lemma}
gives finite-rank corrections \(R_A\) such that
\[
  \Big\|\sum_{A\in\mathcal F}E_A\Big\|
  =
  \Big\|\Phi\Big(\sum_{A\in\mathcal F}(P_A-R_A)\Big)\Big\|
  \le \|\Phi\|.
\]
Thus the \(E_A\)'s are pairwise orthogonal nonzero idempotents with uniformly
bounded finite sums.

Let \(Y_A=E_AY\) and let \(Y_0\) be the closed linear span of the \(Y_A\)'s.
We claim that the family \((Y_A)_{A\in\mathcal A}\) is boundedly complete.
By the open mapping theorem, choose \(K_\Phi<\infty\) such that every
\(T\in\Lop(Y)\) has a lift \(S\in\Lop(X)\) with \(\Phi(S)=T\) and
\(\|S\|\le K_\Phi\|T\|\).  Applying Lemma~\ref{lower-lemma} to finite disjoint
families and then applying \(\Phi\), we get a constant \(C\) such that for all
finite \(A_1,\ldots,A_m\subset\mathcal A\) and all
\(T_1,\ldots,T_m\in\Lop(Y)\),
\[
  \Big\|\sum_{j=1}^m T_jE_{A_j}\Big\|
  \le C\Big(\sum_{j=1}^m\|T_j\|^{s'}\Big)^{1/s'}.
\]
The same rank-one duality argument used in \cite[Theorem 1.1]{JPS} then gives
a disjoint lower \(s\)-estimate on the decomposition:
\[
  \|y\|\ge C^{-1}
  \Big(\sum_{j=1}^m \|E_{A_j}y\|^s\Big)^{1/s},
  \qquad y\in Y.
\]
Consequently, if finite partial sums \(\sum_{A\in F}y_A\), \(y_A\in Y_A\), are
uniformly bounded, then \(\sum_A\|y_A\|^s<\infty\), so only countably many
terms are nonzero and the net of partial sums converges.  This is bounded
completeness.  Since the finite sums of the coordinate projections \(E_A\) are
uniformly bounded, bounded completeness implies that \(Y_0\) is complemented
in \(Y\).

For every subset \(\mathcal S\subseteq\mathcal A\), bounded completeness gives
a projection \(Q_{\mathcal S}:Y_0\to Y_0\) onto
\(\overline{\operatorname{span}}\{Y_A:A\in\mathcal S\}\).  Distinct subsets
give projections at distance at least one, because each \(Y_A\) is nonzero.
Hence
\[
  \dens \Lop(Y_0)\ge 2^{\mathfrak c}.
\]
Since \(Y_0\) is complemented in \(Y\), also
\(\dens \Lop(Y)\ge 2^{\mathfrak c}\).

On the other hand, \(X=R_\omega^{p,0}\) is separable, so
\(\dens\Lop(X)\le\mathfrak c\).  A continuous image of \(\Lop(X)\) cannot have
density exceeding \(\mathfrak c\), contradicting the surjectivity of
\(\Phi:\Lop(X)\to\Lop(Y)\).  Therefore every surjective homomorphism
\(\Lop(X)\to\Lop(Y)\), \(Y\ne0\), is injective, and \(X\) has SHAI.

Finally, \(R_\omega^p\cong \mathbb K\oplus R_\omega^{p,0}\).  The
one-dimensional space has SHAI, and SHAI is stable under finite direct sums
\cite[Proposition 2.9]{Horvath}.  Thus \(R_\omega^p\) has SHAI as well.

\section*{Verification and Novelty Notes}

The cheap run indexes were searched for `2102.03966', `SHAI', `L\^1',
`C\_\(\backslash\)infty', `complemented subspace of L\^p', and BRS-related
phrases.  The only relevant prior run packet was the separate conditional
answer for a \(C(K)\) SHAI subcase of \cite{HK}; it does not overlap with the
present \(L^p\)/BRS target.  Local later-source search found the concrete
first-limit BRS realization and embedding classification in \cite{Sampedro}
and the general BRS FDD/factorization paper \cite{KM}; neither was indexed as
an explicit SHAI answer to Johnson--Phillips--Schechtman's BRS subquestion.

The proof above is not a literature-status identification: it combines the
Bernoulli-block realization of \(R_\omega^{p,0}\) with a modified
Johnson--Phillips--Schechtman quotient-density argument.

Human review should focus on Lemma~\ref{copy-lemma}, especially the assertion
that the finite sums of the deleted block-copy projections are uniformly
bounded, and on the lower-estimate transfer in Lemma~\ref{lower-lemma}.

\begin{thebibliography}{9}

\bibitem{BRS}
J. Bourgain, H. P. Rosenthal, and G. Schechtman,
\emph{An ordinal \(L_p\)-index for Banach spaces, with application to
complemented subspaces of \(L_p\)},
Ann. of Math. (2) 114 (1981), 193--228.

\bibitem{Dales}
H. G. Dales,
\emph{Banach Algebras and Automatic Continuity},
London Mathematical Society Monographs, New Series 24, Oxford Univ. Press,
2000.

\bibitem{Horvath}
B. Horvath,
\emph{When are full representations of algebras of operators on Banach spaces
automatically faithful?},
arXiv:1811.06865.

\bibitem{HK}
B. Horvath and T. Kania,
\emph{Surjective homomorphisms from algebras of operators on long sequence
spaces are automatically injective},
arXiv:2007.14112.

\bibitem{JPS}
W. B. Johnson, N. C. Phillips, and G. Schechtman,
\emph{The SHAI property for the operators on \(L^p\)},
arXiv:2102.03966.

\bibitem{KM}
K. Konstantos and P. Motakis,
\emph{Coordinate systems and distributional embeddings in
Bourgain--Rosenthal--Schechtman spaces: a framework for operator reduction},
arXiv:2510.24487.

\bibitem{Sampedro}
J. C. Sampedro,
\emph{Distributional embeddings of the first limit
Bourgain--Rosenthal--Schechtman space},
arXiv:2606.10260.

\end{thebibliography}

\end{document}
