\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Answer: Barycentric Spaces Have Sharp Metric Cotype}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-19}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.  Later literature
settles the sharp scaling-parameter problem for \(q\)-barycentric metric
spaces, but not for all finite-cotype Banach spaces.

\paragraph{Source question.}
Giladi--Mendel--Naor, \emph{Improved bounds in the metric cotype inequality
for Banach spaces}, arXiv:1003.0279, asks whether the metric cotype inequality
for every Banach space of Rademacher cotype \(q\) can be proved with the sharp
scaling parameter \(m\asymp n^{1/q}\).  Their Theorem 1 gives the general
bound \(m\lesssim n^{1+1/q}\), and the introduction identifies \(L_1\) and
the Schatten trace class \(S_1\) as basic open cotype-2 cases.

\paragraph{Supporting theorem.}
Eskenazis--Mendel--Naor, \emph{Nonpositive curvature is not coarsely
universal}, arXiv:1808.02179, proves Theorem ``\(q\)-barycentric implies sharp
metric cotype \(q\)''.  If \((X,d_X)\) is \(q\)-barycentric with constant
\(\beta\), then for every \(n\in\mathbb N\), every even \(m\), and every
\(f:\mathbb Z_{2m}^{n}\to X\),
\[
\left(\sum_{i=1}^n\sum_x d_X(f(x+me_i),f(x))^q\right)^{1/q}
\le (4n^{1/q}+\beta m)
\left(2^{-n}\sum_{\varepsilon\in\{-1,1\}^n}\sum_x
d_X(f(x+\varepsilon),f(x))^q\right)^{1/q}.
\]
Consequently, \(m\ge \beta^{-1}n^{1/q}\) gives metric cotype \(q\) with
constant \(\Gamma\lesssim\beta\), i.e. sharp scaling.  The same paper proves
that this sign-edge formulation is equivalent, up to universal constants, to
the original \(\ell_\infty\)-edge formulation used in arXiv:1003.0279.

\paragraph{Scope and limitations.}
This is a positive partial answer for \(q\)-barycentric targets, including
CAT(0)/Hadamard spaces and \(q\)-uniformly convex Banach spaces.  It is not a
solution of the main all-Banach problem: arXiv:1808.02179 explicitly states
that whether every Banach space of Rademacher cotype \(q\) has sharp metric
cotype \(q\) remains a fundamental open problem.  In particular, this packet
does not settle the highlighted \(L_1\) or \(S_1\) cases from arXiv:1003.0279.

\paragraph{Why this is an implication rather than an exact answer.}
The supporting paper is not framed as an answer to arXiv:1003.0279's all-Banach
question.  It cites the earlier metric-cotype framework, records the same
remaining Banach-space obstruction, and proves a sharp theorem for a different
structural class.  Thus the correct durable status is a literature-implied
partial subcase.

\paragraph{References.}
\begin{itemize}
\item O. Giladi, M. Mendel, and A. Naor, \emph{Improved bounds in the metric cotype inequality for Banach spaces}, arXiv:1003.0279.
\item A. Eskenazis, M. Mendel, and A. Naor, \emph{Nonpositive curvature is not coarsely universal}, arXiv:1808.02179.
\end{itemize}

\end{document}
