\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\newtheorem*{conjecture}{Source conjecture}
\newtheorem*{answer}{Later Theorem 4.1}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}

\title{Literature Status: The ccc Valdivia Dichotomy}
\author{Run \texttt{fa\_banach\_001} --- lane 5}
\date{22 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\textbf{Status: literature already answered (conditional negative answer).}
The conjecture in arXiv:1505.06727 is explicitly refuted under the Diamond
axiom by Theorem~4.1 of the separate paper arXiv:1512.02610. No new
mathematical result is claimed here.
}}
\end{center}

\section{Original conjecture}

C. Correa and D. V. Tausk, \emph{Nontrivial twisted sums of $c_0$ and
$C(K)$}, arXiv:1505.06727, pose the following unnumbered conjecture in
Section~4, arXiv PDF page~10~\cite{source}.

\begin{conjecture}
If $K$ is a nonempty Valdivia compact space having the countable chain
condition, then either $K$ has a $G_\delta$ point or $K$ admits a
nontrivial convergent sequence in the complement of a dense
$\Sigma$-subset.
\end{conjecture}

The source observes that, under the Continuum Hypothesis, this dichotomy
would yield nontrivial twisted sums of $c_0$ and $C(K)$ for every
nonmetrizable Valdivia compact space.

\section{Separate later answer}

The same authors subsequently wrote \emph{Small Valdivia compacta and
trees}, arXiv:1512.02610~\cite{answerpaper}. Its abstract and introduction
explicitly identify the construction as a counterexample to the conjecture
from the source. Theorem~4.1, on arXiv PDF pages~10--11, states:

\begin{answer}
Assume $\diamondsuit$. There exists a Valdivia compact space $K$ such that
\begin{enumerate}
\item $w(K)=\omega_1$;
\item $K$ has the countable chain condition;
\item $K$ has no $G_\delta$ points;
\item $K$ has no nontrivial convergent sequence in the complement of a
dense $\Sigma$-subset.
\end{enumerate}
\end{answer}

Items (2)--(4) are exactly the hypotheses and simultaneous failure of both
alternatives in the source conjecture. Thus the later theorem is an explicit
conditional counterexample, rather than an implication newly identified by
this run.

\clearpage
\null\vspace{0.15in}
\section{Scope and search status}

The answer is conditional on $\diamondsuit$, a principle consistent with
ZFC and stronger than CH. Consequently the original unrestricted conjecture
cannot be established as a theorem of ZFC, assuming the standard consistency
background. The theorem does not provide a counterexample constructed in ZFC.
Moreover, the supporting paper states that it does not know whether a
nontrivial twisted sum of $c_0$ and $C(K)$ exists for its counterexample;
that Banach-space question remains outside the scope of this status match.

The run registry and local arXiv corpus were searched for the source id,
exact conjecture wording, and the terms ``Valdivia'', ``ccc'',
``$G_\delta$ point'', and ``convergent sequence''. The decisive match was
then checked in arXiv:1512.02610, including its explicit cross-reference and
Theorem~4.1.

\begin{thebibliography}{9}
\bibitem{source}
C. Correa and D. V. Tausk,
\emph{Nontrivial twisted sums of $c_0$ and $C(K)$},
J. Funct. Anal. \textbf{270} (2016), 842--853;
arXiv:1505.06727.

\bibitem{answerpaper}
C. Correa and D. V. Tausk,
\emph{Small Valdivia compacta and trees},
Studia Math. \textbf{235} (2016), 117--135;
arXiv:1512.02610.
\end{thebibliography}

\end{document}
