\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for Two p-Free-Space Reductions in arXiv:2011.12993}
\author{Run fa\_banach\_001}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Source}

Fernando Albiac, Jose L. Ansorena, Marek Cuth, and Michal Doucha,
\emph{Lipschitz algebras and Lipschitz-free spaces over unbounded metric spaces},
arXiv:2011.12993.

The relevant source passages are Remark 2.8 and Remark 2.10. Remark 2.8 recalls
the open problem whether the canonical linearization
\[
L_j:\mathcal F_p(N)\longrightarrow \mathcal F_p(M)
\]
of an inclusion $j:N\subset M$ is an isomorphism for $0<p<1$, and notes that the
paper's bounded-space construction reduces the unbounded metric case to bounded
metric spaces. Remark 2.10 recalls the open problem whether
\[
E_{p,1,M}:\mathcal F_p(M)\longrightarrow \mathcal F(M)
\]
is one-to-one for every metric space $M$ and $0<p<1$, again reducing the issue to
bounded metric spaces.

\section*{Supporting Literature}

Fernando Albiac and Jose L. Ansorena,
\emph{Lipschitz extensions into p-Banach spaces, and canonical embeddings of
Lipschitz-free p-spaces for $0<p<1$}, arXiv:2603.28193.

The abstract states that inclusions of $p$-metric spaces always induce genuine
linear embeddings of Lipschitz-free $p$-spaces, and that the natural envelope map
from $\mathcal F_p(M)$ to its $q$-Banach envelope $\mathcal F_q(M)$ is one-to-one
for $0<p<q\le 1$.

\section*{Identification}

The source's two reductions are answered by stronger later theorems:

\begin{itemize}
\item Theorem 3.13 of arXiv:2603.28193 proves that for every $0<p\le 1$ there is
a constant $C(p)$ such that, for every pointed $p$-metric space $M$ and every
$0\in N\subset M$, the canonical map
$L[N,M;p]:\mathcal F_p(N)\to\mathcal F_p(M)$ is an isomorphic embedding.

\item The final theorem of arXiv:2603.28193 proves that for every
$0<p\le q\le 1$ and every pointed $q$-metric space $M$, the canonical envelope map
$J_{p,q}[M]$ is one-to-one. Taking $q=1$ gives the injectivity of
$E_{p,1,M}:\mathcal F_p(M)\to\mathcal F(M)$ asked about in the source.
\end{itemize}

\section*{Status}

This is a literature-implied answer for arXiv:2011.12993: the later theorem
solves, in stronger generality, the two older open problems whose unbounded-to-
bounded reductions are recorded in the source paper. It is not a new proof
packet. The first item overlaps the existing run packet
\texttt{1811.01265\_canonical\_free\_p\_embedding\_answered\_2603.28193}; this
packet is included to clear arXiv:2011.12993's own queue signal.

\end{document}

