\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\newcommand{\F}{\mathcal F}
\newcommand{\N}{\mathbb N}
\newcommand{\Lip}{\operatorname{Lip}_0}
\newcommand{\dist}{\operatorname{dist}}

\title{A Three-Isomorphism From the Prochazka--Sanchez Free Space to \texorpdfstring{$\ell_1$}{ell1}}
\author{Run \texttt{fa\_banach\_001}, lane 17}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Status}

This is a partial result for the metric space \(M\) introduced by
Prochazka and Sanchez-Gonzalez in \cite{PSG}.  It improves the upper
bound recorded in the source paper for the Banach--Mazur distance
between \(\F(M)\) and \(\ell_1\), but it does not determine the exact
constant.

\section*{Source Question}

Let
\[
M=\{\emptyset\}\cup \N \cup F,\qquad
F=\{A\subset \N:1\le |A|<\infty\},
\]
with graph edges \(\emptyset\sim n\) for \(n\in\N\), and \(n\sim A\)
whenever \(n\in A\).  The corresponding shortest-path metric satisfies
\[
d(\emptyset,n)=1,\quad d(\emptyset,A)=2,\quad d(n,m)=2,
\]
\[
d(n,A)=1 \text{ if }n\in A,\quad d(n,A)=3\text{ if }n\notin A,
\]
and
\[
d(A,B)=2 \text{ if }A\cap B\ne\emptyset,\qquad
d(A,B)=4 \text{ if }A\cap B=\emptyset.
\]
The source paper proves that \(M\) does not embed into any \(L_1(\mu)\)
with distortion strictly less than \(2\), but that \(\F(M)\) is
isomorphic to \(\ell_1\).  It then asks whether
\[
d_{BM}(\F(M),\ell_1)=2.
\]
The paper's argument gives only \(d_{BM}(\F(M),\ell_1)\le 4\), while
the \(L_1\)-distortion obstruction gives \(d_{BM}(\F(M),\ell_1)\ge 2\).

\section*{Proof Intuition}

The usual proof that a bounded uniformly discrete countable metric
space has free space isomorphic to \(\ell_1\) sends every non-basepoint
Dirac mass to an unweighted unit vector.  For this particular \(M\),
that loses a factor \(2\) on the points \(A\in F\), because
\(\|\delta_A\|_{\F(M)}=d(A,\emptyset)=2\).  Rescaling just those
coordinates by \(2\) removes that loss.  The only remaining expensive
pairs are incident pairs \(n\in A\), where the image distance is
\(\|e_n-2e_A\|_1=3\) although \(d(n,A)=1\).

\begin{theorem}
For the metric space \(M\) above,
\[
2\le d_{BM}(\F(M),\ell_1)\le 3.
\]
\end{theorem}

\begin{proof}
The lower bound is due to \cite{PSG}.  Indeed, if
\(S:\F(M)\to \ell_1\) were an isomorphism with
\(\|S\|\,\|S^{-1}\|<2\), then \(x\mapsto S\delta_x\) would be a
bi-Lipschitz embedding of \(M\) into \(\ell_1\) with distortion
strictly less than \(2\).  This contradicts Corollary 3 of \cite{PSG},
which says that \(M\) does not embed into any \(L_1(\mu)\) with
distortion \(<2\).

For the upper bound, let \(E=\N\sqcup F\), and identify
\(\ell_1(E)\) with the \(\ell_1\)-sum of the singleton coordinates and
the finite-subset coordinates.  Define \(f:M\to \ell_1(E)\) by
\[
f(\emptyset)=0,\qquad f(n)=e_n\quad(n\in\N),\qquad f(A)=2e_A\quad(A\in F).
\]
The universal property of the Lipschitz-free space gives a unique
bounded linear operator \(T:\F(M)\to \ell_1(E)\) with
\(T\delta_x=f(x)\), and \(\|T\|=\operatorname{Lip}(f)\).

We compute the Lipschitz constant from the displayed distance table.
For pairs involving \(\emptyset\),
\[
\frac{\|f(n)\|_1}{d(\emptyset,n)}=1,\qquad
\frac{\|f(A)\|_1}{d(\emptyset,A)}=\frac{2}{2}=1.
\]
For two distinct singleton points,
\[
\frac{\|e_n-e_m\|_1}{d(n,m)}=\frac{2}{2}=1.
\]
For \(n\in\N\) and \(A\in F\),
\[
\|f(n)-f(A)\|_1=\|e_n-2e_A\|_1=3.
\]
Thus the quotient by \(d(n,A)\) is \(3\) when \(n\in A\), and \(1\)
when \(n\notin A\).  Finally, for \(A\ne B\) in \(F\),
\[
\|f(A)-f(B)\|_1=\|2e_A-2e_B\|_1=4,
\]
so the quotient is \(2\) if \(A\cap B\ne\emptyset\) and \(1\) if
\(A\cap B=\emptyset\).  Hence \(\|T\|\le 3\).

The map is onto \(\ell_1(E)\).  Its inverse on the canonical basis is
\[
T^{-1}e_n=\delta_n,\qquad T^{-1}e_A=\frac12\delta_A.
\]
Since \(\|\delta_n\|_{\F(M)}=1\) and \(\|\delta_A\|_{\F(M)}=2\), the
operator \(T^{-1}:\ell_1(E)\to \F(M)\) has norm at most \(1\), because
the unit ball of \(\ell_1(E)\) is the closed convex hull of the signed
coordinate vectors.  Therefore
\[
\|T\|\,\|T^{-1}\|\le 3,
\]
which proves the upper bound.
\end{proof}

\section*{Verification Notes And Failed Full-Closure Routes}

The diagonal family \(T_{s,t}\delta_n=s e_n\), \(T_{s,t}\delta_A=t e_A\)
cannot improve the constant \(3\).  Its distortion is
\[
\max\{s+t,t, s\}\cdot \max\{s^{-1},2t^{-1}\},
\]
and the minimum over \(s,t>0\) is attained at \(t=2s\), giving \(3\).
Thus any proof of the conjectural value \(2\), if true, must use a
substantially non-diagonal representation.

Finite \(L_1\)-cut LPs were run for the truncations
\[
M_n=\{\emptyset\}\cup\{1,\dots,n\}\cup
\{A\subset\{1,\dots,n\}:A\ne\emptyset\}.
\]
They gave optimal \(L_1\)-metric distortions \(1\) for \(n=2\),
\(4/3\) for \(n=3\), and approximately \(1.4615384615\) for \(n=4\)
using a symmetry-reduced cut cone.  These computations are consistent
with the source paper's asymptotic lower bound \(2\), but they do not
prove a Banach--Mazur lower bound above \(2\) for \(\F(M)\).

\section*{Novelty Check}

Local run indexes were searched for arXiv:1311.4584, the title, and
the phrases ``Banach--Mazur distance'', ``Prochazka Sanchez-Gonzalez'',
``Lipschitz-free'', and ``\(\ell_1\)''.  No exact prior packet was
found.  Web searches on 2026-06-20 for the exact source question and
nearby phrases found the source paper \cite{PSG}, the Dalet--Kaufmann--
Prochazka isometric characterization for tree metrics \cite{DKP}, and
the Aliaga--Petitjean--Prochazka embedding theorem for free spaces over
subsets of real trees \cite{APP}.  Those later tree results do not
directly apply to the present graph metric, which is not a tree metric.

\section*{Human Review Recommendation}

The proof of the upper bound is elementary and should be quick to
verify.  The packet should be reviewed as a genuine but modest partial
improvement, not as a solution of the exact-distance problem.

\begin{thebibliography}{9}
\bibitem{PSG}
A. Prochazka and L. Sanchez-Gonzalez,
\emph{Low distortion embeddings into Asplund Banach spaces},
arXiv:1311.4584.

\bibitem{DKP}
A. Dalet, P. L. Kaufmann, and A. Prochazka,
\emph{Characterization of metric spaces whose free space is isometric to \(\ell_1\)},
arXiv:1502.02719.

\bibitem{APP}
R. J. Aliaga, C. Petitjean, and A. Prochazka,
\emph{Embeddings of Lipschitz-free spaces into \(\ell_1\)},
arXiv:1909.05285.
\end{thebibliography}

\end{document}
