\documentclass[11pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,mathrsfs}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\begin{document}

\title{Schur Tensor Preservation Answers a Dunford--Pettis Tensor Question}
\author{Run fa\_banach\_001}
\date{2026-06-16}
\maketitle

\noindent
\textbf{Status.} \texttt{literature\_already\_answered}. This is not a new
proof. It records that a later theorem of Rodriguez answers the final tensor
square questions in Gonzalez--Gutierrez arXiv:math/0004101.

\section*{Source Question}

Gonzalez--Gutierrez, \emph{The Dunford-Pettis property on tensor products},
arXiv:math/0004101, consider an infinite-dimensional separable
\(\mathscr L_\infty\)-space \(X\) with the Schur property such that
\(X^*\) is isomorphic to \(C[0,1]^*\). In the final `Questions' environment,
labelled \texttt{qq} in the source, they ask whether
\[
  X\widehat\otimes_\pi X
\]
has the Schur property, and whether it has the Dunford--Pettis property.

\section*{Supporting Answer}

Rodriguez, \emph{On weak compactness in projective tensor products},
arXiv:2206.08651, explicitly cites the Schur-preservation problem for
projective tensor products as open, citing Gonzalez--Gutierrez among the
sources. Immediately afterward, Theorem \texttt{theo:Schur} states:
\[
  \text{if } X \text{ and } Y \text{ have the Schur property, then so does }
  X\widehat\otimes_\pi Y.
\]

Applying this theorem with \(Y=X\) gives that the source paper's
Bourgain--Delbaen space satisfies that \(X\widehat\otimes_\pi X\) has the
Schur property. Since every Banach space with the Schur property has the
Dunford--Pettis property, \(X\widehat\otimes_\pi X\) also has the
Dunford--Pettis property.

\section*{Scope}

This answers the two final questions in arXiv:math/0004101 for the specified
Schur \(\mathscr L_\infty\)-space \(X\): both answers are affirmative. The
packet does not claim a new proof and does not address other unrelated
Dunford--Pettis tensor-product problems from the source paper.

\section*{Search and Provenance Notes}

The run indexes were searched for arXiv:math/0004101 and phrases around the
Dunford--Pettis property, projective tensor products, injective tensor
products, and Schur tensor preservation. No existing packet for the exact
source question was found. A relevant conditional packet for arXiv:1504.00520
uses a hypothetical negative answer to Schur tensor preservation as a
dependency; Rodriguez's theorem gives the positive general preservation
result, so that negative route is no longer viable.

\begin{thebibliography}{9}

\bibitem{GG2001}
M. Gonzalez and J. M. Gutierrez,
\emph{The Dunford-Pettis property on tensor products},
arXiv:math/0004101.

\bibitem{Rodriguez2022}
J. Rodriguez,
\emph{On weak compactness in projective tensor products},
arXiv:2206.08651.

\end{thebibliography}

\end{document}
