\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Literature status for arXiv:0809.2723, Question 7.5}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-14}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight \texttt{literature\_already\_answered} packet. It records
that Question 7.5 from Avilés, Kadets, Martín, Merí, and Shepelska,
\emph{Slicely Countably Determined Banach spaces}, arXiv:0809.2723, was
explicitly answered in later literature by Kadets, Pérez, and Werner,
\emph{Operations with slicely countably determined sets}, arXiv:1708.05218.

\section*{Source question}

Question 7.5 of arXiv:0809.2723 appears on page 27 of the source PDF and at
TeX source lines 2425--2428:
\[
\text{Are the concepts of SCD sets and almost-SCD sets equivalent?}
\]
The question refers to Remark 4.5 of the same source paper for the definition
of almost-SCD.

\section*{Supporting answer}

The supporting paper explicitly cites the source question as
\cite[Question 7.5]{KPW} and states in its introduction that the properties
aSCD and SCD are not equivalent for general bounded closed convex sets. The
negative answer is given by \cite[Theorem 4.3]{KPW}: if \(X\) is a Banach
space with the Daugavet property, then there exists a convex closed bounded
set \(\widetilde C\subset X\) which is aSCD but not SCD.

The same paper also proves the balanced-set refinement
\cite[Theorem 4.5]{KPW}: every convex closed bounded balanced aSCD set is
SCD. Thus Question 7.5 is answered negatively in general, while the balanced
case relevant to many unit-ball applications has a positive answer.

\section*{Scope and novelty}

This packet records an exact later-literature answer, not a new proof from the
run. Local duplicate checks over the run registry, solution, attempt, and
proof-gap indexes found no existing packet for arXiv:0809.2723 /
arXiv:1708.05218 or the almost-SCD/aSCD question.

\begin{thebibliography}{9}

\bibitem{AKMMS}
A. Avilés, V. Kadets, M. Martín, J. Merí, and V. Shepelska,
\emph{Slicely Countably Determined Banach spaces},
arXiv:0809.2723.

\bibitem{KPW}
V. Kadets, A. Pérez, and D. Werner,
\emph{Operations with slicely countably determined sets},
arXiv:1708.05218.

\end{thebibliography}

\end{document}
