\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\newcommand{\Ext}{\operatorname{Ext}}

\title{Literature-Implied Partial Subcase for arXiv:math/0410256}
\author{fa\_banach\_001 agent note}
\date{2026-06-19}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature-implied answer, partial subcase.

The source paper is J. M. F. Castillo and Y. Moreno,
\emph{Extensions by spaces of continuous functions}, arXiv:math/0410256.
In Section 4, item 6, the authors ask whether
\[
  \Ext(M,C[0,1])=0
\]
for every subspace \(M\) of \(\ell_1\).

The supporting paper is N. J. Kalton,
\emph{On subspaces of \(c_0\) and extension of operators into \(C(K)\)-spaces},
arXiv:math/9911144.

\section*{Recorded Subcase}

Let \(M\) be a closed subspace of \(\ell_1\).  If \(M\) has an unconditional
finite-dimensional decomposition, then
\[
  \Ext(M,C(K))=0
\]
for every compact Hausdorff space \(K\).  In particular,
\[
  \Ext(M,C[0,1])=0.
\]
By Castillo--Moreno's main theorem, such an \(M\) also admits a fully
\(w^\ast\)-continuous scalar metric projection \(Z(M,\mathbb R)\to M'\).

\section*{Identification}

Kalton proves that a separable Banach space with a UFDD and the very strong
Schur property is isomorphic to the dual of a subspace of \(c_0\).  This is
Theorem 5.3 in the arXiv PDF.  A closed subspace of \(\ell_1\) inherits the
strong Schur property from \(\ell_1\).  Kalton also records that, for closed
subspaces of \(L_1\), the strong Schur property is equivalent to the very
strong Schur property.  Therefore a UFDD subspace \(M\subset \ell_1\) is
isomorphic to the dual of a subspace of \(c_0\).

Johnson--Zippin's extension theorem, recalled in both the source paper and
Kalton's paper, says that spaces isomorphic to duals of subspaces of \(c_0\)
satisfy \(\Ext(X,C(K))=0\) for every compact \(K\).  Applying this theorem to
the \(M\) above gives the stated subcase.

\section*{Scope and Remaining Problem}

This is not a full solution of Castillo--Moreno's question.  It covers the
UFDD branch of the subspace-of-\(\ell_1\) problem.  The arbitrary closed
subspace case remains open from the searches performed here, as does the broad
question about metric projections continuous at zero for all spaces with
\(\Ext(X,c_0)=0\).

\section*{References}

\begin{itemize}
\item J. M. F. Castillo and Y. Moreno, \emph{Extensions by spaces of continuous
functions}, arXiv:math/0410256.
\item N. J. Kalton, \emph{On subspaces of \(c_0\) and extension of operators
into \(C(K)\)-spaces}, arXiv:math/9911144.
\item W. B. Johnson and M. Zippin, \emph{Extension of operators from
weak*-closed subspaces of \(l_1\) into \(C(K)\) spaces}, Studia Math. 117
(1995), 43--55.
\end{itemize}

\end{document}
