\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\starpre}{_\ast}
\newcommand{\weakstar}{\mathrm{w}^\ast}

\title{A Central Finite-Trace Case of Semifinite Liftability}
\author{Run fa\_banach\_001}
\date{2026-07-18}

\begin{document}
\maketitle

\paragraph{Status.}
This packet records a likely valid partial result for the question in
Y. Ueda, \emph{On the predual of non-commutative \(H^\infty\)},
arXiv:1002.3672:
\[
\texttt{partial\_result\_likely\_valid.}
\]

\paragraph{Source question.}
Ueda proves that for a finite tracial non-commutative \(H^\infty\)-algebra
\(A=H^\infty(M,\tau)\), every weakly relatively compact subset of
\(M_\ast/A_\perp\) has weakly relatively compact unique normal Hahn--Banach
extensions in \(M_\ast\).  In Section 3.1, after proving the basic
semifinite prerequisites, the paper asks whether this liftability survives in
the semifinite tracial setting.

\paragraph{Partial answer.}
The answer is positive when the semifinite algebra is a countable central
sum of finite-trace pieces.  This includes precisely the case where the
semifinite difficulty is only an \(\ell^\infty\)-direct-sum bookkeeping issue,
not a noncentral or continuous exhaustion issue.

\paragraph{Proof Intuition.}
Central finite projections split both the von Neumann algebra and the
subdiagonal algebra into independent finite summands.  On each summand,
Ueda's finite theorem gives the desired liftability.  The only remaining
point is to assemble the pieces.  Weak compactness in an \(\ell^1\)-sum is
controlled by two conditions: coordinatewise weak compactness and uniformly
small \(\ell^1\)-tails.  The coordinate extension maps preserve norms, so the
tail condition is unchanged by lifting.

\begin{lemma}[\(\ell^1\)-sum weak compactness criterion]
Let \(X_n\) be Banach spaces and \(X=(\oplus_{n=1}^\infty X_n)_1\).  A bounded
set \(K\subset X\) is relatively weakly compact if and only if:
\begin{enumerate}
\item for every \(n\), the coordinate set \(\pi_n K\) is relatively weakly
compact in \(X_n\);
\item \(\displaystyle \lim_{N\to\infty}\sup_{x\in K}\sum_{n>N}\|x_n\|=0\).
\end{enumerate}
\end{lemma}

\begin{proof}
The coordinate condition follows from continuity of \(\pi_n\).  For the tail
condition, if it failed, choose \(x^{(N)}\in K\) with tail after \(N\) at least
\(\varepsilon>0\), and choose norm-one functionals supported on that tail
which almost attain the tail norm.  These functionals are weak-star null in
\(X^\ast=(\oplus_n X_n^\ast)_\infty\), contradicting uniform convergence on
weakly compact subsets.

Conversely, take any sequence in \(K\).  By the coordinate weak compactness
and a diagonal extraction, pass to a subsequence whose every coordinate
converges weakly.  The uniform tail condition then shows that the coordinate
limits form an element of \(X\), and testing first on finitely many coordinates
and then using the small tails gives weak convergence in \(X\).  The
Eberlein--Smulian theorem completes the proof.
\end{proof}

\begin{theorem}[Central finite-trace liftability]
Let \(M\) be a sigma-finite von Neumann algebra with faithful normal
semifinite trace \(\operatorname{Tr}\), and let
\[
A=H^\infty(M,\operatorname{Tr})
\]
be a semifinite tracial non-commutative \(H^\infty\)-algebra.  Suppose that
there are mutually orthogonal central projections \(z_n\in D=A\cap A^\ast\)
such that \(\sum_n z_n=1\) strongly and \(0<\operatorname{Tr}(z_n)<\infty\)
for all nonzero \(z_n\).  Then every weakly relatively compact subset
\[
W\subset M_\ast/A_\perp
\]
has weakly relatively compact unique normal Hahn--Banach extensions in
\(M_\ast\).
\end{theorem}

\begin{proof}
Set \(M_n=z_nM\), \(A_n=z_nA\), and normalize the finite trace on \(M_n\) by
\[
\tau_n(x)=\operatorname{Tr}(z_n)^{-1}\operatorname{Tr}(x),\qquad x\in M_n.
\]
Since \(z_n\) is central and lies in \(D\), the conditional expectation for
\(A\) restricts to the conditional expectation for \(A_n\), and each
\[
A_n=H^\infty(M_n,\tau_n)
\]
is a finite tracial non-commutative \(H^\infty\)-algebra.

The central decomposition gives
\[
M=\bigoplus_{n=1}^{\infty}{}^{\ell^\infty} M_n,\qquad
M_\ast=\bigoplus_{n=1}^{\infty}{}^{\ell^1} (M_n)_\ast,
\]
and similarly
\[
A=\bigoplus_{n=1}^{\infty}{}^{\ell^\infty} A_n,\qquad
A_\perp=\bigoplus_{n=1}^{\infty}{}^{\ell^1} (A_n)_\perp.
\]
Hence the quotient isometrically identifies with
\[
M_\ast/A_\perp
\cong
\bigoplus_{n=1}^{\infty}{}^{\ell^1}
\big((M_n)_\ast/(A_n)_\perp\big).
\]
Indeed, the quotient norm separates coordinatewise:
\[
\inf_{\eta\in A_\perp}\sum_n \|\rho_n+\eta_n\|
=
\sum_n \inf_{\eta_n\in(A_n)_\perp}\|\rho_n+\eta_n\|.
\]

Let \(X_n=(M_n)_\ast/(A_n)_\perp\) and \(Y_n=(M_n)_\ast\).  For each \(n\),
Ueda's finite theorem says that the unique normal Hahn--Banach extension map
\[
S_n:X_n\to Y_n
\]
sends relatively weakly compact subsets of \(X_n\) to relatively weakly
compact subsets of \(Y_n\).  It is also isometric:
\[
\|S_n x_n\|=\|x_n\|_{X_n}.
\]

Let \(W\subset(\oplus_n X_n)_1\) be relatively weakly compact.  By the lemma,
each coordinate set \(\pi_n W\) is relatively weakly compact and
\[
\lim_{N\to\infty}\sup_{x\in W}\sum_{n>N}\|x_n\|=0.
\]
Therefore \(S_n(\pi_n W)\) is relatively weakly compact in \(Y_n\) for every
\(n\), and the lifted set
\[
S(W)=\{(S_nx_n)_n:x=(x_n)_n\in W\}\subset(\oplus_nY_n)_1
\]
has the same tails:
\[
\sum_{n>N}\|S_nx_n\|=\sum_{n>N}\|x_n\|.
\]
Applying the lemma again in the \(\ell^1\)-sum of the \(Y_n\)'s shows that
\(S(W)\) is relatively weakly compact in \(M_\ast\).

Finally, \(S(W)\) is exactly the set of unique normal Hahn--Banach extensions
to \(M\).  Coordinatewise uniqueness gives uniqueness on the
\(\ell^\infty\)-sum, and the norm equality above gives the required
norm-preserving extension.  This proves the claimed liftability.
\end{proof}

\paragraph{Verification Notes.}
The proof uses only Ueda's finite liftability theorem, the central direct-sum
identification, and the standard weak compactness criterion for \(\ell^1\)
sums.  No computation is involved.  The most important point for human review
is the quotient identification
\[
M_\ast/A_\perp\cong\bigoplus_1 (M_n)_\ast/(A_n)_\perp,
\]
which uses centrality of the projections \(z_n\).

\paragraph{Limitations.}
This is not a full solution to Ueda's semifinite question.  The argument does
not cover increasing noncentral finite projections \(p_m\in D\), continuous
central decompositions, semifinite factors such as \(B(\ell^2)\) with its
usual trace unless \(A=M\) trivially, or not-necessarily-tracial
non-commutative \(H^\infty\)-algebras.

\paragraph{Novelty Check.}
Before promotion, the run checked the lightweight indexes for arXiv:1002.3672
and the phrases ``predual of non-commutative \(H^\infty\)'',
``weakly relatively compact'', ``semifinite'', and ``liftability''.  A web
search on the exact liftability and semifinite phrases found the source paper
and metadata pages, but no later exact resolution of the semifinite
liftability question.  This packet should therefore be treated as a narrow
partial theorem, not as a known full literature answer.

\paragraph{Human Review Recommendation.}
Likely valid partial result.  Review should focus on the direct-sum quotient
identification and on whether the central-decomposition hypothesis is stated
in the cleanest natural form.

\paragraph{References.}
\begin{itemize}
\item Y. Ueda, \emph{On the predual of non-commutative \(H^\infty\)},
arXiv:1002.3672; Bull. London Math. Soc. 43 (2011), 886--896.
\end{itemize}

\end{document}
