\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Lip}{\operatorname{Lip}}

\begin{document}

\begin{center}
{\Large Literature-implied answer: local complementation vs. Lipschitz retraction}\\[0.5em]
{\large arXiv:2107.11339}
\end{center}

\paragraph{Status.}
\textbf{Literature-implied answer (nonseparable negative; separable case
open).}

\paragraph{Source question.}
In the Introduction of Aviles--Martinez-Cervantes--Rueda Zoca,
\emph{Local complementation in Banach spaces and its preservation under free
constructions}, arXiv:2107.11339, page 2, the authors recall an open problem
posed by Kalton: whether local complementation of a subspace \(Y\subset X\) is
equivalent to the existence of a Lipschitz retraction \(r:X\to Y\).

\paragraph{Identification.}
The broad formulation, with no separability restriction, has a negative answer
by combining two standard facts.  First, by the principle of local reflexivity,
every Banach space \(E\) is locally \(1\)-complemented in its bidual
\(E^{**}\).  Second, Kalton constructed a nonseparable Banach space \(E\) which
is not a Lipschitz retract of \(E^{**}\); this is recorded explicitly in
Quilis--Rueda Zoca, arXiv:2311.13289, page 4, where the authors use it with
local reflexivity to produce a Banach-space local-retract example that is not a
Lipschitz retract.  Therefore \(E\subset E^{**}\) is locally complemented but
there is no Lipschitz retraction \(E^{**}\to E\).

\paragraph{Related reduction and remaining open part.}
Hajek--Quilis, arXiv:2106.13554, page 4, state the useful reduction: a closed
linear subspace \(Y\) locally complemented in a Banach space \(X\) is a
Lipschitz retract of \(X\) if and only if \(Y\) is a Lipschitz retract of its
bidual \(Y^{**}\).  The same passage notes that the corresponding separable
bidual-retraction problem remains open.  Thus the nonseparable broad form of
the problem quoted in arXiv:2107.11339 is answered negatively, while the
separable Lindenstrauss/Benyamini--Lindenstrauss form remains open.

\paragraph{Provenance.}
This is an agent-identified implication, not an original proof and not an
explicit answer claimed by the source authors.  The run already has a separate
attempt note for the separable bidual-retraction problem under arXiv:1606.03926.

\paragraph{References.}
\begin{itemize}
  \item A. Aviles, G. Martinez-Cervantes, A. Rueda Zoca,
  \emph{Local complementation in Banach spaces and its preservation under free
  constructions}, arXiv:2107.11339.
  \item P. Hajek, A. Quilis, \emph{Lipschitz retractions and complementation
  properties of Banach spaces}, arXiv:2106.13554.
  \item A. Quilis, A. Rueda Zoca, \emph{(Almost isometric) local retracts in
  metric spaces}, arXiv:2311.13289.
  \item N. J. Kalton, \emph{Lipschitz and uniform embeddings into
  \(\ell_\infty\)}, Fund. Math. 212 (2011), 53--69.
\end{itemize}

\end{document}
