\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status for arXiv:1504.04202: Ascoli Free Locally Convex Spaces}
\author{Run fa\_banach\_001, agent\_lane\_04}
\date{2026-06-23}

\newcommand{\KR}{k_{\mathbb R}}
\newcommand{\CC}{C_k}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet. It records that the
free locally convex space question in the final section of Gabriyelyan--Kakol--
Plebanek, \emph{The Ascoli property for function spaces and the weak topology
of Banach and Frechet spaces}, arXiv:1504.04202, was answered by Gabriyelyan,
\emph{On reflexivity and the Ascoli property for free locally convex spaces},
arXiv:1805.07028.

\section*{Source Question}

The final section of arXiv:1504.04202, titled ``Proof of Theorem
\texttt{t:Ascoli-E-weak} and final questions'' in the source file, asks the
following two questions relevant to free locally convex spaces:
\[
  \text{If } L(X) \text{ is Ascoli, is } X \text{ Ascoli?}
\]
This is the \(L(X)\)-case of the question labelled
\texttt{q:Ascoli-Free} in the source TeX, which also asks the analogous
questions for the free and free abelian topological groups \(F(X)\) and
\(A(X)\).

The same final section then asks the sharper question labelled
\texttt{q:Ascoli-Free-Discr}:
\[
  \text{If } L(X) \text{ is Ascoli, is } X \text{ countable and discrete?}
\]
The source adds that this was not known even under the stronger assumption
that \(L(X)\) is a \(\KR\)-space.

\section*{Supporting Answer}

The abstract of arXiv:1805.07028 states that, answering a question posed in
the GKP paper, it proves that \(L(X)\) is Ascoli if and only if \(X\) is a
countable discrete space. In the introduction the supporting paper repeats the
exact question, citing GKP, and then states Theorem~1.2:
\[
  \text{For a Tychonoff space } X,\quad
  L(X) \text{ is Ascoli if and only if } X \text{ is countable discrete.}
\]
This is precisely the affirmative answer to \texttt{q:Ascoli-Free-Discr}.
Since every countable discrete space is Ascoli, it also gives an affirmative
answer to the \(L(X)\)-branch of \texttt{q:Ascoli-Free}. The supporting authors
explicitly identify the result as answering the GKP question.

\section*{Scope}

This packet records an already-known answer for the free locally convex space
\(L(X)\). It does not answer the \(F(X)\) or \(A(X)\) branches of
\texttt{q:Ascoli-Free}, and it does not address the separate question
\texttt{q:Ascoli-Free-F} asking for which metrizable spaces the groups
\(F(X)\) and \(A(X)\) are Ascoli.

The theorem also implies the stronger \(\KR\)-variant mentioned after the
source question in the following direction: if \(L(X)\) is a \(\KR\)-space,
then \(L(X)\) is Ascoli, hence \(X\) is countable discrete by Theorem~1.2.

\section*{Search Evidence}

The lane-1 deterministic queue selected arXiv:1504.04202. The cheap run
indexes were searched for the arXiv id, title words, \texttt{Ascoli property},
\texttt{function spaces}, \texttt{free locally convex}, \texttt{L(X)}, and
\texttt{Question 3.6}; no duplicate packet for this target was found. Local
source searches for \texttt{L(X) Ascoli}, \texttt{free locally convex Ascoli},
and \texttt{question posed in GKP} identified arXiv:1805.07028 as the decisive
later paper.

\begin{thebibliography}{9}
\bibitem{GKP}
S.~Gabriyelyan, J.~Kakol, and G.~Plebanek,
\emph{The Ascoli property for function spaces and the weak topology of Banach
and Frechet spaces},
arXiv:1504.04202.

\bibitem{Gab18}
S.~Gabriyelyan,
\emph{On reflexivity and the Ascoli property for free locally convex spaces},
arXiv:1805.07028.
\end{thebibliography}

\end{document}
