\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Holder}{H\"older}
\newcommand{\WH}{weakly \Holder}

\title{Literature Status: Two Hatami Graph-Norm Questions}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 28, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \textbf{literature\_already\_answered} packet. It records that two
questions in the concluding remarks of Hatami's
\emph{Graph norms and Sidorenko's conjecture}, arXiv:0806.0047, were later
answered in the graph-norm literature. It is not a new proof packet.

\section*{Source Questions}

Hatami defines \Holder{} and \WH{} bipartite graphs in Section 2.2. Theorem 2.9
of the source paper identifies these analytic inequalities with norm
properties:
\[
  H \text{ is \Holder} \Longleftrightarrow \|\cdot\|_H
  \text{ is always a seminorm},
\]
and
\[
  H \text{ is \WH} \Longleftrightarrow \|\cdot\|_{r(H)}
  \text{ is always a norm}.
\]
In later terminology these are the norming and weakly norming graph
properties.

The concluding remarks ask, among other questions:
\begin{quote}
Is there any edge transitive bipartite graph that is not weakly \Holder?
\end{quote}
and
\begin{quote}
Prove or disprove that hypercubes are \Holder.
\end{quote}

\section*{Edge-Transitive Weakly \Holder{} Graphs}

The supporting paper
\begin{quote}
Roman Kr\'al, Ta Sheng Noel Sandeep, Jan Volec, and Fan Wei,
\emph{The step Sidorenko property and non-norming edge-transitive graphs},
arXiv:1802.05007; J. Combin. Theory Ser. A 162 (2019), 34--54
\end{quote}
explicitly states in its abstract and introduction that it shows the existence
of a bipartite edge-transitive graph that is not weakly norming, answering a
question of Hatami. The paper proves that most toroidal grids, including
edge-transitive Cartesian products such as \(C_n \square C_n\) outside the
exceptional cases described there, are not weakly norming.

Thus Hatami's question has a positive existence answer: there are
edge-transitive bipartite graphs that are not weakly \Holder.

\section*{Hypercubes}

The supporting paper
\begin{quote}
Joonkyung Lee and Alexander Sidorenko,
\emph{On graph norms for complex-valued functions}, arXiv:2101.12145;
J. London Math. Soc. 106 (2022), 1507--1538
\end{quote}
states that Hatami proposed six open problems about graph norms and that it
answers the last remaining one, namely whether the hypercubes, already known
from Hatami's work to be weakly norming, are norming. Its Theorem 1.4 states:
\[
  Q_d \text{ is not norming whenever } d>2.
\]

Consequently Hatami's question whether hypercubes are \Holder{} has a negative
answer in every dimension \(d>2\).

\section*{Scope}

This packet does not address the general Sidorenko conjecture. It also does
not settle the other concluding questions from arXiv:0806.0047, including the
hypergraph version of the framework, the weakly \Holder{} status of
\(K_2 \square C_6\), the graph obtained from \(K_{5,5}\) by deleting a
Hamiltonian cycle, or the moduli of smoothness and convexity of \(r(H)\).

\section*{Search Evidence}

Local cheap indexes were searched for arXiv:0806.0047, the source title,
``Sidorenko'', ``graph norm'', ``weakly norming'', ``norming'', ``Holder'', and
``weakly Holder''. No exact prior packet for these two Hatami questions was
found at reservation time. The answer classification is based on the primary
supporting arXiv papers listed above, both of which explicitly connect their
results to Hatami's 2010 graph-norm questions.

\begin{thebibliography}{9}

\bibitem{Hatami}
H. Hatami,
\emph{Graph norms and Sidorenko's conjecture},
Israel J. Math. 175 (2010), 125--150; arXiv:0806.0047.

\bibitem{KMPW}
R. Kr\'al, T. S. N. Sandeep, J. Volec, and F. Wei,
\emph{The step Sidorenko property and non-norming edge-transitive graphs},
J. Combin. Theory Ser. A 162 (2019), 34--54; arXiv:1802.05007.

\bibitem{LS}
J. Lee and A. Sidorenko,
\emph{On graph norms for complex-valued functions},
J. London Math. Soc. 106 (2022), 1507--1538; arXiv:2101.12145.

\end{thebibliography}

\end{document}
