\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newcommand{\ellp}{\ell^p}
\newcommand{\elltwo}{\ell^2}
\newcommand{\Int}{\operatorname{Int}}

\title{Status note: the Levitina--Sukochev--Zanin sequence-space conjecture}
\author{fa\_banach\_001 literature-status packet}
\date{2026-06-19}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{Literature already answered.}  This packet does not claim a new
proof.  It records that the conjecture extracted from arXiv:1812.03861 is
answered explicitly by a later paper.

\paragraph{Source question.}
The source paper is Leonard Cadilhac, \emph{Majorization, Interpolation and
noncommutative Khintchine inequalities}, arXiv:1812.03861.  In the
introduction, a conjecture labeled Levitina--Sukochev--Zanin quotes the
Levitina--Sukochev--Zanin conjecture:
\begin{quote}
Let \(E\) be a quasi-Banach symmetric sequence space.  Then \(E\) is
right-\(2\)-monotone if and only if there exists \(p\in(0,2]\) such that
\(E\) is an interpolation space between \(\ell^p\) and \(\ell^2\).
\end{quote}
Cadilhac's paper solves the corresponding function-space statement and
records the sequence-space obstruction: the reverse implication for
sequence spaces was tied to Calderon-type information for
\((\ell^p,\ell^q)\).

\paragraph{Supporting answer.}
The supporting paper is Leonard Cadilhac, Fedor Sukochev, and Dmitriy
Zanin, \emph{Lorentz-Shimogaki-Arazy-Cwikel Theorem revisited},
arXiv:2009.02145.  Its abstract says that, as a byproduct, it solves the
conjecture of Levitina and the last two authors.  The introduction further
states that the authors resolve the conjecture of \cite{LSZ} in the
affirmative and then gives the precise theorem.

The relevant theorem is Theorem 1.2 of arXiv:2009.02145.  It states that if
\(E\subset \ell_\infty\) is a quasi-Banach sequence space and \(q\ge 1\),
then the following are equivalent:
\begin{enumerate}
\item there exists \(p<q\) such that \(E\in \Int(\ell^p,\ell^q)\);
\item there is a constant \(c>0\) such that, for all \(u\in E\) and
      \(v\in \ell_\infty\), tail-majorization
      \(|v|^q \prec\prec_{\rm tl} |u|^q\) implies
      \(v\in E\) and \(\|v\|_E\le c\|u\|_E\);
\item the same tail-majorization implication holds without explicitly
      stating the norm bound.
\end{enumerate}

\paragraph{Specialization to the extracted conjecture.}
Set \(q=2\) in Theorem 1.2.  Cadilhac--Sukochev--Zanin's tail-majorization
condition \(|v|^2\prec\prec_{\rm tl}|u|^2\) is the same orientation as
right-\(2\)-monotonicity in arXiv:1812.03861: the source paper writes that
\(u^2\) right-majorizes \(v^2\) when all tails of \(u^2\) dominate the
corresponding tails of \(v^2\).  Thus Theorem 1.2 gives exactly:
\[
  E \text{ is right-}2\text{-monotone}
  \quad\Longleftrightarrow\quad
  \exists p<2,\ E\in \Int(\ell^p,\ell^2).
\]
This is slightly sharper in the upper endpoint than the source conjecture's
\(p\in(0,2]\), since \(p=2\) is unnecessary in the theorem's conclusion.

\paragraph{Provenance.}
The answer is not an original result of this run.  The supporting authors
explicitly knew they were resolving the Levitina--Sukochev--Zanin
conjecture.  The run contribution is the identification that the later
Theorem 1.2 fully answers the source conjecture quoted in arXiv:1812.03861.

\begin{thebibliography}{9}
\bibitem{Cadilhac1812}
L. Cadilhac,
\emph{Majorization, Interpolation and noncommutative Khintchine inequalities},
arXiv:1812.03861.

\bibitem{CSZ}
L. Cadilhac, F. Sukochev, and D. Zanin,
\emph{Lorentz-Shimogaki-Arazy-Cwikel Theorem revisited},
arXiv:2009.02145.

\bibitem{LSZ}
G. Levitina, F. Sukochev, and D. Zanin,
\emph{Cwikel estimates revisited}.
\end{thebibliography}

\end{document}
