\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature-Implied Answer for arXiv:1607.08488}
\author{fa\_banach\_001, agent\_lane\_01}
\date{2026-07-03}

\begin{document}
\maketitle

\begin{abstract}
Sain's arXiv:1607.08488 conjectured that on \( \ell_p^n \), \(1<p<\infty\),
and more generally on every finite dimensional strictly convex smooth real
Banach space, a left symmetric operator for Birkhoff-James orthogonality must
be the zero operator. Paul, Mal, and Wojcik later proved a stronger compact
operator theorem. In finite dimension it applies directly, so both conjectures
are affirmatively settled by later literature.
\end{abstract}

\section*{Source conjectures}

The source paper proves the zero-operator-only result for \( \ell_p^2 \) when
\(p\geq 2\), and then states two conjectures:
\[
\text{Conjecture 2.13: }\quad
X=\ell_p^n,\ 1<p<\infty,\quad
T\in \mathcal L(X) \text{ left symmetric}
\iff T=0,
\]
and
\[
\begin{aligned}
\text{Conjecture 2.14: }&\quad
X \text{ finite dimensional, strictly convex, smooth, real},\\
&\quad T\in \mathcal L(X) \text{ left symmetric}\iff T=0.
\end{aligned}
\]
The source also notes that Conjecture 2.14 implies Conjecture 2.13.

\section*{Supporting theorem}

Paul, Mal, and Wojcik prove the following stronger statement in
arXiv:1807.11166:
\[
\text{if } X \text{ is reflexive and strictly convex, } Y \text{ is strictly
convex, and } T\in K(X,Y),
\]
then \(T\) is left symmetric if and only if \(T=0\).

\section*{Implication}

Let \(X\) be as in Sain's Conjecture 2.14 and take \(Y=X\). Since \(X\) is
finite dimensional, it is reflexive and every bounded operator on \(X\) is
compact. Since \(X\) is strictly convex, the range hypothesis \(Y\) strictly
convex is also satisfied. Therefore the Paul--Mal--Wojcik theorem applies to
every \(T\in\mathcal L(X)=K(X,X)\) and gives
\[
T \text{ left symmetric} \iff T=0.
\]
This is exactly the conclusion of Conjecture 2.14. Since
\(\ell_p^n\), \(1<p<\infty\), is finite dimensional and strictly convex, the
same theorem also proves Conjecture 2.13.

\section*{Status}

The answer is affirmative by later literature. This packet is classified as a
literature-implied answer because the later theorem subsumes the conjectures
rather than explicitly naming them.

\begin{thebibliography}{9}

\bibitem{Sain}
Debmalya Sain.
\newblock \emph{Birkhoff-James orthogonality of linear operators on finite
dimensional Banach spaces}.
\newblock arXiv:1607.08488; J. Math. Anal. Appl. 447 (2017), 860--866.

\bibitem{PMW}
Kallol Paul, Arpita Mal, and Pawel Wojcik.
\newblock \emph{Symmetry of Birkhoff-James orthogonality of operators defined
between infinite dimensional Banach spaces}.
\newblock arXiv:1807.11166.

\end{thebibliography}

\end{document}
