\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\odotprod}{\odot}
\newcommand{\C}{\mathcal{C}}

\title{Same-Weight Transport and the Weighted Hardy Bottleneck}
\author{Run fa\_banach\_001, lane 16}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source Prompt}

The source is Tomasz Kiwerski and Jakub Tomaszewski, \emph{Arithmetic,
interpolation and factorization of amalgams}, arXiv:2401.05526.  In Section
8.b, page 76, the authors ask for abstract analogues of weighted factorization
results for generalized weighted spaces \(X_w\).

The result below gives such an analogue for the common-weight transport case.
It is a partial result: it does not address different weights, later
symmetrization, or the separate Orlicz-Cesaro multiplier problem.

\section*{Definitions}

Let \(I=(0,\infty)\).  Let \(w\) be a positive weight and set
\[
  W(t)=\int_0^t w(s)\,ds .
\]
Assume \(W(t)<\infty\) for every \(t<\infty\) and \(W(\infty)=\infty\), so that
\(W\) has an increasing inverse \(\tau=W^{-1}\) on \(I\).

For a Banach ideal space \(X\) on \(I\), define its transported weighted copy
\[
  X^{[w]}=\{f: f\circ\tau\in X\},\qquad
  \norm{f}_{X^{[w]}}=\norm{f\circ\tau}_{X}.
\]
When \(X\) is rearrangement invariant, this agrees isometrically with the
source paper's generalized weighted space \(X_w\).  The notation \(X^{[w]}\)
is used only to emphasize that the proof needs the multiplicative transport
map \(T_w f=f\circ\tau\), and hence also applies to non-rearrangement-invariant
Banach ideal spaces such as Cesaro or Tandori-type spaces.

For Banach ideal spaces \(X,Y\), write \(M(X,Y)\) for the pointwise multiplier
space from \(X\) to \(Y\), and \(X\odotprod Y\) for the pointwise product space
with its usual infimum product norm.

Define also the transported Hardy operator
\[
  H_\tau g(s)=\frac{1}{\tau(s)}\int_{[0,s]} |g(r)|\,d\tau(r),
\]
where the integral is taken with respect to the Lebesgue--Stieltjes measure
generated by the increasing function \(\tau\).  Let
\[
  \C_\tau X=\{g: H_\tau g\in X\},\qquad
  \norm{g}_{\C_\tau X}=\norm{H_\tau g}_X .
\]
When \(\tau(s)=s\), this is the usual Cesaro optimal domain \(\C X\).

\section*{Idea of the Proof}

The entire mechanism is the identity
\[
  T_w(fg)=(T_w f)(T_w g).
\]
Thus \(T_w\) is not only a lattice isometry \(X^{[w]}\to X\), but also respects
pointwise products.  Multiplier norms and product factorizations are therefore
transported exactly through the same change of variables.

\begin{theorem}[Same-weight transport of multipliers and products]
Let \(X\) and \(Y\) be Banach ideal spaces on \(I\).  Then \(T_w f=f\circ\tau\)
is a multiplicative lattice isometry from \(X^{[w]}\) onto \(X\), and it
induces isometric identifications
\[
  M(X^{[w]},Y^{[w]}) = M(X,Y)^{[w]}
\]
and
\[
  X^{[w]}\odotprod M(X^{[w]},Y^{[w]})
  \cong
  X\odotprod M(X,Y).
\]
Consequently,
\[
  Y^{[w]} = X^{[w]}\odotprod M(X^{[w]},Y^{[w]})
\]
with constant \(C\) if and only if
\[
  Y = X\odotprod M(X,Y)
\]
with the same constant \(C\).  In particular, isometric factorization is
preserved.
\end{theorem}

\begin{proof}
The definition gives \(\norm{T_w f}_X=\norm{f}_{X^{[w]}}\), so \(T_w\) is an
onto lattice isometry.  Since composition with \(\tau\) respects pointwise
products,
\[
  T_w(hf)=(T_w h)(T_w f).
\]
Therefore
\[
\begin{aligned}
  \norm{h}_{M(X^{[w]},Y^{[w]})}
    &= \sup_{\norm{f}_{X^{[w]}}\le 1} \norm{hf}_{Y^{[w]}}        \\
    &= \sup_{\norm{T_w f}_{X}\le 1} \norm{T_w(hf)}_{Y}           \\
    &= \sup_{\norm{g}_{X}\le 1} \norm{(T_w h)g}_{Y}              \\
    &= \norm{T_w h}_{M(X,Y)} .
\end{aligned}
\]
This proves the multiplier identification \(M(X^{[w]},Y^{[w]})=M(X,Y)^{[w]}\)
isometrically.

For products, take \(u\in X^{[w]}\odotprod M(X^{[w]},Y^{[w]})\).  If
\(|u|\le \sum_k |a_k b_k|\), with \(a_k\in X^{[w]}\) and
\(b_k\in M(X^{[w]},Y^{[w]})\), then
\[
  |T_wu|\le \sum_k |(T_wa_k)(T_wb_k)|.
\]
The product norm of \(T_wu\) in \(X\odotprod M(X,Y)\) is at most the same
sum of products of norms.  Applying the same argument to \(T_w^{-1}\) gives the
reverse inequality, hence an isometric product identification.

Finally, applying \(T_w\) to \(Y^{[w]}\) gives \(Y\), and applying \(T_w\) to the
weighted product gives \(X\odotprod M(X,Y)\).  Thus the two factorization
statements are equivalent, with identical constants.
\end{proof}

\begin{corollary}[Common-weight abstract analogue]
Every factorization theorem of the form
\[
  Y = X\odotprod M(X,Y)
\]
immediately yields the common-weight transported theorem
\[
  Y^{[w]} = X^{[w]}\odotprod M(X^{[w]},Y^{[w]}).
\]
For example, the source paper's unweighted factorizations through \(L_p\),
Cesaro spaces, Tandori spaces, or mixed Cesaro--Tandori pairs all have
same-weight transported versions whenever the weighted spaces are interpreted
through the same \(W\)-change of variables.
\end{corollary}

\begin{theorem}[Transport of the Cesaro side]
The same map \(T_w f=f\circ\tau\) is an isometric lattice isomorphism
\[
  T_w:\C(X^{[w]})\longrightarrow \C_\tau X.
\]
Moreover,
\[
  M(X^{[w]},\C(X^{[w]})) = M(X,\C_\tau X)^{[w]}
\]
isometrically, and
\[
  \C(X^{[w]})=X^{[w]}\odotprod M(X^{[w]},\C(X^{[w]}))
\]
if and only if
\[
  \C_\tau X = X\odotprod M(X,\C_\tau X).
\]
\end{theorem}

\begin{proof}
For \(f\in L_0(I)\) and \(g=T_wf=f\circ\tau\), the change of variables
\(t=\tau(r)\) gives
\[
  (Hf)(\tau(s))
  = \frac{1}{\tau(s)}\int_0^{\tau(s)} |f(t)|\,dt
  = \frac{1}{\tau(s)}\int_{[0,s]} |g(r)|\,d\tau(r)
  = H_\tau g(s).
\]
Therefore
\[
  \norm{f}_{\C(X^{[w]})}
  = \norm{Hf}_{X^{[w]}}
  = \norm{(Hf)\circ\tau}_X
  = \norm{H_\tau(T_wf)}_X,
\]
which proves \(T_w\C(X^{[w]})=\C_\tau X\) isometrically.  The multiplier and
product statements then follow exactly as in the previous theorem, using again
that \(T_w\) respects pointwise products.
\end{proof}

\section*{Full-Push Obstruction}

The second theorem explains why the same-weight result above is not yet a full
solution of Section 8.b for Cesaro spaces.  The ordinary Hardy operator does
not commute with the \(W\)-transport unless \(W(t)\) is linear.  Instead it
becomes \(H_\tau\).  Thus the weighted Cesaro factorization problem is
equivalent to a factorization problem for the optimal domain \(\C_\tau X\).

This is a real obstruction rather than just a notational inconvenience.  In the
special case \(w\equiv1\), we have \(\tau(s)=s\) and \(\C_\tau X=\C X\), so the
transported weighted-Cesaro factorization reduces to the source paper's
previous Section 8.a question
\[
  \C X = X\odotprod M(X,\C X).
\]
Consequently, a blanket full answer to the abstract weighted-Cesaro problem
would already settle that unweighted open problem.

\section*{Limitations}

This theorem is deliberately scoped.  It does not solve weighted factorizations
with different weights on the two sides, where a single multiplicative transport
no longer identifies both spaces at once.  It also does not handle questions
where a further symmetrization is part of the construction, such as abstract
Lorentz spaces \(\Lambda_{X,w}\), nor does it identify the separate open
multiplier space \(M(Ces_M,Ces_N)\) for Orlicz function spaces from Section 8.e
of the source paper.  For Cesaro spaces it gives an exact reduction to
\(\C_\tau X\), not a proof that \(\C_\tau X\) always factorizes through \(X\).

\section*{Verification and Novelty Check}

The proof is purely formal after the change of variables \(T_w f=f\circ W^{-1}\).
The source paper itself uses the same transport observation to identify
\(X_w\) with \(X\) for rearrangement invariant \(X\), but it does not appear to
state the corresponding multiplier and product-factorization transport
principle in Section 8.b.

Run-index searches for arXiv:2401.05526, generalized weighted spaces, and
weighted factorization found no prior packet for this result.  Web searches for
phrases such as \(M(X_w,Y_w)\), generalized weighted space factorization, and
weighted Cesaro factorization found related weighted Cesaro/Copson literature,
including Barza--Marcoci--Marcoci's weighted Hardy factorizations, but no exact
same-weight transport statement under this formulation.  The full-push check
also shows that the Cesaro side is blocked by the weighted Hardy optimal-domain
factorization \(\C_\tau X=X\odotprod M(X,\C_\tau X)\).

\section*{Human Review Recommendation}

Treat this as a likely valid partial result answering the common-weight
transport version of Section 8.b, together with a reduction of the Cesaro
weighted case to a weighted Hardy optimal-domain factorization problem.  It
should not be counted as a full solution to all weighted-space problems raised
in the source paper.

\section*{References}

\begin{enumerate}
\item T. Kiwerski and J. Tomaszewski, \emph{Arithmetic, interpolation and
factorization of amalgams}, arXiv:2401.05526, 2024.
\item S. V. Astashkin and L. Maligranda, \emph{Structure of Cesaro function
spaces}, Indag. Math. (N.S.) 20 (2009), 329--379.
\item S. Barza, A. Marcoci and L. Marcoci, \emph{Factorizations of weighted
Hardy inequalities}, Bull. Braz. Math. Soc. 49 (2018), 915--932.
\end{enumerate}

\end{document}
