\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: A Complex \texorpdfstring{$n_L(X)<n(X)$}{nL<n} Example}
\author{FA/Banach run \texttt{fa\_banach\_001}}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet, not an original proof from the
run.  Wang--Huang--Tan, arXiv:1211.5753, ask at the end of Section 4 whether
there exists a Banach space \(X\) such that
\[
  n_L(X)<n(X).
\]
Perez-Hernandez, arXiv:2507.18208, answers the broad real-or-complex question
affirmatively in the complex case.

\section*{Original Problem}

The original source is:

\begin{quote}
R. Wang, X. Huang, D. Tan, \emph{On the numerical radius of Lipschitz operators
in Banach spaces}, arXiv:1211.5753.
\end{quote}

The paper defines \(\operatorname{Lip}_0(X)\) as all Lipschitz maps
\(X\to X\) which vanish at \(0\), and defines \(n_L(X)\) by taking the
infimum of the Lipschitz numerical radius over norm-one maps in this class.
The final problem asks whether strict inequality \(n_L(X)<n(X)\) can happen.

\section*{Later Answer}

The supporting source is:

\begin{quote}
A. Perez-Hernandez, \emph{Lipschitz vs Linear Numerical Index in certain
Banach spaces}, arXiv:2507.18208.
\end{quote}

In its introduction, the supporting source says that the answer depends on the
underlying scalar field.  For the complex Hilbert plane
\[
  X=\mathbb C^2,\qquad
  \|(z_1,z_2)\|=(|z_1|^2+|z_2|^2)^{1/2},
\]
the classical numerical index is \(n(\mathbb C^2)=1/2\).  The paper then
considers the real-linear Lipschitz map
\[
  F(z_1,z_2)=(\overline{z_2},-\overline{z_1}).
\]
It has \(\|F\|_L=1\).  If \(y=(w_1,w_2)\in S_X\), the unique norming
complex-linear functional is
\[
  x^*(z_1,z_2)=\overline{w_1}z_1+\overline{w_2}z_2.
\]
Therefore
\[
  x^*(F(y))
  =\overline{w_1}\overline{w_2}
   -\overline{w_2}\overline{w_1}
  =0.
\]
Thus the Lipschitz numerical range of \(F\) is \(\{0\}\), so
\[
  n_L(\mathbb C^2)=0<\frac12=n(\mathbb C^2).
\]

\section*{Verification Notes}

The 2025 definition of \(W_L(F)\) is equivalent to the 2012 definition: a
unit functional norming \(x_1-x_2\) is the normalized version of an element of
\(D(x_1-x_2)\).  The map \(F\) is admissible because the Lipschitz numerical
index is taken over all Lipschitz maps fixing the origin, not only over
complex-linear maps.

The 2025 paper keeps the real case open in full generality and proves equality
for real separable spaces and real dual spaces.  This packet records only the
complex affirmative answer to the original broad question.

\section*{Search Bounds}

The local registry, solution index, attempt index, and proof-gap index were
searched for arXiv:1211.5753 and core phrases such as \(n_L(X)<n(X)\),
Lipschitz numerical index, and numerical radius.  No exact prior packet was
found.  The decisive later source passage was found in the local parsed source
for arXiv:2507.18208, whose bibliography identifies arXiv:1211.5753 as the
Wang--Huang--Tan paper.

\end{document}
