\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Enflo Type and Rademacher Type}
\author{Agent lane 18 packet for run fa\_banach\_001}
\date{2026-06-26}

\begin{document}
\maketitle

\section*{Status}

This packet records a literature answer to open-problem signals in
Giladi--Naor~\cite{GN2010} and to the same Enflo-problem occurrence in
Mendel--Naor~\cite{MN2005}. It is not a new proof packet.

\section*{Source Question}

In the introduction of \cite{GN2010}, on page 2 of the PDF, the authors recall
Enflo's question for Banach spaces: whether Rademacher type $p$ implies Enflo
type $p$. They note that Enflo type $p$ immediately implies Rademacher type
$p$, and that Pisier had proved the reverse implication only with exponent
$p'<p$. Thus the endpoint implication Rademacher type $p$ $\Rightarrow$ Enflo
type $p$ is the open problem cited by the source.

The same classical question is recalled in \cite{MN2005}. That paper also
asks whether scaled Enflo type $p$ implies Enflo type $p$; this packet covers
only the Banach-space Enflo/Rademacher endpoint consequence, not the separate
general metric-space implication.

\section*{Supporting Answer}

Ivanisvili, van Handel, and Volberg~\cite{IVV2020} explicitly settle this
problem. Their abstract states that Rademacher type and Enflo type coincide,
and Theorem 1.1 gives the quantitative comparison
\[
  T_p^R(X) \le T_p^E(X) \le \frac{\pi}{\sqrt{2}} T_p^R(X)
\]
for every $p\in[1,2]$ and every Banach space $X$. Since the first inequality
is the immediate Enflo-implies-Rademacher direction and the second is the
previously open Rademacher-implies-Enflo direction, this theorem gives a full
affirmative answer to the question cited in \cite{GN2010} and to the same
Enflo-problem occurrence in \cite{MN2005}.

\section*{Scope}

This is a complete later-literature answer to the Enflo/Rademacher type
equivalence question cited in arXiv:1004.4221 and arXiv:0506215. It does not
represent a new result from this run. It also does not address separate
quantitative questions about the smallest scale $m$ in the scaled Enflo type
inequality, nor the general metric implication from scaled Enflo type to Enflo
type.

\section*{Search Evidence}

The local cheap indexes contained no direct previous packet for arXiv:1004.4221.
Web searches for phrases such as \emph{Rademacher type and Enflo type coincide}
and \emph{Rademacher type p implies Enflo type p} returned arXiv:2003.06345 as
the direct later answer. The supporting paper explicitly frames its theorem as
settling Enflo's long-standing problem.

\begin{thebibliography}{9}

\bibitem{GN2010}
O. Giladi and A. Naor,
\emph{Improved bounds in the scaled Enflo type inequality for Banach spaces},
arXiv:1004.4221.

\bibitem{MN2005}
M. Mendel and A. Naor,
\emph{Scaled Enflo type is equivalent to Rademacher type},
arXiv:0506215.

\bibitem{IVV2020}
P. Ivanisvili, R. van Handel, and A. Volberg,
\emph{Rademacher type and Enflo type coincide},
arXiv:2003.06345.

\end{thebibliography}

\end{document}
