\documentclass[11pt]{amsart}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.15in]{geometry}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\B}{B_2^n}
\newcommand{\vol}{|\cdot|}

\title{A Small Equality-Case Note for the Polar Schneider Collection Inequality}
\author{arxiv\_automatic\_math run fa\_banach\_001}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source and Status}

This note concerns Julian Haddad, Dylan Langharst, Galyna V. Livshyts, and Eli
Putterman, \emph{On the polar of Schneider's difference body}, arXiv:2503.06191.

Status: \texttt{partial\_result\_likely\_valid}.

The source paper proves a polar Schneider inequality for a collection
\(\mathcal K=(K_0,\ldots,K_m)\) of convex bodies.  In Theorem 11 it states that
a necessary condition for equality is that all \(K_i\) are centered ellipsoids,
while a sufficient condition is that all \(K_i\) are the same centered
ellipsoid.  The authors then note that they do not know whether equality can
hold when all \(K_i\) are centered ellipsoids but at least one of them differs
from the others.

The present packet closes only the case \(m=1\).

\section*{Definitions}

For two convex bodies \(K_0,K_1\subset\R^n\), the source paper's collection
difference body is
\[
  D^1(K_0,K_1)=\{x\in\R^n:K_0\cap(K_1+x)\neq\varnothing\}
  =K_0+(-K_1).
\]
If the bodies are centered ellipsoids, they are centrally symmetric, so
\(-K_1=K_1\).  The \(m=1\) instance of Theorem 11 is
\[
  |D^{1,\circ}(K_0,K_1)|\,|K_1|
  \leq |\B|\,|D^{1,\circ}(\B,\B)|.
\]
Since \(D^1(\B,\B)=2\B\), the right-hand side is
\[
  |\B|\,|(2\B)^\circ|=2^{-n}|\B|^2.
\]

\section*{Idea of the Proof}

When \(m=1\), the collection body is just a Minkowski sum.  If \(E_0,E_1\) are
centered ellipsoids and their polar volumes agree, then their ordinary volumes
also agree.  Brunn--Minkowski says \(E_0+E_1\) has volume at least the volume of
\(2E_1\), with equality only when the two ellipsoids are homothetic.  Since the
volumes and centers agree, homothety means equality of the ellipsoids.  Applying
Blaschke--Santalo to \(E_0+E_1\) then gives the desired strictness unless
\(E_0=E_1\).

\begin{theorem}
Let \(E_0,E_1\subset\R^n\) be centered ellipsoids satisfying
\[
  |E_0^\circ|=|E_1^\circ|.
\]
Then equality in the \(m=1\) case of the source paper's Theorem 11 holds if and
only if \(E_0=E_1\).  In particular, if \(E_0\neq E_1\), then
\[
  |(E_0+E_1)^\circ|\,|E_1|
  < 2^{-n}|\B|^2.
\]
\end{theorem}

\begin{proof}
For a centered ellipsoid \(E=A\B\),
\[
  |E|\,|E^\circ|=|\B|^2.
\]
Thus the assumption \(|E_0^\circ|=|E_1^\circ|\) implies
\[
  |E_0|=|E_1|=:V.
\]

Set \(L=E_0+E_1\).  The body \(L\) is centrally symmetric, so the
Blaschke--Santalo inequality applies with the origin as Santalo point:
\[
  |L^\circ|\,|L|\leq |\B|^2.
\]
On the other hand, Brunn--Minkowski gives
\[
  |L|^{1/n}=|E_0+E_1|^{1/n}
  \geq |E_0|^{1/n}+|E_1|^{1/n}=2V^{1/n}.
\]
Therefore \(|L|\geq 2^nV\), and hence
\[
  |(E_0+E_1)^\circ|\,|E_1|
  =|L^\circ|V
  \leq \frac{|\B|^2V}{|L|}
  \leq 2^{-n}|\B|^2.
\]

This is exactly the \(m=1\) collection inequality for centered ellipsoids.

It remains to identify equality.  Equality in the chain above requires equality
in Brunn--Minkowski.  For full-dimensional convex bodies this forces \(E_0\) and
\(E_1\) to be homothetic.  Their volumes are equal, so the homothety ratio is
one; since both ellipsoids are centered at the origin, this gives \(E_0=E_1\).
Conversely, if \(E_0=E_1=E\), then
\[
  |(2E)^\circ|\,|E|
  =2^{-n}|E^\circ|\,|E|
  =2^{-n}|\B|^2,
\]
so equality holds.  This proves the claim.
\end{proof}

\section*{Limitations}

This packet does not settle the source paper's equality question for \(m\geq2\).
There the collection body is no longer just a sum of two full-dimensional
bodies in \(\R^n\), and the above Brunn--Minkowski equality argument does not
directly apply.

It also does not address Schneider's original higher-order conjecture on the
minimum of \(|D^m(K)|\,|K|^{-m}\), which remains a hard Petty-adjacent convex
geometry problem.

\section*{Novelty Check}

Local run indexes were searched for arXiv id \texttt{2503.06191}, the title,
``Polar Schneider'', ``Schneider difference body'', ``Theorem 11'', and
``same centered ellipsoid''.  No prior packet for this equality subcase was
found.  A bounded web search on 2026-07-03 for the exact title together with
phrases from the equality-gap sentence surfaced the source arXiv page and no
separate answer to this \(m=1\) equality subcase.

Novelty confidence is modest: the observation is elementary and may be known to
experts, but it is not stated in the source paper's equality discussion.

\section*{Human Review Recommendation}

Review as a narrow likely-valid partial result.  The main point to verify is
that the equality characterization in Brunn--Minkowski is being applied in its
standard full-dimensional form.

\begin{thebibliography}{9}

\bibitem{HLLP}
J. Haddad, D. Langharst, G. V. Livshyts, and E. Putterman,
\emph{On the polar of Schneider's difference body},
arXiv:2503.06191, 2025.

\bibitem{Gardner}
R. J. Gardner,
\emph{The Brunn--Minkowski inequality},
Bull. Amer. Math. Soc. (N.S.) \textbf{39} (2002), 355--405.

\bibitem{FMZ}
M. Fradelizi, M. Meyer, and A. Zvavitch,
\emph{Volume product},
in \emph{Harmonic analysis and convexity}, Adv. Anal. Geom. 9,
De Gruyter, 2023, 163--222.

\end{thebibliography}

\end{document}
