\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\newtheorem*{question}{Source question}
\newtheorem*{answer}{Later answer (Theorem 1.7 / Theorem 5.8)}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}

\title{Literature Status: Removing Compact Generation\\
from the LCA Balian--Low Theorem}
\author{Run \texttt{fa\_banach\_001} --- lane 13}
\date{22 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\textbf{Status: literature already answered.}
The open problem in the introduction of arXiv:1905.06827 asks whether the
compact-generation hypothesis can be removed from the Kaniuth--Kutyniok
zero theorem.  The separate later paper arXiv:2001.07080 explicitly removes
it in Theorem~1.7, with the stronger characterization in Theorem~5.8.
}}
\end{center}

\section*{Original question}

U. Enstad, \emph{The Balian--Low theorem for locally compact abelian groups
and vector bundles}, arXiv:1905.06827~\cite{source}, recalls that Kaniuth and
Kutyniok proved the relevant Balian--Low statement for every lattice in a
compactly generated, second-countable locally compact abelian group whose
identity component is noncompact.  The introduction then asks, on arXiv PDF
page~3:

\begin{question}
Can the hypothesis that $G$ is compactly generated be dropped from the
Kaniuth--Kutyniok theorem?
\end{question}

In the equivalent Zak-transform formulation used in the paper, the desired
conclusion is that for every lattice $\Lambda\subseteq G$ and every
$f\in L^2(G)$ for which $Z_{G,\Lambda}f$ is continuous, the Zak transform
must have a zero.

\section*{Separate later answer}

U. Enstad, M. S. Jakobsen, F. Luef, and T. Omland,
\emph{Deformations and Balian--Low theorems for Gabor frames on the adeles},
arXiv:2001.07080~\cite{answerpaper}, explicitly says on arXiv PDF page~4
that the compact-generation assumption can be removed and states:

\begin{answer}
Let $G$ be a locally compact abelian group with noncompact identity
component.  For every lattice $\Lambda$ in $G$ and every $f\in L^2(G)$
for which $Z_{G,\Lambda}f$ is continuous, $Z_{G,\Lambda}f$ has a zero.
\end{answer}

This is Theorem~1.7 in the introduction.  The full statement appears as
Theorem~5.8 on arXiv PDF page~24: for any locally compact abelian group $G$
and lattice $\Lambda$, noncompactness of the identity component is equivalent
to every continuous $\Lambda$-quasiperiodic function on
$G\times\widehat G$ having a zero.  The Zak-transform conclusion follows in
particular.

The supporting paper also cites and uses Theorem~5.5 of arXiv:1905.06827 as
its Proposition~5.7, and explicitly describes Theorem~5.8 as removing compact
generatedness.  Thus the authors knew they were answering precisely this
problem; no new mathematical implication is claimed here.

\section*{Scope and search status}

The later theorem completely answers the source question and in fact states
the result for arbitrary locally compact abelian groups in its formulation,
whereas the source question was posed in the second-countable setting.  No
part of that compact-generation-removal question remains open.

A bounded status check on 22 July 2026 searched the run's registry and
solution/attempt indexes, the local arXiv source corpus for arXiv:1905.06827,
the exact phrase ``the hypothesis that $G$ is compactly generated can be
dropped'', and primary-source searches for Balian--Low/Zak-transform results.
The decisive match was arXiv:2001.07080; its local source confirms
Theorems~1.7 and~5.8 and its explicit reliance on arXiv:1905.06827.

\begin{thebibliography}{9}
\bibitem{source}
U. Enstad,
\emph{The Balian--Low theorem for locally compact abelian groups and vector
bundles}, arXiv:1905.06827 (2019).

\bibitem{answerpaper}
U. Enstad, M. S. Jakobsen, F. Luef, and T. Omland,
\emph{Deformations and Balian--Low theorems for Gabor frames on the adeles},
arXiv:2001.07080 (2020; revised 2022).
\end{thebibliography}

\end{document}
