\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\cK}{C(K)}
\newcommand{\cczero}{c_0}
\newcommand{\elltwo}{\ell_2}

\begin{document}

\begin{center}
{\Large Literature-implied partial answer: automorphic separable \(C(K)\) spaces}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:1701.04263; supporting arXiv:0903.0658}
\end{center}

\section*{Status}

\textbf{literature\_implied\_answer (partial subcase).}

Anisca--Ferenczi--Moreno, arXiv:1701.04263, ask in Question 1.1 whether
\(\cczero\) and \(\elltwo\) are the only separable automorphic Banach spaces.
This note records a known-literature implication for the subcase of separable
spaces of the form \(\cK\).

\section*{Claim}

Let \(K\) be compact metrizable. If \(\cK\) is infinite-dimensional and
automorphic, then \(\cK\) is isomorphic to \(\cczero\).

Thus the answer to Question 1.1 is affirmative inside the class of separable
\(C(K)\)-spaces: no non-\(\cczero\) separable \(C(K)\)-space is automorphic.

\section*{Identification}

Every compact metrizable \(K\) is a continuous image of the Cantor set, and
the Cantor set is Valdivia compact. Aviles--Moreno prove that if \(K\) is a
continuous image of a Valdivia compact and \(C(K)\) is extensible, then
\(C(K)\) is isomorphic to \(\cczero(\Gamma)\). Their introduction also recalls
the Moreno--Plichko fact used in the area: automorphic spaces are extensible.
Consequently an automorphic \(C(K)\), with \(K\) compact metrizable, is
isomorphic to \(\cczero(\Gamma)\). Since \(C(K)\) is separable, \(\Gamma\) is
countable in the infinite-dimensional case, and therefore
\(C(K)\simeq \cczero\).

The supporting authors explicitly address the \(C(K)\) case of the general
automorphic-space problem, but arXiv:0903.0658 predates arXiv:1701.04263.
The connection to Question 1.1 of arXiv:1701.04263 is therefore recorded here
as an agent-identified literature implication, not as a new theorem and not as
a later exact answer to that paper.

\section*{Evidence}

The source question appears in arXiv:1701.04263, page 3, Question 1.1.
The supporting theorem is arXiv:0903.0658, page 2, Theorem 1. The supporting
paper's abstract and introduction state the same \(C(K)\)-automorphic
conclusion on page 1.

The packet includes local copies of both PDFs:
\[
\texttt{source\_paper.pdf}, \qquad
\texttt{supporting\_paper\_0903.0658.pdf}.
\]

\section*{Scope}

This is only a \(C(K)\)-subcase. It does not settle the full question for
arbitrary separable Banach spaces, does not address the UFO classification
problem, and does not answer the separate question in arXiv:1701.04263 about
reducing \(E_0\) to positions inside \(C(0,1)\).

\section*{Search Notes}

Local run searches for arXiv:1701.04263, automorphic spaces, UFO/uniformly
finitely extensible spaces, \(C(K)\), \(C[0,1]\), and position keywords found
no prior packet for this subcase. Web searches on 2026-06-15 found the source
paper and arXiv:0903.0658, but no later full resolution of the broad
automorphic-space question.

\begin{thebibliography}{9}

\bibitem{AFM}
R. Anisca, V. Ferenczi, and Y. Moreno,
\emph{On the classification of positions and of complex structures in Banach spaces},
arXiv:1701.04263.

\bibitem{AM}
A. Aviles and Y. Moreno,
\emph{Automorphisms in spaces of continuous functions on Valdivia compacta},
arXiv:0903.0658.

\end{thebibliography}

\end{document}

