\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}
\emergencystretch=2em

\newcommand{\R}{\mathbb{R}}
\newcommand{\HH}{\mathcal{H}}
\newcommand{\Free}{\mathcal{F}}

\title{A Literature-Implied Affirmative Answer for Discrete Metric Spaces}
\author{Math discovery packet}
\date{July 1, 2026}

\begin{document}
\maketitle

\section{Status}

This is a lightweight \emph{literature-implied answer}, not an original
new theorem.  The source paper is
\[
\text{D. Bate and S. Li, \emph{Thick Families of Geodesics and Differentiation},
arXiv:1904.02315.}
\]
In Section 7, after stating that the questions use ``metric space'' to mean
``complete metric space,'' it asks:
\begin{quote}
Does every discrete metric space biLipschitz embed into some RNP space?
\end{quote}

The supporting paper is F. Albiac, C. Gartland, A. Petitjean, and
A. Prochazka, \emph{Purely 1-unrectifiable metric spaces and locally flat
Lipschitz functions}, arXiv:2103.09370.

\section{Supporting theorem}

ArXiv:2103.09370 proves the following characterization for Lipschitz-free
spaces.  For any metric space \(M\), the completion of \(M\) is purely
1-unrectifiable if and only if the Lipschitz-free space \(\Free(M)\) has the
Radon-Nikod\'ym property.  The same paper records the corresponding embedding
consequence: a complete purely 1-unrectifiable metric space embeds
isometrically into a Banach space with the Radon-Nikod\'ym property.

Recall also the canonical metric embedding \(x\mapsto \delta_x\) of \(M\) into
\(\Free(M)\).

\section{Identification}

Let \(M\) be a complete discrete metric space.  We show that \(M\) is purely
1-unrectifiable.  Let \(A\subset \R\) and let \(f:A\to M\) be Lipschitz.  Since
\(A\) is separable and \(f\) is continuous, \(f(A)\) is separable.

A separable subspace of a discrete metric space is countable: if \(D\) is a
countable dense set in a discrete subspace \(Y\), then every singleton
\(\{y\}\) is open in \(Y\), so density forces \(D\cap\{y\}\ne\emptyset\) for
each \(y\in Y\).  Hence \(Y=D\).

Thus \(f(A)\) is countable, and therefore \(\HH^1(f(A))=0\).  This proves that
\(M\) is purely 1-unrectifiable.  Because \(M\) is complete, the theorem of
Albiac--Gartland--Petitjean--Prochazka applies directly: \(\Free(M)\) has the
RNP and \(M\) embeds isometrically into \(\Free(M)\).

\section{Conclusion}

Under the source paper's stated convention that the questions concern complete
metric spaces, Question (Q4) has an affirmative answer in later literature.
Indeed, every complete discrete metric space embeds not merely
bi-Lipschitzly, but isometrically, into a Banach space with the
Radon-Nikod\'ym property.

\section{Scope}

This packet only addresses Q4.  It does not settle the characterization
questions Q1--Q3 or the universal-distortion question Q5.  The supporting
paper does not appear, from the local cheap-index pass, to explicitly cite the
source Q4; the answer recorded here is the direct implication above.

\section{References}

\begin{itemize}[leftmargin=*]
\item D. Bate and S. Li, \emph{Thick Families of Geodesics and
Differentiation}, arXiv:1904.02315.
\item F. Albiac, C. Gartland, A. Petitjean, and A. Prochazka, \emph{Purely
1-unrectifiable metric spaces and locally flat Lipschitz functions},
arXiv:2103.09370.
\end{itemize}

\end{document}
