\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\emergencystretch=2em

\title{Literature Status for arXiv:1601.06159: Numerical-Range Spectral Constants}
\author{Run fa\_banach\_001, agent\_lane\_04}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

This is a scoped \texttt{literature\_already\_answered} packet.  It records that
one concrete challenge in Michel Crouzeix's \emph{Some constants related to
Numerical Ranges}, arXiv:1601.06159, namely to sharply improve the universal
upper bound \(11.08\), is answered by Crouzeix--Palencia, \emph{The numerical
range is a \((1+\sqrt 2)\)-spectral set}, SIAM J. Matrix Anal. Appl. 38
(2017), 649--655.

\section*{Source Question}

The source paper defines best constants \(Q\) and \(Q_{cb}\) for scalar and
complete polynomial functional calculus over numerical ranges, with
\[
2\leq Q\leq Q_{cb}\leq 11.08.
\]
On PDF page~2, in the paragraph headed ``Some open problems,'' it says that
the conjectures \(Q=2\) and \(Q_{cb}=2\), or determining the exact values, are
difficult open problems.  It then identifies a more modest challenge: sharply
improve the upper bound \(11.08\).  The same paragraph also asks whether
\(Q=Q_{cb}\).

\section*{Supporting Answer}

The 2017 Crouzeix--Palencia paper proves the required upper-bound improvement.
Its official SIAM abstract states that the numerical range of a Hilbert-space
operator is a complete \((1+\sqrt 2)\)-spectral set.  In the notation of
arXiv:1601.06159, this gives
\[
Q_{cb}\leq 1+\sqrt 2
\quad\text{and hence}\quad
Q\leq 1+\sqrt 2,
\]
which sharply improves \(11.08\).  The supporting paper explicitly cites
Crouzeix's 2016 source paper in its references.

\section*{Scope}

This packet does not claim a new proof and does not claim that the full
Crouzeix conjecture is solved.  The exact conjectural constants \(Q=2\) and
\(Q_{cb}=2\), the equality question \(Q=Q_{cb}\), the finite-dimensional
questions about \(Q(3)\) and \(Q_{cb}(3)\), and the other domain-constant
questions in the source remain outside this scoped literature-status result.

The supporting publisher PDF was not directly available during this run: the
SIAM PDF endpoint returned an access/challenge page rather than a PDF.  The
official DOI page and abstract provide the decisive bibliographic and theorem
statement used here.

\section*{Search Evidence}

The lane-1 queue selected arXiv:1601.06159.  Cheap run indexes were searched
for the arXiv id, source title, ``numerical ranges'', ``Davis-Wielandt'',
``Crawford'', and ``numerical index''.  Existing adjacent packets on numerical
index and Crawford-number questions were found, but no exact packet for this
source paper or this upper-bound-improvement challenge was found before this
packet was created.  Web search for Crouzeix--Palencia and \(1+\sqrt 2\)
located the official SIAM page for DOI \texttt{10.1137/17M1116672}.

{\raggedright
\begin{thebibliography}{9}

\bibitem{Crouzeix2016}
M.~Crouzeix,
\emph{Some constants related to Numerical Ranges},
arXiv:1601.06159; SIAM J. Matrix Anal. Appl. \textbf{37}, 420--442 (2016).

\bibitem{CrouzeixPalencia2017}
M.~Crouzeix and C.~Palencia,
\emph{The numerical range is a \((1+\sqrt 2)\)-spectral set},
SIAM J. Matrix Anal. Appl. \textbf{38}, 649--655 (2017),
doi:\texttt{10.1137/17M1116672}.

\end{thebibliography}
}

\end{document}
