\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Literature Answer}

\title{Negative Literature Answer to the UMST Hilbert-Characterization Question from arXiv:1906.09279}
\author{FA/Banach run packet}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

This is a literature-already-answered packet. It records that the weaker
uniformly micro-semitransitive (UMST) Hilbert-characterization possibility
raised in Cabello Sanchez--Dantas--Kadets--Kim--Lee--Martin \cite{CDKKLM}
was answered negatively in the later paper of Cabello Sanchez--Cabello Sanchez
\cite{CC}. It is not an original proof from this run.

\section*{Original Problem}

In the final-results section of \cite{CDKKLM}, after proving duality and
finite-dimensional restrictions for micro-transitive and UMST spaces, the
authors state that no non-Hilbert examples of micro-transitive norms were
known and that such norms might all be Hilbertian. They then add that the same
could be true for Banach spaces with uniformly micro-semitransitive norm.

The extracted question for this packet is the weaker part:

\begin{quote}
Does every Banach space with uniformly micro-semitransitive norm have to be
Hilbertian?
\end{quote}

The source location inspected locally is
\texttt{data/parsed/arxiv\_sources/1906.09279/source.tex}, lines 600--610.

\section*{Supporting Answer}

The supporting paper \cite{CC} studies the semigroup of contractive
automorphisms. In Section 4 it defines UMST, cites \cite{CDKKLM}, and explains
that Euclidean norms had been the only previously known UMST norms, which made
it plausible that UMST might characterize Hilbert spaces. It then says this is
false and proves:

\begin{theorem}
The UMST Hilbert-characterization question has a negative answer. There are
two-dimensional non-Hilbert Banach spaces whose norms are uniformly
micro-semitransitive.
\end{theorem}

\begin{proof}[Literature identification]
Theorem 4.1 of \cite{CC} states that every \(C^2\) norm on the plane whose
unit sphere has strictly positive curvature at every point is uniformly
micro-semitransitive. Section 4 then gives polar-coordinate examples: if
\[
  g:\mathbb R\to (0,\infty), \qquad
  2g'(\theta)^2+g(\theta)^2-g(\theta)g''(\theta)>0
\]
is \(C^2\) and \(\pi\)-periodic, then \(\|v\|_g=r/g(\theta)\) defines a plane
norm satisfying the theorem's hypotheses. The same example section exhibits
the non-elliptic curve
\[
  r=1+\frac{1}{17}\sin(4\theta).
\]
A two-dimensional Hilbert norm has an ellipsoidal unit ball; this displayed
curve is not an ellipse. Hence it supplies a non-Hilbertian Banach plane with
UMST norm.
\end{proof}

\section*{Scope Limitations}

This packet answers only the weaker UMST possibility from \cite{CDKKLM}. It
does not answer the stronger micro-transitive question. In particular, the
supporting paper gives contractive automorphisms for the semigroup version,
not surjective isometries witnessing micro-transitivity.

\section*{Verification Notes}

The supporting paper is distinct from the source paper and explicitly cites
\cite{CDKKLM}. Its Section 4 says the proposed UMST characterization is false
before proving the positive-curvature plane theorem. The local duplicate check
covered arXiv ids \texttt{1906.09279} and \texttt{2209.04652}, plus phrases
\texttt{micro-transitive}, \texttt{uniformly micro-semitransitive},
\texttt{UMST}, \texttt{Hilbert}, and \texttt{contractive automorphisms}. The
cheap indexes contained only broader Mazur-rotation entries, not this
literature answer.

\begin{thebibliography}{9}

\bibitem{CDKKLM}
F. Cabello Sanchez, S. Dantas, V. Kadets, S. K. Kim, H. J. Lee, and
M. Martin,
\emph{On Banach spaces whose group of isometries acts micro-transitively on
the unit sphere},
arXiv:1906.09279.

\bibitem{CC}
F. Cabello Sanchez and J. Cabello Sanchez,
\emph{Dynamics of the semigroup of contractive automorphisms of Banach spaces},
arXiv:2209.04652.

\end{thebibliography}

\end{document}
