\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}

\title{Vemuri's Exceptional Times: A One-Dimensional Literature Completion}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_01}}
\date{2026-07-21}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_already\_answered (one-dimensional exceptional-time completion)}.

\section*{Source Question}

For \(a>0\), let \(E_a^\infty(1)\) be the class of functions on
\(\mathbb R\) for which both the function and its Fourier transform have
Gaussian decay of rate \(a\).  Let \(\Phi_f(\cdot,t)\) denote the harmonic
oscillator evolution with initial datum \(f\).

Kulikov, Oliveira, and Ramos state Vemuri's conjecture on PDF page 3 of
arXiv:2202.11193: if
\[
  f\in E_{\tanh(2\alpha)}^\infty(1),
\]
then
\[
  \Phi_f(\cdot,t)\in E_{\tanh(\alpha)}^\infty(1)
  \qquad\text{for every }t\in\mathbb R.
\]
Their Theorem 1.1 on PDF page 4 proves the corresponding statement in
dimension \(n\) except when
\[
  t\in\left\{\frac{1}{16}+\frac{k}{8}:k\in\mathbb Z\right\}.
\]
Thus, in particular, the exceptional times remained open for the original
one-dimensional conjecture \cite{KOR}.

\section*{Supporting Answer}

Radchenko and Ramos explicitly identify this gap.  On PDF page 2 of
arXiv:2305.18546 they write that Kulikov--Oliveira--Ramos proved Vemuri's
conjecture except at those times and that the purpose of their note is to
prove the remaining cases.  Their Theorem 1 states that, in dimension one,
\[
  f\in E_{\tanh(2\alpha)}^\infty
  \quad\Longrightarrow\quad
  |\Phi_f(x,t)|\le C e^{-\pi\tanh(\alpha)|x|^2}
  \quad(x,t\in\mathbb R).
\]
Applying the same all-time estimate after the quarter-period Fourier shift
gives the corresponding bound for the Fourier transform of
\(\Phi_f(\cdot,t)\).  Hence the full \(E_{\tanh(\alpha)}^\infty\) conclusion
holds for every time, including the exceptional progression \cite{RR}.

This is an explicit literature completion: the supporting authors cite the
source paper and state that they are closing exactly its remaining cases.

\section*{Scope Limitations}

The supporting theorem is one-dimensional.  This packet does not claim a
completion of the source paper's higher-dimensional exceptional-time case.
It also does not answer the stronger time-dependent Gaussian exponent
conjecture formulated later in the source (Conjecture 3.1 in the published
numbering), nor the general endpoint conversion question for Gaussian
\(L^2\) bounds.

\section*{Search Evidence}

The run indexes were searched for arXiv:2202.11193, arXiv:2305.18546,
Vemuri's conjecture, and the exceptional-time phrase; no prior packet was
found.  A bounded web/arXiv search on 2026-07-21 located arXiv:2305.18546 and
verified the explicit source-to-answer citation and theorem match.

\begin{thebibliography}{9}

\bibitem{KOR}
A. Kulikov, L. Oliveira, and J. P. G. Ramos,
\emph{On Gaussian decay rates of harmonic oscillators and equivalences of
related Fourier uncertainty principles}, arXiv:2202.11193; Rev. Mat.
Iberoam. \textbf{40} (2024), 481--502.

\bibitem{RR}
D. Radchenko and J. P. G. Ramos,
\emph{Sharp Gaussian decay for the one-dimensional harmonic oscillator},
arXiv:2305.18546; Proc. Amer. Math. Soc. \textbf{153} (2025), 1985--1991.

\end{thebibliography}

\end{document}
