\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{hyperref}

\hypersetup{colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black}

\title{The Bounded-Torsion Sidon Decomposition Problem Is Answered}
\author{Literature-status note for arXiv:1607.01053}
\date{19 July 2026}

\begin{document}
\maketitle

\begin{center}
\fcolorbox{blue!55!black}{blue!4}{\parbox{0.90\textwidth}{
\textbf{Status.} Literature already answered, partial subcase.  Lewko's
arXiv:2606.06669 answers the bounded-torsion, and hence exponent-$4$, case of
Pisier's decomposition question.  The general conjecture remains open.}}
\end{center}

\section*{Original question}

Gilles Pisier, \emph{Subgaussian sequences in probability and Fourier
analysis}, arXiv:1607.01053v3 (2016), formulates in Section 7 the conjecture
that every subgaussian set of characters on a compact Abelian group is a
finite union of quasi-independent sets \cite{pisier}.  The survey explains
the equivalence with the corresponding Sidon-set problem.

After recalling the prime-exponent theorem and Bourgain's squarefree-exponent
extension, Remark 7.3 on source PDF page 23 states that the equivalence was
still open even for exponent $p=4$.

\section*{Answering theorem}

Lewko's 2026 paper \emph{The Sidon Decomposition Problem in Abelian Groups of
Bounded Torsion} proves the needed result.  Theorem 1.2, on supporting PDF
page 2, states \cite{lewko}:

\begin{quote}
If the discrete dual group $\Gamma=\widehat G$ has bounded torsion, then a
set $\Lambda\subseteq\Gamma\setminus\{0\}$ is Sidon if and only if it is a
finite union of quasi-independent sets.
\end{quote}

Taking $\Gamma=(\mathbb Z/4\mathbb Z)^I$ directly answers Pisier's highlighted
exponent-$4$ subproblem.  More generally, the theorem resolves every fixed
bounded-torsion case.  This is an explicit literature answer rather than a
new proof produced by the present run: Lewko cites Pisier's survey, describes
the prime-power obstruction, and says that the main theorem answers the
outstanding bounded-torsion question.

\section*{Scope limitation}

The original conjecture ranges over arbitrary compact Abelian groups.
Lewko's paper explicitly notes that the analogous problem for
$\Gamma=\mathbb Z$ remains open.  Thus the status is a complete answer for
bounded torsion, but only a partial subcase of Pisier's general question.

\section*{Search record}

The run's registry, solution, attempt, and proof-gap indexes were searched for
arXiv:1607.01053, arXiv:2606.06669, and subgaussian/Sidon/quasi-independent
decomposition terms.  No prior packet was found.  A targeted arXiv search on
19 July 2026 located the June 2026 supporting paper.  Both official arXiv PDFs
are stored with this note.

\begin{thebibliography}{9}

\bibitem{pisier}
G. Pisier,
\emph{Subgaussian sequences in probability and Fourier analysis},
Graduate J. Math. 1 (2016), 59--78; arXiv:1607.01053v3.

\bibitem{lewko}
M. Lewko,
\emph{The Sidon Decomposition Problem in Abelian Groups of Bounded Torsion},
arXiv:2606.06669, 2026.

\end{thebibliography}

\end{document}
