\documentclass[11pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,mathrsfs}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem*{theorem*}{Literature-implied subcase}

\begin{document}

\title{Finite-Dimensional Positive Cases for Net Extension}
\author{Run fa\_banach\_001}
\date{2026-06-15}
\maketitle

\noindent
\textbf{Status.} \texttt{literature\_implied\_answer (partial subcase)}.
This is not a new proof and not a full solution of Naor's classification
question. It records that standard finite-Nagata Lipschitz extension theory
implies a positive finite-dimensional-domain subcase.

\section*{Source Question}

Naor's \emph{Uniform nonextendability from nets}, arXiv:1506.05391, proves
that there are Banach spaces \(X,Y\), a \(1\)-net \(\mathscr N\subset X\),
and a Lipschitz map \(f:\mathscr N\to Y\) such that no uniformly continuous
extension \(F:X\to Y\) exists.

Immediately after the theorem, Naor asks for an understanding of those pairs
of Banach spaces \(X,Y\) for which Rosendal's question has a positive answer:
for every \(1\)-net \(\mathscr N\) of \(X\), every \(Y\)-valued Lipschitz map
on \(\mathscr N\) should admit a uniformly continuous extension to \(X\).

\section*{Supporting Literature}

Freeman--Gartland, \emph{Lipschitz functions on unions and quotients of metric
spaces}, arXiv:2212.08707, Lemma 3.1, records that doubling spaces have finite
Nagata dimension and that finite Nagata dimension is preserved under
bi-Lipschitz embeddings. Lemma 3.2 states that if \(Z\) is a metric space and
\(S\subset Z\) is closed with finite Nagata dimension, then there is a
weak-star--weak-star continuous bounded linear extension operator
\[
  E:\operatorname{Lip}_0(S)\longrightarrow \operatorname{Lip}_0(Z).
\]

Aliaga--Medina, \emph{Lipschitz extension and Lipschitz-free spaces over nets
in normed spaces}, arXiv:2601.03131, Fact 2.2(c), identifies the Banach-valued
extension constant \(e(S,M)\) with the infimum of the constants for weak-star
Lipschitz extendability. Equivalently, such an operator implies that every
Banach-valued \(1\)-Lipschitz map on \(S\) extends to an \(L\)-Lipschitz map on
\(M\), for some finite \(L\).

\begin{theorem*}
Let \(X\) be a finite-dimensional Banach space and let \(Y\) be any Banach
space. For every \(1\)-net \(\mathscr N\subset X\), every Lipschitz map
\(f:\mathscr N\to Y\) has a Lipschitz, hence uniformly continuous, extension
\(F:X\to Y\).
\end{theorem*}

\begin{proof}
A \(1\)-net in Naor's sense is uniformly discrete, hence closed in \(X\).
After identifying the finite-dimensional normed space \(X\) with
\(\mathbb R^n\), the metric space \(X\), and therefore every subset
\(\mathscr N\subset X\), is doubling and has finite Nagata dimension.

Apply Freeman--Gartland Lemma 3.2 with \(Z=X\) and \(S=\mathscr N\). This
gives a weak-star continuous bounded linear extension operator
\(\operatorname{Lip}_0(\mathscr N)\to \operatorname{Lip}_0(X)\). By
Aliaga--Medina Fact 2.2(c), \(e(\mathscr N,X)<\infty\). Thus every
Banach-valued Lipschitz map \(f:\mathscr N\to Y\) extends to a Lipschitz map
on \(X\). Lipschitz maps are uniformly continuous, so this is a positive case
of Rosendal's net-extension property.
\end{proof}

\section*{Scope}

This proves only the finite-dimensional-domain subcase of the positive-pairs
classification problem. It does not address infinite-dimensional domains, and
it does not settle either direction of the coarse-versus-uniform embeddability
questions discussed in Naor's introduction.

\section*{Search and Provenance Notes}

The run indexes were searched for arXiv:1506.05391, the title
\emph{Uniform nonextendability from nets}, Rosendal, \(1\)-nets, Lipschitz
extension, finite Nagata dimension, weak-star Lipschitz extendability, and
\(e(S,M)\). No prior packet for this exact finite-dimensional-domain subcase
was found. Aliaga--Medina cite Naor's paper, but the connection to Rosendal's
positive-pairs question is an agent-identified implication rather than an
explicit ``we answer this question'' statement.

\end{document}
