\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\Area}{\operatorname{Area}}

\title{The Bergman Putnam Factor-\(1/2\) Conjecture Is Already Answered}
\author{Agent lane 11}
\date{2026-07-19}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet.  It records that the
open-problem signal in Bell--Ferguson--Lundberg's paper
\emph{Self-commutators of Toeplitz operators and isoperimetric inequalities}
\cite{bfl} is already answered by a separate cited paper of Olsen and
Reguera \cite{or}.

\section*{Source Question}

The source arXiv id is 1211.6937.  In the first concluding remark, the
authors conjecture the following factor-\(1/2\) improvement of Putnam's
inequality for Toeplitz operators with analytic symbol \(\phi\) acting on
the Bergman space of a planar domain \(G\):
\[
\|[T_\phi^*,T_\phi]\|
\leq
\frac{\Area(\phi(G))}{2\pi}.
\]
The same remark contains an ``Added in press'' note stating that
J.-F. Olsen and M. C. Reguera proved the conjecture in Theorem 1 and
Corollary 1 of their paper.

\section*{Supporting Answer}

The supporting arXiv id is 1305.5193.  Olsen and Reguera explicitly state
that their sharp Hankel-operator estimate improves the classical Putnam
inequality for Bergman-space Toeplitz commutators by a factor of \(1/2\),
answering the Bell--Ferguson--Lundberg conjecture.  Their Corollary 1 gives
the weighted-domain estimate
\[
\|T_\psi^*T_\psi-T_\psi T_\psi^*\|_{A^2_\alpha(\Omega)\to A^2_\alpha(\Omega)}
\leq
\frac{\|\psi'\|_{A^2(\Omega)}^2}{2+\alpha}
\]
for \(\alpha\geq -1\), simply connected \(\Omega\subset\mathbb C\), and
analytic \(\psi\).  Taking \(\alpha=0\) and applying this in the setting of
the source conjecture gives the announced factor-\(1/2\) Bergman Putnam
inequality.

\section*{Scope}

This is not a new solution packet and should not be counted as an original
solve.  It is an exact literature answer: the source paper itself identifies
the supporting paper and says the conjecture was proved there.

\begin{thebibliography}{9}

\bibitem{bfl}
S. R. Bell, T. Ferguson, and E. Lundberg,
\emph{Self-commutators of Toeplitz operators and isoperimetric inequalities},
arXiv:1211.6937, 2012.

\bibitem{or}
J.-F. Olsen and M. C. Reguera,
\emph{On a sharp estimate for Hankel operators and Putnam's inequality},
arXiv:1305.5193, 2013.

\end{thebibliography}

\end{document}
