\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\newcommand{\AK}{\mathcal{AK}}
\newcommand{\cK}{\mathcal{K}}
\newcommand{\pre}{\preceq}
\newcommand{\om}{\omega}
\newcommand{\con}{\mathfrak{c}}

\title{Literature-Implied Partial Answer to Problem 8.1 of arXiv:1406.5526}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_16}}
\date{2026-06-16}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.  This note records a
direct consequence of the source paper's own theorems.  It is not a full answer
to the arbitrary non-reflexive case.

\paragraph{Source.}
A. Aviles, G. Plebanek, and J. Rodriguez, \emph{Tukey classification of some
ideals in omega and the lattices of weakly compact sets in Banach spaces},
arXiv:1406.5526v3 \cite{APR}.

\paragraph{Original question.}
The first problem in the source paper's final ``Open problems'' section asks:
\[
  \text{Is it true that } \AK(X)\sim \AK(B_X)
  \text{ for every non-reflexive } X?
\]
In the PDF theorem numbering this is Problem 8.1.

\paragraph{Recorded partial answer.}
The following consequences are immediate from the comparison and classification
results in \cite{APR}.

\begin{enumerate}[label=(\alph*)]
\item If \(X\) is non-reflexive and \(\cK(B_X)\pre \AK(B_X)\), then
  \(\AK(X)\sim \AK(B_X)\).
\item If \(X\) is non-reflexive and SWCG, then
  \(\AK(X)\sim \AK(B_X)\sim \om\).
\item In ZFC, \(\AK(X)\sim\AK(B_X)\) for every separable non-reflexive Banach
  space \(X\) containing no copy of \(\ell^1\).
\item Under analytic determinacy, \(\AK(X)\sim\AK(B_X)\) for every separable
  non-reflexive Banach space \(X\).
\end{enumerate}

\paragraph{Identification.}
For (a), Proposition 3.7(i) of \cite{APR}, applied with \(E=X\), gives
\(\AK(X)\pre \cK(X)\).  Proposition 3.2(iii) gives
\(\cK(X)\sim\cK(B_X)\) whenever \(X\) is non-reflexive.  Therefore
\[
  \AK(X)\pre \cK(X)\sim \cK(B_X)\pre \AK(B_X).
\]
The reverse reduction \(\AK(B_X)\pre\AK(X)\) is Proposition 3.7(ii), so
\(\AK(X)\sim\AK(B_X)\).

For (b), Lemma 4.2(ii) of \cite{APR} gives a countable family of weakly compact
sets in \(X\) which strongly generates every weakly compact subset of \(X\).
After replacing the family by increasing finite unions, the usual rank map
\(K\mapsto n\) such that \(K\subset K_n+\varepsilon B_X\) is a Tukey reduction
\(\AK(X)\pre\om\).  Theorem 4.3 of \cite{APR} gives
\(\AK(B_X)\sim\om\) for non-reflexive SWCG spaces, and Proposition 3.7(ii)
again gives the reverse lower bound.

For (c), Theorem 6.1 of \cite{APR} states that if \(X\) is separable and
contains no copy of \(\ell^1\), then \(\AK(B_X)\sim\cK(B_X)\), so (a) applies.

For (d), Theorem 8.1 of \cite{APR}, under analytic determinacy, classifies
\(\AK(B_X)\) for separable \(X\).  In the non-reflexive case \(\AK(B_X)\sim
\om\), (b) applies via Theorem 4.3.  In the remaining non-reflexive cases
\(\om^\om\), \(\cK(\mathbb Q)\), and \([\con]^{<\om}\), Theorem 8.1 itself
states \(\AK(B_X)\sim\cK(B_X)\), so (a) applies.

\paragraph{Scope limitation.}
This does not settle Problem 8.1 for arbitrary non-reflexive Banach spaces.
The standard scaling proof for \(\cK(X)\sim\cK(B_X)\times\om\) does not
automatically adapt to \(\AK\), because the Tukey tolerance \(\delta\) must be
fixed before the target radius bound is known.

\begin{thebibliography}{9}
\bibitem{APR}
A. Aviles, G. Plebanek, and J. Rodriguez,
\emph{Tukey classification of some ideals in omega and the lattices of weakly
compact sets in Banach spaces}, arXiv:1406.5526v3.
\end{thebibliography}

\end{document}
