\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\emergencystretch=2em

\title{Literature Status for arXiv:math/0002219: Asymptotic \(\ell_p\) FDDs}
\author{Run fa\_banach\_001, agent\_lane\_03}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a \texttt{literature\_already\_answered} packet.  It records that
Problem~5.4 in Odell--Schlumprecht's \emph{Trees and Branches in Banach
Spaces}, arXiv:math/0002219, is explicitly solved by
Odell--Schlumprecht--Zsak, arXiv:math/0603063.

\section*{Source Question}

On PDF page 24 of arXiv:math/0002219, in the final part of Section~5, the
authors ask Problem~5.4.  They define a reflexive space \(X\) to be
asymptotic \(\ell_p\) if there exists \(K<\infty\) such that, for every
\(k\), every \(k\)-term member of the asymptotic structure \(\{X\}_k\) is
\(K\)-equivalent to the unit vector basis of \(\ell_p^k\).  They also define
an FDD \((E_n)\) for a space \(Z\) to be asymptotic \(\ell_p\) if all
normalized \(k\)-block sequences of the tail \((E_i)_{i=k}^{\infty}\) are
uniformly equivalent to \(\ell_p^k\).

The problem asks whether, if \(X\) is reflexive asymptotic \(\ell_p\) for
some \(1<p<\infty\), then \(X\) embeds into a space \(Z\) with an asymptotic
\(\ell_p\) FDD.

\section*{Supporting Answer}

The abstract of arXiv:math/0603063 states the positive answer in essentially
the same language: if \(X\) is separable, reflexive, and asymptotic \(\ell_p\),
then \(X\) embeds into a reflexive space \(Z\) with an asymptotic \(\ell_p\)
finite-dimensional decomposition.  The first page says this is proved as
Corollary~4.9.

The explicit cross-reference appears on PDF page 32: immediately before
Corollary~4.9, the paper says that a special case of Corollary~4.8 solves
Problem~5.4 raised in the earlier Odell--Schlumprecht paper.  Corollary~4.9
then states that every reflexive asymptotic \(\ell_p\) space embeds into a
reflexive space with an asymptotic \(\ell_p\) FDD, and is also a quotient of
such a reflexive space.

\section*{Scope}

This is a positive literature answer to the source problem as stated.  The
supporting result is stronger than the source question because it gives a
reflexive ambient space and a quotient formulation, and it is stated for the
customary endpoint range as well.  This packet does not claim a new proof, a
new quantitative constant, or a strengthening beyond arXiv:math/0603063.

\section*{Search Evidence}

The lane-3 queue selected arXiv:math/0002219.  Cheap run indexes were searched
for the arXiv id, source title, ``0603063'', ``asymptotic \(l_p\) spaces'',
``asymptotic \(\ell_p\) FDD'', and ``Problem 5.4''; no duplicate packet for
this target was found.  Targeted web search for the exact embedding phrase
identified arXiv:math/0603063, and the local parsed TeX verifies the explicit
statement that Corollary~4.9 solves Problem~5.4 from the source paper.

{\raggedright
\begin{thebibliography}{9}

\bibitem{OS00}
E.~Odell and Th.~Schlumprecht,
\emph{Trees and Branches in Banach Spaces},
arXiv:math/0002219.

\bibitem{OSZ06}
E.~Odell, Th.~Schlumprecht, and A.~Zsak,
\emph{On the structure of asymptotic \(l_p\) spaces},
arXiv:math/0603063.

\end{thebibliography}
}

\end{document}
