\documentclass[11pt]{article}
\usepackage[margin=1.1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\newcommand{\Ck}{C(K)}
\newcommand{\R}{\mathbb R}
\newcommand{\eps}{\varepsilon}
\newcommand{\spb}{s}
\newcommand{\gbd}{\omega_0}
\newcommand{\sig}{\sigma}

\title{A Spectrum Criterion for Eventually Positive Semigroups on \(C(K)\)}
\author{fa\_banach\_001 / agent\_super\_01}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Source Question}

Daners--Glueck--Kennedy, \emph{Eventually Positive Semigroups of Linear
Operators}, arXiv:1511.09020, prove in Corollary 6.5 that a real uniformly
eventually strongly positive \(C_0\)-semigroup on \(C(K)\) has generator with
non-empty spectrum.  They then remark that for a positive semigroup this is
true without irreducibility or strong positivity assumptions, and that it is
unclear whether
\[
  \sig(A)\ne\varnothing
\]
holds for uniformly or individually eventually positive semigroups on \(C(K)\)
in general.

\section*{Partial Result}

\begin{theorem}
\label{thm:minorization}
Let \(K\) be a non-empty compact Hausdorff space and let
\((T(t))_{t\ge0}\) be a real individually eventually positive
\(C_0\)-semigroup on \(C(K)\), with generator \(A\).  Suppose that for some
\(t_1>0\), \(T(t_1)\) is a positive operator.  Assume moreover that at least
one of the following two minorization conditions holds:
\begin{enumerate}
\item There are \(u\in C(K)\), \(u\gg0\), and \(\eps>0\) such that
  \[
    T(t_1)u\ge \eps u.
  \]
\item There are a non-zero positive functional \(\varphi\in C(K)'\) and
  \(\eps>0\) such that
  \[
    T(t_1)'\varphi\ge \eps\varphi.
  \]
\end{enumerate}
Then \(\sig(A)\ne\varnothing\).
\end{theorem}

\section*{Proof Intuition}

The source already supplies the hard spectral-bound theorem: on \(C(K)\), for
real individually eventually positive semigroups, the spectral bound equals
the growth bound.  Thus it is enough to rule out growth bound \(-\infty\).
A single positive tail operator with a lower bound on an order unit, or on a
positive functional in the dual, does exactly that: its powers cannot decay
faster than \(\eps^n\).  This gives a finite lower bound for the semigroup
growth, hence a finite spectral bound, hence non-empty spectrum.

\section*{Proof}

We use Theorem 6.4 of Daners--Glueck--Kennedy: since the semigroup is real and
individually eventually positive on \(C(K)\),
\[
  \spb(A)=\gbd(A),
\]
where both quantities are understood in the extended sense.

Assume first that \(T(t_1)u\ge\eps u\) for some \(u\gg0\).  Since \(T(t_1)\)
is positive, induction gives
\[
  T(nt_1)u=T(t_1)^n u\ge \eps^n u
  \qquad(n\in\mathbb N).
\]
Therefore
\[
  \|T(nt_1)\|
  \ge \frac{\|T(nt_1)u\|_\infty}{\|u\|_\infty}
  \ge \eps^n .
\]
It follows that the growth bound satisfies
\[
  \gbd(A)
  \ge \frac{\log\eps}{t_1}>-\infty .
\]
By the source theorem, \(\spb(A)=\gbd(A)>-\infty\).  If \(\sig(A)\) were
empty, then by definition \(\spb(A)=\sup\{\operatorname{Re}\lambda:
\lambda\in\sig(A)\}=-\infty\), a contradiction.

The dual condition is identical.  Since \(T(t_1)\) is positive,
\(T(t_1)'\) is positive, and
\[
  T(nt_1)'\varphi=T(t_1)'^{\,n}\varphi\ge \eps^n\varphi .
\]
For a positive functional on \(C(K)\), \(\|\varphi\|=\varphi(\mathbf 1)>0\);
hence
\[
  \|T(nt_1)\|=\|T(nt_1)'\|
  \ge \frac{\|T(nt_1)'\varphi\|}{\|\varphi\|}
  \ge \eps^n.
\]
The same growth-bound argument proves \(\sig(A)\ne\varnothing\).

\begin{corollary}
Let \((T(t))_{t\ge0}\) be a real uniformly eventually positive
\(C_0\)-semigroup on \(C(K)\).  If there are \(t_1\) beyond the eventual
positivity threshold, \(u\gg0\), and \(\eps>0\) such that
\[
  T(t_1)u\ge\eps u,
\]
then the generator has non-empty spectrum.  The same conclusion holds under
the dual minorization \(T(t_1)'\varphi\ge\eps\varphi\) for a non-zero positive
functional \(\varphi\).
\end{corollary}

\section*{Scope and Novelty Check}

This is a partial result only.  It does not settle the full source remark,
because a uniformly eventually positive semigroup might fail to minorize an
order unit at every positive tail time.  The cheap run indexes were searched
for arXiv:1511.09020 and for the core phrases ``eventually positive'',
``positive semigroups'', ``spectral bound'', and ``spectrum''; no existing
packet for this exact spectrum criterion was found.  The nearby packet for
arXiv:1511.05294 concerns a different resolvent-versus-semigroup implication.

\section*{References}

\begin{thebibliography}{9}

\bibitem{DGK}
D. Daners, J. Glueck, and J. B. Kennedy,
\emph{Eventually Positive Semigroups of Linear Operators},
J. Math. Anal. Appl. 433 (2016), 1561--1593; arXiv:1511.09020.

\end{thebibliography}

\end{document}
