\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\title{Known classification for Conjecture 2 of Montgomery--Smith--Semenov}
\author{arXiv automatic math run fa\_banach\_001}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Status}

This is a \emph{literature-implied answer (full classification)} for
Conjecture 2 of Montgomery--Smith and Semenov \cite{mss0007058}. The packet
records a later accessible arXiv source which states the exact classification
as known and cites the underlying strict-singular embedding literature.

\section*{Source Question}

The source paper is S. J. Montgomery-Smith and E. M. Semenov,
\emph{Embeddings of rearrangement invariant spaces that are not strictly
singular}, arXiv:math/0007058, Positivity 4 (2000), 397--404. On PDF page 2,
Conjecture 2 states:
\[
\text{the natural embedding }E\subset L_1\text{ is not strictly singular}
\quad\Longleftrightarrow\quad
G\text{ embeds into }E\text{ continuously},
\]
where \(E\) is rearrangement invariant on \([0,1]\) and \(G\) is the closure
of the simple functions in the Orlicz space for \(\exp(x^2)-1\).

\section*{Supporting Identification}

Hernandez, Ruiz, and Sanchiz \cite{hrs2406}, Introduction, PDF page 1, recall
the following known fact for symmetric, i.e. rearrangement invariant, function
spaces on finite measure spaces:
\[
E(\mu)\hookrightarrow L_1(\mu)\text{ is strictly singular}
\quad\Longleftrightarrow\quad
L^{\exp x^2}_0\text{ is not included in }E(\mu).
\]
This is precisely the contrapositive form of Conjecture 2, with
\(L^{\exp x^2}_0\) being the Rodin--Semenov space \(G\) used in the source.
The supporting paper cites the results of Hernandez--Novikov--Semenov
\cite{hns2003} and Astashkin--Hernandez--Semenov \cite{ahs2009}.

\section*{Scope}

This packet does not claim a new proof. It records that the main strict
singularity classification in Conjecture 2 is already known in the later
literature. It also does not address the stronger sign Conjecture 3; that
printed statement is handled separately by the companion counterexample packet.

\begin{thebibliography}{9}

\bibitem{mss0007058}
S. J. Montgomery-Smith and E. M. Semenov,
\emph{Embeddings of rearrangement invariant spaces that are not strictly
singular}, Positivity 4 (2000), 397--404.
\url{https://arxiv.org/abs/math/0007058}

\bibitem{hrs2406}
F. L. Hernandez, C. Ruiz, and M. Sanchiz,
\emph{Disjointly strictly singular inclusions between variable Lebesgue
spaces}, arXiv:2406.14175, 2024.
\url{https://arxiv.org/abs/2406.14175}

\bibitem{hns2003}
F. L. Hernandez, S. Ya. Novikov, and E. M. Semenov,
\emph{Strictly singular embeddings between rearrangement invariant spaces},
Positivity 7 (2003), 119--124.

\bibitem{ahs2009}
S. V. Astashkin, F. L. Hernandez, and E. M. Semenov,
\emph{Strictly singular inclusions of rearrangement invariant spaces and
Rademacher spaces}, Studia Math. 193 (2009), 269--283.

\end{thebibliography}

\end{document}
