\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\newcommand{\cG}{\mathcal G}
\newcommand{\cS}{\mathcal S}
\newcommand{\cont}{2^{\aleph_0}}

\title{A Small-Cardinal Partial Answer for \(\alpha\)-Large Families}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-23}

\begin{document}
\sloppy
\maketitle

\paragraph{Status.}
\textbf{Partial result.} This note records a direct restriction consequence
of the construction of Argyros--Motakis \cite{AM}. It answers their
\(\alpha\)-large-family question for all infinite cardinals at most the
continuum.

\paragraph{Source question.}
Argyros--Motakis ask the following question on page 14 of
\cite{AM}, after recalling the Lopez-Abad--Todorcevic characterization of
the ordinary large-family case:
\begin{quote}
Let \(\kappa\) be an infinite cardinal number which is not
\(\omega\)-Erdos and \(\alpha\) be a countable ordinal number. Does there
exist an \(\alpha\)-large, hereditary and compact family of finite subsets
of \(\kappa\)?
\end{quote}

\paragraph{Definitions used.}
If \(A\) is an infinite set and \(\mathcal B\subseteq [A]^{<\omega}\), then
\(\mathcal B\) is \(\alpha\)-large if for every infinite \(B\subseteq A\)
there is a one-to-one map \(\phi:\mathbb N\to B\) such that
\(\phi(F)\in \mathcal B\) for every Schreier set \(F\in\mathcal S_\alpha\).
The family is compact when it is closed in the product space \(2^A\) and all
of its elements are finite. It is hereditary when \(G\subseteq F\in\mathcal B\)
implies \(G\in\mathcal B\).

\paragraph{Proof Intuition.}
Argyros--Motakis already construct, for each countable \(\alpha\), an
\(\alpha\)-large hereditary compact family \(\mathcal G_\alpha\) on the
Cantor set \(2^{\mathbb N}\), which has cardinality \(\cont\). Nothing in the
definition of \(\alpha\)-largeness requires using all Cantor branches. If
\(A\subseteq 2^{\mathbb N}\), then every infinite subset of \(A\) is still an
infinite subset of the Cantor set, so the same witness sequence supplied by
\(\mathcal G_\alpha\) stays inside \(A\). Compactness also restricts because
the coordinate-extension map \(2^A\to 2^{2^{\mathbb N}}\) is a topological
embedding.

\begin{theorem}
Let \(\kappa\) be an infinite cardinal with \(\kappa\leq \cont\), and let
\(\alpha<\omega_1\). Then there exists an \(\alpha\)-large, hereditary and
compact family of finite subsets of \(\kappa\).
\end{theorem}

\begin{proof}
Choose a set \(A\subseteq 2^{\mathbb N}\) of cardinality \(\kappa\), and
identify \(\kappa\) with \(A\). By Theorem 2.20 of Argyros--Motakis
\cite{AM}, there is an \(\alpha\)-large, hereditary and compact family
\(\mathcal G_\alpha\subseteq [2^{\mathbb N}]^{<\omega}\). Define
\[
  \mathcal H_\alpha(A)
  =
  \{F\in \mathcal G_\alpha : F\subseteq A\}.
\]
Clearly \(\mathcal H_\alpha(A)\subseteq [A]^{<\omega}\), and heredity follows
immediately from the heredity of \(\mathcal G_\alpha\).

We next check compactness. Let \(j:2^A\to 2^{2^{\mathbb N}}\) be the map that
extends a subset of \(A\) by zero outside \(A\). This is a topological
embedding onto the closed set \(\{x:x(\tau)=0\text{ for all }\tau\notin A\}\).
If \(x\) belongs to the closure of \(\mathcal H_\alpha(A)\) in \(2^A\), then
\(j(x)\) belongs to the closure of \(\mathcal G_\alpha\) in
\(2^{2^{\mathbb N}}\). Since \(\mathcal G_\alpha\) is compact, \(j(x)\in
\mathcal G_\alpha\). In particular \(j(x)\) is a finite subset of
\(2^{\mathbb N}\), supported inside \(A\), so \(x\) is a finite subset of
\(A\) and \(x\in\mathcal H_\alpha(A)\). Hence \(\mathcal H_\alpha(A)\) is
closed in \(2^A\), and therefore compact.

Finally let \(B\subseteq A\) be infinite. Since \(B\) is also an infinite
subset of \(2^{\mathbb N}\), the \(\alpha\)-largeness of \(\mathcal G_\alpha\)
gives a one-to-one map \(\phi:\mathbb N\to B\) such that
\(\phi(F)\in\mathcal G_\alpha\) for every \(F\in\mathcal S_\alpha\). But
\(\phi(F)\subseteq B\subseteq A\), hence \(\phi(F)\in\mathcal H_\alpha(A)\).
Thus \(\mathcal H_\alpha(A)\) is \(\alpha\)-large on \(A\).
\end{proof}

\begin{remark}
This proves the Argyros--Motakis question for all infinite
\(\kappa\leq 2^{\aleph_0}\). The proof gives no information about
non-\(\omega\)-Erdos cardinals strictly above the continuum. In particular,
the full question remains open from this argument.
\end{remark}

\paragraph{Verification and novelty check.}
The lightweight run indexes were searched for arXiv:1302.0715 and the core
phrases ``alpha-large'', ``omega-Erdos'', and ``hereditary compact family'',
with no existing packet or attempt found. A bounded web search for the exact
question and close variants found the source paper but no later full answer.
The result above is only the restriction subcase \(\kappa\leq\cont\), not a
solution of the full problem.

\begin{thebibliography}{9}

\bibitem{AM}
S. A. Argyros and P. Motakis,
\emph{\(\alpha\)-Large Families and Applications to Banach Space Theory},
arXiv:1302.0715.

\end{thebibliography}

\end{document}
