\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\eps}{\varepsilon}
\newcommand{\clust}{\operatorname{clust}}

\begin{document}

\section*{Human Review: Optimal Bourgain constant}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proposed proof appears to give a correct improvement of the constant in
Rodriguez's Theorem 2.11 from \(2\) to \(1\). The key point is identifying
exactly where the factor \(\eps\) is lost in the original proof and replacing
that estimate by a sharper midpoint estimate.

In Rodriguez's Lemma 2.17, one considers scalar functions of the form
\[
  a_k(t)=\langle z_{n_k},\varphi(t)\rangle
\]
whose pointwise oscillation is bounded by \(\eps\):
\[
  \limsup_k a_k(t)-\liminf_k a_k(t)\leq \eps
  \qquad\text{for a.e. }t.
\]
The original proof centers \(a_k(t)\) at the endpoint
\[
  \liminf_k a_k(t).
\]
This controls the error by the full oscillation, and hence gives an
\(\eps\)-bound.

The corrected argument centers instead at the midpoint
\[
  m(t)=\frac12\left(\limsup_k a_k(t)+\liminf_k a_k(t)\right).
\]
Then
\[
  \limsup_k |a_k(t)-m(t)|
  \leq
  \frac12\left(\limsup_k a_k(t)-\liminf_k a_k(t)\right)
  \leq \frac{\eps}{2}
\]
for almost every \(t\). Applying Rodriguez's reverse Fatou lemma, Lemma 2.13
of the source paper, gives
\[
  \limsup_k\int_0^1 |a_k(t)-m(t)|\,dt\leq \frac{\eps}{2}.
\]

\section*{Improved Lemma 2.17}

With this midpoint replacement, the proof of Rodriguez's Lemma 2.17 gives
\[
  \clust_{L_1([0,1],Z)^{**}}(r_n\otimes z_n)
  \subseteq
  \frac{\eps}{2}B_{L_1([0,1],Z)^{**}}
\]
instead of the original \(\eps B\)-bound.

The last step in the estimate is unchanged. One writes
\[
  a_k(t)=m(t)+(a_k(t)-m(t)).
\]
Then
\[
\begin{aligned}
  |\langle r_{n_k}\otimes z_{n_k},\varphi\rangle|
  &\leq
  \left|\int_0^1 r_{n_k}(t)m(t)\,dt\right|
  +
  \int_0^1 |a_k(t)-m(t)|\,dt.
\end{aligned}
\]
The first term tends to zero because the Rademacher sequence is weakly null in
\(L_1[0,1]\) and \(m\in L_\infty[0,1]\). The second term is bounded by
\(\eps/2\) in limsup by the midpoint-Fatou estimate above.

\section*{Propagation Through the Original Proof}

Once this sharpened version of Lemma 2.17 is available, the rest of the proof
is essentially Rodriguez's original proof of Theorem 2.11. The pointwise
cluster estimate is passed to the Bochner \(L_1\)-space using Rodriguez's
Lemma 2.18. Then Lemma 2.16 excludes uniformly integrable \(\ell_1\)-sequences
with constant \(C>\eps/2\). The general uniformly integrable case is handled
by the same truncation argument as in the source paper.

Finally, the endpoint passage from all \(\eps'>\eps\) back to \(\eps\) uses
Rodriguez's existing closedness lemma for \(\eps\)-weak precompactness. The
one-point probability space example with the scaled unit vector basis of
\(\ell_1\) shows that the constant \(1\) cannot be improved.

\section*{Review Outcome}

Archive this packet as an apparently correct full solution to Question 2.21:
the constant \(2\) is not optimal, and the optimal universal constant is \(1\).
The mathematical content is concentrated in the midpoint correction to the
scalar oscillation estimate; after that correction, the argument follows the
architecture of the original paper.

\end{document}
