\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer to the \texorpdfstring{$C[0,1]$}{C[0,1]} Pre-Komlos Question in arXiv:1509.07914}
\author{fa\_banach\_001, agent\_lane\_17}
\date{2026-06-20}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight \texttt{literature\_already\_answered} packet. It records
that the question whether \(C[0,1]\) has the pre-Komlos property, asked by Gao,
Troitsky, and Xanthos in \emph{Uo-convergence and its applications to Cesaro
means in Banach lattices}, arXiv:1509.07914, was answered by a separate later
paper.

\section*{Source Question}

After Example 5.3, the source paper states:
\[
\text{``We do not know whether }C[0,1]\text{ has the pre-Komlos property,
or more generally, when }C(K)\text{ has the pre-Komlos property.''}
\]
The source definition uses norm-bounded sequences and requires a subsequence
whose every further subsequence has Cesaro means that are uo-Cauchy.

\section*{Supporting Answer}

The supporting paper is E. Y. Emelyanov, N. Erkursun-Ozcan, and
S. G. Gorokhova, \emph{Komlos properties in Banach lattices},
arXiv:1710.02580.

In Section 2, the supporting paper says that the \(nuo\)-Komlos and
\(nuo\)-pre-Komlos properties were introduced in arXiv:1509.07914 under the
names Komlos and pre-Komlos. In Section 3 it explicitly notes that arXiv:1509.07914
left the \(C[0,1]\) case unknown.

The decisive result is Section 3, Theorem 3, followed by Corollary 2. It states
that if \(K\) is a compact metric space possessing a nonempty separable open
subset without isolated points, then \(C(K)\) fails the relevant pre-Komlos
property. Since \(K=[0,1]\) is compact metric and has no isolated points, the
source question has a negative answer:
\[
  C[0,1]\text{ does not have the pre-Komlos property.}
\]

\section*{Scope}

This packet records an already-known literature answer, not a new result from
the run. It answers the explicit \(C[0,1]\) question and a large class of
compact metric \(C(K)\) examples. It does not classify all compact Hausdorff
spaces \(K\) for which \(C(K)\) has the pre-Komlos property.

\section*{Search Bounds}

The literature check used the exact phrases
\[
\texttt{pre-Komlos property C[0,1]},\quad
\texttt{pre-Komlos C(K)},\quad
\texttt{pre-Komlos uo-Cauchy},
\]
and author/title searches around Gao--Troitsky--Xanthos and ``Komlos
properties in Banach lattices''. These searches found arXiv:1710.02580 as the
direct later answer.

\section*{References}

\begin{enumerate}
\item N. Gao, V. G. Troitsky, and F. Xanthos,
\emph{Uo-convergence and its applications to Cesaro means in Banach lattices},
arXiv:1509.07914, 2015.
\item E. Y. Emelyanov, N. Erkursun-Ozcan, and S. G. Gorokhova,
\emph{Komlos properties in Banach lattices},
arXiv:1710.02580, 2017.
\end{enumerate}

\end{document}
