\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer: Compact Manifold CLSI}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_14}}
\date{2026-07-19}

\begin{document}
\maketitle

\section*{Status}

\noindent\textbf{Status:} \texttt{literature\_already\_answered}.
\par\medskip
Problem 1 from the final ``Major Open Problems'' list in
arXiv:1807.08838 is answered by arXiv:2007.06138.

\section*{Source Question}

The source is Li Gao, Marius Junge, and Nicholas LaRacuente,
\emph{Fisher Information and Logarithmic Sobolev Inequality for Matrix
Valued Functions}, arXiv:1807.08838.  In the subsection ``Major Open
Problems'', the authors ask:
\[
\text{Does every compact Riemanin manifold satisfy CLSI?}
\]
This is the first of three questions in that final problem list.

\section*{Supporting Answer}

The supporting paper is Michael Brannan, Li Gao, and Marius Junge,
\emph{Complete logarithmic Sobolev inequalities via Ricci curvature
bounded below}, arXiv:2007.06138, published in \emph{Advances in
Mathematics} 394 (2022), article 108129.

The supporting paper cites arXiv:1807.08838 under the bibliography key
\texttt{CLSI}.  Its introduction states that every heat semigroup on a
connected compact weighted Riemannian manifold satisfies CLSI.  In the
arXiv source, Theorem \texttt{riemann} proves the stronger statement:
if \((M,g,e^{-W}d\mathrm{vol})\) is a compact connected weighted
Riemannian manifold, then the weighted heat semigroup
\[
T_t=e^{-t\Delta_W}
\]
satisfies \(\lambda\)-CLSI for some \(\lambda>0\).  Taking \(W=0\)
gives the Laplace-Beltrami heat semigroup on every compact connected
Riemannian manifold, which is exactly the source question.

\section*{Scope Limitations}

Only Problem 1 is marked answered here.  The source also asks whether
every generator of a selfadjoint semigroup on a matrix algebra satisfies
CLSI, and whether CLSI is stable under free products.  Those two
questions are not resolved by this packet.

\section*{Evidence Used}

The local source file for arXiv:1807.08838 contains the final ``Major
Open Problems'' section.  The arXiv source bundle for arXiv:2007.06138
contains the citation to arXiv:1807.08838 as \texttt{CLSI}, the
introductory compact-manifold claim, and Theorem \texttt{riemann}.
The same result is visible in public article metadata and abstract
records for the Advances in Mathematics paper.

\end{document}
