\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue,hypertexnames=false]{hyperref}

\title{Literature Status: Milman's Multi-Integral Norm Question}
\author{fa\_banach\_001, lane 11}
\date{19 July 2026}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{literature\_already\_answered}.  Bizeul--Klartag's 2025
Corollary~1.7 gives the missing $M$-estimate and explicitly identifies it as
completing the conjecture attributed to V.~Milman in Skarmogiannis's paper.

\paragraph{Original source and question.}
Skarmogiannis, \emph{On a multi-integral norm defined by weighted sums of
log-concave random vectors}, arXiv:2208.06365 \cite{S}, asks in the
Introduction (PDF pages 2--3) whether, for a centrally symmetric convex body
$K\subset\mathbb R^n$, the norm
\[
  \|\mathbf t\|_{K^s,K}
  =\int_K\!\cdots\!\int_K
    \left\|\sum_{j=1}^s t_jx_j\right\|_K
    \,dx_1\cdots dx_s
\]
is equivalent to $\|\mathbf t\|_2$ up to a factor polylogarithmic in $n$.
For a volume-one isotropic image $K_*$, Theorem~1.1 and the universal lower
bound reduce the question to
\begin{equation}
  \sqrt n\,M(K_*)L_{K_*}\le C(\log n)^b. \tag{1}
\end{equation}
The source says immediately after this reduction on PDF page 3, and again in
Remark~4.2 on PDF page 9, that (1) remained open.

\paragraph{Supporting answer.}
Bizeul and Klartag, \emph{Distances between non-symmetric convex bodies:
optimal bounds up to polylog}, arXiv:2510.20511 \cite{BK}, prove in
Corollary~1.7 (PDF page 6) that every convex body $A$ in covariance-one
isotropic position satisfies
\begin{equation}
  M(A)\le C\frac{\psi_n\sqrt{\log n}}{\sqrt n}. \tag{2}
\end{equation}
Their equation (10) records the known estimate
$\psi_n\le C\sqrt{\log n}$, so (2) yields
\begin{equation}
  M(A)\le C\frac{\log n}{\sqrt n}. \tag{3}
\end{equation}

\pagebreak
\paragraph{Normalization and identification.}
Skarmogiannis uses the volume-one convention
$\operatorname{Cov}(K_*)=L_{K_*}^2 I$.  Set
$A=K_*/L_{K_*}$.  Then $A$ is covariance-one isotropic and, by homogeneity
of the Minkowski functional,
\[
  M(A)=L_{K_*}M(K_*).
\]
Therefore (3) is exactly (1), with $b=1$.  Substitution into
Skarmogiannis's Theorem~1.1, whose remaining loss is $(\log n)^5$, gives
the affirmative answer
\begin{equation}
  c\|\mathbf t\|_2
  \le \|\mathbf t\|_{K^s,K}
  \le C(\log n)^6\|\mathbf t\|_2             \tag{4}
\end{equation}
for all $s\ge1$, after the source's volume normalization.

This is a separate-paper explicit answer: on PDF page 7, immediately after
Corollary~1.7, Bizeul--Klartag cite Skarmogiannis and state that their
corollary completes, up to polylogarithmic factors, the conjecture attributed
to V.~Milman on multi-integral norms.

\paragraph{Scope and search evidence.}
Equation (4) settles the qualitative polylogarithmic-equivalence question and
provides exponent $6$.  It does not assert that this exponent is optimal.
The run's four cheap indexes had no prior record for arXiv:2208.06365 or
arXiv:2510.20511.  Exact-title and exact-$M(K)$ searches located the 2025
preprint; its Corollary~1.7 and explicit citation of the source establish that
this is known literature rather than a new proof produced by the run.

\begin{thebibliography}{9}
\bibitem{S}
N.~Skarmogiannis,
\emph{On a multi-integral norm defined by weighted sums of log-concave
random vectors}, arXiv:2208.06365 (2022), Mathematika 69 (2023).

\bibitem{BK}
P.~Bizeul and B.~Klartag,
\emph{Distances between non-symmetric convex bodies: optimal bounds up to
polylog}, arXiv:2510.20511 (2025).
\end{thebibliography}

\end{document}
