\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status for Q8 of arXiv:0901.3029}
\author{FA/Banach run packet}
\date{June 19, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{Result type:} literature already answered.

\textbf{Source problem:} Assadi--Haghshenas, \emph{Some Classical and Recent
Results Concerning Renorming Theory}, arXiv:0901.3029, Q8 in the final
``Some interesting problems'' list, PDF page 14.

\textbf{Supporting answer:} Hajek--Russo--Somaglia--Todorcevic, \emph{An
Asplund space with norming Markushevich basis that is not weakly compactly
generated}, arXiv:2007.14201, Problem 1.1 and Theorem A, PDF page 2.

\section*{Source Question}

The source survey asks:
\[
\text{(Q8) (Godefroy) Assume an Asplund space }X\text{ has a Markushevich}
\]
\[
\text{basis }\{x_i,f_i\}_{i\in I}\text{ with }\operatorname{span}\{f_i\}_{i\in I}
\text{ norming }X^*.\text{ Is }X\text{ WCG?}
\]

This is the norming Markushevich-basis versus weakly compactly generated
problem attributed to Godefroy.

\section*{Supporting Answer}

The later paper arXiv:2007.14201 restates the same problem as Problem 1.1:
if \(X\) is an Asplund space with a norming Markushevich basis, must \(X\) be
weakly compactly generated? It says that the problem was recorded in several
sources, including GMZ Problem 112, and that the main result is a negative
answer.

Theorem A of arXiv:2007.14201 states that there exists an Asplund space \(X\)
with a \(1\)-norming M-basis such that \(X\) is not WCG. This supplies a direct
counterexample to Q8 of arXiv:0901.3029.

\section*{Scope and Verification}

The identification is direct: the supporting authors explicitly know they are
answering Godefroy's norming-M-basis/WCG problem, and their theorem negates the
exact conclusion asked in Q8. No part of Q8 remains open under this reading.
This packet does not address any of the other questions in arXiv:0901.3029.

Local checks used the TeX sources and PDFs for arXiv:0901.3029 and
arXiv:2007.14201. Cheap run indexes were searched for arXiv:0901.3029,
arXiv:2007.14201, Godefroy, norming Markushevich basis, and WCG. A previous
attempt note had already found the answer paper; this packet promotes the
status only because arXiv:0901.3029 provides a separate extracted
open-problem source.

\section*{References}

\begin{thebibliography}{9}

\bibitem{AssadiHaghshenas2009}
A. Assadi and H. Haghshenas,
\emph{Some Classical and Recent Results Concerning Renorming Theory},
arXiv:0901.3029.
\url{https://arxiv.org/abs/0901.3029}

\bibitem{HRST2020}
P. Hajek, T. Russo, J. Somaglia, and S. Todorcevic,
\emph{An Asplund space with norming Markushevich basis that is not weakly
compactly generated},
arXiv:2007.14201.
\url{https://arxiv.org/abs/2007.14201}

\end{thebibliography}

\end{document}
