\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\raggedright

\newtheorem*{claim}{Claim}
\newcommand{\Hh}{\mathcal H}
\newcommand{\Tr}{\operatorname{Tr}}

\begin{document}

\begin{center}
{\Large Literature-implied answer for arXiv:2310.01450}\\[4pt]
{\large The Continuous Kraus Conjecture follows from POVM entropy}
\end{center}

\paragraph{Status.}
\textbf{literature\_implied\_answer (full)}.  The central inequality is a
rank-one continuous-frame specialization of Rumin's 2011 entropic uncertainty
principle for positive operator-valued measures (POVMs)~\cite{Rumin}.  The
identification below is not presented as a new core uncertainty theorem.

\paragraph{Source question.}
Let $(\Omega,\mu)$ and $(\Delta,\nu)$ be measure spaces, and let
$\{\tau_\alpha\}_{\alpha\in\Omega}$ and
$\{\omega_\beta\}_{\beta\in\Delta}$ be 1-bounded continuous Parseval
frames for a Hilbert space $\Hh$.  With
\[
 c=\sup_{\alpha\in\Omega,\,\beta\in\Delta}
       |\langle\tau_\alpha,\omega_\beta\rangle|,
\]
Conjecture~2.5 on page~4 of Krishna~\cite{Krishna2023} asks whether
\[
 S_\tau(h)+S_\omega(h)\ge -2\log c
 \qquad(h\in\Hh_\tau\cap\Hh_\omega).
 \tag{CK}
\]

\paragraph{Decisive supporting theorem.}
Rumin's Theorem~1.1 on page~2 of~\cite{Rumin} associates probability
densities to two POVMs $P,Q$.  If their Liouville measure satisfies
$\mu_{PQ}\le \mu_P\otimes\mu_Q$, then the sum of the two relative entropies
is at least the von Neumann entropy of the state.  For a pure state, the
latter entropy is zero.

\paragraph{Identification in the sigma-finite case.}
The frames define POVMs by
\begin{align*}
 \langle P(E)x,y\rangle
   &=\int_E\langle x,\tau_\alpha\rangle
        \langle\tau_\alpha,y\rangle\,d\mu(\alpha),\\
 \langle Q(F)x,y\rangle
   &=\int_F\langle x,\omega_\beta\rangle
        \langle\omega_\beta,y\rangle\,d\nu(\beta).
\end{align*}
Parseval gives $P(\Omega)=Q(\Delta)=I$.  For the pure state
$\rho_h=|h\rangle\langle h|$, where $\|h\|=1$, put
\[
 p(\alpha)=|\langle h,\tau_\alpha\rangle|^2,
 \qquad q(\beta)=|\langle h,\omega_\beta\rangle|^2.
\]
These are the two measurement densities, and the Liouville density is
\[
 |\langle\tau_\alpha,\omega_\beta\rangle|^2\le c^2.
\]
Use the reference measures $\mu_P=c\mu$ and $\mu_Q=c\nu$.  Their product
dominates the Liouville measure, while the measurement densities with respect
to them are $p/c$ and $q/c$.  Rumin's theorem therefore yields
\begin{align*}
0
&\le -\int_\Omega \frac{p}{c}\log\!\left(\frac{p}{c}\right)c\,d\mu
     -\int_\Delta \frac{q}{c}\log\!\left(\frac{q}{c}\right)c\,d\nu\\
&=S_\tau(h)+S_\omega(h)+2\log c,
\end{align*}
which is exactly \textup{(CK)}.

\paragraph{The unrestricted measure-space wording.}
Rumin assumes sigma-finite reference measures in order to obtain abstract
Radon--Nikodym densities.  Here the densities $p,q$ are already explicit, and
his proof specializes without that step.  For completeness, assume the two
entropies are finite (otherwise \textup{(CK)} is immediate) and define
\[
 A=\frac1c\int_\Omega p(\alpha),|\tau_\alpha\rangle
      \langle\tau_\alpha|\,d\mu(\alpha),
 \qquad
 B=\frac1c\int_\Delta q(\beta),|\omega_\beta\rangle
      \langle\omega_\beta|\,d\nu(\beta).
\]
These positive operators are trace class because the frames are 1-bounded
and $\int p=\int q=1$.  Moreover, using an iterated positive integral,
\begin{align*}
 \Tr(A^{1/2}BA^{1/2})
 &=\frac1{c^2}\int_\Omega p(\alpha)
      \left(\int_\Delta q(\beta)
       |\langle\tau_\alpha,\omega_\beta\rangle|^2,d\nu(\beta)\right)
       d\mu(\alpha)\\
 &\le \left(\int_\Omega p\,d\mu\right)
       \left(\int_\Delta q\,d\nu\right)=1.
\end{align*}
Golden--Thompson and the Gibbs variational formula, exactly as in the proof
of Rumin's Theorem~1.1, give
\[
 -\langle(\log A)h,h\rangle-\langle(\log B)h,h\rangle\ge0.
\]
Operator Jensen for the operator-convex function $-\log$, applied to the two
POVM integrals, gives
\begin{align*}
 -\langle(\log A)h,h\rangle
 &\le -\int_\Omega p\log(p/c)\,d\mu=S_\tau(h)+\log c,\\
 -\langle(\log B)h,h\rangle
 &\le -\int_\Delta q\log(q/c)\,d\nu=S_\omega(h)+\log c.
\end{align*}
Rumin's monotone form-domain argument handles possible zero densities.  The
last three displays again give \textup{(CK)}, without sigma-finiteness.
If $c=0$, Parseval for the $\omega$-frame would force every $\tau_\alpha=0$,
contradicting Parseval for the $\tau$-frame on a nonzero space; hence the
logarithm above always has $c>0$.  The real case follows by complexification.

\begin{claim}
The Continuous Kraus Conjecture, Conjecture~2.5 of arXiv:2310.01450, is true
for the stated measure spaces and 1-bounded continuous Parseval frames.
\end{claim}

\paragraph{Independent later confirmation.}
Theorem~2.4 on page~3 of Krishna~\cite{Krishna2024} proves a continuous
operator-valued-frame uncertainty inequality on finite measure spaces by
Riesz--Thorin interpolation.  Taking the coefficient space to be the scalar
field and
$A_\alpha x=\langle x,\tau_\alpha\rangle$,
$B_\beta x=\langle x,\omega_\beta\rangle$ gives
$\|B_\beta A_\alpha^*\|=|\langle\tau_\alpha,\omega_\beta\rangle|$ and hence
the finite-measure case of \textup{(CK)} verbatim.

\paragraph{Provenance and scope.}
Rumin's theorem predates the conjecture, so its author did not explicitly
know he was answering it.  Krishna's 2024 paper does not cite or name
Conjecture~2.5.  Thus the relation is an agent-identified implication and the
packet belongs in \texttt{literature\_implied\_answers}.  The entropy
inequality is fully resolved; the separate equality-characterization
Question~2.4 of~\cite{Krishna2023} remains outside this packet.

\paragraph{Search evidence.}
The run's four cheap indexes contained no record for arXiv:2310.01450.  A
bounded arXiv/web search used the phrases ``Continuous Kraus Conjecture'',
``continuous frames entropic uncertainty'', ``POVM entropic uncertainty'',
and the exact arXiv id.  It found Rumin's earlier theorem and Krishna's 2024
finite-measure theorem, but no paper explicitly naming Conjecture~2.5 as
resolved.

\begin{thebibliography}{9}
\bibitem{Krishna2023}
K. Mahesh Krishna,
\emph{Continuous Deutsch Uncertainty Principle and Continuous Kraus
Conjecture}, arXiv:2310.01450 (2023).

\bibitem{Rumin}
M. Rumin,
\emph{An entropic uncertainty principle for positive operator valued
measures}, arXiv:1109.5889v2 (2011).

\bibitem{Krishna2024}
K. Mahesh Krishna,
\emph{Continuous Krishna--Parthasarathy Entropic Uncertainty Principle},
arXiv:2405.08003 (2024), published in
\emph{Infinite Dimensional Analysis, Quantum Probability and Related Topics},
doi:10.1142/S0219025724400022.
\end{thebibliography}

\end{document}
