\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\emergencystretch=3em

\title{A ZFC Answer To A Steinhaus Property Renorming Question}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_06}}
\date{June 18, 2026}

\begin{document}
\maketitle

\section*{Status}

This is a \textbf{literature-already-answered} packet.  It records a later
paper that explicitly answers one question left open in Kania--Kochanek
\cite{KK}.  No original proof is claimed here.

\section*{Source Question}

The source paper is Kania--Kochanek, arXiv:1302.6443 \cite{KK}.
In the introduction, after Theorem B, the authors explain that their example of a Banach space with
property \((S)\) but with no equivalent strictly convex norm assumes that the
continuum is a real-valued measurable cardinal.  They then write that it
remains open whether such constructions can be obtained in ZFC.

\section*{Supporting Answer}

The supporting paper is Johnson--Kania, \emph{Uniform Property (S)},
arXiv:2602.09106 \cite{JK}.  In its introduction, immediately before and
after Corollary 1.5, it states that Theorem A positively answers the question
left open in \cite{KK} about the existence, in ZFC, of spaces with property
\((S)\) that do not admit equivalent strictly convex norms.

The mechanism is that for every Banach space \(X\), the Bochner space
\[
  L_1([0,1],X)
\]
has uniform property \((S)\), hence property \((S)\), and contains \(X\)
isometrically as the constant functions.  Choosing \(X\) to be a Banach space
with no equivalent strictly convex renorming, such as \(\ell_\infty(\Gamma)\)
for uncountable \(\Gamma\) or \(\ell_\infty/c_0\), gives in ZFC a Banach
space with property \((S)\) and no equivalent strictly convex norm.

\section*{Scope Limitation}

This packet is only about the ZFC existence question for property \((S)\)
spaces that are not strictly convexifiable.  It does \emph{not} answer the
separate question, also raised in \cite{KK}, whether every Banach space admits
an equivalent norm satisfying property \((F)\), meaning that the unit sphere
has no non-empty relatively open subset contained in a hyperplane.

\begin{thebibliography}{9}
\bibitem{KK}
T. Kania and T. Kochanek,
\emph{Steinhaus' lattice-point problem for Banach spaces},
J. Math. Anal. Appl. 446 (2017), 1219--1229;
arXiv:1302.6443.

\bibitem{JK}
W. B. Johnson and T. Kania,
\emph{Uniform Property (S)},
arXiv:2602.09106.
\end{thebibliography}

\end{document}
