\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\ellTwo}{\ell_2}

\begin{document}

\begin{center}
{\Large Partial result}\\[3pt]
{\large Separable Banach spaces have smooth non-complete norms}
\end{center}

\paragraph{Status.}
\textbf{partial\_result\_likely\_valid.}

\paragraph{Source question.}
In Daniel Azagra, Tadeusz Dobrowolski, and Miguel Garcia-Bravo,
\emph{Smooth approximations without critical points of continuous mappings
between Banach spaces, and diffeomorphic extractions of sets},
arXiv:1811.07587, page 13, just before Lemma 2.10, the authors state that
it is not known whether every infinite-dimensional Banach space with a
\(C^1\) equivalent norm possesses a \(C^1\) smooth non-complete norm.  They
add that for \(C^k\), \(k\ge2\), the answer is positive.

\paragraph{Result.}
The separable case has a simple positive answer, even without assuming the
existence of a smooth equivalent norm.

\begin{theorem}
Let \(X\) be an infinite-dimensional separable Banach space.  Then \(X\)
admits a continuous norm \(|\cdot|\) such that:
\begin{enumerate}
\item \(|\cdot|\) is \(C^\infty\) smooth on \(X\setminus\{0\}\);
\item the normed space \((X,|\cdot|)\) is not complete.
\end{enumerate}
\end{theorem}

\paragraph{Idea of the proof.}
Separable spaces have countably many norm-one functionals which separate
points.  Weighting them by a square-summable scalar sequence gives a compact
injective operator into Hilbert space.  Pulling back the Hilbert norm gives
smoothness.  Compactness prevents this pulled-back norm from being complete:
if it were complete, the compact injective operator would be bounded below,
which is impossible in infinite dimension.

\paragraph{Proof.}
Choose a sequence \((u_n)\) dense in the unit sphere \(S_X\).  For each
\(n\), pick \(x_n^*\in S_{X^*}\) with \(x_n^*(u_n)=1\).  The family
\((x_n^*)\) separates points: if \(x\ne0\), choose \(n\) with
\(\|u_n-x/\|x\|\|<1/2\).  Then
\[
x_n^*(x/\|x\|)\ge x_n^*(u_n)-\|u_n-x/\|x\|\|>1/2.
\]

Define
\[
T:X\longrightarrow \ellTwo,\qquad
Tx=\bigl(2^{-n}x_n^*(x)\bigr)_{n=1}^{\infty}.
\]
Then \(T\) is bounded, injective, and compact.  Indeed, the finite-rank
truncations
\[
T_Nx=(2^{-n}x_n^*(x))_{n=1}^N
\]
satisfy
\[
\|T-T_N\|\le
\left(\sum_{n>N}4^{-n}\right)^{1/2},
\]
so \(T\) is a norm-limit of finite-rank operators.

Set
\[
|x|=\|Tx\|_{\ellTwo}.
\]
Because \(T\) is injective, this is a norm on \(X\), and it is continuous
with respect to the original Banach norm.  Since the Hilbert norm on
\(\ellTwo\) is \(C^\infty\) on \(\ellTwo\setminus\{0\}\), and \(Tx\ne0\)
whenever \(x\ne0\), the composition \(x\mapsto\|Tx\|_{\ellTwo}\) is
\(C^\infty\) on \(X\setminus\{0\}\).

It remains to show that \((X,|\cdot|)\) is not complete.  Suppose otherwise.
Then \(T\) is an isometry from \((X,|\cdot|)\) onto \(T(X)\), so \(T(X)\)
is a closed subspace of \(\ellTwo\).  Hence \(T:X\to T(X)\), viewed as a
bounded bijection from the original Banach space \(X\) onto the Banach space
\(T(X)\), has bounded inverse by the open mapping theorem.  Thus \(T\) is
bounded below in the original norm.

But a compact operator on an infinite-dimensional Banach space cannot be
bounded below.  If it were, the compact set \(\overline{T(B_X)}\) would pull
back under \(T^{-1}\) to a compact set containing the original unit ball
\(B_X\), contradicting Riesz's lemma.  Therefore \((X,|\cdot|)\) is not
complete.

\paragraph{Scope and novelty check.}
This proves the source question for separable spaces, and actually gives a
\(C^\infty\) norm.  It does not address nonseparable spaces, where the proof's
countable separating family is unavailable.  The run indexes had no prior
packet or attempt for arXiv:1811.07587 or smooth non-complete norms.  Bounded
web searches for ``smooth non-complete norm'', ``C1 smooth non-complete
norm'', and variants found no direct later answer; the argument is elementary
and may be folklore, so human review should treat novelty cautiously.

\paragraph{Review note.}
Check that the source's phrase about a smooth non-complete norm is intended
in the standard sense used nearby: a continuous norm on the underlying
Banach space, smooth away from the origin, whose induced normed topology is
not complete.  Under that reading, the proof is complete for the separable
case.

\paragraph{Reference.}
D. Azagra, T. Dobrowolski, and M. Garcia-Bravo,
\emph{Smooth approximations without critical points of continuous mappings
between Banach spaces, and diffeomorphic extractions of sets},
arXiv:1811.07587.

\end{document}
