\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
\usepackage[margin=1in]{geometry}

\newtheorem*{proposition}{Proposition}

\title{Lushness of vector-valued \(L_1\): a literature-implied answer}
\author{Status note for arXiv:1407.7848}
\date{23 July 2026}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_implied\_answer (full)}.

\section*{Source question}

Choi, Kim, Lee, and Mart\'in ask on page 7, immediately after
Corollary 2.13 of \cite{CKLM}:
\begin{quote}
Whether \(L_1(\mu,X)\) is lush for every lush space \(X\) is not known
to the best of our knowledge.
\end{quote}
The surrounding results allow an arbitrary measure \(\mu\).

\section*{Supporting theorem}

Kadets, Mart\'in, Mer\'i, and P\'erez prove in
\cite[Theorem 8.10(b) and Corollary 8.12, p.~92]{KMMB} that, for every
sigma-finite measure \(\nu\),
\[
  X\text{ is lush}\quad\Longleftrightarrow\quad
  L_1(\nu,X)\text{ is lush}.
\]
Their Remark 8.11 says that the lushness assertion is new even for the
identity operator.

\section*{Identification in the arbitrary-measure case}

\begin{proposition}
Let \((\Omega,\Sigma,\mu)\) be an arbitrary measure space.  If \(X\) is
lush, then \(L_1(\mu,X)\) is lush.
\end{proposition}

\begin{proof}
Fix \(f,g\in S_{L_1(\mu,X)}\).  Up to null sets, put
\[
 A=\{\omega:\|f(\omega)\|+\|g(\omega)\|>0\}.
\]
This set is sigma-finite: writing
\[
 A_n=\{\omega:\|f(\omega)\|+\|g(\omega)\|\ge 1/n\},
\]
we have
\[
 \mu(A_n)\le n\bigl(\|f\|_1+\|g\|_1\bigr)=2n,
 \qquad A=\bigcup_{n\ge1}A_n.
\]
Consequently \(Z=L_1(\mu|_A,X)\), identified with the closed subspace
of functions supported in \(A\), is lush by Corollary 8.12 of
\cite{KMMB}.

Given \(\varepsilon>0\), apply lushness in \(Z\) to \(f,g\).  It gives
\(z^*\in S_{Z^*}\) such that \(f\) belongs to the relevant
\(\varepsilon\)-slice of \(B_Z\) and \(g\) lies within \(\varepsilon\)
of its absolutely convex hull.  Extend \(z^*\) to
\(\widetilde z^*\in S_{L_1(\mu,X)^*}\) by Hahn--Banach.  The slice of
\(B_Z\) is contained in the corresponding slice of
\(B_{L_1(\mu,X)}\), so the same witness works for \(f,g\) in the
ambient space.  Since \(f,g\) and \(\varepsilon\) were arbitrary,
\(L_1(\mu,X)\) is lush.
\end{proof}

\section*{Provenance and scope}

The sigma-finite theorem is explicit in the supporting source.  The
passage to an arbitrary measure via the joint sigma-finite support of
two Bochner-integrable functions is the direct identification recorded
here.  Thus the entire forward implication asked in \cite{CKLM} is
settled, but the provenance is a known theorem plus a short reduction,
not a new result of this run.

\begin{thebibliography}{9}
\bibitem{CKLM}
Y. S. Choi, S. K. Kim, H. J. Lee, and M. Mart\'in,
\emph{On Banach spaces with the approximate hyperplane series property},
Banach J. Math. Anal. 9 (2015), no. 4, 243--258;
\href{https://arxiv.org/abs/1407.7848}{arXiv:1407.7848}.

\bibitem{KMMB}
V. Kadets, M. Mart\'in, J. Mer\'i, and A. P\'erez,
\emph{Spear operators between Banach spaces},
Lecture Notes in Mathematics 2205, Springer, 2018;
\href{https://arxiv.org/abs/1701.02977}{arXiv:1701.02977}.
\end{thebibliography}

\end{document}

