\documentclass[11pt]{amsart}
\usepackage[margin=1.05in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[theorem]{Corollary}

\newcommand{\PHS}{\mathrm{PS}_2}
\newcommand{\PiTwo}{\Pi_2}
\newcommand{\calL}{\mathcal L}

\title[Locally Split PHS Factorization]{Locally Split-Range Pre-Hilbert-Schmidt Operators Factor Through Hilbert-Schmidt Spaces}
\author{fa\_banach\_001, agent\_lane\_03}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: strengthened partial result, likely valid.}
This proves the final Abdillah--Esterle--Haak conjecture \cite{AEH}
for pre-Hilbert-Schmidt operators whose natural range factorization is
locally split on both sides. It does not solve the general case.

\section*{Source Problem}

In Section 5 of \cite{AEH}, the authors define $u\in\calL(E,F)$ to be
pre-Hilbert-Schmidt if $wuv:H_1\to H_2$ is Hilbert-Schmidt for every
pair of Hilbert spaces $H_1,H_2$ and every pair of bounded operators
$v:H_1\to E$, $w:F\to H_2$. They denote this class by $\PHS(E,F)$.

At the end of the section, they conjecture that every
pre-Hilbert-Schmidt operator $u:E\to F$ factors through a
Hilbert-Schmidt space. They also prove two facts used here:
\[
  \PHS(E,H)=\PiTwo(E,H)
\]
for every Banach space $E$ and Hilbert space $H$, and a Banach space
$Y$ is Hilbert-Schmidt iff $\calL(Y,H)=\PiTwo(Y,H)$ for every Hilbert
space $H$.

\section*{Proof Intuition}

The source's condition is global in the outer Hilbert-space tests, but
the $2$-summing condition is finite-dimensional in the input sequence.
Thus bounded inverses are not really needed on all of $Y$. It is enough
to extend and lift each finite-dimensional piece of $Y$ with uniform
constants. The only extra point is that a pre-Hilbert-Schmidt operator
has a uniform testing constant; otherwise a direct sum of bad Hilbert
tests would contradict the definition.

\section*{Uniform Testing Lemma}

\begin{theorem}
Let $u:E\to F$ be pre-Hilbert-Schmidt. There is a constant $C_u<\infty$
such that, for every Hilbert space $H$ and every bounded $W:F\to H$,
the operator $Wu:E\to H$ is $2$-summing and
\[
  \pi_2(Wu)\le C_u\|W\|.
\]
\end{theorem}

\begin{proof}
For fixed $W$, Proposition 5.4 of \cite{AEH} gives $Wu\in\Pi_2(E,H)$.
It remains to see that the constants are uniform over Hilbert targets.
Suppose not. Then for each $n$ there are Hilbert spaces $H_n,K_n$ and
contractions $W_n:F\to H_n$, $V_n:K_n\to E$ such that
\[
  \|W_nuV_n\|_{\mathrm{HS}}>2^{2n}.
\]
Let $K=(\oplus_n K_n)_2$ and $H=(\oplus_n H_n)_2$. Define
\[
  V((x_n))=\sum_{n\ge 1}2^{-n}V_nx_n,\qquad
  Wf=(2^{-n}W_nf)_{n\ge 1}.
\]
Then $V:K\to E$ and $W:F\to H$ are bounded. Since $u$ is
pre-Hilbert-Schmidt, $WuV:K\to H$ is Hilbert-Schmidt. But its
diagonal compression to the $n$th summand is
$2^{-2n}W_nuV_n$, so
\[
  \|WuV\|_{\mathrm{HS}}^2
  \ge \sum_{n\ge 1} 2^{-4n}\|W_nuV_n\|_{\mathrm{HS}}^2
  > \sum_{n\ge 1}1,
\]
a contradiction.
\end{proof}

\section*{Theorem}

\begin{theorem}
Let $E,F,Y$ be Banach spaces and let $u:E\to F$ be
pre-Hilbert-Schmidt. Suppose that
\[
  u = j q,\qquad q:E\to Y,\qquad j:Y\to F,
\]
where $q$ is onto and $j$ is an isomorphic embedding. Assume there are
constants $\lambda,\mu<\infty$ such that:
\begin{itemize}
\item for every finite-dimensional $M\subset Y$ there is
  $R_M:M\to E$ with $qR_M=\mathrm{id}_M$ and $\|R_M\|\le\lambda$;
\item for every finite-dimensional $M\subset Y$ there is
  $L_M:F\to M$ with $L_Mj|_M=\mathrm{id}_M$ and $\|L_M\|\le\mu$.
\end{itemize}
Then $Y$ is a Hilbert-Schmidt space. Consequently $u$ factors through a
Hilbert-Schmidt space.
\end{theorem}

\begin{proof}
Let $H$ be a Hilbert space and let $B:Y\to H$ be bounded. We prove that
$B$ is $2$-summing. Let $y_1,\ldots,y_n\in Y$ and put
$M=\mathrm{span}\{y_1,\ldots,y_n\}$. Choose $R_M$ and $L_M$ as in the
hypotheses, and set
\[
  W=B|_M L_M:F\to H.
\]
Then $\|W\|\le\mu\|B\|$. By the uniform testing lemma,
$Wu:E\to H$ is $2$-summing with
$\pi_2(Wu)\le C_u\mu\|B\|$. Since $u=jq$ and $L_Mj$ is the identity on
$M$, for $1\le k\le n$ we have
\[
  WuR_My_k=B L_Mj qR_My_k=By_k.
\]
Therefore
\[
  \Big(\sum_{k=1}^n\|By_k\|^2\Big)^{1/2}
  \le C_u\mu\|B\|\,
  \|(R_My_k)_{k=1}^n\|_{\ell_2^w(E)}.
\]
Finally
\[
  \|(R_My_k)_{k=1}^n\|_{\ell_2^w(E)}
  \le \lambda\,\|(y_k)_{k=1}^n\|_{\ell_2^w(Y)}.
\]
Thus $\pi_2(B)\le C_u\lambda\mu\|B\|$.

Every bounded operator from $Y$ into an arbitrary Hilbert space is
$2$-summing. By Theorem 5.6 of \cite{AEH}, $Y$ is a Hilbert-Schmidt
space. The displayed factorization $u=jq$ is then a factorization
through a Hilbert-Schmidt space.
\end{proof}

\begin{corollary}
Let $u:E\to F$ be pre-Hilbert-Schmidt. If $u=jq$ and $q,j$ have bounded
right and left inverses, respectively, then the intermediate space is a
Hilbert-Schmidt space.
\end{corollary}

\begin{proof}
Use the same inverses on every finite-dimensional subspace.
\end{proof}

\begin{corollary}
Let $u:E\to F$ be pre-Hilbert-Schmidt. Suppose $u(E)$ is closed,
locally complemented in $F$ with a uniform constant, and the quotient
map $E\to u(E)$ locally lifts finite-dimensional subspaces with a
uniform constant. Then $u(E)$ is a Hilbert-Schmidt space, and $u$
factors through it.
\end{corollary}

\begin{proof}
Take $Y=u(E)$, let $j:Y\hookrightarrow F$ be the inclusion, and apply
the theorem.
\end{proof}

\begin{corollary}
If $P:E\to E$ is a pre-Hilbert-Schmidt projection, then $P(E)$ is a
Hilbert-Schmidt space.
\end{corollary}

\begin{proof}
Apply the theorem with $Y=P(E)$, $q=P:E\to Y$, $j:Y\hookrightarrow E$,
$R=j$, and $L=P$.
\end{proof}

\section*{Limitations and Failed Stronger Route}

The result needs both local splitting hypotheses. Complemented range
alone is not enough for this proof: transferring a $2$-summing estimate
from $Bq:E\to H$ to $B:Y\to H$ through a quotient map $q:E\to Y$ would
require uniform lifting of finite weak $\ell_2$ configurations, which is
false in general. For instance, a quotient map $\ell_1\to\ell_2$ would
otherwise force the identity on $\ell_2$ to be $2$-summing.

Thus the unsolved part of the source conjecture remains the genuinely
non-locally-split case, where Hilbert-valued maps on finite pieces of
the range cannot be moved back and forth through the factorization with
uniform constants.

\section*{Novelty Check}

The cheap run indexes were searched for arXiv:1406.7546, the source
title, and the terms ``pre-Hilbert-Schmidt'', ``Hilbert-Schmidt
space'', and ``factorization''. A web search for exact French and
English phrases around the conjecture found the source arXiv paper and
the Studia Mathematica journal page, but no later exact answer to the
full conjecture. This packet is therefore recorded as a strengthened
partial result, not a literature answer and not a full solution.

\begin{thebibliography}{9}

\bibitem{AEH}
Said Amana Abdillah, Jean Esterle, and Bernhard H. Haak,
\emph{Sur quelques extensions au cadre Banachique de la notion
d'operateur de Hilbert-Schmidt},
arXiv:1406.7546; Studia Mathematica 227 (2015), 193--218.
\url{https://arxiv.org/abs/1406.7546}

\end{thebibliography}

\end{document}
