\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note: Problem U in Totally Smooth Renormings}
\author{fa\_banach\_001, agent\_lane\_03}
\date{2026-06-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature\_already\_answered.}
The Problem U and Problem U convex from Oja--Viil--Werner,
\emph{Totally smooth renormings}, arXiv:1807.07335, are answered
positively in full generality by Cobollo--Guirao--Montesinos,
\emph{A remark on totally smooth renormings}, arXiv:2305.11611.

\section*{Source Question}

The source paper is Eve Oja, Tauri Viil, and Dirk Werner,
\emph{Totally smooth renormings}, arXiv:1807.07335, Archiv der
Mathematik 112 (2019), 269--281.

In the introduction, after recalling that an $M$-ideal in its bidual has
property $U$, the authors ask:
\begin{quote}
If $X$ has property $U$ in its bidual $X^{**}$, then does $X$ admit an
equivalent norm under which $X$ is totally smooth in its bidual?
\end{quote}
They label this as Problem U. They then use the Taylor--Foguel
characterization to reformulate it as Problem U convex:
\begin{quote}
If $X$ has property $U$ in its bidual $X^{**}$, then does $X$ admit an
equivalent norm under which the dual space $X^*$ is strictly convex and
$X$ still has property $U$ in its bidual?
\end{quote}
The same paper proves separable and WCG cases, with Theorem 3.3 giving
the WCG partial answer.

\section*{Supporting Answer}

The supporting paper is Ch. Cobollo, A. J. Guirao, and V. Montesinos,
\emph{A remark on totally smooth renormings}, arXiv:2305.11611. Its
abstract explicitly cites Oja--Viil--Werner and states that their WCG
renorming result holds ``in full generality'' and in a stronger form,
using a theorem of M. Raja on dual locally uniformly rotund norms.

The decisive result is Theorem 1 of arXiv:2305.11611. It proves that,
for a Banach space $X$, the following conditions are equivalent:
\begin{enumerate}
\item $X$ has an equivalent norm with Hahn--Banach smoothness (HBS),
      i.e. property $U$ in the bidual.
\item $X$ has an equivalent norm whose dual norm has the
      $WW^*$Kadets property.
\item $X$ has an equivalent norm whose dual norm is LUR.
\item $X$ has an equivalent norm with total smoothness.
\end{enumerate}

The proof combines the Godefroy/Harmand--Werner--Werner equivalence
between HBS and coincidence of the weak and weak-star topologies on the
dual sphere, Raja's equivalence between a dual LUR renorming and an
equivalent $WW^*$Kadets norm, and the Taylor--Foguel theorem relating
total smoothness to HBS plus rotundity of the dual norm.

\section*{Why This Answers Problem U}

Assume $X$ has property $U$ in $X^{**}$ under its original norm. Then
$X$ already satisfies condition (i) of Theorem 1 in arXiv:2305.11611.
Therefore it has an equivalent norm whose dual norm is LUR. In
particular the dual norm is strictly convex. The same theorem also gives
an equivalent norm with total smoothness. Thus Problem U has a positive
answer in full generality.

Moreover, because the LUR dual renorming gives the strict convexity
requested in Problem U convex while preserving the relevant
Hahn--Banach smoothness/property $U$, the equivalent reformulation is
also answered positively.

\section*{Search And Classification Notes}

The local cheap indexes had no prior packet for arXiv:1807.07335,
Problem U, or the title \emph{Totally smooth renormings}. Later local
source arXiv:2506.08458 pointed to the same Raja dual-LUR mechanism, and
an external arXiv search located arXiv:2305.11611, whose abstract and
Theorem 1 explicitly identify the Oja--Viil--Werner problem. Since the
supporting authors knew they were strengthening the Oja--Viil--Werner
result, the correct classification is \texttt{literature\_already\_answered}.

\begin{thebibliography}{9}
\bibitem{OVW}
E. Oja, T. Viil, and D. Werner,
\emph{Totally smooth renormings},
Archiv der Mathematik 112 (2019), 269--281; arXiv:1807.07335.

\bibitem{CGM}
Ch. Cobollo, A. J. Guirao, and V. Montesinos,
\emph{A remark on totally smooth renormings},
arXiv:2305.11611.

\bibitem{Raja}
M. Raja,
\emph{On dual locally uniformly rotund norms},
Israel Journal of Mathematics 129 (2002), 77--91.
\end{thebibliography}

\end{document}
