\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note: The Heisenberg Ball \(L_1\) Distortion Exponent}
\author{fa\_banach\_001, agent\_lane\_03}
\date{2026-06-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature\_already\_answered.}
The open exponent problem in Austin--Naor--Tessera,
\emph{Sharp quantitative nonembeddability of the Heisenberg group into
superreflexive Banach spaces}, arXiv:1007.4238, is answered by
Naor--Young, \emph{Foliated corona decompositions}, arXiv:2004.12522.

\section*{Source Question}

Let \(B_R\) be the radius \(R\) word ball in the discrete Heisenberg group
\[
\mathbb H=\langle a,b\mid aba^{-1}b^{-1}\text{ is central}\rangle,
\]
and let \(c_{L_1}(B_R)\) denote the least bi-Lipschitz distortion of
\((B_R,d_W)\) into \(L_1\).

In the subsection ``Bi-Lipschitz distortion of balls'', Austin--Naor--Tessera
recall the Cheeger--Kleiner--Naor estimate
\[
c_{L_1}(B_R)\gtrsim (\log R)^c
\]
for some universal \(c>0\), and state that evaluating the supremum over
those \(c>0\) remains an important open problem.

\section*{Supporting Answer}

The supporting paper is Assaf Naor and Robert Young,
\emph{Foliated corona decompositions}, arXiv:2004.12522. Its introduction
states that the paper answers the asymptotic evaluation question for
\(c_{\ell_1}(B_n)\) and that the previously best lower bound was the
Cheeger--Kleiner--Naor bound \(c_{\ell_1}(B_n)\ge (\log n)^\delta\) for a
small universal \(\delta>0\).

The decisive statement is Theorem 1.6:
\[
c_{\ell_1}(B_n)\asymp \sqrt[4]{\log n}\qquad\text{for every integer }n\ge 2.
\]
Here \(B_n\) is the word ball in the discrete 3-dimensional Heisenberg group.

\section*{Conclusion}

The source question asks for the supremum of exponents \(c\) such that
\[
c_{L_1}(B_R)\gtrsim (\log R)^c.
\]
Naor--Young's two-sided estimate gives both a lower bound with \(c=1/4\)
and an upper bound that rules out every \(c>1/4\). Hence the supremum is
exactly
\[
\boxed{\frac14}.
\]

This is a literature answer rather than a new result from this run. The
supporting paper explicitly identifies the same asymptotic evaluation problem
in the Cheeger--Kleiner--Naor line and resolves it.

\section*{Scope}

This note concerns the 3-dimensional discrete Heisenberg group from the source
paper. Higher-dimensional Heisenberg groups behave differently for \(L_1\):
Naor--Young's earlier vertical-versus-horizontal theorem gives order
\(\sqrt{\log n}\) for the 5-dimensional case. That does not change the answer
to the source question because the source group is the 3-dimensional
\(\mathbb H\).

\begin{thebibliography}{9}
\bibitem{ANT}
T. Austin, A. Naor, and R. Tessera,
\emph{Sharp quantitative nonembeddability of the Heisenberg group into
superreflexive Banach spaces},
Groups Geom. Dyn. 7 (2013), 497--522; arXiv:1007.4238.

\bibitem{NY}
A. Naor and R. Young,
\emph{Foliated corona decompositions},
arXiv:2004.12522.

\bibitem{CKN}
J. Cheeger, B. Kleiner, and A. Naor,
\emph{Compression bounds for Lipschitz maps from the Heisenberg group to \(L_1\)},
Acta Math. 207 (2011), 291--373.
\end{thebibliography}

\end{document}
