\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\N}{\mathbb N}

\title{A Partial Literature Answer to the Frechet Smooth + LUR Renorming Question}
\author{Run fa\_banach\_001}
\date{2026-07-03}

\begin{document}
\maketitle

\paragraph{Status.}
This is a lightweight literature-implied status note:
\[
\texttt{literature\_implied\_answer (partial subcases).}
\]
It records known positive subcases of a question in Gothwal--Shekhar,
\emph{(Asymptotic) uniform smoothness, ball separation and residuality results},
arXiv:2502.18217.

\paragraph{Source question.}
In Section 5, ``Two open problems'', the source asks:
\[
\text{If }X\text{ has an equivalent Frechet smooth norm and an equivalent LUR norm,}
\]
\[
\text{does }X\text{ admit an equivalent norm which is both Frechet smooth and LUR?}
\]
The question is presented as a consequence that would follow from a positive
answer to the preceding residuality question for Frechet smooth norms.

\paragraph{Supporting literature.}
Hajek--Prochazka, \emph{\(C^k\)-smooth approximations of LUR norms},
arXiv:0901.3623, gives several positive cases.  In the introduction they recall
that every separable Asplund space admits an equivalent norm which is
simultaneously \(C^1\)-Frechet smooth and LUR.  Since the existence of a
Frechet smooth norm gives a \(C^1\)-smooth bump and hence Asplundness, this
covers the separable case of the source question.

More generally, their Corollary 4.4 states that if \(X\) admits a
\(C^k\)-Frechet smooth norm and \(X\) is Vasak (WCD), WLD, or \(C(K)\) with
\(K\) Valdivia compact, then \(X\) admits an equivalent \(C^1\)-Frechet smooth
LUR norm.  Taking \(k=1\) gives a direct positive answer to the source question
on these classes.

\paragraph{Scope limitations.}
The supporting paper predates arXiv:2502.18217 and is not presented there as an
answer to that paper's question; the implication is an agent-identified
literature match.  The full arbitrary Banach-space question remains open by
this packet.  The earlier residuality question,
\[
\text{are Frechet smooth equivalent norms residual whenever one exists?}
\]
also remains open; Hajek--Prochazka explicitly note that density/residuality of
\(C^1\)-Frechet smooth norms is unknown even for some \(C([0,\alpha])\) spaces.

\paragraph{References.}
\begin{itemize}
\item D. Gothwal and V. Shekhar, \emph{(Asymptotic) uniform smoothness, ball
separation and residuality results}, arXiv:2502.18217.
\item P. Hajek and A. Prochazka, \emph{\(C^k\)-smooth approximations of LUR
norms}, arXiv:0901.3623.
\end{itemize}

\end{document}
