\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\raggedright

\newtheorem*{claim}{Conclusion}

\begin{document}

\begin{center}
{\Large Literature-implied answer for arXiv:2009.05503}\\[4pt]
{\large The logarithmic-degree level inequality follows from sharp
hypercontractivity}
\end{center}

\paragraph{Status.}
\textbf{literature\_implied\_answer}. This packet records a quantitative
identification with a later theorem; it does not claim a new proof of the
sharp hypercontractive inequality.

\paragraph{Source question.}
In Section~7.1, ``Global functions are concentrated on the high degrees''
(PDF page~30), Filmus--Kindler--Lifshitz--Minzer write, immediately after
restating their Theorem~1.6:
\begin{quote}
It would be interesting to prove a quantitatively better version of
Theorem~1.6 in terms of $d$, and in particular whether it is the case that for
$d=c\log(1/\varepsilon)$ it holds that
$\lVert f^{=d}\rVert_2^2=\varepsilon^{2-o(1)}$ for sufficiently small (but
constant) $c>0$.
\end{quote}
The surrounding paragraph concerns an improved upper bound. Literal equality
cannot be intended for every admissible function (take $f=0$), so below the
display is read as the requested upper-bound scale.

Here a Boolean function $f:S_n\to\{0,1\}$ is
$(2d,\varepsilon)$-global if every consistent restriction fixing at most
$2d$ input-output pairs has $L^2$-norm at most $\varepsilon$.

\paragraph{Later theorem.}
Keevash--Lifshitz, arXiv:2307.15030, Theorem~4.1 (PDF page~20), proves the
following. If $g\in L^2(S_n)$ is
$(r,\gamma_1,\gamma_2,d)$-biglobal, $r>1$, and
\[
d\leq\min\left\{\frac14\log(\gamma_2/\gamma_1),10^{-5}n\right\},
\]
then
\[
 \lVert g^{=d}\rVert_2^2
 \leq \gamma_1^2
 \left(10^6r^2d^{-1}\log(\gamma_2/\gamma_1)\right)^d.
\]
Their Definition~2.4 says that biglobalness means every restriction of size
$t\leq d$ has $L^1$-norm at most $r^t\gamma_1$ and $L^2$-norm at most
$r^t\gamma_2$.

\paragraph{Parameter identification.}
Assume $0<\varepsilon<1$ and that $f:S_n\to\{0,1\}$ is
$(2d,\varepsilon)$-global in the 2020 sense. For every restriction $f_*$ of
size at most $d$,
\[
 \lVert f_*\rVert_2\leq\varepsilon,
 \qquad
 \lVert f_*\rVert_1=\lVert f_*\rVert_2^2\leq\varepsilon^2,
\]
where the identity uses that $f_*$ remains Boolean. Thus $f$ is
$(2,\varepsilon^2,\varepsilon,d)$-biglobal. Theorem~4.1 gives
\begin{equation}\label{eq:sharp}
 \lVert f^{=d}\rVert_2^2
 \leq \varepsilon^4
 \left(4\cdot10^6d^{-1}\log(1/\varepsilon)\right)^d
\end{equation}
provided
\[
d\leq\min\left\{\frac14\log(1/\varepsilon),10^{-5}n\right\}.
\]

Set $L=\log(1/\varepsilon)$ and $d=cL$ (rounding to an integer if needed).
Then the right-hand side of \eqref{eq:sharp} is
\[
 \varepsilon^{\,4-c\log(4\cdot10^6/c)}.
\]
As $c\downarrow0$, the exponent tends to $4$. In particular, one may choose
an absolute $c>0$ sufficiently small that the exponent is strictly larger
than $2$ (indeed, larger than $3$). This is stronger than an
$\varepsilon^{2-o(1)}$ upper bound.

\begin{claim}
The intended logarithmic-degree upper-bound question in arXiv:2009.05503 has
an affirmative answer by Keevash--Lifshitz, Theorem~4.1. Their theorem also
replaces the source's very large lower bound on $n$ by the essentially linear
condition $d\leq10^{-5}n$ for this application.
\end{claim}

\paragraph{Scope.}
This identification answers the explicit quantitative level-$d$ subquestion.
It does not claim that every separate technical condition in all of the 2020
paper's hypercontractive theorems can be removed, nor does it address the
broader junta-method problem for arbitrary product-free subsets of $A_n$.
The Kruskal--Katona stability question later mentioned in the 2020 paper is
answered in that same paper and is therefore an extraction false positive.

\paragraph{Search evidence.}
The run's cheap indexes contained no packet for arXiv:2009.05503. Searches for
the paper title, ``level-$d$'', ``global'', and ``symmetric group
hypercontractivity'' led to arXiv:2307.15030. Its source was checked at
Definition~2.4 and Theorem~4.1, and the parameter substitution above was
performed directly.

\begin{thebibliography}{9}
\bibitem{FKLM}
Y. Filmus, G. Kindler, N. Lifshitz, and D. Minzer,
\emph{Hypercontractivity on the symmetric group},
arXiv:2009.05503 (2020).

\bibitem{KL}
P. Keevash and N. Lifshitz,
\emph{Sharp hypercontractivity for symmetric groups and its applications},
arXiv:2307.15030 (2023).
\end{thebibliography}

\end{document}

