\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\title{Literature Status: An \texorpdfstring{$\mathcal L_\infty$}{L-infinity} HI Space With No Reflexive Subspace}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_09}}
\date{2026-06-15}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight \texttt{literature\_already\_answered} packet. It records
that a future-work existence problem announced in Argyros--Motakis,
\emph{A dual method of constructing hereditarily indecomposable Banach spaces},
arXiv:1504.01564, is answered in the separate later paper
Argyros--Motakis, \emph{The scalar-plus-compact property in spaces without
reflexive subspaces}, arXiv:1608.01962.

\section*{Source Question}

In the introduction of arXiv:1504.01564, PDF page 2, parsed source lines
159--161, the authors discuss the problem of constructing a norming set whose
space has a shrinking Schauder basis and no subspace with a boundedly complete
basis. They state that this is directly related to the existence of an
$\mathcal L_\infty$ space that is hereditarily indecomposable and has no
reflexive subspace. The paper answers the first problem and announces the
second as forthcoming: there exists an $\mathcal L_\infty$ HI space with no
reflexive subspace.

\section*{Supporting Answer}

The supporting paper arXiv:1608.01962 cites arXiv:1504.01564 as the dual
method paper. Its abstract constructs a hereditarily indecomposable
$\mathcal L_\infty$ space $\mathfrak X_{\mathfrak{nr}}$ which contains no
$c_0$, no $\ell_1$, and no reflexive subspace, and which satisfies the
scalar-plus-compact property.

The theorem-level evidence is explicit. Theorem 6.12 states that
$\mathfrak X_{\mathfrak{nr}}$ contains no reflexive subspace. Theorem 6.10
states that every strictly singular operator on $\mathfrak X_{\mathfrak{nr}}$
is compact, hence $\mathfrak X_{\mathfrak{nr}}$ satisfies the
scalar-plus-compact property. The introduction also states that this is the
first example of an $\mathcal L_\infty$ HI space not containing a reflexive
subspace.

\section*{Scope}

This is not a new proof. It records the already-known later answer to the
$\mathcal L_\infty$ HI/no-reflexive-subspace existence statement announced in
arXiv:1504.01564. The first norming-set problem in the same source paper is
answered by that source paper itself and is therefore not counted as a separate
literature-answer packet.

\section*{References}

\begin{itemize}
\item S. A. Argyros and P. Motakis, \emph{A dual method of constructing
hereditarily indecomposable Banach spaces}, arXiv:1504.01564.
\item S. A. Argyros and P. Motakis, \emph{The scalar-plus-compact property in
spaces without reflexive subspaces}, arXiv:1608.01962.
\end{itemize}

\end{document}
