\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\title{Literature Status: Johnson--Odell Elastic Space Problem}
\author{run fa\_banach\_001}
\date{2026-06-30}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight \emph{literature already answered} packet for
arXiv:math/0310023. It records that a source problem in Johnson--Odell is
explicitly answered by the later paper arXiv:1502.03791.

\section*{Original Problem}

In \emph{The Diameter of the Isomorphism Class of a Banach Space},
Johnson and Odell define an elastic Banach space and ask in Problem~7:

\begin{quote}
Let \(X\) be elastic (and separable, say). Does \(C[0,1]\) embed into
\(X\)?
\end{quote}

The same paper proves the related main theorem that every separable
infinite-dimensional Banach space has infinite Banach--Mazur isomorphism
class diameter, and proves as an intermediate result that a separable
infinite-dimensional elastic space contains \(c_0\). Problem~7 asks for the
stronger \(C[0,1]\) conclusion.

\section*{Supporting Answer}

Alspach and Sari, \emph{Separable Elastic Banach spaces are universal},
arXiv:1502.03791, explicitly state that Johnson and Odell conjectured that
the separable elastic spaces are exactly those containing an isomorphic copy
of \(C[0,1]\), and write that they prove this conjecture.

Their Theorem~1 states:
\begin{quote}
Let \(X\) be a separable infinite dimensional elastic Banach space. Then
\(C[0,1]\) is isomorphic to a subspace of \(X\).
\end{quote}

This is an affirmative answer to the separable version of Johnson--Odell
Problem~7.

\section*{Scope}

The packet records only the separable elastic-space problem asked in
Problem~7. It does not claim to settle any nonseparable extension of that
problem or any nonseparable version of the Banach--Mazur diameter question.

\section*{References}

\begin{itemize}
\item W. B. Johnson and E. Odell, \emph{The Diameter of the Isomorphism
Class of a Banach Space}, arXiv:math/0310023.
\item Dale E. Alspach and Bunyamin Sari, \emph{Separable Elastic Banach
spaces are universal}, arXiv:1502.03791.
\end{itemize}

\end{document}
