\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\ellTwo}{\ell_2}

\begin{document}

\section*{Human Review: Uniformly convex ellipsoid with non-exposed extreme point}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 18 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears correct and clean.  It gives a counterexample to the
question in Remark 4.15 of Garcia-Lirola--Grelier--Rueda Zoca, and in fact
proves a slightly stronger statement: the chosen point is not merely not
strongly exposed by an ambient continuous functional; it is not exposed at
all by such a functional.

The construction makes explicit the phenomenon already suggested in the
source remark: the Minkowski functional of \(K\) may define a stronger norm
than the ambient norm.  The point is intrinsically strongly exposed for the
Minkowski norm, but the corresponding norming functional is not continuous
for the ambient Banach-space norm.

\section*{The Example}

The ambient space is \(X=\ell_2\), and
\[
  K=
  \left\{
    x=(x_n)\in\ell_2:
    \sum_{n=1}^\infty n^2x_n^2\leq 1
  \right\}.
\]
The Minkowski functional is the weighted Hilbert norm
\[
  |x|_K=
  \left(\sum_{n=1}^\infty n^2x_n^2\right)^{1/2}.
\]
Thus \(K\) is the unit ball of a Hilbert norm on \(\operatorname{span}K\).
Since
\[
  \|x\|_2\leq |x|_K,
\]
uniform convexity of the Hilbert ball implies uniform convexity of \(K\) as a
subset of the ambient space \(\ell_2\).

The chosen point is
\[
  x_0=\left(\frac{c}{n^2}\right)_{n\geq1},
  \qquad
  c=\left(\sum_{n=1}^\infty \frac1{n^2}\right)^{-1/2}.
\]
Then \(|x_0|_K=1\), so \(x_0\) is an extreme point of \(K\), because \(K\) is
the unit ball of a strictly convex Hilbert norm.

\section*{Why It Is Not Exposed}

Let an ambient continuous functional be represented by \(b=(b_n)\in\ell_2\):
\[
  \varphi_b(x)=\sum_{n=1}^\infty b_nx_n.
\]
With respect to the weighted Hilbert inner product
\[
  \langle x,z\rangle_K=\sum_{n=1}^\infty n^2x_nz_n,
\]
this functional is represented by
\[
  z=\left(\frac{b_n}{n^2}\right)_{n\geq1}.
\]
If \(\varphi_b\) exposed \(x_0\) over \(K\), then equality in the Hilbert-space
Cauchy-Schwarz inequality would force
\[
  z=\lambda x_0
\]
for some \(\lambda>0\).  Since \(x_{0,n}=c/n^2\), this implies
\[
  \frac{b_n}{n^2}=\lambda\frac{c}{n^2},
  \qquad\text{hence}\qquad
  b_n=\lambda c
\]
for every \(n\).  But a nonzero constant sequence is not in \(\ell_2\).  Thus
no ambient continuous functional can expose \(x_0\).

Therefore \(x_0\) is not exposed, and hence is not strongly exposed.

\section*{Review Outcome}

Approve this packet as an apparently correct counterexample.  The proof is
short, transparent, and directly illustrates the distinction between exposure
for the intrinsic Minkowski functional and exposure by a functional continuous
for the ambient norm.

\end{document}
