\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\newtheorem{proposition}{Proposition}
\newcommand{\R}{\mathbb R}

\title{A Literature-Implied Partial Answer to\\
Dai's Mixed Sequence-Space Stability Problem}
\author{Run \texttt{fa\_banach\_001}, lane 9}
\date{19 July 2026}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.

\section*{Source question}

Dai asks in Problem 4.7(9) of arXiv:1402.2123v4, PDF page 11, whether the
self-pair
\[
 E_{p,q}:=\left(\bigoplus_{n=1}^{\infty}\ell_p\right)_{\ell_q}
          =\ell_q(\ell_p),
 \qquad (E_{p,q},E_{p,q}),
\]
is stable for standard $\varepsilon$-isometries \cite{Dai}.
Here stability means that for every standard $\varepsilon$-isometry
$f:E_{p,q}\to E_{p,q}$ there is a bounded linear $T:E_{p,q}\to E_{p,q}$
and a constant $\gamma$ such that
$\|Tf(x)-x\|\leq\gamma\varepsilon$ for all $x$.

\section*{Literature-implied subcase}

\begin{proposition}
Work over the real scalars.  Suppose
\[
 1<p,q<\infty,\qquad p\ne q,\qquad p,q\ne2,
 \qquad\text{and}\qquad \neg(1<q<p<2).
\]
Then $(E_{p,q},E_{p,q})$ is $(1,2)$-stable.  More precisely, for every
standard $\varepsilon$-isometry $f:E_{p,q}\to E_{p,q}$ there is a linear
operator $T:E_{p,q}\to E_{p,q}$ satisfying
\[
 \|T\|=1,
 \qquad
 \|Tf(x)-x\|\leq2\varepsilon\quad (x\in E_{p,q}).
\]
\end{proposition}

\begin{proof}
Put $E=E_{p,q}$.  Since $1<p,q<\infty$, the real Banach space
$E=\ell_q(\ell_p)$ is uniformly convex and uniformly smooth.

We first identify a consequence of two isometry/projection results.  Realize
the two sequence spaces as $L_q(\mathbb N,\mu)$ and
$L_p(\mathbb N,\nu)$ for strictly positive finite atomic measures $\mu,\nu$;
diagonal coordinate rescaling gives an isometry with the usual counting
measure model.  Koldobsky's Theorem 3 applies to every real linear isometry
$U:E\to E$ provided, in his notation, the outer exponent $r=q$ and inner
exponent $s=p$ satisfy
\[
 r\ne s,\quad s\ne2,\quad s\notin(r,2)\text{ if }r<2.
\]
The last condition is precisely the exclusion of $1<q<p<2$.
The theorem writes $U$ in weighted-rearrangement/fibre form
\cite[Theorem 3, pp.~697--699]{Koldobsky}.

Let $(e_{ij})$ be the canonical double basis of $E$, with $i$ the outer
coordinate, and write $y_{ij}=Ue_{ij}$.  The atomic form of Koldobsky's
description has the following consequences.
For fixed $i$, all $y_{ij}$ have the same outer support $A_i$; the sets
$A_i$ are disjoint as $i$ varies.  At every $k\in A_i$,
\[
 y_{ij}(k)=h_i(k)V_{i,k}e_j,
\]
where $V_{i,k}:\ell_p\to\ell_p$ is a linear isometry.  Since $p\ne2$,
the classical Lamperti description of into isometries of $\ell_p$ implies
that $(V_{i,k}e_j)_j$ is a family of disjointly supported unit vectors.
Consequently, for distinct double indices, either the outer supports are
disjoint, or they are equal and the corresponding inner vectors are
disjoint with equal $\ell_p$-norm at each outer coordinate.

Apply Theorem 5.1 of Lemmens--Randrianantoanina--van Gaans with outer
exponent $q$ and inner exponent $p$.  Its hypotheses also require
$p,q\ne2$, and the basis just described satisfies its exact criterion.
It follows that $U(E)$ is the range of a projection $P:E\to U(E)$ with
$\|P\|=1$ \cite[Theorem 5.1, p.~19]{LRvG}.

Now let $f:E\to E$ be a standard $\varepsilon$-isometry.  Uniform convexity
gives the real linear isometry
\[
 \varphi(x)=\lim_{t\to\infty}\frac{f(tx)}{t}.
\]
By the preceding paragraph there is a norm-one projection $P:E\to\varphi(E)$.
Remarks 2.5(2) of \v Semrl--V\"ais\"al\"a state that their proof applies to
any uniformly convex and uniformly smooth codomain for which this asymptotic
copy is the range of a norm-one projection.  With
$T=\varphi^{-1}P$, that proof gives
\[
 \|T\|=1,
 \qquad
 \|Tf(x)-x\|\leq2\varepsilon
 \quad(x\in E)
\]
\cite[Remarks 2.5(2), p.~9]{SV}.  This is the asserted $(1,2)$-stability.
\end{proof}

\section*{Provenance, search, and limitations}

The supporting results date from 1991, 2002, and 2005/2007, before the
source question was posted.  Their relation to Problem 4.7(9) is an
identification made in this run; none of the supporting papers says that it
answers Dai's later question.  Exact-question and close-variant searches did
not locate a later paper explicitly advertising this subcase as a solution.
The result is therefore recorded as a literature-implied partial answer, not
as a new theorem.

The proof does not cover $p=1$, $q=1$, either exponent equal to $2$, the
remaining real region $1<q<p<2$, any infinite endpoint, the $L_p$-fibre
problem in item (10), or the other items of Problem 4.7.

\begin{thebibliography}{9}

\bibitem{Dai}
D.~Dai,
\emph{On Qian's problem for $\mathcal L_\infty$-spaces},
arXiv:1402.2123v4, 2018.

\bibitem{Koldobsky}
A.~L. Koldobsky,
\emph{Isometries of $L_p(X;L_q)$ and equimeasurability},
Indiana Univ. Math. J. \textbf{40} (1991), no.~2, 677--705,
doi:10.1512/iumj.1991.40.40031.

\bibitem{LRvG}
B.~Lemmens, B.~Randrianantoanina, and O.~van Gaans,
\emph{Second derivatives of norms and contractive complementation in
vector-valued spaces}, arXiv:math/0511044, 2005.

\bibitem{SV}
P.~\v Semrl and J.~V\"ais\"al\"a,
\emph{Nonsurjective nearisometries of Banach spaces},
arXiv:math/0112294v2, 2002.

\end{thebibliography}

\end{document}
