\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{enumitem}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{conditional}{Conditional Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\newcommand{\WC}{\mathbf{WC}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\ord}{\mathrm{Ord}}
\newcommand{\co}{\operatorname{co}}

\title{A Conditional Reduction for the Raw Weak-Compactness Index Cutoffs}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_18}}
\date{2026-06-15}

\begin{document}
\maketitle

\section*{Status}

This is a conditional packet, not a full solution of Question 9.3 of
Beanland--Causey--Freeman--Wallis \cite{BCFW}.  The conditional dependency is
isolated in Lemma \ref{bridge}.  If that lemma is proved, then the raw
weak-compactness cutoff classes at the principal ordinals
$\omega^{\omega^\eta}$, $\eta\geq 1$, are norm-closed operator ideals.

\section{Source Question}

In \cite[Question 9.3]{BCFW}, after defining the raw weak-compactness index
$\WC(A,X,Y)$ by finite sequences in $B_X$ whose images dominate the summing
basis of $c_0$, the authors ask:

\begin{quote}
For which ordinals $\xi$ is the class of operators $A:X\to Y$ such that
$\WC(A,X,Y)\leq \xi$ an ideal?
\end{quote}

The source paper proves that the cutoff $\WC\leq\omega$ is the ideal of super
weakly compact operators and that $\WC<\omega_1$ is an ideal.  A previous
packet in this run proves that finite cutoffs $n\geq 2$ are not closed under
sums.

\section{Definitions}

Let $(s_i)$ denote the summing basis of $c_0$, with
\[
  \left\|\sum_{i=1}^n a_i s_i\right\|
  = \max_{1\leq m\leq n}\left|\sum_{i=1}^m a_i\right|.
\]
For $K\geq 1$, $\WC(A,X,Y,K)$ is the tree of all finite sequences
$(x_i)_{i=1}^n\subset B_X$ such that $(Ax_i)_{i=1}^n$ $K$-dominates
$(s_i)_{i=1}^n$.  Then
\[
  \WC(A,X,Y)=\sup_{K\geq 1} o(\WC(A,X,Y,K)).
\]

Causey's James index \cite{CauseyJ} is built from convexly separated
sequences.  For a body $K\subset X^*$ and $\varepsilon>0$, a finite sequence
$(x_i)_{i=1}^n$ is $(K,\varepsilon)$-convexly separated if, for every
$1\leq m<n$,
\[
 d_K\bigl(\co\{x_i:i\leq m\},\co\{x_i:m<i\leq n\}\bigr)\geq\varepsilon.
\]
For an operator $A:X\to Y$, this is applied to $K=A^*B_{Y^*}$; equivalently,
the image sequence $(Ax_i)$ is convexly separated in norm.  Let
$j(A,\varepsilon)$ be the order of this tree and
$\J(A)=\sup_{\varepsilon>0} j(A,\varepsilon)$.

\section{Elementary Comparison}

\begin{lemma}\label{wc-le-j}
For every operator $A:X\to Y$, $\WC(A,X,Y)\leq \J(A)$.
\end{lemma}

\begin{proof}
Fix $K\geq 1$ and $(x_i)_{i=1}^n\in \WC(A,X,Y,K)$.  Given
$1\leq m<n$, take convex combinations
$u=\sum_{i\leq m}\lambda_i Ax_i$ and
$v=\sum_{i>m}\mu_i Ax_i$.  The coefficient vector
$(\lambda_1,\ldots,\lambda_m,-\mu_{m+1},\ldots,-\mu_n)$ has summing-basis
norm at least $1$, because its $m$th partial sum is $1$.  Hence
\[
  \|u-v\|\geq K^{-1}.
\]
Thus every $\WC(A,K)$ node is a $J(A,K^{-1})$ node, so
$o(\WC(A,K))\leq j(A,K^{-1})$.  Taking the supremum over $K$ gives the claim.
\end{proof}

\section{Conditional Dependencies}

\begin{conditional}[James-to-wide-(s) tree bridge]\label{bridge}
For every operator $A:X\to Y$, every $\varepsilon>0$, and every ordinal
$\alpha$, if
\[
  j(A,\varepsilon)>\omega\alpha,
\]
then there is some $K\geq 1$ such that
\[
  o(\WC(A,X,Y,K))>\alpha.
\]
\end{conditional}

This is the only unproved dependency in the packet.  It is plausible for the
following reasons.  First, Causey's $J(A,\varepsilon)$ trees are closed under
successive positive convex blocks: a positive convex block of a convexly
separated branch remains convexly separated.  Second, BCFW use an
$\omega\alpha\mapsto\alpha$ tree-blocking argument to make branches basic in
related Bourgain trees.  Third, Rosenthal's finite theory of
$\lambda$-wide-(s) sequences \cite{RosenthalWideS} identifies the finite
quantitative version of domination of the summing basis and proves finite
triangular-array extraction results.  A proof of Lemma \ref{bridge} should
combine these three ingredients.

The dependency is not automatic.  Convex separation alone does not imply
summing-basis domination at the same finite level; finite-dimensional monotone
scalar configurations can be convexly separated while failing even length-two
raw summing domination.  The expected loss of one factor of $\omega$ is meant
to remove precisely this finite-dimensional affine obstruction.

\section{Idea of the Proof}

The key observation is that the raw WC index is bounded above by Causey's
James index, while Lemma \ref{bridge} gives a partial converse after one
$\omega$ loss.  At ordinals $\gamma=\omega^{\omega^\eta}$ with $\eta\geq 1$,
this loss disappears, since $\omega\gamma=\gamma$.  Therefore the two ranks
have the same cutoff at these principal ordinals.  Causey's theorem then
transfers ideality for the James cutoff to the raw WC cutoff, and the
elementary comparison transfers the sum back.

\section{Conditional Theorem}

\begin{theorem}\label{main}
Assume Lemma \ref{bridge}.  Let $\eta\geq 1$ and put
$\gamma=\omega^{\omega^\eta}$.  Then the class
\[
  \mathcal{W}_\gamma
  =\{A:X\to Y:\WC(A,X,Y)\leq \gamma\}
\]
is a norm-closed operator ideal.
\end{theorem}

\begin{proof}
We first show that $\WC(A)\leq\gamma$ implies $\J(A)\leq\gamma$.  If not, then
for some $\varepsilon>0$,
\[
  j(A,\varepsilon)>\gamma.
\]
Since $\eta\geq 1$, $\gamma=\omega^{\omega^\eta}$ is fixed by left
multiplication by $\omega$, i.e. $\omega\gamma=\gamma$.  Thus
$j(A,\varepsilon)>\omega\gamma$, and Lemma \ref{bridge} gives
$o(\WC(A,K))>\gamma$ for some $K$, contradicting $\WC(A)\leq\gamma$.
Hence
\[
  \mathcal{W}_\gamma\subseteq \{A:\J(A)\leq\gamma\}.
\]

Causey proves that $\{A:\J(A)\leq\omega^{\omega^\eta}\}$ is a closed operator
ideal for every ordinal $\eta$ \cite{CauseyJ}.  Let $A,B:X\to Y$ lie in
$\mathcal{W}_\gamma$.  By the previous paragraph,
$\J(A),\J(B)\leq\gamma$, so Causey's theorem gives $\J(A+B)\leq\gamma$.
Lemma \ref{wc-le-j} then gives
\[
  \WC(A+B)\leq \J(A+B)\leq\gamma.
\]
Thus $\mathcal{W}_\gamma$ is closed under finite sums.

Closure under composition follows directly from the definition of $\WC$: if
$C:W\to X$ and $D:Y\to Z$ are bounded, any raw WC tree for $DAC$ rescales to a
raw WC tree for $A$, with only the domination constant changed.  Therefore
$\WC(DAC)\leq\WC(A)$.

Finally, if $A_n\to A$ in norm and $A_n\in\mathcal{W}_\gamma$, then
$\J(A_n)\leq\gamma$ by the first paragraph.  Causey's class
$\{T:\J(T)\leq\gamma\}$ is norm closed, so $\J(A)\leq\gamma$.  Lemma
\ref{wc-le-j} gives $\WC(A)\leq\gamma$.  Hence $\mathcal{W}_\gamma$ is norm
closed.
\end{proof}

\section{Verification Notes}

The cheap run indexes were searched for arXiv:1507.06285, ``weak compactness
index'', ``summing basis'', ``Causey'', ``James index'', and ``convexly
separated''.  Existing run memory contains the finite-cutoff partial result
and a prior full-solution push attempt, but no infinite-cutoff solution.

The bounded literature search for this packet found:
\begin{itemize}[leftmargin=2em]
  \item Causey's arXiv:1508.02065 theorem that the James-index cutoffs
  $\J\leq\omega^{\omega^\eta}$ are closed operator ideals.
  \item Rosenthal's arXiv:math/9610209 finite and infinite theory of
  $\lambda$-wide-(s) sequences, triangular arrays, and super weak compactness.
  \item No source in the local index or web search explicitly answering BCFW
  Question 9.3 for the raw $\WC$ cutoffs beyond the source paper's
  $\WC\leq\omega$ result.
\end{itemize}

\section{Limitations}

This packet does not prove Lemma \ref{bridge}.  Without that bridge, Theorem
\ref{main} remains conditional.  The most likely obstruction is that
convex-separation trees may contain high-rank affine configurations that do
not admit a uniform raw summing-basis subtree after one $\omega$ loss.  A
counterexample should probably come from a well-founded James-tree-type
reflexive space with large Causey $\J$ rank but unexpectedly small raw $\WC$
rank.

\begin{thebibliography}{9}

\bibitem{BCFW}
K. Beanland, R. Causey, D. Freeman, and R. Wallis,
\emph{Classes of operators determined by ordinal indices},
arXiv:1507.06285.

\bibitem{CauseyJ}
R. M. Causey,
\emph{An ordinal index characterizing weak compactness of operators},
arXiv:1508.02065.

\bibitem{RosenthalWideS}
H. P. Rosenthal,
\emph{On wide-$(s)$ sequences and their applications to certain classes of
operators},
arXiv:math/9610209.

\end{thebibliography}

\end{document}
