\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.6em}

\title{Literature Status: \(L_1\)-Distortion of Wasserstein Spaces\\
over Iterated Laakso Graphs}
\author{Run \texttt{fa\_banach\_001} --- lane 5}
\date{23 July 2026}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.9\textwidth}{
\textbf{Status: literature already answered.}
Remark~2 of arXiv:2208.13879 records that no nontrivial \(L_1\)-distortion
lower bound was known for the 1-Wasserstein spaces over iterated Laakso
graphs.  Corollary~4.21 of the separate later paper arXiv:2602.14852 proves
the sharp linear-in-level lower bound
\[
 c_1\!\left(\mathrm{TC}(\mathrm{La}^{\oslash n})\right)
 \geq \frac{2-\sqrt 2}{8}\,n .
\]
}}
\end{center}

\section{Original open problem}

F. Baudier, C. Gartland, and Th. Schlumprecht,
\emph{\(L_1\)-distortion of Wasserstein metrics: a tale of two dimensions},
arXiv:2208.13879~\cite{source}, prove a general lower-bound theorem requiring
isoperimetric and Lipschitz-spectral dimension at least \(2\).
Immediately after that theorem, Remark~2 on arXiv PDF page~3 states:

\begin{quote}
For graphs whose dimensions are strictly between \(1\) and \(2\), such as
the Laakso graphs \(\mathrm{La}_1^{\oslash n}\), the authors do not know how
to prove nontrivial lower bounds for the \(L_1\)-distortion of the associated
1-Wasserstein spaces.
\end{quote}

The paper later computes the relevant Laakso dimension as \(3/2\), so this
case lies genuinely outside the method used there.

\section{Separate later answer}

C. Gartland and M. Ostrovskii,
\emph{Lower Estimates for \(L_1\)-Distortion of Transportation Cost
Spaces}, arXiv:2602.14852~\cite{answerpaper}, explicitly identify the
Laakso case as previously unresolved on arXiv PDF page~5, in the paragraph
following Theorem~1.2.  Their Corollary~4.21 on arXiv PDF page~26 proves,
for every \(n\geq0\),
\[
 c_1\!\left(\mathrm{TC}(\mathrm{La}^{\oslash n})\right)
 \geq \frac{2-\sqrt 2}{8}\,n .
\]
Their notation \(\mathrm{TC}(X)\) denotes the transportation-cost, or
Lipschitz-free, space over \(X\).  Section~5 of the same paper records the
standard equality between the \(L_1\)-distortion of the earth-mover
(1-Wasserstein) space and the linear \(L_1\)-distortion of
\(\mathrm{TC}(X)\).  Thus Corollary~4.21 directly gives the lower bound
requested in the source remark.

\section{Scope and status}

The later result is stronger than mere unboundedness: since
\(\log |V(\mathrm{La}^{\oslash n})|=\Theta(n)\), it attains the universal
order \( \Theta(\log |V|)\).  Hence no part of the source's request for a
nontrivial Laakso lower bound remains open at the level stated there.

This identification was found by searching the run's local full-text arXiv
corpus for the exact Laakso/Wasserstein/\(L_1\)-distortion combination and
then checking Theorem~1.2, Corollary~4.21, and the reduction in Section~5
of arXiv:2602.14852.  The supporting authors explicitly say the Laakso
unboundedness was not known before their work.  No new mathematical result
is claimed in this packet.

\begin{thebibliography}{9}
\bibitem{source}
F. Baudier, C. Gartland, and Th. Schlumprecht,
\emph{\(L_1\)-distortion of Wasserstein metrics: a tale of two dimensions},
J. Funct. Anal. \textbf{284} (2023), 109846;
arXiv:2208.13879.

\bibitem{answerpaper}
C. Gartland and M. Ostrovskii,
\emph{Lower Estimates for \(L_1\)-Distortion of Transportation Cost Spaces},
arXiv:2602.14852 (2026).
\end{thebibliography}

\end{document}
