\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\Cc}{C_c^\infty}

\title{Quasi-Interior Points in the Ordered Sobolev Spaces \(W^{k,p}(\mathbb R^d)\)}
\author{Automatic math-discovery packet}
\date{June 20, 2026}

\begin{document}
\maketitle

\section*{Source Question}

The source paper is Jochen Gl\"uck and Martin R. Weber,
\emph{Almost Interior Points in Ordered Banach Spaces and the Long--Term Behaviour of Strongly Positive Operator Semigroups},
arXiv:1901.03306.  In Example 2.20, after defining the ordered Sobolev space
\[
    W^{k,p}(\R^d)_+
    =
    \{f\in W^{k,p}(\R^d): f(\omega)\geq0\ \text{for a.e. }\omega\in\R^d\},
\]
the authors write:

\begin{quote}
We do not know whether the space \(W^{k,p}(\mathbb R^d)\) has almost interior or
even quasi-interior points.
\end{quote}

Here \(k\in\mathbb N_0\) and \(1\leq p<\infty\).  In the terminology recalled in
the source paper, a positive vector \(u\) is a quasi-interior point if the
principal ideal
\[
    X_u=\{y\in X:\ \exists \lambda\geq0 \text{ such that } -\lambda u\leq y\leq \lambda u\}
\]
is dense in \(X\).  Every quasi-interior point is almost interior.

\section*{Idea of the Proof}

The order is pointwise almost everywhere, so a strictly positive smooth function
can dominate compactly supported smooth functions after multiplying by a scalar.
The Gaussian \(u(x)=e^{-|x|^2}\) is the natural choice: it belongs to every
finite-order Sobolev space \(W^{k,p}(\mathbb R^d)\), it is positive everywhere,
and on each compact set it has a positive lower bound.  Since
\(C_c^\infty(\mathbb R^d)\) is dense in \(W^{k,p}(\mathbb R^d)\), the principal
ideal generated by \(u\) is dense.

\section*{The Result}

\begin{theorem}
Let \(d\geq1\), \(k\in\mathbb N_0\), and \(1\leq p<\infty\).  Endow
\(W^{k,p}(\mathbb R^d)\) with the cone of almost everywhere nonnegative
functions.  Then
\[
    u(x)=e^{-|x|^2}
\]
is a quasi-interior point of \(W^{k,p}(\mathbb R^d)_+\).  Consequently
\(W^{k,p}(\mathbb R^d)_+\) has almost interior points.
\end{theorem}

\begin{proof}
First, \(u\in W^{k,p}(\mathbb R^d)\).  Indeed, every weak derivative of \(u\) of
order at most \(k\) is a polynomial times \(e^{-|x|^2}\), hence belongs to
\(L^p(\mathbb R^d)\) for every finite \(p\).

We show that \(C_c^\infty(\mathbb R^d)\) is contained in the principal ideal
generated by \(u\).  Let \(g\in C_c^\infty(\mathbb R^d)\), and let
\(K=\supp g\).  The set \(K\) is compact.  Since \(u\) is continuous and
strictly positive, there is \(m_K>0\) such that \(u(x)\geq m_K\) for all
\(x\in K\).  If \(M_K=\|g\|_\infty\), then
\[
    |g(x)|\leq \frac{M_K}{m_K}u(x)\qquad (x\in K),
\]
and outside \(K\) the left hand side is zero.  Thus
\[
    -\lambda u\leq g\leq \lambda u
    \quad\text{a.e. on }\mathbb R^d,
    \qquad
    \lambda=\frac{M_K}{m_K}.
\]
Hence \(g\in X_u\).

The standard Sobolev density theorem gives
\[
    \overline{C_c^\infty(\mathbb R^d)}^{\,W^{k,p}}=W^{k,p}(\mathbb R^d)
    \qquad (1\leq p<\infty).
\]
Since \(C_c^\infty(\mathbb R^d)\subseteq X_u\), the principal ideal \(X_u\) is
dense in \(W^{k,p}(\mathbb R^d)\).  By definition, \(u\) is a quasi-interior
point.  The implication from quasi-interior to almost interior is recorded in
the source paper immediately after Definition 2.4.
\end{proof}

\section*{Limitations}

This resolves the Sobolev-space question in Example 2.20 of the source paper.
It does not address the broader Open Problem 2.5, which asks whether every
almost interior point must be quasi-interior in arbitrary ordered Banach spaces
with generating cone, or under the additional assumption of normality.

\section*{Novelty and Verification Notes}

The run's cheap indexes contain no prior packet for arXiv:1901.03306 or this
Sobolev question.  Local corpus searches for Sobolev quasi-interior phrases
found the source question but no existing answer.  Web searches for the exact
Sobolev/quasi-interior phrases likewise found no later resolution.

The proof uses only the standard density of \(C_c^\infty(\mathbb R^d)\) in
\(W^{k,p}(\mathbb R^d)\) for \(1\leq p<\infty\).  No numerical computation is
involved.  PDF rendering tools capable of cropping the exact source page were
not available in this environment; the source location is therefore given by
the exact Example 2.20 passage and parsed-source lines 823--837.

\begin{thebibliography}{9}

\bibitem{AdamsFournier}
R. A. Adams and J. J. F. Fournier,
\emph{Sobolev Spaces}, 2nd ed.,
Pure and Applied Mathematics 140, Academic Press, 2003.

\bibitem{GlueckWeber}
J. Gl\"uck and M. R. Weber,
\emph{Almost Interior Points in Ordered Banach Spaces and the Long--Term Behaviour of Strongly Positive Operator Semigroups},
arXiv:1901.03306.

\end{thebibliography}

\end{document}
