\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Answer: Davis Endpoint for Noncommutative Symmetric Spaces}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-07-18}

\newcommand{\M}{\mathcal M}
\newcommand{\Hc}{\mathcal H}
\newcommand{\hc}{\mathsf h}
\newcommand{\Int}{\operatorname{Int}}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}. The extracted endpoint Davis problem
from arXiv:1501.05944 is answered in later literature.

\paragraph{Source question.}
Randrianantoanina--Wu, \emph{Martingale inequalities in noncommutative
symmetric spaces}, arXiv:1501.05944, asks in the final section whether the
assumption \(p_E>1\) can be removed from the first equality in their Davis
corollary. In their notation:
\[
  p_E=1,\quad q_E\le 2
  \qquad\Longrightarrow\qquad
  \Hc_E(\M)=\hc_E(\M)\;?
\]

\paragraph{Later answer.}
Randrianantoanina, \emph{P. Jones' interpolation theorem for noncommutative
martingale Hardy spaces}, arXiv:2212.08714, proves in Proposition
\(\texttt{Davis-symmetric}\) that if \(E\in\Int(L_1,L_2)\), then the adapted
column sequence space decomposes as
\[
  E^{\rm ad}(\M;\ell_2^c)
  =
  E\!\left(\bigoplus_{n\ge1}\M_n\right)
  + E^{\rm cond,ad}(\M;\ell_2^c).
\]
Its Corollary \(\texttt{Davis}\) gives the martingale formulation
\[
  \Hc_E^c(\M)=\hc_E^d(\M)+\hc_E^c(\M),
\]
and hence, by the row version,
\[
  \Hc_E(\M)=\hc_E(\M).
\]
The text immediately before the corollary says this answers
\cite[Problem~4.2]{RW}, where \cite{RW} is exactly the arXiv:1501.05944
paper.

\paragraph{Sharp threshold.}
The same corollary records sharpness: if the column Davis identity holds, then
already \(\hc_E^c(\M)\subseteq \Hc_E^c(\M)\), and a two-step commutative
martingale argument plus Kalton--Montgomery-Smith's criterion forces
\[
  E\in\Int(L_1,L_2).
\]
Thus the correct endpoint criterion is \(E\in\Int(L_1,L_2)\), not merely
\(p_E=1\) and \(q_E\le2\).

\paragraph{Consequence for the 2015 Boyd-index formulation.}
If \(q_E<2\), standard Boyd interpolation implies \(E\in\Int(L_1,L_2)\), so
the answer is affirmative. At the boundary \(q_E=2\), the literal formulation
is false in general. For example, \(E=L_1+L_{2,\infty}\) is a symmetric Fatou
Banach function space with Boyd indices \(p_E=1\) and \(q_E=2\), but it is not
an interpolation space for \((L_1,L_2)\): weak-\(L_2\) contains functions not in
\(L_1+L_2\). The sharpness result therefore rules out the Davis equality for
this \(E\) in general.

\paragraph{Why this is not new.}
The supporting paper explicitly identifies the original Randrianantoanina--Wu
problem and gives both the positive endpoint theorem and the sharpness
criterion.

\begin{thebibliography}{9}
\bibitem{RW}
N. Randrianantoanina and L. Wu,
\emph{Martingale inequalities in noncommutative symmetric spaces},
arXiv:1501.05944.

\bibitem{JonesNC}
N. Randrianantoanina,
\emph{P. Jones' interpolation theorem for noncommutative martingale Hardy
spaces},
arXiv:2212.08714.

\bibitem{KaltonSMS}
N. Kalton and S. Montgomery-Smith,
\emph{Interpolation of Banach spaces},
Handbook of the Geometry of Banach Spaces, Vol. 2, North-Holland, 2003.
\end{thebibliography}

\end{document}
