\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature-Implied Partial Answer to an Additive Lebesgue-Bounds Question}
\author{fa\_banach\_001, agent\_lane\_18}
\date{2026-06-26}

\begin{document}
\maketitle

\paragraph{Status.}
\textbf{literature\_implied\_answer (partial Q1 / broad additive-parameter formulation).}
This is a scoped literature-status packet, not an original proof packet.

\paragraph{Source question.}
In Section 6, ``Further questions,'' of Pablo M. Berna, Oscar Blasco, and Gustavo Garrigos,
\emph{Lebesgue inequalities for the greedy algorithm in general bases}, arXiv:1606.06721,
Q1 asks for bounds for the Lebesgue constants $\mathbf L_N$ and $\widetilde{\mathbf L}_N$
which depend additively on the unconditionality constants and on the democracy/A-property
constants.  In particular, the source asks when one can have
\[
  \mathbf L_N \lesssim k_N+\nu_N
  \quad\text{or}\quad
  \mathbf L_N \lesssim k_N+\widetilde\mu_N .
\]

\paragraph{Supporting theorem.}
Fernando Albiac, Jose L. Ansorena, and Pablo M. Berna,
\emph{New parameters and Lebesgue-type estimates in greedy approximation},
arXiv:2104.10912, introduces squeeze-symmetry parameters $\lambda_m$ and proves
in Theorem 1.2, with proof in Section 3, that for every basis in a quasi-Banach
space there are constants depending only on the modulus of concavity such that
\[
  \mathbf L_m \simeq \max\{k_m,\lambda_m\}.
\]
Equivalently, up to the same structural constants,
\[
  \mathbf L_m \lesssim k_m+\lambda_m
  \quad\text{and}\quad
  \max\{k_m,\lambda_m\}\lesssim \mathbf L_m .
\]
The abstract explicitly frames this as an answer to Temlyakov's 2011 question
asking for natural greedy-type parameters that combine linearly with the
unconditionality parameters to determine the growth of the Lebesgue constants.

\paragraph{Identification and limitation.}
This later theorem gives a clean literature answer to the broad additive-bounds
program behind Q1, after replacing $\nu_N$ or $\widetilde\mu_N$ by the squeeze-symmetry
parameter $\lambda_N$.  The implication is agent-identified rather than stated
as a direct solution to Q1 of arXiv:1606.06721.  It does \emph{not} settle the
literal source variants asking whether $k_N+\nu_N$ or $k_N+\widetilde\mu_N$
suffice, nor does it settle Q2 on arbitrary independent power growth of
$\nu_N$ and $k_N$, or Q3 on $\gamma_N\approx 1$ with maximal $g_N$ growth.

\paragraph{Search bounds.}
On 2026-06-26, exact local index search for arXiv:1606.06721 and the source
title found no prior fa\_banach\_001 packet.  Local source and web searches for
the exact phrases around ``$k_N$ and $\nu_N$ grow independently,'' ``arbitrary
$0<\alpha,\beta\le 1$,'' and ``$\gamma_N\approx1$ and $g_N$ as large as possible''
did not locate a direct resolution.  Later nearby papers on Chebyshev/weak
greedy algorithms and A-property constants were checked for overlap but did
not appear to settle those remaining source questions.

\paragraph{References.}
\begin{itemize}
  \item P. M. Berna, O. Blasco, and G. Garrigos,
  \emph{Lebesgue inequalities for the greedy algorithm in general bases},
  arXiv:1606.06721.
  \item F. Albiac, J. L. Ansorena, and P. M. Berna,
  \emph{New parameters and Lebesgue-type estimates in greedy approximation},
  arXiv:2104.10912.
\end{itemize}

\end{document}

