\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Lip}{\operatorname{Lip}_0}
\newcommand{\F}{\mathcal{F}}
\newcommand{\dens}{\operatorname{dens}}
\newcommand{\w}{\operatorname{w}}

\title{Literature Status Note for arXiv:2010.13098}
\author{run fa\_banach\_001, lane 15}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

This is a lightweight literature-status packet.  The dual-level half of
Question 1 in Candido--Kaufmann, ``On the geometry of Banach spaces of the form
$\Lip(C(K))$'', arXiv:2010.13098, is already answered by a later paper:
Candido--Guzman, ``On large $\ell_1$-sums of Lipschitz-free spaces and
applications'', arXiv:2202.09932.

\section*{Source Question}

The source paper asks in Section 3, p. 3, Question 1: for an infinite
Hausdorff compactum $K$ with $\w(K)=\kappa$, under which hypotheses can one
guarantee
\[
  \F(C(K)) \sim \F(c_0(\kappa)),
\]
or at least the dual-level classification
\[
  \Lip(C(K)) \sim \Lip(c_0(\kappa)).
\]
The same paper records this as only partially answered at the dual level by
its Corollary 4 and Theorem 5.

\section*{Later Answer}

Candido--Guzman, arXiv:2202.09932, state in the introduction, p. 2,
Theorem 3:
if $X$ is an $\mathcal L_p$ space of density $\kappa$, then
\[
  \Lip(X) \sim
  \begin{cases}
    \Lip(\ell_p(\kappa)), & p<\infty,\\
    \Lip(c_0(\kappa)), & p=\infty.
  \end{cases}
\]
They then state Corollary 4:
if $K$ is an infinite Hausdorff compact space of weight $\kappa$, then
\[
  \Lip(C(K)) \sim \Lip(c_0(\kappa)).
\]

\section*{Why This Matches}

Every Banach space $C(K)$ is an $\mathcal L_\infty$ space, and for infinite
Hausdorff compact $K$ one has $\dens(C(K))=\w(K)$. Applying the $p=\infty$
case of Candido--Guzman's Theorem 3 to $X=C(K)$ gives exactly the
dual-level alternative asked for in Question 1.

The supporting paper explicitly knows this relation: it cites the
Candido--Kaufmann paper as reference [5] and says its Corollary 4 extends the
main result of [5] in the dual setting.  Therefore this belongs in
\texttt{solutions/literature\_already\_answered/}, not in the original-results
folders.

\section*{Limitations}

This packet does not answer the free-space part of Question 1, namely whether
\[
  \F(C(K)) \sim \F(c_0(\kappa))
\]
for all infinite Hausdorff compacta $K$ of weight $\kappa$.  Only the
``at least $\Lip$'' half is cleared.

\section*{References}

\begin{itemize}
\item L. Candido and P. L. Kaufmann, ``On the geometry of Banach spaces of the
form $\Lip(C(K))$'', arXiv:2010.13098; Proc. Amer. Math. Soc. 149 (2021),
3335--3345.
\item L. Candido and H. H. T. Guzman, ``On large $\ell_1$-sums of
Lipschitz-free spaces and applications'', arXiv:2202.09932; Proc. Amer. Math.
Soc. 151 (2023), 1135--1145.
\end{itemize}

\end{document}
