\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,mathtools}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.65em}

\title{Literature Status: Complementability of the Kernels of
$AC-I$ and $BA-I$}
\author{Run \texttt{fa\_banach\_001} --- lane 3}
\date{19 July 2026}

\begin{document}
\maketitle

\textbf{Status.} \texttt{literature\_already\_answered}.

\section*{Source question}
Let $X,Y$ be Banach spaces and let
\[
 A\in\mathcal B(X,Y),\qquad B,C\in\mathcal B(Y,X),\qquad ABA=ACA.
\]
Zeng and Zhong, \emph{Common properties of bounded linear operators $AC$ and
$BA$: Spectral theory}, arXiv:1303.5818, state on PDF page~2 that they are
``unable to decide whether $AC-I$ and $BA-I$ share common complementability of
kernels.'' Equivalently, is
\[
 \ker(AC-I_Y)\text{ complemented in }Y
 \quad\Longleftrightarrow\quad
 \ker(BA-I_X)\text{ complemented in }X?
\]

\section*{Decisive later answer}
Zeng, Yan, and Zhang, \emph{New results on common properties of the products
$AC$ and $BA$, II}, \emph{Mathematische Nachrichten} \textbf{293} (2020),
1629--1635, DOI \href{https://doi.org/10.1002/mana.201900038}
{10.1002/mana.201900038}, explicitly state in item~(ii) of the published
abstract:
\begin{quote}
Under the same hypothesis $ABA=ACA$, $I-AC$ and $I-BA$ share common
complementability of kernels and ranges.
\end{quote}
The kernel assertion is exactly the source question; replacing $I-T$ by
$T-I$ does not change a kernel.

\section*{Direct identification check}
Set
\[
 M=\ker(BA-I_X),\qquad N=\ker(AC-I_Y),\qquad D=BAC.
\]
The maps $A:X\to Y$ and $D:Y\to X$ restrict to inverse isomorphisms between
$M$ and $N$. Indeed, for $x\in M$ and $y\in N$, the relation $ABA=ACA$ gives
\[
 AC(Ax)=A(BAx)=Ax,
 \qquad
 BA(Dy)=BABA(Cy)=BACA(Cy)=Dy,
\]
and
\[
 DAx=BACA x=BABA x=x,
 \qquad
 ADy=ABACy=ACACy=y.
\]
Because both inverse maps extend boundedly to the ambient spaces,
complementability transfers. If $P:X\to M$ is a bounded projection, then
$APD:Y\to N$ is a bounded projection. If $Q:Y\to N$ is a bounded projection,
then $DQA:X\to M$ is a bounded projection.

This calculation is included only to verify the exact match between the source
question and the literature claim. No novelty is asserted.

\section*{Search and source note}
The run indexes, local source corpus, exact source wording, titles, DOI,
$ABA=ACA$, and close kernel-complementability phrases were searched. The 2020
paper is a separate later publication and explicitly answers the question.
The original arXiv PDF is retained as \texttt{source\_paper.pdf}. The decisive
publisher PDF endpoint denied automated access, so the supporting PDF is not
copied; the DOI record and published abstract supply the identification.

\end{document}
