\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}

\begin{document}

\begin{center}
{\Large Literature status: slicing and thin-shell conjectures}

\medskip
{\small Run \texttt{fa\_banach\_001}; source arXiv:1310.1204}
\end{center}

\section*{Source conjectures}

Guedon's survey \emph{Concentration phenomena in high dimensional geometry}
records several major conjectures in high-dimensional convex geometry.  This
status note concerns two named conjecture families from the source:

\begin{itemize}
\item Conjecture \texttt{slicing}, the hyperplane conjecture/Bourgain slicing
problem: for every volume-one convex body \(K\subset \mathbb{R}^n\) with
barycenter at the origin, some hyperplane section \(K\cap \theta^\perp\) has
\((n-1)\)-dimensional volume bounded below by a universal positive constant.
\item Conjectures \texttt{ThinShell} and \texttt{ThinShellbis}: for every
isotropic log-concave random vector \(X\in\mathbb{R}^n\), respectively
\[
  \operatorname{Var}|X|_2^2 \le C\,\mathbb{E}|X|_2^2
  \qquad\text{and}\qquad
  \operatorname{Var}|X|_2\le C
\]
with a universal constant \(C\).
\end{itemize}

\section*{Supporting literature}

Klartag and Lehec's paper \emph{Affirmative Resolution of Bourgain's Slicing
Problem using Guan's Bound} explicitly states that it gives the final step in
the affirmative resolution of Bourgain's slicing problem.  Its main theorem
asserts that for any convex body \(K\subseteq \mathbb{R}^n\) of volume one,
there is a hyperplane \(H\) such that
\[
  \operatorname{Vol}_{n-1}(K\cap H)>c
\]
for a universal constant \(c>0\).  This is the source's Conjecture
\texttt{slicing}.

Klartag and Lehec's later paper \emph{Thin-shell bounds via parallel coupling}
states the following theorem.

\begin{theorem}[Klartag--Lehec, arXiv:2507.15495, Theorem 1.1]
Let \(X\) be an isotropic log-concave random vector in \(\mathbb{R}^n\).  Then
\[
  \operatorname{Var}(|X|^2)
  = \mathbb{E}\bigl(|X|^2-n\bigr)^2
  \le Cn,
\]
where \(C>0\) is a universal constant.
\end{theorem}

Since isotropy gives \(\mathbb{E}|X|^2=n\), this is exactly Guedon's
Conjecture \texttt{ThinShell}.  Moreover,
\[
  \operatorname{Var}|X|
  \le \mathbb{E}\bigl(|X|-\mathbb{E}|X|\bigr)^2
  \le \mathbb{E}\bigl(|X|-\sqrt n\bigr)^2
  \lesssim 1,
\]
where the last bound follows from the same thin-shell theorem as stated in the
paper's abstract.  Thus Conjecture \texttt{ThinShellbis} is also answered.

\section*{Status}

The source's slicing conjecture and variance thin-shell conjectures are
already answered by later literature:
\[
  \texttt{slicing}
  \quad\text{by arXiv:2412.15044,}
\]
and
\[
  \texttt{ThinShell},\ \texttt{ThinShellbis}
  \quad\text{by arXiv:2507.15495.}
\]
This packet is a literature-status identification and contains no new proof
from the run.

\section*{Limitations}

This packet does not claim that all conjectures in arXiv:1310.1204 are solved.
In particular, it does not record the Kannan--Lovasz--Simonovits conjecture as
solved, does not claim the stronger all-\(t\) exponential-tail concentration
inequality from Conjecture \texttt{Concentration}, and does not address
Latala's weak/strong moments conjecture.

\section*{Verification}

Before packaging, the run lightweight indexes were searched for arXiv:1310.1204,
the source title, ``slicing'', ``thin shell'', ``KLS'', ``concentration
phenomena'', and weak/strong moment terminology.  No existing exact packet for
this source was found.  Web and arXiv checks on 2026-06-16 identified
arXiv:2412.15044 and arXiv:2507.15495 as the decisive supporting papers.

\begin{thebibliography}{9}

\bibitem{Guedon}
O. Guedon,
\emph{Concentration phenomena in high dimensional geometry},
arXiv:1310.1204.

\bibitem{KLslicing}
B. Klartag and J. Lehec,
\emph{Affirmative Resolution of Bourgain's Slicing Problem using Guan's
Bound},
arXiv:2412.15044.

\bibitem{KLthin}
B. Klartag and J. Lehec,
\emph{Thin-shell bounds via parallel coupling},
arXiv:2507.15495.

\end{thebibliography}

\end{document}
