\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\title{Literature-Implied Answer: WLD Density Above the Continuum}
\author{Run fa\_banach\_001}
\date{2026-06-15}

\begin{document}
\maketitle

\paragraph{Status.}
\emph{Literature-implied answer, partial subcase}, for arXiv:2301.07413.
This note records a known-literature obstruction, not a new proof from this run.

\paragraph{Source question.}
Koszmider--Ryduchowski, \emph{Equilateral and separated sets in some Hilbert
generated Banach spaces}, arXiv:2301.07413, Section 5, Question, asks:
\begin{quote}
Is there a nonseparable Hilbert generated (WCG, WLD) Banach space whose unit
sphere does not admit an uncountable $(1+)$-separated set?
\end{quote}
This is item (4) in the final question list; in the parsed source it appears
at lines 962--971.

\paragraph{Supporting theorem.}
Hajek--Kania--Russo, \emph{Separated sets and Auerbach systems in Banach
spaces}, arXiv:1803.11501, Theorem A(ii), states that if $X$ is a WLD Banach
space with $\operatorname{dens} X>\mathfrak c$, then the unit spheres of $X$
and $X^*$ contain uncountable symmetrically $(1+)$-separated subsets.
In the parsed source this theorem statement appears in the introduction around
lines 147--157, with the formal item at lines 152--153.

\paragraph{Identification.}
Symmetric $(1+)$-separation implies ordinary $(1+)$-separation. Hence the
Hajek--Kania--Russo theorem rules out WLD counterexamples to the
Koszmider--Ryduchowski question whenever $\operatorname{dens} X>\mathfrak c$.
Since Hilbert generated spaces have weak-star dual balls that are uniform
Eberlein compacta, and uniform Eberlein compacta are Corson compacta, Hilbert
generated spaces are WLD; WCG spaces are WLD as well. Thus the same density
obstruction applies to the Hilbert generated and WCG variants.

\paragraph{Scope limitations.}
This answers only the density-above-continuum subcase of Question 5(4). It
does not settle the cases of density at most $\mathfrak c$, especially the
$\omega_1$-density examples emphasized in arXiv:2301.07413. The supporting
authors do not present their theorem as an answer to arXiv:2301.07413, which
appeared later; the relation is an agent-identified literature implication.

\end{document}
