\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status for the \(\ell_1\) NQP-Basis Question}
\author{FA/Banach run packet}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Status}

\textbf{Result type:} literature already answered, basis subquestion.

\textbf{Source:} S. J. Dilworth, E. Odell, Th. Schlumprecht, and A. Zsak,
\emph{Coefficient Quantization in Banach Spaces}, arXiv:math/0606317.

\textbf{Supporting source:} P. G. Casazza, S. J. Dilworth, E. Odell,
Th. Schlumprecht, and A. Zsak, \emph{Coefficient Quantization for Frames in
Banach Spaces}, arXiv:0711.2484.

\section*{Source Question}

In Section 5 of arXiv:math/0606317, PDF page 21, the authors ask:
\[
\text{Does }\ell_1\text{ have an NQP basis (resp. minimal system)?}
\]
The arXiv PDF labels this as Problem 5.17.

\section*{Supporting Answer}

In Section 5 of arXiv:0711.2484, PDF page 30, Corollary 5.15 states that an
infinite-dimensional Banach space with nontrivial cotype cannot have a
semi-normalized basis with the NQP. The corollary then explicitly says, citing
the earlier DOSZ problem, that \(\ell_1\) does not have a semi-normalized basis
with the NQP.

This gives a negative answer to the intended semi-normalized basis version of
the \(\ell_1\) question, because \(\ell_1\) has nontrivial cotype.

\section*{Scope and Limitations}

This is a literature-status packet, not a new proof. It records only the
semi-normalized basis subquestion. It does not claim the ``minimal system''
part of the source question, and it does not settle the broader source Problem
5.16 asking whether every Banach space with an NQP basis contains \(c_0\).

There is a numbering mismatch: the source arXiv PDF labels the question as
Problem 5.17, while the supporting paper cites ``Problem 5.18 in [DOSZ]''.
The cited wording and context identify the same \(\ell_1\) NQP-basis question.

\section*{Search Evidence}

The run's cheap indexes were searched for arXiv:math/0606317, arXiv:0711.2484,
NQP, coefficient quantization, and the \(\ell_1\) NQP-basis wording; no prior
packet or attempt was found. A phrase search for the exact NQP terminology
found the frame follow-up, whose TeX/PDF source was then checked locally.

\section*{References}

\begin{thebibliography}{9}

\bibitem{DOSZ}
S. J. Dilworth, E. Odell, Th. Schlumprecht, and A. Zsak,
\emph{Coefficient Quantization in Banach Spaces},
arXiv:math/0606317.
\url{https://arxiv.org/abs/math/0606317}

\bibitem{CDOSZ}
P. G. Casazza, S. J. Dilworth, E. Odell, Th. Schlumprecht, and A. Zsak,
\emph{Coefficient Quantization for Frames in Banach Spaces},
arXiv:0711.2484.
\url{https://arxiv.org/abs/0711.2484}

\end{thebibliography}

\end{document}

