\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\title{Literature Status: Countable Discrete Extensions of Separable Compact Lines}
\author{Run \texttt{fa\_banach\_001}}
\date{23 July 2026}

\begin{document}
\maketitle

\textbf{Status:} \texttt{literature\_already\_answered (compact-line subproblem)}.

\section*{Source question}

Korpalski and Plebanek ask in Section~7, Problem~7.1, on page~16 of
\cite{KP} whether it is relatively consistent that, whenever \(K\) is a
separable compact space of weight \(\omega_1\),
\[
  \eta(K,L)<\infty \qquad\text{for every }L\in\operatorname{CDE}(K).
\]
Equivalently, every such countable discrete extension \(L\) should admit a
bounded extension operator \(C(K)\to C(L)\).  Immediately after the problem,
the authors explicitly ask whether it can be settled for separable compact
lines.

\section*{Explicit later answer}

Avil\'es and Korpalski prove the following as Theorem~1.4 on page~2 of
\cite{AK}:

\begin{quote}
Under \(\mathsf{MA}(\kappa)\), if \(K\) is a separable compact line of weight
\(\kappa\), then for each countable discrete extension \(L\) of \(K\) there is
an extension operator \(E:C(K)\to C(L)\) of norm at most three.
\end{quote}

Taking \(\kappa=\omega_1\) gives the requested relative consistency statement
for the entire compact-line class.  The paragraph following Theorem~1.4
explicitly states that the theorem solves the compact-line problem posed in
the source paper, so this is an author-identified answer rather than a new
agent inference.

\section*{Scope limitation}

Theorem~1.4 answers the compact-line subproblem completely and strengthens
mere existence by giving \(\lVert E\rVert\leq 3\).  The supporting paper
explicitly leaves open the broader question for arbitrary separable compact
spaces.

\section*{Search evidence}

A bounded search on 23 July 2026 used the exact source title together with
the phrases ``separable compact lines'', ``Martin's axiom'', ``countable
discrete extension'', and ``extension operator''.  It located
arXiv:2403.19327 and its open-access 2024 journal version.

\begin{thebibliography}{9}
\bibitem{KP}
M. Korpalski and G. Plebanek,
\emph{Countable discrete extensions of compact lines},
Fund. Math. \textbf{265} (2024), 75--93;
\href{https://arxiv.org/abs/2305.04565}{arXiv:2305.04565}.

\bibitem{AK}
A. Avil\'es and M. Korpalski,
\emph{Barely alternating real almost chains and extension operators for
compact lines},
RACSAM \textbf{118} (2024), Paper 148;
\href{https://arxiv.org/abs/2403.19327}{arXiv:2403.19327},
\href{https://doi.org/10.1007/s13398-024-01651-7}{doi:10.1007/s13398-024-01651-7}.
\end{thebibliography}

\end{document}
