\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\newcommand{\Gp}{\mathbb G_p}
\newcommand{\K}{\mathbb K}

\title{A Banach-Envelope Obstruction for Separably Injective \(p\)-Banach Spaces}
\author{Run \texttt{fa\_banach\_001}, lane 19}
\date{June 16, 2026}

\begin{document}
\maketitle

\section*{Source Question}

The source paper is Cabello S\'anchez, Garbuli\'nska-Wegrzyn, and Kubi\'s,
\emph{Quasi-Banach spaces of almost universal disposition},
arXiv:1309.7649.  In Section 7.4, after proving that \(c_0(E)\) is
separably injective whenever \(E\) is separably injective among \(p\)-Banach
spaces, the authors ask whether there is a nontrivial separable space
separably injective among \(p\)-Banach spaces when \(p<1\), and say that their
guess is negative.

\section*{Definitions}

Let \(0<p\leq 1\). A \(p\)-Banach space is a complete quasi-normed space whose
quasi-norm satisfies
\[
  \|x+y\|^p \leq \|x\|^p+\|y\|^p .
\]
Such a space \(E\) is separably injective among \(p\)-Banach spaces if, for
every separable \(p\)-Banach space \(X\), every subspace \(Y\subset X\), and
every bounded operator \(t:Y\to E\), there is a bounded extension
\(T:X\to E\).

\section*{Partial Result}

\begin{theorem}
Let \(0<p<1\), and let \(E\) be separably injective among \(p\)-Banach spaces.
If \(F\) is a \(q\)-Banach space for some \(p<q\leq 1\), then every bounded
linear operator \(S:E\to F\) is zero.
\end{theorem}

\section*{Proof Intuition}

Separably injectivity lets one extend maps out of one-dimensional subspaces of
separable \(p\)-Banach spaces.  Apply it to the constants inside
\(L_p[0,1]\).  If \(E\) had any nonzero operator into a more convex
\(q\)-Banach target, then the extension would produce a nonzero operator
\(L_p[0,1]\to F\).  Kalton's classical theorem forbids exactly such operators
when \(p<q\leq 1\).

\section*{Proof}

Assume, toward a contradiction, that \(S:E\to F\) is nonzero.  Choose
\(e\in E\) with \(S(e)\neq 0\).  Let \(L_p=L_p[0,1]\), with its usual
\(p\)-norm, and let \(Y\subset L_p\) be the one-dimensional subspace of
constant functions.  Since the measure of \([0,1]\) is one, the map
\[
  t:Y\to E,\qquad t(\lambda {\bf 1})=\lambda e
\]
is bounded.

The space \(L_p[0,1]\) is separable and is a \(p\)-Banach space.  By separable
injectivity of \(E\), the operator \(t\) extends to a bounded linear operator
\[
  T:L_p[0,1]\to E .
\]
Then \(S\circ T:L_p[0,1]\to F\) is a bounded linear operator and
\[
  (S\circ T)({\bf 1})=S(e)\neq 0.
\]
This contradicts the classical result, quoted in the source paper in Section
7.5, that every operator from \(L_p\) to a \(q\)-Banach space is zero whenever
\(p<q\leq 1\).  Therefore \(S=0\).

\begin{corollary}
If \(0<p<1\) and \(E\) is separably injective among \(p\)-Banach spaces, then
\(E^*=\{0\}\).  Moreover, the Banach envelope of \(E\) is trivial.
\end{corollary}

\begin{proof}
The scalar field \(\K\) is a \(1\)-Banach space, so the theorem gives
\(E^*=\{0\}\).  The canonical map from \(E\) into its Banach envelope is a
bounded operator from \(E\) into a Banach space.  Applying the theorem with
\(q=1\), this canonical map must be zero.  Hence the Banach envelope is the
zero space.
\end{proof}

\section*{Scope and Limitations}

This is only a partial obstruction to the source question.  It does not rule
out a nontrivial separable separably injective \(p\)-Banach space.  It shows
that any such example must have no nonzero maps into Banach spaces, no nonzero
dual, and no nonzero Banach envelope.  In particular, locally convex examples
and examples detectable by Banach-envelope methods are impossible.

\section*{Novelty Check}

The lightweight run indexes were searched for arXiv:1309.7649, separably
injective \(p\)-Banach spaces, Banach envelope, and the \(L_p\)-to-\(q\)-Banach
zero-operator obstruction.  No existing packet or attempt for this partial
obstruction was found.  Web searches for later work on \(p\)-Gurari\u{\i}
spaces, separably injective quasi-Banach spaces, and the \(K\)-space/quotient
questions surfaced the source paper but no later exact answer.

\section*{References}

\begin{itemize}
\item F. Cabello S\'anchez, J. Garbuli\'nska-Wegrzyn, and W. Kubi\'s,
\emph{Quasi-Banach spaces of almost universal disposition},
arXiv:1309.7649.
\item N. J. Kalton, \emph{Locally complemented subspaces and
\(\mathcal L_p\)-spaces for \(p<1\)}, Math. Nachr. 115 (1984), 71--97.
The zero-operator theorem used above is quoted in Section 7.5 of the source
paper.
\end{itemize}

\section*{Human Review Recommendation}

This packet is short and should be checked mainly for the exact formulation of
the Kalton zero-operator theorem and for the convention that \(L_p[0,1]\) is
included among the \(p\)-Banach spaces allowed in the separable-injectivity
definition.  Under those standard conventions, the proof is immediate.

\end{document}
