\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\title{Literature status note for arXiv:math/0201187, Problem 1}
\author{Run \texttt{fa\_banach\_001}, lane 12}
\date{2026-06-20}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.  This packet records an exact later
literature answer, not a new proof produced in the run.

\paragraph{Source question.}
In ``Contractive projections and operator spaces'', arXiv:math/0201187,
Neal and Russo ask as Problem 1 on PDF page 39:
\[
  \text{What is } d_{cb}(H_n^k,R_n)?
\]
The same paper identifies \(H_n^n\) with the row Hilbert space \(R_n\).

\paragraph{Answering source.}
In ``Representation of contractively complemented Hilbertian operator spaces
and the Fock space'', arXiv:math/0410337, Neal and Russo state in the
introduction that they give an explicit formula for the completely bounded
Banach-Mazur distance from \(H_n^k\) to \(R_n=H_n^n\) and \(C_n=H_n^1\),
answering a question posed in their earlier paper.
Theorem 3 gives
\[
  d_{cb}(H_n^k,H_n^1)=\sqrt{\frac{kn}{n-k+1}},
  \qquad 1\leq k\leq n.
\]
Immediately after, a corollary on PDF page 10 says that the following is the
answer to Problem 1 in the earlier paper:
\[
  d_{cb}(H_n^k,H_n^n)=\sqrt{\frac{(n-k+1)n}{k}},
  \qquad 1\leq k\leq n.
\]

\paragraph{Conclusion.}
Using \(R_n=H_n^n\), the exact answer to the extracted source problem is
\[
  \boxed{d_{cb}(H_n^k,R_n)=\sqrt{\frac{n(n-k+1)}{k}}}
  \qquad (1\leq k\leq n).
\]
The supporting authors explicitly knew this was the same problem: the later
paper says the displayed corollary answers Problem 1 in \cite{NR03}.

\paragraph{Scope.}
This resolves only the row-distance Problem 1 from the source paper.  The
broader classification Problem 2 in arXiv:math/0201187 is not settled by this
packet, and arXiv:math/0410337 itself poses further distance and duality
questions.

\begin{thebibliography}{9}

\bibitem{NR03}
M. Neal and B. Russo,
\emph{Contractive projections and operator spaces},
arXiv:math/0201187; Trans. Amer. Math. Soc. \textbf{355} (2003), 2223--2262.

\bibitem{NR06}
M. Neal and B. Russo,
\emph{Representation of contractively complemented Hilbertian operator spaces
and the Fock space},
arXiv:math/0410337; Proc. Amer. Math. Soc. \textbf{134} (2006), 475--485.

\end{thebibliography}

\end{document}
