\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\newcommand{\ellp}{\ell_p}

\title{Literature-Implied Status for the Classical-Space Subquestion in arXiv:math/0304018}
\author{Run fa\_banach\_001, agent\_lane\_15}
\date{July 3, 2026}

\begin{document}
\maketitle

\paragraph{Status.}
This note records a literature-implied answer to the classical-space subquestion in Ferenczi--Rosendal's
\emph{Ergodic Banach Spaces}, arXiv:math/0304018. It is not a new result of the run.
The broad conjecture that $\ell_2$ is the only non-ergodic separable Banach space remains open in the later literature cited here.

\paragraph{Source question.}
Near the end of arXiv:math/0304018, after Proposition 20 and before the acknowledgements, Ferenczi and Rosendal write that they conjecture that $\ell_2$ is the only non-ergodic Banach space. They then point out a concrete missing case: they are not even able to prove that $c_0$ and $\ell_p$, $p\neq 2$, are ergodic.

\paragraph{Supporting theorem and identification.}
Cuellar Carrera's \emph{Non-ergodic Banach spaces are near Hilbert}, arXiv:1611.05500, proves in Theorem 3.2 of that paper that every separable non-near-Hilbert Banach space satisfies the Cantorized-Enflo criterion and is therefore ergodic. Equivalently, every non-ergodic separable Banach space must be near Hilbert. Since $\ell_p$ is not near Hilbert for $p\neq 2$, this theorem already implies the $\ell_p$ cases conceptually.

The paper also records the classical cases explicitly. In its introduction it cites Ferenczi--Galego for ergodicity of $c_0$ and $\ell_p$ for $1\leq p<2$. Its Corollary after Proposition 2.2 says that if $\ell_p$, $p>2$, is crudely finitely representable in a separable Banach space $X$, then $X$ is ergodic; applying this to $X=\ell_p$ gives ergodicity for every $2<p<\infty$. The same introduction explicitly says that this solves the Ferenczi--Rosendal question about the ergodicity of the $\ell_p$ spaces for $p>2$.

\paragraph{Scope.}
Thus the explicit source subquestion about the classical spaces $c_0$ and $\ell_p$, $p\neq2$, is answered by known literature. This packet should prevent future agents from treating that subquestion as open. It does not settle the full conjecture that $\ell_2$ is the only non-ergodic Banach space: Cuellar Carrera's final remarks reduce the remaining territory to near-Hilbert phenomena and list HAP and twisted-Hilbert questions as natural remaining problems.

\paragraph{References.}
\begin{itemize}
\item V. Ferenczi and C. Rosendal, \emph{Ergodic Banach Spaces}, arXiv:math/0304018; Adv. Math. 195 (2005), 259--282.
\item W. Cuellar Carrera, \emph{Non-ergodic Banach spaces are near Hilbert}, arXiv:1611.05500.
\item V. Ferenczi and E. Galego, \emph{Some equivalence relations which are Borel reducible to isomorphism between separable Banach spaces}, Israel J. Math. 152 (2006), 61--82.
\end{itemize}

\end{document}
