\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem*{theorem}{Theorem}
\newtheorem*{corollary}{Corollary}
\newcommand{\linf}{\mathcal L_\infty}
\newcommand{\ellone}{\ell_1}
\newcommand{\czero}{c_0}

\title{Schur Quotients Force \(\ell_1\) in Lopez-Abad Superspaces}
\author{Run fa\_banach\_001}
\date{2026-06-28}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{partial\_result\_likely\_valid}.  This packet proves a narrow
obstruction for the construction route around arXiv:1210.5728.  It is not a
solution of the full nonseparable Bourgain--Delbaen problem.

\paragraph{Source target.}
In the introduction of Lopez-Abad's \emph{A Bourgain-Pisier construction for
general Banach spaces}, arXiv:1210.5728, the author notes that nothing is known
about removing separability in the Freeman--Odell--Schlumprecht embedding
theorem, or even in the more basic problem of whether a nonseparable
Bourgain--Delbaen space exists, i.e. a nonseparable \(\linf\)-space containing
no isomorphic copies of \(\czero\) or \(\ellone\).

\paragraph{Idea of the proof.}
The quotient in the Lopez-Abad/Bourgain--Pisier extension method has the Schur
property.  Infinite-dimensional Schur spaces necessarily contain \(\ellone\),
and \(\ellone\) lifts through quotient maps by its projectivity.  Therefore a
Schur-quotient extension cannot avoid \(\ellone\) in the total space.

\begin{theorem}
Let \(q:Y\to Q\) be a quotient map between Banach spaces.  If \(Q\) is
infinite-dimensional and has the Schur property, then \(Y\) contains a subspace
isomorphic to \(\ellone\).
\end{theorem}

\begin{proof}
First, \(Q\) contains \(\ellone\).  Indeed, choose a bounded sequence in \(Q\)
with no norm-convergent subsequence; by passing to a subsequence, assume it is
separated.  If this sequence had no subsequence equivalent to the unit vector
basis of \(\ellone\), Rosenthal's \(\ellone\) theorem would give a weakly
Cauchy subsequence.  The difference sequence of that weakly Cauchy subsequence
is weakly null, hence norm null by the Schur property, contradicting
separation.  Thus some subspace \(E\subseteq Q\) is isomorphic to \(\ellone\).

Let \(A:\ellone\to Q\) be an isomorphic embedding with range \(E\).  Since
\(\ellone\) is projective, \(A\) lifts through \(q\): for example, for each
unit vector \(e_n\) choose \(y_n\in Y\) with \(q(y_n)=A e_n\) and
\(\|y_n\|\le C\|A e_n\|\), where \(C\) is a fixed quotient-open-mapping
constant.  Then
\[
U((a_n))=\sum_{n=1}^\infty a_n y_n
\]
defines a bounded operator \(U:\ellone\to Y\) and \(qU=A\).  Since \(A\) is
bounded below and \(q\) is bounded, \(U\) is bounded below as well:
\[
\|U a\|\ge \frac{\|A a\|}{\|q\|}\qquad(a\in\ellone).
\]
Hence \(U[\ellone]\) is a subspace of \(Y\) isomorphic to \(\ellone\).
\end{proof}

\begin{corollary}
Any Lopez-Abad / nonseparable Bourgain--Pisier \(\linf\)-space \(Y\) whose
canonical quotient \(Y/X\) is infinite-dimensional with the Schur property
contains an isomorphic copy of \(\ellone\).  Consequently this construction
class cannot provide a nonseparable \(\linf\)-space containing neither
\(\czero\) nor \(\ellone\).
\end{corollary}

\begin{proof}
Apply the theorem to the quotient map \(Y\to Y/X\).  Lopez-Abad's construction
is designed so that \(Y/X\) has the Schur property; the later analysis in
Patri, arXiv:2604.11832, records the nonseparable Bourgain--Pisier
Lopez-Abad class as having infinite-dimensional Schur quotient.
\end{proof}

\paragraph{Verification and limitations.}
The proof uses only Rosenthal's \(\ellone\) theorem, the Schur property, and
the elementary projectivity of \(\ellone\).  The conclusion is route-specific:
it rules out Schur-quotient Bourgain--Pisier superspaces as candidates for the
``no \(\czero\), no \(\ellone\)'' nonseparable Bourgain--Delbaen problem, but
it does not rule out other nonseparable \(\linf\)-space constructions.

\paragraph{Search notes.}
Local index searches for arXiv:1210.5728, Bourgain--Pisier,
Bourgain--Delbaen, nonseparable \(\linf\), \(\czero\), and \(\ellone\) found
no exact prior packet for this obstruction.  A web search on 2026-06-28 found
Patri, arXiv:2604.11832, concerning separable quotients of nonseparable
Bourgain--Pisier spaces, but no full solution of the no-\(\czero\),
no-\(\ellone\) nonseparable Bourgain--Delbaen problem.

\begin{thebibliography}{9}

\bibitem{LopezAbad}
J. Lopez-Abad,
\emph{A Bourgain-Pisier construction for general Banach spaces},
arXiv:1210.5728.

\bibitem{Patri}
K. Patri,
\emph{Mazur's Separable Quotient Problem for Nonseparable Bourgain-Pisier
\(\mathcal L_\infty\)-Spaces},
arXiv:2604.11832.

\bibitem{Rosenthal}
H. P. Rosenthal,
\emph{A characterization of Banach spaces containing \(\ell_1\)},
Proc. Nat. Acad. Sci. U.S.A. 71 (1974), 2411--2413.

\end{thebibliography}

\end{document}
