\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status Note for arXiv:math/0404304}
\author{run \texttt{fa\_banach\_001}, lane 1}
\date{2026-07-03}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered} (non-original; the source itself footnotes the announced positive answer, and a later paper gives a theorem-level write-up).

\paragraph{Source question.}
In Section 4, ``Open Problems'', item (b), Brudnyi and Brudnyi ask whether the conclusion
\[
  \lambda(\ell_p)=\infty \quad (p\neq 2)
\]
also holds for infinite-dimensional Hilbert spaces.  The same item contains a footnote saying that the answer is positive and that a forthcoming paper will prove
\[
  \lambda(X)=\infty
\]
for every infinite-dimensional Banach space \(X\).

\paragraph{Supporting paper and theorem.}
Sofi, \emph{Extension operators and nonlinear structure of Banach spaces}, arXiv:2001.09303, gives the relevant statement in Theorem 2.10: a Banach space \(X\) has the simultaneous Lipschitz extension property (SLEP) if and only if \(X\) is finite dimensional.  In the proof, Sofi explicitly claims and derives that
\[
  \lambda(X)=\infty
\]
for every infinite-dimensional Banach space \(X\), using Dvoretzky's theorem, lower bounds for \(\lambda(\ell_2^n)\), and the retraction inequality for extension constants.  Therefore the source question has a positive answer for \(X=\ell_2\), and in fact for every infinite-dimensional Hilbert space.

\paragraph{Why this is not a new result.}
The source question is already accompanied by a footnote announcing the positive answer.  The supporting paper supplies a later explicit theorem-level account and cites the Brudnyi--Brudnyi literature for the underlying nonextension argument.  This packet is therefore only a duplicate-prevention and literature-status record.

\paragraph{Scope notes.}
The theorem also shows that any infinite-dimensional Hilbert space fails SLEP.  Consequently, if the source's later Alexandrov open problem is read without a finite-dimensional or local-compactness restriction, then \(M=\ell_2\) gives a complete simply connected CAT(0) length-space obstruction to \(\lambda(M)<\infty\).  This packet does not address a possible narrower interpretation restricted to finite-dimensional or locally compact Alexandrov spaces.  It also does not settle the source's general product problem or uniform-lattice conjecture.

\paragraph{Local evidence.}
The source question is visible in the parsed TeX for arXiv:math/0404304 around lines 1072--1083.  Sofi's SLEP theorem and proof are visible in the parsed TeX for arXiv:2001.09303 around lines 231--283.

\end{document}
