\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}

\newcommand{\ellone}{\ell_1}
\newcommand{\ellinf}{\ell_\infty}
\newcommand{\N}{\mathbb{N}}
\newcommand{\ba}{\mathrm{ba}(\N)}
\newcommand{\wstar}{w^\ast}

\title{Literature-Implied Negative Answer to a PGP Variant of Wnuk's Disjoint Test}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_00}}
\date{2026-06-23}

\begin{document}
\sloppy
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer}.  The proposed positive-Grothendieck
analogue of Wnuk's disjoint-test characterization is false.  The counterexample
is the standard Banach lattice \(E=\ellone\).  The relevant separation was
already recorded in arXiv:2011.09319, so this packet is classified as a
literature-implied answer rather than a new counterexample.

\paragraph{Source question.}
In Section 1.2 of Alpay--Emelyanov--Gorokhova, \emph{Generalizations of L- and
M-weakly compact operators}, arXiv:2206.02718 \cite{AEG}, immediately before
Assertion \texttt{Wnuk2013}, the authors recall Wnuk's assertion:
\[
  E\in(\mathrm{DPSP})
  \quad\Longleftrightarrow\quad
  \text{every disjoint \(\wstar\)-null sequence in \(E'_+\) is norm null.}
\]
They ask whether, in this assertion, \((\mathrm{DPSP})\) can be replaced by
\((\mathrm{PGP})\) and ``norm null'' by ``weakly null''.

\paragraph{Supporting literature.}
Lourenco--Miranda, \emph{A note on the Banach lattice
\(c_0(\ell_2^n)\), its dual and its bidual}, arXiv:2011.09319 \cite{LM},
recall in the introduction that \(\ellone\) has the weak Grothendieck property
but fails the positive Grothendieck property.  The weak Grothendieck property is
the condition that every disjoint \(\wstar\)-null sequence in \(E'\) is weakly
null, hence it is stronger than the positive-disjoint test in the question.

\paragraph{Direct verification.}
Let \(E=\ellone\), so \(E'=\ellinf\) with its usual coordinatewise lattice
order, and \((\ellinf)'=\ba\).

First, every bounded disjoint sequence in \(\ellinf\) is weakly null.  Indeed,
let \((x_n)\subseteq \ellinf\) be bounded and disjoint, say
\(\|x_n\|_\infty\le M\).  Put
\[
  A_n=\{k\in\N: x_n(k)\ne 0\}.
\]
The sets \(A_n\) are pairwise disjoint.  If \(\mu\in\ba\) and \(|\mu|\) is its
variation, then
\[
  |\mu(x_n)|\le M\,|\mu|(A_n).
\]
Since \(|\mu|\) is a finite finitely additive positive measure, pairwise
disjointness gives
\[
  \sum_{j=1}^N |\mu|(A_j)\le |\mu|(\N)
  \quad (N\in\N),
\]
and therefore \(|\mu|(A_n)\to 0\).  Thus \(\mu(x_n)\to0\) for every
\(\mu\in(\ellinf)'\), so \(x_n\to0\) weakly in \(\ellinf\).  In particular,
every disjoint \(\wstar\)-null sequence in \(E'_+\) is weakly null.

Second, \(E\) does not have the positive Grothendieck property.  Let
\[
  u_n=\mathbf{1}_{\{k\in\N:k\ge n\}}\in{\ellinf}_+.
\]
For every \(a=(a_k)\in\ellone\),
\[
  \langle u_n,a\rangle=\sum_{k\ge n} a_k\to0,
\]
so \((u_n)\) is \(\wstar\)-null in \(E'=\ellinf\).  However \((u_n)\) is not
weakly null.  If \(\mathcal U\) is a free ultrafilter on \(\N\), then
\[
  \Phi_{\mathcal U}(x)=\lim_{\mathcal U} x_k
\]
defines a positive norm-one functional on \(\ellinf\), and every cofinite set
belongs to \(\mathcal U\).  Hence
\[
  \Phi_{\mathcal U}(u_n)=1\quad(n\in\N).
\]
So \(u_n\) is positive and \(\wstar\)-null but not weakly null.

\paragraph{Conclusion.}
The Banach lattice \(E=\ellone\) satisfies the proposed disjoint positive test
but fails \((\mathrm{PGP})\).  Therefore Wnuk's \((\mathrm{DPSP})\)
characterization does not remain true after replacing \((\mathrm{DPSP})\) by
\((\mathrm{PGP})\) and norm convergence by weak convergence.

\paragraph{Scope and provenance.}
This is a full negative answer to the replacement question in arXiv:2206.02718,
but it is not recorded as a new run counterexample.  The key property separation
for \(\ellone\) appears in \cite{LM}; this packet supplies the direct
identification with the 2022 question and a short verification.

\begin{thebibliography}{9}
\bibitem{AEG}
S. Alpay, E. Emelyanov, and S. Gorokhova,
\emph{Generalizations of L- and M-weakly compact operators},
arXiv:2206.02718.

\bibitem{LM}
M. L. Lourenco and V. C. C. Miranda,
\emph{A note on the Banach lattice \(c_0(\ell_2^n)\), its dual and its bidual},
arXiv:2011.09319.
\end{thebibliography}

\end{document}
