\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\Lipz}{\operatorname{Lip}_0}
\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\FF}{\mathcal F}
\newcommand{\Id}{\operatorname{Id}}

\begin{document}

\section*{Human Review: Linearizing Lipschitz Extension Operators}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 15 June 2026

\noindent Status: Manually checked.

\noindent Verdict: The proof appears correct.

\section*{Human Comments}

The proof appears to correctly answer the question from Sofi's Remark 2.2(ii). The key point is that a Lipschitz, not necessarily linear, extension operator
\[
  F:\Lipz(Z)\longrightarrow \Lipz(X),
  \qquad F(f)|_Z=f,
\]
can be replaced by a bounded linear extension operator by averaging its finite differences over the additive abelian group \(\Lipz(Z)\). Once this linearization is obtained, Sofi's Corollary 2.4 applies and gives that \(X\) is isomorphic to a Hilbert space.

The idea is sound. However, the notation in the automatic proof is slightly more abstract than necessary. Introducing temporary symbols such as \(Y\) and \(V\) makes the proof harder to read, especially at the averaging step. It is clearer to keep the spaces visible throughout: the domain group is \(\Lipz(Z)\), and the values lie in \(\Lipz(X)=\FF(X)^*\).

\section*{Notation-Improved Verification of the Averaging Step}

Assume, after replacing \(F\) by \(F-F(0)\), that
\[
  F(0)=0,
  \qquad F(f)|_Z=f
\]
for every \(f\in\Lipz(Z)\). Let
\[
  L=\Lip(F).
\]

Since \(\Lipz(Z)\) is an additive abelian group, it admits an invariant mean. Thus there is a positive norm-one functional
\[
  m:\ell_\infty(\Lipz(Z))\longrightarrow \mathbb R
\]
such that
\[
  m(\varphi(\cdot+a))=m(\varphi)
  \qquad
  (a\in\Lipz(Z),\ \varphi\in\ell_\infty(\Lipz(Z))).
\]

For each \(h\in\Lipz(Z)\), define the bounded \(\Lipz(X)\)-valued function
\[
  \Delta_h:\Lipz(Z)\longrightarrow \Lipz(X)
\]
by
\[
  \Delta_h(g)=F(g+h)-F(g),
  \qquad g\in\Lipz(Z).
\]
This is bounded because
\[
  \|\Delta_h(g)\|_{\Lip}
  =\|F(g+h)-F(g)\|_{\Lip}
  \leq L\|h\|_{\Lip}
\]
for every \(g\in\Lipz(Z)\).

Now use the canonical duality
\[
  \Lipz(X)=\FF(X)^*.
\]
The invariant mean \(m\) only acts on scalar-valued bounded functions, so the average of \(\Delta_h\) is defined weak-star coordinate by weak-star coordinate. Namely, define \(G(h)\in\FF(X)^*=\Lipz(X)\) by
\[
  \langle \mu,G(h)\rangle
  =
  m\bigl(g\mapsto \langle \mu,\Delta_h(g)\rangle\bigr),
  \qquad \mu\in\FF(X).
\]
For fixed \(\mu\in\FF(X)\), the function
\[
  g\mapsto \langle \mu,\Delta_h(g)\rangle
\]
is bounded, since
\[
  |\langle \mu,\Delta_h(g)\rangle|
  \leq \|\mu\|\,\|\Delta_h(g)\|_{\Lip}
  \leq L\|h\|_{\Lip}\|\mu\|.
\]
Therefore the definition is legitimate. Moreover,
\[
  |\langle \mu,G(h)\rangle|
  \leq L\|h\|_{\Lip}\|\mu\|,
\]
and hence
\[
  \|G(h)\|_{\Lip}\leq L\|h\|_{\Lip}.
\]

Linearity follows from translation invariance of the mean. Indeed, for \(h,k\in\Lipz(Z)\),
\[
  \Delta_{h+k}(g)
  =F(g+h+k)-F(g)
  =\Delta_k(g+h)+\Delta_h(g).
\]
Averaging over \(g\), the first term satisfies
\[
  m\bigl(g\mapsto \langle\mu,\Delta_k(g+h)\rangle\bigr)
  =m\bigl(g\mapsto \langle\mu,\Delta_k(g)\rangle\bigr)
\]
by invariance of \(m\). Thus
\[
  G(h+k)=G(h)+G(k).
\]
Since \(G\) is additive and satisfies
\[
  \|G(h)\|_{\Lip}\leq L\|h\|_{\Lip},
\]
it is continuous at the origin. Additivity gives \(G(qh)=qG(h)\) for rational
\(q\), and continuity then extends this identity to every real scalar. Hence
\(G\) is real linear.

Finally, \(G\) is still an extension operator. Let
\[
  \rho:\Lipz(X)\longrightarrow\Lipz(Z)
\]
be restriction. If
\[
  J:\FF(Z)\longrightarrow\FF(X)
\]
is the canonical map induced by the inclusion \(Z\subset X\), then
\[
  \rho=J^*.
\]
For \(\nu\in\FF(Z)\),
\begin{align*}
  \langle \nu,\rho G(h)\rangle
  &=\langle J\nu,G(h)\rangle \\
  &=m\bigl(g\mapsto \langle J\nu,F(g+h)-F(g)\rangle\bigr)\\
  &=m\bigl(g\mapsto \langle \nu,\rho F(g+h)-\rho F(g)\rangle\bigr)\\
  &=m\bigl(g\mapsto \langle \nu,(g+h)-g\rangle\bigr)\\
  &=\langle \nu,h\rangle.
\end{align*}
Therefore
\[
  \rho G(h)=h,
\]
so \(G(h)|_Z=h\). This proves that the original Lipschitz extension operator can be linearized into a bounded linear extension operator.

\section*{Review Outcome}

Archive this packet as an apparently correct full solution, pending any later author or literature feedback. The proof's central averaging argument looks correct; in a polished version, I would recommend using the notation above rather than the more compressed \(Y,V\) notation, since it makes clear that \(\Delta_h\) is a bounded \(\Lipz(X)\)-valued function on \(\Lipz(Z)\), and that the invariant mean is applied only after pairing with elements of \(\FF(X)\).

\end{document}
