\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}
\emergencystretch=2em

\newcommand{\linf}{\ell_\infty}
\newcommand{\cnull}{c_0}
\newcommand{\Linf}{\mathcal L_\infty}

\title{A Literature-Implied Negative Answer to the Argyros--Haydon \(\Linf\) Strictly Singular Question}
\author{Math discovery packet}
\date{June 29, 2026}

\begin{document}
\maketitle

\section{Status}

This is a lightweight \emph{literature-implied answer}, not a new
construction.  The source paper is S. A. Argyros and R. G. Haydon,
\emph{A hereditarily indecomposable \(\Linf\)-space that solves the
scalar-plus-compact problem}, arXiv:0903.3921.
In the concluding open problems, after asking whether an isomorphic predual of
\(\ell_1\) with scalar-plus-strictly-singular operators must also have the
scalar-plus-compact property, the paper asks the more general problem:
\begin{quote}
Let \(X\) be a \(\Linf\)-space. Is every strictly singular operator on \(X\)
weakly compact?
\end{quote}

The supporting paper is A. Aviles, F. Cabello Sanchez, J. M. F. Castillo,
M. Gonzalez and Y. Moreno, \emph{On separably injective Banach spaces},
arXiv:1103.6064.

\section{Identification}

Section 2 of arXiv:1103.6064 discusses Pelczynski's property \((V)\).  It
states that not all \(\mathcal L_\infty\)-spaces have property \((V)\), and
among its examples records the space \(\Omega\) of Cabello Sanchez--Castillo--
Kalton--Yost in a twisted sum
\[
  0 \longrightarrow C[0,1] \stackrel{i}{\longrightarrow} \Omega
    \stackrel{q}{\longrightarrow} \cnull \longrightarrow 0
\]
with \(q\) a strictly singular quotient map.  Thus \(\Omega\) is an
\(\mathcal L_\infty\)-space and \(q:\Omega\to\cnull\) is strictly singular.

Since \(C[0,1]\) contains a subspace isomorphic to \(\cnull\), choose an
isomorphic embedding \(e:\cnull\to C[0,1]\), and put
\[
  J=i\circ e:\cnull\to\Omega,\qquad T=Jq:\Omega\to\Omega .
\]

\section{The Counterexample Operator}

The operator \(T\) is strictly singular.  Indeed, \(q\) is strictly singular
and the class of strictly singular operators is a two-sided operator ideal, so
post-composition by the bounded map \(J\) preserves strict singularity.

The operator \(T\) is not weakly compact.  Since \(q\) is a quotient map, the
open mapping theorem gives a constant \(C<\infty\) such that every
\(y\in B_{\cnull}\) has some \(x\in C B_\Omega\) with \(q x=y\).  Therefore
\[
  J(B_{\cnull})\subseteq T(CB_\Omega).
\]
If \(T\) were weakly compact, then \(T(CB_\Omega)\) would be relatively weakly
compact, hence so would \(J(B_{\cnull})\).  But \(J\) is an isomorphic
embedding of \(\cnull\), and the weak topology on \(J(\cnull)\) is inherited
from \(\Omega\).  Thus relative weak compactness of \(J(B_{\cnull})\) would
make the unit ball of \(\cnull\) weakly compact, contradicting the
non-reflexivity of \(\cnull\).

Consequently the \(\mathcal L_\infty\)-space \(\Omega\) admits a strictly
singular operator on itself that is not weakly compact.  This gives a negative
answer to the Argyros--Haydon problem as stated.

\section{Scope}

This does not solve the separate reflexive scalar-plus-compact problem from
the same concluding section of arXiv:0903.3921.  It also does not decide the
more special question about isomorphic preduals of \(\ell_1\) with the
scalar-plus-strictly-singular property; the counterexample above is supplied
by a different \(\mathcal L_\infty\)-space.

The implication appears to be agent-identified.  A local search of
arXiv:1103.6064 found the twisted-sum example and found no explicit citation
to arXiv:0903.3921 or to the Argyros--Haydon scalar-plus-compact problem in
the supporting passage.

\section{References}

\begin{itemize}[leftmargin=*]
\item S. A. Argyros and R. G. Haydon, \emph{A hereditarily indecomposable
\(\Linf\)-space that solves the scalar-plus-compact problem},
arXiv:0903.3921.
\item A. Aviles, F. Cabello Sanchez, J. M. F. Castillo, M. Gonzalez and
Y. Moreno, \emph{On separably injective Banach spaces}, arXiv:1103.6064.
\item F. Cabello Sanchez, J. M. F. Castillo, N. J. Kalton and D. T. Yost,
\emph{Twisted sums with \(C(K)\)-spaces}, Trans. Amer. Math. Soc. 355
(2003), 4523--4541.
\end{itemize}

\end{document}
