\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Answer To The Amenable Calkin Algebra Question In arXiv:0909.2628}
\author{Run fa\_banach\_001}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

\textbf{literature\_implied\_answer (full problem).}
This packet records a positive answer to the Calkin-algebra question in
Runde \cite{Runde2009}, obtained by direct identification with the
\(C(K)\)-Calkin realization theorem of Motakis--Puglisi--Zisimopoulou
\cite{MPZ2014}.  The supporting authors do not explicitly say that they
are answering Runde's question; the implication is agent-identified.

\section*{Source Question}

In the final section, `Questions', Runde asks:
\begin{quote}
Is there a Banach space \(E\) such that \(\mathcal C(E)\) is amenable and
infinite-dimensional?
\end{quote}
Here \(\mathcal C(E)=\mathcal B(E)/\mathcal K(E)\) is the Calkin algebra.

\section*{Supporting Theorem}

Motakis--Puglisi--Zisimopoulou prove, as Theorem B in the introduction
and as Theorem 5.1 in the final section, that for every countable compact
metric space \(K\) there is a Banach space \(X\), indeed an
\(\mathcal L_\infty\)-space with \(X^*\cong \ell_1\), such that
\[
\mathcal C(X)\cong C(K)
\]
as Banach algebras.

\section*{Identification}

Let
\[
K=\{0\}\cup \{1/n:n\in \mathbb N\}\subset \mathbb R.
\]
Then \(K\) is an infinite countable compact metric space.  By
\cite{MPZ2014}, there exists a Banach space \(X\) such that
\(\mathcal C(X)\cong C(K)\) as Banach algebras.  The algebra \(C(K)\) is
infinite-dimensional, since \(K\) is infinite and compact Hausdorff.

Moreover \(C(K)\) is a commutative \(C^*\)-algebra.  Commutative
\(C^*\)-algebras are nuclear, and Runde's source paper recalls the
standard theorem that nuclear \(C^*\)-algebras are amenable as Banach
algebras.  Hence \(C(K)\) is amenable.  Amenability is preserved under
Banach algebra isomorphism, so \(\mathcal C(X)\) is amenable and
infinite-dimensional.

\section*{Scope And Search}

This is not a new construction from the run.  It is a full positive
literature-implied answer to Runde's question.  Cheap run indexes were
searched for `0909.2628', `amenable Calkin', `C(K) Calkin', and close
variants; no exact prior packet was found.  Local source search and web
search both surfaced arXiv:1407.8073 as the decisive supporting source.

\begin{thebibliography}{9}
\bibitem{Runde2009}
V. Runde,
\emph{(Non-)amenability of \(\mathcal B(E)\)},
arXiv:0909.2628, 2009.

\bibitem{MPZ2014}
P. Motakis, D. Puglisi, and D. Zisimopoulou,
\emph{A hierarchy of Banach spaces with \(C(K)\) Calkin Algebras},
arXiv:1407.8073, 2014.
\end{thebibliography}

\end{document}
