\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\newcommand{\F}{\mathcal F}
\newcommand{\N}{\mathbb N}
\newcommand{\Id}{\mathrm{Id}}
\newcommand{\BAP}{\mathrm{BAP}}

\title{A BAP Obstruction for Filter Bases over UBP Filters}
\author{Run \texttt{fa\_banach\_001}, target arXiv:2509.20002}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Source And Target}

The source paper is V. Kadets and M. Manskova,
\emph{Norms of partial sums operators for a basis with respect to a filter},
arXiv:2509.20002.  Near the end of the paper the authors write that one of the
most intriguing open problems about $\F$-bases is whether every separable Banach
space has an $\F$-basis for some free filter $\F$, and, for a fixed filter
$\F$, whether a given space has an $\F$-basis.  They mention the statistical
convergence filter as an important concrete case still outside their slow-filter
negative theorem.

This packet records a partial obstruction for a different large class of
filters: Banach-UBP filters in the sense of De Bondt--Vernaeve.

\section*{Definitions}

Let $\F$ be a free filter on $\N$.  A sequence $(e_n)$ in a Banach space $X$ is
an $\F$-basis if for every $x\in X$ there is a unique scalar sequence
$(a_n)$ such that
\[
  \F\text{-}\lim_n \sum_{k=1}^n a_k e_k = x.
\]
When the coordinate functionals $e_n^*(x)=a_n$ are continuous, the partial sums
\[
  S_nx=\sum_{k=1}^n e_k^*(x)e_k
\]
are continuous finite-rank operators and $S_nx\to_\F x$ for every $x\in X$.

Following De Bondt--Vernaeve, $\F$ is a Banach-UBP filter if the uniform
$\F$-boundedness principle holds for every Banach domain.  In the normed
operator setting this means: every pointwise $\F$-bounded sequence
$(T_n)\subset L(X,Y)$ is $\F$-bounded in operator norm.

\section*{Idea Of The Proof}

The partial sums of a continuous-coordinate $\F$-basis are finite-rank
approximants to the identity along $\F$.  Pointwise $\F$-convergence makes them
pointwise $\F$-bounded.  The Banach-UBP property upgrades this to a uniform
operator-norm bound on an $\F$-large set of indices.  Intersect that large set
with the finitely many approximation sets needed for a compact net; one of the
remaining finite-rank partial sums approximates the whole compact set with the
same uniform bound.  That is the bounded approximation property.

\begin{theorem}
Let $\F$ be a Banach-UBP filter.  If a Banach space $X$ has an $\F$-basis whose
coordinate functionals are continuous, then $X$ has the bounded approximation
property.
\end{theorem}

\begin{proof}
Let $(e_n)$ be the $\F$-basis and let $S_n$ be its partial sum operators.  For
each $x\in X$, $S_nx\to_\F x$, hence $(S_nx)$ is $\F$-bounded in $X$.  Thus
$(S_n)$ is pointwise $\F$-bounded in $L(X,X)$.

Since $\F$ is a Banach-UBP filter, $(S_n)$ is $\F$-bounded in operator norm.
Therefore there are a set $A\in\F$ and a constant $C<\infty$ such that
\[
  \sup_{n\in A}\|S_n\|\le C.
\]

Let $K\subset X$ be compact and fix $\varepsilon>0$.  Choose
$x_1,\ldots,x_m\in K$ such that every point of $K$ is within
\[
  \delta=\frac{\varepsilon}{3(C+1)}
\]
of some $x_j$.  For each $j$, the set
\[
  G_j=\{n\in\N:\|S_nx_j-x_j\|<\varepsilon/3\}
\]
belongs to $\F$.  Hence
\[
  A\cap G_1\cap\cdots\cap G_m\in\F
\]
and is nonempty.  Pick $n$ in this intersection.  Then $S_n$ is finite rank,
$\|S_n\|\le C$, and for any $x\in K$, choosing $x_j$ with
$\|x-x_j\|<\delta$, we have
\[
\begin{aligned}
\|S_nx-x\|
&\le \|S_n(x-x_j)\|+\|S_nx_j-x_j\|+\|x_j-x\| \\
&\le C\delta+\varepsilon/3+\delta <\varepsilon.
\end{aligned}
\]
Thus finite-rank operators with a common norm bound approximate the identity
uniformly on arbitrary compact subsets of $X$.  This is the bounded
approximation property.
\end{proof}

\begin{corollary}
Let $X$ be a separable Banach space without the approximation property.  Then
$X$ has no $\F$-basis with continuous coordinate functionals for any Banach-UBP
filter $\F$.
\end{corollary}

\begin{proof}
The bounded approximation property implies the approximation property.
Therefore the theorem rules out such an $\F$-basis on any space failing AP,
for example Enflo's separable counterexample to the approximation problem.
\end{proof}

\begin{corollary}
If $\F$ is both analytic and a Banach-UBP filter, then every separable Banach
space without the approximation property has no $\F$-basis.
\end{corollary}

\begin{proof}
De Rancourt--Kania--Swaczyna prove that for analytic filters the coordinate
functionals of every $\F$-basis are continuous.  The preceding corollary then
applies.
\end{proof}

\section*{Limitations}

This is a partial obstruction, not a full solution of the source problem.  It
does not decide whether every separable Banach space has an $\F$-basis for some
free filter.  It also does not decide the fixed-filter problem for the
statistical convergence filter.  De Bondt--Vernaeve record that the asymptotic
density filter is weak $P^+$ but neither $P^+$ nor rapid$^+$, so it is outside
the Banach-UBP class even though it is analytic and hence has automatic
coordinate continuity by de Rancourt--Kania--Swaczyna.

The separate endpoint problem in the source's description of
$\mathcal A(w^*,\ell_p^*,\F)$ for $1<p<2$ also remains open after this pass.

\section*{Novelty Check}

The run indexes were searched for arXiv:2509.20002, the paper title,
\texttt{F-basis}, \texttt{filter basis}, \texttt{bounded approximation
property}, \texttt{BAP}, \texttt{UBP}, and \texttt{approximation property}.  No
prior packet or attempt for this target was found.  Web searches on
2026-07-01 for exact and close phrases such as ``filter basis bounded
approximation property'', ``F-basis bounded approximation property'', and
``F-basis Uniform Boundedness Principle filter Banach'' did not reveal a direct
prior statement of this obstruction.

\section*{References}

\begin{enumerate}[label={[\arabic*]}]
\item V. Kadets and M. Manskova, \emph{Norms of partial sums operators for a
basis with respect to a filter}, arXiv:2509.20002.
\item M. De Bondt and H. Vernaeve, \emph{Filter-dependent versions of the
Uniform Boundedness Principle}, J. Math. Anal. Appl. 504 (2021), arXiv:2001.01663.
\item N. de Rancourt, T. Kania, and J. Swaczyna, \emph{Continuity of coordinate
functionals of filter bases in Banach spaces}, J. Funct. Anal. 284 (2023),
Article 109869, arXiv:2203.15123.
\item P. Enflo, \emph{A counterexample to the approximation problem in Banach
spaces}, Acta Math. 130 (1973), 309--317.
\end{enumerate}

\end{document}
