\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\G}{\mathcal G}
\newcommand{\C}{\mathbb C}
\newcommand{\T}{\mathbb T}
\newcommand{\supp}{\operatorname{supp}}

\title{A topologically principal partial answer to the twisted \(RD_p\) question}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_17}}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source question}

Austad--Ortega--Palmstrom, \emph{Polynomial growth and property \(RD_p\) for
etale groupoids with applications to \(K\)-theory}, arXiv:2304.14458, define
\(\sigma\)-twisted property \(RD_p\) for a continuous normalized
\(2\)-cocycle \(\sigma\) on an etale groupoid \(\G\).  They note that ordinary
\(RD_p\) implies \(\sigma\)-twisted \(RD_p\), and ask whether the converse holds
when \(\sigma\) is not cohomologous to the trivial cocycle.

\section*{Result}

\begin{theorem}
Let \(l:\G\to [0,\infty)\) be a length function, let
\(\sigma:\G^{(2)}\to\T\) be a continuous normalized \(2\)-cocycle, and let
\(1\le p<\infty\).  If either
\begin{enumerate}
\item \(\G\) is principal etale and \(l\) is continuous, or
\item \(\G\) is \(\sigma\)-compact, topologically principal, etale, and \(l\)
is continuous and proper,
\end{enumerate}
then \(\sigma\)-twisted property \(RD_p\) with respect to \(l\) implies ordinary
property \(RD_p\) with respect to \(l\).

More precisely, for \(1<p<\infty\), \(\sigma\)-twisted \(RD_p\) forces
polynomial growth of \(\G\) with respect to \(l\) in either case.
\end{theorem}

\section*{Proof intuition}

Weygandt proved the corresponding \(p=2\) obstruction for twisted
\(C^*\)-algebras of principal and topologically principal etale groupoids.  The
operator-norm obstruction is not Hilbert-specific.  If a source-fiber ball
contains a large finite set \(F\) on which the range map is injective, the
products \(\gamma\eta^{-1}\), \(\gamma,\eta\in F\), are uniquely labelled by the
pair \((\gamma,\eta)\).  One can therefore choose the values of a compactly
supported twisted test function so that all cocycle phases cancel on the
\(F\times F\) block.

On the normalized vector \(|F|^{-1/p}\chi_F\in \ell^p(\G_u)\), this test
function has operator norm at least \(|F|\).  But its weighted \(I^p\)-norm is
only of order \(|F|^{1/p}\) times a polynomial in the radius.  Twisted \(RD_p\)
therefore forbids super-polynomial growth whenever \(p>1\).

\section*{Proof}

For \(p=1\), ordinary \(RD_1\) is automatic for every etale groupoid, since the
regular representation norm is bounded by the \(I\)-norm, i.e. by
\(\|\cdot\|_{1,0}\).  Assume henceforth \(1<p<\infty\), and let \(q\) be the
conjugate exponent.

Suppose, toward a contradiction, that \(\G\) has \(\sigma\)-twisted \(RD_p\)
with constants \(A>0\) and \(k\in\mathbb N_0\), but does not have polynomial
growth with respect to \(l\).  Then, for arbitrarily large choices of constants,
there are a unit \(u\), a radius \(R\ge 1\), and a finite set
\[
F\subset \{\gamma\in \G_u:l(\gamma)\le R\}
\]
such that
\[
|F|^{1/q}>A(1+3R)^k. \tag{1}
\]
If the ball is infinite, choose a finite subset with this cardinality.  Since
\(\G\) is principal, the range map is injective on each source fiber: if
\(\gamma,\eta\in\G_u\) and \(r(\gamma)=r(\eta)\), then
\(\gamma^{-1}\eta\) is isotropy at \(u\), hence \(\gamma=\eta\).

Put \(Z=FF^{-1}\).  For each \(g\in Z\) there is a unique pair
\((\gamma_g,\eta_g)\in F\times F\) such that \(g=\gamma_g\eta_g^{-1}\).  As in
Weygandt's finite-ball lemma, choose pairwise small precompact open bisection
neighborhoods \(U_g\) of \(g\), with the following two properties:
\[
l(h)\le 3R\quad(h\in U_g),
\]
and every source fiber and every range fiber meets \(\bigcup_{g\in Z}U_g\) in
at most \(|F|\) points.  The latter follows by first choosing bisection
neighborhoods of the elements of \(F\) with pairwise disjoint range sets; then a
point in a source fiber can lie over at most one fixed second coordinate
\(\eta\in F\), and at most \(|F|\) choices of the first coordinate
\(\gamma\in F\).

Choose functions \(\phi_g\in C_c(U_g)\) with \(|\phi_g|\le 1\) and
\(\phi_g(g)=1\).  Define
\[
f=\sum_{g\in Z}\overline{\sigma(g,\eta_g)}\,\phi_g\in C_c(\G,\sigma).
\]
For every unit \(v\), the preceding fiber-counting estimate gives
\[
\left(\sum_{h\in\G_v}|f(h)|^p(1+l(h))^{pk}\right)^{1/p}
\le |F|^{1/p}(1+3R)^k,
\]
and the same estimate on range fibers.  Hence
\[
\|f\|_{p,k}\le |F|^{1/p}(1+3R)^k. \tag{2}
\]

Let \(\xi=|F|^{-1/p}\chi_F\in \ell^p(\G_u)\).  Then \(\|\xi\|_p=1\).  For
\(\gamma\in F\),
\[
\begin{aligned}
(\lambda_u^\sigma(f)\xi)(\gamma)
&=|F|^{-1/p}\sum_{\eta\in F}
f(\gamma\eta^{-1})\sigma(\gamma\eta^{-1},\eta)\\
&=|F|^{-1/p}\sum_{\eta\in F}1
=|F|^{1-1/p}.
\end{aligned}
\]
Therefore
\[
\|\lambda_u^\sigma(f)\xi\|_p
\ge \left(|F|\cdot |F|^{p-1}\right)^{1/p}=|F|,
\]
so \(\|f\|_{F_\lambda^p(\G,\sigma)}\ge |F|\).  Twisted \(RD_p\), (2), and
(1) now give the contradiction
\[
|F|\le A\|f\|_{p,k}\le A|F|^{1/p}(1+3R)^k<|F|.
\]

Thus a principal \(\G\) has polynomial growth with respect to \(l\).

For the topologically principal, \(\sigma\)-compact, proper-length case, use
Weygandt's local-slice argument in place of principality.  If polynomial growth
fails, properness and \(\sigma\)-compactness allow one to choose a large ball
whose cardinality is locally constant near a unit with trivial isotropy.  Taking
that unit as \(u\), the range map is injective on the finite ball in \(\G_u\),
so the same \(F\times F\) construction above contradicts twisted \(RD_p\).  This
is exactly Weygandt's proof of Theorem 3.3 with the \(\ell^2\)-normalized vector
replaced by \(|F|^{-1/p}\chi_F\).

Austad--Ortega--Palmstrom prove that polynomial growth implies ordinary
\(RD_p\) for every \(p\in[1,\infty)\).  Hence \(\G\) has ordinary \(RD_p\), as
claimed.
\(\square\)

\section*{Verification and limitations}

The proof is a direct \(L^p\)-adaptation of Weygandt's finite-ball obstruction.
The only new bookkeeping is the normalization \(|F|^{-1/p}\chi_F\), which keeps
the lower operator bound equal to \(|F|\) and changes the upper weighted norm to
\(|F|^{1/p}\) times a polynomial factor.

This is only a partial answer to the source question.  It does not settle
arbitrary etale groupoids.  In fact, the arbitrary one-unit groupoid case is
already Chatterji's 2006 open question: can a finitely generated group fail
ordinary RD while having \(\sigma\)-twisted RD for some multiplier
\(\sigma\)?  No answer to that group question was found in the bounded
literature search, so this packet deliberately stops at the
topologically-principal families where Weygandt's injective-range finite-ball
obstruction applies.

\section*{References}

\begin{itemize}
\item A. Austad, E. Ortega, M. Palmstrom, \emph{Polynomial growth and property
\(RD_p\) for etale groupoids with applications to \(K\)-theory},
arXiv:2304.14458.
\item A. Weygandt, \emph{Rapid Decay for Principal Etale Groupoids},
arXiv:2304.12262.
\item V. Mathai, \emph{Heat kernels and the range of the trace on completions
of twisted group algebras}, with an appendix by I. Chatterji,
arXiv:math/0606790.
\end{itemize}

\end{document}
