\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\title{Literature Status: Absolute Examples With No Uncountable Equilateral Set}
\author{Run \texttt{fa\_banach\_001}}
\date{2026-06-14}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_already\_answered}.  This is a literature-status packet,
not an original proof from the run.

\paragraph{Source question.}
Koszmider's 2015 paper \emph{Uncountable equilateral sets in Banach spaces of
the form $C(K)$}, arXiv:1503.06356, constructs consistent nonseparable
$C(K)$ examples with no uncountable equilateral set.  In the abstract and
introduction it records the remaining absolute-example problem: whether there
is a ZFC example of a nonseparable Banach space with no uncountable
equilateral set.  The same discussion also mentions sharper variants involving
$C(K)$ spaces and equivalent renormings.

\paragraph{Supporting answer.}
Koszmider's later paper \emph{Banach spaces in which large subsets of spheres
concentrate}, arXiv:2104.05335, proves in ZFC that there is a strictly convex
Banach space of density continuum such that every uncountable subset of its
unit sphere has an uncountable subset with all mutual distances below
$1-\varepsilon$ for some $\varepsilon>0$.  The paper then invokes the standard
Terenzi reduction from arbitrary equilateral sets to unit-sphere
$1$-equilateral sets and states the consequence as Theorem 2: there is a
strictly convex Banach space of density continuum which does not admit an
uncountable equilateral set.

\paragraph{Identification.}
This directly supplies the absolute nonseparable Banach-space example asked
for in the 2015 discussion.  The supporting paper explicitly compares this
ZFC result with the earlier consistent $C(K)$ examples from arXiv:1503.06356.

\paragraph{Scope limitations.}
This packet does not claim that the sharper absolute $C(K)$ version is solved.
It also does not answer the separate question whether there are consistent
examples whose every equivalent renorming has no uncountable equilateral set.

\begin{thebibliography}{9}
\bibitem{Koszmider2015}
P. Koszmider,
\emph{Uncountable equilateral sets in Banach spaces of the form $C(K)$},
arXiv:1503.06356.

\bibitem{Koszmider2021}
P. Koszmider,
\emph{Banach spaces in which large subsets of spheres concentrate},
arXiv:2104.05335.
\end{thebibliography}

\end{document}
