\documentclass[11pt]{amsart}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\Lip}{\operatorname{Lip}}
\newcommand{\ellinf}{\ell_\infty}
\newcommand{\elltwo}{\ell_2}

\newtheorem*{theorem*}{Literature-implied negative answer}

\begin{document}

\title{No Uniform Finite Interpolation Constant for All Banach Pairs}
\author{Run fa\_banach\_001}
\date{2026-06-28}
\maketitle

\noindent
\textbf{Status.} \texttt{literature\_implied\_answer (negative answer)}.
This note records that a standard later Lipschitz-extension bound negatively
answers the finite interpolation question asked by van Neerven--Veraar.
It is not a new counterexample from the run.

\section*{Source question}

Van Neerven and Veraar's paper
\emph{On the action of Lipschitz functions on vector-valued random sums},
arXiv:math/0504452, asks whether for every pair of Banach spaces \(X,Y\)
there is a constant \(c(X,Y)\), independent of \(n\), such that for all
distinct \(x_1,\ldots,x_n\in X\) and all \(y_1,\ldots,y_n\in Y\), there is a
Lipschitz map \(f:X\to Y\) satisfying \(f(x_j)=y_j\) and
\[
  \|f\|_{\rm Lip}\le c(X,Y)
  \max_{\substack{1\le j,k\le n\\j\ne k}}
  \frac{\|y_j-y_k\|}{\|x_j-x_k\|}.
\]
They emphasize that the important point is that \(c(X,Y)\) should not depend
on \(n\), while Johnson--Lindenstrauss--Schechtman give logarithmic constants
for each fixed \(n\).

\section*{Supporting theorem}

For metric spaces \(M,Z\) and \(S\subset M\), let \(e(M,S,Z)\) denote the
least extension constant for Lipschitz maps \(S\to Z\), and let \(e_n(M,Z)\)
be the supremum of \(e(M,S,Z)\) over all \(S\subset M\) with \(|S|\le n\).

Naor--Rabani, \emph{On Lipschitz extension from finite subsets},
arXiv:1506.04398, Section 1.4, equation (1.17), record the
Johnson--Lindenstrauss bounds
\[
  \frac{\sqrt{\log n}}{\sqrt{\log\log n}}
  \lesssim e_n(\ell_\infty,\ell_2)
  \lesssim \sqrt{\log n}.
\]
In particular \(e_n(\ell_\infty,\ell_2)\to\infty\).

\begin{theorem*}
The van Neerven--Veraar interpolation question has a negative answer. Already
the fixed pair \(X=\ell_\infty\) and \(Y=\ell_2\) admits no constant
\(c(X,Y)\) independent of \(n\).
\end{theorem*}

\begin{proof}
Assume that such a constant \(c(\ell_\infty,\ell_2)\) existed. Let
\(S=\{x_1,\ldots,x_m\}\subset \ell_\infty\), with \(m\le n\), and let
\(g:S\to\ell_2\) be any Lipschitz map, writing \(y_j=g(x_j)\). The source
question's asserted interpolation property would give an extension
\(f:\ell_\infty\to\ell_2\) with
\[
  \|f\|_{\rm Lip}\le c(\ell_\infty,\ell_2)\|g\|_{\rm Lip}.
\]
Thus \(e(\ell_\infty,S,\ell_2)\le c(\ell_\infty,\ell_2)\) for every finite
\(S\), and hence
\[
  e_n(\ell_\infty,\ell_2)\le c(\ell_\infty,\ell_2)
  \qquad \text{for all }n.
\]
This contradicts the Johnson--Lindenstrauss lower bound quoted by
Naor--Rabani, which implies
\[
  e_n(\ell_\infty,\ell_2)\gtrsim
  \frac{\sqrt{\log n}}{\sqrt{\log\log n}}\to\infty.
\]
Therefore no such pairwise constant exists.
\end{proof}

\section*{Scope and provenance}

This is a full negative answer to the all-pairs question as stated, by the
single pair \((\ell_\infty,\ell_2)\). The supporting paper does not explicitly
identify arXiv:math/0504452 as the question being answered; the connection is
an agent-identified implication through the standard extension constant
\(e_n(X,Y)\).

The run indexes were searched for arXiv:0504452, the source title,
\(c(X,Y)\), ``distinct elements \(x_1\)'', ``Lipschitz extension'',
\(e_n(\ell_\infty,\ell_2)\), Johnson--Lindenstrauss, and
\emph{On Lipschitz extension from finite subsets}. No exact prior packet for
this source problem was found. Existing nearby packets for arXiv:1506.04398
concern different later growth-rate questions.

\begin{thebibliography}{9}

\bibitem{NV}
J. van Neerven and M. Veraar,
\emph{On the action of Lipschitz functions on vector-valued random sums},
arXiv:math/0504452.

\bibitem{JL}
W. B. Johnson and J. Lindenstrauss,
\emph{Extensions of Lipschitz mappings into a Hilbert space},
in \emph{Conference in modern analysis and probability}, Contemp. Math. 26,
Amer. Math. Soc., 1984, 189--206.

\bibitem{JLS}
W. B. Johnson, J. Lindenstrauss, and G. Schechtman,
\emph{Extensions of Lipschitz maps into Banach spaces},
Israel J. Math. 54 (1986), 129--138.

\bibitem{NR}
A. Naor and Y. Rabani,
\emph{On Lipschitz extension from finite subsets},
Israel J. Math. 219 (2017), 115--161; arXiv:1506.04398.

\end{thebibliography}

\end{document}
