\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\newcommand{\ellone}{\ell^1(\mathbb N)}

\title{Literature-Implied Answer to Morillon's Asymptotically Isometric \(\ell^1\) Question}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_06}}
\date{2026-06-29}

\begin{document}
\sloppy
\maketitle

\section*{Status}

\textbf{Literature-implied answer, ZFC variant of Question 3.}
This note records that a theorem of Pfitzner answers, in ZFC, the third question in Marianne Morillon's \emph{A new proof of James' sup theorem}, arXiv:math/0505176.

\section*{Source Question}

Morillon asks in the subsection ``Questions'', Question 3, PDF page 4, whether the Valdivia/Bourgain--Diestel/Bourgain--Fremlin--Talagrand weak* convex block compactness theorem remains true, in \(\mathbf{ZF}\) or \(\mathbf{ZFC}\), when the hypothesis ``no isomorphic copy of \(\ellone\)'' is weakened to ``no asymptotically isometric copy of \(\ellone\)''.

\section*{Supporting Literature}

Jimenez-Sevilla and Moreno, \emph{A note on James' theorem for weak compactness}, arXiv:1508.00496, state in the final remarks, item (iii), PDF page 16:

\begin{quote}
Pfitzner proved that if \(E\) does not contain asymptotically isometric copies of \(\ell^1\), then \((B_{E^*},\omega^*)\) is convex block compact.
\end{quote}

They cite H. Pfitzner, \emph{Boundaries for Banach spaces determine weak compactness}, Invent. Math. 182 (2010), 585--604, page 601, Proposition 11.

\section*{Identification}

Morillon's requested replacement is exactly:
\[
\begin{gathered}
  E \text{ does not contain asymptotically isometric copies of } \ellone \\
  \Longrightarrow \\
  (B_{E^*},w^*) \text{ is convex block compact}.
\end{gathered}
\]
The Pfitzner proposition, as recorded in arXiv:1508.00496, proves precisely this implication in the usual ZFC setting.  Therefore the ZFC version of Morillon's Question 3 has a positive answer.

\section*{Scope Limitations}

This is not a new proof packet.  It is a provenance packet identifying a later theorem that answers the extracted question after matching terminology.

The fully choiceless ZF version is not settled here.  Morillon's Question 2, asking whether weak* block compactness can differ from weak* convex block compactness, also remains open here; arXiv:1508.00496 explicitly notes that this equivalence problem is still open in general.

\section*{Search Notes}

The cheap run indexes had no prior packet for arXiv:math/0505176.  Exact web searches on 2026-06-29 for the weak-block/convex-block and asymptotically-isometric \(\ell^1\) phrases did not surface a direct answer to Morillon's paper, but local source search found arXiv:1508.00496, whose final remarks identify Pfitzner's Proposition 11 as the exact ZFC strengthening.

\section*{References}

\begin{itemize}
\item M. Morillon, \emph{A new proof of James' sup theorem}, arXiv:math/0505176.
\item M. Jimenez-Sevilla and J. P. Moreno, \emph{A note on James' theorem for weak compactness}, arXiv:1508.00496.
\item H. Pfitzner, \emph{Boundaries for Banach spaces determine weak compactness}, Invent. Math. 182 (2010), 585--604.
\end{itemize}

\end{document}
