\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Status Note for arXiv:1305.6288}
\author{Run \texttt{fa\_banach\_001}}
\date{July 18, 2026}

\begin{document}
\maketitle

\noindent\textbf{Status.}
\texttt{literature\_implied\_answer (partial subcase)}.

\section*{Source Question}

The source paper is Tomasz Kobos, \emph{Equilateral dimension of some classes
of normed spaces}, arXiv:1305.6288v2.  In the concluding remarks, after the
codimension-one result for subspaces of $\ell_\infty^n$, Kobos asks:
\[
\text{Prove that for any }(n-2)\text{-dimensional subspace }X
\text{ of }\ell_\infty^n\text{ we have }e(X)\ge n-1.
\]
Here $e(X)$ denotes the maximum cardinality of an equilateral subset of $X$.

\section*{Supporting Literature}

The supporting paper is Nora Frankl, \emph{Large Equilateral Sets in Subspaces
of $\ell_\infty^n$ of Small Codimension}, Discrete Comput. Geom. 67 (2022),
882--893, DOI
\href{https://doi.org/10.1007/s00454-020-00272-2}{10.1007/s00454-020-00272-2}.

Frankl explicitly identifies Kobos' problem in the introduction and states that
Theorem 1.2 solves it in large ambient dimension.  The relevant theorem says
that if $X$ is an $(n-k)$-dimensional subspace of $\ell_\infty^n$, then, among
other lower bounds,
\[
e(X)\ge
1+\frac{1}{2^{k-1}}\sum_{r=1}^{\ell}\binom{n-k\ell}{r}
\qquad
\left(1\le \ell\le \frac{n}{k+1}\right).
\]
Taking $k=2$ and $\ell=2$ gives
\[
e(X)\ge 1+\frac12\left[\binom{n-4}{1}+\binom{n-4}{2}\right].
\]
For every $n\ge 9$ this lower bound is at least $n-1$.  Thus Frankl's theorem
implies Kobos' desired inequality for codimension-two subspaces of
$\ell_\infty^n$ whenever the ambient dimension satisfies $n\ge 9$.

\section*{Scope}

This packet records a literature-implied partial answer, not a new proof from
the run.  The implication is direct but requires matching notation: Frankl's
ambient dimension $n$ is the same ambient dimension as in Kobos' final problem,
and $k=2$ is the codimension.

The source problem is not fully closed by this packet.  The cases $n\le 6$
follow from the known validity of Petty's conjecture in dimensions at most
$4$, since then $\dim X=n-2\le 4$.  Frankl covers $n\ge 9$.  The ambient
dimensions $n=7$ and $n=8$ remain outside this identification.

\section*{Search Evidence}

The run indexes had no prior packet for arXiv:1305.6288.  Nearby equilateral
entries concerned infinite equilateral sets, nonseparable examples, or other
finite-dimensional questions.  Web and local searches for the codimension-two
subspace problem found Frankl's later open-access paper, whose introduction
explicitly cites Kobos and says the theorem solves the problem for $n\ge 9$.

\begin{thebibliography}{9}

\bibitem{Kobos}
T. Kobos,
\emph{Equilateral dimension of some classes of normed spaces},
Numer. Funct. Anal. Optim. 35 (2014), 1340--1358.
arXiv:1305.6288.

\bibitem{Frankl}
N. Frankl,
\emph{Large Equilateral Sets in Subspaces of $\ell_\infty^n$ of Small
Codimension},
Discrete Comput. Geom. 67 (2022), 882--893.
DOI: 10.1007/s00454-020-00272-2.

\end{thebibliography}

\end{document}

