\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\newcommand{\covN}{\operatorname{cov}(\mathcal N)}
\newcommand{\nonM}{\operatorname{non}(\mathcal M)}
\newcommand{\bfrak}{\mathfrak b}
\newcommand{\yfrak}{\mathfrak y}
\newcommand{\spanop}{\operatorname{span}}

\title{Literature Status: The \(\covN\) Lower Bound for Normed Barrelled Spaces}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 16, 2026}

\begin{document}
\sloppy
\maketitle

\section*{Status}

This is a \textbf{literature\_already\_answered} packet.  It records that a
later note explicitly answers Question 4.13 from arXiv:2410.13970.  It is not
a new proof packet.

\section*{Source Question}

The source paper is:

\begin{quote}
Will Brian and Christopher Stuart,
\emph{Small-dimensional normed barrelled spaces}, arXiv:2410.13970.
\end{quote}

In Question 4.13, the authors ask:

\begin{quote}
Does every barrelled subspace of an infinite-dimensional Banach space have
dimension \(\geq \covN\)?  In particular, is \(\covN \leq \yfrak\)?
\end{quote}

Here \(\covN\) is the covering number of the Lebesgue null ideal, and
\(\yfrak\) is the least algebraic dimension of an infinite-dimensional normed
barrelled space.

\section*{Supporting Answer}

The supporting paper is:

\begin{quote}
Damian Sobota,
\emph{A small remark on small-dimensional normed barrelled spaces},
arXiv:2511.13355.
\end{quote}

The note states Question 4.13 of arXiv:2410.13970 explicitly and says that its
aim is to answer it affirmatively.  Its main theorem, Theorem
\texttt{thm:main}, proves that whenever \(A\) is a subset of an
infinite-dimensional Banach space \(E\) and \(\spanop(A)\) is barrelled, then
\[
  |A| \geq \covN.
\]
The proof combines the Brian--Stuart method with Dvoretzky's theorem, via the
intermediate property \((\dagger')\), which Sobota proves is satisfied by every
infinite-dimensional Banach space.

\section*{Identification}

Corollary \texttt{cor:covN} of arXiv:2511.13355 gives the source question in
exact form:

\[
  \text{every infinite-dimensional normed barrelled space has dimension at
  least }\covN.
\]

Corollary \texttt{cor:y\_covN} then records the resulting estimate
\[
  \max(\bfrak,\covN) \leq \yfrak \leq \nonM.
\]
Thus arXiv:2511.13355 gives a positive answer to Question 4.13 of
arXiv:2410.13970.

\section*{Scope Limitations}

This packet clears only the \(\covN\)-lower-bound question.  It does not settle
the later residual question asked at the end of arXiv:2511.13355, namely
whether \(\yfrak=\nonM\) holds in ZFC.

\section*{Search Evidence}

Local cheap indexes for arXiv:2410.13970, ``small-dimensional normed
barrelled'', ``barrelled subspace'', and ``\(\covN\)'' had no prior exact
packet at reservation time.  The run target pool listed arXiv:2511.13355,
which directly cites Brian--Stuart's Question 4.13 and answers it by Theorem
\texttt{thm:main} and Corollary \texttt{cor:covN}.

\begin{thebibliography}{9}

\bibitem{BS2410}
W. Brian and C. Stuart,
\emph{Small-dimensional normed barrelled spaces}, arXiv:2410.13970.

\bibitem{Sobota2511}
D. Sobota,
\emph{A small remark on small-dimensional normed barrelled spaces},
arXiv:2511.13355.

\end{thebibliography}

\end{document}
