\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: scalar \texorpdfstring{$U(d,a)$}{U(d,a)} edge case}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 10 June 2026

\noindent Status: Manually checked.

\noindent Verdict: Rejected as a solution to the intended problem.

\section*{Human Comments}

The calculation in \texttt{solution\_packet.pdf} is a valid computation in the
one-dimensional real Banach space \(X=\mathbb R\). However, this is only a
trivial scalar edge case. The obstruction comes from the fact that the unit
sphere of \(\mathbb R\) is just \(\{-1,1\}\), so for every \(0<d<2\) the
infimum defining \(U(d,a)\) only sees the antipodal pair.

This is certainly not what was intended by the authors. The question was
meant to probe genuinely small-distance geometry in Banach spaces with
uniform property (S), not the degenerate behaviour of a two-point unit sphere.
For that reason, the proposed solution should be rejected as an answer to the
intended problem.

For the result to be relevant as a substantive contribution, one would need
to address a nontrivial setting, for instance spaces whose unit sphere has
admissible pairs at every small distance, or infinite-dimensional spaces with
uniform property (S).

\section*{Short Version}

This is a trivial one-dimensional obstruction and not the intended question.
The packet should not be counted as resolving Open Problem (3).

\section*{Review Outcome}

Reject this candidate as a solution to the intended problem. At most, archive
it as a warning that automatic extraction can turn an intended geometric
question into a degenerate scalar edge case.

\end{document}
