\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: finite-dimensional misreading}

\noindent Packet identifier:
\texttt{1705.06797\_l2\_superreflexive\_finite\_dim\_literal\_counterexample}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 13 June 2026

\noindent Status: Manually checked.

\noindent Verdict: Incorrect as a solution to the intended problem.  This is a miss.

\section*{Human Comments}

The proposed solution in \texttt{solution\_packet.pdf} should not be accepted as
a solution of Problem 5.1.  It answers only a finite-dimensional loophole by
taking the one-dimensional Banach space \(\mathbb R\).  That is not the problem
the authors were asking.

The question was clearly intended for infinite-dimensional Banach spaces.  The
text immediately following the problem says that a counterexample would have
to be a super-reflexive space without an unconditional basic sequence, and
points to the Ferenczi-space context.  This makes clear that the
finite-dimensional case is not the intended mathematical target.

For that reason, this candidate has to be discarded.  It does not answer the
intended infinite-dimensional super-reflexive question and should be classified
as an incorrect hit by the pipeline.

\section*{Short Version}

This is a miss.  The candidate exploits a finite-dimensional reading, whereas
the intended question concerns infinite-dimensional Banach spaces.

\section*{Review Outcome}

Discard this as a proposed solution of Problem 5.1.  At most, archive it as a
warning that automatic extraction must retain the surrounding context of an
open problem.

\end{document}
