\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\title{Literature Status: Helson and Embedding Problems for Dirichlet Series}
\author{Run \texttt{fa\_banach\_001}, lane 8}
\date{2026-07-19}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature\_already\_answered} for Helson's problem, and
\textbf{literature\_already\_answered (partial subrange)} for the embedding
problem. This packet records already known answers, not new proofs from the
run.

\section*{Source Question}

The source paper is Eero Saksman and Kristian Seip,
\emph{Some open questions in analysis for Dirichlet series}, arXiv:1601.01616.
In Section 3, Problem \texttt{helson} asks:
\[
  \left\|\sum_{n=1}^N n^{-s}\right\|_{\mathcal H^1}
  = o(\sqrt N)
  \qquad (N\to\infty)?
\]

The surrounding text explains the probabilistic interpretation: by viewing
\(p_j^{-s}\) as independent Steinhaus variables, this is Helson's conjecture for
sums of a Steinhaus random multiplicative function.

The same paper also asks the embedding problem in Section 2, Problem
\texttt{embedding}: whether the local \(L^p\) integral of a Dirichlet
polynomial on a fixed segment of the line \(\operatorname{Re}s=1/2\) is bounded
by a universal constant times its \(\mathcal H^p\)-norm to the \(p\)-th power.

\section*{Supporting Answer}

The supporting paper is Adam J. Harper,
\emph{Moments of random multiplicative functions, I: Low moments, better than
squareroot cancellation, and critical multiplicative chaos}, arXiv:1703.06654,
published in \emph{Forum of Mathematics, Pi} 8 (2020), e1.

Harper's Theorem 1 states that for a Steinhaus random multiplicative function
\(f\), uniformly for \(0\le q\le 1\),
\[
  \mathbb E\left|\sum_{n\le x} f(n)\right|^{2q}
  \asymp
  \left(
    \frac{x}{1+(1-q)\sqrt{\log\log x}}
  \right)^q .
\]
Taking \(q=1/2\) gives
\[
  \mathbb E\left|\sum_{n\le x} f(n)\right|
  \asymp
  \frac{\sqrt x}{(\log\log x)^{1/4}}
  = o(\sqrt x).
\]
Harper explicitly notes after Theorem 2 that this proves Helson's conjecture.
Through the Bohr correspondence used in the source paper, this is exactly the
affirmative answer to Problem \texttt{helson}.

\section*{Secondary Embedding Consequence}

Harper also explicitly states that Theorem 1 gives a negative answer to the
embedding problem for all exponents \(0<2q<2\), i.e. \(0<p<2\). The
counterexample sequence is the family
\[
  P_x(s)=\sum_{n\le x} n^{-s}.
\]
For fixed \(0<q<1\), Riemann--Stieltjes integration gives
\[
  \int_0^1 \left|\sum_{n\le x} n^{-1/2-it}\right|^{2q}\,dt
  \asymp x^q,
\]
whereas Theorem 1 gives
\[
  \|P_x\|_{\mathcal H^{2q}}^{2q}
  =
  \mathbb E\left|\sum_{n\le x} f(n)\right|^{2q}
  =
  o(x^q).
\]
Thus no universal embedding constant can exist for \(0<p<2\).

\section*{Scope}

This gives a full literature answer to Problem \texttt{helson}. It gives a
negative literature answer to Problem \texttt{embedding} only in the subrange
\(0<p<2\). The source paper already records the positive \(p=2\) and even
integer cases; this packet does not classify the remaining exponents or the
other survey problems.

\section*{Evidence}

The source PDF is included as \texttt{source\_paper.pdf}. The supporting Harper
PDF is included as \texttt{supporting\_paper\_1703.06654.pdf}. The identification
was checked against the source LaTeX lines 174--181 and 265--267, and
Harper's Theorem 1 statement plus following explanatory paragraphs at lines
148--162 of the parsed source.

\begin{thebibliography}{9}

\bibitem{SaksmanSeip}
E. Saksman and K. Seip,
\emph{Some open questions in analysis for Dirichlet series},
arXiv:1601.01616, 2016.

\bibitem{Harper}
A. J. Harper,
\emph{Moments of random multiplicative functions, I: Low moments, better than
squareroot cancellation, and critical multiplicative chaos},
Forum of Mathematics, Pi 8 (2020), e1; arXiv:1703.06654.

\end{thebibliography}

\end{document}
