\documentclass[10pt]{article}
\usepackage[margin=0.76in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue!55!black,citecolor=blue!55!black]{hyperref}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.32em}

\begin{document}

\begin{center}
{\Large Literature-Already-Answered Status Note}\\[0.3em]
{\large Bornological differentiability and weakly compact operators}\\[0.4em]
\textbf{Status:} weak-Hadamard case and property-(S) framework answered in later literature
\end{center}

\section*{Source question}

Bachir, Flores, and Tapia-Garc\'ia ask in Open Question 5.7 of
\emph{Compact and Limited Operators} (arXiv:1910.07362, PDF page 13) whether
there is a differentiability characterization for the weak-Hadamard bornology
and, more generally, for a prescribed bornology $\beta$ on a Banach space
\cite{source}. In their notation, they seek a class $\mathcal F_\beta$ such
that
\[
 T(B_Y)\in\beta
 \quad\Longleftrightarrow\quad
 f\circ T\text{ is Fr\'echet differentiable at }y
\]
whenever $f\in\mathcal F_\beta$ is G\^ateaux differentiable at $Ty$.

\section*{Explicit later answer}

Bachir and Tapia-Garc\'ia explicitly state on PDF page 2 of
\emph{Non-linear operators and differentiability of Lipschitz functions}
(arXiv:2110.00099) that their work answers Question 5.7 of the source
\cite{answer}. Their Theorem 1.3 (PDF page 3) gives the highlighted missing
case. A bounded linear map $T:Y\to X$ is weakly compact if and only if, for
every Lipschitz $f:X\to\mathbb R$, the composition $f\circ T$ is Fr\'echet
differentiable at $y$ whenever $f$ is weak-Hadamard differentiable at $Ty$.
Thus the desired class is the real-valued Lipschitz functions, with
weak-Hadamard differentiability imposed at the image point.

The same paper also gives the intended abstract framework. Theorem 4.5
(PDF page 11, proof through page 13) treats vector bornologies $\beta_X$ and
$\beta_Y$ when $\beta_X$ has property (S). It characterizes when the
positively homogeneous differential of $T$ maps $\beta_Y$-sets to
$\beta_X$-sets by the composition behavior of all real-valued Lipschitz
functions that are $\beta_X$-differentiable. The paper proves property (S)
for the Hadamard, weak-Hadamard, and limited bornologies, thereby recovering
compact and limited operators and adding weakly compact and completely
continuous operators.

\section*{Classification and scope}

The match is explicit: the supporting authors cite the source as reference
[4], name Question 5.7, and say their paper answers it. The weak-Hadamard case
is completely settled by Theorem 1.3, so it is not a viable target for a new
proof. The abstract theorem is broad but assumes a vector bornology satisfying
property (S). Consequently, it should not be read as an assertion for every
possible bornology with no structural hypothesis; that unrestricted literal
formulation lies outside the theorem.

The status search used the source arXiv id, the exact phrase
``weak-Hadamard differentiability,'' and combinations of ``bornology,''
``operator,'' and ``differentiability.'' It located arXiv:2110.00099, whose
abstract, introduction, Theorem 1.3, and Theorem 4.5 provide the decisive
identification.

\begin{thebibliography}{9}

\bibitem{source}
M. Bachir, G. Flores, and S. Tapia-Garc\'ia,
\emph{Compact and Limited Operators},
Math. Nachr. 294 (2021), 1085--1098,
\href{https://arxiv.org/abs/1910.07362}{arXiv:1910.07362}.

\bibitem{answer}
M. Bachir and S. Tapia-Garc\'ia,
\emph{Non-linear operators and differentiability of Lipschitz functions},
\href{https://arxiv.org/abs/2110.00099}{arXiv:2110.00099}, 2021.

\end{thebibliography}

\end{document}
