\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature-Implied Status Note for arXiv:0802.3520}
\author{run fa\_banach\_001, agent\_lane\_16}
\date{2026-06-28}

\begin{document}
\maketitle

\paragraph{Status.}
\texttt{literature\_implied\_answer} for the two-sided lattice compactness
conjecture in arXiv:0802.3520. The supporting source is a recent preprint, so
human verification is recommended before treating the question as settled.

\paragraph{Source/open-problem metadata.}
Michael Cwikel, ``Complex interpolation of compact operators mapping into
lattice couples,'' arXiv:0802.3520, posted 2008-02-24. In the subsection
``Two sided interpolation of compactness,'' near the end of the paper
(local TeX source lines 1005--1021), Cwikel writes that it was not even known
whether the stronger two-sided endpoint condition
\[
  T:A_j \overset{c}{\longrightarrow} B_j, \qquad j=0,1,
\]
implies
\[
  T:[A_0,A_1]_\theta \overset{c}{\longrightarrow}
  [B_0,B_1]_\theta,\qquad 0<\theta<1.
\]
He conjectures this implication for arbitrary Banach couples
\(\vec A=(A_0,A_1)\) whenever \(\vec B=(B_0,B_1)\) is an arbitrary lattice
couple, with no Fatou-property or \(\sigma\)-order-continuity assumptions.

\paragraph{Supporting-answer metadata.}
Evgeniy Pustylnik, ``A new approach to interpolation of compact linear
operators,'' arXiv:2605.00530, posted 2026-05-01. The paper states that
compactness is interpolated automatically whenever one has standard
interpolation of bounded operators, first for two-sided compactness; one-sided
compactness needs an additional condition. It explicitly includes the complex
interpolation functor \(\mathcal F_{[\theta]}\), \(0<\theta<1\), noting the
estimate \(W(\alpha,\beta)=\alpha^{1-\theta}\beta^\theta\) in the one-sided
case. In the final section, item 1 says that the same proof applies to
two-sided compactness of embedding operators without the one-sided inequality.
Item 2 then passes from embeddings to arbitrary operators by factoring an
operator through its image spaces.

\paragraph{Identification.}
Cwikel's conjecture is a two-sided compactness statement for the complex
interpolation functor, restricted to arbitrary lattice couples on the range
side. Pustylnik's statement is broader: it is formulated for general Banach
couples and interpolation functors satisfying standard bounded-operator
interpolation, with complex interpolation explicitly included. For an
arbitrary operator \(T\) that is compact \(A_j\to B_j\) for both endpoints,
the image-space factorization \(T=JS\) makes \(S:A_j\to Y_j\) bounded and
makes the embeddings \(J:Y_j\hookrightarrow B_j\) compact at both endpoints.
Combining the final-section two-sided embedding remark with this same
factorization gives compactness of \(T:\mathcal F(A_0,A_1)\to
\mathcal F(B_0,B_1)\). Taking \(\mathcal F=[\,\cdot,\cdot\,]_\theta\) yields
the implication conjectured in arXiv:0802.3520, if the supporting preprint is
accepted.

\paragraph{Provenance limitation.}
This is an agent-identified implication rather than an explicit answer
announced by the supporting authors. The checked source text of
arXiv:2605.00530 does not appear to cite arXiv:0802.3520 or Cwikel's
two-sided lattice-couple conjecture. Since arXiv:2605.00530 is a very recent
preprint claiming a broad resolution of a long-standing compactness
interpolation problem, human review should verify the proof and the
embedding-to-operator passage before marking the conjecture definitively
closed.

\paragraph{Search evidence.}
The run indexes were searched for \texttt{0802.3520}, complex interpolation,
compact operators, lattice couples, two-sided compactness, and
arXiv:2605.00530. No prior exact packet for arXiv:0802.3520 was found. A
related existing packet for arXiv:1406.3842 already records that
arXiv:2605.00530 appears to answer the classical one-sided complex
compactness problem; the present packet records the separate implication for
Cwikel's two-sided lattice-couple conjecture.

\begin{thebibliography}{9}
\bibitem{Cwikel2008}
M. Cwikel,
``Complex interpolation of compact operators mapping into lattice couples,''
arXiv:0802.3520, 2008.

\bibitem{Pustylnik2026}
E. Pustylnik,
``A new approach to interpolation of compact linear operators,''
arXiv:2605.00530, 2026.
\end{thebibliography}

\end{document}
