\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}

\newtheorem*{answer}{Answer}
\newcommand{\cB}{\mathcal B}

\title{Property (A) and Property (C) Do Not Imply Semi-Greediness\\
\large A literature identification for arXiv:1803.05052}
\author{Run \texttt{fa\_banach\_001}, lane 13}
\date{July 21, 2026}

\begin{document}
\maketitle

\section*{Source question}

Bern\'a, Dilworth, Kutzarova, Oikhberg, and Wallis ask in Section 6,
Question 3 of \emph{The weighted Property (A) and the greedy algorithm}
(arXiv:1803.05052, PDF p.~19):
\begin{quote}
If a basis has Properties (C) and (A), is it necessarily semi-greedy?
\end{quote}
Here the source works with a semi-normalized Schauder basis.  Property (C)
is the uniform estimate
\[
 \min_{j\in\Lambda}|e_j^*(x)|\,
 \left\|\sum_{j\in\Lambda}\varepsilon_j e_j\right\|
 \le C\|x\|
\]
for every greedy set $\Lambda$ of $x$ and every choice of signs.  Property
(A) is the usual symmetry-for-largest-coefficients condition.

\begin{answer}
No.  There exists a Schauder basis with Properties (A) and (C) that is not
semi-greedy.
\end{answer}

\section*{Decisive later result}

P. M. Bern\'a, \emph{Equivalence between almost-greedy and semi-greedy
bases} (arXiv:1804.05730), proves in Theorem 1.10 that a semi-greedy
Schauder basis is quasi-greedy (and super-democratic).  More precisely, if
$C_s$ is its semi-greedy constant and $K_b$ its basis constant, the theorem
gives a finite quasi-greedy constant, explicitly bounded there by
\[
 K_b\bigl(2+3(K_bC_s)^2\bigr).
\]

On PDF p.~7, immediately before Section 4, the supporting paper explicitly
returns to Question 3 of arXiv:1803.05052.  It cites the example in
Bern\'a--Blasco--Garrig\'os, Subsection 5.5, which has Property (A) and the
inequality defining Property (C), but is not quasi-greedy.  By Theorem 1.10,
that basis cannot be semi-greedy.  Thus the cited example is a counterexample
to the source question.

The logical implication is simply
\[
 \text{semi-greedy Schauder}
 \Longrightarrow \text{quasi-greedy},
 \qquad
 \cB_{\rm ex}\text{ is not quasi-greedy},
\]
while $\cB_{\rm ex}$ has both requested properties.

\section*{Provenance and scope}

This is a literature-already-answered identification, not a new
counterexample.  The question appears in arXiv:1803.05052 (submitted March
2018), and the explicit negative answer appears in arXiv:1804.05730 (April
2018).  The packet is restricted to Question 3.  It makes no claim about the
other four questions in Section 6 of the source.

\section*{References}

\begin{enumerate}[leftmargin=*,label={[\arabic*]}]
\item P. M. Bern\'a, S. J. Dilworth, D. Kutzarova, T. Oikhberg, and
  B. Wallis, \emph{The weighted Property (A) and the greedy algorithm},
  arXiv:1803.05052.
\item P. M. Bern\'a, \emph{Equivalence between almost-greedy and
  semi-greedy bases}, arXiv:1804.05730.
\item P. M. Bern\'a, \`O. Blasco, and G. Garrig\'os,
  \emph{Lebesgue inequalities for the greedy algorithm in general bases},
  Rev. Mat. Complut. 30 (2017), 369--392.
\end{enumerate}

\end{document}

