\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue}
\emergencystretch=1em
\title{Literature-Implied Answer: The Atomic Masa Subcase}
\author{Run \texttt{fa\_banach\_001}, lane 1}
\date{19 July 2026}

\begin{document}
\maketitle

\begin{center}
\textbf{Status: literature-implied answer (partial subcase)}
\end{center}

\section*{Source question}

In Section 4, PDF page 9, of Wassermann's \emph{Tensor Products of Maximal
Abelian Subalgebras of C*-Algebras}~\cite{W}, the author asks whether
\((C\otimes1)^c=C\otimes B(H)\) in
\(B(H)\otimes_{\max}B(H)\) for every masa \(C\subset B(H)\), and whether
\(C_1\otimes C_2\) is maximal abelian there for every pair of masas.  The
paper calls the case
\[
 C_1\cong C_2\cong\ell^\infty(\mathbb N)
\]
particularly intriguing and observes that a positive solution of the
Kadison--Singer problem would imply a positive answer for this product-masa
case by its Corollary 3.

\section*{Identification}

Marcus, Spielman, and Srivastava prove Weaver's \(KS_2\) conjecture and an
Anderson paving formulation, both known to imply a positive solution of the
Kadison--Singer problem~\cite{MSS}; see their abstract and Question 1.1 on PDF
pages 1--2.  Therefore the standard diagonal masa
\(D=\ell^\infty(\mathbb N)\subset B(\ell^2(\mathbb N))\) has the extension
property.

Wassermann's Theorem 2 now applies with \(C=D\), \(A_1=A_2=B(H)\), and the
maximal norm, giving
\[
 (D\otimes1)^c=D\otimes B(H)
 \quad\hbox{in }B(H)\otimes_{\max}B(H).
\]
His Corollary 3, applied to \(C_1=C_2=D\), gives
\[
 D\otimes D\text{ is a masa in }B(H)\otimes_{\max}B(H).
\]
Thus both atomic diagonal subcases have a positive answer.  This is a direct
post-2013 literature implication, not a new mathematical solution, and the
supporting paper does not identify Wassermann's question explicitly.

\section*{Scope and search evidence}

The conclusion does not cover the non-atomic masa
\(L^\infty(0,1)\subset B(L^2(0,1))\), nor arbitrary pairs of masas.  Searches
of the run indexes for arXiv:0711.0131, masa, maximal tensor product, and the
exact relative-commutant formulas found no earlier packet.  A bounded external
search found the source and Kadison--Singer literature but no primary source
settling the remaining diffuse/arbitrary-masa questions.

\begin{thebibliography}{9}
\bibitem{W}
S. Wassermann,
\emph{Tensor Products of Maximal Abelian Subalgebras of C*-Algebras},
Glasgow Math. J. 50 (2008), 209--216; arXiv:0711.0131.

\bibitem{MSS}
A. W. Marcus, D. A. Spielman, and N. Srivastava,
\emph{Interlacing Families II: Mixed Characteristic Polynomials and the
Kadison--Singer Problem},
Ann. of Math. 182 (2015), 327--350; arXiv:1306.3969.
\end{thebibliography}

\end{document}
