\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{enumitem}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  citecolor=blue
}
\emergencystretch=2em

\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\cG}{\mathcal G}
\newcommand{\cF}{\mathcal F}

\title{A Critical-Density Literature Answer for the Scalar Hermite Interpolation Problem}
\author{Run fa\_banach\_001, lane 1}
\date{July 19, 2026}

\begin{document}
\maketitle

\section{Status}

This is a lightweight \emph{literature-implied answer}, not an original
solution.  The source paper is
\[
\text{K. Grochenig and Y. Lyubarskii, \emph{Gabor (Super)Frames with Hermite Functions},
arXiv:0804.4613.}
\]
In Section 4.2, immediately after equation (3.2), the authors write that, for
the scalar \(n\)-th Hermite window, they do not know whether the interpolation
problem
\[
  \sum_{k=0}^n \binom{n}{k}(-\pi \mu)^k
  G_n^{(n-k)}(\overline{\mu})=\delta_{\mu,0},
  \qquad \mu\in\Lambda^\circ,
\]
has a solution \(G_n\in\cF\) when \(s(\Lambda)\ge 1/(n+1)\).  They note that it
is conceivable that the sufficient condition \(s(\Lambda)<1/(n+1)\) is also
necessary.

The supporting paper is M. Faulhuber, I. Shafkulovska, and I. Zlotnikov,
\emph{On the Frame Property of Hermite Functions and Exploration of their Frame
Sets}, J. Fourier Anal. Appl. 31:21 (2025).

\section{Identification}

The source paper recalls the characterization from its earlier Proposition 3.3:
\(\cG(H_n,\Lambda)\) is a scalar Gabor frame for \(L^2(\R)\) if and only if
there is a Bessel dual window \(\gamma_n\) whose Bargmann transform \(G_n\in\cF\)
satisfies the displayed interpolation problem above.  Thus any later theorem
showing that \(\cG(H_n,\Lambda)\) is a frame supplies a solution of equation
(3.2).

Faulhuber--Shafkulovska--Zlotnikov prove, in their Theorem 1.1, that for
\[
  \Lambda_n=(1/\sqrt{n+1})\Z^2
\]
the system \(\cG(h_n,\Lambda_n)\) is a Gabor frame for \(L^2(\R)\) if and only
if \(n\ge4\).  Their normalization uses \(\operatorname{vol}(\Lambda)=ab\) for
\(\Lambda=a\Z\times b\Z\), while the source paper's \(s(\Lambda)\) is the same
covolume.  Therefore
\[
  s(\Lambda_n)=\operatorname{vol}(\Lambda_n)=\frac{1}{n+1}.
\]

Combining these two facts gives the promised critical examples: for every
\(n\ge4\), equation (3.2) has a solution in the Fock space at the critical
density \(s(\Lambda)=1/(n+1)\).  Consequently, the proposed necessity of the
strict inequality \(s(\Lambda)<1/(n+1)\) is false for the scalar Hermite
interpolation problem.

\section{Scope}

This does not classify all lattices with \(s(\Lambda)\ge 1/(n+1)\).  It gives
explicit square-lattice critical examples.  It also does not answer the broader
general \(M^1\) superframe strict-density conjecture stated earlier in the
source paper; that conjecture concerns vector-valued superframes for arbitrary
\(M^1\) windows, whereas the implication recorded here concerns the scalar
Hermite window and the source's interpolation problem (3.2).

The supporting paper is aware that it enlarges the Grochenig--Lyubarskii
``safety region'' and cites the Hermite-frame literature, but it does not state
the source's equation (3.2).  The relation to the interpolation problem is the
agent-identified consequence of the source paper's frame/interpolation
equivalence.

\section{Search Notes}

The run indexes were searched for arXiv:0804.4613, Hermite, superframe,
polyanalytic, and critical-density keywords; no prior packet for this exact
source question was found.  Web searches for Hermite Gabor frame density and
the Grochenig--Lyubarskii conjecture found the 2025 JFAA article, whose
Theorem 1.1 is the decisive supporting theorem.

\section{References}

\begin{itemize}[leftmargin=*]
\item K. Grochenig and Y. Lyubarskii, \emph{Gabor (Super)Frames with Hermite
Functions}, Math. Ann. 345 (2009), 267--286; arXiv:0804.4613.
\item M. Faulhuber, I. Shafkulovska, and I. Zlotnikov, \emph{On the Frame
Property of Hermite Functions and Exploration of their Frame Sets}, J. Fourier
Anal. Appl. 31:21 (2025), DOI: \href{https://doi.org/10.1007/s00041-025-10153-y}{10.1007/s00041-025-10153-y}.
\end{itemize}

\end{document}
