\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Conditional Bases with Property (A)}
\author{Automatic Math Discovery Run \texttt{fa\_banach\_001}}
\date{June 14, 2026}

\begin{document}
\maketitle

\section*{Original Problem}

The source paper is Fernando Albiac, Jos\'e L. Ansorena, and Vladimir
Temlyakov, \emph{Twenty-five years of greedy bases}, arXiv:2405.20939.
In Section 4, ``Isometric almost greediness'', PDF page 11, Problem 6 asks:
\[
\text{Does Property (A) imply unconditionality?}
\]
The same page notes that it was also unknown whether
\(1\)-suppression quasi-greediness implies unconditionality.

\section*{Supporting Answer Source}

The supporting paper is Fernando Albiac, Jos\'e L. Ansorena, Miguel
Berasategui, and Pablo M. Bern\'a, \emph{Conditional bases with Property (A)},
arXiv:2409.04883. Its introduction cites the source paper as AAT2024 and says
that Question G was explicitly raised in AAT2024, Problem 6. On PDF page 4 it
states that the paper answers Question G negatively.

\section*{Answer}

The 2405.20939 question is already answered negatively in the later literature.
Theorem 3.3 of arXiv:2409.04883 constructs Schauder bases with Property (A)
whose unconditionality parameters are unbounded when the chosen symmetric
space properly couples with the weight. Corollary 3.7 then states explicitly
that there exist Banach spaces with a bidemocratic Schauder basis which fails
to be unconditional and yet has Property (A). Hence Property (A) does not imply
unconditionality.

The supporting paper also addresses the adjacent question mentioned after
Problem 6 in the source paper: on PDF page 17 it states that, since a basis
with Property (A) is \(1\)-almost greedy and therefore
\(1\)-suppression quasi-greedy, Theorem 3.3 answers negatively whether
\(1\)-suppression quasi-greediness implies unconditionality. It then gives a
reflexive version with a conditional, bimonotone, isometrically bidemocratic
\(1\)-suppression quasi-greedy basis.

\section*{Verification Notes}

Local source text checks:
\begin{itemize}
\item \texttt{data/parsed/arxiv\_sources/2405.20939/source.tex}, lines
487--493, contains Problem 6 and the nearby \(1\)-suppression quasi-greedy
question.
\item \texttt{data/parsed/arxiv\_sources/2409.04883/source.tex}, lines
202--214, states Question G and says it is raised in AAT2024 Problem 6 and
answered negatively.
\item \texttt{data/parsed/arxiv\_sources/2409.04883/source.tex}, lines
587--599 and 707--715, contain Theorem 3.3 and Corollary 3.7.
\item \texttt{data/parsed/arxiv\_sources/2409.04883/source.tex}, lines
776--787, records the negative answer to the \(1\)-suppression quasi-greedy
variant.
\end{itemize}

\section*{Search Bounds}

Before making this packet, the run registry, solution index, attempt index,
proof-gap index, existing solution folders, and existing attempt folders were
searched for arXiv:2409.04883, the title phrase ``Conditional bases with
Property (A)'', and the Property (A) unconditionality question. No existing run
packet or ledger row was found. Web search on June 14, 2026 found the arXiv
record for arXiv:2409.04883, whose abstract says the paper builds Schauder
bases with Property (A) that fail to be unconditional.

\section*{Limitations}

This is a literature-status packet, not a new proof or counterexample produced
by the run. It records that the extracted open problem from arXiv:2405.20939
was answered by a later paper. It does not claim any resolution of the new
questions raised at the end of arXiv:2409.04883.

\section*{Human Review Recommendation}

Check that AAT2024 in arXiv:2409.04883 is exactly arXiv:2405.20939 and that
the cited Problem 6 is the same Property (A) unconditionality problem recorded
in the source paper. The identification is explicit, so this should be a
straightforward literature-already-answered entry.

\end{document}
