\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\emergencystretch=2em

\title{Literature-Implied Answer: A Limit on Relaxing Weak-Star Compactness}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_15}}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature-implied negative answer to the broad relaxation
of Theorem \texttt{boundary} in arXiv:1302.0160 obtained by deleting the
$w^*$-$\sigma$-compactness hypothesis.

\section*{Source Question}

In arXiv:1302.0160, \emph{Polyhedrality in Pieces}, Fonf, Pallares,
Smith, and Troyanski prove Theorem \texttt{boundary}: if $E\subset X^*$ is
$\sigma$-$w^*$-LRC and $w^*$-$\sigma$-compact and contains a boundary of
$X$, then every $\varepsilon>0$ admits an $\varepsilon$-approximating
equivalent polyhedral norm.  Immediately after the theorem they explain that
the extra $w^*$-$\sigma$-compactness assumption is used to control the
locations of limit points, and that they do not know to what extent it can be
relaxed.

\section*{Supporting Literature}

In arXiv:1804.02899, \emph{Topology, isomorphic smoothness and
polyhedrality in Banach spaces}, Smith recalls the standard necessary
condition that if a Banach space admits a polyhedral norm, then it is Asplund
and $c_0$-saturated; see Theorem \texttt{thm\_nec\_conditions}.  Smith also
records Bible's example
\[
   Z=\ell_1\oplus \ell_1(S_{\ell_\infty}),
\]
which is neither Asplund nor $c_0$-saturated and hence is not
isomorphically polyhedral, but nevertheless admits an equivalent norm with a
relatively $w^*$-discrete boundary.  The same paper states in Example
\texttt{weakstarlrcex} that any $w^*$-relatively discrete subset of a dual
Banach space is $w^*$-LRC.

\section*{Identification}

Bible's boundary for the renormed space $Z$ is relatively $w^*$-discrete, so
it is $w^*$-LRC and therefore $\sigma$-$w^*$-LRC using just one piece.  It is
also a boundary for the chosen equivalent norm on $Z$.

If Theorem \texttt{boundary} from arXiv:1302.0160 remained true after simply
removing $w^*$-$\sigma$-compactness, then applying that hypothetical theorem
to this renormed $Z$ would produce an equivalent polyhedral norm on $Z$.
This contradicts Smith's necessary conditions, since $Z$ is not Asplund and
is not $c_0$-saturated.  Thus the $w^*$-$\sigma$-compactness hypothesis
cannot be dropped outright.

\section*{Scope}

This is not a new proof of an original counterexample; it is an
agent-identified implication from Smith's published discussion of Bible's
example.  The packet only answers the strongest naive relaxation
\[
  \sigma\text{-}w^*\text{-LRC boundary}
  \;\nRightarrow\;
  \text{isomorphically polyhedral}.
\]
It does not settle finer intermediate relaxations of the source theorem that
still impose some replacement for limit-point control, such as countable
decompositions whose $w^*$-closures remain inside the boundary set.

\section*{Search Evidence}

The cheap run indexes contained one previous attempt for arXiv:1302.0160 and
one related literature-implied packet for arXiv:2502.17001.  The related
packet already identified the same Bible/Smith example as a negative answer
to the later weak-star $\sigma$-discrete boundary implication.  Direct index
searches for arXiv:1302.0160, \emph{Polyhedrality in Pieces},
$\sigma$-$w^*$-LRC, and $w^*$-$\sigma$-compactness showed no prior durable
packet for this exact 1302.0160 relaxation target.

\section*{References}

\begin{thebibliography}{9}
\bibitem{fpst}
V. P. Fonf, A. J. Pallares, R. J. Smith, and S. Troyanski,
\emph{Polyhedrality in Pieces}, arXiv:1302.0160.

\bibitem{smith}
R. J. Smith,
\emph{Topology, isomorphic smoothness and polyhedrality in Banach spaces},
arXiv:1804.02899.

\bibitem{castillo-salguero}
J. M. F. Castillo and R. Salguero Alarcon,
\emph{Polyhedrality for twisted sums with $C(\omega^\alpha)$},
arXiv:2502.17001.
\end{thebibliography}

\end{document}
