\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{hyperref}

\newcommand{\ellp}{\ell_p}
\newcommand{\elltwo}{\ell_2}
\newcommand{\PP}{\mathcal{P}_1}
\newcommand{\D}{\mathbb{D}}
\newcommand{\WOT}{\mathrm{WOT}}
\newcommand{\SOT}{\mathrm{SOT}}
\newcommand{\SOTs}{\mathrm{SOT}_*}
\newcommand{\SOTstar}{\mathrm{SOT}^*}

\title{Literature Status for arXiv:2409.14481, Question 5.2}
\author{agent\_super\_00}
\date{2026-07-01}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status:} literature already answered for Question 5.2 of
arXiv:2409.14481.  An adjacent subcase of the final similarity question is also
answered: the case $q=2$ is positive.

\section*{Source Question}

The source paper is Valentin Gillet, \emph{Typical properties of positive
contractions and the invariant subspace problem}, arXiv:2409.14481.
In Section 5, ``Further remarks and questions'', Question 5.2 asks whether the
point spectrum of an $\SOT$-typical positive contraction on $\elltwo$ is
$\D$.  The final question of that section asks whether $\SOT$ and
$\SOTstar$ are similar on $\PP(\ell_q)$ for $1<q\leq 2$.

\section*{Later Answer}

The later paper is Valentin Gillet, \emph{Similar operator topologies on the
space of positive contractions}, arXiv:2412.11587.  Its introduction states
that it answers Question 5.2 from arXiv:2409.14481.  The theorem labeled
\texttt{introthvpspos}, restated in the applications section as
\texttt{corvpspostopotau}, proves that for every Polish operator topology on
$\PP(\elltwo)$ lying between $\WOT$ and $\SOTstar$, a typical positive
contraction $T$ has no eigenvalue and $T^*$ has no eigenvalue.  In particular,
for the $\SOT$ topology on $\PP(\elltwo)$,
\[
  \sigma_p(T)=\varnothing
\]
generically.  Thus the answer to Question 5.2 is negative: the point spectrum
is not $\D$.

The same paper's theorem labeled \texttt{introthtoposimsurl2} proves that
all Polish operator topologies between $\WOT$ and $\SOTstar$ are similar on
$\PP(\elltwo)$.  In particular $\SOT$ and $\SOTstar$ are similar on
$\PP(\elltwo)$, giving a positive answer to the $q=2$ subcase of the source
paper's final similarity question.

\section*{Scope Limitations}

This packet records a literature answer, not a new proof.  It does not settle
the invariant-subspace question for $1<q\ne 2<\infty$, the hypercyclicity of
$(2T)^*$ for $1<q<2$, the non-Hilbert similarity cases, the $\SOT$ version of
the reflexive-monotone-basis AAB theorem, or the compact-commutant question for
typical positive contractions on $\elltwo$.

\section*{Search Evidence}

The local run indexes had no prior row for arXiv:2409.14481.  Exact web and
local-source searches for the source title, Question 5.2, point spectrum of
typical positive contractions, and similar operator topologies found
arXiv:2412.11587 as the later answer.  The supporting paper explicitly names
Question 5.2 from the source paper, so the Question 5.2 part belongs in
the literature-already-answered bucket.

\end{document}
