\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\newcommand{\R}{\mathbb R}
\newcommand{\Lp}{L^p(\mathbb R)}
\newcommand{\Lq}{L^q(\mathbb R)}
\newcommand{\Cc}{C_c^\infty(\mathbb R)}

\title{A negative answer to the continuous same-sign Gabor ASF problem}
\author{agent\_lane\_14}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Source problem}

The source paper is K. Mahesh Krishna, \emph{The \((abc,pqr)\)-problem for
Approximate Schauder Frames for Banach Spaces}, arXiv:2201.04421.  At the end
of Section 2 it asks:

\begin{quote}
Let \(1<p<\infty\) and \(q\) be the conjugate index of \(p\). Characterize
functions \(g\in L^p(\mathbb R)\), \(h\in L^q(\mathbb R)\) such that the pair
\[
  (\{\widetilde E_b\widetilde T_a h\}_{a,b\in\mathbb R},
    \{E_bT_ag\}_{a,b\in\mathbb R})
\]
is a continuous approximate Schauder frame for \(L^p(\mathbb R)\).
\end{quote}

The same paper defines the dual pairing by
\[
   [x,\omega]=\int_{\mathbb R}x(t)\omega(t)\,dt
\]
and defines
\[
 (E_b f)(t)=e^{2\pi i bt}f(t),\qquad
 (T_a f)(t)=f(t-a),
\]
with the analogous same-sign definitions for \(\widetilde E_b,\widetilde T_a\)
on \(L^q\).  The continuous ASF definition used by the source paper is the one
in Krishna's arXiv:2201.00980: for every \(x\in X\) and \(\phi\in X^*\), the
coefficient product is measurable and integrable, and the Pettis frame operator
\[
 Sx=\int_\Omega f_\alpha(x)\tau_\alpha\,d\mu(\alpha)
\]
is bounded and invertible.

\section*{Result}

\begin{theorem}
Let \(1<p<\infty\), let \(q\) be conjugate to \(p\), and let
\(g\in L^p(\mathbb R)\), \(h\in L^q(\mathbb R)\).  With the same-sign
translation-modulation convention above, the pair
\[
  (\{\widetilde E_b\widetilde T_a h\}_{a,b\in\mathbb R},
    \{E_bT_ag\}_{a,b\in\mathbb R})
\]
is not a continuous approximate Schauder frame for \(L^p(\mathbb R)\).
\end{theorem}

\section*{Proof Intuition}

For Hilbert-space continuous Gabor frames, the analysis coefficient carries the
opposite phase from the synthesis vector.  In the source problem, both phases
have the same sign with respect to the \(L^p\)-\(L^q\) bilinear pairing.  When
one integrates over the full frequency line, this does not produce
\(\delta(t-s)\); it produces \(\delta(t+s)\).  Thus the putative frame operator
is forced to be reflection, \(x(s)\mapsto x(-s)\), followed by multiplication
by a correlation of \(h\) and \(g\).  That correlation is a \(C_0\)-function, so
it decays at infinity and cannot be bounded away from zero.  Hence the operator
cannot be invertible on \(L^p(\mathbb R)\).

\section*{Proof}

Assume, toward a contradiction, that the displayed pair is a continuous ASF.
Thus for all \(x\in L^p\) and all \(y\in L^q\), the scalar function
\[
 (a,b)\mapsto
 \left(\int_\R x(t)e^{2\pi i bt}h(t-a)\,dt\right)
 \left(\int_\R e^{2\pi i bs}g(s-a)y(s)\,ds\right)
\]
is integrable over \(\R^2\), and the Pettis integral defines a bounded
invertible operator \(S:L^p\to L^p\).

Fix \(x,y\in C_c^\infty(\mathbb R)\).  For fixed \(a\), set
\[
  u_a(t)=x(t)h(t-a),\qquad v_a(t)=y(t)g(t-a).
\]
Then \(u_a,v_a\in L^1(\mathbb R)\).  With the Fourier transform convention
\(\widehat f(\xi)=\int_\R f(t)e^{-2\pi i t\xi}\,dt\), the two coefficients are
\(\widehat u_a(-b)\) and \(\widehat v_a(-b)\).  By the continuous ASF
integrability hypothesis and Fubini's theorem, for almost every \(a\) the
product \(\widehat u_a(-b)\widehat v_a(-b)\) is integrable in \(b\).  For
\(L^1\)-functions whose Fourier-transform product is integrable, Fourier
inversion for the product gives
\[
 \int_\R \widehat u_a(-b)\widehat v_a(-b)\,db
 =\int_\R u_a(t)v_a(-t)\,dt .
\]
Therefore
\begin{align*}
 \langle Sx,y\rangle
 &= \int_\R\int_\R x(t)y(-t)h(t-a)g(-t-a)\,dt\,da  \\
 &= \int_\R x(t)y(-t)c(t)\,dt,
\end{align*}
where
\[
  c(t)=\int_\R h(t-a)g(-t-a)\,da
      =\int_\R h(u)g(u-2t)\,du .
\]
The interchange of the \(a\)- and \(t\)-integrals is justified by
\[
 \int_\R |h(t-a)g(-t-a)|\,da
 \le \|h\|_q\|g\|_p
\]
and the compact support of \(x(t)y(-t)\).

Thus, for every \(x,y\in C_c^\infty(\mathbb R)\),
\[
  \langle Sx,y\rangle=\int_\R c(-s)x(-s)y(s)\,ds.
\]
Since \(C_c^\infty\) is dense in \(L^q\), it follows that
\[
  (Sx)(s)=m(s)x(-s),\qquad m(s)=c(-s)=\int_\R h(u)g(u+2s)\,du
\]
for every \(x\in C_c^\infty(\mathbb R)\).

Now \(m\in C_0(\mathbb R)\).  Indeed, if \(\check g(r)=g(-r)\), then
\[
  c(t)=(h*\check g)(2t),
\]
and the standard \(L^q*L^p\subset C_0\) convolution fact applies for conjugate
\(p,q\) with \(1<p<\infty\).  In particular \(m\) is bounded and tends to zero
at infinity.

The operator \(x\mapsto m(\cdot)x(-\cdot)\) is bounded on \(L^p\).  Since it
agrees with \(S\) on the dense subspace \(C_c^\infty\), the boundedness of
\(S\) forces
\[
  Sx=m(\cdot)x(-\cdot)\qquad (x\in L^p(\mathbb R)).
\]
But no such operator is bounded below when \(m\in C_0(\mathbb R)\).  Given
\(\varepsilon>0\), choose a measurable set \(E\) of positive finite measure
outside a compact set on which \(|m|<\varepsilon\), and take
\(x=\mathbf 1_{-E}\).  Then
\[
 \|Sx\|_p=\|m\,\mathbf 1_E\|_p\le \varepsilon \|\mathbf 1_E\|_p
       =\varepsilon\|x\|_p .
\]
As \(\varepsilon\) is arbitrary, \(S\) is not bounded below, contradicting
invertibility.  This proves the theorem.

\section*{Verification and Limitations}

The argument proves a negative answer only for the continuous full-plane
problem as written in arXiv:2201.04421, using the source paper's same-sign
definition of \(\widetilde E_b\) on the dual side.  It does not address the
discrete \((abc,pqr)\)-problem, the discrete \((MN,PQ)\)-problem, or a modified
continuous Gabor problem with the opposite phase in the dual coefficient.

The proof is non-computational.  The only analytic inputs are the continuous ASF
integrability hypothesis, the elementary Fourier identity
\(\int \widehat u(\xi)\widehat v(\xi)\,d\xi=\int u(t)v(-t)\,dt\) when
\(u,v\in L^1\) and \(\widehat u\,\widehat v\in L^1\), and the standard
convolution inclusion \(L^q*L^p\subset C_0\).

\section*{Novelty Check}

The run indexes were searched for arXiv:2201.04421 and the keywords
`abc', `pqr', `approximate Schauder frame', `continuous approximate Schauder
frame', and `Gabor'.  Adjacent frame packets were found, but no packet for this
paper.  Web searches on 2026-06-28 for exact phrases including
`abc,pqr approximate Schauder frames', `continuous approximate Schauder frame
Gabor Lp', and `tilde E tilde T approximate Schauder frame Lp' found the source
arXiv page and the Eisner--Freeman continuous Schauder frame paper, but no later
answer to this same-sign continuous formulation.

\section*{References}

\begin{enumerate}
\item K. Mahesh Krishna, \emph{The \((abc,pqr)\)-problem for Approximate
Schauder Frames for Banach Spaces}, arXiv:2201.04421,
\url{https://arxiv.org/abs/2201.04421}.
\item K. Mahesh Krishna, \emph{Discrete and continuous Welch bounds for Banach
spaces with applications}, arXiv:2201.00980.
\item Joseph Eisner and Daniel Freeman, \emph{Continuous Schauder frames for
Banach spaces}, arXiv:1812.08360.
\end{enumerate}

\section*{Human Review Recommendation}

Review as a likely valid counterexample/negative solution to the continuous
problem in arXiv:2201.04421.  The key convention to verify is that the source
paper's dual pairing is bilinear, \([x,\omega]=\int x\omega\), and its dual
modulation \(\widetilde E_b\) has the same sign as \(E_b\).

\end{document}
