\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}

\title{Literature Status: Daws--Runde's \(B(\ell^p)\) Amenability Question}
\author{run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_06}}
\date{2026-07-18}

\begin{document}
\maketitle

\section*{Status}

\textbf{Status: literature already answered.} The source paper is Matthew
Daws and Volker Runde, \emph{Can \(B(\ell^p)\) ever be amenable?},
arXiv:0711.4311, Studia Mathematica 188 (2008), 151--174. The supporting
answer is Volker Runde, \emph{\(B(\ell^p)\) is never amenable},
arXiv:0907.3984, J. Amer. Math. Soc. 23 (2010), 1175--1185.

\section*{Source Question}

The abstract and introduction of arXiv:0711.4311 record the then-open problem:
\[
  \text{is } {\cal B}(\ell^p) \text{ amenable for }
  p\in (1,\infty)\setminus\{2\}?
\]
The paper proves consequences of a hypothetical positive answer. In particular,
it shows that amenability of \({\cal B}(\ell^p)\) would imply amenability of
\(\ell^\infty({\cal B}(\ell^p))\) and \(\ell^\infty({\cal K}(\ell^p))\), and
it develops a dichotomy for \(\ell^\infty({\cal K}(E))\) over
infinite-dimensional \({\cal L}^p\)-spaces.

\section*{Answering Paper}

Runde's later paper arXiv:0907.3984 explicitly addresses this same line of
questions. Its abstract states that
\[
  \ell^\infty({\cal K}(\ell^2\oplus E))
\]
is not amenable for a class of spaces including \(E=\ell^p\),
\(p\in(1,\infty)\). It further states the consequence that
\(\ell^\infty({\cal K}(E))\) is not amenable for every infinite-dimensional
\({\cal L}^p\)-space \(E\), and hence that \({\cal B}(\ell^p(E))\) is not
amenable for any \({\cal L}^p\)-space \(E\). Taking \(E=\mathbb C\) gives
non-amenability of \({\cal B}(\ell^p)\) for the open range from the source
paper.

\section*{Scope}

This clears the main open problem in arXiv:0711.4311 and the main
\(\ell^\infty({\cal K}(E))\) side frontier for \({\cal L}^p\)-spaces. It does
not settle Johnson's general problem asking whether \({\cal B}(E)\) can be
amenable for some infinite-dimensional Banach space \(E\), nor the fully
general abstract question whether amenability of \(\ell^\infty(A)\) forces
amenability of \(A^{**}\) with an Arens product.

\section*{Run Note}

The run already contains a related literature-status packet for Ozawa's earlier
formulation. This packet records the direct answer relation for the later
Daws--Runde source and its stronger \(\ell^\infty({\cal K}(E))\) side
questions.

\end{document}
