\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: Sharp Covering-Index Decay for Schatten Classes}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 19 June 2026

\noindent Status: Manually checked, focusing on Theorem 1.

\noindent Verdict: The proof of Theorem 1 appears correct.

\section*{Human Comments}

I have checked Theorem 1 of the packet, which appears to be the new technical
addition in the solution.  The theorem proves the upper estimate
\[
  \Theta_{S_p(H)}(n)\le n^{-1/p}
\]
for the classical Schatten classes by constructing an explicit cover of the
unit ball by the sets
\[
  A_k=\{T\in B_{S_p(H)}:\|P_kTP_k\|_p\le n^{-1/p}\}.
\]
The argument looks correct.

The covering step is clear.  The finite pinching
\[
  E(T)=\sum_{k=1}^n P_kTP_k
\]
is written as an average of unitary conjugates of \(T\).  Since Schatten norms
are unitarily invariant and convex, \(\|E(T)\|_p\le \|T\|_p\).  As \(E(T)\) is
block diagonal, this gives
\[
  \sum_{k=1}^n \|P_kTP_k\|_p^p\le 1
\]
for \(T\in B_{S_p(H)}\), so at least one diagonal block has norm at most
\(n^{-1/p}\).  Hence the sets \(A_k\) cover the unit ball.

The computation of the essential inradius of each \(A_k\) also appears
correct.  The easy inequality \(\varrho(A_k)\ge n^{-1/p}\) follows from
\(n^{-1/p}B_{S_p(H)}\subseteq A_k\).  For the reverse inequality, the proof
uses a finite-codimensional subspace
\[
  Y=\bigcap_{j=1}^m\ker\Phi_j
\]
and represents the functionals \(\Phi_j\) by trace-duality operators
\(B_j\).  One then chooses a rank-one operator \(W=\theta_{u,v}\) supported in
the infinite-dimensional tail of the \(k\)-th block, with
\[
  \langle B_j u,v\rangle=0\qquad(j=1,\\dots,m),
\]
so that \(W\in Y\).  This is the key finite-codimensional tail argument.

The use of a finite-rank projection \(R\le P_k\) is sound.  Since finite-rank
compressions approximate \(V=P_kTP_k\) in Schatten norm, one can choose \(R\)
so that
\[
  \bigl(\|RVR\|_p^p+r^p\bigr)^{1/p}-\|V-RVR\|_p>n^{-1/p}
\]
for every \(r>n^{-1/p}\).  Then \(RVR\) and the chosen rank-one perturbation
\(rW\) live on orthogonal summands, so
\[
  \|RVR+rW\|_p^p=\|RVR\|_p^p+r^p.
\]
The reverse triangle inequality then gives
\[
  \|P_k(T+rW)P_k\|_p>n^{-1/p},
\]
and therefore \(T+rW\notin A_k\).  This proves
\(\varrho(A_k)\le n^{-1/p}\), completing Theorem 1.

\section*{Minor Amendment}

There is one small wording issue in the proof.  The sentence saying that the
left-hand side tends to
\[
  (\|V\|_p^p+r^p)^{1/p}>r>n^{-1/p}
\]
should be slightly weakened.  If \(V=0\), then
\[
  (\|V\|_p^p+r^p)^{1/p}=r,
\]
not strictly larger than \(r\).  The correct statement is
\[
  (\|V\|_p^p+r^p)^{1/p}\ge r>n^{-1/p},
\]
which is fully sufficient for the argument.

\section*{Relation to the Lower Bound}

The matching lower bound in the later sharp-decay statement seems essentially
to come from the work of Kania--Ma\'slany/Raja.  Namely, the diagonal copy of
\(\ell_p\) inside \(S_p(H)\) is contractively complemented, and the monotonicity
of the covering index under contractively complemented subspaces transfers
the known scalar lower estimate to the Schatten class.  Thus the genuinely new
technical point in the packet appears to be Theorem 1, i.e. the explicit
Schatten upper-bound cover and the verification of the exact essential
inradius of its pieces.

\section*{Review Outcome}

Approve this packet as an apparently correct solution of the classical
Schatten sharp-decay problem, with the minor inequality wording correction
above.  The proof of Theorem 1 appears correct, and the lower-bound side is
consistent with the existing Kania--Ma\'slany/Raja machinery.

\end{document}
