\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}

\newcommand{\ellTwo}{\ell_2}
\newcommand{\K}{\mathscr K}
\newcommand{\Id}{\mathrm{Id}}

\title{A Range-Complemented Counterexample to a Compatibility Question}
\author{Run \texttt{fa\_banach\_001}, agent \texttt{agent\_lane\_14}}
\date{2026-07-03}

\begin{document}
\maketitle

\section*{Source Question}

Castillo, Cuellar, Ferenczi, and Moreno ask in Problem 3 of
\emph{Complex structures on twisted Hilbert spaces} \cite{CCFM}:

\begin{quote}
Assume $\Omega:\ell_2\to \ell_2$ is a singular quasi-linear map, and that
$T,U$ are bounded linear operators on $\ell_2$ such that $(T,U)$ is compatible
with $\Omega$. Does it follow that $T-U$ is compact?
\end{quote}

Here compatibility means $T\Omega \equiv \Omega U$, i.e. the difference is
the sum of a bounded homogeneous map and a linear map. We use the standard
equivalent formulation that a quasi-linear map is singular when it is
nontrivial on every infinite-dimensional subspace of its domain.

\section*{Idea of the Proof}

The compactness conclusion is false for a very simple reason: the statement
does not require the range of $\Omega$ to be essential in the target copy of
$\ell_2$. Put a singular quasi-linear map into a complemented half of
$\ell_2$. The projection onto the other half annihilates $\Omega$, hence is
compatible with the zero operator on the domain, but that projection is not
compact.

\section*{Counterexample}

\begin{theorem}
Problem 3 has a negative answer as stated. There exist a singular
quasi-linear map $\Omega:\ell_2\to\ell_2$ and bounded operators
$T,U:\ell_2\to\ell_2$ such that $(T,U)$ is compatible with $\Omega$, while
$T-U$ is not compact.
\end{theorem}

\begin{proof}
Let $\K:\ell_2\to\ell_2$ be the Kalton--Peck quasi-linear map
\[
  \K(x)=x\log\frac{|x|}{\|x\|_2},
\]
with the usual coordinatewise interpretation and $\K(0)=0$. This is a
singular quasi-linear map, as recalled in the source paper before Corollary
4.6.

Decompose $\ell_2$ as the direct sum of its even and odd coordinate subspaces,
\[
  \ell_2 = H_{\mathrm{even}}\oplus H_{\mathrm{odd}}.
\]
Let $J:\ell_2\to H_{\mathrm{even}}$ be the isometric embedding
$J e_n=e_{2n}$, and let $R:\ell_2\to\ell_2$ be the bounded left inverse
defined by $R e_{2n}=e_n$ and $R e_{2n-1}=0$. Define
\[
  \Omega=J\K:\ell_2\to\ell_2.
\]
Since $J$ is bounded linear and $\K$ is quasi-linear, $\Omega$ is
quasi-linear.

We first check that $\Omega$ is singular. Suppose that $\Omega$ were trivial
on an infinite-dimensional subspace $E\subset \ell_2$. Then for some linear
map $L:E\to\ell_2$ and bounded homogeneous map $B:E\to\ell_2$ we would have
$\Omega|_E=L+B$. Applying $R$ gives
\[
  \K|_E = R\Omega|_E = RL + RB,
\]
where $RL$ is linear and $RB$ is bounded homogeneous. Thus $\K$ would be
trivial on $E$, contradicting the singularity of the Kalton--Peck map.
Therefore $\Omega$ is singular.

Let $T=P_{\mathrm{odd}}$ be the coordinate projection onto
$H_{\mathrm{odd}}$, and let $U=0$. Then
\[
  T\Omega = P_{\mathrm{odd}}J\K =0
  \qquad\text{and}\qquad
  \Omega U=\Omega 0=0.
\]
Hence $(T,U)$ is compatible with $\Omega$, even with equality rather than just
equivalence.

Finally, $T-U=P_{\mathrm{odd}}$ is not compact: it fixes the orthonormal
sequence $(e_{2n-1})_{n\ge 1}$, which has no norm-convergent subsequence.
This completes the counterexample.
\end{proof}

\section*{Verification Notes}

The proof uses only two standard facts: the Kalton--Peck map is singular, and
singularity is preserved by postcomposition with an isomorphic embedding whose
range has a bounded left inverse. The construction does not rely on any
unproved property of $Z_2$.

\section*{Scope and Limitations}

This answers only the arbitrary singular quasi-linear-map Problem 3. The
construction is deliberately not a centralizer counterexample, and it does not
address the subsequent source questions about exact sequences representing
$Z_2$, singular centralizers on $\ell_2$, compatible complex structures on
hyperplanes of derived spaces, or uniqueness of complex structure on $Z_2$.

\section*{Novelty Check}

The run indexes were searched for the arXiv id, title, Kalton--Peck,
singular quasi-linear maps, compatible pairs, and compactness of $T-U$. No
duplicate packet or attempt for this source problem was found. Bounded web
searches for exact phrases from the problem and for
\texttt{Kalton-Peck compatible T-U compact} did not surface a later answer or
the range-complemented counterexample recorded here.

\begin{thebibliography}{9}

\bibitem{CCFM}
J. M. F. Castillo, W. Cuellar, V. Ferenczi, and Y. Moreno,
\emph{Complex structures on twisted Hilbert spaces},
arXiv:1511.05867.

\bibitem{KP}
N. J. Kalton and N. T. Peck,
\emph{Twisted sums of sequence spaces and the three space problem},
Transactions of the American Mathematical Society 255 (1979), 1--30.

\end{thebibliography}

\end{document}
