\documentclass[11pt]{article}
\usepackage[margin=1.05in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage[hidelinks]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

\newcommand{\R}{\mathbb{R}}
\newcommand{\ellinf}{\ell_\infty}
\newcommand{\elltwo}{\ell_2}
\newcommand{\ellone}{\ell_1}
\newcommand{\op}{\operatorname{op}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\lmax}{\lambda_{\max}}
\newcommand{\gammatwo}{\gamma_2}
\newcommand{\Id}{I}

\title{An SDP Formula for the \texorpdfstring{$\gamma_2$}{gamma2} Norm on
\texorpdfstring{$\ell_\infty^n\otimes \ell_2^m$}{ell-infinity tensor ell-2}}
\author{Run \texttt{fa\_banach\_001}, lane 14}
\date{2026-06-28}

\begin{document}
\maketitle

\section*{Status}

\textbf{Claimed full answer, likely valid.}
The source paper asks, in Section 3 before introducing the mixed norm, whether
the norm $\gamma_2$ on $\ell_\infty^n\otimes \ell_2^m$ can be computed easily as a
standard convex optimization problem.  The answer is yes: it has a polynomial-size
semidefinite programming formula.

\section*{Source Question}

The target is the following passage from Lee--Srinivasa--Junge--Romberg,
\emph{Approximately low-rank recovery from noisy and local measurements by convex
program}, arXiv:2110.15205, Section 3:
\begin{quote}
Although Lemma 3.1 also applies to $\ell_\infty^n\otimes \ell_2^m$, it has not
been known whether the $\gamma_2$ norm on $\ell_\infty^n\otimes \ell_2^m$ can be
computed easily as a standard convex optimization problem.
\end{quote}

The paper then uses a different tensor norm, the mixed norm, because that norm is
shown there to have an SDP formulation.  The theorem below gives the missing SDP
formulation for $\gamma_2$ itself.

\section*{Definitions}

Let $M\in\R^{m\times n}$ be viewed as an operator
$M:\ell_1^n\to\ell_2^m$, equivalently as an element of
$\ell_\infty^n\otimes \ell_2^m$.  Its Hilbert factorization norm is
\[
\gamma_2(M)=
\inf\left\{\|A\|_{2\to2}\,\|B\|_{\ell_1^n\to\ell_2^d}:
d\in\mathbb N,\ A:\ell_2^d\to\ell_2^m,\ B:\ell_1^n\to\ell_2^d,\ M=AB
\right\}.
\]
If $B=[b_1\ \cdots\ b_n]$, then
\[
\|B\|_{\ell_1^n\to\ell_2^d}=\max_{1\le j\le n}\|b_j\|_2.
\]

\section*{Proof Intuition}

The usual max-norm SDP for $\ell_\infty^n\otimes \ell_\infty^m$ is just a Gram
matrix encoding of two Hilbert families.  In the present asymmetric case the
right-hand factor is still controlled column-by-column, but the left factor is
an operator into Euclidean space.  Thus the right Gram matrix only needs bounded
diagonal entries, while the left Gram matrix must be bounded in Loewner order by
$t I_m$.  Scaling the two factors balances their two bounds at the same value
$t$, turning the product norm into a linear SDP objective.

\section*{Theorem}

\begin{theorem}
For every real matrix $M\in\R^{m\times n}$,
\[
\gamma_2(M)=\min t
\]
where the minimum is taken over $t\ge0$ and symmetric matrices
$P\in\R^{m\times m}$, $Q\in\R^{n\times n}$ satisfying
\[
\begin{pmatrix}
P & M\\
M^T & Q
\end{pmatrix}\succeq 0,\qquad
P\preceq t I_m,\qquad
Q_{jj}\le t\quad(1\le j\le n).
\]
Equivalently,
\[
\gamma_2(M)=
\inf\left\{
\max\{\lambda_{\max}(P),\max_j Q_{jj}\}:
\begin{pmatrix}P&M\\M^T&Q\end{pmatrix}\succeq0
\right\}.
\]
In particular $\gamma_2$ on
$\ell_\infty^n\otimes\ell_2^m$ is computable by a standard semidefinite program.
\end{theorem}

\begin{proof}
First suppose $M=AB$, where
$A:\ell_2^d\to\ell_2^m$ and $B:\ell_1^n\to\ell_2^d$.  Write
$b_j=Be_j$.  Put $a=\|A\|_{2\to2}$ and
$b=\max_j\|b_j\|_2$.  If $M\ne0$, rescale the factorization by replacing
$A$ with $\widetilde A=(b/a)^{1/2}A$ and $B$ with
$\widetilde B=(a/b)^{1/2}B$; if $a=0$ or $b=0$, then $M=0$ and the formula is
trivial.  The rescaled factorization still satisfies $M=\widetilde A\widetilde
B$, and
\[
\|\widetilde A\|_{2\to2}^2=ab,\qquad
\max_j\|\widetilde B e_j\|_2^2=ab.
\]
Set
\[
P=\widetilde A\widetilde A^T,\qquad
Q=\widetilde B^T\widetilde B .
\]
Then
\[
\begin{pmatrix}
P&M\\M^T&Q
\end{pmatrix}
=
\begin{pmatrix}
\widetilde A\\
\widetilde B^T
\end{pmatrix}
\begin{pmatrix}
\widetilde A^T&\widetilde B
\end{pmatrix}\succeq0,
\]
while $P\preceq ab\,I_m$ and $Q_{jj}\le ab$ for all $j$.  Taking the infimum
over all factorizations gives that the SDP value is at most $\gamma_2(M)$.

Conversely, suppose that $P,Q,t$ are feasible.  Since the block matrix is
positive semidefinite, it is the Gram matrix of vectors
$x_1,\ldots,x_m,y_1,\ldots,y_n$ in some finite-dimensional Hilbert space $H$:
\[
P_{ik}=\langle x_i,x_k\rangle,\qquad
M_{ij}=\langle x_i,y_j\rangle,\qquad
Q_{jl}=\langle y_j,y_l\rangle.
\]
Define $A:H\to\ell_2^m$ by
$Ah=(\langle h,x_i\rangle)_{i=1}^m$ and define
$B:\ell_1^n\to H$ by $Be_j=y_j$.  Then $AB=M$.  Moreover
\[
\|A\|_{2\to2}^2=\|AA^*\|_{2\to2}=\|P\|_{2\to2}\le t
\]
and
\[
\|B\|_{\ell_1^n\to H}=\max_j\|y_j\|=\max_j Q_{jj}^{1/2}\le t^{1/2}.
\]
Thus $\gamma_2(M)\le t$.  Taking the infimum over feasible triples gives the
reverse inequality.
\end{proof}

\section*{Verification Notes}

The proof is finite-dimensional and uses only the standard Gram factorization
criterion for positive semidefinite block matrices.  The SDP has variables
$t$, $P$, and $Q$ and uses only linear matrix inequalities:
\[
\begin{pmatrix}P&M\\M^T&Q\end{pmatrix}\succeq0,\qquad
tI_m-P\succeq0,\qquad Q_{jj}\le t.
\]
Hence it is a standard semidefinite program in the usual sense.

\begin{remark}
The formula differs from the mixed-norm SDP in the source paper exactly where
the left Hilbert factor is measured.  The mixed norm uses a Frobenius/trace
bound on the left Gram matrix; $\gamma_2$ uses the spectral/Loewner bound
$P\preceq tI_m$.
\end{remark}

\section*{Limitations and Novelty Check}

This packet answers only the computability question for the $\gamma_2$ norm.
It does not claim that substituting this norm into the source paper's estimator
automatically preserves the same statistical error analysis; that would require
fresh entropy estimates for the corresponding SDP ball.

Cheap run-index searches found no prior packet for arXiv:2110.15205 or for the
phrases ``$\gamma_2$'', ``$\ell_\infty^n\otimes\ell_2^m$'', and semidefinite
computability.  Web searches on 2026-06-28 for
\texttt{gamma\_2 ell\_infty ell\_2 semidefinite programming},
\texttt{gamma\_2 norm SDP ell\_2 ell\_infty}, and related factorization-norm
queries found the standard max-norm/$\ell_\infty\otimes\ell_\infty$ SDP but no
explicit formula for this asymmetric $\ell_\infty\otimes\ell_2$ case.

\section*{Human Review Recommendation}

Review as a short full solution to the source paper's explicit computability
question.  The main points to check are the orientation convention for
$\ell_\infty^n\otimes\ell_2^m$ as operators $\ell_1^n\to\ell_2^m$, and the
balanced rescaling step converting the factorization product into one SDP
scalar $t$.

\begin{thebibliography}{9}
\bibitem{LSJR}
K. Lee, R. S. Srinivasa, M. Junge, and J. Romberg,
\emph{Approximately low-rank recovery from noisy and local measurements by
convex program}, arXiv:2110.15205.

\bibitem{Srebro}
N. Srebro, J. D. M. Rennie, and T. S. Jaakkola,
\emph{Maximum-margin matrix factorization}, Advances in Neural Information
Processing Systems 17, 2004.
\end{thebibliography}

\end{document}
