\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage[hidelinks]{hyperref}

\begin{document}

\section*{Human Review: \(\tau_\infty\)-Density Without \(p\)-OAP}

\noindent Original automatic proof: \texttt{solution\_packet.pdf}

\noindent Checked date: 14 June 2026

\noindent Status: Rejected after a second AI pass; not independently verified by the human reviewer.

\noindent Verdict: This packet should not be treated as a verified solution. A second AI review identified a serious gap in the key density lemma. The human reviewer did not directly verify the full argument independently.

\section*{Reason for Rejection}

The proposed proof rests on the lemma claiming that, for arbitrary operator spaces \(W,V\),
\[
\mathcal F(W,V)
\]
is \(\tau_{\mathrm{cc}}\)-dense in \(\mathcal{CB}(W,V)\), and hence also \(\tau_\infty\)-dense.

The second AI pass identified a gap in the proof of this lemma. The argument chooses, for a completely compact matrix set, a finite-dimensional subspace \(E\subseteq W\) which approximates the test set within some tolerance \(\delta\). It then chooses a finite-rank completely bounded map
\[
P:W\to E
\]
with \(P|_E=\mathrm{id}_E\), and estimates
\[
\|(T-T\circ P)_n x\|
\leq
\|T\|_{\mathrm{cb}}(1+\|P\|_{\mathrm{cb}})\delta.
\]
The problem is that the projection \(P\), and especially its completely bounded norm \(\|P\|_{\mathrm{cb}}\), depends on the finite-dimensional space \(E\). But \(E\) itself was chosen depending on \(\delta\). Thus the final instruction to choose
\[
\delta < \frac{\varepsilon}{\|T\|_{\mathrm{cb}}(1+\|P\|_{\mathrm{cb}})}
\]
is circular.

Complete compactness gives approximation by finite-dimensional subspaces, but it does not provide finite-rank projections onto those subspaces with uniformly controlled completely bounded norm. This is analogous to the classical false argument that every Banach space has the approximation property: compact sets can be approximated by finite-dimensional subspaces, but without controlled projections this does not yield finite-rank approximation of the identity.

\section*{Scope of This Review}

This note records a rejection after a second pass by the AI model. It should not be read as a direct independent human verification of all details by Antonio Acuaviva. Rather, the packet is being reclassified because the second AI pass found a serious and plausible obstruction in the central lemma.

\section*{Review Outcome}

Rejected. The proposed solution does not currently prove the claimed answer to the source question. Unless the projection-norm problem can be repaired by an additional argument or by a different construction, this packet should be excluded from the verified examples.

\end{document}
